### 2014-06-06 R compile notebooks/sla.Rmd
copied all data and scripts to repo folder for new project, backup on google drive

Summary stats for leaf mass area
========================================================

```{r,include=FALSE}
#source functions and packages
source("functions and packages/functions.R")
source("functions and packages/load packages.R")
```

```{r}
#read in plot design, lma data, merge
plotsumm <- read.csv("raw data/plot_summary.csv")
plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")

lma <- read.csv("raw data/seedling leaf mass area.csv")
lma$ID <- paste(lma$plot, lma$pot, sep = "-")
lma <- merge(lma, plotsumm[3:4], all=TRUE)
lma$volume <- as.factor(lma$volume)

#run function to add campaign dates, caluclate sla
lma <- add_campaign_date(lma)
lma$sla <- with(lma, area/mass)

#remove missing values
lma_noNA <- subset(lma, !is.na(sla))

#subset with only sla and parameters of lm
lma_lm <- subset(lma_noNA, select = c("ID", "volume", "campaign", "sla"))
#----------------------------------------------------------------------------------------------
#Visualize changes in SLA across campaigns (Date messes things up so stay with campaign# (interval=2wks))

#function to create groupData set
grp_func <- function(dfr){

  sub_dfr <- subset(dfr, select = c("ID", "campaign", "sla"))
  lma.new <- groupedData(sla ~ campaign|ID, data=sub_dfr)
}
#create groupdData objects by volume
groupData_ls<- dlply(lma_lm, .(volume) , grp_func)
#generate trellis plots
lapply(groupData_ls, plot)

#----------------------------------------------------------------------------------------------
#fit seperate linear regression models for each pot through time, grouped by volume
LMlist_func <- function(dfr){

  sub_dfr <- subset(dfr, select = c("ID", "campaign", "sla"))
  lma.new <- groupedData(sla ~ campaign|ID, data=sub_dfr)
  models_ID <- lmList(sla ~ campaign,  data=lma.new)
}

#run LMlist for all pots, split by volume
sla_stats_ls<- dlply(lma_lm, .(volume) , LMlist_func)

#return coefs and CI(need to add a 'ID' name column)
ldply(sla_stats_ls, coef)
#plot confidence intervals
lapply(sla_stats_ls, function(x) plot(intervals(x)))

```

### 2014-06-06 Scripts/WP_photosyn.R

@@ -1,0 +1,56 @@
+setwd("C:/Users/90919620/Google Drive/EucPVE/R Database")
+
+library(sciplot)
+
+#Read in spot measurements 
+WPgasexchange <- read.csv("WP_gasexchange.csv")
+WPgasexchange$ID <- paste(WPgasexchange$plot, WPgasexchange$pot, sep = "-")
+WP_photo <-  aggregate(cbind(Photo, Cond, Ci, Trmmol) ~ ID, data=WPgasexchange, FUN=mean)
+
+#water potential
+WP <- read.csv("waterpotential.csv")
+WP$ID <- paste(WP$plot, WP$pot, sep = "-")
+WP$predawn <- with(WP, ((bar_pre/10)*-1))
+WP$peak <- with(WP, ((bar_peak/10)*-1))
+WP <- subset(WP, !is.na(WP$bar_pre))
+
+WP_PS <- merge(WP, WP_photo)
+
+#plot design
+plotsumm <- read.csv("plot_summary.csv")
+plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
+
+WP_PS <- merge(WP_PS, plotsumm)
+
+#factor designations
+WP_PS$volume <- as.factor(WP_PS$volume)
+
+WP_PS$WPdiff <- with(WP_PS, predawn - peak)
+WP_PS$K <- with(WP_PS,Trmmol/WPdiff)
+
+WP_trt <- aggregate(cbind(K, Trmmol, Photo, Ci, Cond, predawn, peak) ~ volume, data=WP_PS, FUN=mean)
+
+
+#plot
+leglab <- c(5, 10, 15, 20, 25, 35, "free")
+palette <- c("red", "orange", "yellow", "green", "blue", "purple", "black")
+
+                        
+with(WP_PS, bargraph.CI(volume, K, ylim=c(-0.5,0), border="blue"))
+box()
+    
+with(WP_PS, bargraph.CI(volume, Photo, border="blue"))
+box()
+
+with(WP_PS, plot(Trmmol, peak, 
+                 ylim=c(-3,0)))
+
+
+plot(peak~Trmmol, ylim=c(-3,0), xlim=c(0, 7.5),pch=16, col=volume, data=WP_PS)
+
+legend("topright", leglab, lty = 1, lwd = 2, col = palette(), 
+       title = expression(Pot ~ volume ~ (l)), inset = 0.01, bty = "n")
+
+
+
+

### 2014-06-06 Scripts/stopgrow.R

@@ -1,0 +1,90 @@
+library(reshape)
+library(RColorBrewer)
+library(doBy)
+library(sciplot)
+
+#read in plot design
+plotsumm <- read.csv("plot_summary.csv")
+plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
+
+#HEIGHT
+height <- read.csv("seedling height.csv")
+
+#format data
+height <- melt(height, id=c("plot", "pot"))
+height$variable <- gsub ("X", "", height$variable)
+names(height)[3:4] <- c("Date", "height")
+height$Date <- as.Date(height$Date, format = "%m.%d.%Y")
+height <- subset(height, !is.na(height))
+height$ID <- paste(height$plot, height$pot, sep = "-")
+
+#merge with plot summary
+height <- merge(height, plotsumm, by = c("pot", "plot", "ID"))
+height$volume <- as.factor(height$volume)
+
+#order date for clarity
+dateorder<-order(height$ID, by=height$Date)
+height <- height[dateorder,]
+
+
+allNheight<-list()
+
+#make a loop to caluclate normailized height
+for (i in unique(height$ID)) {
+  treeid <- subset(height, ID == i)  
+  timax <- max(treeid$height)
+  Nheight <- treeid$height/timax
+allNheight[[i]] <- Nheight
+}
+
+normalH <- do.call(cbind, allNheight)
+
+#transpose normalH so I can merge them with height
+normalH <- melt(normalH, id=c("ID", "Nheight"))
+names(normalH)[2:3] <- c("ID", "Nheight")
+
+#add new variable to the height dfr, should be in correct date order
+heightstop <- cbind(height, normalH[3])
+
+
+###now I have the  normalized height
+###approx to determine when 95% growth stopped
+
+#first I create a column for the x axis that has the lenght of the experiment in days
+heightstop$durationday <- with(heightstop, Date - min(Date))
+heightstop$durationday <- as.numeric(heightstop$durationday)
+
+
+stopgrowth <-list()
+
+for (i in unique(heightstop$ID)) {
+  treeid <- subset(heightstop, ID == i)
+  growthdone <- approx(treeid$Nheight, treeid$durationday, xout=0.95)
+  stopgrowth[[i]] <- growthdone
+  
+}
+
+datestop <- do.call(rbind, stopgrowth)
[…]

### 2014-06-06 Scripts/stopleaf.R

@@ -1,0 +1,48 @@
+library(reshape)
+library(RColorBrewer)
+library(doBy)
+library(sciplot)
+
+#read in plot design
+plotsumm <- read.csv("plot_summary.csv")
+plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
+
+#LEAF COUNT
+leafno <- read.csv("seedling leaf count.csv")
+
+#format data
+leafno$X1.21.2013   <- as.integer(leafno$X1.21.2013)
+leafno <- melt(leafno, id=c("plot", "pot"))
+names(leafno)[3:4] <- c("Date", "count")
+leafno$Date <- gsub ("X", "", leafno$Date)
+leafno$Date <- as.Date(leafno$Date, format = "%m.%d.%Y")
+leafno <- subset(leafno, !is.na(count))
+leafno$ID <- paste(leafno$plot, leafno$pot, sep = "-")
+leafno$count <- as.numeric(leafno$count)
+
+#merge with plot summary and sort
+leafno <- merge(leafno, plotsumm, by = c("pot", "plot", "ID"))
+leafno$volume <- as.factor(leafno$volume)
+
+#order date for clarity
+dateorder<-order(leafno$ID, by=leafno$Date)
+leafno <- leafno[dateorder,]
+
+allNleafno<-list()
+
+#make a loop to caluclate normailized height
+for (i in unique(leafno$ID)) {
+  treeid <- subset(leafno, ID == i)  
+  timax <- max(treeid$count)
+  Nleaf <- treeid$count/timax
+  allNleafno[[i]] <- Nleaf
+}
+
+normalH <- do.call(cbind, allNleafno)
+
+
+
+
+
+
+

### 2014-06-06 Stats/Photo_TNC.R

@@ -1,0 +1,147 @@
+source("functions and packages/functions.R")
+source("functions and packages/load packages.R")
+source("functions and packages/plot objects.R")
+
+#read in Asat and leaf Ndata, merge
+Amax <- read.csv("calculated data/Amax.csv")
+Asat <- read.csv("calculated data/Asat.csv")
+leaf_tnc <- read.csv("calculated data/leaf_tnc.csv")
+
+Asat_starch <- merge(Asat[, c(1:2,5:6,9)], leaf_tnc)
+Asat_starch$volume <- as.factor(Asat_starch$volume)
+
+Amax_starch <- merge(Amax[, c(1:2,5:6,9)], leaf_tnc)
+Amax_starch$volume <- as.factor(Amax_starch$volume)
+#--------------------------------------------------------------------------------------
+#calculate overall means and means for each date
+
+#means(all dates)
+Amax_starch_agg <- summaryBy(Photo+leafstarch+percstarch ~ volume, FUN=c(mean, se), 
+                             keep.names=TRUE, data=Amax_starch)
+
+Asat_starch_agg <- summaryBy(Photo+leafstarch+percstarch ~ volume, FUN=c(mean, se), 
+                             keep.names=TRUE, data=Asat_starch)
+
+
+#means(campaign)
+Asat_starch_campaign <- summaryBy(Photo+leafstarch+percstarch ~ campaign + volume, FUN=c(mean, se), 
+                                  keep.names=TRUE, data=Asat_starch)
+
+Amax_starch_campaign <- summaryBy(Photo+leafstarch+percstarch ~ campaign + volume, FUN=c(mean, se), 
+                                  keep.names=TRUE, data=Amax_starch)
+
+#---------------------------------------------------------------------------------------
+#plot stuff
+manX <- seq(0, 18, 3)
+meanX <- seq(0, 18, 3)
+#---------------------------------------------------------------------------------------
+#panel graph for each relationship with raw, overall mean, and mean by date
+
+
+#Amax and starch%
+windows(10,10)
+par(mfrow=c(2,2))
+
+#raw
+plot(Photo ~ percstarch, data = Amax_starch, col=volume, ylim=c(0,50), xlim=c(0, 20), pch=pchs[volume], ylab="", 
[…]

### 2014-06-06 Stats/SLA_TNCfree_stats.R

@@ -1,0 +1,134 @@
+#Does TNC-free LMA change through time within a container volume?
+
+#source functions and packages
+source("functions and packages/functions.R")
+source("functions and packages/load packages.R")
+source("functions and packages/plot objects.R")
+
+#read in plot design, lma data, merge
+plotsumm <- read.csv("raw data/plot_summary.csv")
+plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
+
+lma <- read.csv("raw data/seedling leaf mass area.csv")
+lma$ID <- paste(lma$plot, lma$pot, sep = "-")
+lma <- merge(lma, plotsumm[3:4], all=TRUE)
+lma$volume <- as.factor(lma$volume)
+
+#run function to add campaign dates, caluclate sla
+lma <- add_campaign_date(lma)
+
+#remove missing values
+lma_noNA <- subset(lma, !is.na(area))
+
+#read in TNC data, substract mass of TNC from mass of leaves and then calculate TNC-free SLA
+#Read in spot measurements and merge plot design
+TNC <- read.csv("raw data/TNC.csv")
+
+#run function to add campaign Date
+TNC <- add_campaign_noID(TNC)
+TNC$volume <- as.factor(TNC$volume)
+TNC$tnc_mgperg <- with(TNC, starch_mgperg+sugar_mgperg)
+
+SLA_TNCfree <- merge(lma, TNC)
+
+SLA_TNCfree$mass_noTNC <- with(SLA_TNCfree, mass-((mass*tnc_mgperg)/1000))
+#TNC free sla and lma
+SLA_TNCfree$sla_free <- with(SLA_TNCfree, area/mass_noTNC)
+SLA_TNCfree$lma_free <- with(SLA_TNCfree, mass_noTNC/area)
+
+#remove missing values
+SLA_TNCfree_noNA <- subset(SLA_TNCfree, !is.na(sla_free))
+
+#---------------------------------------------------------------------------------------------
+#new dfr creating starch and sugar content per leaf for use in other analyses
+leaf_tnc <- SLA_TNCfree_noNA[, c(1:4, 8:10,12,14)]
+leaf_tnc$leafstarch <- with(leaf_tnc, (mass*starch_mgperg)/1000)
+leaf_tnc$leafsugar <- with(leaf_tnc, (mass*sugar_mgperg)/1000)
+leaf_tnc$percstarch <- with(leaf_tnc, (leafstarch/mass)*100)
[…]

### 2014-06-06 Stats/aci_stats.R

@@ -1,0 +1,51 @@
+
+source("functions and packages/load packages.R")
+
+#read 2 ACi datasets (they are from two seperate dates during the experiment...deal with this later)
+source("read data scripts/physiology read data.R")
+
+
+acifunction_raw <- function(x) {
+  
+  aci_model <- fitacis(x, "ID",varnames = list(ALEAF="Photo", Tleaf = "Temp", Ci="Ci", PPFD="PPFD"), 
+                       Tcorrect=TRUE)
+  
+  aci_coef <- coef(aci_model)
+  aci_coef <- merge(aci_coef, plotsumm, by = "ID")
+  #aci_means <- summaryBy(Vcmax+Jmax+Rd ~ volume , data = aci_coef,  FUN=c(mean,se))
+  #aci1_means$Date <- as.Date("2013-03-14")
+  
+  return(aci_coef)
+}
+
+aci1coef <- acifunction_raw(aci1)
+aci1coef$campaign <- "a"
+
+aci2coef <- acifunction_raw(aci2)
+aci2coef$campaign <- "b"
+
+acitstats <- rbind(aci1coef, aci2coef)
+
+#test if two sets are different by volume
+
+
+aci_means <- summaryBy(Vcmax+Jmax ~ volume+campaign , data = acitstats,  FUN=c(mean,se))
+
+boxplot(Vcmax.mean ~ volume, data = subset(aci_means, campaing="a"))
+boxplot(Vcmax.mean ~ volume, data = subset(aci_means, campaing="b"))
+boxplot(Jmax.mean ~ volume, data = aci_means)
+
+#models
+
+volumeVc <- lm(Vcmax ~ volume, data = acitstats)
+volumeJ <- lm(Jmax ~ volume, data = acitstats)
+
+
+Vc_campaign <- lm(Vcmax ~ volume+campaign, data = acitstats)
+J_campaign <- lm(Jmax ~ volume+campaign, data = acitstats)
+
+#-----------------------------------------------------------------
+#jmax and vcmax are difffent by volume but not date...use means of volume across samples to model A
+aci_parameters <- aggregate(cbind(Vcmax, Jmax) ~ volume, data=acitstats, FUN="mean")
+
+write.csv(aci_parameters, "calculated data/aci_parameters.csv", row.names=FALSE)

### 2014-06-06 Stats/belowground_CN.R

@@ -1,0 +1,167 @@
+#how does soil and root N change?
+#specific root length?
+#root mass by volume?
+
+#source functions and packages
+source("functions and packages/functions.R")
+source("functions and packages/load packages.R")
+#read in plot design and harvest data
+plotsumm <- read.csv("raw data/plot_summary.csv")
+plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
+
+#root mass and c/n
+root_cn <- read.csv("raw data/fine root CN.csv")
+root_mass <- read.csv("calculated data/seedling mass.csv")
+root_mass <- root_mass[,c(1:3, 8)]
+
+root_chem <- merge(root_cn, root_mass, all=TRUE)
+root_chem$Nfr <- with(root_chem, fineroot*(N_perc/100))
+root_chem$Ncr <- with(root_chem, Croot*(N_perc/100))
+root_chem$rootN <- with(root_chem, Nfr+Ncr)
+root_chem$rootmass <- with(root_chem, Croot+fineroot)
+
+#replace 1000 with free
+root_chem$volume <- gsub("1000", "free", root_chem$volume)
+root_chem$volume <- gsub("^5", "05", root_chem$volume)
+root_chem$volume <- as.factor(root_chem$volume)
+
+#roots no free
+root_pot <- subset(root_chem, volume != "1000")
+
+#soil CN
+soil <- read.csv("raw data/soil CN.csv")
+
+#pre experiment soils
+soilpre <- soil[48:53,]
+soilpre$volume <- as.numeric(gsub("pre", "", soilpre$ID))
+volumeorder<-order(soilpre$volume, by=soilpre$ID)
+soilpre <- soilpre[volumeorder,]
+
+soilN_mean = round(mean(soilpre$n_perc),3)
+
+
+#soil harvest
+soil_harvest <- soil[0:48,]
+harvestmean <- summaryBy(n_perc~volume, data=soil_harvest, keep.names=TRUE)
+Hmean <- round(mean(harvestmean$n_perc),3)
+
+soil_harvest$volume <- gsub("1000", "free", soil_harvest$volume)
+soil_harvest$volume <- gsub("^5", "05", soil_harvest$volume)
+soil_harvest$volume <- as.factor(soil_harvest$volume)
+
+srl <- read.csv("raw data/SRLmass.csv")
+srl$ID <- paste(srl$plot, srl$pot, sep = "-")
[…]

### 2014-06-06 Stats/harvest stats.R

@@ -1,0 +1,42 @@
+source("functions and packages/load packages.R")
+
+#read data
+source("calculated data/seedling mass.csv")
+
+
+#treatment means for total mass and ratios
+finalmass <- subset(seedlingmass, select = c("ID", "volume", "totalmass", 
+                                             "rootshoot", "frootleaf"))
+mass_agg <- summaryBy( .~ volume , data = finalmass,  FUN=c(mean,sd,length))
+
+mass_agg$massSE <- with(mass_agg, totalmass.sd/sqrt(totalmass.length))
+mass_agg$rootshootSE <- with(mass_agg, rootshoot.sd/sqrt(rootshoot.length))
+mass_agg$frootleafSE <- with(mass_agg, frootleaf.sd/sqrt(frootleaf.length))
+mass_agg$finerootSE <- with(mass_agg, frootleaf.sd/sqrt(frootleaf.length))
+mass_agg$shootSE <- with(mass_agg, frootleaf.sd/sqrt(frootleaf.length))
+
+#Stats
+totalmasslm <- lm(totalmass ~ as.factor(volume), data=finalmass)
+rootshootlm <- lm(rootshoot ~ as.factor(volume), data=finalmass)
+frootleaflm <- lm(frootleaf ~ as.factor(volume), data=finalmass)
+
+getP <- function(x)anova(x)[[5]][1]
+getP(totalmasslm)
+getP(rootshootlm)
+getP(frootleaflm)
+
+
+# Pot size effect.
+totalmass_potsize <- lm(totalmass ~ as.factor(volume), data=finalmass, subset=volume != "1000")
+rootshoot_potsize <- lm(rootshoot ~ as.factor(volume), data=finalmass, subset=volume != "1000")
+frootleaf_potsize <- lm(frootleaf ~ as.factor(volume), data=finalmass, subset=volume != "1000")
+
+getP(totalmass_potsize)
+getP(rootshoot_potsize)
+getP(frootleaf_potsize)
+
+#Plotting
+
+with(finalmass, bargraph.CI(as.factor(volume), totalmass))
+with(finalmass, bargraph.CI(as.factor(volume), rootshoot))
+with(finalmass, bargraph.CI(as.factor(volume), frootleaf))

### 2014-06-06 Stats/leafN_tnc_stats.R

@@ -1,0 +1,111 @@
+source("functions and packages/functions.R")
+source("functions and packages/load packages.R")
+source("functions and packages/plot objects.R")
+
+#read TNC and calculated leafN, merge
+
+tnc_leaf <- read.csv("calculated data/leaf_tnc.csv")
+N_leaf <- read.csv( "calculated data/leaf N content.csv")
+
+leaf_traits <- merge(N_leaf, tnc_leaf[,c(1:4,8:11)])
+leaf_traits$volume <- as.factor(leaf_traits$volume)
+leaf_traits$Date <- as.Date(leaf_traits$Date)
+leaf_traits$invest <- with(leaf_traits, Nmass/leafstarch)
+leaf_traits$N_TNC <- with(leaf_traits, Nmass/(leafstarch+leafsugar))
+#tnc free leaf N
+leaf_traits$N_noTNC <- with(leaf_traits, (mass-(leafstarch+leafsugar))*Nperc)
+leaf_traits$Narea_noTNC <- with(leaf_traits, N_noTNC/area)
+
+#means
+
+Nleafagg_noTNC<- summaryBy(N_noTNC +Narea_noTNC~ volume+Date, data=leaf_traits, FUN=c(mean, se))
+
+#---------------------------------------------------------------------------------------
+#plot raw data
+
+#Nmass
+windows()
+par(mfrow=c(3,3))
+leafN_mass<- dlply(leaf_traits, .(volume), function(x) c(plotBy(N_noTNC ~ Date | ID, how="col", type='o', 
+              legend=F, col=x$volume, ylim=c(0, .02),lty=1, ylab="", xlab="", data=x), 
+              title(main=paste("volume = ", unique(x$volume)), line=-1.5, font.main=1, adj=.05, cex.main=1),
+              title(ylab=nmasslab, mgp=ypos)))
+dev.copy2pdf(file="output/stats_plots/Nmass_noTNC_date.pdf")
+dev.off()
+
+#Nmass
+windows()
+par(mfrow=c(3,3))
+leafN_mass<- dlply(leaf_traits, .(volume), function(x) c(plotBy(Narea_noTNC ~ Date | ID, how="col", type='o', 
+             legend=F, col=x$volume, ylim=c(0, .0005),lty=1, ylab="", xlab="", data=x), 
+             title(main=paste("volume = ", unique(x$volume)), line=-1.5, font.main=1, adj=.05, cex.main=1),
[…]

### 2014-06-06 Stats/lma_stats.R

@@ -1,0 +1,145 @@
+
+#Does LMA change through time within a container volume?
+
+source("functions and packages/functions.R")
+source("functions and packages/load packages.R")
+source("functions and packages/plot objects.R")
+
+#read in plot design, lma data, merge
+plotsumm <- read.csv("raw data/plot_summary.csv")
+plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
+  
+lma <- read.csv("raw data/seedling leaf mass area.csv")
+lma$ID <- paste(lma$plot, lma$pot, sep = "-")
+lma <- merge(lma, plotsumm[3:4], all=TRUE)
+lma$volume <- as.factor(lma$volume)
+  
+#run function to add campaign dates, caluclate lma(g m-2 and sla m g-1)
+lma <- add_campaign_date(lma)
+lma$sla <- with(lma, (area/mass)/10000)
+lma$massarea <- with(lma, (mass/area)*10000)
+  
+#remove missing values
+lma_noNA <- subset(lma, !is.na(sla))
+
+write.csv(lma_noNA, "calculated data/leafmassarea.csv", row.names=FALSE)
+  
+#subset with only sla and parameters of lm
+lma_lm <- subset(lma_noNA, select = c("ID", "volume", "campaign", "sla", "massarea"))
+lma_lm <- add_campaign_date(lma_lm)
+#treatment means
+sla_means<- summaryBy(sla +massarea~ volume+Date, data=lma_lm, FUN=c(mean, se))
+
+#----------------------------------------------------------------------------------------------
+#Visualize changes in SLA across campaigns (raw)
+
+#sla
+windows()
+par(mfrow=c(3,3))
+SLA_plots<- dlply(lma_lm, .(volume), function(x) c(plotBy(sla ~ Date | ID, how="col", type='o', 
+            legend=F, lty=1,col=x$volume, ylim=c(0, 300), xlab="", pch=16, ylab="", data=x), 
+            title(main=paste("volume = ", unique(x$volume)), line=-1.5, font.main=1, 
+             adj=.05, cex.main=1),title(ylab=slalab, mgp=ypos)))
+
+                    
+dev.copy2pdf(file="output/stats_plots/sla_raw.pdf")
+dev.off()
+
+#lma
+windows()
+par(mfrow=c(3,3))
[…]

### 2014-06-06 Stats/mass growth increment.R

@@ -1,0 +1,161 @@
+#develop a linear model equation for either h/D or leaf number with seedling biomass
+
+source("functions and packages/functions.R")
+source("functions and packages/load packages.R")
+source("functions and packages/plot objects.R")
+
+#harvest mass
+biomass <- read.csv("calculated data/seedling mass.csv")
+treemass <- biomass[,c(1,11)]
+
+#leaf count harvest
+leafharvest <- read.csv("raw data/harvest leaf area.csv")
+leafharvest$ID <- paste(leafharvest$plot, leafharvest$pot, sep = "-")
+leafno <- leafharvest[, c(4,11)]
+leafnum <- subset(leafno, !is.na(leaf_count))
+row.names(leafnum) <- NULL
+
+#read survey data
+height <- read.csv("calculated data/height.csv")
+diameter <- read.csv("calculated data/diameter.csv")
+leafno <- read.csv("calculated data/leaf_number.csv")
+
+#format the hieght and diameter data and create a dfr from the last date
+finaldate <- function(H, D){
+  H$Date <- as.Date(H$Date)
+  D$Date <- as.Date(D$Date)
+  lastH <- subset(H, Date==max(Date))
+  lastD <- subset(D, Date==max(Date))
+  HD <- merge(lastH, lastD)
+  HD <- HD[, 3:7]
+}
+
+allom <- finaldate(height, diameter)
+#merge with leaf num and tree mass
+allomvar <- merge(allom, leafnum)
+allomvar <- merge(allomvar, treemass)
+allomvar$d2h <- with(allomvar, (diameter^2)*height)
+#re work labels for volume
+allomvar$volume <- gsub("1000", "free", allomvar$volume)
+allomvar$volume <- gsub("^5", "05", allomvar$volume)
+allomvar$volume <- as.factor(allomvar$volume)
+
+#visulaise each realtionship with mass
+
+plot(totalmass~height, data=allomvar,col=volume, pch=pchs[volume])
+#nonlinear and variance increase with height
+plot(totalmass~diameter, data=allomvar,col=volume, pch=pchs[volume])
+#nonlinear and equal variance
+plot(totalmass~leaf_count, data=allomvar,col=volume, pch=pchs[volume])
+#linear and variance increase with leaf count
+plot(totalmass~d2h, data=allomvar,col=volume, pch=pchs[volume])
+#linear and variance increase with leaf count
[…]

### 2014-06-06 Stats/photochem_reg.R

@@ -1,0 +1,393 @@
+#source functions and packages
+source("functions and packages/functions.R")
+source("functions and packages/stats packages.R")
+source("functions and packages/plot objects.R")
+photo_chem <- read.csv("calculated data/Amax_chem.csv")
+
+#re work labels for volume
+photo_chem$volume <- gsub("free", "1000", photo_chem$volume)
+photo_chem$volume <- gsub("^5", "05", photo_chem$volume)
+photo_chem$volume <- as.factor(photo_chem$volume)
+
+#--------------------------------------------------------------------------------------
+#calculate overall means and means for each date
+
+#means(all dates)
+photo_chem_agg <- summaryBy(A_mass+starch+Nmass_notnc ~ volume, FUN=c(mean, se), 
+                            data=photo_chem)
+
+volumeorder <- order(photo_chem_agg$A_mass.mean, by=photo_chem_agg$volume)
+photo_chem_agg<-photo_chem_agg[volumeorder,]
+
+# #means(campaign)
+# photo_chem_campaign <- summaryBy(A_mass+starch+Nmass_notnc ~ campaign + volume, FUN=c(mean, se), 
+#                                   keep.names=TRUE, data=photo_chem)
+
+#simple model mass based--------------------------------------------------------------------
+
+#simple models first
+#model3 (adds campaign as fixed effect)
+Amass_simple <- lm(A_mass~ starch*Nmass_notnc, data=photo_chem)
+anova(Amass_simple)
+summary(Amass_simple)
+
+AmassN <- lm(A_mass~ Nmass_notnc, data=photo_chem)
+anova(AmassN)
+summary(AmassN)
+
+AmassS <- lm(A_mass~ starch, data=photo_chem)
+anova(AmassS)
+summary(AmassS)
+#-----------------------------------------------------------------------------------------
+#visualise effects in 3d
+windows()
+with(photo_chem, {
+  scatterplot3d(Nmass_notnc,   # x axis
+                starch,     # y axis
+                A_mass,    # z axis
[…]

### 2014-06-06 calculated data/photo_chem.R

@@ -1,0 +1,31 @@
+#Read amax, leafN, and TNC
+amax <- read.csv("calculated data/Amax.csv")
+leafN <- read.csv("calculated data/leaf N content.csv")
+
+tnc <- read.csv("calculated data/tnc_leaf.csv")
+tnc$ID <- gsub("'", "",tnc$ID)
+
+#merge data sets
+photo_N <- merge(amax[,c(1:2, 5:6, 9)], leafN, all=TRUE)
+#remove the missing values for amax (4-7 #3)
+photo_N_noNA <-  subset(photo_N, !is.na(Photo))
+#re work labels for volume
+photo_N_noNA$volume <- gsub("1000", "free", photo_N_noNA$volume)
+photo_N_noNA$volume <- gsub("^5", "05", photo_N_noNA$volume)
+photo_N_noNA$volume <- as.factor(photo_N_noNA$volume)
+
+#add tnc
+photo_chem <- merge(photo_N_noNA, tnc, all=TRUE)
+#remove the missing vales from both the N and tnc dataset
+photo_chem <-  subset(photo_chem, !is.na(Nperc))
+photo_chem <-  subset(photo_chem, !is.na(starch_mgperg))
+row.names(photo_chem) <- NULL
+
+#calculate variables for stats
+#tnc variables are g g-1, everything else should be g m-2
+
+photo_chem$Nmass_notnc <- with(photo_chem, Nmass/(1-tnc))
+photo_chem$lma_notnc <- with(photo_chem, ((mass/area)*10000)/(1-tnc))
+photo_chem$A_mass <- with(photo_chem, Photo*sla*1000) #amax on a mass basis on nanomoles
+
+write.csv(photo_chem, "calculated data/Amax_chem.csv", row.names=FALSE)

### 2014-06-06 clean Scripts/Rdark.R

@@ -1,0 +1,73 @@
+
+source("functions and packages/load packages.R")
+
+#Read in R dark spot measurements,  plot design
+source("read data scripts/physiology read data.R")
+leafmass <- read.csv("raw data/seedling leaf mass area.csv")
+
+rdark <- merge(plotsumm, subset(resp_dark, select = c("Date", "plot", "pot", "Photo", "Cond", 
+                                                  "Ci", "CTleaf", "Area", "Trmmol")))
+#---------------------------------------------------------------------------------------------
+###need to calculate a q10 function to model Rdark through time
+##use rdark at 25c for upper end, average my data by volume
+
+rd25 <- 1.86
+
+#pot volume means
+rdark_agg <- aggregate(cbind(Photo, Cond, Ci, Trmmol, CTleaf) ~  volume, data=rdark, FUN=mean)
+rdark_agg$Photo <- -1*rdark_agg$Photo
+
+rdark_eq <- cbind(subset(rdark_agg, select = c("volume", "Photo", "CTleaf")), rd25)
+mean(rdark_eq$CTleaf)
+names(rdark_eq)[2] <- "rd12.3"
+
+#q10 equation 
+rdark_eq$q10 <- with(rdark_eq, (rd25/rd12.3)^(10/(25-CTleaf)))
+
+
+write.csv(subset(rdark_eq, select = c("volume","q10", "rd12.3")), "calculated data/rdarkq10.csv", row.names=FALSE)
+
+#--------------------------------------------------------------------------------------------
+
+#calculate Respiration/Leaf area
+lma <- subset(leafmass, select=c("pot","plot","campaign","mass"))
+lma <- subset(lma, campaign =="6")
+#format data
+lma <- subset(lma, !is.na(mass))
+lma$ID <- paste(lma$plot, lma$pot, sep = "-")
+#merge
+rdark <- merge(lma, rdark, by=c("plot", "pot", "ID"))
+#new variable
+rdark$resppermass <- with(rdark, Photo/mass)
+
+write.csv(rdark, "calculated data/Rd_leaf.csv")
+
+#PLOTTING
+with(rdark, bargraph.CI(as.factor(volume), Photo, 
+                        border="blue",
+                        ylim = c(-1,0), ylab = "Dark Respiration", 
+                        xlab = "Pot Volume (l)"))
+box()
+dev.copy2pdf(file= "output/Rdark.pdf")
+
+with(rdark, bargraph.CI(as.factor(volume), resppermass, 
[…]

### 2014-06-06 clean Scripts/Seedling Leaf Traits.R

@@ -1,0 +1,99 @@
+source("functions and packages/functions.R")
+source("functions and packages/load packages.R")
+
+#read leaf traits data from surveys
+source("read data scripts/survey read data.R")
+
+#LEAF LENGTH, format data
+leaflength <- melt(leaflength, id=c("plot", "pot", "LeafSS"))
+names(leaflength)[4:5] <- c("Date", "length")
+leaflength$Date <- gsub("X", "", leaflength$Date)
+leaflength$Date <- as.Date(leaflength$Date, format = "%m.%d.%Y")
+leaflength <- subset(leaflength, !is.na(length))
+leaflength$ID <- paste(leaflength$plot, leaflength$pot, sep = "-")
+#merge with plot summary
+leaflength <- merge(leaflength, plotsumm, by =  "ID")
+leaflength$volume <- as.factor(leaflength$volume)
+
+#average length per pot
+leaflength_avg <- aggregate(length ~ Date + ID, data = leaflength, FUN = mean)
+#treatment means
+leaflength_agg <- aggregate(length ~ Date + volume, data = leaflength, FUN = mean)
+
+
+#LEAF MASS AREA
+lma1 <- subset(lma, select=c("ID","campaign",	"area",	"mass"))
+#format data
+lma1 <- subset(lma1, !is.na(area))
+lma1 <- merge(lma1, plotsumm, by =  "ID")
+lma1$volume <- as.factor(lma1$volume)
+lma1$massperarea <- with(lma1, mass/area)
+#add campaign date
+lma2 <- add_campaign_date(lma1)
+
+#average lma per pot
+lma_avg <- aggregate(massperarea ~ Date + ID, data = lma2, FUN = mean)
+#treatment means
+lma_agg <- aggregate(cbind(area , massperarea) ~ Date + volume, data = lma2, FUN = mean)
+
+#----------------------------------------------------------------------------------------------------
+#plot stuff
+
+#colors
+gradient <- colorRampPalette(c("red", "blue"))
+palette(gradient(7))
+
+# ticks on the X axis as a Date object ('DateTime').
+xAT <- seq.Date(from=as.Date("2013-3-1"), length=5, by="month")
+pchs = c(rep(16,6),17)
+#labels
+leglab <- c(5, 10, 15, 20, 25, 35, "free")
[…]

### 2014-06-06 clean Scripts/Starch.R

@@ -1,0 +1,52 @@
+source("functions and packages/load packages.R")
+
+#read in plot design and TNC data
+plotsumm <- read.csv("raw data/plot_summary.csv")
+plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
+
+starch <- read.csv("raw data/starch_harvest.csv")
+names(starch)[1] <- "ID"
+
+#standard means
+standard <- starch[1:6,]
+standard_agg <- summaryBy( Abs510 ~ ID , data = standard,  FUN=c(mean))
+#convert mean of 100 standard from abs to ug
+standard100 <- with(standard, (Abs510[4] +Abs510[6])/2)
+fvalue <- 100/standard_agg[2,2]
+
+#Data subset
+starch1 <- starch[7:150,]
+
+starch_agg <- summaryBy( .~ ID , data = starch1,  FUN=c(mean, sd, length))
+starch_agg$abs_SE <- with(starch_agg, Abs510.sd/sqrt(Abs510.length))
+
+starch_agg$mg_glu_sample <- (100*starch_agg$Abs510.mean*100*162)/(1000*180)
+
+starch_agg$g_glu_g_DW <- (100*starch_agg$Abs510.mean*100*162)/(1000*180*starch_agg$mass.mean)
+starch_agg$mg_glu_per_gDW <- starch_agg$g_glu_g_DW*1000
+
+starch_agg$percglu <- starch_agg$Abs510.mean * (standard100 / starch_agg$mass.mean) *10*.9
+starch_agg$starchcontent <- starch_agg$percglu *10
+
+
+#merge with plot summary
+starch_agg <- merge(starch_agg, plotsumm, by = "ID")
+starch_agg$volume <- as.factor(starch_agg$volume)
+
+
+#Stats
+getP <- function(x)anova(x)[[5]][1]
+
+#POT effect
+starchlm <- lm(starchcontent ~ volume, data=starch_agg)
+getP(starchlm)
+
+# Pot size effect.
+starch_potsize <- lm(starchcontent ~ volume, data=starch_agg, subset=volume != "1000")
+getP(starch_potsize)
+
+
+#Plotting
+with(starch_agg, bargraph.CI(as.factor(volume), starchcontent))
+                                         
+

### 2014-06-06 clean Scripts/TNC.R

@@ -1,0 +1,107 @@
+#source functions
+source("functions and packages/functions.R")
+source("functions and packages/load packages.R")
+source("functions and packages/plot objects.R")
+
+#raw data
+leaf_tnc <- read.csv("raw data/leaf_tnc.csv")
+#add Date from campaign #
+leaf_tnc<- add_campaign_date(leaf_tnc)
+
+#re work labels for volume
+leaf_tnc$volume <- gsub("1000", "free", leaf_tnc$volume)
+leaf_tnc$volume <- gsub("^5", "05", leaf_tnc$volume)
+leaf_tnc$volume <- as.factor(leaf_tnc$volume)
+
+# removed 4-6. 7-1, 5-4 from v15, c#2
+#tnc15 <- subset(leaf_tnc, volume=="15" & campaign =="2")
+
+#remove missing values
+leaf_tnc <- subset(leaf_tnc, !is.na(starch_mgperg))
+row.names(leaf_tnc)<-NULL
+
+#convert tnc to g g-1 (this is also the percentage)
+leaf_tnc$starch <- with(leaf_tnc, starch_mgperg /1000)
+leaf_tnc$sugars <- with(leaf_tnc, sugars_mgperg /1000)
+leaf_tnc$tnc <- with(leaf_tnc, sugars+starch)
+
+#save this dfr as calculated data (raw with no missing values)
+write.csv(leaf_tnc, "calculated data/tnc_leaf.csv", row.names=FALSE)
+
+#generate means from raw data
+tnc_means <- summaryBy(starch+sugars+tnc~ volume+Date, data=leaf_tnc, FUN=c(mean, se))   
+#save these means as dfr going forward?????
+
+#---------------------------------------------------------------------------------------------------
+#plot bits and plotting functions
+xAT <- seq.Date(from=as.Date("2013-3-1"), length=12, by="2 weeks")
+
+#bar plot function
+tncbar <- function(d, v, label, ...){
+     bargraph.CI(x.factor = d$volume,  response = d[,v],  ylab = label, xlab = "Pot Volume (l)", ...)
+     box()
+}
+#---------------------------------------------------------------------------------------------------
+
+#overal means plots
[…]

### 2014-06-06 clean Scripts/fix_tnc_ID.R

@@ -1,0 +1,14 @@
+leaf_tnc <- read.csv("raw data/leaf_tnc.csv")
+
+a <- strsplit(as.character(leaf_tnc$ID), "-")
+a.df <- ldply(a)
+
+#function to change abbreviated month to numeric, pulls number from month.abb vector
+motonum <- function(x) match(tolower(x), tolower(month.abb))
+#run function on vector of month names
+a.df$n.month <- motonum(a.df$V2)
+
+leaf_tnc$ID <- paste(a.df$V1, a.df$n.month, sep = "-")
+
+write.csv(leaf_tnc, "raw data/leaf_tnc_corr.csv", row.names=FALSE)
+

### 2014-06-06 clean Scripts/harvest leaves.R

@@ -1,0 +1,104 @@
+source("functions and packages/load packages.R")
+
+#read  leaf data from harvest and surveys
+source("read data scripts/harvest read data.R")
+source("read data scripts/survey read data.R")
+
+
+leafharvest <- subset(leafharvest, !is.na(leaf_area))
+leafharvest$areaperleaf <- with(leafharvest, leaf_area/leaf_count)
+leafharvest$totalarea <- with(leafharvest, leaf_area + newleaf_area)
+leafharvest$totalcount <- with(leafharvest, leaf_count + newleaf_count)
+
+#merge with plot summary
+leafharvest <- merge(leafharvest, plotsumm, by = c("pot", "plot", "ID"))
+leafharvest$volume <- as.factor(leafharvest$volume)
+
+
+#treatment means for total area and count
+leafharvest_agg <- aggregate(cbind(totalarea, totalcount) ~ volume , data = leafharvest, FUN = mean)
+
+
+#calculate leaf area trough time
+leafindex <- subset(leafharvest, select = c("ID", "areaperleaf", "volume"))
+
+
+#format leaf count data
+leafcount$X1.21.2013   <- as.integer(leafcount$X1.21.2013)
+leafcount <- melt(leafcount, id=c("plot", "pot"))
+names(leafcount)[3:4] <- c("Date", "count")
+leafcount$Date <- gsub ("X", "", leafcount$Date)
+leafcount$Date <- as.Date(leafcount$Date, format = "%m.%d.%Y")
+leafcount <- subset(leafcount, !is.na(count))
+leafcount$ID <- paste(leafcount$plot, leafcount$pot, sep = "-")
+
+leaftime <- merge(leafindex, leafcount, by = "ID")
+
+#calculate cumulative leaf area through time
+leaftime$canopyarea <- with(leaftime, areaperleaf * count)
+leaftime$canopysqm <- with(leaftime, areaperleaf * count/10000)
+
+write.csv(leaftime, "calculated data/leafareabypot.csv", row.names=FALSE)
+
+#treatment means for total area and count
+leaftime_agg <- summaryBy(canopysqm ~ Date + volume , data = leaftime,  FUN=c(mean,sd,length))
+leaftime_agg$SE <- with(leaftime_agg, canopysqm.sd/sqrt(canopysqm.length))
+
[…]

### 2014-06-06 clean Scripts/leaf area interpolation.R

@@ -1,0 +1,45 @@
+#this script reads in a leaf area calculated from another script
+
+#leaf area across sample dates
+leafarea <- read.csv("calculated data/leafareabypot.csv")
+
+#plot summary
+plotsumm <- read.csv("raw data/plot_summary.csv")
+plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
+
+#need to interpolate leaf area in m2 across all dates
+leafarea1 <- subset(leafarea, select = c("Date", "ID", "canopysqm"))
+
+
+#FIRST create dfr with all days for interpolation
+
+#empty list
+datels <- list()
+#date seq loop
+datemaker <- for (i in unique(plotsumm$ID)){
+  datels[[i]] <- data.frame(Date = seq(from = as.Date("2013-1-21"), to = as.Date("2013-5-21"), by = "day"), 
+                            ID = i)} 
+
+# row-bind everything together:
+dateseq <- do.call(rbind,datels)
+
+#SECOND merge leaf area dataset with dateseq dfr and interpolate
+leafarea_alldays <- merge(dateseq, leafarea1, by = c("Date", "ID"), all=TRUE)
+
+
+#use dateseq for interpolation
+leafarea_sp <- split(leafarea_alldays, leafarea_alldays$ID)
+leafarea_sp <- lapply(leafarea_sp, function(z){
+  
+  apfun_LA <- approxfun(x=z$Date, y=z$canopysqm)
+  
+  z$LA_pred <- apfun_LA(z$Date)
+  
+  
+  return(z)
+})
+leafarea_pred <- do.call(rbind, leafarea_sp)
+
+leafpred <- subset(leafarea_pred, select = c("Date", "ID", "LA_pred"))
+
+write.csv(leafpred, "calculated data/LApredbypot.csv", row.names=FALSE)

### 2014-06-06 clean Scripts/met data for HFE.R

@@ -1,0 +1,34 @@
+source("functions and packages/load model packages.R")
+
+setToken("fgCPRjG5Aoy9Dnx9pnpv")
+
+#I need to download met data across the entire pot experiment
+
+#Search HIEv for the ROS weather station data during the pot experiment
+ros_search <- searchHIEv(filename="ROS_WS", startDate="2013-01-01", endDate="2013-06-01")
+
+#search for which one of the files above has all the data I need
+ros_ex15 <-downloadTOA5(filename="ROS_WS_Table15min_20130531.dat")
+ros_ex5 <-downloadTOA5(filename="ROS_WS_Table05min_20130430.dat")
+
+with(ros_ex15, plot(DateTime, PTemp_C_Avg, type = "l"))
+with(ros_ex5, plot(DateTime, RH , type = "l"))
+
+#so i want the 5 minute data for the duration of the experiment
+ros_ws_exp <-  downloadTOA5(filename="ROS_WS_Table05min", startDate="2013-01-01", endDate="2013-06-01")
+
+#test with a graph and summary to see if the date range is covered
+with(ros_ws_exp, plot(DateTime, RH, type = "l"))
+summary(row_ws_exp)
+
+#need to aggregate to a 15 minute time step (within HIEv package)
+# First add the nearest 315min timestep.
+ros_ws_exp$DateTime15 <- nearestTimeStep(ros_ws_exp$DateTime, 15, "ceiling")
+
+# Then aggregate all numeric variables using summaryBy
+
+metdata_15 <- summaryBy(. ~ DateTime15, data=ros_ws_exp, FUN=mean, na.rm=TRUE)
+
+eucpve_met <- metdata_15[,1:5]
+
+write.csv(eucpve_met, "calculated data/eucpve_met.csv", row.names=FALSE)

### 2014-06-06 clean Scripts/ps_model.R

@@ -1,0 +1,213 @@
+#apply photosynthesis model to generate PS over the experiment
+#apply values to leaf area that has been generated
+#compare to actual measurements
+
+###made change
+source("functions and packages/load packages.R")
+source("functions and packages/functions.R")
+
+#READ DATA, calculated data for A parameters, met data, and leaf area
+
+#generated jmax and vcmax
+jmax_vcmax <- read.csv("calculated data/aci_parameters,csv")
+
+#site weather data, rename variables, format date stuff
+eucpve_met <- read.csv("calculated data/eucpve_met.csv")
+names(eucpve_met)[2:5] <- c("record", "PPFD", "temp", "RH")
+eucpve_met$DateTime15 <- as.Date(ymd_hms(eucpve_met$DateTime15))
+eucpve_met$Date <- as.Date(ymd(eucpve_met$DateTime15))
+#subset by Date range of experiment
+eucpve_met1 <- subset(eucpve_met, DateTime15  >= "2013-01-21" & DateTime15  <= "2013-05-21")
+
+#plot summary
+plotsumm <- read.csv("raw data/plot_summary.csv")
+plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
+
+#interpolated leaf area in m2 by pot
+leafpred <- read.csv("calculated data/LApredbypot.csv")
+leafpred$Date <- as.Date(ymd(leafpred$Date))
+
+#observed Ps data
+#Read in Asat treatment means and add ID variable
+Asat_means <- read.csv("calculated data/Asat treatment means.csv")
+Asat_obs <- read.csv("calculated data/Asat.csv")
+Asat_obs$Date <- as.Date(Asat_obs$Date)
+
+#Rdark Q10 equations by volume
+rdarkq10 <- read.csv("calculated data/rdarkq10.csv")
+
+
+#plot bits
+gradient <- colorRampPalette(c("red", "blue"))
+palette(gradient(7))
+pchs <- c(rep(16,6),17)
+
+
+#---------------------------------------------------------------------------------------------
+#A_model, use met data from site to generate parameters to enter into the model
+#enter a vector of parameters over the period of the study to model PS with volume specific vcmax and jmax
+
[…]

### 2014-06-06 clean Scripts/soil moisture.R

@@ -1,0 +1,80 @@
+
+source("functions and packages/load packages.R")
+
+#read in water potential data from weekly surveys
+source("read data scripts/survey read data.R")
+
+#format pre-SM
+SMpre <- melt(SMpre, id=c("plot", "pot"))
+SMpre$variable <- gsub ("X", "", SMpre$variable)
+names(SMpre)[3:4] <- c("Date", "perc_water")
+SMpre$Date <- as.Date(SMpre$Date, format = "%m.%d.%Y")
+SMpre <- subset(SMpre, !is.na(SMpre))
+SMpre$ID <- paste(SMpre$plot, SMpre$pot, sep = "-")
+SMpre <- merge(SMpre, plotsumm, by = c("pot", "plot", "ID"))
+SMpre$volume <- as.factor(SMpre$volume)
+
+#treatment means
+SMpre_agg <- aggregate(perc_water ~ Date + volume , data = SMpre, FUN = mean)
+
+
+#format SM
+SM <- melt(SM, id=c("plot", "pot"))
+SM$variable <- gsub ("X", "", SM$variable)
+names(SM)[3:4] <- c("Date", "perc_water")
+SM$Date <- as.Date(SM$Date, format = "%m.%d.%Y")
+SM <- subset(SM, !is.na(perc_water))
+SM$ID <- paste(SM$plot, SM$pot, sep = "-")
+SM <- merge(SM, plotsumm, by = c("pot", "plot", "ID"))
+SM$volume <- as.factor(SM$volume)
+#treatment means
+SM_agg <- aggregate(perc_water ~ Date + volume , data = SM, FUN = mean)
+
+#2 panel plot with allometry mean data
+#plot bits
+gradient <- colorRampPalette(c("red", "blue"))
+palette(gradient(7))
+
+# ticks on the X axis as a Date object ('DateTime').
+xAT <- seq.Date(from=as.Date("2013-3-20"), length=30, by="week")
+
+#legend labels
+leglab <- c(5, 10, 15, 20, 25, 35, "free")
+volume <- SMpre_agg$volume
+pchs<-c(rep(16,6),17)
+
+#PLOT
+windows(8,12)
+par(cex.axis=0.9,
+    cex.lab= 1.3, 
+    mfrow=c(2,1),  
+    omi=c(1,1,0.2,0.2),  # outer margin (inches)
+    mar=c(0,0,0,0))  # margin around plots (they are tight together)   
+
[…]

### 2014-06-06 functions and packages/functions.R

@@ -1,0 +1,151 @@
+# standard error function
+se <- function(x) sd(x)/sqrt(length(x))
+
+#-----------------------------------------------------------------------------------
+#fit aci curve function
+acifunction <- function(x) {
+  
+  aci_model <- fitacis(x, "ID",varnames = list(ALEAF="Photo", Tleaf = "Temp", Ci="Ci", PPFD="PPFD"), 
+                       Tcorrect=TRUE)
+  
+  aci_coef <- coef(aci_model)
+  aci_coef <- merge(aci_coef, plotsumm, by = "ID")
+  aci_means <- summaryBy(Vcmax+Jmax+Rd ~ volume , data = aci_coef,  FUN=c(mean,se))
+  #aci1_means$Date <- as.Date("2013-03-14")
+  
+  return(aci_means)
+}
+#-----------------------------------------------------------------------------------
+#format raw leaf CN data from ANU
+leafCN_format <- function(dfr){
+  
+  dfr$ID <- as.character(dfr$ID)
+  
+  idsp <- strsplit(dfr$ID, "")
+  
+  plot <- sapply(idsp, "[", 1)
+  pot <- sapply(idsp, "[",2)
+  campaign <- sapply(idsp, "[",3)
+  
+  leaf_perCN <- cbind(dfr[2:3], plot)
+  leaf_perCN <- cbind(leaf_perCN, pot)
+  leaf_perCN <- cbind(leaf_perCN, campaign)
+  leaf_perCN$ID <-  paste(leaf_perCN$plot, leaf_perCN$pot, sep = "-")
+  leaf_perCN <- leaf_perCN[ -c(3:4) ]
+  leaf_perCN$Nperc <- leaf_perCN$Nperc/100
+  leaf_perCN$Cperc <- leaf_perCN$Cperc/100
+  leaf_perCN$campaign <- as.integer(leaf_perCN$campaign)
+  return(leaf_perCN)
+}
+#------------------------------------------------------------------------------------
+
+#generate basic summary statistics
+summary_stats <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
+                          conf.interval=.95, .drop=TRUE) {
+  require(plyr)
+  
+  # New version of length which can handle NA's: if na.rm==T, don't count them
+  length2 <- function (x, na.rm=TRUE) {
+    if (na.rm) sum(!is.na(x))
+    else       length(x)
+  }
+  # This does the summary. For each group's data frame, return a vector with
+  # N, mean, and sd
[…]

### 2014-06-06 functions and packages/stats packages.R

@@ -1,0 +1,12 @@
+#packages for stats
+require(lme4)
+require(nlme)
+require(car)
+library(effects)
+library(doBy)
+library(plyr)
+library(plotrix)
+
+#special plotting
+library(scatterplot3d)
+library(rgl)

### 2014-06-06 functions and packages/unused list.R

@@ -1,0 +1,15 @@
+volume <- unique(plotsumm$volume)
+
+#function to add volume to met data for each campaign
+met_volume<- function(vol,cam){
+  merge(subset(eucpve_met,campaign==cam), subset(ps_param,campaign==cam&volume==vol))
+}
+
+lista <- list()
+listb <- list()
+for (i in 1:length(volume)){
+  lista[[i]] <- met_volume(vol=volume[i],cam="a")
+  lista[[i]] <- met_volume(vol=volume[i],cam="b") 
+}
+
+model_parameters <- rbind.fill(rbind.fill(testa),rbind.fill(testb))

### 2014-06-06 history/server.R

@@ -1,0 +1,34 @@
+
+#R code to due the work in the shiny app
+
+
+library(shiny)
+library(Lahman)
+library(ggplot2)
+
+# Define server logic required to plot various variables against year
+shinyServer(function(input, output) {
+  
+  # Compute the forumla text in a reactive function since it is 
+  # shared by the output$caption and output$mpgPlot functions
+  formulaText <- reactive({
+    paste("Variable:", input$variable,
+          "relationship with seedling photosynthesis, constrained by container volume"#,
+          #input$range[1], "to", input$range[2])#try to make this volume?
+  })
+  
+  # Return the formula text for printing as a caption
+  output$caption <- renderText({
+    formulaText()
+  })
+  
+  # Generate a plot of the requested variable against mpg and only 
+  # include outliers if requested
+  output$Asat_plot <- renderPlot({
+    Asat_variable <- subset(Nphoto, volume != "1000")
+    #Teams.recent$stat.game <- Teams.recent[, input$variable] / Teams.recent[, "G"]
+    print(plot(Nphoto, Photo(Nmass, volume)) 
+            xlab("Photosynthesis") + ylab("N per unit leaf mass (g/g)")   
+    )
+  }, width=600, height=500)
+})

### 2014-06-06 history/ui.R

@@ -1,0 +1,44 @@
+#this scrupt defines the interface(sliders, etc)
+
+
+library(shiny)
+
+# Define UI for miles per gallon application
+shinyUI(pageWithSidebar(
+  
+  # Application title
+  headerPanel("Effects of belowground space limitation on performance of Eucalyptus seedlings: 
+              barrier sensing or nutrient limitation?"),
+  
+  # Sidebar with controls to select the variables to plot against Photosynthesis
+  # and to specify whether outliers should be included
+  sidebarPanel(
+    selectInput("variable", "Variable:",
+                list("Runs" = "R",
+                     "Hits" = "H", 
+                     "Home Runs" = "HR", 
+                     "Doubles" = "X2B",
+                     "Triples" = "X3B",         
+                     "Walks" = "BB",
+                     "Strikeouts" = "SO",
+                     "Stolen Bases" = "SB",
+                     "Errors" = "E")),
+    sliderInput("range", "Range:",
+                min = 1901, max = 2012, format="###",
+                value = c(1901, 2012), step = 1),
+    sliderInput("decimal", "Loess Smoothing Fraction:", 
+                min = 0.05, max = 0.95, value = 0.2, step= 0.05)
+  ),
+  
+  # Show the caption and plot of the requested variable against mpg
+  mainPanel(
+    h3(textOutput("caption")),
+    
+    plotOutput("mpgPlot")
+  )
+))
+
+
+
+#start with Photo synthesis (Asat and Amax)
+#then use the covariates as the list (N, tnc, lma, )

### 2014-06-06 read data scripts/survey read data.R

@@ -1,0 +1,24 @@
+#weekly survey data
+height <- read.csv("raw data/seedling height.csv")
+diam <- read.csv("raw data/seedling diameter.csv")
+leafno <- read.csv("raw data/seedling leaf count.csv")
+leafcount <- read.csv("raw data/seedling leaf count.csv")
+leaflength <- read.csv("raw data/seedling leaf length.csv")
+
+
+#LEAF MASS AREA
+lma <- read.csv("raw data/seedling leaf mass area.csv")
+lma$ID <- paste(lma$plot, lma$pot, sep = "-")
+
+  #ACI leaves (subset of whole experiment with random leaves from each volume)
+  acileaf <- read.csv("raw data/aci leaves.csv")
+  acileaf$Date <- as.Date(acileaf$Date, format = "%m/%d/%Y")
+  acileaf$ID <- paste(acileaf$plot, acileaf$pot, sep = "-")
+
+#plot design
+plotsumm <- read.csv("raw data/plot_summary.csv")
+plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
+
+#rsoil moisture
+SMpre <- read.csv("raw data/pre-soil moisture.csv")
+SM <- read.csv("raw data/soil moisture.csv")

### 2014-06-06 shiny.R

@@ -1,0 +1,3 @@
+#once all the files are created in the ui.R and the server.R run from this script
+library(shiny)
+runApp("history")

### 2014-07-23 markdowns/master.rmd
added soilN percent plots to master and markdowsn
still cant get root shoot to markdown

still working at function of Cgain model

---
title: "EUV_PVE"
author: "Court Campany"
date: "Tuesday, July 22, 2014"
output: html_document
---

```
These are the plots and relevatn statistics for the Eucalpytus tereticornis  
pot study.  6 total contatiner volumes and 'free'seedlings all grown under  
natural field conditions during the summer of 2012
```
```{r setup}
library(knitr)
opts_knit$set(root.dir = '../')
```
```

```{r loads functions packages and plot objects, echo=FALSE, include=FALSE}
#source functions, packages, anbd plot objects
source("functions and packages/startscripts.R")

```

```
seedling growth through time
```
```{r allometry panel plot}
source("master_scripts/allometryplotting.R")
```

```
seedling total leaf area through time
```
```{r leaf area plot}
source("master_scripts/leafarea_plotting.R")
```

```
root:shoot and leaf:fine root at harvest
```

```{r root:shoot plots }
source("master_scripts/rootshoot_plotting.R")
```

```
aci curves and jmax/vcmax
```

```{r aci means plots }
source("master_scripts/aci_plotting.R")
```

```
seedling predawn and midday water potentials
```

```{r water potential plots}
source("clean scripts/seedling water potential.R")
```

```
Modelled C gain versus harvest seedling total carbon
```

```{r Cgain vs Cmass }
cgain<- read.csv("calculated data/euc_cgain.csv")
cgain$volume <- as.factor(cgain$volume)

windows()
with(cgain, plot(carbon_gain, totalC, pch=pchs[volume], col=volume))
abline(0,1)
abline(lm(totalC ~ carbon_gain, data=cgain), lty=5)
```

```
Soil N percent pre expeeriment and at harvest
```
```{r Soil N percent}
source("master_scripts/soilN_plotting.R")
```

### 2014-07-23 markdowns/test.Rmd
added soilN percent plots to master and markdowsn
still cant get root shoot to markdown

still working at function of Cgain model

---
title: "test"
author: "Court Campany"
date: "Tuesday, July 22, 2014"
output: html_document
---

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r loads functions packages and plot objects, echo=FALSE}
#source functions, packages, anbd plot objects
library(knitr)
opts_knit$set(root.dir=normalizePath('../'))
source("functions and packages/startscripts.R")

```

### 2014-07-23 cgain_model.R

@@ -56,26 +56,19 @@ plot(leafarea~Date, data=Cgain_loop)
 require(plyr)
 #need to split Cday, but also get a list of 49 that only include the Cgain vector
 
-cday_sp2 <- dlply(Cday, .(ID))
-cday_sp3 <- lapply(cday_sp2, )
-
-cday_sp <- split(Cday[,c(1,3)], "ID", drop=TRUE)
-
-
-cday_sp2 <- cday_sp[[1]]$Adayumol
-
 modelfunction <- function(x) {
   for (i in 2:numdays) {
     production <- x[i-1] * leafarea[i-1]
     biomass[i] <- biomass[i-1] + production
     leafarea[i] <- leafarea[i-1] + (production*leafrac*sla)
+    dfr <- data.frame(mass=biomass, la = leafrea)
+    return(dfr)
   }
 }
 
-Cid <- Cday[,c(1,3)]
+cday_sp2 <- dlply(Cday, .(ID))
 
-runmodel <- dlply(Cid, .(id), function(x) c(x<- as.vector(x[,2]), modelfunction(x)))
-
-test <- dlply(Cid, .(id), function(x) y<-as.vector(x[,2]))
+runmodel <- apply(cday_sp2, ,modelfunction)
+runmodel<- modelfunction(cday_sp2[["carbon_day"]]) 
 
 

### 2014-07-23 eucpve_master.R

@@ -23,3 +23,5 @@ with(cgain, plot(carbon_gain, totalC, pch=pchs[volume], col=volume))
 abline(0,1)
 abline(lm(totalC ~ carbon_gain, data=cgain), lty=5)
 
+#Soil Nitrogen bar plot
+source("master_scripts/soilN_plotting.R")

### 2014-07-23 markdowns/master.rmd
cleaned md file

@@
 ```
-
 ```{r loads functions packages and plot objects, echo=FALSE, include=FALSE}
@@
 source("functions and packages/startscripts.R")
-
 ```
@@
 ```{r root:shoot plots }
-source("master_scripts/rootshoot_plotting.R")
+#source("master_scripts/rootshoot_plotting.R")
 ```

### 2014-07-23 markdowns/master.rmd
no code blocks

@@
 ---
-title: "EUV_PVE"
+title: "EUC_PVE"
 author: "Court Campany"
@@
 
-```
-seedling predawn and midday water potentials
-```
+### seedling predawn and midday water potentials
 
@@
 
-```
 Modelled C gain versus harvest seedling total carbon
-```
 

### 2014-07-24 markdowns/master.rmd
split photochem script into just model analysis and then predict plots with bins for master
added photochem predict to master and md

added new lables to plot objects

@@
 
-```
 seedling growth through time
-```
+
 ```{r allometry panel plot}
@@
 
-```
 seedling total leaf area through time
-```
+
 ```{r leaf area plot}
@@
 
-```
 root:shoot and leaf:fine root at harvest
-```
 
@@
 
-```
 aci curves and jmax/vcmax
-```
 
@@
 
-```
 Soil N percent pre expeeriment and at harvest
-```
+
 ```{r Soil N percent}
@@
 ```
+
+Predicted responses of Amax on a mass basis to leaf starch and N levels
+```{r Amass vs TNC and N}
+source(("master_scripts/photochem_predict.R")
+```

### 2014-07-24 eucpve_master.R

@@ -25,3 +25,6 @@ abline(lm(totalC ~ carbon_gain, data=cgain), lty=5)
 
 #Soil Nitrogen bar plot
 source("master_scripts/soilN_plotting.R")
+
+#Amass vs N and TNC with levels
+source(("master_scripts/photochem_predict.R")

### 2014-07-24 master_scripts/photochem_predict.R

@@ -1,0 +1,256 @@
+#THis script has the code to calculate predictions from simple and full models
+#but plots only from the full models now
+#when testing just free plants the two models are the same
+
+#simple model plots moved to end
+
+#source functions and packages
+source("functions and packages/startscripts.R")
+require(lmerTest)
+
+photo_chem <- read.csv("calculated data/Amax_chem.csv")
+#run volume format func
+photo_chem<- vollab_func(photo_chem)
+
+#plot predicted and observed in bins------------------------------------------------------
+
+#make bin levels and mid points for both starch and nitrogen
+starchbin <- c(0, 0.04, 0.08, 0.12, 0.16, 100)
+starchmid <- c(0.02, 0.06, 0.1, 0.14, 0.2)
+
+nitrobin <- c(0, 0.0025, 0.005, 0.0075, 0.01, 100)
+nitromid <- c(0.00125, 0.00375, 0.00625, 0.00875, 0.0125)
+
+#set bins in raw dfr
+photo_chem$starchbin <- cut(photo_chem$starch, breaks = starchbin)
+photo_chem$nitrobin <- cut(photo_chem$Nmass_notnc, breaks = nitrobin)
+
+#create models and extract coefs (for simple and full model)
+#use two fits so the equations stay the same for pred, y=b+b1*x1+b2*x2
+# Afit <- lm(A_mass ~ Nmass_notnc * starch, data=photo_chem)
+# p <- coef(Afit)
+# Afit2 <- lm(A_mass ~ starch*Nmass_notnc, data=photo_chem)
+# p2 <- coef(Afit2)
+
+
+Afit_full <- lmer(A_mass ~ Nmass_notnc+starch+Nmass_notnc:starch + (1|ID), data=photo_chem)
+f <- fixef(Afit_full)
+Afit2_full <- lmer(A_mass ~ starch+Nmass_notnc+starch:Nmass_notnc + (1|ID), data=photo_chem)
+f2 <- fixef(Afit2_full)
+
+
+#plot and predict (2 graphs)---------------------------------------------------------------------
+cols <- c("green2", "cyan4", "blue2", "darkviolet", "red")
[…]

### 2014-07-28 markdowns/master.rmd
failed attempt at getting rootshoot to work with markdown

@@
 ```{r root:shoot plots }
-#source("master_scripts/rootshoot_plotting.R")
+source("master_scripts/rootshoot_plotting.R")
 ```
@@
 ```{r Amass vs TNC and N}
-source(("master_scripts/photochem_predict.R")
+#source(("master_scripts/photochem_predict.R")
 ```

### 2014-07-30 master_scripts/sla_notnc_plotting.R
added spot A measurement to MD
started sla no tnc markdown master script

@@ -1,0 +1,74 @@
+#Does TNC-free LMA change through time within a container volume?
+
+#source functions and packages
+source("functions and packages/startscripts.R")
+
+#read in plot design, lma data, merge
+plotsumm <- read.csv("raw data/plot_summary.csv")
+  plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
+
+lma <- read.csv("raw data/seedling leaf mass area.csv")
+  lma$ID <- paste(lma$plot, lma$pot, sep = "-")
+lma <- merge(lma, plotsumm[3:4], all=TRUE)
+  lma$volume <- as.factor(lma$volume)
+
+#run function to add campaign dates, caluclate sla
+lma <- add_campaign_date(lma)
+
+#remove missing values
+lma_noNA <- subset(lma, !is.na(area))
+
+#read in TNC data, substract mass of TNC from mass of leaves and then calculate TNC-free SLA
+#Read in spot measurements and merge plot design
+TNC <- read.csv("raw data/leaf_TNC.csv")
+  #run function to add campaign Date
+  TNC <- add_campaign_noID(TNC)
+  TNC$volume <- as.factor(TNC$volume)
+  TNC$ID <- as.character(TNC$ID)
+  TNC$tnc_mgperg <- with(TNC, starch_mgperg+sugars_mgperg)
+
+SLA_TNCfree <- merge(lma, TNC, by=c("Date", "ID"))
+
+SLA_TNCfree$mass_noTNC <- with(SLA_TNCfree, mass-((mass*tnc_mgperg)/1000))
+  #TNC free sla and lma
+  SLA_TNCfree$sla_free <- with(SLA_TNCfree, area/mass_noTNC)
+  SLA_TNCfree$lma_free <- with(SLA_TNCfree, mass_noTNC/area)
+
+#remove missing values
+SLA_TNCfree_noNA <- subset(SLA_TNCfree, !is.na(sla_free))
+
+
+leaf_TNCfree <- subset(SLA_TNCfree_noNA, select = c("ID", "campaign", "volume", "sla_free", "lma_free","Date"))
+  volorder<-order(leaf_TNCfree$volume, by=leaf_TNCfree$Date)
+  leaf_TNCfree <- SLA_TNCfree[volorder,]
+
+#treatment means
+sla_tnc_campaign <- summaryBy(sla_free+lma_free ~ volume+Date, data=leaf_TNCfree, FUN=c(mean, se))
+
+#---------------------------------------------------------------------------------------------------
[…]

### 2014-07-30 markdowns/master.rmd
added spot A measurement to MD
started sla no tnc markdown master script
uncommented master.rmd source()

@@
 
+asat and amax
+
+```{r photosynthesis plotting}
+source("master_scripts/A_plotting.R")
+```
+
 aci curves and jmax/vcmax
@@
 ```{r Amass vs TNC and N}
-#source(("master_scripts/photochem_predict.R")
+source("master_scripts/photochem_predict.R")
 ```

### 2014-08-29 master_scripts/soilCN_plotting.R
fixed soilN part of markdown script

@@ -7,14 +7,19 @@ soil$volume <- gsub(1000, "free", soil$volume)
 soil[is.na(soil)] <- "pre"
 
 soilN <- soil[1:52, 4:5]
+soilC <- soil[1:52, c(3,5)]
   #soilN$volume <- as.factor(soilN$volume)
 
 # New sorting order
 desired_order <- c("pre", "5", "10", "15", "20", "25", "35", "free")
+
 # Re-order the levels
 soilN$volume <- factor(as.character(soilN$volume), levels=desired_order )
+soilC$volume <-  factor(as.character(soilC$volume), levels=desired_order )
+
 # Re-order the data.frame
 soilN <- soilN[order(soilN$volume),]
+soilC <- soilC[order(soilC$volume),]
 
 #simple plot
 
@@ -24,3 +29,8 @@ bargraph.CI(volume,n_perc, data=soilN,  xlab = "Pot Volume (l)",  col="grey98",
             ylab = "Soil Nitrogen (%)",ylim = c(0, .06))
 box()
 
+
+par(lwd=1.25, mgp=c(2.5,1,0))
+bargraph.CI(volume,c_perc, data=soilC,  xlab = "Pot Volume (l)",  col="grey98", 
+            ylab = "Soil Carbon (%)",ylim = c(0, .65))
+box()

### 2014-09-03 markdowns/master.rmd
fixed soilN part of markdown script
change to C gain model and master.Rmd

--- 2014-07-28 markdowns/master.rmd
@@
 
-```{r leaf area plot}
+```{r leafareaplot}
 source("master_scripts/leafarea_plotting.R")
@@
 
-```{r root:shoot plots }
+```{r rootshootplots }
 source("master_scripts/rootshoot_plotting.R")
+```
+
+asat and amax
+
+```{r photosynthesisplotting}
+source("master_scripts/A_plotting.R")
 ```
@@
 
-```{r aci means plots }
+```{r acimeansplots }
 source("master_scripts/aci_plotting.R")
@@
 
-```{r water potential plots}
+```{r waterpotentialplots}
 source("clean scripts/seedling water potential.R")
@@
 
-```{r Cgain vs Cmass }
+```{r CgainvsCmass }
 cgain<- read.csv("calculated data/euc_cgain.csv")
@@
 
-```{r Soil N percent}
-source("master_scripts/soilN_plotting.R")
+```{r SoilNpercent}
+source("master_scripts/soilCN_plotting.R")
 ```
@@
 Predicted responses of Amax on a mass basis to leaf starch and N levels
-```{r Amass vs TNC and N}
-#source(("master_scripts/photochem_predict.R")
+```{r AmassvsTNCandN}
+source("master_scripts/photochem_predict.R")
 ```

### 2014-10-31 markdowns/master.rmd
added more plots to markdown

@@
 
-### seedling predawn and midday water potentials
+seedling predawn and midday water potentials
 
@@
 ```{r AmassvsTNCandN}
-source("master_scripts/photochem_predict.R")
+source("master_scripts/Amax_TNC_N_plotting.R")
 ```
+
+Mass allocaiton and LMF plotting
+```{r Harvest allocation and LMF}
+source("master_scripts/allocation_plotting.R")
+```

### 2014-10-31 master_scripts/Amax_TNC_N_plotting.R

@@ -1,0 +1,77 @@
+#this script is for sourcing the Amax vs TNC and N plots into master
+source("functions and packages/startscripts.R")
+
+require(lme4)
+require(scales)
+
+photo_chem <- read.csv("calculated data/Amax_chem.csv")
+#run volume format func
+photo_chem<- vollab_func(photo_chem)
+
+#model
+Afit_full <- lmer(A_mass ~ Nmass_notnc+starch+Nmass_notnc:starch + (1|ID), data=photo_chem)
+
+###same model with fixed effects in different order for ease of plotting preductions later
+Afit2_full <- lmer(A_mass ~ starch+Nmass_notnc+starch:Nmass_notnc + (1|ID), data=photo_chem)
+
+
+###two panel of graph above, using predict------------------------------------------------------------
+
+#make bin levelsfor starch and nitrogen
+starchbin <- c(0, 0.04, 0.08, 0.12, 0.16, 100)
+nitrobin <- c(0, 0.0025, 0.005, 0.0075, 0.01, 100)
+
+#plot objects
+cols <- c("green3", "cyan4", "#0081FFFF", "darkviolet", "red")
+coln <- c("red", "darkviolet", "#0081FFFF", "cyan4", "green3")
+
+coln2 <- alpha(coln, .75)
+cols2 <- alpha(cols, .75)
+
+binlab <- c("0-4", "4-8", "8-12", "12-16", ">16")
+binlab2 <- c(" 0    -.001", ".001-.003", ".003-.006", ".006-.008", ".008-.012")
+
+#using predict instead of eqautions
+Npred <- expand.grid(starch = c(0.02, 0.06, 0.1, 0.14, 0.2),
+                     Nmass_notnc = seq(0.0007432, 0.0175502, length=101))
+Npred$Amass_pred <- predict(Afit_full, Npred, re.form=NA)
+
+TNCpred <- expand.grid(Nmass_notnc = c(0.00125, 0.00375, 0.00625, 0.00875, 0.0125),
+                       starch = seq(min(photo_chem$starch), max(photo_chem$starch), length=101))
+TNCpred$Amass_pred <- predict(Afit2_full, TNCpred, re.form=NA)
+
+windows(12, 8)
+par(cex.axis=1.5, cex.lab=1.5,
+    mfrow=c(1,2),  
[…]

### 2015-07-14 manuscript/manuscript_pve.Rmd
added new files to manuscript folder to start manuscript here

---
title: "Effects of below-ground space limitation on performance of Eucalyptus seedlings:  Does photosynthesis really control growth?"
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: tree-physiology.csl
bibliography: references.bib
---

\
Courtney E. Campany^1^, Belinda Medlyn^1^, Remko A. Duursma^1^.

\
^1^ Hawkesbury Institute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW, Australia

\
*Corresponding author*: 
Courtney Campany
E: courtneycampany@gmail.com

```{r, results='asis', echo=FALSE, warning=FALSE}
library(knitr)
opts_knit$set(root.dir = '../')
```

```{r global data/sourcing, echo=FALSE, message=FALSE, warning=FALSE}
# Two useful packages for printing numbers, accessing content of objects.
library(broom)
library(reporttools)
# Set Flag to include figures in text or not.
includeFigs <- TRUE

source("functions and packages/startscripts.R")
source("functions and packages/gamplotfunctions.R")

```

# Abstract {.unnumbered}

Interpreting limitations to plant growth requires understanding of the balance between carbon (C) source and sink activity in order to assess C allocation and biomass partitioning. This study used manipulations of soil volume to test how growth is coupled to physiology, allocation, and sink activity in *Eucalyptus tereticornis* seedlings. We grew seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown seedlings (free). Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings. It was hypothesized that soil volume effect would be largest in the smallest containers, resulting in physical constraints to growth independently of photosynthesis (A). Photosynthesis would then become sink-limited, resulting in the build-up of leaf nonstructural carbohydrates eventually leading to photosynthetic down regulation. We observed a negative container effect on aboveground growth soon after the experiment started. Although growth was consistently different across soil volumes mass, partitioning to leaves, stems, roots was conserved after 120 days. Photosynthetic capacity was also significantly reduced in containers, and was related to both leaf nitrogen content and starch accumulation. We developed a seedling growth model that utilized leaf A rates to allocate daily C uptake towards mass growth of stems, leaves and roots. We then asked whether the observed reductions in A explained the observed differences in seedling biomass. We found that although belowground sink limitation resulted in the down regulation of A, these reductions were not significant enough to explain observed growth responses. Thus, as photosynthesis and growth were not coordinated an excess pool of non-biomass C resulted in seedlings with soil volume restriction. This research highlights the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that A and growth are not always directly related.

# Keywords {.unnumbered}
photosynthesis, growth, sink regulation, carbon allocation, soil volume

# Introduction

# Materials and Methods

## Experimental design

## Growth and morphology metrics

## Photosynthetic parameters

## Leaf water potential

## Leaf, root and soil chemistry

## Seedling growth model

##Data analysis
Differences in experimental parameters with soil volume were analysed by one-way analysis of variance (ANOVA) in R [@RDevelopment] with individual containers as random effects and soil volume as a categorical fixed effect. Tukey’s post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different. Mixed model ANOVAs of A~max~ and leaf chemistry were performed using the 'nlme' package [@nlme] in R and R^2^ values of mixed models were computed as in [@nakagawa2013general]. Tests of allometric relationships between biomass components were implemented using major axis regression in the 'smatr' package in R [@warton2012smatr]. Results were considered significant at P&leq;0.05..

# Results

## Growth and morphology metrics

## Leaf chemistry

## Gas exchange and photosynthetic parameters

## Modelling seedling biomass

# Discussion

![figure](master_scripts/manuscript_figs/png/Cday.png)

# Tables {.unnumbered}

```{r table1, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(ascii)
pve_data <- read.csv("master_scripts/pve_table1.csv")

colnames(pve_data) <- c("Volume (L)", 
                        "Seedling~mass~(g)", 
                        "SLA\\textsubscript{TNC-free}~(m\\textsuperscript{2}~kg\\textsuperscript{-1})",
                        "Leaf~Starch~(\\%)", 
                        "Leaf~Sugars~(\\%)", 
                        "Leaf~Nitrogen~(\\%)",
                        "Root~Nitrogen~(\\%)",
                        "SRL~(cm~m\\textsuperscript{-1})",
                        "{Leaf~\\textdelta}\\textsuperscript{13}C~(\\text{\\textperthousand})")
print(ascii(pve_data,include.rownames=FALSE),type='pandoc')

```
**Table 1.** Responses of plant and leaf characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments. Each value reflects the mean(standard error) for each treatment. Seedling mass, SRL, root nitrogen and leaf $\delta$^13C values are from final harvest. Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6). Different letters represent significant differences between treatments. The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.

```{r table2, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(ascii)
phys_data <- read.csv("master_scripts/pve_table2.csv")
colnames(phys_data) <- c("Volume~(L)", 
                        "\\textit{A}\\textsubscript{max}", 
                        "\\textit{R}\\textsubscript{dark}",
                        "\\textit{J}\\textsubscript{max}",
                        "\\textit{Vc}\\textsubscript{max}",
                        "\\textit{g}\\textsubscript{s}",
                        "\\textit{g}\\textsubscript{1}")
print(ascii(phys_data,include.rownames=FALSE),type='pandoc')

```
**Table 2.** Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments. Each value reflects the mean(standard error) for each treatment. Units for A~max~ and R~dark~ are $\mu$mol m^-2^ s^-1^ and g~s~ are mol m^-2^ s^-1^, each at at 25&deg;C. Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n=6). R~dark~, J~max~ and Vc~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements. Different letters represent significant differences between treatments. The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.

# Figures {.unnumbered}

```{r airvars, fig.width=6, fig.height=8, echo=FALSE}
source("master_scripts/airvars_plotting.R")
```

**Figure 1**. Daily maximum and minimum temperature (a), cumulative daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.

```{r allometry, fig.width=6, fig.height=8, echo=FALSE}
source("master_scripts/allometryplotting.R")
```

**Figure 2**. Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.

```{r allocation, fig.width=6, fig.height=10, echo=FALSE, warning=FALSE, message=FALSE}
source("master_scripts/allocation_plotting.R")
```

**Figure 3**. Soil volume treatment means of mass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c). For (b) lines represent standardized major axis fitting of the log transformed allometric relationships of leaf mass fraction by treatment. For (c) the dashed line is the 1:1 relationship and the solid line represents the significant linear model fit (R^2^=0.81).

```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE}
source("master_scripts/A_stats_plotting.R")
```

**Figure 4**. Soil volume treatment means &pm; standard error, across all measurement campaigns (n=6), of light saturated rates of photosynthesis at 25&deg;C. Different letters represent significant differences between treatments.

```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE}
source("master_scripts/Amax_TNC_N_plotting2.R")
```

**Figure 5**. Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).  Colors represent bins levels (n=5) of both leaf starch and nitrogen grouped from low to high .  Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~max~ as a function of starch and nitrogen. The marginal R^2^ (fixed effects only) was 0.37 and the conditional R^2^ (fixed and random effects) was 0.48 for the complete model.

```{r massmodel, fig.width=6, fig.height=8, echo=FALSE}
source("master_scripts/massmodel_optimize.R")
```

**Figure 6**. Total carbon mass for harvested and modeled seedlings versus predicted total carbon gain after 120 days (a) and  reductions in final seedling carbon mass, both modeled and observed, as a function of the reduction in leaf photosynthesis across treatments (b). For (a) the dashed 1:1 identifies the difference between net total leaf carbon gain and gross seedling production. For (b) both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.

# Supporting Information {.unnumbered}

```{r model_scenarios, fig.width=6, fig.height=8, echo=FALSE}
source("master_scripts/massmodel_optimize_scenarios.R")
```

**Figure S1**. Sensitivity testing of seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50% (b).  Open and filled symbols represent default model and harvest values, while shaded symbols represent model sensitivity to each scenario by soil volume treatment. Both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.

**Table S1** Seedling Growth Model Default Parameters

# References {.unnumbered}

### 2015-07-14 manuscript/manuscript_pve.Rmd
added in methods

@@
 ## Experimental design
+This experiment was located at the Hawkesbury Forest Experiment site in Richmond, NSW, Australia.
+Plots were located in open cover with a site history that consists of a paddock that was converted from native pasture grasses.
+Top soils at this site, used for the study, are an alluvial formation of low-fertility sandy loam soils (380 and 108 mg kg^-1^ total N and phosphorus respectively) with low organic matter (0.7%) and low water holding capacity.
+At this site a soil hard layer exists at ~1.0 m with a transition to heavy clay soils.
+The climate for the region is classified as sub-humid temperate.
+
+\
+*Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain cohort.
+Previous experiments have confirmed that species with tap roots (similar to *E.
+tereticornis*) use the center of the container as the medium for thick roots leaving the periphery of the soil as the most active sites for fine root proliferation [@biran1980a; @biran1980b].
+This is generally hypothesized to be a different response than seedlings with no taproot.
+By using a species with tap root growth and manipulations of container length rather than width, it is believed that a more realistic test of inhibition of growth through constrained soil volume would be achieved.
+Six seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.
+
+\
+Six container volumes were used ranging from 5 l to 35 l, with a 22.5 cm diameter, and lengths ranging from 15 to 100 cm.
+Containers were constructed of PVC pipe and were filled with local top soil (described above).
+Soil in each container was packed to achieve a target soil bulk density of 1.7 g m^-3^.
+A Imidacloprid (BAYER CropScience) insecticide tablet was planted 5 cm below the roots of each seedling.
+Containers were planted flush with the soil surface inside metal sleeves, designed to minimize excess air space between the container and outside soil while also allowing for container removal.
+This allowed for soil temperatures in containers to reflect conditions of naturally sown (free) seedlings.
+Each experimental block (n=7) contained a complete replicate set of container volumes as well as one free seedling, with 1 m^2^ spacing.
+For each free seedling, used as the control, a 1 m^2^ subplot was excavated to 0.5 m and replaced with the same soil used in each container.
+A border of root exclusion material was buried 0.25 m deep and extended 0.25 m above the ground surface around each subplot to exclude local vegetation.
+
+\
+Plants were watered weekly or when needed, accounting for natural precipitation, to maintain soil moisture at field capacity (13-15%).
+Drain systems were built into each pot to prevent pooling of water in containers before root expansion, from reduced root uptake, or from large rainfall events.
+These conditions could lead to an anaerobic environment around the root that could hinder the uptake of water through reduced root conductance [@poorter2009causes], an undesired experimental artifact.
+A collection compartment in the bottom of containers, containing gravel covered by root exclusion mesh, was used to collect excess water for 20, 25, and 35 l containers.
+Plastic tubing (6~mm diameter) was inset into the gravel layer and extended through the top of the container.
+A lysimeter pump was then used to suction excess water, through the tubing, as needed .
+As small containers (5, 10, and 15 l) have a larger irradiation effect a simple bottom plug was used to drain excess water from the gravel compartment.
 
 ## Growth and morphology metrics
+Seedlings were planted on January 21^st^ 2013 and stem height, diameter at 15~cm and leaf count were measured weekly thereafter.
+Once the growth rate of individual plants had significantly declined a full biomass harvest was completed (May 21^st^ 2013).
+Dry mass of leaves, stems, roots and cumulative leaf area (LI-3100C Area Meter; LI-COR, Lincoln, NE, USA) was measured for each seedling.
+Mean individual leaf area for each harvested seedling was calculated by dividing cumulative leaf area by total leaf count of only fully expanded leaves.
+This value was then used to interpolate cumulative leaf area through time with weekly leaf counts.
+Root mass was collected by passing soil from each container through a 1 mm sieve, washing, separating into fine and coarse roots (<2 mm and >2 mm diameter, respectively) and then drying to a constant mass.
+Roots from the free seedlings were collected by excavating each 1 m^2^ subplot to 0.5 m depth.
+25 g fresh weight subsamples of washed fine roots were analyzed, using WhinoRhizo software (Regent Instruments Inc.), for specific root length (SRL, cm~m^-1^).
 
 ## Photosynthetic parameters
+Leaf gas exchange measurements were performed bi-weekly at saturating light (A~sat~) and saturating light and [CO~2~] (A~max~) on new fully expanded leaves.
+Measurements were initiated only after sufficient new leaf growth occurred (March 17^th^, 2013), approximately 6 weeks following planting, and continued until the biomass harvest.
+Leaf level gas exchange was measured with a standard leaf chamber equipped with blue-red light emitting diodes using a portable gas exchange system (LI-6400, LI-COR, Lincoln, NE, USA).
+A~sat~ measurements were made at PPFD of 1800 $\mu$mol m^-1^ s^-1^ and [CO~2~] of 400 $\mu$l l^-1^ and A~max~ with [CO~2~] of 1600 $\mu$l l^-1^ and PPFD of 1800 $\mu$mol~photons m^-1^ s^-1^.
+This choice of light level to achieve light saturation is consistent with other studies on *Eucalyptus* species [@kallarackal1997ecophysiological;@pinkard1998photosynthetic;@crous2013photosynthesis;@drake2014capacity].
+These measurements were conducted during midday (10:00-14:00 h) with leaf temperature maintained at 25&deg;C.
+After leaves acclimated to the chamber environment, net CO~2~ assimilation rate and stomatal conductance (g~s~) were logged 5 times for both A~sat~ and A~max~.
+
+\
+Photosynthetic CO~2~ response (AC~i~) curves were also developed at 25&deg;C on a random subset of each container size (n=3) after new leaves were first produced and immediately prior to the final harvest (May 23^rd^ 2013).
+Each AC~i~ curve began at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25&deg;C at saturating light (above).
+From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical].
+
+\
+Leaf dark respiration rates (R~d~) was measured on each seedling during the same dates as AC~i~ curves using detached leaves inside a conifer chamber attached to the Licor 6400 at least 1 hour after sundown.
+Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions.
+Reported values of R~d~ are standardized rates at 25&deg;C using a Q10 value (1.86) developed for these seedlings in a separate experiment (Drake et al.
+unpublished).
+Leaf area and dry mass were recorded for each leaf during gas exchange campaigns.
 
 ## Leaf water potential
+Predawn ($\Psi$~pd~) and midday ($\Psi$~l~) leaf water potentials were measured for each seedling using a PMS 1505D pressure chamber (PMS Instruments, Albany, OR, USA) on fully expanded leaves during the same time period as AC~i~ and R~d~.
+Leaves were detached and immediately stored inside foil covered bags before water potential measurements were performed.
+$\Psi$~pd~ was measured before sunrise and $\Psi$~l~ at midday 13:00-14:30 h.
+These measurements were used as a measure of static water stress on the seedlings \citep{sellin1999does}, and to ensure that the bulk soil water availability was high enough for plants as they became larger and roots filled the soil volume.
 
 ## Leaf, root and soil chemistry
+Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of N content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
+Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis.
+Nitrogen concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of N~2~ and CO~2~).
+The percentage of N in the sample was calculated by comparison with known standards.
+Leaf $\delta$^13^C was analyzed  with an Delta V Advantage coupled to a Flash HT and Conflo IV isotope ratio mass spectrometer.
+Leaf samples were flash combusted at 1000&deg;C to convert to to CO~2~, feed to the mass spectrometer and isotopic signatures are reported relative to the VPDP scale.
+Leaf TNC concentration was analyzed using a total starch assay kit (Megazyme International 303 Ireland Ltd., Wicklow, Ireland) and includes the starch (mg g^-1^) and soluble sugar (mg g^-1^) concentrations.
+Starch was quantified using a thermostable $\alpha$-amylase and amyloglucosidase assay [@McCleary_starch] and soluble sugars were determined following the anthrone method [@ebell1969variation].
+Complete methods of the TNC assay are described in [@mitchell2013drought].
+Specific leaf area (SLA, m^2^ kg^-1^), for leaves sampled during gas exchange campaigns, was then calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass.
 
 ## Seedling growth model
+
+We developed a simple seedling growth model that utilized leaf A rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
+The model begins with mean initial tissue component biomass (leaf~i~, stem~i~ and root~i~) and a starting leaf area (LA~i~ measured prior to planting.
+The initial biomass of roots was divided evenly between fine and coarse roots.
+The daily net biomass production of seedlings (P~i~) is then given by
+
+\
+(1)
+$$P_i = L\left(\frac{C_{day'i}~\sigma_s}{\epsilon_c}\right) - R$$
+where L is total plant leaf area, C~day,i~ is the predicted daily carbon assimilation, $\sigma$~s~ is a self shading parameter, $\textepsilon$~c~ is a biomass conversion efficiency parameter and R is the total respiration of all tissue components.
+Total respiration was calculated as
+
+\
+(2)
+$$R = \Sigma(R_c~M_c)$$
+where R~c~ is tissue respiration of fine roots, coarse roots or stems on a mass basis and M~c~ is the standing biomass of each component.
+R~leaf~ is represented in the calculation of C~day~ (described below).
+The change in individual component biomass (M~c~), here solved on a daily time step, is given by
+
+\
+(3)
+$$\frac{dM_c}{dt} = A_{c}~P_{i}~-~(\Lambda_{c}~M_{c})$$
+where A~c~ is the component specific biomass partitioning  to whole plant biomass (%) and $\Lambda$~c~ is component specific turnover rate.
+Due to the duration of the experiment $\Lambda~stem~ was assumed to equal 0.
+Total seedling biomass, per time step, was then equal to the sum of all biomass components; leaves, stems, fine roots and coarse roots.
+
+\
+C~day~ was predicted by fitting a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] in the 'plantecophys' package in R [@Duursma2014] to the mean photosynthetic parameters (R~d~, J~max~, V~cmax~, and g~1~) for each treatment and meteorological data from an onsite weather station.
+Examples of the photosynthesis model are described in Medlyn et al.
+[-@medlyn2002temperature] and the approach of the coupled leaf gas exchange model are described in Duursma et al [-@duursma2014peaked].
+The g~1~ parameter was generated by fitting observed g~s~ values into the optimal stomatal conductance model from [@medlyn2012reconciling].
+Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15~m intervals, leaf A rates ($\mu$mol~CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
+Rates were assumed to be representative of the entire 15~min meteorological interval.
+C~day~ was calculated by converting predicted rates to mass C gain over 15~min (g~m^-2^) and then summed for 24 h.
+This resulted in 120 unique values of C~day~ for each soil volume treatment, one value for each day of the experiment.
+Thus, each daily time step for model runs included a value of C~day~ that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
+
+\
+It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf A with total plant leaf area.
+This was accomplished by utilizing 61 previously digitized Eucalyptus seedlings, covering 5 total species which include *E.
+tereticornis*, from Duursma et al.
+[-@duursma2012light] to run in 'YplantQMC' package in R (fix cite YplantQMC) to build a 3d plant structure based on digitized metrics of plant allometry and crown structure.
+Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total A, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
+The ratio of total A with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedling, independently for each treatment.
+Next, the linear relationship between $\sigma$~s~ and total leaf area was for determined across digitized seedlings, within each treatment.
+For the growth model, $\sigma$~s~ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to C~day,i~.
+All default parameters used in model simulations are reported in Table.~\ref{table:Table3}.
 
@@
 # Discussion
-
-![figure](master_scripts/manuscript_figs/png/Cday.png)
 

### 2015-07-15 manuscript/manuscript_pve.Rmd
finsihed results, started on intro

@@
 
+```{r, echo=FALSE}
+airvarsfig <- "1"
+allomfig <- "2"
+allocfig <- "3"
+asatfig <- "4"
+achemfig <- "5"
+massmodelfig <- "6"
+massmodelfig2 <- "S1"
+```
+
 # Abstract {.unnumbered}
@@
 # Introduction
+
+##Growth and photosynthesis are not always correlated when either sinks (controlling G) or photosynthesis is manipulated.
+
+Should be more about allocation.
+You mention this but carbon balance must always be respected, so it is about where does the carbon end up (and what do we normally assume about this), not so much about whether A 'controls' G or vice versa.
+This is certainly how much of the literature has been phrased but you should comment on that, not follow that.
+
+##This begs the question where the carbon ends up; clearly we must still have carbon balance
+
+##Let's do another manipulative experiment where we affect the sink because we know little about carbon allocation responses to source or sink manipulations in trees.
+
+##We hypothesized that trees would grow slower in small pots but that growth and photosynthesis would be coordinated mediated by a down-regulation of photosynthesis
+This study utilizes a novel field design to investigate the coordination between growth and A in *Eucalyptus tereticornis* Sm.~seedlings, by manipulating container size and thus rooting volume.
+Seedlings were maintained under well watered conditions in order to evaluate only the effect of restricted soil volume and the limited nutrient resource pool.
+We used freely-rooted seedlings as a control for the container size treatments.
+Empirical results were combined with a simple plant growth model to simulate seedling growth with a C mass balance approach, which was then compared to observed harvested seedling mass.
+The model used whole-plant C gain, scaled from instantaneous rates of leaf A, to quantify seedling production over 120 days.
+
+1).
+The manipulations of container size were expected to induce a belowground sink limitation compared to free seedlings.
+We hypothesized that declines in seedling grow would be largest in the smallest containers, mediated by a down-regulation of photosynthesis.
+
+2).
+Resuced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, which can inhibit photosynthsis.
+We therefore expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume.
+
+3). Last, the growth model was expected to find agreement between simulated and observed seedling mass, through direct correlation of the effects of limiiting soil volume on A.
 
@@
 Leaf level gas exchange was measured with a standard leaf chamber equipped with blue-red light emitting diodes using a portable gas exchange system (LI-6400, LI-COR, Lincoln, NE, USA).
-A~sat~ measurements were made at PPFD of 1800 $\mu$mol m^-1^ s^-1^ and [CO~2~] of 400 $\mu$l l^-1^ and A~max~ with [CO~2~] of 1600 $\mu$l l^-1^ and PPFD of 1800 $\mu$mol~photons m^-1^ s^-1^.
+A~sat~ measurements were made at PPFD of 1800 $\mu$mol m^-1^ s^-1^ and [CO~2~] of 400 $\mu$l l^-1^ and A~max~ with [CO~2~] of 1600 $\mu$l l^-1^ and PPFD of 1800 $\mu$mol photons m^-1^ s^-1^.
 This choice of light level to achieve light saturation is consistent with other studies on *Eucalyptus* species [@kallarackal1997ecophysiological;@pinkard1998photosynthetic;@crous2013photosynthesis;@drake2014capacity].
@@
 $$P_i = L\left(\frac{C_{day'i}~\sigma_s}{\epsilon_c}\right) - R$$
-where L is total plant leaf area, C~day,i~ is the predicted daily carbon assimilation, $\sigma$~s~ is a self shading parameter, $\textepsilon$~c~ is a biomass conversion efficiency parameter and R is the total respiration of all tissue components.
+where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g d^-1^), $\sigma$~s~ is a self shading parameter, $\textepsilon$~c~ is a biomass conversion efficiency parameter and R is the mass based total respiration of all tissue components.
 Total respiration was calculated as
@@
 $$R = \Sigma(R_c~M_c)$$
-where R~c~ is tissue respiration of fine roots, coarse roots or stems on a mass basis and M~c~ is the standing biomass of each component.
+where R~c~ is tissue respiration of fine roots, coarse roots or stems (g C g mass^-1^) and M~c~ is the standing biomass of each component.
 R~leaf~ is represented in the calculation of C~day~ (described below).
@@
 \
-C~day~ was predicted by fitting a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] in the 'plantecophys' package in R [@Duursma2014] to the mean photosynthetic parameters (R~d~, J~max~, V~cmax~, and g~1~) for each treatment and meteorological data from an onsite weather station.
+C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] in the 'plantecophys' package in R [@Duursma2014] with the mean photosynthetic parameters (J~max~, V~cmax~, R~d~ and g~1~) for each treatment and meteorological data from an onsite weather station.
+J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), R~d~ was emprically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2012reconciling] with observed g~s~ values.
 Examples of the photosynthesis model are described in Medlyn et al.
 [-@medlyn2002temperature] and the approach of the coupled leaf gas exchange model are described in Duursma et al [-@duursma2014peaked].
-The g~1~ parameter was generated by fitting observed g~s~ values into the optimal stomatal conductance model from [@medlyn2012reconciling].
 Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15~m intervals, leaf A rates ($\mu$mol~CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
-Rates were assumed to be representative of the entire 15~min meteorological interval.
-C~day~ was calculated by converting predicted rates to mass C gain over 15~min (g~m^-2^) and then summed for 24 h.
+C~day~ was calculated by converting predicted rates to mass C gain over 15~min timesteps (g~m^-2^) and then summed for 24 h.
 This resulted in 120 unique values of C~day~ for each soil volume treatment, one value for each day of the experiment.
@@
 ## Growth and morphology metrics
+In this field study, colder temperatures and reductions in cumulative PPFD per day (Fig.
+`r airvarsfig`) most likely lead to the reduced growth in the free seedlings in the final weeks of the experiment (Fig.
+`r allomfig`).
+Combined with severe growth reductions in the smallest container volumes the experiment was chosen to be harvested after 120 days.
+Over this duration height, diameter, and leaf area diverged between container volumes (Fig.
+`r allomfig`).
+First, seedling leaf area significantly diverged between soil volumes (P<0.026) during the 5^th^ week of the experiment.
+Following this period both height (8^th^} week) and then diameter (9^th^ week) significantly deviated across soil volumes (P<0.002 & 0.001, respectively).
+Negative growth effects then manifested as severely reduced height gain and declining leaf area through time with small soil volumes across the final two months of the experiment.
+Seedlings maintained diameter growth throughout the experiment, although marginal with smaller soil volumes in the final month.
+Final seedling height significantly increased with increasing soil volume (P<0.001).
+Increases in both final stem diameter (P<0.001) and cumulative leaf area (both P<0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling.
+
+\
+Total seedling biomass at harvest was significantly different across container volumes (P<0.001) and with free seedlings (P<0.001, Table.
+1).
+We analyzed the relationship between biomass growth with each fold increase in soil volume and found an increase of 34% with a doubling of pot size, consistent with the meta-analysis of Poorter et al.
+[-@poorter2012pot].
+Additionally, plant biomass was highly correlated with total leaf area across all treatments (R^2^ = 0.97, P<0.001).
+Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass within treatments was factored in the analysis (Fig.`r allocfig`a,b).
+Across all treatments, the final harvested root:shoot was conserved in these seedlings, with a slightly higher shoot than root mass on average ($\overline{x}$=0.904, Fig.
+`r allomfig`c).
+
+\
+SRL of harvested fine roots was not different across soil volumes (Table.
+1).
+Over the duration of the experiment SLA was higher in free seedlings but was not different across containers sizes (Table.
+1, P<0.001) and this pattern was evident in the first gas exchange measurement campaign (P<0.001).
 
 ## Leaf chemistry
+Leaf N % was significantly higher in free seedlings and the largest container volume at the onset of gas exchange measurements (6th week, P<0.001).
+Over the remaining duration of the experiment the smallest container volume had a significant reduction in leaf N % compared to other soil volumes, while free seedlings maintained the highest leaf N % (Table.
+1, P<0.001).
+Leaf starch content in the smallest container was double that of free seedlings (P=0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table.
+1).
+Differences in leaf starch between the free seedling and the smallest container were also evident during the first gas exchange campaign (P=0.0013).
 
 ## Gas exchange and photosynthetic parameters
+A~sat~ and A~max~ were both significantly higher in the largest container volume and the free seedling at the first measurement campaign (both P<0.001).
+Across all measurement campaigns A~sat~ (Fig.
+`r asatfig`) and A~max~ (Table 2.) were consistently higher in free seedlings than in containers (boht P<0.001).
+The interaction between photosynthetic capacity, leaf starch, and leaf N on a mass basis was marginally significant (P=0.0584) but A~max~ was highly correlated to both leaf N content and leaf starch (both P<0.001).
+Across all measurement campaign A~max~ was higher when foliar N was also higher, usually associated with low levels of leaf starch (Fig.
+`r achemfig`a).
+A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Fig.
+`r achemfig`b)
+
+\
+The photosynthetic parameters J~max~ and Vc~max~ were not different within treatments at the beginning and end of gas exchange campaigns, therefore the parameter means per treatment are reported here (Table.
+2).
+Overall, both J~max~ and Vc~max~ were significantly higher in free seedlings with little variation between soil volume treatments (P=0.0012 & 0.0021, respectively).
+Leaf dark respiration rates were not significantly different across soil volumes (Table.
+2).
+The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2012reconciling] optimal stomatal conductance model, was lowest in the free seedling and was marginally different across soil volume treatments (Table.
+2).
+Predicted values of g~s~, using the g~1~parameter, where highly correlated with observed values (R^2^= .74, P<0.001, data not shown).
+
+\
+Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 mPa across all seedlings, respectively.
+Although P=0.001), the mean rates for all seedlings were high at 0.37 mol H~2~0 m^-2^ s^-1^ and did not decline significantly across the experiment duration.
+Additionally, leaf {$\delta$^13^C at final harvest was not different across treatments (Table.
+1).
+Combined these indices provide strong evidence that water stress was not apparent on these well-watered seedlings throughout the experiment.
+Soil N % at harvest was not different across soil volumes ($\bar{x}$=04.5 %) and decreased approximately 3 % across all containers over the experiment duration.
+This indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
 
 ## Modelling seedling biomass
+Model M~0~, was able to converge on an optimum leaf mass fraction (LMF, 21.6 \%) which predicted the mean harvest total biomass of free seedlings within 1.2 %.
+Using this optimized LMF, the total biomass of modeled seedlings with soil volume restriction (M~1~) was on average 23&pm;2.4 g C more than measured seedlings when comparing against predicted total net leaf C gain (Fig.
+`r massmodelfig`a).
+Thus, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the reductions in daily C assimilation per treatment (Fig.
+`r massmodelfig`b).
+As a result, the reductions in leaf A were not sufficient enough to explain the reduction in harvested seedling biomass with soil volume restriction.
+This resulted in an unexplained pool of excess C, generated from A, that was not allocated to biomass.
+
+\
+The remaining model simulations tested possible C allocation scenarios to account for this excess pool of C.
+Constraining the model by treatment-specific LMF from the final harvest (M~2~) still overestimated seedling total C by 32&pm;11.1 %, but provided the most improved model predictions (Fig.
+`r massmodelfig2`a).
+Using harvested LMF, however, does not capture the increase in senescence of seedlings in small containers (Fig.
+`r allomfig`c).
+Thus, the 7-61 % reduction in measured harvested leaf mass fraction from large to small soil volumes compared to the optimized LMF (M~0~) represents an underestimation of realized leaf C allocation.
+Increases of 50 % in non-leaf tissue respiration (M~3~) improved biomass estimates slightly but overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Fig.
+`r massmodelfig2`b).
+It was further determined that non-tissue respiration rates in modeled seedlings would need to increase by ca.
+250 % to account for this entire pool of C.
 
 # Discussion
+As issues still remain regarding how source-sink coordination affects growth of woody species, this study utilized a simple but novel field design to manipulate belowground sink limitations in order to physically restrict *Eucalyptus tereticornis* seedling production.
+We then addressed questions regarding the coordination of A and growth by complementing empirical results with modelling approaches.
+We found that reductions in leaf A rates were not sufficient to explain observed reductions in total plant biomass production.
+We thus encourage the utilization of mass balance approaches and provide direction for future studies when testing factors that control of plant growth under environmental change.
+
+##model setup
+I think the point here is that the model is quite standard and classical.
+It has growth driven by fluctuations in photoynthesis but respiration and allocation are very fixed processes.
+This reflects much of the growth&production modelling work out there.
+It turns out that in your experiment this did not really work, which means we must take a closer look at allocation and respiration (including root exudation)
+##growth and photosythesis not coordianted as expeceted, consequences for studies of biomass allocation
 

### 2015-07-16 manuscript/manuscript_pve.Rmd
add intro to manuscript

@@
 
-##Growth and photosynthesis are not always correlated when either sinks (controlling G) or photosynthesis is manipulated.
+Understanding plant growth requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
+As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues sinks.
+At long enough time scales A and growth must be correlated in respect to mass balance, however, at shorter temproal scales growth is not necessarily limited by the availability of recent photosynthate.
+This has led to the current debate over how strongly plant growth is controlled by either source of sink activity.
+Consequently, plant growth cannot be simply determined by rates of A making it complex to understand and challenging to model [@fourcaud2008plant].
+Despite a wealth of studies large uncertainties still remain regarding the coordination of C supply, via A, and growth of woody species.
 
-Should be more about allocation.
-You mention this but carbon balance must always be respected, so it is about where does the carbon end up (and what do we normally assume about this), not so much about whether A 'controls' G or vice versa.
-This is certainly how much of the literature has been phrased but you should comment on that, not follow that.
+\
+In woody species, the coordination of A and growth has been studied with manipulations of C source activity.
+Examples included elevated CO~2~ experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments.
+Elevated CO~2~ has been shown to increase A rates [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a conserved increase in forest production [@norby2005forest].
+Evidence from elevated CO~2~ experiments, however, also reveals that the growth response tends to be much smaller than the photosynthetic enhancement [@kirschbaum2011does].
+In defoliation experiments, compensatory increases in A are commonly shown yet are attributed to variable mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], leaf nutrient status [@turnbull2007increased], and regulatory sugar signaling [@eyles2013whole].
+However, increases in A did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
+These manipulations of C source activity expose unresolved issues with how changes in A do not always infer similar responses in growth.
 
-##This begs the question where the carbon ends up; clearly we must still have carbon balance
+\
+Alternatively, manipulating plant tissue C sinks is often used to investigate the correlation of A and growth.
+This is because metabolic signaling networks, relaying information on C and N status of different tissues, can down regulate photosynthetic activity [@paul2001sink].
+If this sink inhibition of A occurs then a close coordination between declines in A and growth should be expected.
+Whether this photosynthetic down regulation is evident in woody species has been tested through fruit removal, girdling, and low temperatures.
+In these studies, down regulation of A was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
+However, reductions in A were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic], and stomatal limitation [@li2005photosynthesis].
+These mixed results are not surprising as we still know little about the pathways in which plants achieve balance between assimilation, storage, and growth across temporal scales [@smith2007coordination].
+As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to large annual fruiting sinks, they tell us little about source-sink coordination in ‘normal’ field-grown woody species.
 
-##Let's do another manipulative experiment where we affect the sink because we know little about carbon allocation responses to source or sink manipulations in trees.
+\
+If source or sink manipulations do not lead to equivalent changes in growth then understanding the fate of assimilated carbon becomes even more crucial.
+As programmed plasticity in C allocation naturally occur as plants growth and develop, this must be accounted for when evaluating induced variation in growth [@wright2002interpreting].
+Thus, when C allocation is altered by a treatment, it should be shown whether these allocation patterns differ from common sized untreated plants [@reich2002root;@poorter2012biomass].
+Only then can we test if functional balance preservation or optimal foraging occurs from changes in C uptake.
+For example, seedlings in containers may shift allocation to leaves if root restriction occurs or alter fine root morphology to increase nutrient uptake.
+In woody species, shifts in allometric relationships of leaves, stems and roots can reveal if growth is ontogenetically constrained or actively adjusted when A is affected.
+This then allows additional pools of carbon, such as root exudation or changes in tissue respiration, to be accounted for and mass balance to be achieved.
 
-##We hypothesized that trees would grow slower in small pots but that growth and photosynthesis would be coordinated mediated by a down-regulation of photosynthesis
-This study utilizes a novel field design to investigate the coordination between growth and A in *Eucalyptus tereticornis* Sm.~seedlings, by manipulating container size and thus rooting volume.
+\
+An alternative experimental approach is to lower belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size.
+The advantage of this approach is it allows a large range of manipulations, can be easily compared to naturally planted seedlings and mimics natural conditions as seedlings compete for space or reach bedrock.
+Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, A, water relations, nutrient uptake and respiration [@nesmith1998effect, and references therein].
+Inadequate rooting volume may decrease carbon sink strength by progressively restricting root growth [@thomas1991root].
+Container size studies frequently have photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
+A meta-analysis by Poorter et al.
+[-@poorter2012pot] concluded that A is the process likely to be the strongest affected by pot size and may best explain the observed effect on biomass seen in the large number of studies where containers are used.
+This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower C exchange and assimilate export rates [@robbins1988effect].
+However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].
+Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test how growth and A are coordinated.
+
+\
+This study utilizes a novel field design to investigate the coordination between growth and A in *Eucalyptus tereticornis* Sm.
+seedlings, by manipulating container size and thus rooting volume.
 Seedlings were maintained under well watered conditions in order to evaluate only the effect of restricted soil volume and the limited nutrient resource pool.
@@
 2).
-Resuced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, which can inhibit photosynthsis.
+Reduced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, which is known to inhibit photosynthsis.
 We therefore expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume.
@@
 ## Seedling growth model
-
 We developed a simple seedling growth model that utilized leaf A rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
@@
 $$P_i = L\left(\frac{C_{day'i}~\sigma_s}{\epsilon_c}\right) - R$$
-where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g d^-1^), $\sigma$~s~ is a self shading parameter, $\textepsilon$~c~ is a biomass conversion efficiency parameter and R is the mass based total respiration of all tissue components.
+where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g d^-1^), $\sigma$~s~ is a self shading parameter, $epsilon$~c~ is a biomass conversion efficiency parameter and R is the mass based total respiration of all tissue components.
 Total respiration was calculated as
@@
 $$R = \Sigma(R_c~M_c)$$
-where R~c~ is tissue respiration of fine roots, coarse roots or stems (g C g mass^-1^) and M~c~ is the standing biomass of each component.
+where R~c~ is tissue respiration of fine roots, coarse roots or stems (g C g mass^-1^) and M~c~ is the standing biomass of each component (g).
 R~leaf~ is represented in the calculation of C~day~ (described below).
@@
 where A~c~ is the component specific biomass partitioning  to whole plant biomass (%) and $\Lambda$~c~ is component specific turnover rate.
-Due to the duration of the experiment $\Lambda~stem~ was assumed to equal 0.
+Due to the duration of the experiment $\Lambda$~stem~ was assumed to equal 0.
 Total seedling biomass, per time step, was then equal to the sum of all biomass components; leaves, stems, fine roots and coarse roots.
@@
 \
-C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] in the 'plantecophys' package in R [@Duursma2014] with the mean photosynthetic parameters (J~max~, V~cmax~, R~d~ and g~1~) for each treatment and meteorological data from an onsite weather station.
+C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] in the 'plantecophys' package [@Duursma2014] in R [@RDevelopment] with the mean photosynthetic parameters (J~max~, V~cmax~, R~d~ and g~1~) for each treatment and meteorological data from an onsite weather station.
 J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), R~d~ was emprically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2012reconciling] with observed g~s~ values.
@@
 [-@medlyn2002temperature] and the approach of the coupled leaf gas exchange model are described in Duursma et al [-@duursma2014peaked].
-Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15~m intervals, leaf A rates ($\mu$mol~CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
-C~day~ was calculated by converting predicted rates to mass C gain over 15~min timesteps (g~m^-2^) and then summed for 24 h.
+Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15~m intervals, leaf A rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
+C~day~ was calculated by converting predicted rates to mass C gain over 15~min timesteps (g m^-2^) and then summed for 24 h.
 This resulted in 120 unique values of C~day~ for each soil volume treatment, one value for each day of the experiment.
@@
 For the growth model, $\sigma$~s~ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to C~day,i~.
-All default parameters used in model simulations are reported in Table.~\ref{table:Table3}.
+All default parameters used in model simulations are reported in Table.3.
+
+\
+We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf A where sufficient to accurately predict overall seedling biomass production after 120 days.
+Each model run utilized changes in A and leaf mass fraction (LMF), with published or local values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
+Cumulative net leaf carbon gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling carbon was assumed to equal half of the final mass for both modeled and observed seedlings.
+First, a default model was optimized to produce a final LMF that correctly predicted both the final leaf mass and total biomass of the harvested free seedling controls (M~0~).
+This optimized LMF was then applied to model runs with treatment specific C~day~ to determine if changes in leaf A alone could accurately predict biomass (M~1~).
+Next, model sensitivity to different C allocation scenarios, including non-optimized treatment specific LMF and up regulation of non-leaf tissue respiration by 50 % of default values (M~2,3~, respectively), was used to improve predictions of initial model simulations from measured harvest biomass.
+For all cases, seedling production was compared between model output and harvested seedlings with treatment specific mean daily carbon assimilation by first scaling values to the free seedling control.
 
 ##Data analysis
-Differences in experimental parameters with soil volume were analysed by one-way analysis of variance (ANOVA) in R [@RDevelopment] with individual containers as random effects and soil volume as a categorical fixed effect.
+Differences in experimental parameters with soil volume were analysed by one-way analysis of variance (ANOVA) in R with individual containers as random effects and soil volume as a categorical fixed effect.
 Tukey’s post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
@@
 Tests of allometric relationships between biomass components were implemented using major axis regression in the 'smatr' package in R [@warton2012smatr].
-Results were considered significant at P&leq;0.05..
+Results were considered significant at P&leq;0.05.
 
@@
 Although P=0.001), the mean rates for all seedlings were high at 0.37 mol H~2~0 m^-2^ s^-1^ and did not decline significantly across the experiment duration.
-Additionally, leaf {$\delta$^13^C at final harvest was not different across treatments (Table.
+Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table.
 1).
@@
 ## Modelling seedling biomass
-Model M~0~, was able to converge on an optimum leaf mass fraction (LMF, 21.6 \%) which predicted the mean harvest total biomass of free seedlings within 1.2 %.
+Model M~0~, was able to converge on an optimum LMF (21.6 %) which predicted the mean harvest total biomass of free seedlings within 1.2 %.
 Using this optimized LMF, the total biomass of modeled seedlings with soil volume restriction (M~1~) was on average 23&pm;2.4 g C more than measured seedlings when comparing against predicted total net leaf C gain (Fig.
@@
 
+Our lack of knowledge regarding the allocation of C in woody species is still a major obstable in understanding the cooridatnation between A and growth.
+
+A lack of knowledge regarding the allocation of carbon diminishes our ability to distinguish the drivers of plant growth because mass balance cannot be reached.
+
 ##model setup
@@
 ##growth and photosythesis not coordianted as expeceted, consequences for studies of biomass allocation
+
+ If control is indeed distributed aroundthe plant, an experiment designed qualitatively to detect the presence of some source limitation shouldﬁnd it; but so should an experiment designed to testfor sink limitation (Farrah and Jones).
+The reason that so many conflicting reslutls exist is because....
+
+ The fraction of assimilation used for respiration varies greatly among plants and increases with decreasing growth rates (Lambers et sl.
+2008)......
+problems with how we evaluate the respiration contribution of c allocation over shorter temporal scales .
+Our understanding of tissue respiration may also confound these short-term relationships with A and G.
+
+  It is rather the norm than the
+exception that sink activity feeds back on source activity (e.g. through end-product inhibition
+in the chloroplast), causing growth (demand for carbon) to control photosynthesis, rather than
+the other way round (Korner 2013).
 

### 2015-07-20 tables_latex/pve_manuscript.Rnw
added new folder with latek markdown for tables

\documentclass[a4paper]{article}

%--- Load packages. 
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{framed}
\usepackage{textcomp}

% avoid ugly indentation of paragraphs
\usepackage{parskip}
\usepackage{graphicx}

% open sans font
\usepackage[default,osfigures,scale=0.95]{opensans}

% subfolder with the figures (within manuscript/)
\graphicspath{ {./figures/} }

% for author affiliations
\usepackage{authblk}

%allows inline citations
\usepackage[round]{natbib}
\bibliographystyle{plainnat}

% for degree symbol
\usepackage{gensymb}

% for line numbers
\usepackage{lineno}

% margin size
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}

% for bibtex
% \usepackage{authordate1-4}
% \bibliographystyle{authordate1}

%allows subscripts in text mode
\usepackage{fixltx2e}

%allows rotation of table??
\usepackage{rotating}

%allows alignment of caption to the left
\usepackage{caption} 
\captionsetup[table]{singlelinecheck=false}

%allows not italic greek letters
\usepackage{textgreek}

\begin{document}

\linenumbers

\title{Effects of below-ground space limitation on performance of Eucalyptus seedlings:  Does photosynthesis really control growth?}

\author[1,3]{Courtney E. Campany}
\author[2]{Belinda E. Medlyn}
\author[1]{Remko A. Duursma}

\affil[1]{Hawkesbury Institute for the Environment, University of Western Sydney, Richmond, NSW 2753, Australia}
\affil[2]{Department of Biological Sciences, Macquarie University, North Ryde, NSW 2109, Australia}
\affil[3]{Corresponding author (c.campany@uws.edu.au)}

\renewcommand\Authands{ and }
\maketitle

%--------------------------------------------------------------------------------------------%

<<preload, echo=FALSE>>=
library(knitr)
opts_chunk$set(echo=FALSE)
@

%--------------------------------------------------------------------------------------------%

\section*{Abstract}

Interpreting limitations to plant growth requires understanding of the balance between carbon (\textit{C}) source and sink activity in order to assess \textit{C} allocation and biomass partitioning. This study used manipulations of soil volume to test how growth is coupled to physiology, allocation, and sink activity in \textit{Eucalyptus tereticornis} seedlings. We grew seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown seedlings (free). Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings. It was hypothesized that soil volume effect would be largest in the smallest containers, resulting in physical constraints to growth independently of photosynthesis (\textit{A}). Photosynthesis would then become sink-limited, resulting in the build-up of leaf nonstructural carbohydrates eventually leading to photosynthetic down regulation. We observed a negative container effect on aboveground growth soon after the experiment started. Although growth was consistently different across soil volumes mass, partitioning to leaves, stems, roots was conserved after 120 days. Photosynthetic capacity was also significantly reduced in containers, and was related to both leaf nitrogen content and starch accumulation. We developed a seedling growth model that utilized leaf \textit{A} rates to allocate daily \textit{C} uptake towards mass growth of stems, leaves and roots. We then asked whether the observed reductions in \textit{A} explained the observed differences in seedling biomass. We found that although belowground sink limitation resulted in the down regulation of \textit{A}, these reductions were not significant enough to explain observed growth responses. Thus, as photosynthesis and growth were not coordinated an excess pool of non-biomass \textit{C} resulted in seedlings with soil volume restriction. This research highlights the need to further utilize mass balance approaches when evaluating plant \textit{C} allocation and confirms that \textit{A} and growth are not always directly related.

\section*{Key Words}

photosynthesis, growth, sink regulation, carbon allocation, soil volume

\section*{Introduction}

Understanding plant growth requires knowledge of the mass balance that must be achieved between \textit{C} uptake and subsequent allocation to growth, storage, and respiration. It is commonly assumed plant growth is limited by \textit{C} availability, yet it has long been demonstrated that correlations between \textit{A} and growth are weak or seldom present. \citet{korner2013growth} argues that growth instead controls \textit{A}, as it is the norm for sink activity to feedback on source activity. This is supported by evidence that growth of plants under environmental stress is not limited by the supply of photoassimilates \citep{palacio2014does}. As woody plants have highly integrated systems of competing carbohydrate sinks \citep{kozlowski1992carbohydrate}, growth should principally depend on the transport of these photoassimilates between different tissue and organ sinks. Despite a wealth of studies, however, large uncertainties still remain regarding the coordination of \textit{C} supply, via \textit{A}, and growth of woody species.

In woody species, how \textit{A} controls growth has been studied with manipulations of \textit{C} source activity. Examples included elevated CO\textsubscript{2} experiments, for example FACE (reviewed in  \citet{ainsworth2005have}, and partial defoliation experiments. Elevated CO\textsubscript{2} has been shown to increase \textit{A} rates \citep{drake1997more,ainsworth2007response} and across four FACE experiments this resulted in a conserved increase in forest production \citep{norby2005forest}. Evidence from elevated CO\textsubscript{2} experiments, however, also reveals that the growth response tends to be much smaller than the photosynthetic enhancement \citep{kirschbaum2011does}. In defoliation experiments, compensatory increases in \textit{A} are commonly shown yet are attributed to variable mechanisms, including reduction in end product inhibition \citep{iglesias2002regulation,zhou2003changes,handa2005test}, enhanced biochemical activity \citep{ovaska1993b,layne1995end}, increased stomatal conductance \citep{layne1995end}, leaf nutrient status \citep{turnbull2007increased}, and regulatory sugar signaling \citep{eyles2013whole}. However, increases in \textit{A} did not always produce increased growth due to reductions in meristem sink strength (Palacio et al. 2012), \textit{C} limitation to mycorrhizal colonization (Markkola et al. 2004), or an overall decrease in whole plant \textit{C} gain \citep{ovaska1993a}. These manipulations of \textit{C} source activity expose unresolved issues with how changes in \textit{A} do not always infer similar responses in growth.

Alternatively, manipulation of plant tissue carbon sinks is often used to investigate the correlation of photosynthesis and growth. Tissue sink activity can restrict biomass production when limited by environmental or developmental constraints \citep{korner2003carbon}. This is because metabolic signaling networks, relaying information on \textit{C} and nitrogen (\textit{N}) status of different tissues, can down regulate photosynthetic activity \citep{paul2001sink}.  Whether this down regulation, via sink inhibition, is evident in woody species has been tested through fruit removal, girdling, and low temperatures. In these studies, down regulation of \textit{A} was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength \citep{iglesias2002regulation,hoch2002altitudinal,urban2007girdling, haouari2013fruit}. However, reductions in \textit{A} were also attributed to biochemical limitations prior to carbohydrate accumulation \citep{nebauer2011photosynthesis}, irreversible photo-oxidative damage \citep{duan2008photosynthetic}, and stomatal limitation \citep{li2005photosynthesis}. These mixed results are not surprising as we still know little about the pathways in which plants achieve balance between assimilation, storage, and growth across temporal scales \citep{smith2007coordination}. As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to large annual fruiting sinks, they tell us little about source-sink coordination in ‘normal’ field-grown woody species.

An alternative experimental approach is to lower belowground \textit{C} sink strength in tree seedlings by manipulating rooting volume, by varying the container size. The advantage of this approach is it allows a large range of manipulations, can be easily compared to naturally planted seedlings and mimics natural conditions as seedlings compete for space or reach bedrock. Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, \textit{A}, water relations, nutrient uptake and respiration \citep[and references therein]{nesmith1998effect}. Inadequate rooting volume may decrease carbon sink strength by progressively restricting root growth \citep{thomas1991root}.  Container size studies frequently have photosynthetic down-regulation, likely as a result of sink limitation \citep{arp1991effects, mcconnaughay1991physical, gunderson1994photosynthetic, sage1994acclimation, maina2002intra, ronchi2006growth}. A meta-analysis by \citet{poorter2012pot} concluded that \textit{A} is the process likely to be the strongest affected by pot size and may best explain the observed effect on biomass seen in the large number of studies where containers are used. This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower \textit{C} exchange and assimilate export rates \citep{robbins1988effect}. However, evidence in support for a trade-off between \textit{C} storage and growth in trees is, to date, inconclusive \citep{palacio2014does}. Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test how growth and \textit{A} are coordinated.

Our lack of knowledge regarding the allocation of \textit{C} in woody species is still a major obstable in understanding the cooridatnation between  \textit{A} and growth. Understanding the fate of assimilated \textit{C} is crucial when source or sink manipulations do not directly lead to equivalent changes in growth. As programmed plasticity in \textit{C} allocation naturally occur as plants growth and develop, this must be accounted for when evaluating induced variation in growth \citep{wright2002interpreting}. Thus, when \textit{C} allocation is altered by a treatment, it should be shown whether these allocation patterns differ from common sized untreated plants \citep{reich2002root, poorter2012biomass}. Only then can we test if functional balance preservation or optimal foraging occurs from changes in \textit{C} uptake. For example, seedlings in containers may shift allocation to leaves if root restriction occurs or alter fine root morphology to increase nutrient uptake. In woody species, shifts in allometric relationships of leaves, stems and roots can reveal if growth is ontogenetically constrained or actively adjusted when \textit{A} is affected. This then allows additional pools of \textit{C}, such as root exudation or changes in tissue respiration, to be accounted for and evaluated.

This study utilizes a novel field design to investigate the coordination between growth and \textit{A} in \textit{Eucalyptus tereticornis} Sm.~seedlings, by manipulating container size and thus rooting volume. Seedlings were maintained under well watered conditions in order to evaluate only the effect of restricted soil volume and the limited nutrient resource pool. We used freely-rooted seedlings as a control for the container size treatments.  Empirical results were combined with a simple plant growth model to simulate seedling growth with a \textit{C} mass balance approach, which was then compared to observed harvested seedling mass.  The model used whole-plant \textit{C} gain, scaled from instantaneous rates of leaf \textit{A}, to quantify seedling production over 120 days.

1). The manipulations of container size were hypothesized to induce a belowground sink limitation in these seedlings which was expected to be largest in the smallest containers, resulting in physical constraints to growth independently of \textit{A}.

2). Reducing soil volume was then expected to induce negative effects on leaf physiology compared to free seedlings (‘container effect’). This accumulation of leaf nonstructural carbohydrates was expected to trigger photosynthetic down regulation as a function of soil volume and create further negative feedbacks to growth through time.

3). Last, the growth model was expected to find agreement between simulated and observed seedling mass, through direct correlation of the effects of soil volume on rates of leaf \textit{A}.

\section*{Methods}

\subsubsection*{\textit{Experimental Design}}

This experiment was located on the Hawkesbury Forest Experiment site in Richmond, NSW, Australia. Plots were located in open cover with a site history that consists of a paddock that was converted from native pasture grasses. Top soils at this site, used for the study, are an alluvial formation of low-fertility sandy loam soils (380 and 108~mg~kg\textsuperscript{-1} total \textit{N} and phosphorus respectively) with low organic matter (0.7~\%) and low water holding capacity. At this site a soil hard layer exists at $\sim$1.0~m with a transition to heavy clay soils. The climate for the region is classified as sub-humid temperate.

\textit{Eucalyptus tereticornis} seedlings, 20~weeks old and approximately 40~cm tall in tube stock, were chosen from a single local Cumberland plain cohort. Previous experiments have confirmed that species with tap roots (similar to \textit{E. tereticornis}) use the center of the container as the medium for thick roots leaving the periphery of the soil as the most active sites for fine root proliferation \citep{biran1980a,biran1980b}. This is generally hypothesized to be a different response than seedlings with no taproot. By using a species with tap root growth and manipulations of container length rather than width, it is believed that a more realistic test of inhibition of growth through constrained soil volume would be achieved. Six seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.

Six container volumes were used ranging from 5~l to 35~l, with a 22.5~cm diameter, and lengths ranging from 15 to 100~cm. Containers were constructed of PVC pipe and were filled with local top soil (described above). Soil in each container was packed to achieve a target soil bulk density of 1.7~g~m\textsuperscript{-3}. A Imidacloprid (BAYER CropScience) insecticide tablet was planted 5 cm below the roots of each seedling. Containers were planted flush with the soil surface inside metal sleeves, designed to minimize excess air space between the container and outside soil while also allowing for container removal. This allowed for soil temperatures in containers to reflect conditions of naturally sown (free) seedlings. Each experimental block (n=7) contained a complete replicate set of container volumes as well as one free seedling, with 1 m\textsuperscript{2} spacing. For each free seedling, used as the control, a 1~m\textsuperscript{2} subplot was excavated to 0.5~m and replaced with the same soil used in each container. A border of root exclusion material was buried 0.25~m deep and extended 0.25~m above the ground surface around each subplot to exclude local vegetation.

Plants were watered weekly or when needed, accounting for natural precipitation, to maintain soil moisture at field capacity (13-15~\%). Drain systems were built into each pot to prevent pooling of water in containers before root expansion, from reduced root uptake, or from large rainfall events. These conditions could lead to an anaerobic environment around the root that could hinder the uptake of water through reduced root conductance \citep{poorter2009causes}, an undesired experimental artifact. A collection compartment in the bottom of containers, containing gravel covered by root exclusion mesh, was used to collect excess water for 20, 25, and 35~l containers. Plastic tubing (6~mm diameter) was inset into the gravel layer and extended through the top of the container. A lysimeter pump was then used to suction excess water, through the tubing, as needed . As small containers (5, 10, and 15~l) have a larger irradiation effect a simple bottom plug was used to drain excess water from the gravel compartment.

\subsubsection*{\textit{Growth and morphology metrics}}

Seedlings were planted on January 21\textsuperscript{st} 2013 and stem height, diameter at 15~cm and leaf count were measured weekly thereafter. Once the growth rate of individual plants had significantly declined a full biomass harvest was completed (May 21\textsuperscript{st} 2013). Dry mass of leaves, stems, roots and cumulative leaf area (LI-3100C Area Meter; LI-COR, Lincoln, NE, USA) was measured for each seedling. Mean individual leaf area for each harvested seedling was calculated by dividing cumulative leaf area by total leaf count of only fully expanded leaves. This value was then used to interpolate cumulative leaf area through time with weekly leaf counts. Root mass was collected by passing soil from each container through a 1~mm sieve, washing, separating into fine and coarse roots (\textless2~mm and \textgreater2~mm diameter, respectively) and then drying to a constant mass. Roots from the free seedlings were collected by excavating each 1~m\textsuperscript{2} subplot to 0.5~m depth.  25~g fresh weight subsamples of washed fine roots were analyzed, using WhinoRhizo software (Regent Instruments Inc.), for specific root length (SRL, cm~m\textsuperscript{-1}).

\subsubsection*{\textit{Photosynthetic parameters}}

Leaf gas exchange measurements were performed bi-weekly at saturating light (\textit{A}\textsubscript{sat}) and saturating light and [CO\textsubscript{2}] (\textit{A}\textsubscript{max}) on new fully expanded leaves. Measurements were initiated only after sufficient new leaf growth occurred (March 17\textsuperscript{th}, 2013), approximately 6 weeks following planting, and continued until the biomass harvest. Leaf level gas exchange was measured with a standard leaf chamber equipped with blue-red light emitting diodes using a portable gas exchange system (LI-6400, LI-COR, Lincoln, NE, USA). \textit{A}\textsubscript{sat} measurements were made at PPFD of 1800~{\textmugreek}mol~m\textsuperscript{-1}~s\textsuperscript{-1} and [CO\textsubscript{2}] of 400~{\textmugreek}l~l\textsuperscript{-1} and \textit{A}\textsubscript{max} with [CO\textsubscript{2}] of 1600~{\textmugreek}l~l\textsuperscript{-1} and PPFD of 1800~{\textmugreek}mol~photons~m\textsuperscript{-1}~s\textsuperscript{-1}. This choice of light level to achieve light saturation is consistent with other studies on \textit{Eucalyptus} species \citep{kallarackal1997ecophysiological,pinkard1998photosynthetic,crous2013photosynthesis,drake2014capacity}. These measurements were conducted during midday (10:00-14:00~h) with leaf temperature maintained at 25$\degree$C. After leaves acclimated to the chamber environment, net CO\textsubscript{2} assimilation rate and stomatal conductance (\textit{g}\textsubscript{s}) were logged 5 times for both \textit{A}\textsubscript{sat} and \textit{A}\textsubscript{max}. Photosynthetic CO\textsubscript{2} response (AC\textsubscript{i}) curves were also developed at 25$\degree$C on a random subset of each container size (n=3) after new leaves were first produced and immediately prior to the final harvest (May 23\textsuperscript{rd} 2013). Each AC\textsubscript{i} curve began at the reference [CO\textsubscript{2}] of 400~{\textmugreek}l~l\textsuperscript{-1} and then consisted of 12 additional steps from [CO\textsubscript{2}] of 50 to 1800~{\textmugreek}l~l\textsuperscript{-1}at 25$\degree$C at saturating light (above). From these curves the photosynthetic parameters, \textit{J}\textsubscript{max} and \textit{Vc}\textsubscript{max}, were quantified using the biochemical model of \citet{farquhar1980biochemical}. Leaf dark respiration rates (\textit{R}\textsubscript{d}) was measured on each seedling during the same dates as AC\textsubscript{i} curves using detached leaves inside a conifer chamber attached to the Licor 6400 at least 1 hour after sundown.   Measurements were taken at a reference [CO\textsubscript{2}] of 400~{\textmugreek}l~l\textsuperscript{-1} while leaf temperature was maintained at current ambient conditions. Reported values of \textit{R}\textsubscript{d} are standardized rates at 25$\degree$C using a Q10 value (1.86) developed for these seedlings in a separate experiment (Drake et al. unpublished). Leaf area and dry mass were recorded for each leaf during gas exchange campaigns.

\subsubsection*{\textit{Leaf water potential}}

Predawn ($\Psi\textsubscript{pd}$) and midday ($\Psi\textsubscript{l}$) leaf water potentials were measured for each seedling using a PMS 1505D pressure chamber (PMS Instruments, Albany, OR, USA) on fully expanded leaves during the same time period as AC\textsubscript{i} and \textit{R}\textsubscript{d}. Leaves were detached and immediately stored inside foil covered bags before water potential measurements were performed. $\Psi\textsubscript{pd}$ was measured before sunrise and $\Psi\textsubscript{l}$ at midday 13:00-14:30~h. These measurements were used as a measure of static water stress on the seedlings \citep{sellin1999does}, and to ensure that the bulk soil water availability was high enough for plants as they became larger and roots filled the soil volume.

\subsubsection*{\textit{Leaf, root and soil chemistry}}

Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of \textit{N} content, {\textdelta}\textsuperscript{13}C, and total non-structural carbohydrates (TNC). Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis. \textit{N} concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of \textit{N}\textsubscript{2} and CO\textsubscript{2}).  The percentage of \textit{N} in the sample was calculated by comparison with known standards. Leaf {\textdelta}\textsuperscript{13}C was analyzed  with an Delta V Advantage coupled to a Flash HT and Conflo IV isotope ratio mass spectrometer. Leaf samples were flash combusted at 1000$\degree$C to convert to to CO\textsubscript{2}, feed to the mass spectrometer and isotopic signatures are reported relative to the VPDP scale. Leaf TNC concentration was analyzed using a total starch assay kit (Megazyme International 303 Ireland Ltd., Wicklow, Ireland) and includes the starch (mg~g\textsuperscript{-1}) and soluble sugar (mg~g\textsuperscript{-1}) concentrations. Starch was quantified using a thermostable $\alpha$-amylase and amyloglucosidase assay \citep{McCleary_starch} and soluble sugars were determined following the anthrone method \citep{ebell1969variation}. Complete methods of the TNC assay are described in \citep{mitchell2013drought}. Specific leaf area (SLA, m\textsuperscript{2}~kg\textsuperscript{-1}), for leaves sampled during gas exchange campaigns, was then calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass.

\subsubsection*{\textit{Seedling growth model}}

We developed a simple seedling growth model that utilized leaf \textit{A} rates to allocate daily \textit{C} assimilate towards biomass production of stems, leaves, fine roots and coarse roots. The model begins with mean initial tissue component biomass (leaf\textsubscript{i}, stem\textsubscript{i} and root\textsubscript{i}) and a starting leaf area (LA\textsubscript{i}) measured prior to planting. The initial biomass of roots was divided evenly between fine and coarse roots. The daily net biomass production of seedlings (P\textsubscript{i}) is then given by
\begin{equation} P\textsubscript{i}=L~(C\textsubscript{day,i}~\sigma\textsubscript{s}~\epsilon\textsubscript{c}\textsuperscript{-1})-R
\label{eq:prod}
\end{equation}
where L is standing cumulative leaf area, C\textsubscript{day,i} is the predicted daily carbon assimilation, $\sigma\textsubscript{s}$ is a self shading parameter, \textepsilon\textsubscript{c} is a biomass conversion efficiency parameter and R is the total respiration of all tissue components. Total respiration was calculated as 
\begin{equation} R=\Sigma(R\textsubscript{c}~M\textsubscript{c})
\label{eq:resp}
\end{equation}
where R\textsubscript{c} is tissue respiration of fine roots, coarse roots or stems on a mass basis and M\textsubscript{c} is the standing biomass of each component. R\textsubscript{leaf} is represented in the calculation of C\textsubscript{day} (described below). The change in individual component biomass (M\textsubscript{c}), here solved on a daily time step, is given by
\begin{equation} \frac{dM\textsubscript{c}}{dt}=A\textsubscript{c}~P\textsubscript{i}-(\Lambda\textsubscript{c}~M\textsubscript{c})
\label{eq:mass}
\end{equation}
where A\textsubscript{c} is the component specific biomass partitioning  to whole plant biomass (\%) and $\Lambda\textsubscript{c}$ is component specific turnover rate. Due to the duration of the experiment $\Lambda\textsubscript{stem}$ was assumed to equal 0.  Total seedling biomass, per time step, was then equal to the sum of all biomass components; leaves, stems, fine roots and coarse roots.

\textit{C}\textsubscript{day} was predicted by fitting a coupled photosynthesis - stomatal conductance model \citep{farquhar1980biochemical,medlyn2011reconciling} in the 'plantecophys' package in R \citep{Duursma2014} to the mean photosynthetic parameters (R\textsubscript{d}, J\textsubscript{max}, V\textsubscript{cmax}, and g\textsubscript{1}) for each treatment and meteorological data from an onsite weather station.  Examples of the photosynthesis model are described in \citet{medlyn2002temperature} and the approach of the coupled leaf gas exchange model are described in \citet{duursma2014peaked}. The g\textsubscript{1} parameter was generated by fitting observed \textit{g}\textsubscript{s} values into the optimal stomatal conductance model from \citep{medlyn2012reconciling}. Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15~m intervals, leaf \textit{A} rates ({\textmugreek}mol~CO\textsubscript{2}~m\textsuperscript{-2}~s\textsuperscript{-1}) were then predicted for each soil volume treatment. Rates were assumed to be representative of the entire 15~min meteorological interval. \textit{C}\textsubscript{day} was calculated by converting predicted rates to mass \textit{C} gain over 15~min (g~m\textsuperscript{-2}) and then summed for 24~h. This resulted in 120 unique values of \textit{C}\textsubscript{day} for each soil volume treatment, one value for each day of the experiment. Thus, each daily time step for model runs included a value of \textit{C}\textsubscript{day} that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.

It was further necessary to calculate a self-shading parameter ($\sigma\textsubscript{s}$) when scaling leaf \textit{A} with cumulative seedling leaf area. This was accomplished by utilizing 61 previously digitized Eucalyptus seedlings, covering 5 total species which include \textit{E. tereticornis}, from \citet{duursma2012light} to run in 'YplantQMC' package in R (fix cite YplantQMC) to build a 3d plant structure based on digitized metrics of plant allometry and crown structure. Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total \textit{A}, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.  The ratio of total \textit{A} with self-shading to horizontal leaf was then used to calculate $\sigma\textsubscript{s}$ for each of the 61 digitized seedling, independently for each treatment. Next, the linear relationship between $\sigma\textsubscript{s}$ and total leaf area was for determined across digitized seedlings, within each treatment. For the growth model, $\sigma\textsubscript{s}$ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to \textit{C}\textsubscript{day,i}. All default parameters used in model simulations are reported in Table.~\ref{table:Table3}.

We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf \textit{A} where sufficient to accurately predict overall seedling biomass production after 120 days. Each model run utilized changes in \textit{A} and leaf mass fraction, with published or local values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.  Cumulative net leaf carbon gain for each treatment was equal to the sum of each value of \textit{C}\textsubscript{day,i} over 120 days and final seedling carbon was assumed to equal half of the final mass for both modeled and observed seedlings. First, a default model was optimized to produce a final leaf mass fraction that correctly predicted both the final leaf mass and total biomass of the harvested free seedling controls (M\textsubscript{0}).  This optimized leaf mass fraction was then applied to model runs with treatment specific \textit{C}\textsubscript{day} to determine if changes in  leaf \textit{A} alone could accurately predict biomass (M\textsubscript{1}). Next, model sensitivity to different \textit{C} allocation scenarios, including non-optimized treatment specific leaf mass fraction and up regulation of non-leaf tissue respiration by 50~\% of default values (M\textsubscript{2,3, respectively}), was used to improve predictions of initial model simulations from measured harvest biomass. For all cases, seedling production was compared between model output and harvested seedlings with treatment specific mean daily carbon assimilation by first scaling values to the free seedling control.

\subsubsection*{\textit{Data Analysis}}

Differences in experimental parameters with soil volume were analysed by one-way analysis of variance (ANOVA) in R with individual containers as random effects and soil volume as a categorical fixed effect. Tukey’s post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different. Mixed model ANOVAs of \textit{A}\textsubscript{max} and leaf chemistry were performed using the 'nlme' package \citep{nlme} in R and \textit{r}\textsuperscript{2} values of mixed models were computed as in \citet{nakagawa2013general}. Tests of allometric relationships between biomass components were implemented using major axis regression in the 'smatr' package in R \citep{warton2012smatr}. Results were considered significant at P$\leq$0.05.

\section*{Results}

\subsubsection*{\textit{Growth and morphology metrics}}

In this field study, colder temperatures and reductions in cumulative PPFD per day (Fig.~\ref{fig:figure1}) most likely lead to the reduced growth in the free seedlings in the final weeks of the experiment (Fig.~\ref{fig:figure2}).  Combined with severe growth reductions in the smallest container volumes the experiment was chosen to be harvested after 120~days. Over this duration height, diameter, and leaf area diverged between container volumes (Fig.~\ref{fig:figure2}).  First, seedling leaf area significantly diverged between soil volumes (\textit{P}\textless0.026) during the 5\textsuperscript{th} week of the experiment. Following this period both height (8\textsuperscript{th} week) and then diameter (9\textsuperscript{th} week) significantly deviated across soil volumes (\textit{P}\textless0.002 \& 0.001, respectively).  Negative growth effects then manifested as severely reduced height gain and declining leaf area through time with small soil volumes across the final two months of the experiment. Seedlings maintained diameter growth throughout the experiment, although marginal with smaller soil volumes in the final month. Final seedling height significantly increased with increasing soil volume (\textit{P}\textless0.001).  Increases in both final stem diameter (\textit{P}\textless0.001) and cumulative leaf area (both \textit{P}\textless0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling.

Total seedling biomass at harvest was significantly different across container volumes (\textit{P}\textless0.001) and with free seedlings (\textit{P}\textless0.001, Table.~\ref{table:Table1}). We analyzed the relationship between biomass growth with each fold increase in soil volume and found an increase of 34~\% with a doubling of pot size, consistent with the meta-analysis of \citet{poorter2012pot}. Additionally, plant biomass was highly correlated with total leaf area across all treatments (\textit{r}\textsuperscript{2}~=~0.97, \textit{P}\textless0.001). Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass within treatments was factored in the analysis (Fig.~\ref{fig:figure3}a,b). Across all treatments, the final harvested root:shoot was conserved in these seedlings, with a slightly higher shoot than root mass on average ($\overline{x}$=0.904, Fig.~\ref{fig:figure3}c).

SRL of harvested fine roots was not different across soil volumes (Table.~\ref{table:Table1}). Over the duration of the experiment SLA was higher in free seedlings but was not different across containers sizes (Table.~\ref{table:Table1}, \textit{P}\textless0.001) and this pattern was evident in the first gas exchange measurement campaign (\textit{P}\textless0.001).

\subsubsection*{\textit{Leaf chemistry}}

Leaf \textit{N}~\% was significantly higher in free seedlings and the largest container volume at the onset of gas exchange measurements (6th week, \textit{P}\textless0.001).  Over the remaining duration of the experiment the smallest container volume had a significant reduction in leaf \textit{N}~\% compared to other soil volumes, while free seedlings maintained the highest leaf \textit{N}~\% (Table.~\ref{table:Table1}, \textit{P}\textless0.001).  Leaf starch content in the smallest container was double that of free seedlings (\textit{P}=0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table.~\ref{table:Table1}).  Differences in leaf starch between the free seedling and the smallest container were also evident during the first gas exchange campaign (\textit{P}=0.0013).

\subsubsection*{\textit{Gas exchange and photosynthetic parameters}}

\textit{A}\textsubscript{sat} (Fig.~\ref{fig:figure4}) and \textit{A}\textsubscript{max} (Table.~\ref{table:Table2}) were both significantly higher in the largest container volume and the free seedling at the first measurement campaign (both \textit{P}\textless0.001). Across all measurement campaigns \textit{A}\textsubscript{sat} was consistently higher in free seedlings than in containers (Figure 3, \textit{P}\textless0.001). The interaction between photosynthetic capacity, leaf starch, and leaf \textit{N} on a mass basis was marginally significant (\textit{P}=0.0584) but \textit{A}\textsubscript{max} was highly correlated to both leaf \textit{N} content and leaf starch (both \textit{P}\textless0.001). Across all measurement campaign \textit{A}\textsubscript{max} was higher when foliar \textit{N} was also higher, usually associated with low levels of leaf starch (Fig.~\ref{fig:figure3}a). \textit{A}\textsubscript{max} was also lower when leaf starch was high as higher leaf \textit{N} often did not coincide with high leaf starch (Fig.~\ref{fig:figure3}b)

The photosynthetic parameters~\textit{J}\textsubscript{max} and~\textit{Vc}\textsubscript{max} were not different within treatments at the beginning and end of gas exchange campaigns, therefore the parameter means per treatment are reported here (Table.~\ref{table:Table2}).  Overall, both \textit{J}\textsubscript{max} and \textit{Vc}\textsubscript{max} were significantly higher in free seedlings with little variation between soil volume treatments (\textit{P}=0.0012 \& 0.0021, respectively). Leaf dark respiration rates were not significantly different across soil volumes (Table.~\ref{table:Table2}). The \textit{g}\textsubscript{1} parameter, generated for each seedling from the \citet{medlyn2012reconciling} optimal stomatal conductance model, was lowest in the free seedling and was marginally different across soil volume treatments (Table.~\ref{table:Table2}). Predicted values of \textit{g}\textsubscript{s}, using the \textit{g}\textsubscript{1} parameter, where highly correlated with observed values (\textit{r}\textsuperscript{2}= .74, \textit{P}\textless{0.001}, data not shown).

Neither $\Psi\textsubscript{pd}$ nor $\Psi\textsubscript{l}$ were different across treatments, with mean values of -0.27 and -1.2~mPa across all seedlings, respectively. Although \textit{g}\textsubscript{s} in free seedlings was generally higher than those in containers (Table.~\ref{table:Table2}, \textit{P}=0.001), the mean rates for all seedlings were high at 0.37~mol~H\textsubscript{2}0~m\textsubscript{-2}~s\textsubscript{-1} and did not decline significantly across the experiment duration. Additionally, leaf {\textdelta}\textsuperscript{13}C at final harvest was not different across treatments (Table.~\ref{table:Table1}). Combined these indices provide strong evidence that water stress was not apparent on these well-watered seedlings throughout the experiment. Soil \textit{N}~\% at harvest was not different across soil volumes ($\bar{x}$=04.5~\%) and decreased approximately 3~\% across all containers over the experiment duration. This indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.

\subsubsection*{\textit{Modelling seedling biomass}}

Model M\textsubscript{0}, was able to converge on an optimum leaf mass fraction (21.6~\%) which accurately predicted the mean harvest total biomass of free seedlings within 1.2~\%. Using this optimized leaf mass fraction the gross primary productivity of modeled seedlings with soil volume restriction (M\textsubscript{1}) were on average 23$\pm$2.4~g \textit{C} more than measured seedlings When comparing against predicted total net leaf \textit{C} gain (Fig.~\ref{fig:figure6}a). Thus, seedling mass \textit{C} was overestimated by an average of 50$\pm$8.7~\% in modeled seedlings across the reductions in daily \textit{C} assimilation per treatment (Fig.~\ref{fig:figure6}b). As a result, the reductions in leaf \textit{A} were not sufficiently high enough to explain the reduction in harvested seedling biomass with soil volume restriction. With mass balance this resulted in an unexplained pool of excess \textit{C}, generated from \textit{A}, that did not end up in biomass.

The remaining model simulations tested \textit{C} allocation scenarios in an attempt to account for this remaining pool of missing \textit{C}. Constraining the model with the measured treatment specific leaf mass fraction from the final harvest (M\textsubscript{2}) still overestimated seedling total \textit{C} by 32$\pm$11.1~\%, but provided the most improved model predictions (Fig.~\ref{fig:figureSI1}a). Harvested leaf mass fraction, however, does not capture the likely increase in senescence of seedlings in small containers (Fig.~\ref{fig:figure2}c). Thus, the 7-61~\% reduction in measured harvested leaf mass fraction from large to small soil volumes compared to the optimized leaf mass fractions (M\textsubscript{0}) represents an underestimation of realized leaf \textit{C} allocation. Increases of 50~\% in non-leaf tissue respiration (M\textsubscript{3}) improved biomass estimates slightly but still overestimated mass \textit{C} by an average of 46$\pm$9.3~\% in seedlings with soil volume restriction (Fig.~\ref{fig:figureSI1}b). It was further determined that non-tissue respiration rates in modeled seedlings would need to increase by ca.~250~\% to account for this entire pool of \textit{C}.

\section*{Discussion}

As issues still remain regarding how source-sink coordination affects growth of woody species, this study utilized a simple but novel field design to manipulate belowground sink limitations in order to physically restrict \textit{Eucalyptus tereticornis} seedling production. After successfully created a belowground sink limitation we then addressed questions regarding the coordination of \textit{A} and growth by complementing empirical results with modelling approaches. We found that reductions in leaf \textit{A} rates were not sufficient to explain observed reductions in total plant biomass production after 120 days. We thus encourage the utilization of mass balance approaches and provide direction for future studies when testing factors that control of plant growth under environmental change.

\subsubsection*{\textit{Soil volume restriction and reduced seedling growth}}

As soon as seedlings became established both height and diameter growth were negatively affected as a function of available soil volume compared to free seedlings, providing immediate evidence in support of H1. These growth reductions were expected, as the impedance of root growth can cause reductions overall plant growth and activity \citep{mcconnaughay1991physical, young1997mechanical}. It has been shown that roots undergoing difficult conditions may send inhibitory signals to the shoots that affect stomatal conductance, cell expansion, cell division and the rate of leaf appearance \citep{passioura2002soil}. This was evident in the large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers. As growth was so strongly affected in containers we then asked if biomass partitioning strategies manifested through time that could explain the observed differences in seedling growth.	As mass partitioning is likely controlled by source and sinks strength of all organs \citep{poorter2012biomass} it was important to determine what tissue components were most affected in order to evaluate and then model the biomass response accurately.

As changes to mass allocation of leaves, stems or roots occurs at the expense of other structures \citep{mccarthy2007consistency} it was necessary to first distinguish if belowground sink limitation affected growth beyond ontogenetic constraints. In this study, there were no significant changes in root, leaf, or stem mass fractions to reduced soil volume compared to free seedlings, outside of ontogenetic drift. This is significant as shifts in allocation, beyond ontogeny, have been noted specifically for nutrient limitation compared to light, CO\textsubscript{2}, and water \citep[references therein]{mcconnaughay1999biomass}. Additionally, this provides evidence against the preservation of functional balance through optimal foraging, a common explanation for changes in plant growth under environmental stress. In response to root restriction these seedlings might alter biomass allocation to ephemeral tissues, including fine roots or leaves, in order to meet the resource requirements for \textit{A}. Fine root mass to leaf mass ratio was instead conserved, regardless of plant size or treatment, suggesting an active biomass partitioning strategy to optimize resource gain did not occur.

Alternatively, physical restriction of root proliferation could have impacted root development or morphology prior to shifts in mass partitioning. Plants in containers have been shown to have different root morphology to field grown plants as roots essentially compete with themselves for nutrients \citep{nesmith1998effect}, but data for woody species is still limited.For example, lateral root development is affected by inanimate obstacles and avoiding growth towards container walls could improve the efficiency of resource allocation \citep{falik2005root}. Also, the sensitivity of roots to their own exudates near obstructions may be used to adjust growth before stressful conditions occur \citep{semchenko2008foraging}. As a result, seedlings in small container sizes might alter fine root morphology, by increasing fine root length, to increase resource uptake potential. 
As neither SRL nor partitioning between fine and coarse root mass fractions differed across treatments, this provides further evidence against any functional plant response beyond developmental isometric growth.

\subsubsection*{\textit{Linkage between belowground sink limitation and photosynthesis}}

As plants must balance allocation to leaves, stems and roots in a way that matches the physiological activities performed by these organs \citep{poorter2012biomass}, the observed reductions in seedling growth could instead have resulted from \textit{C} source-sink imbalances. For example, the consequences of either stomatal closure or soil resource depletion to the sensitivity of these source-sink activities could lead to reductions in \textit{A}, the central driver of plant \textit{C} gain and growth. Contrary to what was hypothesized, just as height reductions were immediately evident with new growth, so were leaf \textit{A} rates on newly formed leaves. As physical restriction to growth was expected to precede effects on leaf physiology this initially suggests a tight link between reduced \textit{A} and seedling growth. It was therefore necessary to distinguish if source or sink limitation resulted in the reduction of \textit{A}\textsubscript{sat} and \textit{A}\textsubscript{max}  throughout the experiment.

With high rates of \textit{g}\textsubscript{s}, non-limiting leaf water potential and consistent leaf {\textdelta}\textsuperscript{13}C across soil volume treatments there was little evidence of source limitation to \textit{A} in this study. This finding is consistent with other container size studies, with source manipulation via elevated CO\textsubscript{2}, where inhibition of CO\textsubscript{2} enrichment often results from sink limitation on \textit{A}\textsubscript{max} \citep{arp1991effects, robbins1988effect}. For example, reduced \textit{A}\textsubscript{max} in cotton seedlings grown at elevated CO\textsubscript{2} was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased \textit{g}\textsubscript{s} \citep{thomas1991root}. Our results lend support to more general conclusions that neither growth \citep{korner2003carbon} nor \textit{A} \citep{millard2007environmental} of woody species is directly \textit{C} limited. Instead it was likely that reductions in \textit{A} occurred from the impact of a limited soil resource pool on belowground sink strength.

As both belowground space and resources were finite in containers, the limited ability of these seedlings to increase the capacity of the belowground \textit{C} sink was hypothesized to result in the buildup of \textit{C} assimilate in the leaves. This buildup, occurring via accumulation of leaf starch, was present as a function of decreasing container size throughout the study. As a result, \textit{A}\textsubscript{max} for all seedlings was highly correlated to leaf starch content across all measurement campaigns. The accumulation of leaf starch was accompanied by significant decreases \textit{J}\textsubscript{max} and \textit{Vc}\textsubscript{max}, both immediately evident during the first gas exchange campaign. Together this provides strong evidence that down regulation of \textit{A} likely occurred from reduced belowground \textit{C} sink strength in these seedlings. This down regulation was likely apparent throughout the entire experiment as leaf TNC content remained high in seedlings with soil volume restriction and the effects on \textit{J}\textsubscript{max} and \textit{Vc}\textsubscript{max} were again noted at the end of the experiment.

As limited understanding between source-sink feedbacks to photosynthetic down regulation still exists in woody species, this container size approach also allowed us to directly relate an induced belowground sink limitation to impacts on leaf physiology. Evidence for sink limitation of \textit{A} was evident in the stark contrast in leaf \textit{N} between free seedlings and seedlings in containers, combined with the strong correlation between leaf \textit{N} and \textit{A}\textsubscript{max}. Leaf \textit{N} was also reduced compared to free seedlings when excess accumulation of leaf starch was present. Although the soil \textit{N} pool declined evenly across all treatments leaf \textit{N} was lowest in the smallest soil volume, suggesting that sink limitation was the greatest in these containers. This makes sense as small containers may reduce \textit{N} uptake, either from physical root restriction or decreased supply, which affects growth, Rubisco limitation, sugar metabolism, and carbohydrate partitioning between source and sink tissues (Stitt, 1991; Hermans et al., 2006). Mycorrhizal colonization could have also been significantly affected by the ‘container effect’. Whether unrestricted mycorrhizal recruitment instead facilitated an increase in leaf \textit{N} uptake to leaves in free seedlings is unknown. Regardless, the belowground sink strength of seedlings with soil volume treatments was greatly reduced and appears to be strongly linked with negative feedbacks to \textit{A}.

\subsubsection*{\textit{Modeling the coordination of photosynthesis and growth with carbon mass balance}}

If feedbacks between sink limitation and leaf \textit{A} controlled seedling growth the growth model was expected to find agreement between simulated and observed seedling biomass. A linkage between sink limitation and \textit{A}, however, does not necessarily imply the same level of coordination between reduced \textit{A} and growth. It was therefore necessary to test, using a mass balance approach, if the measured reductions in \textit{A} could be used to predict the patterns in seedling growth after 120~days. Constraining the initial model run (M\textsubscript{1}) by an optimized leaf mass fraction allowed us to test if feedbacks from reduced \textit{A} could predict seedling growth with soil volume restriction. The result was a difference in the fate of assimilated \textit{C}, with a larger fraction of available \textit{C} ending up in final biomass of modeled seedlings. Consequently, this also revealed a pool of missing \textit{C} in measured seedlings unaccounted for with mass balance. This finding lends strong evidence that \textit{A} and growth may not be entirely synced under environmental change, an important distinction often missed in studies that manipulate source and sink activity. Thus, without \textit{C} mass balance approaches inferences to the nature of mechanisms controlling growth under environmental stress should only be speculative. As a result, we utilized the flexibility of the model to test potential sources of \textit{C} loss not explicitly measured, including changes to leaf \textit{C} allocation or non-leaf tissue respiration.  Through this approach, similar to \citep{lohier2014explaining}, we manipulated processes contributing to seedling \textit{C} mass balance and quantitatively tested their respective influences on model predictions.

Altering the leaf mass fraction from that of the optimized free seedling control (M\textsubscript{2}) improved model biomass predictions and provided insight into how sink limitation may impact leaf \textit{C} allocation beyond that of \textit{A}. As this was a field study it was impossible to quantify all impacts to leaf \textit{C} allocation which could have occurred. Model predictions, however, provided evidence for how the feedback between rates of photosynthesis and \textit{C} allocated to leaves can severely impact seedling growth. The observed sub-optimal decrease in leaf mass fraction with increasing soil volume restriction has several possible explanations.  First, TNC accumulation due to sink limitation can lead to accelerated leaf senescence \citep{paul2001sink}. Alternatively, as rates of \textit{A} were not different between soil volume treatments these seedlings could have reduced leaf production to maintain laws of stoichiometry (leaf \textit{C}:\textit{N} ratio) associated with reduced belowground \textit{C} sink strength and measured declines in leaf N. Thus, future empirical studies and modelling efforts should focus on the feedbacks from sink activity not only on leaf A rates but also on the fate of \textit{C} allocated to leaves.  It is the interaction between these two components that will drive patterns of total canopy \textit{C} gain available for growth for the rest of the plant.

Increases in non-leaf respiration rates  (M\textsubscript{3}) improved biomass predictions but to a lesser extent than changes to leaf \textit{C} allocation.  This finding is still significant as it justifies the need to strengthen our knowledge of the effects of environmental change on respiration of different tissues components above and belowground. As \textit{C} balance is a delicate equilibrium between fluxes of photosynthesis and respiration, partial accounting of \textit{C} dynamics can easily lead to erroneous conclusions (Valentini et al. 2000). For example, there is strong evidence for coupling between photosynthesis and respiration yet \textit{C} use efficiency is not always constant \citep{cannell2000modelling}. In addition, our understanding of how changes in sink activity affect this coupling or regulation of respiration across different tissues components in woody species is still poor.  Thus, it is likely inappropriate to assume that respiration is an constant fraction of gross primary production in models \citep{delucia2007forest}. We reveal that any significant impact to tissue respiration will likely impact the synchronization of \textit{A} and growth and should be accounted for in  future empirical studies and modelling efforts that predict plant growth under environmental change.

\subsubsection*{\textit{Conclusions}}

Although there is renewed debate of the coordination of \textit{A} and growth this is not a new issue. It has long been know that conditions which affect the photosynthetic process affect growth but there is also an interrelationship between growth and \textit{A} \citep{sweet1966role}. We found that the fate of assimilated \textit{C}, available for plant growth, was different between free seedlings and seedlings in containers. This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles but how these results actually reflect field-grown plants has seldom been studied. Utilizing a mass-balance approach with a simple production model revealed that a combination of different mechanisms must be at play in driving this observed seedling biomass response to sink manipulation. However, which of the mechanisms and the role they have in determining growth response will undoubtedly shift across different experimental manipulations and plant species. We argue that attempts to quantify or at least predict the fate of assimilated \textit{C} into known pools of growth, storage and \textit{C} loss are necessary before definitive resolution of the controls of plant growth are to be found. The widespread implications of this type of approach, allowing the flexibility to account for multiple potential drivers of \textit{C} allocation and plant growth, can help answer questions about the fate of \textit{C} in plants undergoing environmental change.

%--------------------------------------------------------------------------------------------%
\section*{Tables}
% Load xtable for printing tables.
<<echo=FALSE, message=FALSE, warning=FALSE>>=
library(xtable)
pve_data <- read.csv("table/pve_table1.csv")

colnames(pve_data) <- c("Volume (L)", 
                        "Seedling~mass~(g)", 
                        "SLA\\textsubscript{TNC-free}~(m\\textsuperscript{2}~kg\\textsuperscript{-1})",
                        "Leaf~Starch~(\\%)", 
                        "Leaf~Sugars~(\\%)", 
                        "Leaf~Nitrogen~(\\%)",
                        "Root~Nitrogen~(\\%)",
                        "SRL~(cm~m\\textsuperscript{-1})",
                        "{Leaf~\\textdelta}\\textsuperscript{13}C~(\\text{\\textperthousand})")

phys_data <- read.csv("table/pve_table2.csv")
colnames(phys_data) <- c("Volume~(L)", 
                        "\\textit{A}\\textsubscript{max}", 
                        "\\textit{R}\\textsubscript{dark}",
                        "\\textit{J}\\textsubscript{max}",
                        "\\textit{Vc}\\textsubscript{max}",
                        "\\textit{g}\\textsubscript{s}",
                        "\\textit{g}\\textsubscript{1}")

@

%seedling data table
<<results='asis'>>=
datatab <- xtable(pve_data, label="table:Table1", caption="Responses of plant and leaf characterisitics of \\textit{Eucalyptus tereticornis} seedlings to soil volume treatments. Each value reflects the mean(standard error) for each treatment. Seedling mass, SRL, root nitrogen and leaf \\textdelta\\textsuperscript{13}C values are from final harvest. Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6). Different letters represent significant differences between treatments. The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.")

print(datatab, include.rownames=FALSE,sanitize.colnames.function=function(x){x},
      floating.environment='sidewaystable', caption.placement="top", 
      hline.after = getOption("xtable.hline.after", c(-1,0,7,nrow(datatab))))

@

%data.df$taxa <- paste("\\emph{",taxa,"}", sep="")

<<results='asis'>>=
phystab <- xtable(phys_data, label="table:Table2",caption="Responses of leaf level gas exchange parameters of \\textit{Eucalyptus tereticornis} seedlings to soil volume treatments. Each value reflects the mean(standard error) for each treatment. Units for \\textit{A}\\textsubscript{max} and \\textit{R}\\textsubscript{dark} are {\\textmugreek}mol~m\\textsuperscript{-2}~s\\textsuperscript{-1} and \\textit{g}\\textsubscript{s} are mol~m\\textsuperscript{-1}~s\\textsuperscript{-1}, each at at 25$\\degree$C. Values of \\textit{A}\\textsubscript{max}, \\textit{g}\\textsubscript{s} and \\textit{g}\\textsubscript{1} represent overall means across measurement campaigns (n=6). \\textit{R}\\textsubscript{dark}, \\textit{J}\\textsubscript{max} and \\textit{Vc}\\textsubscript{max} values are means of two measurement campaigns at beginning and end of gas exchange measurements. Different letters represent significant differences between treatments. The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.")

print(phystab, include.rownames=FALSE,sanitize.colnames.function=function(x){x},
      floating.environment='sidewaystable',caption.placement="top",
       hline.after = getOption("xtable.hline.after", c(-1,0,7,nrow(datatab))))
@

%--------------------------------------------------------------------------------------------%
\clearpage
\section*{Figures}

%air variables figure
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{airvars.pdf}
    \caption{Daily maximum and minimum temperature (a), cumulative daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.}
    \label{fig:figure1}
\end{figure}

%allometry figure
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{allometry.pdf}
    \caption{Soil volume treatment means~$\pm$ standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of \textit{Eucalyptus tereticornis} seedlings across the experiment duration in 2013.}
    \label{fig:figure2}
\end{figure}

%partitioning figure
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{massfractions.pdf}
    \caption{Soil volume treatment means of mass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with $\pm$ standard error (c). For (b) lines represent standardized major axis fitting of the log transformed allometric relationships of leaf mass fraction by treatment. For (c) the dashed line is the 1:1 relationship and the solid line represents the significant linear model fit (\textit{r}\textsuperscript{2}~=~0.81).}
    \label{fig:figure3}
\end{figure}

%asat figure
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{Asat.pdf}
    \caption{Soil volume treatment means~$\pm$ standard error, across all measurement campaigns (n=6), of light saturated rates of photosynthesis at 25$\degree$C. Different letters represent significant differences between treatments.}
    \label{fig:figure4}
\end{figure}

%photochem figure
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{A_leafchem.pdf}
    \caption{Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).  Colors represent bins levels (n=5) of both leaf starch and nitrogen grouped from low to high .  Lines represents predictions, for each bin level, from the linear mixed effects model equation of \textit{A}\textsubscript{max} as a function of starch and nitrogen. The marginal \textit{r}\textsuperscript{2} (fixed effects only) was 0.37 and the conditional \textit{r}\textsuperscript{2} (fixed and random effects) was 0.48 for the complete model.}
    \label{fig:figure5}
\end{figure}

%model base figure
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{massmodel_totalC.pdf}
    \caption{Total carbon mass for harvested and modeled seedlings versus predicted total carbon gain after 120 days (a) and  reductions in final seedling carbon mass, both modeled and observed, as a function of the reduction in leaf photosynthesis across treatments (b). For (a) the dashed 1:1 identifies the difference between net total leaf carbon gain and gross seedling production. For (b) both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.}
    \label{fig:figure6}
\end{figure}

%--------------------------------------------------------------------------------------------%
\clearpage
\section{Supporting Information Figures}
% Supporting information. Make sure Figures continue with Fig S1 etc.

\renewcommand\thefigure{S\arabic{figure}}    
\setcounter{figure}{0}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{massmodel_resp.pdf}
    \caption{Sensitivity testing of seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50~\% (b).  Open and filled symbols represent default model and harvest values, while shaded symbols represent model sensitivity to each scenario by soil volume treatment. Both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.}
    \label{fig:figureSI1}
\end{figure}

\begin{table}[h!]
  \caption{Seedling Growth Model Default Parameters} 
  \centering 
  \begin{tabular}{l l l l l } 
  \hline
  Variable & Description & Default Value & Units & Source  \\ [0.5ex] 
  \hline
  Leaf area\textsubscript{i} & initial leaf area & 0.035 & m\textsuperscript{2} & this study \\

  Leaf mass\textsubscript{i} & initial leaf mass & 3.45 & g & this study \\

  Stem mass\textsubscript{i} & initial stem mass & 1.51 & g & this study \\

  Root mass\textsubscript{i} & initial root mass & 0.99 & g & this study \\

  \textepsilon\textsubscript{c} & biomass conversion efficiency & .65 & g~C g~mass\textsuperscript{-1} 
  & \citet{makela1997carbon} \\

  R\textsubscript{coarse root} & coarse root respiration & 0.00124 & g~C g~root\textsuperscript{-1} 
  & \citet{marsden2008relating} \\

  R\textsubscript{fine root} & fine root respiration & 0.010368 & g~C g~root\textsuperscript{-1} & \citet{ryan2010factors} \\

  R\textsubscript{stem} & stem respiration & 0.00187 & g~C g~stem\textsuperscript{-1} & Drake 2014 (unpublished) \\

  C\textsubscript{day} & Daily Leaf Carbon Assimilation &5.4-7.6 & g~C m\textsuperscript{-2} d\textsuperscript{-1}
  & this study \\

  $\Lambda$ & tissue turnover & 1/365 & yr\textsuperscript{-1} & theoretical\\

  \hline 
  \end{tabular}
  \label{table:Table3} 
\end{table}

%--------------------------------------------------------------------------------------------%
\clearpage
\bibliography{pve_cites}

%--------------------------------------------------------------------------------------------%
\end{document}

### 2015-07-20 tables_latex/pve_manuscript.tex
added new folder with latek markdown for tables

--- 2015-07-20 tables_latex/pve_manuscript.Rnw
@@
-\documentclass[a4paper]{article}
+\documentclass[a4paper]{article}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 
@@
 \usepackage{textgreek}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 %--------------------------------------------------------------------------------------------%
-
-<<preload, echo=FALSE>>=
-library(knitr)
-opts_chunk$set(echo=FALSE)
-@
 
@@
 
-Alternatively, manipulation of plant tissue carbon sinks is often used to investigate the correlation of photosynthesis and growth.
-Tissue sink activity can restrict biomass production when limited by environmental or developmental constraints \citep{korner2003carbon}.
+Alternatively, tissue sink activity can restrict biomass production when limited by environmental or developmental constraints \citep{korner2003carbon}.
 This is because metabolic signaling networks, relaying information on \textit{C} and nitrogen (\textit{N}) status of different tissues, can down regulate photosynthetic activity \citep{paul2001sink}.
-Whether this down regulation, via sink inhibition, is evident in woody species has been tested through fruit removal, girdling, and low temperatures.
+Whether this down regulation, via sink inhibition, exists in woody species has been tested through fruit removal, girdling, and low temperatures.
 In these studies, down regulation of \textit{A} was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength \citep{iglesias2002regulation,hoch2002altitudinal,urban2007girdling, haouari2013fruit}.
@@
 As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to large annual fruiting sinks, they tell us little about source-sink coordination in ‘normal’ field-grown woody species.
+This coordination is further confounded by the fact that under normal growing conditions, \textit{A} is not always correlated to photosynthate accumulation, as with fir needles \citep{little1973effect}.
+Unfortunately, there is still limited understating of the physiological roles of carbohydrates in photosynthetic regulation and the elements triggering the down-regulation process \citep{nebauer2011photosynthesis}.
 
-An alternative experimental approach is to lower belowground \textit{C} sink strength in tree seedlings by manipulating rooting volume, by varying the container size.
+An alternative approach is to lower belowground \textit{C} sink strength in tree seedlings by manipulating rooting volume, by varying the container size.
 The advantage of this approach is it allows a large range of manipulations, can be easily compared to naturally planted seedlings and mimics natural conditions as seedlings compete for space or reach bedrock.
 Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, \textit{A}, water relations, nutrient uptake and respiration \citep[and references therein]{nesmith1998effect}.
-Inadequate rooting volume may decrease carbon sink strength by progressively restricting root growth \citep{thomas1991root}.
+The rooting volume available to plants can decrease \textit{C} sink strength by reducing root growth.
 Container size studies frequently have photosynthetic down-regulation, likely as a result of sink limitation \citep{arp1991effects, mcconnaughay1991physical, gunderson1994photosynthetic, sage1994acclimation, maina2002intra, ronchi2006growth}.
@@
 
-Our lack of knowledge regarding the allocation of \textit{C} in woody species is still a major obstable in understanding the cooridatnation between  \textit{A} and growth.
+Another barrier in understanding the coordination between \textit{A} and growth is a lack of knowledge regarding the allocation of \textit{C} in woody species.
 Understanding the fate of assimilated \textit{C} is crucial when source or sink manipulations do not directly lead to equivalent changes in growth.
@@
 % Load xtable for printing tables.
-<<echo=FALSE, message=FALSE, warning=FALSE>>=
-library(xtable)
-pve_data <- read.csv("table/pve_table1.csv")
-
-colnames(pve_data) <- c("Volume (L)", 
-                        "Seedling~mass~(g)", 
-                        "SLA\\textsubscript{TNC-free}~(m\\textsuperscript{2}~kg\\textsuperscript{-1})",
-                        "Leaf~Starch~(\\%)", 
-                        "Leaf~Sugars~(\\%)", 
-                        "Leaf~Nitrogen~(\\%)",
-                        "Root~Nitrogen~(\\%)",
-                        "SRL~(cm~m\\textsuperscript{-1})",
-                        "{Leaf~\\textdelta}\\textsuperscript{13}C~(\\text{\\textperthousand})")
-
-phys_data <- read.csv("table/pve_table2.csv")
-colnames(phys_data) <- c("Volume~(L)", 
-                        "\\textit{A}\\textsubscript{max}", 
-                        "\\textit{R}\\textsubscript{dark}",
-                        "\\textit{J}\\textsubscript{max}",
-                        "\\textit{Vc}\\textsubscript{max}",
-                        "\\textit{g}\\textsubscript{s}",
-                        "\\textit{g}\\textsubscript{1}")
-
-@
 
 %seedling data table
-<<results='asis'>>=
-datatab <- xtable(pve_data, label="table:Table1", caption="Responses of plant and leaf characterisitics of \\textit{Eucalyptus tereticornis} seedlings to soil volume treatments.
+% latex table generated in R 3.1.2 by xtable 1.7-4 package
+% Sun Jul 12 11:12:17 2015
+\begin{sidewaystable}[ht]
+\centering
+\caption{Responses of plant and leaf characterisitics of \textit{Eucalyptus tereticornis} seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.
-Seedling mass, SRL, root nitrogen and leaf \\textdelta\\textsuperscript{13}C values are from final harvest.
+Seedling mass, SRL, root nitrogen and leaf \textdelta\textsuperscript{13}C values are from final harvest.
 Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6).
 Different letters represent significant differences between treatments.
-The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.")
-
-print(datatab, include.rownames=FALSE,sanitize.colnames.function=function(x){x},
-      floating.environment='sidewaystable', caption.placement="top", 
-      hline.after = getOption("xtable.hline.after", c(-1,0,7,nrow(datatab))))
-
-@
+The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.}
+\label{table:Table1}
+\begin{tabular}{lllllllll}
+  \hline
+Volume (L) & Seedling~mass~(g) & SLA\textsubscript{TNC-free}~(m\textsuperscript{2}~kg\textsuperscript{-1}) & Leaf~Starch~(\%) & Leaf~Sugars~(\%) & Leaf~Nitrogen~(\%) & Root~Nitrogen~(\%) & SRL~(cm~m\textsuperscript{-1}) & {Leaf~\textdelta}\textsuperscript{13}C~(\text{\textperthousand}) \\
+  \hline
+5 & 14.8 (1.82) a & 11.8 (0.32) a & 12.7 (0.97) b & 6.4 (0.28) a & 1.1 (0.02) a & 0.78 (0.04) ab & 39.1 (5.47) a & -30.1 (0.26) a \\ 
+  10 & 20.0 (2.38) ab & 11.7 (0.31) a & 9.4 (0.75) ab & 6.7 (0.25) a & 1.3 (0.04) ab & 0.75 (0.02) a & 34.2 (5.83) a & -30.2 (0.25) a \\ 
+  15 & 25.4 (2.49) ab & 12.7 (0.48) a & 7.3 (0.73) a & 7.2 (0.28) a & 1.4 (0.06) ab & 0.71 (0.02) a & 37.6 (4.63) a & -30.3 (0.36) a \\ 
+  20 & 23.4 (1.63) ab & 11.8 (0.37) a & 9.5 (0.88) ab & 6.6 (0.26) a & 1.4 (0.05) ab & 0.76 (0.04) a & 45.3 (5.50) a & -29.7 (0.28) a \\ 
+  25 & 30.4 (5.49) ab & 12.4 (0.40) a & 9.8 (0.71) ab & 6.9 (0.24) a & 1.3 (0.06) ab & 0.74 (0.02) a & 47.0 (7.10) a & -29.7 (0.25) a \\ 
+  35 & 52.2 (9.55) b & 13.5 (0.46) ab & 9.8 (0.65) ab & 6.8 (0.22) a & 1.5 (0.08) b & 0.77 (0.03) ab & 50.6 (11.61) a & -30.6 (0.38) a \\ 
+  Free & 174.5 (18.02) c & 15.1 (0.47) b & 6.8 (0.65) a & 7.4 (0.25) a & 2.4 (0.09) c & 0.9 (0.03) b & 43.7 (6.24) a & -30.0 (0.34) a \\ 
+   \hline
+Container Effect (P) & 0.001 & 0.001 & 0.039 & 0.128 & 0.001 & 0.015 & 0.662 & 0.458 \\ 
+   \hline
+\end{tabular}
+\end{sidewaystable}
 
@@
 
-<<results='asis'>>=
-phystab <- xtable(phys_data, label="table:Table2",caption="Responses of leaf level gas exchange parameters of \\textit{Eucalyptus tereticornis} seedlings to soil volume treatments.
+% latex table generated in R 3.1.2 by xtable 1.7-4 package
+% Sun Jul 12 11:12:17 2015
+\begin{sidewaystable}[ht]
+\centering
+\caption{Responses of leaf level gas exchange parameters of \textit{Eucalyptus tereticornis} seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.
-Units for \\textit{A}\\textsubscript{max} and \\textit{R}\\textsubscript{dark} are {\\textmugreek}mol~m\\textsuperscript{-2}~s\\textsuperscript{-1} and \\textit{g}\\textsubscript{s} are mol~m\\textsuperscript{-1}~s\\textsuperscript{-1}, each at at 25$\\degree$C.
-Values of \\textit{A}\\textsubscript{max}, \\textit{g}\\textsubscript{s} and \\textit{g}\\textsubscript{1} represent overall means across measurement campaigns (n=6).
-\\textit{R}\\textsubscript{dark}, \\textit{J}\\textsubscript{max} and \\textit{Vc}\\textsubscript{max} values are means of two measurement campaigns at beginning and end of gas exchange measurements.
+Units for \textit{A}\textsubscript{max} and \textit{R}\textsubscript{dark} are {\textmugreek}mol~m\textsuperscript{-2}~s\textsuperscript{-1} and \textit{g}\textsubscript{s} are mol~m\textsuperscript{-1}~s\textsuperscript{-1}, each at at 25$\degree$C.
+Values of \textit{A}\textsubscript{max}, \textit{g}\textsubscript{s} and \textit{g}\textsubscript{1} represent overall means across measurement campaigns (n=6).
+\textit{R}\textsubscript{dark}, \textit{J}\textsubscript{max} and \textit{Vc}\textsubscript{max} values are means of two measurement campaigns at beginning and end of gas exchange measurements.
 Different letters represent significant differences between treatments.
-The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.")
-
-print(phystab, include.rownames=FALSE,sanitize.colnames.function=function(x){x},
-      floating.environment='sidewaystable',caption.placement="top",
-       hline.after = getOption("xtable.hline.after", c(-1,0,7,nrow(datatab))))
-@
+The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.}
+\label{table:Table2}
+\begin{tabular}{lllllll}
+  \hline
+Volume~(L) & \textit{A}\textsubscript{max} & \textit{R}\textsubscript{dark} & \textit{J}\textsubscript{max} & \textit{Vc}\textsubscript{max} & \textit{g}\textsubscript{s} & \textit{g}\textsubscript{1} \\
+  \hline
+5 & 21.2 (0.9) a & 0.61 (0.04) a & 104.5 (3.3) a & 63.3 (2.5) a & 0.30 (0.01) a & 5.1 (0.1) bc \\ 
+  10 & 22.3 (1.4) ab & 0.79 (0.06) a & 116.5 (7.5) a & 69.4 (4.7) a & 0.36 (0.01) ab & 5.4 (0.1) cd \\ 
+  15 & 23.3 (1.2) ab & 0.70 (0.05) a & 125.4 (7.8) a & 80.8 (5.1) ab & 0.42 (0.01) ab & 5.8 (0.1) d \\ 
+  20 & 26.1 (0.7) b & 0.73 (0.11) a & 131.5 (8.6) a & 82.1 (4.7) ab & 0.37 (0.01) ab & 4.9 (0.1) ac \\ 
+  25 & 23.9 (0.9) ab & 0.53 (0.13) a & 132.8 (13.1) a & 79.0 (8.7) a & 0.30 (0.01) a & 4.5 (0.1) a \\ 
+  35 & 25.0 (1.0) ab & 0.61 (0.04) a & 127.2 (6.1) a & 82.4 (3.6) a & 0.31 (0.01) a & 4.4 (0.2) a \\ 
+  Free & 33.1 (0.7) c & 0.64 (0.07) a & 169.0 (8.2) b & 100.4 (3.3) b & 0.44 (0.01) b & 4.5 (0.1) ab \\ 
+   \hline
+Container Effect (P) & 0.001 & 0.039 & 0.001 & 0.002 & 0.001 & 0.079 \\ 
+   \hline
+\end{tabular}
+\end{sidewaystable}
 

### 2015-07-20 manuscript/manuscript_pve.Rmd
added in discussion

@@
 
-```{r, results='asis', echo=FALSE, warning=FALSE}
+```{r, results="asis", echo=FALSE, warning=FALSE}
 library(knitr)
@@
 We observed a negative container effect on aboveground growth soon after the experiment started.
-Although growth was consistently different across soil volumes mass, partitioning to leaves, stems, roots was conserved after 120 days.
+Although growth was consistently different across soil volumes mass, partitioning to leaves, stems and roots was conserved after 120 days.
 Photosynthetic capacity was also significantly reduced in containers, and was related to both leaf nitrogen content and starch accumulation.
@@
 Understanding plant growth requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
-As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues sinks.
-At long enough time scales A and growth must be correlated in respect to mass balance, however, at shorter temproal scales growth is not necessarily limited by the availability of recent photosynthate.
+As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues and organs.
+At long enough time scales A and growth must be correlated in respect to mass balance, however, at shorter temporal scales growth is not necessarily limited by the availability of recent photosynthate.
 This has led to the current debate over how strongly plant growth is controlled by either source of sink activity.
@@
 These mixed results are not surprising as we still know little about the pathways in which plants achieve balance between assimilation, storage, and growth across temporal scales [@smith2007coordination].
-As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to large annual fruiting sinks, they tell us little about source-sink coordination in ‘normal’ field-grown woody species.
+As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to large annual fruiting sinks, they tell us little about source-sink coordination in normal field-grown woody species.
 
 \
-If source or sink manipulations do not lead to equivalent changes in growth then understanding the fate of assimilated carbon becomes even more crucial.
+If source or sink manipulations do not lead to equivalent changes in growth then understanding the fate of assimilated C becomes even more crucial.
 As programmed plasticity in C allocation naturally occur as plants growth and develop, this must be accounted for when evaluating induced variation in growth [@wright2002interpreting].
@@
 In woody species, shifts in allometric relationships of leaves, stems and roots can reveal if growth is ontogenetically constrained or actively adjusted when A is affected.
-This then allows additional pools of carbon, such as root exudation or changes in tissue respiration, to be accounted for and mass balance to be achieved.
+This then allows additional pools of C, such as root exudation or changes in tissue respiration, to be accounted for and mass balance to be achieved.
 
@@
 An alternative experimental approach is to lower belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size.
-The advantage of this approach is it allows a large range of manipulations, can be easily compared to naturally planted seedlings and mimics natural conditions as seedlings compete for space or reach bedrock.
+The advantage of this approach is it allows a large range of manipulations, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
 Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, A, water relations, nutrient uptake and respiration [@nesmith1998effect, and references therein].
-Inadequate rooting volume may decrease carbon sink strength by progressively restricting root growth [@thomas1991root].
+Inadequate rooting volume may decrease C sink strength by progressively restricting root growth [@thomas1991root].
 Container size studies frequently have photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
@@
 2).
-Reduced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, which is known to inhibit photosynthsis.
-We therefore expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume.
+Reduced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, which is known to inhibit A We therefore expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume.
 
-3). Last, the growth model was expected to find agreement between simulated and observed seedling mass, through direct correlation of the effects of limiiting soil volume on A.
+3). Last, the growth model was expected to find agreement between simulated and observed seedling mass, through direct correlation of the effects of limiting soil volume on A.
 
@@
 Plots were located in open cover with a site history that consists of a paddock that was converted from native pasture grasses.
-Top soils at this site, used for the study, are an alluvial formation of low-fertility sandy loam soils (380 and 108 mg kg^-1^ total N and phosphorus respectively) with low organic matter (0.7%) and low water holding capacity.
+Top soils at this site, used for the study, are an alluvial formation of low-fertility sandy loam soils (380 and 108 mg kg^-1^ total N and phosphorus respectively) with low organic matter (0.7 %) and low water holding capacity.
 At this site a soil hard layer exists at ~1.0 m with a transition to heavy clay soils.
@@
 \
-Plants were watered weekly or when needed, accounting for natural precipitation, to maintain soil moisture at field capacity (13-15%).
+Plants were watered weekly or when needed, accounting for natural precipitation, to maintain soil moisture at field capacity (13-15 %).
 Drain systems were built into each pot to prevent pooling of water in containers before root expansion, from reduced root uptake, or from large rainfall events.
@@
 A collection compartment in the bottom of containers, containing gravel covered by root exclusion mesh, was used to collect excess water for 20, 25, and 35 l containers.
-Plastic tubing (6~mm diameter) was inset into the gravel layer and extended through the top of the container.
-A lysimeter pump was then used to suction excess water, through the tubing, as needed .
+Plastic tubing (6 mm diameter) was inset into the gravel layer and extended through the top of the container.
+A lysimeter pump was then used to suction excess water, through the tubing, as needed.
 As small containers (5, 10, and 15 l) have a larger irradiation effect a simple bottom plug was used to drain excess water from the gravel compartment.
@@
 ## Growth and morphology metrics
-Seedlings were planted on January 21^st^ 2013 and stem height, diameter at 15~cm and leaf count were measured weekly thereafter.
+Seedlings were planted on January 21^st^ 2013 and stem height, diameter at 15 cm and leaf count were measured weekly thereafter.
 Once the growth rate of individual plants had significantly declined a full biomass harvest was completed (May 21^st^ 2013).
@@
 Roots from the free seedlings were collected by excavating each 1 m^2^ subplot to 0.5 m depth.
-25 g fresh weight subsamples of washed fine roots were analyzed, using WhinoRhizo software (Regent Instruments Inc.), for specific root length (SRL, cm~m^-1^).
+25 g fresh weight subsamples of washed fine roots were analyzed, using WhinoRhizo software (Regent Instruments Inc.), for specific root length (SRL, m g^-1^).
 
@@
 This choice of light level to achieve light saturation is consistent with other studies on *Eucalyptus* species [@kallarackal1997ecophysiological;@pinkard1998photosynthetic;@crous2013photosynthesis;@drake2014capacity].
-These measurements were conducted during midday (10:00-14:00 h) with leaf temperature maintained at 25&deg;C.
+These measurements were conducted during midday (10:00-14:00 h) with leaf temperature maintained at 25 &deg;C.
 After leaves acclimated to the chamber environment, net CO~2~ assimilation rate and stomatal conductance (g~s~) were logged 5 times for both A~sat~ and A~max~.
@@
 \
-Photosynthetic CO~2~ response (AC~i~) curves were also developed at 25&deg;C on a random subset of each container size (n=3) after new leaves were first produced and immediately prior to the final harvest (May 23^rd^ 2013).
-Each AC~i~ curve began at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25&deg;C at saturating light (above).
+Photosynthetic CO~2~ response (AC~i~) curves were also developed at 25 &deg;C on a random subset of each container size (n=3) after new leaves were first produced and immediately prior to the final harvest (May 23^rd^ 2013).
+Each AC~i~ curve began at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light (above).
 From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical].
@@
 Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions.
-Reported values of R~d~ are standardized rates at 25&deg;C using a Q10 value (1.86) developed for these seedlings in a separate experiment (Drake et al.
+Reported values of R~d~ are standardized rates at 25 &deg;C using a Q10 value (1.86) developed for these seedlings in a separate experiment (Drake et al.
 unpublished).
@@
 $\Psi$~pd~ was measured before sunrise and $\Psi$~l~ at midday 13:00-14:30 h.
-These measurements were used as a measure of static water stress on the seedlings \citep{sellin1999does}, and to ensure that the bulk soil water availability was high enough for plants as they became larger and roots filled the soil volume.
+These measurements were used as a measure of static water stress on the seedlings [@sellin1999does] and to ensure that the bulk soil water availability was high enough for plants as they became larger and roots filled the soil volume.
 
@@
 Leaf $\delta$^13^C was analyzed  with an Delta V Advantage coupled to a Flash HT and Conflo IV isotope ratio mass spectrometer.
-Leaf samples were flash combusted at 1000&deg;C to convert to to CO~2~, feed to the mass spectrometer and isotopic signatures are reported relative to the VPDP scale.
+Leaf samples were flash combusted at 1000&deg;C to convert to CO~2~, feed to the mass spectrometer and isotopic signatures are reported relative to the VPDP scale.
+
+\
 Leaf TNC concentration was analyzed using a total starch assay kit (Megazyme International 303 Ireland Ltd., Wicklow, Ireland) and includes the starch (mg g^-1^) and soluble sugar (mg g^-1^) concentrations.
@@
 $$P_i = L\left(\frac{C_{day'i}~\sigma_s}{\epsilon_c}\right) - R$$
-where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g d^-1^), $\sigma$~s~ is a self shading parameter, $epsilon$~c~ is a biomass conversion efficiency parameter and R is the mass based total respiration of all tissue components.
+where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g d^-1^), $\sigma$~s~ is a self shading parameter, $\epsilon$~c~ is a biomass conversion efficiency parameter and R is the mass based total respiration of all tissue components.
 Total respiration was calculated as
@@
 \
-C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] in the 'plantecophys' package [@Duursma2014] in R [@RDevelopment] with the mean photosynthetic parameters (J~max~, V~cmax~, R~d~ and g~1~) for each treatment and meteorological data from an onsite weather station.
-J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), R~d~ was emprically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2012reconciling] with observed g~s~ values.
+C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] in the 'plantecophys' package [@Duursma2014] in R [@RDevelopmentCoreTeam2011] with the mean photosynthetic parameters (J~max~, V~cmax~, R~d~ and g~1~) for each treatment and meteorological data from an onsite weather station.
+J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), R~d~ was empirically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2012reconciling] with observed g~s~ values.
 Examples of the photosynthesis model are described in Medlyn et al.
 [-@medlyn2002temperature] and the approach of the coupled leaf gas exchange model are described in Duursma et al [-@duursma2014peaked].
-Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15~m intervals, leaf A rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
-C~day~ was calculated by converting predicted rates to mass C gain over 15~min timesteps (g m^-2^) and then summed for 24 h.
+Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf A rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
+C~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
 This resulted in 120 unique values of C~day~ for each soil volume treatment, one value for each day of the experiment.
@@
 tereticornis*, from Duursma et al.
-[-@duursma2012light] to run in 'YplantQMC' package in R (fix cite YplantQMC) to build a 3d plant structure based on digitized metrics of plant allometry and crown structure.
+[-@duursma2012light] to run in 'YplantQMC' package in R (fix cite YplantQMC) to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
 Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total A, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
@@
 Across all measurement campaigns A~sat~ (Fig.
-`r asatfig`) and A~max~ (Table 2.) were consistently higher in free seedlings than in containers (boht P<0.001).
+`r asatfig`) and A~max~ (Table 2.) were consistently higher in free seedlings than in containers (both P<0.001).
 The interaction between photosynthetic capacity, leaf starch, and leaf N on a mass basis was marginally significant (P=0.0584) but A~max~ was highly correlated to both leaf N content and leaf starch (both P<0.001).
@@
 2).
-Predicted values of g~s~, using the g~1~parameter, where highly correlated with observed values (R^2^= .74, P<0.001, data not shown).
+Predicted values of g~s~, using the g~1~ parameter, where highly correlated with observed values (R^2^= .74, P<0.001, data not shown).
 
@@
 As a result, the reductions in leaf A were not sufficient enough to explain the reduction in harvested seedling biomass with soil volume restriction.
-This resulted in an unexplained pool of excess C, generated from A, that was not allocated to biomass.
+This resulted in an unexplained pool of excess C, generated from A, which was not allocated to biomass.
 
@@
 # Discussion
-As issues still remain regarding how source-sink coordination affects growth of woody species, this study utilized a simple but novel field design to manipulate belowground sink limitations in order to physically restrict *Eucalyptus tereticornis* seedling production.
+This study utilized a simple but novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling production.
 We then addressed questions regarding the coordination of A and growth by complementing empirical results with modelling approaches.
@@
 
-Our lack of knowledge regarding the allocation of C in woody species is still a major obstable in understanding the cooridatnation between A and growth.
+## Soil volume restiction compared to field plants
+As soon as seedlings became established both height and diameter growth were negatively affected as a function of available soil volume when compared to free seedlings.
+These growth reductions were expected, as the impedance of root growth can cause reductions overall plant growth and activity [@mcconnaughay1991physical; @young1997mechanical].
+It has been shown that roots undergoing difficult conditions may send inhibitory signals to the shoots that affect g~s~, cell expansion, cell division and the rate of leaf appearance [@passioura2002soil].
+Here, this was evident in a large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
 
-A lack of knowledge regarding the allocation of carbon diminishes our ability to distinguish the drivers of plant growth because mass balance cannot be reached.
+\
+Decreases in A~sat~ paralleled the reductions in allometric growth parameters of seedlings in containers.
+This initially suggests a tight link between A and growth, consistent with our hypothesis that growth declines would be mediated by the down regulation of A.
+However, there are several possible mechanisms that can explain reduced A in small pots, including nutrient content, water or reduced sink strength [@poorter2012pot].
+It was therefore necessary to examine each of these factors to distinguish if the induced belowground sink limitation actually triggered photosynthetic down regulation.
 
-##model setup
-I think the point here is that the model is quite standard and classical.
-It has growth driven by fluctuations in photoynthesis but respiration and allocation are very fixed processes.
-This reflects much of the growth&production modelling work out there.
-It turns out that in your experiment this did not really work, which means we must take a closer look at allocation and respiration (including root exudation)
-##growth and photosythesis not coordianted as expeceted, consequences for studies of biomass allocation
+\
+With high rates of g~s~, non-limiting leaf water potential and consistent leaf $delta$^13^C across soil volume treatments there was little evidence of water supply inducing a source limitation to A.
+This finding is consistent with other container size studies without drought treatments.
+For example, reduced A~max~ in cotton seedlings grown at elevated CO^2^ was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased g~s~ [@thomas1991root].
+Additionally, severe reductions in A in coffee plants was not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
+In these well watered seedlings it was likely that reductions in A were instead the result of a limited soil nutrient resource pool on belowground sink strength.
 
- If control is indeed distributed aroundthe plant, an experiment designed qualitatively to detect the presence of some source limitation shouldﬁnd it; but so should an experiment designed to testfor sink limitation (Farrah and Jones).
-The reason that so many conflicting reslutls exist is because....
+\
+Although the soil N pool declined evenly across all treatments leaf N was lowest in the smallest containers, suggesting that sink limitation was the greatest in these containers.
+This makes sense as small containers may reduce N uptake, either from physical root restriction or decreased supply, which affects growth, Rubisco limitation, sugar metabolism, and carbohydrate partitioning between source and sink tissues [@stitt1991rising; @hermans2006plants].
+Mycorrhizal colonization could also have been affected by the container effect.
+Whether unrestricted mycorrhizal recruitment facilitated the increase in leaf N uptake to leaves in free seedlings is unknown.
+Regardless of whether the sink limitation occurred from root or mycorrhizal restriction, the stark contrast between leaf N between free seedlings and seedlings in containers was significantly correlated to reductions in A.
 
- The fraction of assimilation used for respiration varies greatly among plants and increases with decreasing growth rates (Lambers et sl.
-2008)......
-problems with how we evaluate the respiration contribution of c allocation over shorter temporal scales .
-Our understanding of tissue respiration may also confound these short-term relationships with A and G.
+\
+As both rooting space and resources were finite in containers, the limited ability of these seedlings to increase the capacity of the belowground C sink was hypothesized to result in the buildup of C assimilate in the leaves.
+The feedback inhibition of A from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process (Nebauer et al.
+2011).
+Here, declines in A~max~ where correlated with higher starch content throughout the experiment.
+This agrees with findings from Equiza et a.
+(2006) where photosynthetic downregulation from reduced sink strength showed a greater correlation with starch than with sugar content in a deciduous conifer.
+As starch content in the smallest containers was nearly double that of free seedlings this suggests the response of A to sink inhibition was regulated by this accumulation, as hypothesized.
 
-  It is rather the norm than the
-exception that sink activity feeds back on source activity (e.g. through end-product inhibition
-in the chloroplast), causing growth (demand for carbon) to control photosynthesis, rather than
-the other way round (Korner 2013).
+## Carbon allocation under sink limitation
+As mass partitioning is likely controlled by source and sink strength of all organs [@poorter2012biomass] it was important to determine what tissue components were most affected by the sink limitation to then model the biomass response accurately.
+It was necessary to distinguish if growth was affected beyond ontogenetic constraints, by correcting for size, as biomass distribution is strongly size-dependent [@gould1966allometry; @lleonart2000removing].
+In this study, there were no significant changes in root, leaf, or stem mass fractions to reduced soil volume compared to free seedlings, outside of ontogenetic drift.
+This is significant as shifts in allocation, beyond ontogeny, have been noted specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein].
+In response to root restriction these seedlings might have altered allocation to ephemeral tissues, including fine roots or leaves to meet the changing resource requirements for A.
+Fine root mass to leaf mass ratio was instead conserved, regardless of plant size or treatment, suggesting an active biomass partitioning strategy to optimize resource gain did not occur.
+
+## Does reductions in photosynthesis explain reductions in seedling growth
+Our growth model used a simple but conventional approach to drive seedling growth with fluctuations in A while treating carbon use efficiency, respiration and carbon allocation as fixed processes.
+Contrary to expectation, the model consistently overestimated growth of seedlings in containers when parameterized with an optimal LMF from control seedlings.
+A linkage between sink limitation and A, however, does not necessarily imply the same level of coordination between reduced A and growth.
+These findings are important as this model reflects classical approaches in tree growth and production modelling.
+Our results indicate a need to evaluate the use of fixed processes in models which distinguish the fate of assimilate carbon within a plant.
+Doing so will provide valuable input to future plant growth models as assimilate allocation is a key component in functional-structural tree models, yet C partitioning remains a weak point [@lacointe2000carbon].
+To address this issue we utilized the flexibility of this model to test plausible fates of the extra pool of non-biomass carbon unaccounted for with mass balance.
+Through this approach, similar to [@lohier2014explaining], we manipulated processes contributing to seedling C mass balance, including changes to leaf C allocation or non-leaf tissue respiration, to quantitatively test their respective influences on model predictions.
+
+\
+Altering the LMF from that of the optimized seedling controls (M~2~) improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond A.
+The observed sub-optimal decrease LMF with increasing soil volume restriction has several possible explanations.
+Shifts in LMF could represent changes in senescence or leaf production that could not be explicitly quantified in this field study.
+As TNC accumulation due to sink limitation can lead to accelerated leaf senescence [@paul2001sink], this could explain the large declines in total leaf area of seedlings in small containers.
+Alternatively, as A was similar between soil volume treatments seedlings could have reduced leaf production to maintain laws of stoichiometry (leaf C:N ratio).
+The two-fold decrease in leaf N % in small containers from control seedlings provides support to this possible scenario.
+Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of A and the fate of C allocated to leaves.
+It will be the interactions between these two components that will determine the total C gain available for plant growth.
+
+\
+Increasing rates of non-leaf respiration (M~3~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation.
+This finding is still noteworthy as it justifies an evaluation of how changes in sink activity may differentially affect respiration of component tissues.
+The fraction of photosynthate used in respiration varies substantially among species and environments  and is sensitive to changes in growth rates [@Lambers2008].
+As C balance is a delicate equilibrium between fluxes of A and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions (Valentini et al.
+2000).
+Keeping rates of respiration fixed in growth models may underestimate impacts of environmental change on tissue respiration above and belowground.
+We agree with Delucia et al.
+[-@delucia2007forest] that it is likely inappropriate to assume that respiration is a constant fraction of gross primary production in models.
+Our findings reveal that a combination of different mechanisms, beyond A, is likely at play in driving the observed seedling biomass response to sink manipulation.
+However, the degree to which these mechanisms will regulate a growth will undoubtedly shift across different experimental manipulations and plant species.
+
+## Conclusions
+It has long been know that conditions which affect the photosynthetic process affect growth but that there is also an interrelationship between growth and A [@sweet1966role].
+Here, the fate of assimilated C available for plant growth varied between naturally sown seedlings and seedlings with belowground sink inhibition.
+First, this is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles but how these results actually reflect field-grown plants has seldom been studied.
+Second, our finding add more evidence that A and growth are not always entirely synced, an important distinction often missed in studies that manipulate source/sink activity.
+Korner [@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control A through the demand for C  Although this may be true, we argue that attempts to quantify or at least predict the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
+Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
+A lack of knowledge regarding C allocation restricts our ability to achieve mass balance and is a major obstacle in understanding the coordination between A and growth.
+In any case, we should not assume that
 
@@
 phys_data <- read.csv("master_scripts/pve_table2.csv")
-colnames(phys_data) <- c("Volume~(L)", 
+colnames(phys_data) <- c("Volume (L)", 
                         "\\textit{A}\\textsubscript{max}", 
@@
 Each value reflects the mean(standard error) for each treatment.
-Units for A~max~ and R~dark~ are $\mu$mol m^-2^ s^-1^ and g~s~ are mol m^-2^ s^-1^, each at at 25&deg;C.
+Units for A~max~ and R~dark~ are $\mu$mol m^-2^ s^-1^ and g~s~ are mol m^-2^ s^-1^, each at at 25 &deg;C.
 Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n=6).
@@
 
-```{r airvars, fig.width=6, fig.height=8, echo=FALSE}
+```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=300, dev.args=list(type="cairo")}
 source("master_scripts/airvars_plotting.R")
@@
 
-```{r allometry, fig.width=6, fig.height=8, echo=FALSE}
+```{r allometry, fig.width=6, fig.height=8, echo=FALSE,  dev="png", dpi=300, dev.args=list(type="cairo")}
 source("master_scripts/allometryplotting.R")
@@
 
-```{r allocation, fig.width=6, fig.height=10, echo=FALSE, warning=FALSE, message=FALSE}
+```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=300, dev.args=list(type="cairo")}
 source("master_scripts/allocation_plotting.R")
@@
 
-```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE}
+```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=300, dev.args=list(type="cairo")}
 source("master_scripts/A_stats_plotting.R")
@@
 
-```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE}
+```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=300, dev.args=list(type="cairo")}
 source("master_scripts/Amax_TNC_N_plotting2.R")
@@
 
-```{r massmodel, fig.width=6, fig.height=8, echo=FALSE}
+```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=300, dev.args=list(type="cairo")}
 source("master_scripts/massmodel_optimize.R")
@@
 
-```{r model_scenarios, fig.width=6, fig.height=8, echo=FALSE}
+```{r model_scenarios, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=300, dev.args=list(type="cairo")}
 source("master_scripts/massmodel_optimize_scenarios.R")

### 2015-07-20 tables_latex/pve_manuscript.Rnw
added tables to manuscript (jpg)

@@
 \usepackage{textcomp}
+
+\pagestyle{empty}
 
@@
 
-% for author affiliations
-\usepackage{authblk}
-
-%allows inline citations
-\usepackage[round]{natbib}
-\bibliographystyle{plainnat}
-
 % for degree symbol
 \usepackage{gensymb}
-
-% for line numbers
-\usepackage{lineno}
 
@@
 \geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
-
-% for bibtex
-% \usepackage{authordate1-4}
-% \bibliographystyle{authordate1}
 
@@
 \begin{document}
-
-\linenumbers
-
-\title{Effects of below-ground space limitation on performance of Eucalyptus seedlings:  Does photosynthesis really control growth?}
-
-\author[1,3]{Courtney E. Campany}
-\author[2]{Belinda E. Medlyn}
-\author[1]{Remko A. Duursma}
-
-\affil[1]{Hawkesbury Institute for the Environment, University of Western Sydney, Richmond, NSW 2753, Australia}
-\affil[2]{Department of Biological Sciences, Macquarie University, North Ryde, NSW 2109, Australia}
-\affil[3]{Corresponding author (c.campany@uws.edu.au)}
-
-\renewcommand\Authands{ and }
-\maketitle
+\SweaveOpts{concordance=TRUE}
 
@@
 
-%--------------------------------------------------------------------------------------------%
-
-\section*{Abstract}
-
-Interpreting limitations to plant growth requires understanding of the balance between carbon (\textit{C}) source and sink activity in order to assess \textit{C} allocation and biomass partitioning.
-This study used manipulations of soil volume to test how growth is coupled to physiology, allocation, and sink activity in \textit{Eucalyptus tereticornis} seedlings.
-We grew seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown seedlings (free).
-Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
-It was hypothesized that soil volume effect would be largest in the smallest containers, resulting in physical constraints to growth independently of photosynthesis (\textit{A}).
-Photosynthesis would then become sink-limited, resulting in the build-up of leaf nonstructural carbohydrates eventually leading to photosynthetic down regulation.
-We observed a negative container effect on aboveground growth soon after the experiment started.
-Although growth was consistently different across soil volumes mass, partitioning to leaves, stems, roots was conserved after 120 days.
-Photosynthetic capacity was also significantly reduced in containers, and was related to both leaf nitrogen content and starch accumulation.
-We developed a seedling growth model that utilized leaf \textit{A} rates to allocate daily \textit{C} uptake towards mass growth of stems, leaves and roots.
-We then asked whether the observed reductions in \textit{A} explained the observed differences in seedling biomass.
-We found that although belowground sink limitation resulted in the down regulation of \textit{A}, these reductions were not significant enough to explain observed growth responses.
-Thus, as photosynthesis and growth were not coordinated an excess pool of non-biomass \textit{C} resulted in seedlings with soil volume restriction.
-This research highlights the need to further utilize mass balance approaches when evaluating plant \textit{C} allocation and confirms that \textit{A} and growth are not always directly related.
-
-\section*{Key Words}
-
-photosynthesis, growth, sink regulation, carbon allocation, soil volume
-
-\section*{Introduction}
-
-Understanding plant growth requires knowledge of the mass balance that must be achieved between \textit{C} uptake and subsequent allocation to growth, storage, and respiration.
-It is commonly assumed plant growth is limited by \textit{C} availability, yet it has long been demonstrated that correlations between \textit{A} and growth are weak or seldom present.
-\citet{korner2013growth} argues that growth instead controls \textit{A}, as it is the norm for sink activity to feedback on source activity.
-This is supported by evidence that growth of plants under environmental stress is not limited by the supply of photoassimilates \citep{palacio2014does}.
-As woody plants have highly integrated systems of competing carbohydrate sinks \citep{kozlowski1992carbohydrate}, growth should principally depend on the transport of these photoassimilates between different tissue and organ sinks.
-Despite a wealth of studies, however, large uncertainties still remain regarding the coordination of \textit{C} supply, via \textit{A}, and growth of woody species.
-
-In woody species, how \textit{A} controls growth has been studied with manipulations of \textit{C} source activity.
-Examples included elevated CO\textsubscript{2} experiments, for example FACE (reviewed in  \citet{ainsworth2005have}, and partial defoliation experiments.
-Elevated CO\textsubscript{2} has been shown to increase \textit{A} rates \citep{drake1997more,ainsworth2007response} and across four FACE experiments this resulted in a conserved increase in forest production \citep{norby2005forest}.
-Evidence from elevated CO\textsubscript{2} experiments, however, also reveals that the growth response tends to be much smaller than the photosynthetic enhancement \citep{kirschbaum2011does}.
-In defoliation experiments, compensatory increases in \textit{A} are commonly shown yet are attributed to variable mechanisms, including reduction in end product inhibition \citep{iglesias2002regulation,zhou2003changes,handa2005test}, enhanced biochemical activity \citep{ovaska1993b,layne1995end}, increased stomatal conductance \citep{layne1995end}, leaf nutrient status \citep{turnbull2007increased}, and regulatory sugar signaling \citep{eyles2013whole}.
-However, increases in \textit{A} did not always produce increased growth due to reductions in meristem sink strength (Palacio et al.
-2012), \textit{C} limitation to mycorrhizal colonization (Markkola et al.
-2004), or an overall decrease in whole plant \textit{C} gain \citep{ovaska1993a}.
-These manipulations of \textit{C} source activity expose unresolved issues with how changes in \textit{A} do not always infer similar responses in growth.
-
-Alternatively, manipulation of plant tissue carbon sinks is often used to investigate the correlation of photosynthesis and growth.
-Tissue sink activity can restrict biomass production when limited by environmental or developmental constraints \citep{korner2003carbon}.
-This is because metabolic signaling networks, relaying information on \textit{C} and nitrogen (\textit{N}) status of different tissues, can down regulate photosynthetic activity \citep{paul2001sink}.
-Whether this down regulation, via sink inhibition, is evident in woody species has been tested through fruit removal, girdling, and low temperatures.
-In these studies, down regulation of \textit{A} was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength \citep{iglesias2002regulation,hoch2002altitudinal,urban2007girdling, haouari2013fruit}.
-However, reductions in \textit{A} were also attributed to biochemical limitations prior to carbohydrate accumulation \citep{nebauer2011photosynthesis}, irreversible photo-oxidative damage \citep{duan2008photosynthetic}, and stomatal limitation \citep{li2005photosynthesis}.
-These mixed results are not surprising as we still know little about the pathways in which plants achieve balance between assimilation, storage, and growth across temporal scales \citep{smith2007coordination}.
-As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to large annual fruiting sinks, they tell us little about source-sink coordination in ‘normal’ field-grown woody species.
-
-An alternative experimental approach is to lower belowground \textit{C} sink strength in tree seedlings by manipulating rooting volume, by varying the container size.
-The advantage of this approach is it allows a large range of manipulations, can be easily compared to naturally planted seedlings and mimics natural conditions as seedlings compete for space or reach bedrock.
-Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, \textit{A}, water relations, nutrient uptake and respiration \citep[and references therein]{nesmith1998effect}.
-Inadequate rooting volume may decrease carbon sink strength by progressively restricting root growth \citep{thomas1991root}.
-Container size studies frequently have photosynthetic down-regulation, likely as a result of sink limitation \citep{arp1991effects, mcconnaughay1991physical, gunderson1994photosynthetic, sage1994acclimation, maina2002intra, ronchi2006growth}.
-A meta-analysis by \citet{poorter2012pot} concluded that \textit{A} is the process likely to be the strongest affected by pot size and may best explain the observed effect on biomass seen in the large number of studies where containers are used.
-This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower \textit{C} exchange and assimilate export rates \citep{robbins1988effect}.
-However, evidence in support for a trade-off between \textit{C} storage and growth in trees is, to date, inconclusive \citep{palacio2014does}.
-Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test how growth and \textit{A} are coordinated.
-
-Our lack of knowledge regarding the allocation of \textit{C} in woody species is still a major obstable in understanding the cooridatnation between  \textit{A} and growth.
-Understanding the fate of assimilated \textit{C} is crucial when source or sink manipulations do not directly lead to equivalent changes in growth.
-As programmed plasticity in \textit{C} allocation naturally occur as plants growth and develop, this must be accounted for when evaluating induced variation in growth \citep{wright2002interpreting}.
-Thus, when \textit{C} allocation is altered by a treatment, it should be shown whether these allocation patterns differ from common sized untreated plants \citep{reich2002root, poorter2012biomass}.
-Only then can we test if functional balance preservation or optimal foraging occurs from changes in \textit{C} uptake.
-For example, seedlings in containers may shift allocation to leaves if root restriction occurs or alter fine root morphology to increase nutrient uptake.
-In woody species, shifts in allometric relationships of leaves, stems and roots can reveal if growth is ontogenetically constrained or actively adjusted when \textit{A} is affected.
-This then allows additional pools of \textit{C}, such as root exudation or changes in tissue respiration, to be accounted for and evaluated.
-
-This study utilizes a novel field design to investigate the coordination between growth and \textit{A} in \textit{Eucalyptus tereticornis} Sm.~seedlings, by manipulating container size and thus rooting volume.
-Seedlings were maintained under well watered conditions in order to evaluate only the effect of restricted soil volume and the limited nutrient resource pool.
-We used freely-rooted seedlings as a control for the container size treatments.
-Empirical results were combined with a simple plant growth model to simulate seedling growth with a \textit{C} mass balance approach, which was then compared to observed harvested seedling mass.
-The model used whole-plant \textit{C} gain, scaled from instantaneous rates of leaf \textit{A}, to quantify seedling production over 120 days.
-
-1).
-The manipulations of container size were hypothesized to induce a belowground sink limitation in these seedlings which was expected to be largest in the smallest containers, resulting in physical constraints to growth independently of \textit{A}.
-
-2).
-Reducing soil volume was then expected to induce negative effects on leaf physiology compared to free seedlings (‘container effect’).
-This accumulation of leaf nonstructural carbohydrates was expected to trigger photosynthetic down regulation as a function of soil volume and create further negative feedbacks to growth through time.
-
-3). Last, the growth model was expected to find agreement between simulated and observed seedling mass, through direct correlation of the effects of soil volume on rates of leaf \textit{A}.
-
-\section*{Methods}
-
-\subsubsection*{\textit{Experimental Design}}
-
-This experiment was located on the Hawkesbury Forest Experiment site in Richmond, NSW, Australia.
-Plots were located in open cover with a site history that consists of a paddock that was converted from native pasture grasses.
-Top soils at this site, used for the study, are an alluvial formation of low-fertility sandy loam soils (380 and 108~mg~kg\textsuperscript{-1} total \textit{N} and phosphorus respectively) with low organic matter (0.7~\%) and low water holding capacity.
-At this site a soil hard layer exists at $\sim$1.0~m with a transition to heavy clay soils.
-The climate for the region is classified as sub-humid temperate.
-
-\textit{Eucalyptus tereticornis} seedlings, 20~weeks old and approximately 40~cm tall in tube stock, were chosen from a single local Cumberland plain cohort.
-Previous experiments have confirmed that species with tap roots (similar to \textit{E.
-tereticornis}) use the center of the container as the medium for thick roots leaving the periphery of the soil as the most active sites for fine root proliferation \citep{biran1980a,biran1980b}.
-This is generally hypothesized to be a different response than seedlings with no taproot.
-By using a species with tap root growth and manipulations of container length rather than width, it is believed that a more realistic test of inhibition of growth through constrained soil volume would be achieved.
-Six seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.
-
-Six container volumes were used ranging from 5~l to 35~l, with a 22.5~cm diameter, and lengths ranging from 15 to 100~cm.
-Containers were constructed of PVC pipe and were filled with local top soil (described above).
-Soil in each container was packed to achieve a target soil bulk density of 1.7~g~m\textsuperscript{-3}.
-A Imidacloprid (BAYER CropScience) insecticide tablet was planted 5 cm below the roots of each seedling.
-Containers were planted flush with the soil surface inside metal sleeves, designed to minimize excess air space between the container and outside soil while also allowing for container removal.
-This allowed for soil temperatures in containers to reflect conditions of naturally sown (free) seedlings.
-Each experimental block (n=7) contained a complete replicate set of container volumes as well as one free seedling, with 1 m\textsuperscript{2} spacing.
-For each free seedling, used as the control, a 1~m\textsuperscript{2} subplot was excavated to 0.5~m and replaced with the same soil used in each container.
-A border of root exclusion material was buried 0.25~m deep and extended 0.25~m above the ground surface around each subplot to exclude local vegetation.
-
-Plants were watered weekly or when needed, accounting for natural precipitation, to maintain soil moisture at field capacity (13-15~\%).
-Drain systems were built into each pot to prevent pooling of water in containers before root expansion, from reduced root uptake, or from large rainfall events.
-These conditions could lead to an anaerobic environment around the root that could hinder the uptake of water through reduced root conductance \citep{poorter2009causes}, an undesired experimental artifact.
-A collection compartment in the bottom of containers, containing gravel covered by root exclusion mesh, was used to collect excess water for 20, 25, and 35~l containers.
-Plastic tubing (6~mm diameter) was inset into the gravel layer and extended through the top of the container.
-A lysimeter pump was then used to suction excess water, through the tubing, as needed .
-As small containers (5, 10, and 15~l) have a larger irradiation effect a simple bottom plug was used to drain excess water from the gravel compartment.
-
-\subsubsection*{\textit{Growth and morphology metrics}}
-
-Seedlings were planted on January 21\textsuperscript{st} 2013 and stem height, diameter at 15~cm and leaf count were measured weekly thereafter.
-Once the growth rate of individual plants had significantly declined a full biomass harvest was completed (May 21\textsuperscript{st} 2013).
-Dry mass of leaves, stems, roots and cumulative leaf area (LI-3100C Area Meter; LI-COR, Lincoln, NE, USA) was measured for each seedling.
-Mean individual leaf area for each harvested seedling was calculated by dividing cumulative leaf area by total leaf count of only fully expanded leaves.
-This value was then used to interpolate cumulative leaf area through time with weekly leaf counts.
-Root mass was collected by passing soil from each container through a 1~mm sieve, washing, separating into fine and coarse roots (\textless2~mm and \textgreater2~mm diameter, respectively) and then drying to a constant mass.
-Roots from the free seedlings were collected by excavating each 1~m\textsuperscript{2} subplot to 0.5~m depth.
-25~g fresh weight subsamples of washed fine roots were analyzed, using WhinoRhizo software (Regent Instruments Inc.), for specific root length (SRL, cm~m\textsuperscript{-1}).
-
-\subsubsection*{\textit{Photosynthetic parameters}}
-
-Leaf gas exchange measurements were performed bi-weekly at saturating light (\textit{A}\textsubscript{sat}) and saturating light and [CO\textsubscript{2}] (\textit{A}\textsubscript{max}) on new fully expanded leaves.
-Measurements were initiated only after sufficient new leaf growth occurred (March 17\textsuperscript{th}, 2013), approximately 6 weeks following planting, and continued until the biomass harvest.
-Leaf level gas exchange was measured with a standard leaf chamber equipped with blue-red light emitting diodes using a portable gas exchange system (LI-6400, LI-COR, Lincoln, NE, USA).
-\textit{A}\textsubscript{sat} measurements were made at PPFD of 1800~{\textmugreek}mol~m\textsuperscript{-1}~s\textsuperscript{-1} and [CO\textsubscript{2}] of 400~{\textmugreek}l~l\textsuperscript{-1} and \textit{A}\textsubscript{max} with [CO\textsubscript{2}] of 1600~{\textmugreek}l~l\textsuperscript{-1} and PPFD of 1800~{\textmugreek}mol~photons~m\textsuperscript{-1}~s\textsuperscript{-1}.
-This choice of light level to achieve light saturation is consistent with other studies on \textit{Eucalyptus} species \citep{kallarackal1997ecophysiological,pinkard1998photosynthetic,crous2013photosynthesis,drake2014capacity}.
-These measurements were conducted during midday (10:00-14:00~h) with leaf temperature maintained at 25$\degree$C.
-After leaves acclimated to the chamber environment, net CO\textsubscript{2} assimilation rate and stomatal conductance (\textit{g}\textsubscript{s}) were logged 5 times for both \textit{A}\textsubscript{sat} and \textit{A}\textsubscript{max}.
-Photosynthetic CO\textsubscript{2} response (AC\textsubscript{i}) curves were also developed at 25$\degree$C on a random subset of each container size (n=3) after new leaves were first produced and immediately prior to the final harvest (May 23\textsuperscript{rd} 2013).
-Each AC\textsubscript{i} curve began at the reference [CO\textsubscript{2}] of 400~{\textmugreek}l~l\textsuperscript{-1} and then consisted of 12 additional steps from [CO\textsubscript{2}] of 50 to 1800~{\textmugreek}l~l\textsuperscript{-1}at 25$\degree$C at saturating light (above).
-From these curves the photosynthetic parameters, \textit{J}\textsubscript{max} and \textit{Vc}\textsubscript{max}, were quantified using the biochemical model of \citet{farquhar1980biochemical}.
-Leaf dark respiration rates (\textit{R}\textsubscript{d}) was measured on each seedling during the same dates as AC\textsubscript{i} curves using detached leaves inside a conifer chamber attached to the Licor 6400 at least 1 hour after sundown.
-Measurements were taken at a reference [CO\textsubscript{2}] of 400~{\textmugreek}l~l\textsuperscript{-1} while leaf temperature was maintained at current ambient conditions.
-Reported values of \textit{R}\textsubscript{d} are standardized rates at 25$\degree$C using a Q10 value (1.86) developed for these seedlings in a separate experiment (Drake et al.
-unpublished).
-Leaf area and dry mass were recorded for each leaf during gas exchange campaigns.
-
-\subsubsection*{\textit{Leaf water potential}}
-
-Predawn ($\Psi\textsubscript{pd}$) and midday ($\Psi\textsubscript{l}$) leaf water potentials were measured for each seedling using a PMS 1505D pressure chamber (PMS Instruments, Albany, OR, USA) on fully expanded leaves during the same time period as AC\textsubscript{i} and \textit{R}\textsubscript{d}.
-Leaves were detached and immediately stored inside foil covered bags before water potential measurements were performed.
-$\Psi\textsubscript{pd}$ was measured before sunrise and $\Psi\textsubscript{l}$ at midday 13:00-14:30~h.
-These measurements were used as a measure of static water stress on the seedlings \citep{sellin1999does}, and to ensure that the bulk soil water availability was high enough for plants as they became larger and roots filled the soil volume.
-
-\subsubsection*{\textit{Leaf, root and soil chemistry}}
-
-Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of \textit{N} content, {\textdelta}\textsuperscript{13}C, and total non-structural carbohydrates (TNC).
-Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis.
-\textit{N} concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of \textit{N}\textsubscript{2} and CO\textsubscript{2}).
-The percentage of \textit{N} in the sample was calculated by comparison with known standards.
-Leaf {\textdelta}\textsuperscript{13}C was analyzed  with an Delta V Advantage coupled to a Flash HT and Conflo IV isotope ratio mass spectrometer.
-Leaf samples were flash combusted at 1000$\degree$C to convert to to CO\textsubscript{2}, feed to the mass spectrometer and isotopic signatures are reported relative to the VPDP scale.
-Leaf TNC concentration was analyzed using a total starch assay kit (Megazyme International 303 Ireland Ltd., Wicklow, Ireland) and includes the starch (mg~g\textsuperscript{-1}) and soluble sugar (mg~g\textsuperscript{-1}) concentrations.
-Starch was quantified using a thermostable $\alpha$-amylase and amyloglucosidase assay \citep{McCleary_starch} and soluble sugars were determined following the anthrone method \citep{ebell1969variation}.
-Complete methods of the TNC assay are described in \citep{mitchell2013drought}.
-Specific leaf area (SLA, m\textsuperscript{2}~kg\textsuperscript{-1}), for leaves sampled during gas exchange campaigns, was then calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass.
-
-\subsubsection*{\textit{Seedling growth model}}
-
-We developed a simple seedling growth model that utilized leaf \textit{A} rates to allocate daily \textit{C} assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
-The model begins with mean initial tissue component biomass (leaf\textsubscript{i}, stem\textsubscript{i} and root\textsubscript{i}) and a starting leaf area (LA\textsubscript{i}) measured prior to planting.
-The initial biomass of roots was divided evenly between fine and coarse roots.
-The daily net biomass production of seedlings (P\textsubscript{i}) is then given by
-\begin{equation} P\textsubscript{i}=L~(C\textsubscript{day,i}~\sigma\textsubscript{s}~\epsilon\textsubscript{c}\textsuperscript{-1})-R
-\label{eq:prod}
-\end{equation}
-where L is standing cumulative leaf area, C\textsubscript{day,i} is the predicted daily carbon assimilation, $\sigma\textsubscript{s}$ is a self shading parameter, \textepsilon\textsubscript{c} is a biomass conversion efficiency parameter and R is the total respiration of all tissue components.
-Total respiration was calculated as
-\begin{equation} R=\Sigma(R\textsubscript{c}~M\textsubscript{c})
-\label{eq:resp}
-\end{equation}
-where R\textsubscript{c} is tissue respiration of fine roots, coarse roots or stems on a mass basis and M\textsubscript{c} is the standing biomass of each component.
-R\textsubscript{leaf} is represented in the calculation of C\textsubscript{day} (described below).
-The change in individual component biomass (M\textsubscript{c}), here solved on a daily time step, is given by
-\begin{equation} \frac{dM\textsubscript{c}}{dt}=A\textsubscript{c}~P\textsubscript{i}-(\Lambda\textsubscript{c}~M\textsubscript{c})
-\label{eq:mass}
-\end{equation}
-where A\textsubscript{c} is the component specific biomass partitioning  to whole plant biomass (\%) and $\Lambda\textsubscript{c}$ is component specific turnover rate.
-Due to the duration of the experiment $\Lambda\textsubscript{stem}$ was assumed to equal 0.
-Total seedling biomass, per time step, was then equal to the sum of all biomass components; leaves, stems, fine roots and coarse roots.
-
-\textit{C}\textsubscript{day} was predicted by fitting a coupled photosynthesis - stomatal conductance model \citep{farquhar1980biochemical,medlyn2011reconciling} in the 'plantecophys' package in R \citep{Duursma2014} to the mean photosynthetic parameters (R\textsubscript{d}, J\textsubscript{max}, V\textsubscript{cmax}, and g\textsubscript{1}) for each treatment and meteorological data from an onsite weather station.
-Examples of the photosynthesis model are described in \citet{medlyn2002temperature} and the approach of the coupled leaf gas exchange model are described in \citet{duursma2014peaked}.
-The g\textsubscript{1} parameter was generated by fitting observed \textit{g}\textsubscript{s} values into the optimal stomatal conductance model from \citep{medlyn2012reconciling}.
-Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15~m intervals, leaf \textit{A} rates ({\textmugreek}mol~CO\textsubscript{2}~m\textsuperscript{-2}~s\textsuperscript{-1}) were then predicted for each soil volume treatment.
-Rates were assumed to be representative of the entire 15~min meteorological interval.
-\textit{C}\textsubscript{day} was calculated by converting predicted rates to mass \textit{C} gain over 15~min (g~m\textsuperscript{-2}) and then summed for 24~h.
-This resulted in 120 unique values of \textit{C}\textsubscript{day} for each soil volume treatment, one value for each day of the experiment.
-Thus, each daily time step for model runs included a value of \textit{C}\textsubscript{day} that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
-
-It was further necessary to calculate a self-shading parameter ($\sigma\textsubscript{s}$) when scaling leaf \textit{A} with cumulative seedling leaf area.
-This was accomplished by utilizing 61 previously digitized Eucalyptus seedlings, covering 5 total species which include \textit{E.
-tereticornis}, from \citet{duursma2012light} to run in 'YplantQMC' package in R (fix cite YplantQMC) to build a 3d plant structure based on digitized metrics of plant allometry and crown structure.
-Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total \textit{A}, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
-The ratio of total \textit{A} with self-shading to horizontal leaf was then used to calculate $\sigma\textsubscript{s}$ for each of the 61 digitized seedling, independently for each treatment.
-Next, the linear relationship between $\sigma\textsubscript{s}$ and total leaf area was for determined across digitized seedlings, within each treatment.
-For the growth model, $\sigma\textsubscript{s}$ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to \textit{C}\textsubscript{day,i}.
-All default parameters used in model simulations are reported in Table.~\ref{table:Table3}.
-
-We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf \textit{A} where sufficient to accurately predict overall seedling biomass production after 120 days.
-Each model run utilized changes in \textit{A} and leaf mass fraction, with published or local values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
-Cumulative net leaf carbon gain for each treatment was equal to the sum of each value of \textit{C}\textsubscript{day,i} over 120 days and final seedling carbon was assumed to equal half of the final mass for both modeled and observed seedlings.
-First, a default model was optimized to produce a final leaf mass fraction that correctly predicted both the final leaf mass and total biomass of the harvested free seedling controls (M\textsubscript{0}).
-This optimized leaf mass fraction was then applied to model runs with treatment specific \textit{C}\textsubscript{day} to determine if changes in  leaf \textit{A} alone could accurately predict biomass (M\textsubscript{1}).
-Next, model sensitivity to different \textit{C} allocation scenarios, including non-optimized treatment specific leaf mass fraction and up regulation of non-leaf tissue respiration by 50~\% of default values (M\textsubscript{2,3, respectively}), was used to improve predictions of initial model simulations from measured harvest biomass.
-For all cases, seedling production was compared between model output and harvested seedlings with treatment specific mean daily carbon assimilation by first scaling values to the free seedling control.
-
-\subsubsection*{\textit{Data Analysis}}
-
-Differences in experimental parameters with soil volume were analysed by one-way analysis of variance (ANOVA) in R with individual containers as random effects and soil volume as a categorical fixed effect.
-Tukey’s post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
-Mixed model ANOVAs of \textit{A}\textsubscript{max} and leaf chemistry were performed using the 'nlme' package \citep{nlme} in R and \textit{r}\textsuperscript{2} values of mixed models were computed as in \citet{nakagawa2013general}.
-Tests of allometric relationships between biomass components were implemented using major axis regression in the 'smatr' package in R \citep{warton2012smatr}.
-Results were considered significant at P$\leq$0.05.
-
-\section*{Results}
-
-\subsubsection*{\textit{Growth and morphology metrics}}
-
-In this field study, colder temperatures and reductions in cumulative PPFD per day (Fig.~\ref{fig:figure1}) most likely lead to the reduced growth in the free seedlings in the final weeks of the experiment (Fig.~\ref{fig:figure2}).
-Combined with severe growth reductions in the smallest container volumes the experiment was chosen to be harvested after 120~days.
-Over this duration height, diameter, and leaf area diverged between container volumes (Fig.~\ref{fig:figure2}).
-First, seedling leaf area significantly diverged between soil volumes (\textit{P}\textless0.026) during the 5\textsuperscript{th} week of the experiment.
-Following this period both height (8\textsuperscript{th} week) and then diameter (9\textsuperscript{th} week) significantly deviated across soil volumes (\textit{P}\textless0.002 \& 0.001, respectively).
-Negative growth effects then manifested as severely reduced height gain and declining leaf area through time with small soil volumes across the final two months of the experiment.
-Seedlings maintained diameter growth throughout the experiment, although marginal with smaller soil volumes in the final month.
-Final seedling height significantly increased with increasing soil volume (\textit{P}\textless0.001).
-Increases in both final stem diameter (\textit{P}\textless0.001) and cumulative leaf area (both \textit{P}\textless0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling.
-
-Total seedling biomass at harvest was significantly different across container volumes (\textit{P}\textless0.001) and with free seedlings (\textit{P}\textless0.001, Table.~\ref{table:Table1}).
-We analyzed the relationship between biomass growth with each fold increase in soil volume and found an increase of 34~\% with a doubling of pot size, consistent with the meta-analysis of \citet{poorter2012pot}.
-Additionally, plant biomass was highly correlated with total leaf area across all treatments (\textit{r}\textsuperscript{2}~=~0.97, \textit{P}\textless0.001).
-Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass within treatments was factored in the analysis (Fig.~\ref{fig:figure3}a,b).
-Across all treatments, the final harvested root:shoot was conserved in these seedlings, with a slightly higher shoot than root mass on average ($\overline{x}$=0.904, Fig.~\ref{fig:figure3}c).
-
-SRL of harvested fine roots was not different across soil volumes (Table.~\ref{table:Table1}).
-Over the duration of the experiment SLA was higher in free seedlings but was not different across containers sizes (Table.~\ref{table:Table1}, \textit{P}\textless0.001) and this pattern was evident in the first gas exchange measurement campaign (\textit{P}\textless0.001).
-
-\subsubsection*{\textit{Leaf chemistry}}
-
-Leaf \textit{N}~\% was significantly higher in free seedlings and the largest container volume at the onset of gas exchange measurements (6th week, \textit{P}\textless0.001).
-Over the remaining duration of the experiment the smallest container volume had a significant reduction in leaf \textit{N}~\% compared to other soil volumes, while free seedlings maintained the highest leaf \textit{N}~\% (Table.~\ref{table:Table1}, \textit{P}\textless0.001).
-Leaf starch content in the smallest container was double that of free seedlings (\textit{P}=0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table.~\ref{table:Table1}).
-Differences in leaf starch between the free seedling and the smallest container were also evident during the first gas exchange campaign (\textit{P}=0.0013).
-
-\subsubsection*{\textit{Gas exchange and photosynthetic parameters}}
-
-\textit{A}\textsubscript{sat} (Fig.~\ref{fig:figure4}) and \textit{A}\textsubscript{max} (Table.~\ref{table:Table2}) were both significantly higher in the largest container volume and the free seedling at the first measurement campaign (both \textit{P}\textless0.001).
-Across all measurement campaigns \textit{A}\textsubscript{sat} was consistently higher in free seedlings than in containers (Figure 3, \textit{P}\textless0.001).
-The interaction between photosynthetic capacity, leaf starch, and leaf \textit{N} on a mass basis was marginally significant (\textit{P}=0.0584) but \textit{A}\textsubscript{max} was highly correlated to both leaf \textit{N} content and leaf starch (both \textit{P}\textless0.001).
-Across all measurement campaign \textit{A}\textsubscript{max} was higher when foliar \textit{N} was also higher, usually associated with low levels of leaf starch (Fig.~\ref{fig:figure3}a).
-\textit{A}\textsubscript{max} was also lower when leaf starch was high as higher leaf \textit{N} often did not coincide with high leaf starch (Fig.~\ref{fig:figure3}b)
-
-The photosynthetic parameters~\textit{J}\textsubscript{max} and~\textit{Vc}\textsubscript{max} were not different within treatments at the beginning and end of gas exchange campaigns, therefore the parameter means per treatment are reported here (Table.~\ref{table:Table2}).
-Overall, both \textit{J}\textsubscript{max} and \textit{Vc}\textsubscript{max} were significantly higher in free seedlings with little variation between soil volume treatments (\textit{P}=0.0012 \& 0.0021, respectively).
-Leaf dark respiration rates were not significantly different across soil volumes (Table.~\ref{table:Table2}).
-The \textit{g}\textsubscript{1} parameter, generated for each seedling from the \citet{medlyn2012reconciling} optimal stomatal conductance model, was lowest in the free seedling and was marginally different across soil volume treatments (Table.~\ref{table:Table2}).
-Predicted values of \textit{g}\textsubscript{s}, using the \textit{g}\textsubscript{1} parameter, where highly correlated with observed values (\textit{r}\textsuperscript{2}= .74, \textit{P}\textless{0.001}, data not shown).
-
-Neither $\Psi\textsubscript{pd}$ nor $\Psi\textsubscript{l}$ were different across treatments, with mean values of -0.27 and -1.2~mPa across all seedlings, respectively.
-Although \textit{g}\textsubscript{s} in free seedlings was generally higher than those in containers (Table.~\ref{table:Table2}, \textit{P}=0.001), the mean rates for all seedlings were high at 0.37~mol~H\textsubscript{2}0~m\textsubscript{-2}~s\textsubscript{-1} and did not decline significantly across the experiment duration.
-Additionally, leaf {\textdelta}\textsuperscript{13}C at final harvest was not different across treatments (Table.~\ref{table:Table1}).
-Combined these indices provide strong evidence that water stress was not apparent on these well-watered seedlings throughout the experiment.
-Soil \textit{N}~\% at harvest was not different across soil volumes ($\bar{x}$=04.5~\%) and decreased approximately 3~\% across all containers over the experiment duration.
-This indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
-
-\subsubsection*{\textit{Modelling seedling biomass}}
-
-Model M\textsubscript{0}, was able to converge on an optimum leaf mass fraction (21.6~\%) which accurately predicted the mean harvest total biomass of free seedlings within 1.2~\%.
-Using this optimized leaf mass fraction the gross primary productivity of modeled seedlings with soil volume restriction (M\textsubscript{1}) were on average 23$\pm$2.4~g \textit{C} more than measured seedlings When comparing against predicted total net leaf \textit{C} gain (Fig.~\ref{fig:figure6}a).
-Thus, seedling mass \textit{C} was overestimated by an average of 50$\pm$8.7~\% in modeled seedlings across the reductions in daily \textit{C} assimilation per treatment (Fig.~\ref{fig:figure6}b).
-As a result, the reductions in leaf \textit{A} were not sufficiently high enough to explain the reduction in harvested seedling biomass with soil volume restriction.
-With mass balance this resulted in an unexplained pool of excess \textit{C}, generated from \textit{A}, that did not end up in biomass.
-
-The remaining model simulations tested \textit{C} allocation scenarios in an attempt to account for this remaining pool of missing \textit{C}.
-Constraining the model with the measured treatment specific leaf mass fraction from the final harvest (M\textsubscript{2}) still overestimated seedling total \textit{C} by 32$\pm$11.1~\%, but provided the most improved model predictions (Fig.~\ref{fig:figureSI1}a).
-Harvested leaf mass fraction, however, does not capture the likely increase in senescence of seedlings in small containers (Fig.~\ref{fig:figure2}c).
-Thus, the 7-61~\% reduction in measured harvested leaf mass fraction from large to small soil volumes compared to the optimized leaf mass fractions (M\textsubscript{0}) represents an underestimation of realized leaf \textit{C} allocation.
-Increases of 50~\% in non-leaf tissue respiration (M\textsubscript{3}) improved biomass estimates slightly but still overestimated mass \textit{C} by an average of 46$\pm$9.3~\% in seedlings with soil volume restriction (Fig.~\ref{fig:figureSI1}b).
-It was further determined that non-tissue respiration rates in modeled seedlings would need to increase by ca.~250~\% to account for this entire pool of \textit{C}.
-
-\section*{Discussion}
-
-As issues still remain regarding how source-sink coordination affects growth of woody species, this study utilized a simple but novel field design to manipulate belowground sink limitations in order to physically restrict \textit{Eucalyptus tereticornis} seedling production.
-After successfully created a belowground sink limitation we then addressed questions regarding the coordination of \textit{A} and growth by complementing empirical results with modelling approaches.
-We found that reductions in leaf \textit{A} rates were not sufficient to explain observed reductions in total plant biomass production after 120 days.
-We thus encourage the utilization of mass balance approaches and provide direction for future studies when testing factors that control of plant growth under environmental change.
-
-\subsubsection*{\textit{Soil volume restriction and reduced seedling growth}}
-
-As soon as seedlings became established both height and diameter growth were negatively affected as a function of available soil volume compared to free seedlings, providing immediate evidence in support of H1.
-These growth reductions were expected, as the impedance of root growth can cause reductions overall plant growth and activity \citep{mcconnaughay1991physical, young1997mechanical}.
-It has been shown that roots undergoing difficult conditions may send inhibitory signals to the shoots that affect stomatal conductance, cell expansion, cell division and the rate of leaf appearance \citep{passioura2002soil}.
-This was evident in the large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
-As growth was so strongly affected in containers we then asked if biomass partitioning strategies manifested through time that could explain the observed differences in seedling growth.	As mass partitioning is likely controlled by source and sinks strength of all organs \citep{poorter2012biomass} it was important to determine what tissue components were most affected in order to evaluate and then model the biomass response accurately.
-
-As changes to mass allocation of leaves, stems or roots occurs at the expense of other structures \citep{mccarthy2007consistency} it was necessary to first distinguish if belowground sink limitation affected growth beyond ontogenetic constraints.
-In this study, there were no significant changes in root, leaf, or stem mass fractions to reduced soil volume compared to free seedlings, outside of ontogenetic drift.
-This is significant as shifts in allocation, beyond ontogeny, have been noted specifically for nutrient limitation compared to light, CO\textsubscript{2}, and water \citep[references therein]{mcconnaughay1999biomass}.
-Additionally, this provides evidence against the preservation of functional balance through optimal foraging, a common explanation for changes in plant growth under environmental stress.
-In response to root restriction these seedlings might alter biomass allocation to ephemeral tissues, including fine roots or leaves, in order to meet the resource requirements for \textit{A}.
-Fine root mass to leaf mass ratio was instead conserved, regardless of plant size or treatment, suggesting an active biomass partitioning strategy to optimize resource gain did not occur.
-
-Alternatively, physical restriction of root proliferation could have impacted root development or morphology prior to shifts in mass partitioning.
-Plants in containers have been shown to have different root morphology to field grown plants as roots essentially compete with themselves for nutrients \citep{nesmith1998effect}, but data for woody species is still limited.For example, lateral root development is affected by inanimate obstacles and avoiding growth towards container walls could improve the efficiency of resource allocation \citep{falik2005root}.
-Also, the sensitivity of roots to their own exudates near obstructions may be used to adjust growth before stressful conditions occur \citep{semchenko2008foraging}.
-As a result, seedlings in small container sizes might alter fine root morphology, by increasing fine root length, to increase resource uptake potential.
-As neither SRL nor partitioning between fine and coarse root mass fractions differed across treatments, this provides further evidence against any functional plant response beyond developmental isometric growth.
-
-\subsubsection*{\textit{Linkage between belowground sink limitation and photosynthesis}}
-
-As plants must balance allocation to leaves, stems and roots in a way that matches the physiological activities performed by these organs \citep{poorter2012biomass}, the observed reductions in seedling growth could instead have resulted from \textit{C} source-sink imbalances.
-For example, the consequences of either stomatal closure or soil resource depletion to the sensitivity of these source-sink activities could lead to reductions in \textit{A}, the central driver of plant \textit{C} gain and growth.
-Contrary to what was hypothesized, just as height reductions were immediately evident with new growth, so were leaf \textit{A} rates on newly formed leaves.
-As physical restriction to growth was expected to precede effects on leaf physiology this initially suggests a tight link between reduced \textit{A} and seedling growth.
-It was therefore necessary to distinguish if source or sink limitation resulted in the reduction of \textit{A}\textsubscript{sat} and \textit{A}\textsubscript{max}  throughout the experiment.
-
-With high rates of \textit{g}\textsubscript{s}, non-limiting leaf water potential and consistent leaf {\textdelta}\textsuperscript{13}C across soil volume treatments there was little evidence of source limitation to \textit{A} in this study.
-This finding is consistent with other container size studies, with source manipulation via elevated CO\textsubscript{2}, where inhibition of CO\textsubscript{2} enrichment often results from sink limitation on \textit{A}\textsubscript{max} \citep{arp1991effects, robbins1988effect}.
-For example, reduced \textit{A}\textsubscript{max} in cotton seedlings grown at elevated CO\textsubscript{2} was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased \textit{g}\textsubscript{s} \citep{thomas1991root}.
-Our results lend support to more general conclusions that neither growth \citep{korner2003carbon} nor \textit{A} \citep{millard2007environmental} of woody species is directly \textit{C} limited.
-Instead it was likely that reductions in \textit{A} occurred from the impact of a limited soil resource pool on belowground sink strength.
-
-As both belowground space and resources were finite in containers, the limited ability of these seedlings to increase the capacity of the belowground \textit{C} sink was hypothesized to result in the buildup of \textit{C} assimilate in the leaves.
-This buildup, occurring via accumulation of leaf starch, was present as a function of decreasing container size throughout the study.
-As a result, \textit{A}\textsubscript{max} for all seedlings was highly correlated to leaf starch content across all measurement campaigns.
-The accumulation of leaf starch was accompanied by significant decreases \textit{J}\textsubscript{max} and \textit{Vc}\textsubscript{max}, both immediately evident during the first gas exchange campaign.
-Together this provides strong evidence that down regulation of \textit{A} likely occurred from reduced belowground \textit{C} sink strength in these seedlings.
-This down regulation was likely apparent throughout the entire experiment as leaf TNC content remained high in seedlings with soil volume restriction and the effects on \textit{J}\textsubscript{max} and \textit{Vc}\textsubscript{max} were again noted at the end of the experiment.
-
-As limited understanding between source-sink feedbacks to photosynthetic down regulation still exists in woody species, this container size approach also allowed us to directly relate an induced belowground sink limitation to impacts on leaf physiology.
-Evidence for sink limitation of \textit{A} was evident in the stark contrast in leaf \textit{N} between free seedlings and seedlings in containers, combined with the strong correlation between leaf \textit{N} and \textit{A}\textsubscript{max}.
-Leaf \textit{N} was also reduced compared to free seedlings when excess accumulation of leaf starch was present.
-Although the soil \textit{N} pool declined evenly across all treatments leaf \textit{N} was lowest in the smallest soil volume, suggesting that sink limitation was the greatest in these containers.
-This makes sense as small containers may reduce \textit{N} uptake, either from physical root restriction or decreased supply, which affects growth, Rubisco limitation, sugar metabolism, and carbohydrate partitioning between source and sink tissues (Stitt, 1991; Hermans et al., 2006).
-Mycorrhizal colonization could have also been significantly affected by the ‘container effect’.
-Whether unrestricted mycorrhizal recruitment instead facilitated an increase in leaf \textit{N} uptake to leaves in free seedlings is unknown.
-Regardless, the belowground sink strength of seedlings with soil volume treatments was greatly reduced and appears to be strongly linked with negative feedbacks to \textit{A}.
-
-\subsubsection*{\textit{Modeling the coordination of photosynthesis and growth with carbon mass balance}}
-
-If feedbacks between sink limitation and leaf \textit{A} controlled seedling growth the growth model was expected to find agreement between simulated and observed seedling biomass.
-A linkage between sink limitation and \textit{A}, however, does not necessarily imply the same level of coordination between reduced \textit{A} and growth.
-It was therefore necessary to test, using a mass balance approach, if the measured reductions in \textit{A} could be used to predict the patterns in seedling growth after 120~days.
-Constraining the initial model run (M\textsubscript{1}) by an optimized leaf mass fraction allowed us to test if feedbacks from reduced \textit{A} could predict seedling growth with soil volume restriction.
-The result was a difference in the fate of assimilated \textit{C}, with a larger fraction of available \textit{C} ending up in final biomass of modeled seedlings.
-Consequently, this also revealed a pool of missing \textit{C} in measured seedlings unaccounted for with mass balance.
-This finding lends strong evidence that \textit{A} and growth may not be entirely synced under environmental change, an important distinction often missed in studies that manipulate source and sink activity.
-Thus, without \textit{C} mass balance approaches inferences to the nature of mechanisms controlling growth under environmental stress should only be speculative.
-As a result, we utilized the flexibility of the model to test potential sources of \textit{C} loss not explicitly measured, including changes to leaf \textit{C} allocation or non-leaf tissue respiration.
-Through this approach, similar to \citep{lohier2014explaining}, we manipulated processes contributing to seedling \textit{C} mass balance and quantitatively tested their respective influences on model predictions.
-
-Altering the leaf mass fraction from that of the optimized free seedling control (M\textsubscript{2}) improved model biomass predictions and provided insight into how sink limitation may impact leaf \textit{C} allocation beyond that of \textit{A}.
-As this was a field study it was impossible to quantify all impacts to leaf \textit{C} allocation which could have occurred.
-Model predictions, however, provided evidence for how the feedback between rates of photosynthesis and \textit{C} allocated to leaves can severely impact seedling growth.
-The observed sub-optimal decrease in leaf mass fraction with increasing soil volume restriction has several possible explanations.
-First, TNC accumulation due to sink limitation can lead to accelerated leaf senescence \citep{paul2001sink}.
-Alternatively, as rates of \textit{A} were not different between soil volume treatments these seedlings could have reduced leaf production to maintain laws of stoichiometry (leaf \textit{C}:\textit{N} ratio) associated with reduced belowground \textit{C} sink strength and measured declines in leaf N.
-Thus, future empirical studies and modelling efforts should focus on the feedbacks from sink activity not only on leaf A rates but also on the fate of \textit{C} allocated to leaves.
-It is the interaction between these two components that will drive patterns of total canopy \textit{C} gain available for growth for the rest of the plant.
-
-Increases in non-leaf respiration rates  (M\textsubscript{3}) improved biomass predictions but to a lesser extent than changes to leaf \textit{C} allocation.
-This finding is still significant as it justifies the need to strengthen our knowledge of the effects of environmental change on respiration of different tissues components above and belowground.
-As \textit{C} balance is a delicate equilibrium between fluxes of photosynthesis and respiration, partial accounting of \textit{C} dynamics can easily lead to erroneous conclusions (Valentini et al.
-2000).
-For example, there is strong evidence for coupling between photosynthesis and respiration yet \textit{C} use efficiency is not always constant \citep{cannell2000modelling}.
-In addition, our understanding of how changes in sink activity affect this coupling or regulation of respiration across different tissues components in woody species is still poor.
-Thus, it is likely inappropriate to assume that respiration is an constant fraction of gross primary production in models \citep{delucia2007forest}.
-We reveal that any significant impact to tissue respiration will likely impact the synchronization of \textit{A} and growth and should be accounted for in  future empirical studies and modelling efforts that predict plant growth under environmental change.
-
-\subsubsection*{\textit{Conclusions}}
-
-Although there is renewed debate of the coordination of \textit{A} and growth this is not a new issue.
-It has long been know that conditions which affect the photosynthetic process affect growth but there is also an interrelationship between growth and \textit{A} \citep{sweet1966role}.
-We found that the fate of assimilated \textit{C}, available for plant growth, was different between free seedlings and seedlings in containers.
-This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles but how these results actually reflect field-grown plants has seldom been studied.
-Utilizing a mass-balance approach with a simple production model revealed that a combination of different mechanisms must be at play in driving this observed seedling biomass response to sink manipulation.
-However, which of the mechanisms and the role they have in determining growth response will undoubtedly shift across different experimental manipulations and plant species.
-We argue that attempts to quantify or at least predict the fate of assimilated \textit{C} into known pools of growth, storage and \textit{C} loss are necessary before definitive resolution of the controls of plant growth are to be found.
-The widespread implications of this type of approach, allowing the flexibility to account for multiple potential drivers of \textit{C} allocation and plant growth, can help answer questions about the fate of \textit{C} in plants undergoing environmental change.
-
-%--------------------------------------------------------------------------------------------%
-\section*{Tables}
-% Load xtable for printing tables.
 <<echo=FALSE, message=FALSE, warning=FALSE>>=
 library(xtable)
-pve_data <- read.csv("table/pve_table1.csv")
+pve_data <- read.csv("/master_scripts/pve_table1.csv")
 
@@
 
-phys_data <- read.csv("table/pve_table2.csv")
+phys_data <- read.csv("/master_scripts/pve_table2.csv")
 colnames(phys_data) <- c("Volume~(L)", 
@@
 
-%data.df$taxa <- paste("\\emph{",taxa,"}", sep="")
+\clearpage
 
@@
 
-%--------------------------------------------------------------------------------------------%
 \clearpage
-\section*{Figures}
-
-%air variables figure
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{airvars.pdf}
-    \caption{Daily maximum and minimum temperature (a), cumulative daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.}
-    \label{fig:figure1}
-\end{figure}
-
-%allometry figure
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{allometry.pdf}
-    \caption{Soil volume treatment means~$\pm$ standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of \textit{Eucalyptus tereticornis} seedlings across the experiment duration in 2013.}
-    \label{fig:figure2}
-\end{figure}
-
-%partitioning figure
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{massfractions.pdf}
-    \caption{Soil volume treatment means of mass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with $\pm$ standard error (c).
-For (b) lines represent standardized major axis fitting of the log transformed allometric relationships of leaf mass fraction by treatment.
-For (c) the dashed line is the 1:1 relationship and the solid line represents the significant linear model fit (\textit{r}\textsuperscript{2}~=~0.81).}
-    \label{fig:figure3}
-\end{figure}
-
-%asat figure
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{Asat.pdf}
-    \caption{Soil volume treatment means~$\pm$ standard error, across all measurement campaigns (n=6), of light saturated rates of photosynthesis at 25$\degree$C.
-Different letters represent significant differences between treatments.}
-    \label{fig:figure4}
-\end{figure}
-
-%photochem figure
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{A_leafchem.pdf}
-    \caption{Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).
-Colors represent bins levels (n=5) of both leaf starch and nitrogen grouped from low to high .
-Lines represents predictions, for each bin level, from the linear mixed effects model equation of \textit{A}\textsubscript{max} as a function of starch and nitrogen.
-The marginal \textit{r}\textsuperscript{2} (fixed effects only) was 0.37 and the conditional \textit{r}\textsuperscript{2} (fixed and random effects) was 0.48 for the complete model.}
-    \label{fig:figure5}
-\end{figure}
-
-%model base figure
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{massmodel_totalC.pdf}
-    \caption{Total carbon mass for harvested and modeled seedlings versus predicted total carbon gain after 120 days (a) and  reductions in final seedling carbon mass, both modeled and observed, as a function of the reduction in leaf photosynthesis across treatments (b).
-For (a) the dashed 1:1 identifies the difference between net total leaf carbon gain and gross seedling production.
-For (b) both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.}
-    \label{fig:figure6}
-\end{figure}
-
-%--------------------------------------------------------------------------------------------%
-\clearpage
-\section{Supporting Information Figures}
-% Supporting information. Make sure Figures continue with Fig S1 etc.
-
-\renewcommand\thefigure{S\arabic{figure}}    
-\setcounter{figure}{0}
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{massmodel_resp.pdf}
-    \caption{Sensitivity testing of seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50~\% (b).
-Open and filled symbols represent default model and harvest values, while shaded symbols represent model sensitivity to each scenario by soil volume treatment.
-Both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.}
-    \label{fig:figureSI1}
-\end{figure}
 
@@
 
-%--------------------------------------------------------------------------------------------%
-\clearpage
-\bibliography{pve_cites}
-
-%--------------------------------------------------------------------------------------------%
 \end{document}

### 2015-07-20 tables_latex/pve_manuscript.tex
added tables to manuscript (jpg)

--- 2015-07-20 tables_latex/pve_manuscript.Rnw
@@
 
+\usepackage{Sweave}
 \begin{document}
-
-\linenumbers
-
-\title{Effects of below-ground space limitation on performance of Eucalyptus seedlings:  Does photosynthesis really control growth?}
-
-\author[1,3]{Courtney E. Campany}
-\author[2]{Belinda E. Medlyn}
-\author[1]{Remko A. Duursma}
-
-\affil[1]{Hawkesbury Institute for the Environment, University of Western Sydney, Richmond, NSW 2753, Australia}
-\affil[2]{Department of Biological Sciences, Macquarie University, North Ryde, NSW 2109, Australia}
-\affil[3]{Corresponding author (c.campany@uws.edu.au)}
-
-\renewcommand\Authands{ and }
-\maketitle
+\input{pve_manuscript-concordance}
 
 %--------------------------------------------------------------------------------------------%
-
-<<preload, echo=FALSE>>=
-library(knitr)
-opts_chunk$set(echo=FALSE)
-@
-
-%--------------------------------------------------------------------------------------------%
-
-\section*{Abstract}
-
-Interpreting limitations to plant growth requires understanding of the balance between carbon (\textit{C}) source and sink activity in order to assess \textit{C} allocation and biomass partitioning.
-This study used manipulations of soil volume to test how growth is coupled to physiology, allocation, and sink activity in \textit{Eucalyptus tereticornis} seedlings.
-We grew seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown seedlings (free).
-Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
-It was hypothesized that soil volume effect would be largest in the smallest containers, resulting in physical constraints to growth independently of photosynthesis (\textit{A}).
-Photosynthesis would then become sink-limited, resulting in the build-up of leaf nonstructural carbohydrates eventually leading to photosynthetic down regulation.
-We observed a negative container effect on aboveground growth soon after the experiment started.
-Although growth was consistently different across soil volumes mass, partitioning to leaves, stems, roots was conserved after 120 days.
-Photosynthetic capacity was also significantly reduced in containers, and was related to both leaf nitrogen content and starch accumulation.
-We developed a seedling growth model that utilized leaf \textit{A} rates to allocate daily \textit{C} uptake towards mass growth of stems, leaves and roots.
-We then asked whether the observed reductions in \textit{A} explained the observed differences in seedling biomass.
-We found that although belowground sink limitation resulted in the down regulation of \textit{A}, these reductions were not significant enough to explain observed growth responses.
-Thus, as photosynthesis and growth were not coordinated an excess pool of non-biomass \textit{C} resulted in seedlings with soil volume restriction.
-This research highlights the need to further utilize mass balance approaches when evaluating plant \textit{C} allocation and confirms that \textit{A} and growth are not always directly related.
-
-\section*{Key Words}
-
-photosynthesis, growth, sink regulation, carbon allocation, soil volume
-
-\section*{Introduction}
-
-Understanding plant growth requires knowledge of the mass balance that must be achieved between \textit{C} uptake and subsequent allocation to growth, storage, and respiration.
-It is commonly assumed plant growth is limited by \textit{C} availability, yet it has long been demonstrated that correlations between \textit{A} and growth are weak or seldom present.
-\citet{korner2013growth} argues that growth instead controls \textit{A}, as it is the norm for sink activity to feedback on source activity.
-This is supported by evidence that growth of plants under environmental stress is not limited by the supply of photoassimilates \citep{palacio2014does}.
-As woody plants have highly integrated systems of competing carbohydrate sinks \citep{kozlowski1992carbohydrate}, growth should principally depend on the transport of these photoassimilates between different tissue and organ sinks.
-Despite a wealth of studies, however, large uncertainties still remain regarding the coordination of \textit{C} supply, via \textit{A}, and growth of woody species.
-
-In woody species, how \textit{A} controls growth has been studied with manipulations of \textit{C} source activity.
-Examples included elevated CO\textsubscript{2} experiments, for example FACE (reviewed in  \citet{ainsworth2005have}, and partial defoliation experiments.
-Elevated CO\textsubscript{2} has been shown to increase \textit{A} rates \citep{drake1997more,ainsworth2007response} and across four FACE experiments this resulted in a conserved increase in forest production \citep{norby2005forest}.
-Evidence from elevated CO\textsubscript{2} experiments, however, also reveals that the growth response tends to be much smaller than the photosynthetic enhancement \citep{kirschbaum2011does}.
-In defoliation experiments, compensatory increases in \textit{A} are commonly shown yet are attributed to variable mechanisms, including reduction in end product inhibition \citep{iglesias2002regulation,zhou2003changes,handa2005test}, enhanced biochemical activity \citep{ovaska1993b,layne1995end}, increased stomatal conductance \citep{layne1995end}, leaf nutrient status \citep{turnbull2007increased}, and regulatory sugar signaling \citep{eyles2013whole}.
-However, increases in \textit{A} did not always produce increased growth due to reductions in meristem sink strength (Palacio et al.
-2012), \textit{C} limitation to mycorrhizal colonization (Markkola et al.
-2004), or an overall decrease in whole plant \textit{C} gain \citep{ovaska1993a}.
-These manipulations of \textit{C} source activity expose unresolved issues with how changes in \textit{A} do not always infer similar responses in growth.
-
-Alternatively, manipulation of plant tissue carbon sinks is often used to investigate the correlation of photosynthesis and growth.
-Tissue sink activity can restrict biomass production when limited by environmental or developmental constraints \citep{korner2003carbon}.
-This is because metabolic signaling networks, relaying information on \textit{C} and nitrogen (\textit{N}) status of different tissues, can down regulate photosynthetic activity \citep{paul2001sink}.
-Whether this down regulation, via sink inhibition, is evident in woody species has been tested through fruit removal, girdling, and low temperatures.
-In these studies, down regulation of \textit{A} was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength \citep{iglesias2002regulation,hoch2002altitudinal,urban2007girdling, haouari2013fruit}.
-However, reductions in \textit{A} were also attributed to biochemical limitations prior to carbohydrate accumulation \citep{nebauer2011photosynthesis}, irreversible photo-oxidative damage \citep{duan2008photosynthetic}, and stomatal limitation \citep{li2005photosynthesis}.
-These mixed results are not surprising as we still know little about the pathways in which plants achieve balance between assimilation, storage, and growth across temporal scales \citep{smith2007coordination}.
-As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to large annual fruiting sinks, they tell us little about source-sink coordination in ‘normal’ field-grown woody species.
-
-An alternative experimental approach is to lower belowground \textit{C} sink strength in tree seedlings by manipulating rooting volume, by varying the container size.
-The advantage of this approach is it allows a large range of manipulations, can be easily compared to naturally planted seedlings and mimics natural conditions as seedlings compete for space or reach bedrock.
-Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, \textit{A}, water relations, nutrient uptake and respiration \citep[and references therein]{nesmith1998effect}.
-Inadequate rooting volume may decrease carbon sink strength by progressively restricting root growth \citep{thomas1991root}.
-Container size studies frequently have photosynthetic down-regulation, likely as a result of sink limitation \citep{arp1991effects, mcconnaughay1991physical, gunderson1994photosynthetic, sage1994acclimation, maina2002intra, ronchi2006growth}.
-A meta-analysis by \citet{poorter2012pot} concluded that \textit{A} is the process likely to be the strongest affected by pot size and may best explain the observed effect on biomass seen in the large number of studies where containers are used.
-This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower \textit{C} exchange and assimilate export rates \citep{robbins1988effect}.
-However, evidence in support for a trade-off between \textit{C} storage and growth in trees is, to date, inconclusive \citep{palacio2014does}.
-Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test how growth and \textit{A} are coordinated.
-
-Our lack of knowledge regarding the allocation of \textit{C} in woody species is still a major obstable in understanding the cooridatnation between  \textit{A} and growth.
-Understanding the fate of assimilated \textit{C} is crucial when source or sink manipulations do not directly lead to equivalent changes in growth.
-As programmed plasticity in \textit{C} allocation naturally occur as plants growth and develop, this must be accounted for when evaluating induced variation in growth \citep{wright2002interpreting}.
-Thus, when \textit{C} allocation is altered by a treatment, it should be shown whether these allocation patterns differ from common sized untreated plants \citep{reich2002root, poorter2012biomass}.
-Only then can we test if functional balance preservation or optimal foraging occurs from changes in \textit{C} uptake.
-For example, seedlings in containers may shift allocation to leaves if root restriction occurs or alter fine root morphology to increase nutrient uptake.
-In woody species, shifts in allometric relationships of leaves, stems and roots can reveal if growth is ontogenetically constrained or actively adjusted when \textit{A} is affected.
-This then allows additional pools of \textit{C}, such as root exudation or changes in tissue respiration, to be accounted for and evaluated.
-
-This study utilizes a novel field design to investigate the coordination between growth and \textit{A} in \textit{Eucalyptus tereticornis} Sm.~seedlings, by manipulating container size and thus rooting volume.
-Seedlings were maintained under well watered conditions in order to evaluate only the effect of restricted soil volume and the limited nutrient resource pool.
-We used freely-rooted seedlings as a control for the container size treatments.
-Empirical results were combined with a simple plant growth model to simulate seedling growth with a \textit{C} mass balance approach, which was then compared to observed harvested seedling mass.
-The model used whole-plant \textit{C} gain, scaled from instantaneous rates of leaf \textit{A}, to quantify seedling production over 120 days.
-
-1).
-The manipulations of container size were hypothesized to induce a belowground sink limitation in these seedlings which was expected to be largest in the smallest containers, resulting in physical constraints to growth independently of \textit{A}.
-
-2).
-Reducing soil volume was then expected to induce negative effects on leaf physiology compared to free seedlings (‘container effect’).
-This accumulation of leaf nonstructural carbohydrates was expected to trigger photosynthetic down regulation as a function of soil volume and create further negative feedbacks to growth through time.
-
-3). Last, the growth model was expected to find agreement between simulated and observed seedling mass, through direct correlation of the effects of soil volume on rates of leaf \textit{A}.
-
-\section*{Methods}
-
-\subsubsection*{\textit{Experimental Design}}
-
-This experiment was located on the Hawkesbury Forest Experiment site in Richmond, NSW, Australia.
-Plots were located in open cover with a site history that consists of a paddock that was converted from native pasture grasses.
-Top soils at this site, used for the study, are an alluvial formation of low-fertility sandy loam soils (380 and 108~mg~kg\textsuperscript{-1} total \textit{N} and phosphorus respectively) with low organic matter (0.7~\%) and low water holding capacity.
-At this site a soil hard layer exists at $\sim$1.0~m with a transition to heavy clay soils.
-The climate for the region is classified as sub-humid temperate.
-
-\textit{Eucalyptus tereticornis} seedlings, 20~weeks old and approximately 40~cm tall in tube stock, were chosen from a single local Cumberland plain cohort.
-Previous experiments have confirmed that species with tap roots (similar to \textit{E.
-tereticornis}) use the center of the container as the medium for thick roots leaving the periphery of the soil as the most active sites for fine root proliferation \citep{biran1980a,biran1980b}.
-This is generally hypothesized to be a different response than seedlings with no taproot.
-By using a species with tap root growth and manipulations of container length rather than width, it is believed that a more realistic test of inhibition of growth through constrained soil volume would be achieved.
-Six seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.
-
-Six container volumes were used ranging from 5~l to 35~l, with a 22.5~cm diameter, and lengths ranging from 15 to 100~cm.
-Containers were constructed of PVC pipe and were filled with local top soil (described above).
-Soil in each container was packed to achieve a target soil bulk density of 1.7~g~m\textsuperscript{-3}.
-A Imidacloprid (BAYER CropScience) insecticide tablet was planted 5 cm below the roots of each seedling.
-Containers were planted flush with the soil surface inside metal sleeves, designed to minimize excess air space between the container and outside soil while also allowing for container removal.
-This allowed for soil temperatures in containers to reflect conditions of naturally sown (free) seedlings.
-Each experimental block (n=7) contained a complete replicate set of container volumes as well as one free seedling, with 1 m\textsuperscript{2} spacing.
-For each free seedling, used as the control, a 1~m\textsuperscript{2} subplot was excavated to 0.5~m and replaced with the same soil used in each container.
-A border of root exclusion material was buried 0.25~m deep and extended 0.25~m above the ground surface around each subplot to exclude local vegetation.
-
-Plants were watered weekly or when needed, accounting for natural precipitation, to maintain soil moisture at field capacity (13-15~\%).
-Drain systems were built into each pot to prevent pooling of water in containers before root expansion, from reduced root uptake, or from large rainfall events.
-These conditions could lead to an anaerobic environment around the root that could hinder the uptake of water through reduced root conductance \citep{poorter2009causes}, an undesired experimental artifact.
-A collection compartment in the bottom of containers, containing gravel covered by root exclusion mesh, was used to collect excess water for 20, 25, and 35~l containers.
-Plastic tubing (6~mm diameter) was inset into the gravel layer and extended through the top of the container.
-A lysimeter pump was then used to suction excess water, through the tubing, as needed .
-As small containers (5, 10, and 15~l) have a larger irradiation effect a simple bottom plug was used to drain excess water from the gravel compartment.
-
-\subsubsection*{\textit{Growth and morphology metrics}}
-
-Seedlings were planted on January 21\textsuperscript{st} 2013 and stem height, diameter at 15~cm and leaf count were measured weekly thereafter.
-Once the growth rate of individual plants had significantly declined a full biomass harvest was completed (May 21\textsuperscript{st} 2013).
-Dry mass of leaves, stems, roots and cumulative leaf area (LI-3100C Area Meter; LI-COR, Lincoln, NE, USA) was measured for each seedling.
-Mean individual leaf area for each harvested seedling was calculated by dividing cumulative leaf area by total leaf count of only fully expanded leaves.
-This value was then used to interpolate cumulative leaf area through time with weekly leaf counts.
-Root mass was collected by passing soil from each container through a 1~mm sieve, washing, separating into fine and coarse roots (\textless2~mm and \textgreater2~mm diameter, respectively) and then drying to a constant mass.
-Roots from the free seedlings were collected by excavating each 1~m\textsuperscript{2} subplot to 0.5~m depth.
-25~g fresh weight subsamples of washed fine roots were analyzed, using WhinoRhizo software (Regent Instruments Inc.), for specific root length (SRL, cm~m\textsuperscript{-1}).
-
-\subsubsection*{\textit{Photosynthetic parameters}}
-
-Leaf gas exchange measurements were performed bi-weekly at saturating light (\textit{A}\textsubscript{sat}) and saturating light and [CO\textsubscript{2}] (\textit{A}\textsubscript{max}) on new fully expanded leaves.
-Measurements were initiated only after sufficient new leaf growth occurred (March 17\textsuperscript{th}, 2013), approximately 6 weeks following planting, and continued until the biomass harvest.
-Leaf level gas exchange was measured with a standard leaf chamber equipped with blue-red light emitting diodes using a portable gas exchange system (LI-6400, LI-COR, Lincoln, NE, USA).
-\textit{A}\textsubscript{sat} measurements were made at PPFD of 1800~{\textmugreek}mol~m\textsuperscript{-1}~s\textsuperscript{-1} and [CO\textsubscript{2}] of 400~{\textmugreek}l~l\textsuperscript{-1} and \textit{A}\textsubscript{max} with [CO\textsubscript{2}] of 1600~{\textmugreek}l~l\textsuperscript{-1} and PPFD of 1800~{\textmugreek}mol~photons~m\textsuperscript{-1}~s\textsuperscript{-1}.
-This choice of light level to achieve light saturation is consistent with other studies on \textit{Eucalyptus} species \citep{kallarackal1997ecophysiological,pinkard1998photosynthetic,crous2013photosynthesis,drake2014capacity}.
-These measurements were conducted during midday (10:00-14:00~h) with leaf temperature maintained at 25$\degree$C.
-After leaves acclimated to the chamber environment, net CO\textsubscript{2} assimilation rate and stomatal conductance (\textit{g}\textsubscript{s}) were logged 5 times for both \textit{A}\textsubscript{sat} and \textit{A}\textsubscript{max}.
-Photosynthetic CO\textsubscript{2} response (AC\textsubscript{i}) curves were also developed at 25$\degree$C on a random subset of each container size (n=3) after new leaves were first produced and immediately prior to the final harvest (May 23\textsuperscript{rd} 2013).
-Each AC\textsubscript{i} curve began at the reference [CO\textsubscript{2}] of 400~{\textmugreek}l~l\textsuperscript{-1} and then consisted of 12 additional steps from [CO\textsubscript{2}] of 50 to 1800~{\textmugreek}l~l\textsuperscript{-1}at 25$\degree$C at saturating light (above).
-From these curves the photosynthetic parameters, \textit{J}\textsubscript{max} and \textit{Vc}\textsubscript{max}, were quantified using the biochemical model of \citet{farquhar1980biochemical}.
-Leaf dark respiration rates (\textit{R}\textsubscript{d}) was measured on each seedling during the same dates as AC\textsubscript{i} curves using detached leaves inside a conifer chamber attached to the Licor 6400 at least 1 hour after sundown.
-Measurements were taken at a reference [CO\textsubscript{2}] of 400~{\textmugreek}l~l\textsuperscript{-1} while leaf temperature was maintained at current ambient conditions.
-Reported values of \textit{R}\textsubscript{d} are standardized rates at 25$\degree$C using a Q10 value (1.86) developed for these seedlings in a separate experiment (Drake et al.
-unpublished).
-Leaf area and dry mass were recorded for each leaf during gas exchange campaigns.
-
-\subsubsection*{\textit{Leaf water potential}}
-
-Predawn ($\Psi\textsubscript{pd}$) and midday ($\Psi\textsubscript{l}$) leaf water potentials were measured for each seedling using a PMS 1505D pressure chamber (PMS Instruments, Albany, OR, USA) on fully expanded leaves during the same time period as AC\textsubscript{i} and \textit{R}\textsubscript{d}.
-Leaves were detached and immediately stored inside foil covered bags before water potential measurements were performed.
-$\Psi\textsubscript{pd}$ was measured before sunrise and $\Psi\textsubscript{l}$ at midday 13:00-14:30~h.
-These measurements were used as a measure of static water stress on the seedlings \citep{sellin1999does}, and to ensure that the bulk soil water availability was high enough for plants as they became larger and roots filled the soil volume.
-
-\subsubsection*{\textit{Leaf, root and soil chemistry}}
-
-Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of \textit{N} content, {\textdelta}\textsuperscript{13}C, and total non-structural carbohydrates (TNC).
-Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis.
-\textit{N} concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of \textit{N}\textsubscript{2} and CO\textsubscript{2}).
-The percentage of \textit{N} in the sample was calculated by comparison with known standards.
-Leaf {\textdelta}\textsuperscript{13}C was analyzed  with an Delta V Advantage coupled to a Flash HT and Conflo IV isotope ratio mass spectrometer.
-Leaf samples were flash combusted at 1000$\degree$C to convert to to CO\textsubscript{2}, feed to the mass spectrometer and isotopic signatures are reported relative to the VPDP scale.
-Leaf TNC concentration was analyzed using a total starch assay kit (Megazyme International 303 Ireland Ltd., Wicklow, Ireland) and includes the starch (mg~g\textsuperscript{-1}) and soluble sugar (mg~g\textsuperscript{-1}) concentrations.
-Starch was quantified using a thermostable $\alpha$-amylase and amyloglucosidase assay \citep{McCleary_starch} and soluble sugars were determined following the anthrone method \citep{ebell1969variation}.
-Complete methods of the TNC assay are described in \citep{mitchell2013drought}.
-Specific leaf area (SLA, m\textsuperscript{2}~kg\textsuperscript{-1}), for leaves sampled during gas exchange campaigns, was then calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass.
-
-\subsubsection*{\textit{Seedling growth model}}
-
-We developed a simple seedling growth model that utilized leaf \textit{A} rates to allocate daily \textit{C} assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
-The model begins with mean initial tissue component biomass (leaf\textsubscript{i}, stem\textsubscript{i} and root\textsubscript{i}) and a starting leaf area (LA\textsubscript{i}) measured prior to planting.
-The initial biomass of roots was divided evenly between fine and coarse roots.
-The daily net biomass production of seedlings (P\textsubscript{i}) is then given by
-\begin{equation} P\textsubscript{i}=L~(C\textsubscript{day,i}~\sigma\textsubscript{s}~\epsilon\textsubscript{c}\textsuperscript{-1})-R
-\label{eq:prod}
-\end{equation}
-where L is standing cumulative leaf area, C\textsubscript{day,i} is the predicted daily carbon assimilation, $\sigma\textsubscript{s}$ is a self shading parameter, \textepsilon\textsubscript{c} is a biomass conversion efficiency parameter and R is the total respiration of all tissue components.
-Total respiration was calculated as
-\begin{equation} R=\Sigma(R\textsubscript{c}~M\textsubscript{c})
-\label{eq:resp}
-\end{equation}
-where R\textsubscript{c} is tissue respiration of fine roots, coarse roots or stems on a mass basis and M\textsubscript{c} is the standing biomass of each component.
-R\textsubscript{leaf} is represented in the calculation of C\textsubscript{day} (described below).
-The change in individual component biomass (M\textsubscript{c}), here solved on a daily time step, is given by
-\begin{equation} \frac{dM\textsubscript{c}}{dt}=A\textsubscript{c}~P\textsubscript{i}-(\Lambda\textsubscript{c}~M\textsubscript{c})
-\label{eq:mass}
-\end{equation}
-where A\textsubscript{c} is the component specific biomass partitioning  to whole plant biomass (\%) and $\Lambda\textsubscript{c}$ is component specific turnover rate.
-Due to the duration of the experiment $\Lambda\textsubscript{stem}$ was assumed to equal 0.
-Total seedling biomass, per time step, was then equal to the sum of all biomass components; leaves, stems, fine roots and coarse roots.
-
-\textit{C}\textsubscript{day} was predicted by fitting a coupled photosynthesis - stomatal conductance model \citep{farquhar1980biochemical,medlyn2011reconciling} in the 'plantecophys' package in R \citep{Duursma2014} to the mean photosynthetic parameters (R\textsubscript{d}, J\textsubscript{max}, V\textsubscript{cmax}, and g\textsubscript{1}) for each treatment and meteorological data from an onsite weather station.
-Examples of the photosynthesis model are described in \citet{medlyn2002temperature} and the approach of the coupled leaf gas exchange model are described in \citet{duursma2014peaked}.
-The g\textsubscript{1} parameter was generated by fitting observed \textit{g}\textsubscript{s} values into the optimal stomatal conductance model from \citep{medlyn2012reconciling}.
-Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15~m intervals, leaf \textit{A} rates ({\textmugreek}mol~CO\textsubscript{2}~m\textsuperscript{-2}~s\textsuperscript{-1}) were then predicted for each soil volume treatment.
-Rates were assumed to be representative of the entire 15~min meteorological interval.
-\textit{C}\textsubscript{day} was calculated by converting predicted rates to mass \textit{C} gain over 15~min (g~m\textsuperscript{-2}) and then summed for 24~h.
-This resulted in 120 unique values of \textit{C}\textsubscript{day} for each soil volume treatment, one value for each day of the experiment.
-Thus, each daily time step for model runs included a value of \textit{C}\textsubscript{day} that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
-
-It was further necessary to calculate a self-shading parameter ($\sigma\textsubscript{s}$) when scaling leaf \textit{A} with cumulative seedling leaf area.
-This was accomplished by utilizing 61 previously digitized Eucalyptus seedlings, covering 5 total species which include \textit{E.
-tereticornis}, from \citet{duursma2012light} to run in 'YplantQMC' package in R (fix cite YplantQMC) to build a 3d plant structure based on digitized metrics of plant allometry and crown structure.
-Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total \textit{A}, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
-The ratio of total \textit{A} with self-shading to horizontal leaf was then used to calculate $\sigma\textsubscript{s}$ for each of the 61 digitized seedling, independently for each treatment.
-Next, the linear relationship between $\sigma\textsubscript{s}$ and total leaf area was for determined across digitized seedlings, within each treatment.
-For the growth model, $\sigma\textsubscript{s}$ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to \textit{C}\textsubscript{day,i}.
-All default parameters used in model simulations are reported in Table.~\ref{table:Table3}.
-
-We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf \textit{A} where sufficient to accurately predict overall seedling biomass production after 120 days.
-Each model run utilized changes in \textit{A} and leaf mass fraction, with published or local values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
-Cumulative net leaf carbon gain for each treatment was equal to the sum of each value of \textit{C}\textsubscript{day,i} over 120 days and final seedling carbon was assumed to equal half of the final mass for both modeled and observed seedlings.
-First, a default model was optimized to produce a final leaf mass fraction that correctly predicted both the final leaf mass and total biomass of the harvested free seedling controls (M\textsubscript{0}).
-This optimized leaf mass fraction was then applied to model runs with treatment specific \textit{C}\textsubscript{day} to determine if changes in  leaf \textit{A} alone could accurately predict biomass (M\textsubscript{1}).
-Next, model sensitivity to different \textit{C} allocation scenarios, including non-optimized treatment specific leaf mass fraction and up regulation of non-leaf tissue respiration by 50~\% of default values (M\textsubscript{2,3, respectively}), was used to improve predictions of initial model simulations from measured harvest biomass.
-For all cases, seedling production was compared between model output and harvested seedlings with treatment specific mean daily carbon assimilation by first scaling values to the free seedling control.
-
-\subsubsection*{\textit{Data Analysis}}
-
-Differences in experimental parameters with soil volume were analysed by one-way analysis of variance (ANOVA) in R with individual containers as random effects and soil volume as a categorical fixed effect.
-Tukey’s post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
-Mixed model ANOVAs of \textit{A}\textsubscript{max} and leaf chemistry were performed using the 'nlme' package \citep{nlme} in R and \textit{r}\textsuperscript{2} values of mixed models were computed as in \citet{nakagawa2013general}.
-Tests of allometric relationships between biomass components were implemented using major axis regression in the 'smatr' package in R \citep{warton2012smatr}.
-Results were considered significant at P$\leq$0.05.
-
-\section*{Results}
-
-\subsubsection*{\textit{Growth and morphology metrics}}
-
-In this field study, colder temperatures and reductions in cumulative PPFD per day (Fig.~\ref{fig:figure1}) most likely lead to the reduced growth in the free seedlings in the final weeks of the experiment (Fig.~\ref{fig:figure2}).
-Combined with severe growth reductions in the smallest container volumes the experiment was chosen to be harvested after 120~days.
-Over this duration height, diameter, and leaf area diverged between container volumes (Fig.~\ref{fig:figure2}).
-First, seedling leaf area significantly diverged between soil volumes (\textit{P}\textless0.026) during the 5\textsuperscript{th} week of the experiment.
-Following this period both height (8\textsuperscript{th} week) and then diameter (9\textsuperscript{th} week) significantly deviated across soil volumes (\textit{P}\textless0.002 \& 0.001, respectively).
-Negative growth effects then manifested as severely reduced height gain and declining leaf area through time with small soil volumes across the final two months of the experiment.
-Seedlings maintained diameter growth throughout the experiment, although marginal with smaller soil volumes in the final month.
-Final seedling height significantly increased with increasing soil volume (\textit{P}\textless0.001).
-Increases in both final stem diameter (\textit{P}\textless0.001) and cumulative leaf area (both \textit{P}\textless0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling.
-
-Total seedling biomass at harvest was significantly different across container volumes (\textit{P}\textless0.001) and with free seedlings (\textit{P}\textless0.001, Table.~\ref{table:Table1}).
-We analyzed the relationship between biomass growth with each fold increase in soil volume and found an increase of 34~\% with a doubling of pot size, consistent with the meta-analysis of \citet{poorter2012pot}.
-Additionally, plant biomass was highly correlated with total leaf area across all treatments (\textit{r}\textsuperscript{2}~=~0.97, \textit{P}\textless0.001).
-Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass within treatments was factored in the analysis (Fig.~\ref{fig:figure3}a,b).
-Across all treatments, the final harvested root:shoot was conserved in these seedlings, with a slightly higher shoot than root mass on average ($\overline{x}$=0.904, Fig.~\ref{fig:figure3}c).
-
-SRL of harvested fine roots was not different across soil volumes (Table.~\ref{table:Table1}).
-Over the duration of the experiment SLA was higher in free seedlings but was not different across containers sizes (Table.~\ref{table:Table1}, \textit{P}\textless0.001) and this pattern was evident in the first gas exchange measurement campaign (\textit{P}\textless0.001).
-
-\subsubsection*{\textit{Leaf chemistry}}
-
-Leaf \textit{N}~\% was significantly higher in free seedlings and the largest container volume at the onset of gas exchange measurements (6th week, \textit{P}\textless0.001).
-Over the remaining duration of the experiment the smallest container volume had a significant reduction in leaf \textit{N}~\% compared to other soil volumes, while free seedlings maintained the highest leaf \textit{N}~\% (Table.~\ref{table:Table1}, \textit{P}\textless0.001).
-Leaf starch content in the smallest container was double that of free seedlings (\textit{P}=0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table.~\ref{table:Table1}).
-Differences in leaf starch between the free seedling and the smallest container were also evident during the first gas exchange campaign (\textit{P}=0.0013).
-
-\subsubsection*{\textit{Gas exchange and photosynthetic parameters}}
-
-\textit{A}\textsubscript{sat} (Fig.~\ref{fig:figure4}) and \textit{A}\textsubscript{max} (Table.~\ref{table:Table2}) were both significantly higher in the largest container volume and the free seedling at the first measurement campaign (both \textit{P}\textless0.001).
-Across all measurement campaigns \textit{A}\textsubscript{sat} was consistently higher in free seedlings than in containers (Figure 3, \textit{P}\textless0.001).
-The interaction between photosynthetic capacity, leaf starch, and leaf \textit{N} on a mass basis was marginally significant (\textit{P}=0.0584) but \textit{A}\textsubscript{max} was highly correlated to both leaf \textit{N} content and leaf starch (both \textit{P}\textless0.001).
-Across all measurement campaign \textit{A}\textsubscript{max} was higher when foliar \textit{N} was also higher, usually associated with low levels of leaf starch (Fig.~\ref{fig:figure3}a).
-\textit{A}\textsubscript{max} was also lower when leaf starch was high as higher leaf \textit{N} often did not coincide with high leaf starch (Fig.~\ref{fig:figure3}b)
-
-The photosynthetic parameters~\textit{J}\textsubscript{max} and~\textit{Vc}\textsubscript{max} were not different within treatments at the beginning and end of gas exchange campaigns, therefore the parameter means per treatment are reported here (Table.~\ref{table:Table2}).
-Overall, both \textit{J}\textsubscript{max} and \textit{Vc}\textsubscript{max} were significantly higher in free seedlings with little variation between soil volume treatments (\textit{P}=0.0012 \& 0.0021, respectively).
-Leaf dark respiration rates were not significantly different across soil volumes (Table.~\ref{table:Table2}).
-The \textit{g}\textsubscript{1} parameter, generated for each seedling from the \citet{medlyn2012reconciling} optimal stomatal conductance model, was lowest in the free seedling and was marginally different across soil volume treatments (Table.~\ref{table:Table2}).
-Predicted values of \textit{g}\textsubscript{s}, using the \textit{g}\textsubscript{1} parameter, where highly correlated with observed values (\textit{r}\textsuperscript{2}= .74, \textit{P}\textless{0.001}, data not shown).
-
-Neither $\Psi\textsubscript{pd}$ nor $\Psi\textsubscript{l}$ were different across treatments, with mean values of -0.27 and -1.2~mPa across all seedlings, respectively.
-Although \textit{g}\textsubscript{s} in free seedlings was generally higher than those in containers (Table.~\ref{table:Table2}, \textit{P}=0.001), the mean rates for all seedlings were high at 0.37~mol~H\textsubscript{2}0~m\textsubscript{-2}~s\textsubscript{-1} and did not decline significantly across the experiment duration.
-Additionally, leaf {\textdelta}\textsuperscript{13}C at final harvest was not different across treatments (Table.~\ref{table:Table1}).
-Combined these indices provide strong evidence that water stress was not apparent on these well-watered seedlings throughout the experiment.
-Soil \textit{N}~\% at harvest was not different across soil volumes ($\bar{x}$=04.5~\%) and decreased approximately 3~\% across all containers over the experiment duration.
-This indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
-
-\subsubsection*{\textit{Modelling seedling biomass}}
-
-Model M\textsubscript{0}, was able to converge on an optimum leaf mass fraction (21.6~\%) which accurately predicted the mean harvest total biomass of free seedlings within 1.2~\%.
-Using this optimized leaf mass fraction the gross primary productivity of modeled seedlings with soil volume restriction (M\textsubscript{1}) were on average 23$\pm$2.4~g \textit{C} more than measured seedlings When comparing against predicted total net leaf \textit{C} gain (Fig.~\ref{fig:figure6}a).
-Thus, seedling mass \textit{C} was overestimated by an average of 50$\pm$8.7~\% in modeled seedlings across the reductions in daily \textit{C} assimilation per treatment (Fig.~\ref{fig:figure6}b).
-As a result, the reductions in leaf \textit{A} were not sufficiently high enough to explain the reduction in harvested seedling biomass with soil volume restriction.
-With mass balance this resulted in an unexplained pool of excess \textit{C}, generated from \textit{A}, that did not end up in biomass.
-
-The remaining model simulations tested \textit{C} allocation scenarios in an attempt to account for this remaining pool of missing \textit{C}.
-Constraining the model with the measured treatment specific leaf mass fraction from the final harvest (M\textsubscript{2}) still overestimated seedling total \textit{C} by 32$\pm$11.1~\%, but provided the most improved model predictions (Fig.~\ref{fig:figureSI1}a).
-Harvested leaf mass fraction, however, does not capture the likely increase in senescence of seedlings in small containers (Fig.~\ref{fig:figure2}c).
-Thus, the 7-61~\% reduction in measured harvested leaf mass fraction from large to small soil volumes compared to the optimized leaf mass fractions (M\textsubscript{0}) represents an underestimation of realized leaf \textit{C} allocation.
-Increases of 50~\% in non-leaf tissue respiration (M\textsubscript{3}) improved biomass estimates slightly but still overestimated mass \textit{C} by an average of 46$\pm$9.3~\% in seedlings with soil volume restriction (Fig.~\ref{fig:figureSI1}b).
-It was further determined that non-tissue respiration rates in modeled seedlings would need to increase by ca.~250~\% to account for this entire pool of \textit{C}.
-
-\section*{Discussion}
-
-As issues still remain regarding how source-sink coordination affects growth of woody species, this study utilized a simple but novel field design to manipulate belowground sink limitations in order to physically restrict \textit{Eucalyptus tereticornis} seedling production.
-After successfully created a belowground sink limitation we then addressed questions regarding the coordination of \textit{A} and growth by complementing empirical results with modelling approaches.
-We found that reductions in leaf \textit{A} rates were not sufficient to explain observed reductions in total plant biomass production after 120 days.
-We thus encourage the utilization of mass balance approaches and provide direction for future studies when testing factors that control of plant growth under environmental change.
-
-\subsubsection*{\textit{Soil volume restriction and reduced seedling growth}}
-
-As soon as seedlings became established both height and diameter growth were negatively affected as a function of available soil volume compared to free seedlings, providing immediate evidence in support of H1.
-These growth reductions were expected, as the impedance of root growth can cause reductions overall plant growth and activity \citep{mcconnaughay1991physical, young1997mechanical}.
-It has been shown that roots undergoing difficult conditions may send inhibitory signals to the shoots that affect stomatal conductance, cell expansion, cell division and the rate of leaf appearance \citep{passioura2002soil}.
-This was evident in the large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
-As growth was so strongly affected in containers we then asked if biomass partitioning strategies manifested through time that could explain the observed differences in seedling growth.	As mass partitioning is likely controlled by source and sinks strength of all organs \citep{poorter2012biomass} it was important to determine what tissue components were most affected in order to evaluate and then model the biomass response accurately.
-
-As changes to mass allocation of leaves, stems or roots occurs at the expense of other structures \citep{mccarthy2007consistency} it was necessary to first distinguish if belowground sink limitation affected growth beyond ontogenetic constraints.
-In this study, there were no significant changes in root, leaf, or stem mass fractions to reduced soil volume compared to free seedlings, outside of ontogenetic drift.
-This is significant as shifts in allocation, beyond ontogeny, have been noted specifically for nutrient limitation compared to light, CO\textsubscript{2}, and water \citep[references therein]{mcconnaughay1999biomass}.
-Additionally, this provides evidence against the preservation of functional balance through optimal foraging, a common explanation for changes in plant growth under environmental stress.
-In response to root restriction these seedlings might alter biomass allocation to ephemeral tissues, including fine roots or leaves, in order to meet the resource requirements for \textit{A}.
-Fine root mass to leaf mass ratio was instead conserved, regardless of plant size or treatment, suggesting an active biomass partitioning strategy to optimize resource gain did not occur.
-
-Alternatively, physical restriction of root proliferation could have impacted root development or morphology prior to shifts in mass partitioning.
-Plants in containers have been shown to have different root morphology to field grown plants as roots essentially compete with themselves for nutrients \citep{nesmith1998effect}, but data for woody species is still limited.For example, lateral root development is affected by inanimate obstacles and avoiding growth towards container walls could improve the efficiency of resource allocation \citep{falik2005root}.
-Also, the sensitivity of roots to their own exudates near obstructions may be used to adjust growth before stressful conditions occur \citep{semchenko2008foraging}.
-As a result, seedlings in small container sizes might alter fine root morphology, by increasing fine root length, to increase resource uptake potential.
-As neither SRL nor partitioning between fine and coarse root mass fractions differed across treatments, this provides further evidence against any functional plant response beyond developmental isometric growth.
-
-\subsubsection*{\textit{Linkage between belowground sink limitation and photosynthesis}}
-
-As plants must balance allocation to leaves, stems and roots in a way that matches the physiological activities performed by these organs \citep{poorter2012biomass}, the observed reductions in seedling growth could instead have resulted from \textit{C} source-sink imbalances.
-For example, the consequences of either stomatal closure or soil resource depletion to the sensitivity of these source-sink activities could lead to reductions in \textit{A}, the central driver of plant \textit{C} gain and growth.
-Contrary to what was hypothesized, just as height reductions were immediately evident with new growth, so were leaf \textit{A} rates on newly formed leaves.
-As physical restriction to growth was expected to precede effects on leaf physiology this initially suggests a tight link between reduced \textit{A} and seedling growth.
-It was therefore necessary to distinguish if source or sink limitation resulted in the reduction of \textit{A}\textsubscript{sat} and \textit{A}\textsubscript{max}  throughout the experiment.
-
-With high rates of \textit{g}\textsubscript{s}, non-limiting leaf water potential and consistent leaf {\textdelta}\textsuperscript{13}C across soil volume treatments there was little evidence of source limitation to \textit{A} in this study.
-This finding is consistent with other container size studies, with source manipulation via elevated CO\textsubscript{2}, where inhibition of CO\textsubscript{2} enrichment often results from sink limitation on \textit{A}\textsubscript{max} \citep{arp1991effects, robbins1988effect}.
-For example, reduced \textit{A}\textsubscript{max} in cotton seedlings grown at elevated CO\textsubscript{2} was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased \textit{g}\textsubscript{s} \citep{thomas1991root}.
-Our results lend support to more general conclusions that neither growth \citep{korner2003carbon} nor \textit{A} \citep{millard2007environmental} of woody species is directly \textit{C} limited.
-Instead it was likely that reductions in \textit{A} occurred from the impact of a limited soil resource pool on belowground sink strength.
-
-As both belowground space and resources were finite in containers, the limited ability of these seedlings to increase the capacity of the belowground \textit{C} sink was hypothesized to result in the buildup of \textit{C} assimilate in the leaves.
-This buildup, occurring via accumulation of leaf starch, was present as a function of decreasing container size throughout the study.
-As a result, \textit{A}\textsubscript{max} for all seedlings was highly correlated to leaf starch content across all measurement campaigns.
-The accumulation of leaf starch was accompanied by significant decreases \textit{J}\textsubscript{max} and \textit{Vc}\textsubscript{max}, both immediately evident during the first gas exchange campaign.
-Together this provides strong evidence that down regulation of \textit{A} likely occurred from reduced belowground \textit{C} sink strength in these seedlings.
-This down regulation was likely apparent throughout the entire experiment as leaf TNC content remained high in seedlings with soil volume restriction and the effects on \textit{J}\textsubscript{max} and \textit{Vc}\textsubscript{max} were again noted at the end of the experiment.
-
-As limited understanding between source-sink feedbacks to photosynthetic down regulation still exists in woody species, this container size approach also allowed us to directly relate an induced belowground sink limitation to impacts on leaf physiology.
-Evidence for sink limitation of \textit{A} was evident in the stark contrast in leaf \textit{N} between free seedlings and seedlings in containers, combined with the strong correlation between leaf \textit{N} and \textit{A}\textsubscript{max}.
-Leaf \textit{N} was also reduced compared to free seedlings when excess accumulation of leaf starch was present.
-Although the soil \textit{N} pool declined evenly across all treatments leaf \textit{N} was lowest in the smallest soil volume, suggesting that sink limitation was the greatest in these containers.
-This makes sense as small containers may reduce \textit{N} uptake, either from physical root restriction or decreased supply, which affects growth, Rubisco limitation, sugar metabolism, and carbohydrate partitioning between source and sink tissues (Stitt, 1991; Hermans et al., 2006).
-Mycorrhizal colonization could have also been significantly affected by the ‘container effect’.
-Whether unrestricted mycorrhizal recruitment instead facilitated an increase in leaf \textit{N} uptake to leaves in free seedlings is unknown.
-Regardless, the belowground sink strength of seedlings with soil volume treatments was greatly reduced and appears to be strongly linked with negative feedbacks to \textit{A}.
-
-\subsubsection*{\textit{Modeling the coordination of photosynthesis and growth with carbon mass balance}}
-
-If feedbacks between sink limitation and leaf \textit{A} controlled seedling growth the growth model was expected to find agreement between simulated and observed seedling biomass.
-A linkage between sink limitation and \textit{A}, however, does not necessarily imply the same level of coordination between reduced \textit{A} and growth.
-It was therefore necessary to test, using a mass balance approach, if the measured reductions in \textit{A} could be used to predict the patterns in seedling growth after 120~days.
-Constraining the initial model run (M\textsubscript{1}) by an optimized leaf mass fraction allowed us to test if feedbacks from reduced \textit{A} could predict seedling growth with soil volume restriction.
-The result was a difference in the fate of assimilated \textit{C}, with a larger fraction of available \textit{C} ending up in final biomass of modeled seedlings.
-Consequently, this also revealed a pool of missing \textit{C} in measured seedlings unaccounted for with mass balance.
-This finding lends strong evidence that \textit{A} and growth may not be entirely synced under environmental change, an important distinction often missed in studies that manipulate source and sink activity.
-Thus, without \textit{C} mass balance approaches inferences to the nature of mechanisms controlling growth under environmental stress should only be speculative.
-As a result, we utilized the flexibility of the model to test potential sources of \textit{C} loss not explicitly measured, including changes to leaf \textit{C} allocation or non-leaf tissue respiration.
-Through this approach, similar to \citep{lohier2014explaining}, we manipulated processes contributing to seedling \textit{C} mass balance and quantitatively tested their respective influences on model predictions.
-
-Altering the leaf mass fraction from that of the optimized free seedling control (M\textsubscript{2}) improved model biomass predictions and provided insight into how sink limitation may impact leaf \textit{C} allocation beyond that of \textit{A}.
-As this was a field study it was impossible to quantify all impacts to leaf \textit{C} allocation which could have occurred.
-Model predictions, however, provided evidence for how the feedback between rates of photosynthesis and \textit{C} allocated to leaves can severely impact seedling growth.
-The observed sub-optimal decrease in leaf mass fraction with increasing soil volume restriction has several possible explanations.
-First, TNC accumulation due to sink limitation can lead to accelerated leaf senescence \citep{paul2001sink}.
-Alternatively, as rates of \textit{A} were not different between soil volume treatments these seedlings could have reduced leaf production to maintain laws of stoichiometry (leaf \textit{C}:\textit{N} ratio) associated with reduced belowground \textit{C} sink strength and measured declines in leaf N.
-Thus, future empirical studies and modelling efforts should focus on the feedbacks from sink activity not only on leaf A rates but also on the fate of \textit{C} allocated to leaves.
-It is the interaction between these two components that will drive patterns of total canopy \textit{C} gain available for growth for the rest of the plant.
-
-Increases in non-leaf respiration rates  (M\textsubscript{3}) improved biomass predictions but to a lesser extent than changes to leaf \textit{C} allocation.
-This finding is still significant as it justifies the need to strengthen our knowledge of the effects of environmental change on respiration of different tissues components above and belowground.
-As \textit{C} balance is a delicate equilibrium between fluxes of photosynthesis and respiration, partial accounting of \textit{C} dynamics can easily lead to erroneous conclusions (Valentini et al.
-2000).
-For example, there is strong evidence for coupling between photosynthesis and respiration yet \textit{C} use efficiency is not always constant \citep{cannell2000modelling}.
-In addition, our understanding of how changes in sink activity affect this coupling or regulation of respiration across different tissues components in woody species is still poor.
-Thus, it is likely inappropriate to assume that respiration is an constant fraction of gross primary production in models \citep{delucia2007forest}.
-We reveal that any significant impact to tissue respiration will likely impact the synchronization of \textit{A} and growth and should be accounted for in  future empirical studies and modelling efforts that predict plant growth under environmental change.
-
-\subsubsection*{\textit{Conclusions}}
-
-Although there is renewed debate of the coordination of \textit{A} and growth this is not a new issue.
-It has long been know that conditions which affect the photosynthetic process affect growth but there is also an interrelationship between growth and \textit{A} \citep{sweet1966role}.
-We found that the fate of assimilated \textit{C}, available for plant growth, was different between free seedlings and seedlings in containers.
-This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles but how these results actually reflect field-grown plants has seldom been studied.
-Utilizing a mass-balance approach with a simple production model revealed that a combination of different mechanisms must be at play in driving this observed seedling biomass response to sink manipulation.
-However, which of the mechanisms and the role they have in determining growth response will undoubtedly shift across different experimental manipulations and plant species.
-We argue that attempts to quantify or at least predict the fate of assimilated \textit{C} into known pools of growth, storage and \textit{C} loss are necessary before definitive resolution of the controls of plant growth are to be found.
-The widespread implications of this type of approach, allowing the flexibility to account for multiple potential drivers of \textit{C} allocation and plant growth, can help answer questions about the fate of \textit{C} in plants undergoing environmental change.
-
-%--------------------------------------------------------------------------------------------%
-\section*{Tables}
-% Load xtable for printing tables.
-<<echo=FALSE, message=FALSE, warning=FALSE>>=
-library(xtable)
-pve_data <- read.csv("table/pve_table1.csv")
-
-colnames(pve_data) <- c("Volume (L)", 
-                        "Seedling~mass~(g)", 
-                        "SLA\\textsubscript{TNC-free}~(m\\textsuperscript{2}~kg\\textsuperscript{-1})",
-                        "Leaf~Starch~(\\%)", 
-                        "Leaf~Sugars~(\\%)", 
-                        "Leaf~Nitrogen~(\\%)",
-                        "Root~Nitrogen~(\\%)",
-                        "SRL~(cm~m\\textsuperscript{-1})",
-                        "{Leaf~\\textdelta}\\textsuperscript{13}C~(\\text{\\textperthousand})")
-
-phys_data <- read.csv("table/pve_table2.csv")
-colnames(phys_data) <- c("Volume~(L)", 
-                        "\\textit{A}\\textsubscript{max}", 
-                        "\\textit{R}\\textsubscript{dark}",
-                        "\\textit{J}\\textsubscript{max}",
-                        "\\textit{Vc}\\textsubscript{max}",
-                        "\\textit{g}\\textsubscript{s}",
-                        "\\textit{g}\\textsubscript{1}")
-
-@
-
-%seedling data table
-<<results='asis'>>=
-datatab <- xtable(pve_data, label="table:Table1", caption="Responses of plant and leaf characterisitics of \\textit{Eucalyptus tereticornis} seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
-Seedling mass, SRL, root nitrogen and leaf \\textdelta\\textsuperscript{13}C values are from final harvest.
-Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6).
-Different letters represent significant differences between treatments.
-The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.")
-
-print(datatab, include.rownames=FALSE,sanitize.colnames.function=function(x){x},
-      floating.environment='sidewaystable', caption.placement="top", 
-      hline.after = getOption("xtable.hline.after", c(-1,0,7,nrow(datatab))))
-
-@
-
-%data.df$taxa <- paste("\\emph{",taxa,"}", sep="")
-
-<<results='asis'>>=
-phystab <- xtable(phys_data, label="table:Table2",caption="Responses of leaf level gas exchange parameters of \\textit{Eucalyptus tereticornis} seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
-Units for \\textit{A}\\textsubscript{max} and \\textit{R}\\textsubscript{dark} are {\\textmugreek}mol~m\\textsuperscript{-2}~s\\textsuperscript{-1} and \\textit{g}\\textsubscript{s} are mol~m\\textsuperscript{-1}~s\\textsuperscript{-1}, each at at 25$\\degree$C.
-Values of \\textit{A}\\textsubscript{max}, \\textit{g}\\textsubscript{s} and \\textit{g}\\textsubscript{1} represent overall means across measurement campaigns (n=6).
-\\textit{R}\\textsubscript{dark}, \\textit{J}\\textsubscript{max} and \\textit{Vc}\\textsubscript{max} values are means of two measurement campaigns at beginning and end of gas exchange measurements.
-Different letters represent significant differences between treatments.
-The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.")
-
-print(phystab, include.rownames=FALSE,sanitize.colnames.function=function(x){x},
-      floating.environment='sidewaystable',caption.placement="top",
-       hline.after = getOption("xtable.hline.after", c(-1,0,7,nrow(datatab))))
-@
-
-%--------------------------------------------------------------------------------------------%
-\clearpage
-\section*{Figures}
-
-%air variables figure
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{airvars.pdf}
-    \caption{Daily maximum and minimum temperature (a), cumulative daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.}
-    \label{fig:figure1}
-\end{figure}
-
-%allometry figure
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{allometry.pdf}
-    \caption{Soil volume treatment means~$\pm$ standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of \textit{Eucalyptus tereticornis} seedlings across the experiment duration in 2013.}
-    \label{fig:figure2}
-\end{figure}
-
-%partitioning figure
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{massfractions.pdf}
-    \caption{Soil volume treatment means of mass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with $\pm$ standard error (c).
-For (b) lines represent standardized major axis fitting of the log transformed allometric relationships of leaf mass fraction by treatment.
-For (c) the dashed line is the 1:1 relationship and the solid line represents the significant linear model fit (\textit{r}\textsuperscript{2}~=~0.81).}
-    \label{fig:figure3}
-\end{figure}
-
-%asat figure
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{Asat.pdf}
-    \caption{Soil volume treatment means~$\pm$ standard error, across all measurement campaigns (n=6), of light saturated rates of photosynthesis at 25$\degree$C.
-Different letters represent significant differences between treatments.}
-    \label{fig:figure4}
-\end{figure}
-
-%photochem figure
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{A_leafchem.pdf}
-    \caption{Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).
-Colors represent bins levels (n=5) of both leaf starch and nitrogen grouped from low to high .
-Lines represents predictions, for each bin level, from the linear mixed effects model equation of \textit{A}\textsubscript{max} as a function of starch and nitrogen.
-The marginal \textit{r}\textsuperscript{2} (fixed effects only) was 0.37 and the conditional \textit{r}\textsuperscript{2} (fixed and random effects) was 0.48 for the complete model.}
-    \label{fig:figure5}
-\end{figure}
-
-%model base figure
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{massmodel_totalC.pdf}
-    \caption{Total carbon mass for harvested and modeled seedlings versus predicted total carbon gain after 120 days (a) and  reductions in final seedling carbon mass, both modeled and observed, as a function of the reduction in leaf photosynthesis across treatments (b).
-For (a) the dashed 1:1 identifies the difference between net total leaf carbon gain and gross seedling production.
-For (b) both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.}
-    \label{fig:figure6}
-\end{figure}
-
-%--------------------------------------------------------------------------------------------%
-\clearpage
-\section{Supporting Information Figures}
-% Supporting information. Make sure Figures continue with Fig S1 etc.
-
-\renewcommand\thefigure{S\arabic{figure}}    
-\setcounter{figure}{0}
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.99\textwidth]{massmodel_resp.pdf}
-    \caption{Sensitivity testing of seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50~\% (b).
-Open and filled symbols represent default model and harvest values, while shaded symbols represent model sensitivity to each scenario by soil volume treatment.
-Both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.}
-    \label{fig:figureSI1}
-\end{figure}
-
-\begin{table}[h!]
-  \caption{Seedling Growth Model Default Parameters} 
-  \centering 
-  \begin{tabular}{l l l l l } 
-  \hline
-  Variable & Description & Default Value & Units & Source  \\ [0.5ex] 
-  \hline
-  Leaf area\textsubscript{i} & initial leaf area & 0.035 & m\textsuperscript{2} & this study \\
-
-  Leaf mass\textsubscript{i} & initial leaf mass & 3.45 & g & this study \\
-
-  Stem mass\textsubscript{i} & initial stem mass & 1.51 & g & this study \\
-
-  Root mass\textsubscript{i} & initial root mass & 0.99 & g & this study \\
-
-  \textepsilon\textsubscript{c} & biomass conversion efficiency & .65 & g~C g~mass\textsuperscript{-1} 
-  & \citet{makela1997carbon} \\
-
-  R\textsubscript{coarse root} & coarse root respiration & 0.00124 & g~C g~root\textsuperscript{-1} 
-  & \citet{marsden2008relating} \\
-
-  R\textsubscript{fine root} & fine root respiration & 0.010368 & g~C g~root\textsuperscript{-1} & \citet{ryan2010factors} \\
-
-  R\textsubscript{stem} & stem respiration & 0.00187 & g~C g~stem\textsuperscript{-1} & Drake 2014 (unpublished) \\
-
-  C\textsubscript{day} & Daily Leaf Carbon Assimilation &5.4-7.6 & g~C m\textsuperscript{-2} d\textsuperscript{-1}
-  & this study \\
-
-  $\Lambda$ & tissue turnover & 1/365 & yr\textsuperscript{-1} & theoretical\\
-
-  \hline 
-  \end{tabular}
-  \label{table:Table3} 
-\end{table}
-
-%--------------------------------------------------------------------------------------------%
-\clearpage
-\bibliography{pve_cites}
-
-%--------------------------------------------------------------------------------------------%
-\end{document}

### 2015-07-21 manuscript/manuscript_pve.Rmd
added tables to manuscript (jpg)
messed with srl stats and output
added srl changes in manuscript

@@
 Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
-It was hypothesized that soil volume effect would be largest in the smallest containers, resulting in physical constraints to growth independently of photosynthesis (A).
-Photosynthesis would then become sink-limited, resulting in the build-up of leaf nonstructural carbohydrates eventually leading to photosynthetic down regulation.
+It was hypothesized that soil volume effect would be largest in the smallest containers, mediated by a down-regulation of photosynthesis (A).
+The accumulation of leaf non-structural carbohydrates, resulting from reduced sink strengh, was expected to correleltae to reductions in photosynthetic capacity.
 We observed a negative container effect on aboveground growth soon after the experiment started.
@@
 \
-SRL of harvested fine roots was not different across soil volumes (Table.
+Overall, SRL was higher in seedlings in containers than free seedlings but not significantly in every soil volume treatment   (Table.
 1).
@@
 
+\
+Alternatively, physical restriction of root proliferation could have impacted root development or morphology prior to shifts in mass partitioning.
+Here, increases in root length occurred in several of the soil volume treatments while no shifts in partitioning between fine and coarse root mass fractions were detected.
+The overall poor quality of the soil or the effects of root restriction, however, likely decreased the capacity of this morphological response to increase leaf N uptake.
+This is not surprising, as plants in containers have been shown to have different root morphology to field grown plants as roots essentially compete with themselves for nutrients [@nesmith1998effect].
+As the root mass fractions did not differ this provides evidence against an optimal foraging response in seedlings in containers.
+This could be because lateral root development is affected by inanimate obstacles and avoiding growth towards container walls could improve the efficiency of resource allocation [@falik2005root].
+Also, the sensitivity of roots to their own exudates near obstructions may be used to adjust growth before stressful conditions occur [@semchenko2008foraging].
+
 ## Does reductions in photosynthesis explain reductions in seedling growth
@@
 A lack of knowledge regarding C allocation restricts our ability to achieve mass balance and is a major obstacle in understanding the coordination between A and growth.
-In any case, we should not assume that
+The approach used here has the flexibility to account for multiple drivers of C allocation and provides an avenue to address future questions regarding the impact of environmental change on plant growth.
 
 # Tables {.unnumbered}
+
+<!---
+![table2](harvesttable.jpg)
+![table2](phystable.jpg)
+![table3](modeltable.jpg)
+-->
 

### 2015-07-21 clean Scripts/rootleaf_morph_plotting.R

@@ -4,39 +4,24 @@ source("functions and packages/startscripts.R")
 plotsumm <- read.csv("raw data/plot_summary.csv")
   plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
 
-##SLA[tncfree]------------------------------------------------------------------------------------------
-
-sla_tnc <- read.csv("calculated data/TNC_content")
-  sla_tnc$volume <- as.factor(sla_tnc$volume) 
-  sla_tnc$Date <- as.Date(sla_tnc$Date)
-  sla_tnc$sla <- with(sla_tnc, area/mass)
-  sla_tnc$lma <- with(sla_tnc, mass/area)
-
-leaf_TNCfree <- subset(sla_tnc, select = c("ID", "volume", "sla_free", "lma_free","sla", "lma","Date"))
-  volorder<-order(leaf_TNCfree$volume, by=leaf_TNCfree$Date)
-  leaf_TNCfree <- leaf_TNCfree[volorder,]
-
-#treatment means
-sla_tnc_campaign <- summaryBy(sla_free+lma_free+ sla+ lma ~ volume+Date, data=leaf_TNCfree, FUN=c(mean, se))
-#treatment means
-sla_tnc_agg <- summaryBy(sla_free+lma_free+ sla+ lma~volume, data=leaf_TNCfree, FUN=c(mean, se))
-
 #SRL------------------------------------------------------------------------------------------------------
 srl <- read.csv("raw data/SRLmass.csv")
   srl$ID <- paste(srl$plot, srl$pot, sep = "-")
   srl <- merge(srl, plotsumm[3:4], all=TRUE)
   srl <- subset(srl, !is.na(volume))
-  #srl$SRL <- with(srl, (total_length_cm/100)*(srl_fw*(ss_dw/ss_fw)))
+  srl$SRL <- with(srl, (total_length_cm/100)*(srl_fw*(ss_dw/ss_fw)))
   srl$SRL2 <- with(srl, (total_length_cm/100)/(srl_fw*(ss_dw/ss_fw)))
   srl$volume <- as.factor(srl$volume)
   row.names(srl) <- NULL
   #srl <- vollab_func(srl)
   
-srl_clean <- srl[srl$SRL2 <= 100,]  
+##some values really high, remove to pots from boxplot of data  
+#srl_clean <- srl[srl$SRL2 <= 100,]  
[…]

### 2015-07-22 manuscript/manuscript_pve.Rmd
changes to bibtex CO2
edits to manuscript

small edits to figures and table dfrs

@@
 ---
-title: "Effects of below-ground space limitation on performance of Eucalyptus seedlings:  Does photosynthesis really control growth?"
+title: "Effects of below-ground sink limitation on growth and carbon balance of Eucalyptus seedlings"
 author: ""
@@
 Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
-It was hypothesized that soil volume effect would be largest in the smallest containers, mediated by a down-regulation of photosynthesis (A).
+It was hypothesized that soil volume effect would be largest in the smallest containers, negatively impacting mass partitioning belowground.
 The accumulation of leaf non-structural carbohydrates, resulting from reduced sink strengh, was expected to correleltae to reductions in photosynthetic capacity.
@@
 Photosynthetic capacity was also significantly reduced in containers, and was related to both leaf nitrogen content and starch accumulation.
-We developed a seedling growth model that utilized leaf A rates to allocate daily C uptake towards mass growth of stems, leaves and roots.
+We developed a seedling growth model that utilized leaf photosynthesis (A) rates to allocate daily C uptake towards mass growth of stems, leaves and roots.
 We then asked whether the observed reductions in A explained the observed differences in seedling biomass.
 We found that although belowground sink limitation resulted in the down regulation of A, these reductions were not significant enough to explain observed growth responses.
-Thus, as photosynthesis and growth were not coordinated an excess pool of non-biomass C resulted in seedlings with soil volume restriction.
+Thus, as A and growth were not coordinated an excess pool of non-biomass C resulted in seedlings with soil volume restriction.
 This research highlights the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that A and growth are not always directly related.
@@
 As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues and organs.
-At long enough time scales A and growth must be correlated in respect to mass balance, however, at shorter temporal scales growth is not necessarily limited by the availability of recent photosynthate.
+At long enough time scales photosynthesis (A) and growth must be correlated to maintain mass balance, however, at shorter temporal scales growth is not necessarily limited by the availability of recent photosynthate.
 This has led to the current debate over how strongly plant growth is controlled by either source of sink activity.
-Consequently, plant growth cannot be simply determined by rates of A making it complex to understand and challenging to model [@fourcaud2008plant].
-Despite a wealth of studies large uncertainties still remain regarding the coordination of C supply, via A, and growth of woody species.
+Consequently, plant growth cannot always be simply determined by the photosynthesis rate, making it complex to understand and challenging to model [@fourcaud2008plant].
+Despite a wealth of studies large uncertainties still remain regarding the coordination of C supply and growth of woody species.
 
@@
 Examples included elevated CO~2~ experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments.
-Elevated CO~2~ has been shown to increase A rates [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a conserved increase in forest production [@norby2005forest].
-Evidence from elevated CO~2~ experiments, however, also reveals that the growth response tends to be much smaller than the photosynthetic enhancement [@kirschbaum2011does].
-In defoliation experiments, compensatory increases in A are commonly shown yet are attributed to variable mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], leaf nutrient status [@turnbull2007increased], and regulatory sugar signaling [@eyles2013whole].
+Elevated CO~2~ has been shown to increase A rates [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a conserved increase in forest biomass production [@norby2005forest].
+Evidence from elevated CO~2~ experiments, however, also reveals that even with average photosynthetic enhancement of over 30 % the growth rate only increases by around 10 %  [@kirschbaum2011does].
+In defoliation experiments, increases in A of the remaining foliage are commonly shown yet are attributed to variable mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], leaf nutrient status [@turnbull2007increased], and regulatory sugar signaling [@eyles2013whole].
 However, increases in A did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
@@
 These mixed results are not surprising as we still know little about the pathways in which plants achieve balance between assimilation, storage, and growth across temporal scales [@smith2007coordination].
-As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to large annual fruiting sinks, they tell us little about source-sink coordination in normal field-grown woody species.
-
-\
-If source or sink manipulations do not lead to equivalent changes in growth then understanding the fate of assimilated C becomes even more crucial.
-As programmed plasticity in C allocation naturally occur as plants growth and develop, this must be accounted for when evaluating induced variation in growth [@wright2002interpreting].
-Thus, when C allocation is altered by a treatment, it should be shown whether these allocation patterns differ from common sized untreated plants [@reich2002root;@poorter2012biomass].
-Only then can we test if functional balance preservation or optimal foraging occurs from changes in C uptake.
-For example, seedlings in containers may shift allocation to leaves if root restriction occurs or alter fine root morphology to increase nutrient uptake.
-In woody species, shifts in allometric relationships of leaves, stems and roots can reveal if growth is ontogenetically constrained or actively adjusted when A is affected.
-This then allows additional pools of C, such as root exudation or changes in tissue respiration, to be accounted for and mass balance to be achieved.
+As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to large annual fruiting sinks, they tell us little about source-sink coordination in typical field conditions for woody species.
 
@@
 
+\
+Our hypotheses were as follows:
+\
 1).
 The manipulations of container size were expected to induce a belowground sink limitation compared to free seedlings.
-We hypothesized that declines in seedling grow would be largest in the smallest containers, mediated by a down-regulation of photosynthesis.
+We hypothesized that declines in seedling growth would be largest in the smallest containers.
 
-2).
-Reduced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, which is known to inhibit A We therefore expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume.
+2). As the finite pool of rooting volume and soil nutrients will decline faster in small containers we expected decreases in partitioning to fine root mass with decreasing container size.
 
-3). Last, the growth model was expected to find agreement between simulated and observed seedling mass, through direct correlation of the effects of limiting soil volume on A.
+3).
+Reduced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, which is known to inhibit A.
+We therefore expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume.
+
+4). Last, the growth model was expected to find agreement between observed seedlings mass and mass predicted from a simple carbon balance model taking into account measured rates of photosynthesis.
 
@@
 Roots from the free seedlings were collected by excavating each 1 m^2^ subplot to 0.5 m depth.
-25 g fresh weight subsamples of washed fine roots were analyzed, using WhinoRhizo software (Regent Instruments Inc.), for specific root length (SRL, m g^-1^).
+25 g fresh weight subsamples of washed fine roots were analyzed, using WhinoRhizo software (Regent Instruments Inc., Quebec, QC, Canada), for specific root length (SRL, m g^-1^).
 
@@
 \
-Leaf TNC concentration was analyzed using a total starch assay kit (Megazyme International 303 Ireland Ltd., Wicklow, Ireland) and includes the starch (mg g^-1^) and soluble sugar (mg g^-1^) concentrations.
+Leaf TNC concentration was analyzed using a total starch assay kit (Megazyme International, Wicklow, Ireland) and includes the starch (mg g^-1^) and soluble sugar (mg g^-1^) concentrations.
 Starch was quantified using a thermostable $\alpha$-amylase and amyloglucosidase assay [@McCleary_starch] and soluble sugars were determined following the anthrone method [@ebell1969variation].
@@
 Each model run utilized changes in A and leaf mass fraction (LMF), with published or local values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
-Cumulative net leaf carbon gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling carbon was assumed to equal half of the final mass for both modeled and observed seedlings.
+Cumulative net leaf C gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling C was assumed to equal half of the final mass for both modeled and observed seedlings.
 First, a default model was optimized to produce a final LMF that correctly predicted both the final leaf mass and total biomass of the harvested free seedling controls (M~0~).
@@
 Next, model sensitivity to different C allocation scenarios, including non-optimized treatment specific LMF and up regulation of non-leaf tissue respiration by 50 % of default values (M~2,3~, respectively), was used to improve predictions of initial model simulations from measured harvest biomass.
-For all cases, seedling production was compared between model output and harvested seedlings with treatment specific mean daily carbon assimilation by first scaling values to the free seedling control.
+For all cases, seedling production was compared between model output and harvested seedlings with treatment specific mean daily C assimilation by first scaling values to the free seedling control.
 
@@
 Differences in experimental parameters with soil volume were analysed by one-way analysis of variance (ANOVA) in R with individual containers as random effects and soil volume as a categorical fixed effect.
-Tukey’s post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
+Tukey's post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
 Mixed model ANOVAs of A~max~ and leaf chemistry were performed using the 'nlme' package [@nlme] in R and R^2^ values of mixed models were computed as in [@nakagawa2013general].
 Tests of allometric relationships between biomass components were implemented using major axis regression in the 'smatr' package in R [@warton2012smatr].
-Results were considered significant at P&leq;0.05.
+Results were considered significant at P &leq; 0.05.
 
@@
 `r allomfig`).
-First, seedling leaf area significantly diverged between soil volumes (P<0.026) during the 5^th^ week of the experiment.
-Following this period both height (8^th^} week) and then diameter (9^th^ week) significantly deviated across soil volumes (P<0.002 & 0.001, respectively).
+First, seedling leaf area significantly diverged between soil volumes (P < 0.026) during the 5^th^ week of the experiment.
+Following this period both height (8^th^} week) and then diameter (9^th^ week) significantly deviated across soil volumes (P < 0.002 & 0.001, respectively).
 Negative growth effects then manifested as severely reduced height gain and declining leaf area through time with small soil volumes across the final two months of the experiment.
 Seedlings maintained diameter growth throughout the experiment, although marginal with smaller soil volumes in the final month.
-Final seedling height significantly increased with increasing soil volume (P<0.001).
-Increases in both final stem diameter (P<0.001) and cumulative leaf area (both P<0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling.
+Final seedling height significantly increased with increasing soil volume (P < 0.001).
+Increases in both final stem diameter (P < 0.001) and cumulative leaf area (both P < 0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling.
 
 \
-Total seedling biomass at harvest was significantly different across container volumes (P<0.001) and with free seedlings (P<0.001, Table.
+Total seedling biomass at harvest was significantly different across container volumes (P < 0.001) and with free seedlings (P < 0.001, Table.
 1).
-We analyzed the relationship between biomass growth with each fold increase in soil volume and found an increase of 34% with a doubling of pot size, consistent with the meta-analysis of Poorter et al.
+We analyzed the relationship between biomass growth with each fold increase in soil volume and found an increase of 34 % with a doubling of pot size, consistent with the meta-analysis of Poorter et al.
 [-@poorter2012pot].
-Additionally, plant biomass was highly correlated with total leaf area across all treatments (R^2^ = 0.97, P<0.001).
+Additionally, plant biomass was highly correlated with total leaf area across all treatments (R^2^ = 0.97, P < 0.001).
 Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass within treatments was factored in the analysis (Fig.`r allocfig`a,b).
-Across all treatments, the final harvested root:shoot was conserved in these seedlings, with a slightly higher shoot than root mass on average ($\overline{x}$=0.904, Fig.
+Across all treatments, the final harvested root:shoot was conserved in these seedlings, with a slightly higher shoot than root mass on average ($\overline{x}$ = 0.904, Fig.
 `r allomfig`c).
@@
 \
-Overall, SRL was higher in seedlings in containers than free seedlings but not significantly in every soil volume treatment   (Table.
+Overall, SRL was higher in seedlings in containers compared to free seedlings but not significantly in every soil volume treatment   (Table.
 1).
 Over the duration of the experiment SLA was higher in free seedlings but was not different across containers sizes (Table.
-1, P<0.001) and this pattern was evident in the first gas exchange measurement campaign (P<0.001).
+1, P < 0.001) and this pattern was evident in the first gas exchange measurement campaign (P < 0.001).
 
 ## Leaf chemistry
-Leaf N % was significantly higher in free seedlings and the largest container volume at the onset of gas exchange measurements (6th week, P<0.001).
+Leaf N % was significantly higher in free seedlings and the largest container volume at the onset of gas exchange measurements (6th week, P < 0.001).
 Over the remaining duration of the experiment the smallest container volume had a significant reduction in leaf N % compared to other soil volumes, while free seedlings maintained the highest leaf N % (Table.
-1, P<0.001).
+1, P < 0.001).
 Leaf starch content in the smallest container was double that of free seedlings (P=0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table.
 1).
-Differences in leaf starch between the free seedling and the smallest container were also evident during the first gas exchange campaign (P=0.0013).
+Differences in leaf starch between the free seedling and the smallest container were also evident during the first gas exchange campaign (P = 0.001).
 
 ## Gas exchange and photosynthetic parameters
-A~sat~ and A~max~ were both significantly higher in the largest container volume and the free seedling at the first measurement campaign (both P<0.001).
+A~sat~ and A~max~ were both significantly higher in the largest container volume and the free seedling at the first measurement campaign (both P < 0.001).
 Across all measurement campaigns A~sat~ (Fig.
-`r asatfig`) and A~max~ (Table 2.) were consistently higher in free seedlings than in containers (both P<0.001).
-The interaction between photosynthetic capacity, leaf starch, and leaf N on a mass basis was marginally significant (P=0.0584) but A~max~ was highly correlated to both leaf N content and leaf starch (both P<0.001).
+`r asatfig`) and A~max~ (Table 2.) were consistently higher in free seedlings than in containers (both P < 0.001).
+The interaction between photosynthetic capacity, leaf starch, and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ was highly correlated to both leaf N content and leaf starch (both P < 0.001).
 Across all measurement campaign A~max~ was higher when foliar N was also higher, usually associated with low levels of leaf starch (Fig.
@@
 2).
-Overall, both J~max~ and Vc~max~ were significantly higher in free seedlings with little variation between soil volume treatments (P=0.0012 & 0.0021, respectively).
+Overall, both J~max~ and Vc~max~ were significantly higher in free seedlings with little variation between soil volume treatments (P = 0.001 & 0.002, respectively).
 Leaf dark respiration rates were not significantly different across soil volumes (Table.
@@
 2).
-Predicted values of g~s~, using the g~1~ parameter, where highly correlated with observed values (R^2^= .74, P<0.001, data not shown).
+Predicted values of g~s~, using the g~1~ parameter, where highly correlated with observed values (R^2^ = .74, P < 0.001, data not shown).
 
@@
 Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 mPa across all seedlings, respectively.
-Although P=0.001), the mean rates for all seedlings were high at 0.37 mol H~2~0 m^-2^ s^-1^ and did not decline significantly across the experiment duration.
+Although g~s~ in free seedlings was genearlly higher htan those in containers (Table 2.
+P=0.001), the mean rates for all seedlings were high at 0.37 mol H~2~0 m^-2^ s^-1^ and did not decline significantly across the experiment duration.
 Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table.
@@
 Combined these indices provide strong evidence that water stress was not apparent on these well-watered seedlings throughout the experiment.
-Soil N % at harvest was not different across soil volumes ($\bar{x}$=04.5 %) and decreased approximately 3 % across all containers over the experiment duration.
+Soil N % at harvest was not different across soil volumes ($\bar{x}$ = 04.5 %) and decreased approximately 3 % across all containers over the experiment duration.
 This indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
@@
 We found that reductions in leaf A rates were not sufficient to explain observed reductions in total plant biomass production.
-We thus encourage the utilization of mass balance approaches and provide direction for future studies when testing factors that control of plant growth under environmental change.
+We thus encourage the utilization of mass balance approaches and provide direction for future studies when testing factors that control plant growth under environmental change.
 
-## Soil volume restiction compared to field plants
-As soon as seedlings became established both height and diameter growth were negatively affected as a function of available soil volume when compared to free seedlings.
+## Reductions in growth and physiology under sink limitation
+As soon as seedlings became established both height and diameter growth were negatively affected by decreasing soil volume.
+This lead to the large reductions in harvested biomass in small containers when compared to free seedlings.
 These growth reductions were expected, as the impedance of root growth can cause reductions overall plant growth and activity [@mcconnaughay1991physical; @young1997mechanical].
@@
 Decreases in A~sat~ paralleled the reductions in allometric growth parameters of seedlings in containers.
-This initially suggests a tight link between A and growth, consistent with our hypothesis that growth declines would be mediated by the down regulation of A.
-However, there are several possible mechanisms that can explain reduced A in small pots, including nutrient content, water or reduced sink strength [@poorter2012pot].
+This initially suggests a strong link between growth and an apparent down regulation of A.
+However, there are several possible mechanisms that can explain reduced A in small pots including nutrient content, water or reduced sink strength [@poorter2012pot].
 It was therefore necessary to examine each of these factors to distinguish if the induced belowground sink limitation actually triggered photosynthetic down regulation.
@@
 \
-With high rates of g~s~, non-limiting leaf water potential and consistent leaf $delta$^13^C across soil volume treatments there was little evidence of water supply inducing a source limitation to A.
+With high rates of g~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence of water stress inducing a limitation to A.
 This finding is consistent with other container size studies without drought treatments.
-For example, reduced A~max~ in cotton seedlings grown at elevated CO^2^ was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased g~s~ [@thomas1991root].
+For example, reduced A~max~ in cotton seedlings grown at elevated CO~2~ was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased g~s~ [@thomas1991root].
 Additionally, severe reductions in A in coffee plants was not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
-In these well watered seedlings it was likely that reductions in A were instead the result of a limited soil nutrient resource pool on belowground sink strength.
+Here, it is likely that reductions in A of these well watered seedlings was instead the result of limiting soil nutrients on belowground sink strength.
 
@@
 This makes sense as small containers may reduce N uptake, either from physical root restriction or decreased supply, which affects growth, Rubisco limitation, sugar metabolism, and carbohydrate partitioning between source and sink tissues [@stitt1991rising; @hermans2006plants].
-Mycorrhizal colonization could also have been affected by the container effect.
-Whether unrestricted mycorrhizal recruitment facilitated the increase in leaf N uptake to leaves in free seedlings is unknown.
-Regardless of whether the sink limitation occurred from root or mycorrhizal restriction, the stark contrast between leaf N between free seedlings and seedlings in containers was significantly correlated to reductions in A.
+Mycorrhizal colonization could also have been affected in containers.
+Whether unrestricted mycorrhizal recruitment facilitated the increase in leaf N uptake in free seedlings is unknown.
+Regardless of whether sink limitation occurred from root or mycorrhizal restriction, the stark contrast in leaf N between free seedlings and seedlings in containers was significantly correlated to reductions in A.
 
 \
-As both rooting space and resources were finite in containers, the limited ability of these seedlings to increase the capacity of the belowground C sink was hypothesized to result in the buildup of C assimilate in the leaves.
+As both rooting space and resources were finite in containers, the inability of seedlings to increase the capacity of the belowground C sink resulted in the buildup of C assimilate in leaves.
 The feedback inhibition of A from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process (Nebauer et al.
@@
 
-## Carbon allocation under sink limitation
-As mass partitioning is likely controlled by source and sink strength of all organs [@poorter2012biomass] it was important to determine what tissue components were most affected by the sink limitation to then model the biomass response accurately.
+## Mass partitioning under sink limitation
+As mass partitioning is likely controlled by the source and sink strength of all organs [@poorter2012biomass] it was important to determine what tissue components were most affected by the sink limitation.
 It was necessary to distinguish if growth was affected beyond ontogenetic constraints, by correcting for size, as biomass distribution is strongly size-dependent [@gould1966allometry; @lleonart2000removing].
 In this study, there were no significant changes in root, leaf, or stem mass fractions to reduced soil volume compared to free seedlings, outside of ontogenetic drift.
-This is significant as shifts in allocation, beyond ontogeny, have been noted specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein].
-In response to root restriction these seedlings might have altered allocation to ephemeral tissues, including fine roots or leaves to meet the changing resource requirements for A.
-Fine root mass to leaf mass ratio was instead conserved, regardless of plant size or treatment, suggesting an active biomass partitioning strategy to optimize resource gain did not occur.
+This is significant as shifts in allocation have been noted specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein].
+Surprisingly, fine root to leaf mass ratio was conserved across all treatments suggesting a functional partitioning response to optimize resource gain did not occur.
 
 \
-Alternatively, physical restriction of root proliferation could have impacted root development or morphology prior to shifts in mass partitioning.
-Here, increases in root length occurred in several of the soil volume treatments while no shifts in partitioning between fine and coarse root mass fractions were detected.
-The overall poor quality of the soil or the effects of root restriction, however, likely decreased the capacity of this morphological response to increase leaf N uptake.
-This is not surprising, as plants in containers have been shown to have different root morphology to field grown plants as roots essentially compete with themselves for nutrients [@nesmith1998effect].
-As the root mass fractions did not differ this provides evidence against an optimal foraging response in seedlings in containers.
+As partitioning to fine roots did not change this provides evidence against an optimal foraging strategy for seedlings in containers.
 This could be because lateral root development is affected by inanimate obstacles and avoiding growth towards container walls could improve the efficiency of resource allocation [@falik2005root].
 Also, the sensitivity of roots to their own exudates near obstructions may be used to adjust growth before stressful conditions occur [@semchenko2008foraging].
+Alternatively, physical restriction of root proliferation could have impacted root development or morphology prior to shifts in mass partitioning.
+Here, increases in root length where detected in several of the soil volume treatments .
+This is not surprising, as plants in containers have been shown to have different root morphology to field grown plants as roots essentially compete with themselves for nutrients [@nesmith1998effect].
+Poor soil quality and root restriction, however, likely decreased the capacity of this morphological response to increase N uptake.
 
-## Does reductions in photosynthesis explain reductions in seedling growth
+## Do reductions in photosynthesis explain reductions in seedling growth?
 Our growth model used a simple but conventional approach to drive seedling growth with fluctuations in A while treating carbon use efficiency, respiration and carbon allocation as fixed processes.
-Contrary to expectation, the model consistently overestimated growth of seedlings in containers when parameterized with an optimal LMF from control seedlings.
-A linkage between sink limitation and A, however, does not necessarily imply the same level of coordination between reduced A and growth.
+Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF.
+This provides further evidence that links between sink limitation and A do not necessarily imply the same coordination between reduced A and growth.
 These findings are important as this model reflects classical approaches in tree growth and production modelling.
-Our results indicate a need to evaluate the use of fixed processes in models which distinguish the fate of assimilate carbon within a plant.
-Doing so will provide valuable input to future plant growth models as assimilate allocation is a key component in functional-structural tree models, yet C partitioning remains a weak point [@lacointe2000carbon].
+Our results indicate a need to evaluate the use of fixed processes in models which distinguish the fate of assimilate C within a plant.
+Doing so will provide valuable input to future models as assimilate allocation is a key component in functional-structural tree models, yet C partitioning remains a weak point [@lacointe2000carbon].
 To address this issue we utilized the flexibility of this model to test plausible fates of the extra pool of non-biomass carbon unaccounted for with mass balance.
-Through this approach, similar to [@lohier2014explaining], we manipulated processes contributing to seedling C mass balance, including changes to leaf C allocation or non-leaf tissue respiration, to quantitatively test their respective influences on model predictions.
+Similar to Lohier et al.
+[-@lohier2014explaining] we manipulated processes contributing to seedling C mass balance, including changes to leaf C allocation or non-leaf tissue respiration, to quantitatively test their respective influences on model predictions.
 
@@
 Shifts in LMF could represent changes in senescence or leaf production that could not be explicitly quantified in this field study.
-As TNC accumulation due to sink limitation can lead to accelerated leaf senescence [@paul2001sink], this could explain the large declines in total leaf area of seedlings in small containers.
-Alternatively, as A was similar between soil volume treatments seedlings could have reduced leaf production to maintain laws of stoichiometry (leaf C:N ratio).
-The two-fold decrease in leaf N % in small containers from control seedlings provides support to this possible scenario.
+As TNC accumulation can lead to accelerated leaf senescence [@paul2001sink], this could explain the large declines in total leaf area of seedlings in small containers.
+Alternatively, seedlings in containers could have reduced leaf production to maintain laws of stoichiometry (leaf C:N ratio).
+The two-fold decrease in leaf N % in small containers from free seedlings provides support to this possible scenario.
 Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of A and the fate of C allocated to leaves.
@@
 Increasing rates of non-leaf respiration (M~3~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation.
-This finding is still noteworthy as it justifies an evaluation of how changes in sink activity may differentially affect respiration of component tissues.
+This finding is still noteworthy as it shows that that sink limitation could differentially affect respiration of component tissues.
+Additionally, keeping rates of respiration fixed in growth models may underestimate impacts of environmental change on tissue respiration above and belowground.
 The fraction of photosynthate used in respiration varies substantially among species and environments  and is sensitive to changes in growth rates [@Lambers2008].
 As C balance is a delicate equilibrium between fluxes of A and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions (Valentini et al.
-2000).
-Keeping rates of respiration fixed in growth models may underestimate impacts of environmental change on tissue respiration above and belowground.
-We agree with Delucia et al.
+2000).We agree with Delucia et al.
 [-@delucia2007forest] that it is likely inappropriate to assume that respiration is a constant fraction of gross primary production in models.
@@
 Second, our finding add more evidence that A and growth are not always entirely synced, an important distinction often missed in studies that manipulate source/sink activity.
-Korner [@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control A through the demand for C  Although this may be true, we argue that attempts to quantify or at least predict the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
+Korner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control A through the demand for C.
+Although this may be true, we argue that attempts to quantify or at least predict the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
 Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
@@
 
+# List of Tables
+
+**Table 1**.
+Responses of plant and leaf characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Each value reflects the mean(standard error) for each treatment.
+Seedling mass, SRL, root nitrogen and leaf $\delta$^13C values are from final harvest.
+Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6).
+Different letters represent significant differences between treatments.
+The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
+
+\
+**Table 2**.
+Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Each value reflects the mean(standard error) for each treatment.
+Units for A~max~ and R~dark~ are $\mu$mol m^-2^ s^-1^ and g~s~ are mol m^-2^ s^-1^, each at at 25 &deg;C.
+Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n = 6).
+R~dark~, J~max~ and Vc~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements.
+Different letters represent significant differences between treatments.
+The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
+
+**Table S1**. Seedling growth model default parameters.
+
+# List of Figures
+**Figure 1**. Daily maximum and minimum temperature (a), cumulative daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.
+
+\
+**Figure 2**.
+Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
+
+\
+**Figure 3**.
+Soil volume treatment means of mass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c).
+For (b) lines represent standardized major axis fitting of the log transformed allometric relationships of leaf mass fraction by treatment.
+For (c) the dashed line is the 1:1 relationship and the solid line represents the significant linear model fit (R^2^=0.81).
+
+\
+**Figure 4**.
+Soil volume treatment means &pm; standard error, across all measurement campaigns (n=6), of light saturated rates of photosynthesis at 25&deg;C.
+Different letters represent significant differences between treatments.
+
+\
+**Figure 5**.
+Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).
+Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high .
+Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~max~ as a function of starch and nitrogen.
+The marginal R^2^ (fixed effects only) was 0.37 and the conditional R^2^ (fixed and random effects) was 0.48 for the complete model.
+
+\
+**Figure 6**.
+Total carbon mass for harvested and modeled seedlings versus predicted total carbon gain after 120 days (a) and  reductions in final seedling carbon mass, both modeled and observed, as a function of the reduction in leaf photosynthesis across treatments (b).
+For (a) the dashed 1:1 identifies the difference between net total leaf carbon gain and gross seedling production.
+For (b) both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.
+
+\
+**Figure S1**.
+Sensitivity testing of seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50 % (b).
+Open and filled symbols represent default model and harvest values, while shaded symbols represent model sensitivity to each scenario by soil volume treatment.
+Both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.
+
 # Tables {.unnumbered}
+**Table 1**.
 
+\
+**Table 2**.
 <!---
@@
 
+<!---
 ```{r table1, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
@@
 The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
+-->
 
@@
 
-```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=300, dev.args=list(type="cairo")}
+```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
 source("master_scripts/airvars_plotting.R")
@@
 
-**Figure 1**. Daily maximum and minimum temperature (a), cumulative daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.
+**Figure 1**.
 
-```{r allometry, fig.width=6, fig.height=8, echo=FALSE,  dev="png", dpi=300, dev.args=list(type="cairo")}
+```{r allometry, fig.width=6, fig.height=8, echo=FALSE,  dev="png", dpi=400, dev.args=list(type="cairo")}
 source("master_scripts/allometryplotting.R")
@@
 **Figure 2**.
-Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
 
-```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=300, dev.args=list(type="cairo")}
+```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
 source("master_scripts/allocation_plotting.R")
@@
 **Figure 3**.
-Soil volume treatment means of mass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c).
-For (b) lines represent standardized major axis fitting of the log transformed allometric relationships of leaf mass fraction by treatment.
-For (c) the dashed line is the 1:1 relationship and the solid line represents the significant linear model fit (R^2^=0.81).
 
-```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=300, dev.args=list(type="cairo")}
+```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
 source("master_scripts/A_stats_plotting.R")
@@
 **Figure 4**. 
-Soil volume treatment means &pm; standard error, across all measurement campaigns (n=6), of light saturated rates of photosynthesis at 25&deg;C.
-Different letters represent significant differences between treatments.
-
-```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=300, dev.args=list(type="cairo")}
+<!---
+```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
 source("master_scripts/Amax_TNC_N_plotting2.R")
 ```  
+-->
 
 **Figure 5**.
-Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).
-Colors represent bins levels (n=5) of both leaf starch and nitrogen grouped from low to high .
-Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~max~ as a function of starch and nitrogen.
-The marginal R^2^ (fixed effects only) was 0.37 and the conditional R^2^ (fixed and random effects) was 0.48 for the complete model.
 
-```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=300, dev.args=list(type="cairo")}
+```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
 source("master_scripts/massmodel_optimize.R")
@@
 **Figure 6**.
-Total carbon mass for harvested and modeled seedlings versus predicted total carbon gain after 120 days (a) and  reductions in final seedling carbon mass, both modeled and observed, as a function of the reduction in leaf photosynthesis across treatments (b).
-For (a) the dashed 1:1 identifies the difference between net total leaf carbon gain and gross seedling production.
-For (b) both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.
 
 # Supporting Information {.unnumbered}
+**Table S1**.
 
@@
 **Figure S1**.
-Sensitivity testing of seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50% (b).
-Open and filled symbols represent default model and harvest values, while shaded symbols represent model sensitivity to each scenario by soil volume treatment.
-Both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.
-
-**Table S1** Seedling Growth Model Default Parameters
 

### 2015-07-22 master_scripts/Amax_TNC_N_plotting2.R

@@ -65,6 +65,8 @@ nitro_noTNC <- expression(Leaf~Nitrogen[TNC[free]]~~(mg~g^-1))
 
 
 #windows(10, 7)
+
+#png(filename = "manuscript/photo_chem.png", width = 8, height = 6, units = "in", res= 400)
 par(cex.axis=.96, cex.lab=1.2,mfrow=c(1,2),  oma=c(0.1,0.1,0.1,0.1), las=1)
 
 # First Panel
@@ -103,7 +105,7 @@ plot(A_mass ~ nitro_mg, data=photo_chem, type='n',ylab="", axes=FALSE, xlim=c(0,
   legend("bottomright", binlab, pch=21, text.font=1.2, inset=0.02, pt.bg=coln2,title="Leaf Starch (%)" , bty='n', cex=1.2)
 
 # dev.copy2pdf(file= "master_scripts/manuscript_figs/A_leafchem.pdf")
-# dev.off()
+ #dev.off()
 
 
 

### 2015-07-22 master_scripts/allocation_plotting.R

@@ -64,7 +64,7 @@ text(1.3, .95, "(a)", cex=1.51)
 par(mar=c(4,7,1,.3))
 plot(Mf_mod2, xlab="Stem+Root Mass  (g)" , ylab="Leaf Mass  (g)", col=palette(), pch=pchs, cex=2, lwd=2)
 legend("bottomright", leglab, pch=pchs,text.font=3, inset=0.02, title=vollab, 
-       col=palette(), bty='n',cex=1.2)
+       col=palette(), bty='n',cex=1)
 text(x=7.1, 63, "(b)", cex=1.51)
 
 #3. Fine root to leaves

### 2015-07-23 manuscript/manuscript_pve.Rmd
minor edits to manuscript

@@
 It was hypothesized that soil volume effect would be largest in the smallest containers, negatively impacting mass partitioning belowground.
-The accumulation of leaf non-structural carbohydrates, resulting from reduced sink strengh, was expected to correleltae to reductions in photosynthetic capacity.
+The accumulation of leaf non-structural carbohydrates, resulting from reduced sink strength, was expected to correlate to reductions in photosynthetic capacity.
 We observed a negative container effect on aboveground growth soon after the experiment started.
@@
 For the growth model, $\sigma$~s~ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to C~day,i~.
-All default parameters used in model simulations are reported in Table.3.
+All default parameters used in model simulations are reported in Table S1.
 
@@
 ## Growth and morphology metrics
-In this field study, colder temperatures and reductions in cumulative PPFD per day (Fig.
-`r airvarsfig`) most likely lead to the reduced growth in the free seedlings in the final weeks of the experiment (Fig.
-`r allomfig`).
+In this field study, colder temperatures and reductions in cumulative PPFD per day (Figure `r airvarsfig`) most likely lead to the reduced growth in the free seedlings in the final weeks of the experiment (Figure `r allomfig`).
 Combined with severe growth reductions in the smallest container volumes the experiment was chosen to be harvested after 120 days.
-Over this duration height, diameter, and leaf area diverged between container volumes (Fig.
-`r allomfig`).
+Over this duration height, diameter, and leaf area diverged between container volumes (Figure `r allomfig`).
 First, seedling leaf area significantly diverged between soil volumes (P < 0.026) during the 5^th^ week of the experiment.
@@
 \
-Total seedling biomass at harvest was significantly different across container volumes (P < 0.001) and with free seedlings (P < 0.001, Table.
-1).
+Total seedling biomass at harvest was significantly different across container volumes (P < 0.001) and with free seedlings (P < 0.001, Table 1).
 We analyzed the relationship between biomass growth with each fold increase in soil volume and found an increase of 34 % with a doubling of pot size, consistent with the meta-analysis of Poorter et al.
@@
 Additionally, plant biomass was highly correlated with total leaf area across all treatments (R^2^ = 0.97, P < 0.001).
-Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass within treatments was factored in the analysis (Fig.`r allocfig`a,b).
-Across all treatments, the final harvested root:shoot was conserved in these seedlings, with a slightly higher shoot than root mass on average ($\overline{x}$ = 0.904, Fig.
-`r allomfig`c).
+Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass within treatments was factored in the analysis (Figure`r allocfig`a,b).
+Across all treatments, the final harvested root:shoot was conserved in these seedlings, with a slightly higher shoot than root mass on average ($\overline{x}$ = 0.904, Figure `r allomfig`c).
 
 \
-Overall, SRL was higher in seedlings in containers compared to free seedlings but not significantly in every soil volume treatment   (Table.
-1).
-Over the duration of the experiment SLA was higher in free seedlings but was not different across containers sizes (Table.
-1, P < 0.001) and this pattern was evident in the first gas exchange measurement campaign (P < 0.001).
+Overall, SRL was higher in seedlings in containers compared to free seedlings but not significantly in every soil volume treatment   (Table 1).
+Over the duration of the experiment SLA was higher in free seedlings but was not different across containers sizes (Table 1, P < 0.001) and this pattern was evident in the first gas exchange measurement campaign (P < 0.001).
 
@@
 Leaf N % was significantly higher in free seedlings and the largest container volume at the onset of gas exchange measurements (6th week, P < 0.001).
-Over the remaining duration of the experiment the smallest container volume had a significant reduction in leaf N % compared to other soil volumes, while free seedlings maintained the highest leaf N % (Table.
-1, P < 0.001).
-Leaf starch content in the smallest container was double that of free seedlings (P=0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table.
-1).
+Over the remaining duration of the experiment the smallest container volume had a significant reduction in leaf N % compared to other soil volumes, while free seedlings maintained the highest leaf N % (Table 1, P < 0.001).
+Leaf starch content in the smallest container was double that of free seedlings (P=0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table 1).
 Differences in leaf starch between the free seedling and the smallest container were also evident during the first gas exchange campaign (P = 0.001).
@@
 A~sat~ and A~max~ were both significantly higher in the largest container volume and the free seedling at the first measurement campaign (both P < 0.001).
-Across all measurement campaigns A~sat~ (Fig.
-`r asatfig`) and A~max~ (Table 2.) were consistently higher in free seedlings than in containers (both P < 0.001).
+Across all measurement campaigns A~sat~ (Figure `r asatfig`) and A~max~ (Table 2.) were consistently higher in free seedlings than in containers (both P < 0.001).
 The interaction between photosynthetic capacity, leaf starch, and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ was highly correlated to both leaf N content and leaf starch (both P < 0.001).
-Across all measurement campaign A~max~ was higher when foliar N was also higher, usually associated with low levels of leaf starch (Fig.
-`r achemfig`a).
-A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Fig.
-`r achemfig`b)
+Across all measurement campaign A~max~ was higher when foliar N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
+A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b)
 
 \
-The photosynthetic parameters J~max~ and Vc~max~ were not different within treatments at the beginning and end of gas exchange campaigns, therefore the parameter means per treatment are reported here (Table.
-2).
+The photosynthetic parameters J~max~ and Vc~max~ were not different within treatments at the beginning and end of gas exchange campaigns, therefore the parameter means per treatment are reported here (Table 2).
 Overall, both J~max~ and Vc~max~ were significantly higher in free seedlings with little variation between soil volume treatments (P = 0.001 & 0.002, respectively).
-Leaf dark respiration rates were not significantly different across soil volumes (Table.
-2).
-The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2012reconciling] optimal stomatal conductance model, was lowest in the free seedling and was marginally different across soil volume treatments (Table.
-2).
+Leaf dark respiration rates were not significantly different across soil volumes (Table 2).
+The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2012reconciling] optimal stomatal conductance model, was lowest in the free seedling and was marginally different across soil volume treatments (Table 2).
 Predicted values of g~s~, using the g~1~ parameter, where highly correlated with observed values (R^2^ = .74, P < 0.001, data not shown).
@@
 Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 mPa across all seedlings, respectively.
-Although g~s~ in free seedlings was genearlly higher htan those in containers (Table 2.
+Although g~s~ in free seedlings was generally higher than those in containers (Table 2.
 P=0.001), the mean rates for all seedlings were high at 0.37 mol H~2~0 m^-2^ s^-1^ and did not decline significantly across the experiment duration.
-Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table.
-1).
+Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table 1).
 Combined these indices provide strong evidence that water stress was not apparent on these well-watered seedlings throughout the experiment.
@@
 Model M~0~, was able to converge on an optimum LMF (21.6 %) which predicted the mean harvest total biomass of free seedlings within 1.2 %.
-Using this optimized LMF, the total biomass of modeled seedlings with soil volume restriction (M~1~) was on average 23&pm;2.4 g C more than measured seedlings when comparing against predicted total net leaf C gain (Fig.
-`r massmodelfig`a).
-Thus, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the reductions in daily C assimilation per treatment (Fig.
-`r massmodelfig`b).
+Using this optimized LMF, the total biomass of modeled seedlings with soil volume restriction (M~1~) was on average 23&pm;2.4 g C more than measured seedlings when comparing against predicted total net leaf C gain (Figure `r massmodelfig`a).
+Thus, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the reductions in daily C assimilation per treatment (Figure `r massmodelfig`b).
 As a result, the reductions in leaf A were not sufficient enough to explain the reduction in harvested seedling biomass with soil volume restriction.
@@
 The remaining model simulations tested possible C allocation scenarios to account for this excess pool of C.
-Constraining the model by treatment-specific LMF from the final harvest (M~2~) still overestimated seedling total C by 32&pm;11.1 %, but provided the most improved model predictions (Fig.
-`r massmodelfig2`a).
-Using harvested LMF, however, does not capture the increase in senescence of seedlings in small containers (Fig.
-`r allomfig`c).
+Constraining the model by treatment-specific LMF from the final harvest (M~2~) still overestimated seedling total C by 32&pm;11.1 %, but provided the most improved model predictions (Figure `r massmodelfig2`a).
+Using harvested LMF, however, does not capture the increase in senescence of seedlings in small containers (Figure `r allomfig`c).
 Thus, the 7-61 % reduction in measured harvested leaf mass fraction from large to small soil volumes compared to the optimized LMF (M~0~) represents an underestimation of realized leaf C allocation.
-Increases of 50 % in non-leaf tissue respiration (M~3~) improved biomass estimates slightly but overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Fig.
-`r massmodelfig2`b).
+Increases of 50 % in non-leaf tissue respiration (M~3~) improved biomass estimates slightly but overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
 It was further determined that non-tissue respiration rates in modeled seedlings would need to increase by ca.
@@
 Additionally, severe reductions in A in coffee plants was not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
-Here, it is likely that reductions in A of these well watered seedlings was instead the result of limiting soil nutrients on belowground sink strength.
+It is likely that reductions in A of these well watered seedlings was instead the result of limiting soil nutrients on belowground sink strength.
 
 \
-Although the soil N pool declined evenly across all treatments leaf N was lowest in the smallest containers, suggesting that sink limitation was the greatest in these containers.
+Although the soil N pool declined evenly across all treatments leaf N was lowest in the smallest containers, suggesting sink limitation was the greatest in these containers.
 This makes sense as small containers may reduce N uptake, either from physical root restriction or decreased supply, which affects growth, Rubisco limitation, sugar metabolism, and carbohydrate partitioning between source and sink tissues [@stitt1991rising; @hermans2006plants].
@@
 2011).
-Here, declines in A~max~ where correlated with higher starch content throughout the experiment.
+Here, declines in A~max~ were correlated with higher starch content throughout the experiment.
 This agrees with findings from Equiza et a.
-(2006) where photosynthetic downregulation from reduced sink strength showed a greater correlation with starch than with sugar content in a deciduous conifer.
+(2006) where photosynthetic downregulation from reduced sink strength was more correlated with starch than sugar content in a deciduous conifer.
 As starch content in the smallest containers was nearly double that of free seedlings this suggests the response of A to sink inhibition was regulated by this accumulation, as hypothesized.
@@
 Also, the sensitivity of roots to their own exudates near obstructions may be used to adjust growth before stressful conditions occur [@semchenko2008foraging].
-Alternatively, physical restriction of root proliferation could have impacted root development or morphology prior to shifts in mass partitioning.
+Alternatively, physical restriction of root proliferation could have impacted root development and morphology prior to shifts in mass partitioning.
 Here, increases in root length where detected in several of the soil volume treatments .
-This is not surprising, as plants in containers have been shown to have different root morphology to field grown plants as roots essentially compete with themselves for nutrients [@nesmith1998effect].
+This is not surprising as plants in containers have been shown to have different root morphology to field grown plants as roots essentially compete with themselves for nutrients [@nesmith1998effect].
 Poor soil quality and root restriction, however, likely decreased the capacity of this morphological response to increase N uptake.
@@
 Increasing rates of non-leaf respiration (M~3~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation.
-This finding is still noteworthy as it shows that that sink limitation could differentially affect respiration of component tissues.
+This is still noteworthy as it shows that sink limitation could differentially affect respiration of component tissues.
 Additionally, keeping rates of respiration fixed in growth models may underestimate impacts of environmental change on tissue respiration above and belowground.
@@
 ## Conclusions
-It has long been know that conditions which affect the photosynthetic process affect growth but that there is also an interrelationship between growth and A [@sweet1966role].
+It has long been known that conditions which affect the photosynthetic process affect growth but that there is also an interrelationship between growth and A [@sweet1966role].
 Here, the fate of assimilated C available for plant growth varied between naturally sown seedlings and seedlings with belowground sink inhibition.
@@
 Second, our finding add more evidence that A and growth are not always entirely synced, an important distinction often missed in studies that manipulate source/sink activity.
-Korner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control A through the demand for C.
+K&#246rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control A through the demand for C.
 Although this may be true, we argue that attempts to quantify or at least predict the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
@@
 **Table 1**.
-Responses of plant and leaf characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.
@@
 Each value reflects the mean(standard error) for each treatment.
-Units for A~max~ and R~dark~ are $\mu$mol m^-2^ s^-1^ and g~s~ are mol m^-2^ s^-1^, each at at 25 &deg;C.
+Units for A~max~ and R~dark~ are $\mu$mol m^-2^ s^-1^ and g~s~ are mol m^-2^ s^-1^, each at 25 &deg;C.
 Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n = 6).

### 2015-07-24 manuscript/manuscript_pve.Rmd
added Remkos comments to manuscript
added references

some small scripts changes to calculate effet sizes

@@
 ```{r, echo=FALSE}
-airvarsfig <- "1"
-allomfig <- "2"
+allomfig <- "1"
+airvarsfig <- "2"
 allocfig <- "3"
@@
 Interpreting limitations to plant growth requires understanding of the balance between carbon (C) source and sink activity in order to assess C allocation and biomass partitioning.
-This study used manipulations of soil volume to test how growth is coupled to physiology, allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
-We grew seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown seedlings (free).
+This study used manipulations of soil volume to test how growth is coupled to physiology, allocation, and sink activity in Eucalyptus tereticornis seedlings.
+We grew seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown (‘free’) seedlings.
 Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
-It was hypothesized that soil volume effect would be largest in the smallest containers, negatively impacting mass partitioning belowground.
+It was hypothesized that the soil volume effect would be largest in the smallest containers, negatively impacting mass partitioning belowground.
 The accumulation of leaf non-structural carbohydrates, resulting from reduced sink strength, was expected to correlate to reductions in photosynthetic capacity.
 We observed a negative container effect on aboveground growth soon after the experiment started.
-Although growth was consistently different across soil volumes mass, partitioning to leaves, stems and roots was conserved after 120 days.
-Photosynthetic capacity was also significantly reduced in containers, and was related to both leaf nitrogen content and starch accumulation.
+Although growth was consistently different across soil volumes, partitioning to leaves, stems and roots was unchanged after 120 days.
+Photosynthetic capacity was significantly reduced in containers, and was related to both leaf nitrogen content and starch accumulation.
 We developed a seedling growth model that utilized leaf photosynthesis (A) rates to allocate daily C uptake towards mass growth of stems, leaves and roots.
 We then asked whether the observed reductions in A explained the observed differences in seedling biomass.
-We found that although belowground sink limitation resulted in the down regulation of A, these reductions were not significant enough to explain observed growth responses.
-Thus, as A and growth were not coordinated an excess pool of non-biomass C resulted in seedlings with soil volume restriction.
-This research highlights the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that A and growth are not always directly related.
+We found that although belowground sink limitation resulted in down regulation of A, these reductions were not large enough to explain observed growth responses.
+Thus, as A and growth were not coordinated, an unaccounted pool of non-biomass C resulted in seedlings with soil volume restriction.
+These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that A and growth are not always directly related.
 
@@
 As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues and organs.
-At long enough time scales photosynthesis (A) and growth must be correlated to maintain mass balance, however, at shorter temporal scales growth is not necessarily limited by the availability of recent photosynthate.
-This has led to the current debate over how strongly plant growth is controlled by either source of sink activity.
+At long enough time scales photosynthesis (A) and growth must be coordinated to maintain mass balance, however, at shorter temporal scales growth is not necessarily limited by the availability of recent photosynthate.
+This has led to the current debate on how strongly plant growth is controlled by either source of sink activity.
 Consequently, plant growth cannot always be simply determined by the photosynthesis rate, making it complex to understand and challenging to model [@fourcaud2008plant].
@@
 In woody species, the coordination of A and growth has been studied with manipulations of C source activity.
-Examples included elevated CO~2~ experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments.
-Elevated CO~2~ has been shown to increase A rates [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a conserved increase in forest biomass production [@norby2005forest].
-Evidence from elevated CO~2~ experiments, however, also reveals that even with average photosynthetic enhancement of over 30 % the growth rate only increases by around 10 %  [@kirschbaum2011does].
-In defoliation experiments, increases in A of the remaining foliage are commonly shown yet are attributed to variable mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], leaf nutrient status [@turnbull2007increased], and regulatory sugar signaling [@eyles2013whole].
+Examples included elevated CO2 experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments.
+Elevated CO~2~ has been shown to increase A rates [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a conserved stimulation of 23 % in forest biomass production [@norby2005forest].
+Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with average photosynthetic enhancement of over 30 % the growth rate only increases by around 10 % [@kirschbaum2011does].
+In partial defoliation experiments, increases in A of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], leaf nutrient status [@turnbull2007increased], and regulatory sugar signaling [@eyles2013whole].
 However, increases in A did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
@@
 This is because metabolic signaling networks, relaying information on C and N status of different tissues, can down regulate photosynthetic activity [@paul2001sink].
-If this sink inhibition of A occurs then a close coordination between declines in A and growth should be expected.
+If this sink inhibition of A occurs, a close coordination between declines in A and growth should be expected.
 Whether this photosynthetic down regulation is evident in woody species has been tested through fruit removal, girdling, and low temperatures.
@@
 An alternative experimental approach is to lower belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size.
-The advantage of this approach is it allows a large range of manipulations, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
-Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, A, water relations, nutrient uptake and respiration [@nesmith1998effect, and references therein].
+The advantage of this approach is that it allows a large range of manipulations, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
+Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, A, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
 Inadequate rooting volume may decrease C sink strength by progressively restricting root growth [@thomas1991root].
@@
 seedlings, by manipulating container size and thus rooting volume.
-Seedlings were maintained under well watered conditions in order to evaluate only the effect of restricted soil volume and the limited nutrient resource pool.
+Seedlings were maintained under well watered conditions in order to evaluate only the effect of restricted soil volume.
 We used freely-rooted seedlings as a control for the container size treatments.
@@
 
-2). As the finite pool of rooting volume and soil nutrients will decline faster in small containers we expected decreases in partitioning to fine root mass with decreasing container size.
+2). As the finite pool of rooting volume and soil nutrients will decline faster in small containers we expected changes in partitioning to fine root mass with decreasing container size.
 
 3).
-Reduced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, which is known to inhibit A.
+Reduced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, and a resulting downregulation of A.
 We therefore expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume.
@@
 tereticornis*) use the center of the container as the medium for thick roots leaving the periphery of the soil as the most active sites for fine root proliferation [@biran1980a; @biran1980b].
-This is generally hypothesized to be a different response than seedlings with no taproot.
-By using a species with tap root growth and manipulations of container length rather than width, it is believed that a more realistic test of inhibition of growth through constrained soil volume would be achieved.
-Six seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.
+By using a species with tap root growth and manipulations of container length rather than width, we believed that a more realistic test of growth inhibition through constrained soil volume would be achieved.
+Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.
 
 \
-Six container volumes were used ranging from 5 l to 35 l, with a 22.5 cm diameter, and lengths ranging from 15 to 100 cm.
+Six container volumes were used ranging from 5 L to 35 L, with a 22.5 cm diameter, and lengths ranging from 15 to 100 cm.
 Containers were constructed of PVC pipe and were filled with local top soil (described above).
-Soil in each container was packed to achieve a target soil bulk density of 1.7 g m^-3^.
+Soil in each container was packed to achieve a target soil bulk density relative to local soil conditions of 1.7 g m^-3^.
 A Imidacloprid (BAYER CropScience) insecticide tablet was planted 5 cm below the roots of each seedling.
 Containers were planted flush with the soil surface inside metal sleeves, designed to minimize excess air space between the container and outside soil while also allowing for container removal.
-This allowed for soil temperatures in containers to reflect conditions of naturally sown (free) seedlings.
+This allowed for soil temperatures in containers to reflect conditions of naturally sown ('free') seedlings.
 Each experimental block (n=7) contained a complete replicate set of container volumes as well as one free seedling, with 1 m^2^ spacing.
-For each free seedling, used as the control, a 1 m^2^ subplot was excavated to 0.5 m and replaced with the same soil used in each container.
+For each free seedling, used as the control, a 1 m^2^ subplot was excavated to the hard layer and replaced with the same soil used in each container.
 A border of root exclusion material was buried 0.25 m deep and extended 0.25 m above the ground surface around each subplot to exclude local vegetation.
@@
 \
-Plants were watered weekly or when needed, accounting for natural precipitation, to maintain soil moisture at field capacity (13-15 %).
+Plants were watered weekly or when needed to maintain soil moisture at field capacity (13-15 %).
 Drain systems were built into each pot to prevent pooling of water in containers before root expansion, from reduced root uptake, or from large rainfall events.
@@
 A lysimeter pump was then used to suction excess water, through the tubing, as needed.
-As small containers (5, 10, and 15 l) have a larger irradiation effect a simple bottom plug was used to drain excess water from the gravel compartment.
+For small containers (5, 10, and 15 L) a simple bottom plug was used to drain excess water from the gravel compartment.
 
@@
 Once the growth rate of individual plants had significantly declined a full biomass harvest was completed (May 21^st^ 2013).
-Dry mass of leaves, stems, roots and cumulative leaf area (LI-3100C Area Meter; LI-COR, Lincoln, NE, USA) was measured for each seedling.
-Mean individual leaf area for each harvested seedling was calculated by dividing cumulative leaf area by total leaf count of only fully expanded leaves.
-This value was then used to interpolate cumulative leaf area through time with weekly leaf counts.
+Dry mass of leaves, stems, roots and total leaf area (LI-3100C Area Meter; LI-COR, Lincoln, NE, USA) were measured for each seedling.
+Mean individual leaf area for each harvested seedling was calculated by dividing total leaf area by total leaf count of only fully expanded leaves.
+This value was then used to interpolate leaf area through time with weekly leaf counts.
 Root mass was collected by passing soil from each container through a 1 mm sieve, washing, separating into fine and coarse roots (<2 mm and >2 mm diameter, respectively) and then drying to a constant mass.
-Roots from the free seedlings were collected by excavating each 1 m^2^ subplot to 0.5 m depth.
+Roots from the free seedlings were collected by excavating each 1 m^2^ subplot to the hard layer and keeping only roots within the subplot.
 25 g fresh weight subsamples of washed fine roots were analyzed, using WhinoRhizo software (Regent Instruments Inc., Quebec, QC, Canada), for specific root length (SRL, m g^-1^).
@@
 \
-Photosynthetic CO~2~ response (AC~i~) curves were also developed at 25 &deg;C on a random subset of each container size (n=3) after new leaves were first produced and immediately prior to the final harvest (May 23^rd^ 2013).
-Each AC~i~ curve began at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light (above).
-From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical].
+Photosynthetic CO~2~ response (AC~i~) curves were measured at 25 &deg;C on a random subset of each container size (n=3) after new leaves were first produced and immediately prior to the final harvest (May 23^rd^ 2013).
+Each AC~i~ curve was started at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light (above).
+From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@Duursma2014] in R [@RDevelopmentCoreTeam2011]
 
@@
 Complete methods of the TNC assay are described in [@mitchell2013drought].
-Specific leaf area (SLA, m^2^ kg^-1^), for leaves sampled during gas exchange campaigns, was then calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass.
+TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^), for leaves sampled during gas exchange campaigns, was then calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass.
 
@@
 where A~c~ is the component specific biomass partitioning  to whole plant biomass (%) and $\Lambda$~c~ is component specific turnover rate.
-Due to the duration of the experiment $\Lambda$~stem~ was assumed to equal 0.
+Because we did not observe branch turnover, $\Lambda$~stem~ was assumed to equal 0.
 Total seedling biomass, per time step, was then equal to the sum of all biomass components; leaves, stems, fine roots and coarse roots.
@@
 \
-C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] in the 'plantecophys' package [@Duursma2014] in R [@RDevelopmentCoreTeam2011] with the mean photosynthetic parameters (J~max~, V~cmax~, R~d~ and g~1~) for each treatment and meteorological data from an onsite weather station.
-J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), R~d~ was empirically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2012reconciling] with observed g~s~ values.
-Examples of the photosynthesis model are described in Medlyn et al.
-[-@medlyn2002temperature] and the approach of the coupled leaf gas exchange model are described in Duursma et al [-@duursma2014peaked].
+C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package in R with the mean photosynthetic parameters (J~max~, V~cmax~, R~d~ and g~1~) for each treatment and meteorological data from an onsite weather station.
+J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), R~d~ was empirically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed g~s~ values.
+Methods of the coupled leaf gas exchange model are described in Duursma et al [-@duursma2014peaked].
 Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf A rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
@@
 tereticornis*, from Duursma et al.
-[-@duursma2012light] to run in 'YplantQMC' package in R (fix cite YplantQMC) to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
+[-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC]in R (fix cite YplantQMC) to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
 Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total A, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
@@
 ##Data analysis
-Differences in experimental parameters with soil volume were analysed by one-way analysis of variance (ANOVA) in R with individual containers as random effects and soil volume as a categorical fixed effect.
+Differences in experimental parameters with soil volume were analysed by a mixed-effects model R with individual containers as random effects and soil volume as a categorical fixed effect.
 Tukey's post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
-Mixed model ANOVAs of A~max~ and leaf chemistry were performed using the 'nlme' package [@nlme] in R and R^2^ values of mixed models were computed as in [@nakagawa2013general].
+A linear mixed effect model of Amax and leaf chemistry were performed using the 'nlme' package [@nlme] in R.
+Explained variance (R^2^) of mixed models were computed as in  [@nakagawa2013general].
 Tests of allometric relationships between biomass components were implemented using major axis regression in the 'smatr' package in R [@warton2012smatr].
-Results were considered significant at P &leq; 0.05.
+Results were considered significant at P < 0.05.
 
@@
 
-## Growth and morphology metrics
-In this field study, colder temperatures and reductions in cumulative PPFD per day (Figure `r airvarsfig`) most likely lead to the reduced growth in the free seedlings in the final weeks of the experiment (Figure `r allomfig`).
-Combined with severe growth reductions in the smallest container volumes the experiment was chosen to be harvested after 120 days.
-Over this duration height, diameter, and leaf area diverged between container volumes (Figure `r allomfig`).
-First, seedling leaf area significantly diverged between soil volumes (P < 0.026) during the 5^th^ week of the experiment.
-Following this period both height (8^th^} week) and then diameter (9^th^ week) significantly deviated across soil volumes (P < 0.002 & 0.001, respectively).
-Negative growth effects then manifested as severely reduced height gain and declining leaf area through time with small soil volumes across the final two months of the experiment.
+## Growth and morphology
+
+Plant height, diameter, and leaf area diverged between container volumes soon after start of the experiment (Figure `r allomfig`).
+First, seedling leaf area significantly diverged between soil volumes (P < 0.026) during the 5th week of the experiment.
+Following this period both height (8th) week) and then diameter (9th week) significantly deviated across soil volumes (P < 0.002 & 0.001, respectively).
+The large reductions in height gain and total leaf area in small containers continued throughout the experiment.
+In this field study, colder temperatures and reductions in total PPFD per day (Figure `r airvarsfig`) most likely led to the reduced growth in the free seedlings in the final weeks of the experiment (Figure `r allomfig`).
 Seedlings maintained diameter growth throughout the experiment, although marginal with smaller soil volumes in the final month.
@@
 Total seedling biomass at harvest was significantly different across container volumes (P < 0.001) and with free seedlings (P < 0.001, Table 1).
+On average, harvested biomas of free seedlings was 84% higher than seedlings in containers.
 We analyzed the relationship between biomass growth with each fold increase in soil volume and found an increase of 34 % with a doubling of pot size, consistent with the meta-analysis of Poorter et al.
@@
 Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass within treatments was factored in the analysis (Figure`r allocfig`a,b).
-Across all treatments, the final harvested root:shoot was conserved in these seedlings, with a slightly higher shoot than root mass on average ($\overline{x}$ = 0.904, Figure `r allomfig`c).
+Across all treatments, the final harvested root:shoot was conserved in these seedlings, with a slightly higher shoot than root mass on average ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119], Figure `r allomfig`c).
 
 \
-Overall, SRL was higher in seedlings in containers compared to free seedlings but not significantly in every soil volume treatment   (Table 1).
-Over the duration of the experiment SLA was higher in free seedlings but was not different across containers sizes (Table 1, P < 0.001) and this pattern was evident in the first gas exchange measurement campaign (P < 0.001).
+Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table 1).
+Over the duration of the experiment SLA~f~ was higher in free seedlings but was not different across containers sizes (Table 1, P < 0.001) and this pattern was evident in the first gas exchange measurement campaign (P < 0.001).
 
@@
 Over the remaining duration of the experiment the smallest container volume had a significant reduction in leaf N % compared to other soil volumes, while free seedlings maintained the highest leaf N % (Table 1, P < 0.001).
-Leaf starch content in the smallest container was double that of free seedlings (P=0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table 1).
+Leaf starch content in the smallest container was ca.
+double  that of free seedlings (P=0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table 1).
 Differences in leaf starch between the free seedling and the smallest container were also evident during the first gas exchange campaign (P = 0.001).
@@
 A~sat~ and A~max~ were both significantly higher in the largest container volume and the free seedling at the first measurement campaign (both P < 0.001).
-Across all measurement campaigns A~sat~ (Figure `r asatfig`) and A~max~ (Table 2.) were consistently higher in free seedlings than in containers (both P < 0.001).
+Across all measurement campaigns A~sat~ (Figure `r asatfig`) and A~max~ (Table 2.) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
 The interaction between photosynthetic capacity, leaf starch, and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ was highly correlated to both leaf N content and leaf starch (both P < 0.001).
 Across all measurement campaign A~max~ was higher when foliar N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
-A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b)
+A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b).
+Overall, A~max was significantly correlated with final harvest biomass across all seedlings (P < 0.001)
 
 \
-The photosynthetic parameters J~max~ and Vc~max~ were not different within treatments at the beginning and end of gas exchange campaigns, therefore the parameter means per treatment are reported here (Table 2).
-Overall, both J~max~ and Vc~max~ were significantly higher in free seedlings with little variation between soil volume treatments (P = 0.001 & 0.002, respectively).
+Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) with little variation between soil volume treatments (Table 2).
 Leaf dark respiration rates were not significantly different across soil volumes (Table 2).
-The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2012reconciling] optimal stomatal conductance model, was lowest in the free seedling and was marginally different across soil volume treatments (Table 2).
-Predicted values of g~s~, using the g~1~ parameter, where highly correlated with observed values (R^2^ = .74, P < 0.001, data not shown).
+The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling and was marginally different across soil volume treatments (Table 2).
 
 \
-Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 mPa across all seedlings, respectively.
+Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 MPa across all seedlings, respectively.
 Although g~s~ in free seedlings was generally higher than those in containers (Table 2.
-P=0.001), the mean rates for all seedlings were high at 0.37 mol H~2~0 m^-2^ s^-1^ and did not decline significantly across the experiment duration.
+P=0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not decline significantly across the experiment duration.
 Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table 1).
-Combined these indices provide strong evidence that water stress was not apparent on these well-watered seedlings throughout the experiment.
+Combined these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment.
 Soil N % at harvest was not different across soil volumes ($\bar{x}$ = 04.5 %) and decreased approximately 3 % across all containers over the experiment duration.
@@
 ## Modelling seedling biomass
-Model M~0~, was able to converge on an optimum LMF (21.6 %) which predicted the mean harvest total biomass of free seedlings within 1.2 %.
+Model M~0~, was optimized so that the free seedling would fit as well as possible and then used to predicted biomass for seedlings in containers.
+M~0~ was able to converge on an optimum LMF (21.6 %) which predicted the mean harvest total biomass of free seedlings within 1.2 %.
 Using this optimized LMF, the total biomass of modeled seedlings with soil volume restriction (M~1~) was on average 23&pm;2.4 g C more than measured seedlings when comparing against predicted total net leaf C gain (Figure `r massmodelfig`a).
 Thus, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the reductions in daily C assimilation per treatment (Figure `r massmodelfig`b).
-As a result, the reductions in leaf A were not sufficient enough to explain the reduction in harvested seedling biomass with soil volume restriction.
-This resulted in an unexplained pool of excess C, generated from A, which was not allocated to biomass.
+As a result, the reductions in leaf A were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
 
 \
-The remaining model simulations tested possible C allocation scenarios to account for this excess pool of C.
-Constraining the model by treatment-specific LMF from the final harvest (M~2~) still overestimated seedling total C by 32&pm;11.1 %, but provided the most improved model predictions (Figure `r massmodelfig2`a).
+Next, we performed a series of model simulations to test possible C allocation scenarios to account for this excess pool of C.
+Testing the sensitivity of the model to treatment-specific absoulte LMF from the final harvest (M~2~) improved model predictions but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
 Using harvested LMF, however, does not capture the increase in senescence of seedlings in small containers (Figure `r allomfig`c).
-Thus, the 7-61 % reduction in measured harvested leaf mass fraction from large to small soil volumes compared to the optimized LMF (M~0~) represents an underestimation of realized leaf C allocation.
+Thus, the 7-61 % reduction in harvested LMF from large to small soil volumes compared to the optimized LMF (M~0~) represents an underestimation of realized leaf C allocation.
 Increases of 50 % in non-leaf tissue respiration (M~3~) improved biomass estimates slightly but overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
-It was further determined that non-tissue respiration rates in modeled seedlings would need to increase by ca.
-250 % to account for this entire pool of C.
+With M~3~, non-tissue respiration rates would need to be increased by ca.
+250% in order for mass balance to be achieved.
 
@@
 This study utilized a simple but novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling production.
-We then addressed questions regarding the coordination of A and growth by complementing empirical results with modelling approaches.
-We found that reductions in leaf A rates were not sufficient to explain observed reductions in total plant biomass production.
+We addressed questions regarding the coordination of A and growth by complementing empirical results with a carbon balance model.
+We found that reductions in leaf A across container sizes were not sufficient to explain observed reductions in total plant biomass production.
 We thus encourage the utilization of mass balance approaches and provide direction for future studies when testing factors that control plant growth under environmental change.
@@
 ## Reductions in growth and physiology under sink limitation
-As soon as seedlings became established both height and diameter growth were negatively affected by decreasing soil volume.
-This lead to the large reductions in harvested biomass in small containers when compared to free seedlings.
-These growth reductions were expected, as the impedance of root growth can cause reductions overall plant growth and activity [@mcconnaughay1991physical; @young1997mechanical].
+Soon after seedlings became established both height and diameter growth were negatively affected by decreasing soil volume.
+This led to the large reductions in biomass in small containers, compared to freely rooted seedlings.
+These growth reductions were expected, as the impedance of root growth can cause reductions in overall plant growth and activity [@mcconnaughay1991physical; @young1997mechanical].
 It has been shown that roots undergoing difficult conditions may send inhibitory signals to the shoots that affect g~s~, cell expansion, cell division and the rate of leaf appearance [@passioura2002soil].
@@
 \
-Decreases in A~sat~ paralleled the reductions in allometric growth parameters of seedlings in containers.
+Decreases in A~sat~ occurred at the same time as reductions in allometric growth parameters of seedlings in containers.
 This initially suggests a strong link between growth and an apparent down regulation of A.
@@
 \
-With high rates of g~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence of water stress inducing a limitation to A.
+With high rates of g~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence of water stress causing the reduction in A.
 This finding is consistent with other container size studies without drought treatments.
@@
 Additionally, severe reductions in A in coffee plants was not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
-It is likely that reductions in A of these well watered seedlings was instead the result of limiting soil nutrients on belowground sink strength.
+It is likely that reductions in A of these well watered seedlings was instead the result of limiting soil nutrients or barrier sensing on belowground sink strength.
 
 \
-Although the soil N pool declined evenly across all treatments leaf N was lowest in the smallest containers, suggesting sink limitation was the greatest in these containers.
-This makes sense as small containers may reduce N uptake, either from physical root restriction or decreased supply, which affects growth, Rubisco limitation, sugar metabolism, and carbohydrate partitioning between source and sink tissues [@stitt1991rising; @hermans2006plants].
+Although the soil N pool declined evenly across all treatments, leaf N was lowest in the smallest containers, suggesting sink limitation was the greatest in these containers.
+This makes sense as small containers may result in a reduction of total N uptake, either from physical root restriction or decreased supply, which will affect growth, Rubisco limitation, sugar metabolism, and carbohydrate partitioning between source and sink tissues [@stitt1991rising; @hermans2006plants].
 Mycorrhizal colonization could also have been affected in containers.
@@
 2011).
-Here, declines in A~max~ were correlated with higher starch content throughout the experiment.
-This agrees with findings from Equiza et a.
-(2006) where photosynthetic downregulation from reduced sink strength was more correlated with starch than sugar content in a deciduous conifer.
-As starch content in the smallest containers was nearly double that of free seedlings this suggests the response of A to sink inhibition was regulated by this accumulation, as hypothesized.
+Here, declines in Amax were correlated with higher starch content throughout the experiment.
+This agrees with a study on a deciduous conifer by Equiza et al.
+(2006) where photosynthetic downregulation from reduced sink strength was more correlated with starch than sugar content.
+As starch content in the smallest containers was nearly double that of free seedlings in our study, this suggests the response of A to sink inhibition was regulated by this accumulation, as hypothesized.
 
-## Mass partitioning under sink limitation
-As mass partitioning is likely controlled by the source and sink strength of all organs [@poorter2012biomass] it was important to determine what tissue components were most affected by the sink limitation.
-It was necessary to distinguish if growth was affected beyond ontogenetic constraints, by correcting for size, as biomass distribution is strongly size-dependent [@gould1966allometry; @lleonart2000removing].
-In this study, there were no significant changes in root, leaf, or stem mass fractions to reduced soil volume compared to free seedlings, outside of ontogenetic drift.
-This is significant as shifts in allocation have been noted specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein].
+## Biomass partitioning under sink limitation
+As biomass partitioning is likely controlled by the source and sink strength of all organs [@poorter2012biomass] it was important to determine which tissue components were most affected by the container size treatments.
+It was necessary to distinguish if growth was affected beyond ontogenetic constraints, by correcting for size, as biomass distribution is strongly size-dependent [@gould1966allometry; @lleonart2000removing].In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, outside of ontogenetic drift.
+This is a surprising result as shifts in allocation have been noted specifically for nutrient limitation  [@mcconnaughay1999biomass, and references therein].
 Surprisingly, fine root to leaf mass ratio was conserved across all treatments suggesting a functional partitioning response to optimize resource gain did not occur.
-
 \
@@
 Here, increases in root length where detected in several of the soil volume treatments .
-This is not surprising as plants in containers have been shown to have different root morphology to field grown plants as roots essentially compete with themselves for nutrients [@nesmith1998effect].
-Poor soil quality and root restriction, however, likely decreased the capacity of this morphological response to increase N uptake.
+This is not surprising as plants in containers have been shown to have different root morphology to field grown plants as roots essentially compete among themselves for nutrients  [@nesmith1998effect].
+The poor soil quality used in our experiment and root restriction, however, likely decreased the capacity of this morphological response to increase N uptake.
 
@@
 Our growth model used a simple but conventional approach to drive seedling growth with fluctuations in A while treating carbon use efficiency, respiration and carbon allocation as fixed processes.
-Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF.
-This provides further evidence that links between sink limitation and A do not necessarily imply the same coordination between reduced A and growth.
-These findings are important as this model reflects classical approaches in tree growth and production modelling.
+Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
+Although reductions in A~max~ and biomass were strongly correlated, as hypothesized by Poorter et al.
+[-@poorter2012pot], we provide evidence that links between sink limitation and A do not necessarily imply the same coordination between reduced A and growth.
+These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilationa and processes such as respiration are considered proportional to biomass [@le2001carbon].
 Our results indicate a need to evaluate the use of fixed processes in models which distinguish the fate of assimilate C within a plant.
-Doing so will provide valuable input to future models as assimilate allocation is a key component in functional-structural tree models, yet C partitioning remains a weak point [@lacointe2000carbon].
+Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven  plant growth models, yet C partitioning remains a key weakness  [@lacointe2000carbon].
 To address this issue we utilized the flexibility of this model to test plausible fates of the extra pool of non-biomass carbon unaccounted for with mass balance.
@@
 \
-Altering the LMF from that of the optimized seedling controls (M~2~) improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond A.
-The observed sub-optimal decrease LMF with increasing soil volume restriction has several possible explanations.
-Shifts in LMF could represent changes in senescence or leaf production that could not be explicitly quantified in this field study.
-As TNC accumulation can lead to accelerated leaf senescence [@paul2001sink], this could explain the large declines in total leaf area of seedlings in small containers.
-Alternatively, seedlings in containers could have reduced leaf production to maintain laws of stoichiometry (leaf C:N ratio).
-The two-fold decrease in leaf N % in small containers from free seedlings provides support to this possible scenario.
+Using measured LMF from the harvest, instead of the optimized seedling control (M~2~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond A.
+The sensitivity of the model to decreases in LMF with increasing soil volume restriction has several possible explanations.
+Shifts in LMF could represent changes in senescence that could not be explicitly quantified in this field study.
+As TNC accumulation can lead to accelerated leaf senescence [@paul2001sink], this could explain the observed decline in total leaf area of seedlings in small containers.
 Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of A and the fate of C allocated to leaves.
@@
 ## Conclusions
-It has long been known that conditions which affect the photosynthetic process affect growth but that there is also an interrelationship between growth and A [@sweet1966role].
-Here, the fate of assimilated C available for plant growth varied between naturally sown seedlings and seedlings with belowground sink inhibition.
-First, this is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles but how these results actually reflect field-grown plants has seldom been studied.
-Second, our finding add more evidence that A and growth are not always entirely synced, an important distinction often missed in studies that manipulate source/sink activity.
+
+The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
+Here, although biomass partitioning was conserved our model results infer that the allocation of photosynthate between non-biomass pools was altered by sink inhibition.
+This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles but how these results actually reflect field-grown plants has seldom been studied.
+Our findings add more evidence that A and growth are not always entirely synced, an important distinction often missed in studies that manipulate source/sink activity.
 K&#246rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control A through the demand for C.
@@
 Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
-A lack of knowledge regarding C allocation restricts our ability to achieve mass balance and is a major obstacle in understanding the coordination between A and growth.
 The approach used here has the flexibility to account for multiple drivers of C allocation and provides an avenue to address future questions regarding the impact of environmental change on plant growth.
@@
 Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
-Seedling mass, SRL, root nitrogen and leaf $\delta$^13C values are from final harvest.
+Each value reflects the mean (&pm; 1 standard error) for each treatment.
+Seedling mass, SRL, root nitrogen and leaf $\delta$^13^C values are from final harvest.
 Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6).
@@
 Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
-Units for A~max~ and R~dark~ are $\mu$mol m^-2^ s^-1^ and g~s~ are mol m^-2^ s^-1^, each at 25 &deg;C.
+Each value reflects the mean (&pm; 1 standard error) for each treatment.
+Units for A~max~ and R~dark~ are $\mu$mol m^-2^ s^-1^ and g~s~ are mol m^-2^ s^-1^, each measured at 25 &deg;C.
 Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n = 6).
@@
 # List of Figures
-**Figure 1**. Daily maximum and minimum temperature (a), cumulative daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.
-
-\
-**Figure 2**.
+**Figure 1**.
 Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
@@
 \
+**Figure 2**. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.
+
+\
 **Figure 3**.
-Soil volume treatment means of mass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c).
+Soil volume treatment means of biomass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c).
 For (b) lines represent standardized major axis fitting of the log transformed allometric relationships of leaf mass fraction by treatment.
@@
 # Figures {.unnumbered}
-
-```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
-source("master_scripts/airvars_plotting.R")
+```{r allometry, fig.width=6, fig.height=8, echo=FALSE,  dev="png", dpi=400, dev.args=list(type="cairo")}
+source("master_scripts/allometryplotting.R")
 ```
@@
 
-```{r allometry, fig.width=6, fig.height=8, echo=FALSE,  dev="png", dpi=400, dev.args=list(type="cairo")}
-source("master_scripts/allometryplotting.R")
+```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+source("master_scripts/airvars_plotting.R")
 ```

### 2015-07-24 master_scripts/allocation_plotting.R

@@ -40,6 +40,7 @@ ratio <- subset(seedlingmass, select = c("ID", "volume", "fineroot", "leafmass",
   ratio$volume <- as.factor(ratio$volume)
 
 ratio_lm <- lm(log10(leafmass) ~ log10(fineroot), data=ratio)
+#confint(ratio_lm)
 
 #treatment means
 ratio_agg <- summaryBy( .~ volume , data = ratio,  FUN=c(mean,se))

### 2015-07-26 manuscript/manuscript_pve.Rmd
minor edits to manuscript

@@
 This study used manipulations of soil volume to test how growth is coupled to physiology, allocation, and sink activity in Eucalyptus tereticornis seedlings.
-We grew seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown (‘free’) seedlings.
+We grew seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown ('free') seedlings.
 Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
@@
 We found that although belowground sink limitation resulted in down regulation of A, these reductions were not large enough to explain observed growth responses.
-Thus, as A and growth were not coordinated, an unaccounted pool of non-biomass C resulted in seedlings with soil volume restriction.
+Thus, as A and growth were not coordinated, an unaccounted for pool of non-biomass C resulted in seedlings with soil volume restriction.
 These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that A and growth are not always directly related.
@@
 In woody species, the coordination of A and growth has been studied with manipulations of C source activity.
-Examples included elevated CO2 experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments.
+Examples included elevated CO~2~ experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments.
 Elevated CO~2~ has been shown to increase A rates [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a conserved stimulation of 23 % in forest biomass production [@norby2005forest].
@@
 A meta-analysis by Poorter et al.
-[-@poorter2012pot] concluded that A is the process likely to be the strongest affected by pot size and may best explain the observed effect on biomass seen in the large number of studies where containers are used.
+[-@poorter2012pot] concluded that A is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used.
 This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower C exchange and assimilate export rates [@robbins1988effect].
@@
 
-4). Last, the growth model was expected to find agreement between observed seedlings mass and mass predicted from a simple carbon balance model taking into account measured rates of photosynthesis.
+4). Last, the growth model was expected to find agreement between observed seedlings mass and mass predicted from a simple C balance model taking into account measured rates of photosynthesis.
 
@@
 Each AC~i~ curve was started at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light (above).
-From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@Duursma2014] in R [@RDevelopmentCoreTeam2011]
+From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@Duursma2014] in R [@RDevelopmentCoreTeam2011].
 
@@
 \
-Leaf TNC concentration was analyzed using a total starch assay kit (Megazyme International, Wicklow, Ireland) and includes the starch (mg g^-1^) and soluble sugar (mg g^-1^) concentrations.
+Leaf TNC concentration was analyzed using a total starch assay kit (Megazyme International, Wicklow, Ireland) and includes the starch  and soluble sugar concentrations (mg g^-1^).
 Starch was quantified using a thermostable $\alpha$-amylase and amyloglucosidase assay [@McCleary_starch] and soluble sugars were determined following the anthrone method [@ebell1969variation].
@@
 We developed a simple seedling growth model that utilized leaf A rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
-The model begins with mean initial tissue component biomass (leaf~i~, stem~i~ and root~i~) and a starting leaf area (LA~i~ measured prior to planting.
+The model begins with mean initial tissue component biomass (leaf~i~, stem~i~ and root~i~) and a starting leaf area (LA~i~) measured prior to planting.
 The initial biomass of roots was divided evenly between fine and coarse roots.
@@
 tereticornis*, from Duursma et al.
-[-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC]in R (fix cite YplantQMC) to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
+[-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
 Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total A, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
@@
 ##Data analysis
-Differences in experimental parameters with soil volume were analysed by a mixed-effects model R with individual containers as random effects and soil volume as a categorical fixed effect.
+Differences in experimental parameters with soil volume were analysed by mixed-effects models in R with individual containers as random effects and soil volume as a categorical fixed effect.
 Tukey's post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
-A linear mixed effect model of Amax and leaf chemistry were performed using the 'nlme' package [@nlme] in R.
+A linear mixed effect model of A~max~ and leaf chemistry was performed using the 'nlme' package [@nlme] in R.
 Explained variance (R^2^) of mixed models were computed as in  [@nakagawa2013general].
@@
 Plant height, diameter, and leaf area diverged between container volumes soon after start of the experiment (Figure `r allomfig`).
-First, seedling leaf area significantly diverged between soil volumes (P < 0.026) during the 5th week of the experiment.
-Following this period both height (8th) week) and then diameter (9th week) significantly deviated across soil volumes (P < 0.002 & 0.001, respectively).
+First, seedling leaf area significantly diverged between soil volumes (P < 0.026) during the 5^th^ week of the experiment.
+Following this period both height (8^th^) week) and then diameter (9^th^ week) significantly deviated across soil volumes (P < 0.002 & 0.001, respectively).
 The large reductions in height gain and total leaf area in small containers continued throughout the experiment.
@@
 Total seedling biomass at harvest was significantly different across container volumes (P < 0.001) and with free seedlings (P < 0.001, Table 1).
-On average, harvested biomas of free seedlings was 84% higher than seedlings in containers.
+On average, harvested biomass of free seedlings was 84% higher than seedlings in containers.
 We analyzed the relationship between biomass growth with each fold increase in soil volume and found an increase of 34 % with a doubling of pot size, consistent with the meta-analysis of Poorter et al.
@@
 Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass within treatments was factored in the analysis (Figure`r allocfig`a,b).
-Across all treatments, the final harvested root:shoot was conserved in these seedlings, with a slightly higher shoot than root mass on average ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119], Figure `r allomfig`c).
+Across all treatments, the final harvested root:shoot was conserved in these seedlings with a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119]) and a near identical ratio of leaf to fine root mass (Figure `r allocfig`c).
 
@@
 A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b).
-Overall, A~max was significantly correlated with final harvest biomass across all seedlings (P < 0.001)
+Overall, A~max~ was significantly correlated with final harvest biomass across all seedlings (P < 0.001)
 
@@
 Next, we performed a series of model simulations to test possible C allocation scenarios to account for this excess pool of C.
-Testing the sensitivity of the model to treatment-specific absoulte LMF from the final harvest (M~2~) improved model predictions but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
+Testing the sensitivity of the model to treatment-specific absolute LMF from the final harvest (M~2~) improved model predictions but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
 Using harvested LMF, however, does not capture the increase in senescence of seedlings in small containers (Figure `r allomfig`c).
@@
 2011).
-Here, declines in Amax were correlated with higher starch content throughout the experiment.
+Here, declines in A~max~ were correlated with higher starch content throughout the experiment.
 This agrees with a study on a deciduous conifer by Equiza et al.
@@
 As biomass partitioning is likely controlled by the source and sink strength of all organs [@poorter2012biomass] it was important to determine which tissue components were most affected by the container size treatments.
-It was necessary to distinguish if growth was affected beyond ontogenetic constraints, by correcting for size, as biomass distribution is strongly size-dependent [@gould1966allometry; @lleonart2000removing].In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, outside of ontogenetic drift.
+It was necessary to distinguish if growth was affected beyond ontogenetic constraints, by correcting for size, as biomass distribution is strongly size-dependent [@gould1966allometry; @lleonart2000removing].
+In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, outside of ontogenetic drift.
 This is a surprising result as shifts in allocation have been noted specifically for nutrient limitation  [@mcconnaughay1999biomass, and references therein].
 Surprisingly, fine root to leaf mass ratio was conserved across all treatments suggesting a functional partitioning response to optimize resource gain did not occur.
+
 \
@@
 Alternatively, physical restriction of root proliferation could have impacted root development and morphology prior to shifts in mass partitioning.
-Here, increases in root length where detected in several of the soil volume treatments .
+Here, increases in root length where detected in several of the soil volume treatments.
 This is not surprising as plants in containers have been shown to have different root morphology to field grown plants as roots essentially compete among themselves for nutrients  [@nesmith1998effect].
@@
 ## Do reductions in photosynthesis explain reductions in seedling growth?
-Our growth model used a simple but conventional approach to drive seedling growth with fluctuations in A while treating carbon use efficiency, respiration and carbon allocation as fixed processes.
+Our growth model used a simple but conventional approach to drive seedling growth with fluctuations in A while treating C use efficiency, respiration and C allocation as fixed processes.
 Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
@@
 [-@poorter2012pot], we provide evidence that links between sink limitation and A do not necessarily imply the same coordination between reduced A and growth.
-These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilationa and processes such as respiration are considered proportional to biomass [@le2001carbon].
+These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon].
 Our results indicate a need to evaluate the use of fixed processes in models which distinguish the fate of assimilate C within a plant.
 Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven  plant growth models, yet C partitioning remains a key weakness  [@lacointe2000carbon].
-To address this issue we utilized the flexibility of this model to test plausible fates of the extra pool of non-biomass carbon unaccounted for with mass balance.
+To address this issue we utilized the flexibility of this model to test plausible fates of the extra pool of non-biomass C unaccounted for with mass balance.
 Similar to Lohier et al.
@@
 Using measured LMF from the harvest, instead of the optimized seedling control (M~2~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond A.
-The sensitivity of the model to decreases in LMF with increasing soil volume restriction has several possible explanations.
-Shifts in LMF could represent changes in senescence that could not be explicitly quantified in this field study.
+The sensitivity of the model to shifts in LMF could represent changes in senescence that could not be explicitly quantified in this field study.
 As TNC accumulation can lead to accelerated leaf senescence [@paul2001sink], this could explain the observed decline in total leaf area of seedlings in small containers.
@@
 As C balance is a delicate equilibrium between fluxes of A and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions (Valentini et al.
-2000).We agree with Delucia et al.
+2000).
+We agree with Delucia et al.
 [-@delucia2007forest] that it is likely inappropriate to assume that respiration is a constant fraction of gross primary production in models.
@@
 Our findings add more evidence that A and growth are not always entirely synced, an important distinction often missed in studies that manipulate source/sink activity.
-K&#246rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control A through the demand for C.
+K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control A through the demand for C.
 Although this may be true, we argue that attempts to quantify or at least predict the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.

### 2015-07-26 clean Scripts/harvest root shoot.R

@@ -1,10 +1,12 @@
 
 #read data
-source("calculated data/seedling mass.csv")
+seedlingmass<- read.csv("calculated data/seedling mass.csv") 
 
 
 #subset with data for root:shoot comparisons
 ratio <- subset(seedlingmass, select = c("ID", "volume", "fineroot", "leafmass", "root", "shoot"))
+
+ratio_lm <- lm(log10(leafmass) ~ log10(fineroot), data=ratio)
 
 #PLOTTING
 pchs <- c(rep(16,6),17)
@@ -31,6 +33,9 @@ ratio_agg$leafmassSE <- with(ratio_agg, leafmass.sd/sqrt(leafmass.length))
 ratio_agg$rootSE <- with(ratio_agg, root.sd/sqrt(root.length))
 ratio_agg$shootSE <- with(ratio_agg, shoot.sd/sqrt(shoot.length))
 
+##RS and leaf froot leaf means
+rs_mean <- with(ratio_agg, mean(root.mean) / mean(shoot.mean))
+fl_mean <- with(ratio_agg, mean(fineroot.mean) / mean(leafmass.mean))
 
 
 #quick plot of means, root:shoot $ leaf:froot

### 2015-07-26 master_scripts/allocation_plotting.R

@@ -1,5 +1,5 @@
 #this script is for sourcing the allocation plots into master
-source("functions and packages/startscripts.R")
+#source("functions and packages/startscripts.R")
 
 library(smatr)
 

### 2015-08-21 manuscript/manuscript_pve.Rmd
moved a random file

@@
 Leaf starch content in the smallest container was ca.
-double  that of free seedlings (P=0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table 1).
+double  that of free seedlings (P = 0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table 1).
 Differences in leaf starch between the free seedling and the smallest container were also evident during the first gas exchange campaign (P = 0.001).
@@
 Although g~s~ in free seedlings was generally higher than those in containers (Table 2.
-P=0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not decline significantly across the experiment duration.
+P = 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not decline significantly across the experiment duration.
 Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table 1).

### 2015-09-20 manuscript/manuscript_pve.Rmd
space fix
edits to manuscript from MT

@@
 ---
-title: "Effects of below-ground sink limitation on growth and carbon balance of Eucalyptus seedlings"
+title: "Below-ground sink limitation alters growth and carbon balance of Eucalyptus seedlings"
 author: ""
@@
 Interpreting limitations to plant growth requires understanding of the balance between carbon (C) source and sink activity in order to assess C allocation and biomass partitioning.
-This study used manipulations of soil volume to test how growth is coupled to physiology, allocation, and sink activity in Eucalyptus tereticornis seedlings.
-We grew seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown ('free') seedlings.
+This study used manipulations of soil volume to test how growth is coupled to physiology, allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
+We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown ('free') seedlings.
 Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
 It was hypothesized that the soil volume effect would be largest in the smallest containers, negatively impacting mass partitioning belowground.
-The accumulation of leaf non-structural carbohydrates, resulting from reduced sink strength, was expected to correlate to reductions in photosynthetic capacity.
-We observed a negative container effect on aboveground growth soon after the experiment started.
+An accumulation of leaf non-structural carbohydrates, resulting from reduced belowground sink strength, was expected to correlate to reductions in photosynthetic capacity.
+We observed a negative effect of contatiner volume on aboveground growth soon after the experiment started.
 Although growth was consistently different across soil volumes, partitioning to leaves, stems and roots was unchanged after 120 days.
@@
 We found that although belowground sink limitation resulted in down regulation of A, these reductions were not large enough to explain observed growth responses.
-Thus, as A and growth were not coordinated, an unaccounted for pool of non-biomass C resulted in seedlings with soil volume restriction.
+Thus, as A and growth were not tightly coordinated, an unaccounted for pool of non-biomass C resulted in seedlings with soil volume restriction.
 These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that A and growth are not always directly related.
@@
 
-Understanding plant growth requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
+Understanding plant growth and its relationship to C assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
 As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues and organs.
 At long enough time scales photosynthesis (A) and growth must be coordinated to maintain mass balance, however, at shorter temporal scales growth is not necessarily limited by the availability of recent photosynthate.
-This has led to the current debate on how strongly plant growth is controlled by either source of sink activity.
+This has led to the current debate on how strongly plant growth is controlled by either source or sink activity.
 Consequently, plant growth cannot always be simply determined by the photosynthesis rate, making it complex to understand and challenging to model [@fourcaud2008plant].
-Despite a wealth of studies large uncertainties still remain regarding the coordination of C supply and growth of woody species.
+Despite a wealth of studies, large uncertainties still remain regarding the coordination of C supply and growth of woody species.
 
@@
 Examples included elevated CO~2~ experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments.
-Elevated CO~2~ has been shown to increase A rates [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a conserved stimulation of 23 % in forest biomass production [@norby2005forest].
-Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with average photosynthetic enhancement of over 30 % the growth rate only increases by around 10 % [@kirschbaum2011does].
+Elevated CO~2~ has been shown to increase A rates [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a stimulation of 23 % in forest biomass production [@norby2005forest].
+Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
 In partial defoliation experiments, increases in A of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], leaf nutrient status [@turnbull2007increased], and regulatory sugar signaling [@eyles2013whole].

### 2015-09-23 manuscript/manuscript_pve.Rmd
edits to manuscript MT

@@
 
-Interpreting limitations to plant growth requires understanding of the balance between carbon (C) source and sink activity in order to assess C allocation and biomass partitioning.
+Interpreting limitations to plant growth requires understanding of the balance between carbon (C) source and sink activity.
 This study used manipulations of soil volume to test how growth is coupled to physiology, allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
@@
 We observed a negative effect of contatiner volume on aboveground growth soon after the experiment started.
-Although growth was consistently different across soil volumes, partitioning to leaves, stems and roots was unchanged after 120 days.
+Although growth was consistently different across soil volumes, dry mass partitioning to leaves, stems and roots was unchanged after 120 days.
 Photosynthetic capacity was significantly reduced in containers, and was related to both leaf nitrogen content and starch accumulation.
-We developed a seedling growth model that utilized leaf photosynthesis (A) rates to allocate daily C uptake towards mass growth of stems, leaves and roots.
+We developed a seedling growth model that utilized leaf photosynthesis rates (A) to allocate daily C uptake towards mass growth of stems, leaves and roots.
 We then asked whether the observed reductions in A explained the observed differences in seedling biomass.
@@
 Examples included elevated CO~2~ experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments.
-Elevated CO~2~ has been shown to increase A rates [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a stimulation of 23 % in forest biomass production [@norby2005forest].
+Elevated CO~2~ has been shown to increase A [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a stimulation of 23 % in forest biomass production [@norby2005forest].
 Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
-In partial defoliation experiments, increases in A of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], leaf nutrient status [@turnbull2007increased], and regulatory sugar signaling [@eyles2013whole].
-However, increases in A did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
+In partial defoliation experiments, increases in A of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased], and regulatory sugar signaling [@eyles2013whole].
+However, increases in A in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
 These manipulations of C source activity expose unresolved issues with how changes in A do not always infer similar responses in growth.
@@
 Alternatively, manipulating plant tissue C sinks is often used to investigate the correlation of A and growth.
-This is because metabolic signaling networks, relaying information on C and N status of different tissues, can down regulate photosynthetic activity [@paul2001sink].
-If this sink inhibition of A occurs, a close coordination between declines in A and growth should be expected.
-Whether this photosynthetic down regulation is evident in woody species has been tested through fruit removal, girdling, and low temperatures.
+This is because metabolic signaling networks, relaying information on C and N status of different tissues, can regulate photosynthetic activity [@paul2001sink].
+If sink inhibition of A occurs, a close coordination between declines in A and growth should be expected.
+Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal, phloem girdling, and low temperatures.
 In these studies, down regulation of A was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
@@
 These mixed results are not surprising as we still know little about the pathways in which plants achieve balance between assimilation, storage, and growth across temporal scales [@smith2007coordination].
-As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to large annual fruiting sinks, they tell us little about source-sink coordination in typical field conditions for woody species.
+As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to the occurence large fruiting sinks, they tell us little about source-sink coordination in typical growing conditions for woody species.
 
 \
-An alternative experimental approach is to lower belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size.
-The advantage of this approach is that it allows a large range of manipulations, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
+An alternative experimental approach is to reduce belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size.
+The advantage of this approach is that it allows a large range of treatment levels, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
 Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, A, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
 Inadequate rooting volume may decrease C sink strength by progressively restricting root growth [@thomas1991root].
-Container size studies frequently have photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
+Container size studies frequently exhibit photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
 A meta-analysis by Poorter et al.
@@
 However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].
-Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test how growth and A are coordinated.
+Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test the extent to which growth and A are coordinated.
 
@@
 seedlings, by manipulating container size and thus rooting volume.
-Seedlings were maintained under well watered conditions in order to evaluate only the effect of restricted soil volume.
+Seedlings were maintained under well watered conditions in order to isolate the effect of restricted soil volume.
 We used freely-rooted seedlings as a control for the container size treatments.
 Empirical results were combined with a simple plant growth model to simulate seedling growth with a C mass balance approach, which was then compared to observed harvested seedling mass.
-The model used whole-plant C gain, scaled from instantaneous rates of leaf A, to quantify seedling production over 120 days.
+The model used whole-plant C gain, scaled from instantaneous rates of leaf A, to quantify seedling dry mass production over the 120 day experiment.
 
@@
 
-2). As the finite pool of rooting volume and soil nutrients will decline faster in small containers we expected changes in partitioning to fine root mass with decreasing container size.
+2).
+As the finite pool of rooting volume and soil nutrients will decline faster in trees growing in small containers, we expected changes in partitioning to fine root mass to be magnified with decreasing container size.
 
@@
 
-4). Last, the growth model was expected to find agreement between observed seedlings mass and mass predicted from a simple C balance model taking into account measured rates of photosynthesis.
+4). Last, observed seedling mass was expected to correspond to growth model mass predicted from a simple C balance model taking into account measured rates of photosynthesis.
 
@@
 This experiment was located at the Hawkesbury Forest Experiment site in Richmond, NSW, Australia.
-Plots were located in open cover with a site history that consists of a paddock that was converted from native pasture grasses.
-Top soils at this site, used for the study, are an alluvial formation of low-fertility sandy loam soils (380 and 108 mg kg^-1^ total N and phosphorus respectively) with low organic matter (0.7 %) and low water holding capacity.
+Plots were located in an open cover paddock that was converted from native pasture grasses.
+Top soils at this site are an alluvial formation of low-fertility sandy loam soils (380 and 108 mg kg^-1^ total N and phosphorus respectively) with low organic matter (0.7 %) and low water holding capacity.
 At this site a soil hard layer exists at ~1.0 m with a transition to heavy clay soils.
@@
 *Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain cohort.
-Previous experiments have confirmed that species with tap roots (similar to *E.
+Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.Previous experiments have confirmed that species with tap roots (similar to *E.
 tereticornis*) use the center of the container as the medium for thick roots leaving the periphery of the soil as the most active sites for fine root proliferation [@biran1980a; @biran1980b].
 By using a species with tap root growth and manipulations of container length rather than width, we believed that a more realistic test of growth inhibition through constrained soil volume would be achieved.
-Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.
 
@@
 Containers were constructed of PVC pipe and were filled with local top soil (described above).
-Soil in each container was packed to achieve a target soil bulk density relative to local soil conditions of 1.7 g m^-3^.
+Soil in each container was packed to achieve a target soil bulk density that matched local soil conditions of 1.7 g m^-3^.
 A Imidacloprid (BAYER CropScience) insecticide tablet was planted 5 cm below the roots of each seedling.
 Containers were planted flush with the soil surface inside metal sleeves, designed to minimize excess air space between the container and outside soil while also allowing for container removal.
-This allowed for soil temperatures in containers to reflect conditions of naturally sown ('free') seedlings.
-Each experimental block (n=7) contained a complete replicate set of container volumes as well as one free seedling, with 1 m^2^ spacing.
+This allowed for soil temperatures in containers to reflect conditions of naturally planted ('free') seedlings.
+Each experimental block (n=7) contained a complete replicate set of six container volumes as well as one free seedling, with 1 m^2^ spacing.
 For each free seedling, used as the control, a 1 m^2^ subplot was excavated to the hard layer and replaced with the same soil used in each container.
@@
 Drain systems were built into each pot to prevent pooling of water in containers before root expansion, from reduced root uptake, or from large rainfall events.
-These conditions could lead to an anaerobic environment around the root that could hinder the uptake of water through reduced root conductance [@poorter2009causes], an undesired experimental artifact.
+Pooling of water could lead to an anaerobic environment around the root that could hinder the uptake of water through reduced root conductance [@poorter2009causes], an undesired experimental artifact.
 A collection compartment in the bottom of containers, containing gravel covered by root exclusion mesh, was used to collect excess water for 20, 25, and 35 l containers.
@@
 ## Growth and morphology metrics
-Seedlings were planted on January 21^st^ 2013 and stem height, diameter at 15 cm and leaf count were measured weekly thereafter.
-Once the growth rate of individual plants had significantly declined a full biomass harvest was completed (May 21^st^ 2013).
+Seedlings were planted in summer (January 21^st^ 2013) and stem height, diameter at 15 cm and leaf count were measured weekly thereafter.
+Once the growth rate of individual plants had significantly declined a full biomass harvest was completed abd the experiment ended (May 21^st^ 2013).
 Dry mass of leaves, stems, roots and total leaf area (LI-3100C Area Meter; LI-COR, Lincoln, NE, USA) were measured for each seedling.
-Mean individual leaf area for each harvested seedling was calculated by dividing total leaf area by total leaf count of only fully expanded leaves.
-This value was then used to interpolate leaf area through time with weekly leaf counts.
-Root mass was collected by passing soil from each container through a 1 mm sieve, washing, separating into fine and coarse roots (<2 mm and >2 mm diameter, respectively) and then drying to a constant mass.
+Mean individual leaf area for each harvested seedling was calculated by dividing total measured leaf area by total leaf count of only fully expanded leaves.
+Mean individual leaf area was then used to interpolate total seedling leaf area through time with weekly leaf counts.
+Root mass was collected by removing the roots system and passing soil from each container through a 1 mm sieve, washing, separating into fine and coarse roots (<2 mm and >2 mm diameter, respectively) and then drying to a constant mass.
 Roots from the free seedlings were collected by excavating each 1 m^2^ subplot to the hard layer and keeping only roots within the subplot.
@@
 ## Photosynthetic parameters
-Leaf gas exchange measurements were performed bi-weekly at saturating light (A~sat~) and saturating light and [CO~2~] (A~max~) on new fully expanded leaves.
-Measurements were initiated only after sufficient new leaf growth occurred (March 17^th^, 2013), approximately 6 weeks following planting, and continued until the biomass harvest.
-Leaf level gas exchange was measured with a standard leaf chamber equipped with blue-red light emitting diodes using a portable gas exchange system (LI-6400, LI-COR, Lincoln, NE, USA).
+Leaf gas exchange measurements were performed fortnightly at saturating light (A~sat~) and saturating light and [CO~2~] (A~max~) on new fully expanded leaves.
+Measurements were initiated only after sufficient new leaf growth occurred (March 05^th^, 2013), approximately 6 weeks following planting, and continued until the biomass harvest.
+Leaf level gas exchange was measured with a standard leaf chamber (2 x 3 cm) equipped with blue-red light emitting diodes using a portable gas exchange system (LI-6400, LI-COR, Lincoln, NE, USA).
 A~sat~ measurements were made at PPFD of 1800 $\mu$mol m^-1^ s^-1^ and [CO~2~] of 400 $\mu$l l^-1^ and A~max~ with [CO~2~] of 1600 $\mu$l l^-1^ and PPFD of 1800 $\mu$mol photons m^-1^ s^-1^.
@@
 These measurements were conducted during midday (10:00-14:00 h) with leaf temperature maintained at 25 &deg;C.
-After leaves acclimated to the chamber environment, net CO~2~ assimilation rate and stomatal conductance (g~s~) were logged 5 times for both A~sat~ and A~max~.
+After CO~2~ and water vapor flux values stabalized in the leaf chamber, net CO~2~ assimilation rate and stomatal conductance (g~s~) were logged 5 times and averaged for both A~sat~ and A~max~.
 
 \
-Photosynthetic CO~2~ response (AC~i~) curves were measured at 25 &deg;C on a random subset of each container size (n=3) after new leaves were first produced and immediately prior to the final harvest (May 23^rd^ 2013).
+Photosynthetic CO~2~ response (AC~i~) curves were measured at 25 &deg;C on a random subset of each container size (n=3) after new leaves were first produced (March 13-14^th^, 2013) and prior to the final harvest (May 14-15~th~, 2013).
 Each AC~i~ curve was started at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light (above).
@@
 \
-Leaf dark respiration rates (R~d~) was measured on each seedling during the same dates as AC~i~ curves using detached leaves inside a conifer chamber attached to the Licor 6400 at least 1 hour after sundown.
+Leaf dark respiration rates (R~d~) was measured on each seedling during the same dates as AC~i~ curves.
+Freshly detached leaves were collected at least 1 hour after sundown and placed inside a conifer chamber attached to the Licor 6400.
 Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions.
@@
 $\Psi$~pd~ was measured before sunrise and $\Psi$~l~ at midday 13:00-14:30 h.
-These measurements were used as a measure of static water stress on the seedlings [@sellin1999does] and to ensure that the bulk soil water availability was high enough for plants as they became larger and roots filled the soil volume.
+These measurements were used as a measure of static water stress on the seedlings [@sellin1999does] and to ensure that the bulk soil water availability was high enough for plants to avoid water stress as they became larger and roots filled the soil volume.
 
@@
 Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of N content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
-Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis.
+Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis of N.
 Nitrogen concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of N~2~ and CO~2~).
-The percentage of N in the sample was calculated by comparison with known standards.
+The percentage of N in the sample was calculated by comparison with certified standards.
 Leaf $\delta$^13^C was analyzed  with an Delta V Advantage coupled to a Flash HT and Conflo IV isotope ratio mass spectrometer.
@@
 \
-Leaf TNC concentration was analyzed using a total starch assay kit (Megazyme International, Wicklow, Ireland) and includes the starch  and soluble sugar concentrations (mg g^-1^).
+Leaf total non-structural carbohydrate (TNC) concentration was analyzed on dried and milled leaf samples using a total starch assay kit (Megazyme International, Wicklow, Ireland) and includes the starch  and soluble sugar concentrations (mg g^-1^).
 Starch was quantified using a thermostable $\alpha$-amylase and amyloglucosidase assay [@McCleary_starch] and soluble sugars were determined following the anthrone method [@ebell1969variation].
@@
 Next, model sensitivity to different C allocation scenarios, including non-optimized treatment specific LMF and up regulation of non-leaf tissue respiration by 50 % of default values (M~2,3~, respectively), was used to improve predictions of initial model simulations from measured harvest biomass.
-For all cases, seedling production was compared between model output and harvested seedlings with treatment specific mean daily C assimilation by first scaling values to the free seedling control.
+For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment specific mean daily C assimilation by first scaling values to the free seedling control.
 
 ##Data analysis
-Differences in experimental parameters with soil volume were analysed by mixed-effects models in R with individual containers as random effects and soil volume as a categorical fixed effect.
+Differences in experimental parameters with soil volume were analysed by mixed-effects models in R with individual containers as random effects and soil volume treatment as a categorical fixed effect iwth seven levels.
 Tukey's post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
@@
 Explained variance (R^2^) of mixed models were computed as in  [@nakagawa2013general].
-Tests of allometric relationships between biomass components were implemented using major axis regression in the 'smatr' package in R [@warton2012smatr].
+Tests of allometric relationships between log-transformed biomass components were implemented using major axis regression in the 'smatr' package in R [@warton2012smatr].
 Results were considered significant at P < 0.05.
@@
 Following this period both height (8^th^) week) and then diameter (9^th^ week) significantly deviated across soil volumes (P < 0.002 & 0.001, respectively).
-The large reductions in height gain and total leaf area in small containers continued throughout the experiment.
+The large reductions in height gain and total leaf area in smaller compared to larger containers continued throughout the experiment.
 In this field study, colder temperatures and reductions in total PPFD per day (Figure `r airvarsfig`) most likely led to the reduced growth in the free seedlings in the final weeks of the experiment (Figure `r allomfig`).
@@
 Final seedling height significantly increased with increasing soil volume (P < 0.001).
-Increases in both final stem diameter (P < 0.001) and cumulative leaf area (both P < 0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling.
+Increases in both final stem diameter (P < 0.001) and cumulative leaf area (both P < 0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling treatments.
 
@@
 On average, harvested biomass of free seedlings was 84% higher than seedlings in containers.
-We analyzed the relationship between biomass growth with each fold increase in soil volume and found an increase of 34 % with a doubling of pot size, consistent with the meta-analysis of Poorter et al.
+We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, consistent with the meta-analysis of Poorter et al.
 [-@poorter2012pot].
 Additionally, plant biomass was highly correlated with total leaf area across all treatments (R^2^ = 0.97, P < 0.001).
-Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass within treatments was factored in the analysis (Figure`r allocfig`a,b).
-Across all treatments, the final harvested root:shoot was conserved in these seedlings with a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119]) and a near identical ratio of leaf to fine root mass (Figure `r allocfig`c).
+Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass across treatments was factored in the analysis (Figure `r allocfig`a,b).
+Across all treatments, the final harvest root:shoot biomass ratio was conserved in these seedlings which exhibited a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119]) and a near identical ratio of leaf to fine root mass (Figure `r allocfig`c).
 
@@
 Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table 1).
-Over the duration of the experiment SLA~f~ was higher in free seedlings but was not different across containers sizes (Table 1, P < 0.001) and this pattern was evident in the first gas exchange measurement campaign (P < 0.001).
+Over the duration of the experiment SLA~f~ was higher in free seedlings but was not different across containers sizes (Table 1, P < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (P < 0.001).
 
 ## Leaf chemistry
-Leaf N % was significantly higher in free seedlings and the largest container volume at the onset of gas exchange measurements (6th week, P < 0.001).
-Over the remaining duration of the experiment the smallest container volume had a significant reduction in leaf N % compared to other soil volumes, while free seedlings maintained the highest leaf N % (Table 1, P < 0.001).
+Leaf N % was significantly higher in free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, P < 0.001).
+Throughout the remainder of the experiment the smallest container volume had a significant reduction in leaf N % compared to other soil volumes, while free seedlings maintained the highest leaf N % (Table 1, P < 0.001).
 Leaf starch content in the smallest container was ca.
 double  that of free seedlings (P = 0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table 1).
-Differences in leaf starch between the free seedling and the smallest container were also evident during the first gas exchange campaign (P = 0.001).
+Differences in leaf starch between the free seedling and the smallest container were evident during the first gas exchange campaign (P = 0.001).
 

### 2015-09-23 manuscript/manuscript_pve.Rmd
edits MT

@@
 Interpreting limitations to plant growth requires understanding of the balance between carbon (C) source and sink activity.
-This study used manipulations of soil volume to test how growth is coupled to physiology, allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
+This study used manipulations of soil volume to test how growth is coupled to physiology, carbon allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
 We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown ('free') seedlings.
+We developed a seedling growth model that utilized leaf photosynthesis rates (A) to allocate daily C uptake towards mass growth of stems, leaves and roots.
 Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
@@
 Although growth was consistently different across soil volumes, dry mass partitioning to leaves, stems and roots was unchanged after 120 days.
-Photosynthetic capacity was significantly reduced in containers, and was related to both leaf nitrogen content and starch accumulation.
-We developed a seedling growth model that utilized leaf photosynthesis rates (A) to allocate daily C uptake towards mass growth of stems, leaves and roots.
+Photosynthetic capacity was significantly reduced in containers compared to free seedlings, and was related to both leaf nitrogen content and starch accumulation.
 We then asked whether the observed reductions in A explained the observed differences in seedling biomass.
@@
 ## Gas exchange and photosynthetic parameters
-A~sat~ and A~max~ were both significantly higher in the largest container volume and the free seedling at the first measurement campaign (both P < 0.001).
-Across all measurement campaigns A~sat~ (Figure `r asatfig`) and A~max~ (Table 2.) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
-The interaction between photosynthetic capacity, leaf starch, and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ was highly correlated to both leaf N content and leaf starch (both P < 0.001).
+A~sat~ and A~max~ were each significantly higher in the largest container volume and the free seedling treatment compared to the smaller containers at the first measurement campaign (both P < 0.001).
+Across all measurement campaigns mean A~sat~ (Figure `r asatfig`) and A~max~ (Table 2) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
+The relationships between photosynthetic capacity, leaf starch, and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001).
 Across all measurement campaign A~max~ was higher when foliar N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
@@
 \
-Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) with little variation between soil volume treatments (Table 2).
+Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table 2).
 Leaf dark respiration rates were not significantly different across soil volumes (Table 2).
-The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling and was marginally different across soil volume treatments (Table 2).
+The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table 2).
 
@@
 Although g~s~ in free seedlings was generally higher than those in containers (Table 2.
-P = 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not decline significantly across the experiment duration.
+P < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
 Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table 1).
 Combined these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment.
-Soil N % at harvest was not different across soil volumes ($\bar{x}$ = 04.5 %) and decreased approximately 3 % across all containers over the experiment duration.
+Soil N % at harvest was not different across soil volumes ($\bar{x}$ = 4.5 %) and decreased approximately 3 % across all containers over the experiment duration.
 This indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
@@
 Using this optimized LMF, the total biomass of modeled seedlings with soil volume restriction (M~1~) was on average 23&pm;2.4 g C more than measured seedlings when comparing against predicted total net leaf C gain (Figure `r massmodelfig`a).
-Thus, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the reductions in daily C assimilation per treatment (Figure `r massmodelfig`b).
-As a result, the reductions in leaf A were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
+Thus, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments (Figure `r massmodelfig`b).
+As a result, the observed reductions in leaf A with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
 
@@
 Next, we performed a series of model simulations to test possible C allocation scenarios to account for this excess pool of C.
-Testing the sensitivity of the model to treatment-specific absolute LMF from the final harvest (M~2~) improved model predictions but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
-Using harvested LMF, however, does not capture the increase in senescence of seedlings in small containers (Figure `r allomfig`c).
-Thus, the 7-61 % reduction in harvested LMF from large to small soil volumes compared to the optimized LMF (M~0~) represents an underestimation of realized leaf C allocation.
+Testing the sensitivity of the model to treatment-specific LMF from the final harvest (M~2~) improved model predictions of seedling C mass but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
+Using harvest values of LMF, however, does not capture the increase in senescence of seedlings in small containers (Figure `r allomfig`c).
+Thus, the 7-61 % reduction in harvest avlues of LMF from large to small soil volumes compared to the optimized LMF (M~0~) represents an underestimation of realized leaf C allocation.
 Increases of 50 % in non-leaf tissue respiration (M~3~) improved biomass estimates slightly but overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
@@
 # Discussion
-This study utilized a simple but novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling production.
+This study utilized a simple but novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
 We addressed questions regarding the coordination of A and growth by complementing empirical results with a carbon balance model.
@@
 These growth reductions were expected, as the impedance of root growth can cause reductions in overall plant growth and activity [@mcconnaughay1991physical; @young1997mechanical].
-It has been shown that roots undergoing difficult conditions may send inhibitory signals to the shoots that affect g~s~, cell expansion, cell division and the rate of leaf appearance [@passioura2002soil].
+It has been shown that roots subjected to environmental stress may send inhibitory signals to the shoots that affect g~s~, cell expansion, cell division and the rate of leaf appearance [@passioura2002soil].
 Here, this was evident in a large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
@@
 However, there are several possible mechanisms that can explain reduced A in small pots including nutrient content, water or reduced sink strength [@poorter2012pot].
-It was therefore necessary to examine each of these factors to distinguish if the induced belowground sink limitation actually triggered photosynthetic down regulation.
+It was therefore necessary to examine each of these factors to determine if the induced belowground sink limitation actually triggered photosynthetic down regulation.
 
 \
-With high rates of g~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence of water stress causing the reduction in A.
+With high rates of g~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in A.
 This finding is consistent with other container size studies without drought treatments.
 For example, reduced A~max~ in cotton seedlings grown at elevated CO~2~ was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased g~s~ [@thomas1991root].
-Additionally, severe reductions in A in coffee plants was not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
-It is likely that reductions in A of these well watered seedlings was instead the result of limiting soil nutrients or barrier sensing on belowground sink strength.
+Additionally, severe reductions in A in coffee plants were not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
+It is likely that reductions in A of well-watered seedlings oberved in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or barrier sensing on belowground sink strength.
 
 \
-Although the soil N pool declined evenly across all treatments, leaf N was lowest in the smallest containers, suggesting sink limitation was the greatest in these containers.
+Although the soil N % declined evenly across all treatments, leaf N was lowest in the smallest containers, suggesting sink limitation was the greatest in these containers.
 This makes sense as small containers may result in a reduction of total N uptake, either from physical root restriction or decreased supply, which will affect growth, Rubisco limitation, sugar metabolism, and carbohydrate partitioning between source and sink tissues [@stitt1991rising; @hermans2006plants].
@@
 \
-As both rooting space and resources were finite in containers, the inability of seedlings to increase the capacity of the belowground C sink resulted in the buildup of C assimilate in leaves.
+As both rooting space and resources were finite in containers, the inability of seedlings to maintain the capacity of the belowground C sink resulted in the buildup of C assimilate in leaves.
 The feedback inhibition of A from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process (Nebauer et al.
@@
 This agrees with a study on a deciduous conifer by Equiza et al.
-(2006) where photosynthetic downregulation from reduced sink strength was more correlated with starch than sugar content.
-As starch content in the smallest containers was nearly double that of free seedlings in our study, this suggests the response of A to sink inhibition was regulated by this accumulation, as hypothesized.
+(2006) where photosynthetic downregulation from reduced sink strength was correlated with starch content.
+As starch content in leaves of plants grown in the smallest containers was nearly double that of free seedlings in our study, this suggests the response of A to sink inhibition was regulated by this accumulation, as hypothesized.
 
 ## Biomass partitioning under sink limitation
-As biomass partitioning is likely controlled by the source and sink strength of all organs [@poorter2012biomass] it was important to determine which tissue components were most affected by the container size treatments.
+As biomass partitioning is likely controlled by the source and sink strength of all organs [@poorter2012biomass], it was important to determine which tissue components were most affected by the container size treatments.
 It was necessary to distinguish if growth was affected beyond ontogenetic constraints, by correcting for size, as biomass distribution is strongly size-dependent [@gould1966allometry; @lleonart2000removing].
@@
 Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high .
-Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~max~ as a function of starch and nitrogen.
+Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~mass~ as a function of starch and nitrogen.
 The marginal R^2^ (fixed effects only) was 0.37 and the conditional R^2^ (fixed and random effects) was 0.48 for the complete model.

### 2015-09-25 manuscript/manuscript_pve.Rmd
pixiedust tables into manuscript

@@
 source("functions and packages/gamplotfunctions.R")
+
+#table data
+library(pixiedust)
+table1 <- read.csv("master_scripts/pve_table1.csv")
+table2 <- read.csv("master_scripts/pve_table2.csv")
 
@@
 # Tables {.unnumbered}
-**Table 1**.
-
-\
-**Table 2**.
-<!---
-![table2](harvesttable.jpg)
-![table2](phystable.jpg)
-![table3](modeltable.jpg)
--->
-
-<!---
-```{r table1, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
-library(ascii)
-pve_data <- read.csv("master_scripts/pve_table1.csv")
-
-colnames(pve_data) <- c("Volume (L)", 
-                        "Seedling~mass~(g)", 
-                        "SLA\\textsubscript{TNC-free}~(m\\textsuperscript{2}~kg\\textsuperscript{-1})",
-                        "Leaf~Starch~(\\%)", 
-                        "Leaf~Sugars~(\\%)", 
-                        "Leaf~Nitrogen~(\\%)",
-                        "Root~Nitrogen~(\\%)",
-                        "SRL~(cm~m\\textsuperscript{-1})",
-                        "{Leaf~\\textdelta}\\textsuperscript{13}C~(\\text{\\textperthousand})")
-print(ascii(pve_data,include.rownames=FALSE),type='pandoc')
-
-```
-**Table 1.** Responses of plant and leaf characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+**Table 1**.Responses of plant and leaf characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.
-Seedling mass, SRL, root nitrogen and leaf $\delta$^13C values are from final harvest.
+Seedling mass, SRL, root nitrogen and leaf $\delta$^13^C values are from final harvest.
 Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6).
@@
 
-```{r table2, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
-library(ascii)
-phys_data <- read.csv("master_scripts/pve_table2.csv")
-colnames(phys_data) <- c("Volume (L)", 
-                        "\\textit{A}\\textsubscript{max}", 
-                        "\\textit{R}\\textsubscript{dark}",
-                        "\\textit{J}\\textsubscript{max}",
-                        "\\textit{Vc}\\textsubscript{max}",
-                        "\\textit{g}\\textsubscript{s}",
-                        "\\textit{g}\\textsubscript{1}")
-print(ascii(phys_data,include.rownames=FALSE),type='pandoc')
+```{r, echo=FALSE, warning=FALSE}
+greeks=c(alpha='\u03b1', Delta='\u0394', Sigma='\u03A3', mu='\u03bc',delta = '\u03b4')
 
+dust(table1)+
+  sprinkle_colnames("Volume (L)", 
+                        "Seedling~mass (g)", 
+                        "SLA TNC-free (m^2^ kg^-1^)",
+                        "Leaf Starch (%)", 
+                        "Leaf Sugars (%)", 
+                        "Leaf Nitrogen (%)",
+                        "Root Nitrogen (%)",
+                        "SRL (cm m^-1^)",
+                        paste0("Leaf ", greeks['delta'],"^13^C"," (\u2030)")) +
+  sprinkle(rows= 1, part="head",bold=TRUE)+
+  sprinkle_print_method("markdown")
 ```
+
+\
 **Table 2.** Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
@@
 The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
--->
+
+```{r table2, echo=FALSE, warning=FALSE}
+dust(table2)+
+  sprinkle_colnames("Volume (L)", 
+                        "A~max~", 
+                        "R~dark~",
+                        "J~max~",
+                        "Vc~max~",
+                        "g~s~",
+                        "g~1~") +
+  sprinkle(rows= 1, part="head",bold=TRUE)+
+  sprinkle_print_method("markdown")
+```
 

### 2015-09-25 master_scripts/paper_table.R

@@ -129,11 +129,11 @@ pve_table2[[7]] <- paste(pve_table2[[7]], siglet3[[4]][,1])
 pve_table2[[8]] <- paste(pve_table2[[8]], siglet3[[6]][,1])
 pve_table2[[9]] <- paste(pve_table2[[9]], siglet3[[1]][,1])
 
-pval <- as.vector(c("Container Effect (P)", 0.001, 0.001, 0.039, 0.128, 0.001, 0.015, 0.001, 0.458))
+pval_row <- c("P value","Container Effect", 0.001, 0.001, 0.039, 0.128, 0.001, 0.015, 0.001, 0.458)
 
 pve_table2$leglab <- as.character(pve_table2$leglab)
 
-pve_table3 <- rbind(pve_table2, pval)
+pve_table3 <- rbind(pve_table2, pval_row)
 
 write.csv(pve_table3, "master_scripts/pve_table1.csv", row.names=FALSE)
 

### 2015-09-25 master_scripts/phys_table.R

@@ -97,16 +97,12 @@ pve_table2 <- cbind(leglab, phys1)
 # lets <- sigletter_list[[1]][,1]
 # paste(nums, lets)
   
-pval <- as.vector(c("Container Effect (P)", 0.001, 0.039,0.001, 0.002, 0.001, 0.079))
+pval <- as.vector(c("P value","Container Effect", 0.001, 0.039,0.001, 0.002, 0.001, 0.079))
 
 pve_table2$leglab <- as.character(pve_table2$leglab)
 
 pve_table3 <- rbind(pve_table2, pval)
 
-  
-##var order= volume, amax, rd, jmax, vcmax, gs, g1, 
-##maybe add this as a additional hline in table in latex  
-  #phys_table_P <- ('     ', 0.0001, 0.03969, 0.0012, 0.0021, 0.0001, 0.0799)
   
 write.csv(pve_table3, "master_scripts/pve_table2.csv", row.names=FALSE)
 

### 2015-09-29 manuscript/manuscript_pve.Rmd
manuscript corrections from MT

@@
 As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues and organs.
-At long enough time scales photosynthesis (A) and growth must be coordinated to maintain mass balance, however, at shorter temporal scales growth is not necessarily limited by the availability of recent photosynthate.
+At long enough time scales photosynthesis (A) and growth must be coordinated to maintain mass balance, however, at shorter temporal scales growth can instead be mediated by tissue C storage pools.
 This has led to the current debate on how strongly plant growth is controlled by either source or sink activity.
@@
 If sink inhibition of A occurs, a close coordination between declines in A and growth should be expected.
-Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal, phloem girdling, and low temperatures.
+Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal, phloem girdling, and low temperatures at high elevations.
 In these studies, down regulation of A was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
@@
 Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, A, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
-Inadequate rooting volume may decrease C sink strength by progressively restricting root growth [@thomas1991root].
+Inadequate rooting volume may decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root].
 Container size studies frequently exhibit photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
@@
 2).
-As the finite pool of rooting volume and soil nutrients will decline faster in trees growing in small containers, we expected changes in partitioning to fine root mass to be magnified with decreasing container size.
+As the finite pool of rooting volume and soil nutrients will decline faster in trees growing in small containers, we expected reductions in partitioning to fine root mass to be magnified with decreasing container size.
 
@@
 *Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain cohort.
-Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.Previous experiments have confirmed that species with tap roots (similar to *E.
+Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.Previous pot experiments have confirmed that species with tap roots (similar to *E.
 tereticornis*) use the center of the container as the medium for thick roots leaving the periphery of the soil as the most active sites for fine root proliferation [@biran1980a; @biran1980b].
@@
 Containers were constructed of PVC pipe and were filled with local top soil (described above).
-Soil in each container was packed to achieve a target soil bulk density that matched local soil conditions of 1.7 g m^-3^.
+Soil in each container was packed to achieve a target soil bulk density that matched local soil conditions of 1.7 g cm^-3^.
 A Imidacloprid (BAYER CropScience) insecticide tablet was planted 5 cm below the roots of each seedling.
@@
 Plants were watered weekly or when needed to maintain soil moisture at field capacity (13-15 %).
-Drain systems were built into each pot to prevent pooling of water in containers before root expansion, from reduced root uptake, or from large rainfall events.
+Drain systems were built into each pot to prevent pooling of water throughout the experiment.
 Pooling of water could lead to an anaerobic environment around the root that could hinder the uptake of water through reduced root conductance [@poorter2009causes], an undesired experimental artifact.
@@
 For small containers (5, 10, and 15 L) a simple bottom plug was used to drain excess water from the gravel compartment.
+Each containers was inspected after every rainfall event to determine if pooling had occurred.
 
@@
 $$P_i = L\left(\frac{C_{day'i}~\sigma_s}{\epsilon_c}\right) - R$$
-where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g d^-1^), $\sigma$~s~ is a self shading parameter, $\epsilon$~c~ is a biomass conversion efficiency parameter and R is the mass based total respiration of all tissue components.
+where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g C d^-1^), $\sigma$~s~ is a self shading parameter, $\epsilon$~c~ is a biomass conversion efficiency parameter and R is the mass based total respiration of all tissue components (g C d^-1^).
 Total respiration was calculated as
@@
 $$R = \Sigma(R_c~M_c)$$
-where R~c~ is tissue respiration of fine roots, coarse roots or stems (g C g mass^-1^) and M~c~ is the standing biomass of each component (g).
+where R~c~ is tissue respiration of fine roots, coarse roots or stems (g C d^-1^) and M~c~ is the standing biomass of each component (g).
 R~leaf~ is represented in the calculation of C~day~ (described below).
@@
 Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total A, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
-The ratio of total A with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedling, independently for each treatment.
+The ratio of total A with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments.
 Next, the linear relationship between $\sigma$~s~ and total leaf area was for determined across digitized seedlings, within each treatment.
@@
 The large reductions in height gain and total leaf area in smaller compared to larger containers continued throughout the experiment.
-In this field study, colder temperatures and reductions in total PPFD per day (Figure `r airvarsfig`) most likely led to the reduced growth in the free seedlings in the final weeks of the experiment (Figure `r allomfig`).
+In this field study, colder temperatures and reductions in total PPFD per day (Figure `r airvarsfig`) likely slowed the growth of seedlings in the final weeks of the experiment (Figure `r allomfig`).
 Seedlings maintained diameter growth throughout the experiment, although marginal with smaller soil volumes in the final month.
@@
 \
-Total seedling biomass at harvest was significantly different across container volumes (P < 0.001) and with free seedlings (P < 0.001, Table 1).
+Total seedling biomass at harvest was significantly different across container volumes (P < 0.001) and between container treatments and free seedlings (P < 0.001, Table 1).
 On average, harvested biomass of free seedlings was 84% higher than seedlings in containers.
@@
 ## Gas exchange and photosynthetic parameters
-A~sat~ and A~max~ were each significantly higher in the largest container volume and the free seedling treatment compared to the smaller containers at the first measurement campaign (both P < 0.001).
+At the first measurement campaign, both A~sat~ and A~max~ were significantly higher in the free seedling treatment compared to seedlings in containers (both P < 0.001).
 Across all measurement campaigns mean A~sat~ (Figure `r asatfig`) and A~max~ (Table 2) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
 The relationships between photosynthetic capacity, leaf starch, and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001).
-Across all measurement campaign A~max~ was higher when foliar N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
+Across all measurement campaigns and treatments A~max~ was higher when foliar N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
 A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b).
-Overall, A~max~ was significantly correlated with final harvest biomass across all seedlings (P < 0.001)
+Overall, A~max~ was postively correlated with final harvest biomass across all seedlings (P < 0.001).
 
@@
 Combined these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment.
-Soil N % at harvest was not different across soil volumes ($\bar{x}$ = 4.5 %) and decreased approximately 3 % across all containers over the experiment duration.
+Soil N % at harvest was not different across soil volumes ($\bar{x}$ = 4.5 %), with minimal decreases from pre-planting value ($\bar{x}$ = 4.9 %).
 This indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
@@
 \
-Decreases in A~sat~ occurred at the same time as reductions in allometric growth parameters of seedlings in containers.
+Decreases in A~sat~ occurred at the same time as reductions in height and diameter of seedlings in containers.
 This initially suggests a strong link between growth and an apparent down regulation of A.
@@
 Additionally, severe reductions in A in coffee plants were not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
-It is likely that reductions in A of well-watered seedlings oberved in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or barrier sensing on belowground sink strength.
+It is likely that reductions in A of well-watered seedlings oberved in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
 
@@
 Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
-Although reductions in A~max~ and biomass were strongly correlated, as hypothesized by Poorter et al.
+Although reductions in A~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
 [-@poorter2012pot], we provide evidence that links between sink limitation and A do not necessarily imply the same coordination between reduced A and growth.
@@
 Increasing rates of non-leaf respiration (M~3~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation.
-This is still noteworthy as it shows that sink limitation could differentially affect respiration of component tissues.
+This is noteworthy as it shows that sink limitation could differentially affect respiration of component tissues.
 Additionally, keeping rates of respiration fixed in growth models may underestimate impacts of environmental change on tissue respiration above and belowground.
@@
 Here, although biomass partitioning was conserved our model results infer that the allocation of photosynthate between non-biomass pools was altered by sink inhibition.
-This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles but how these results actually reflect field-grown plants has seldom been studied.
+This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants has seldom been studied.
 Our findings add more evidence that A and growth are not always entirely synced, an important distinction often missed in studies that manipulate source/sink activity.
@@
 Different letters represent significant differences between treatments.
-The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
+The container effect P value represents the overall difference between seedlings with soil volume restriction and the free seedling treatment.
 

### 2015-09-30 manuscript/manuscript_pve.Rmd
edits to manuscript (including tables) from MT

@@
 table2 <- read.csv("master_scripts/pve_table2.csv")
+modeltable <- read.csv("master_scripts/modeltable.csv")
 
@@
 \
-Leaf dark respiration rates (R~d~) was measured on each seedling during the same dates as AC~i~ curves.
+Leaf dark respiration rates (R) was measured on each seedling during the same dates as AC~i~ curves.
 Freshly detached leaves were collected at least 1 hour after sundown and placed inside a conifer chamber attached to the Licor 6400.
 Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions.
-Reported values of R~d~ are standardized rates at 25 &deg;C using a Q10 value (1.86) developed for these seedlings in a separate experiment (Drake et al.
+Reported values of R are standardized rates at 25 &deg;C using a Q10 value (1.86) developed for these seedlings in a separate experiment (Drake et al.
 unpublished).
@@
 $$P_i = L\left(\frac{C_{day'i}~\sigma_s}{\epsilon_c}\right) - R$$
-where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g C d^-1^), $\sigma$~s~ is a self shading parameter, $\epsilon$~c~ is a biomass conversion efficiency parameter and R is the mass based total respiration of all tissue components (g C d^-1^).
+where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^), $\sigma$~s~ is a self shading parameter, $\epsilon$~c~ is a biomass conversion efficiency parameter and R is the mass based total respiration of all tissue components (g C d^-1^).
 Total respiration was calculated as
@@
 $$R = \Sigma(R_c~M_c)$$
-where R~c~ is tissue respiration of fine roots, coarse roots or stems (g C d^-1^) and M~c~ is the standing biomass of each component (g).
+where R~c~ is publsihed or local tissue respiration rates of fine roots, coarse roots or stems (Table S1, g C g mass ^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
 R~leaf~ is represented in the calculation of C~day~ (described below).
@@
 We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf A where sufficient to accurately predict overall seedling biomass production after 120 days.
-Each model run utilized changes in A and leaf mass fraction (LMF), with published or local values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
+Each model run utilized changes in A and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
 Cumulative net leaf C gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling C was assumed to equal half of the final mass for both modeled and observed seedlings.
@@
 Explained variance (R^2^) of mixed models were computed as in  [@nakagawa2013general].
-Tests of allometric relationships between log-transformed biomass components were implemented using major axis regression in the 'smatr' package in R [@warton2012smatr].
+Tests of allometric relationships between log-transformed biomass components were implemented using standardized major axis regression in the 'smatr' package in R [@warton2012smatr].
 Results were considered significant at P < 0.05.
@@
 This is a surprising result as shifts in allocation have been noted specifically for nutrient limitation  [@mcconnaughay1999biomass, and references therein].
-Surprisingly, fine root to leaf mass ratio was conserved across all treatments suggesting a functional partitioning response to optimize resource gain did not occur.
+Surprisingly, a constant ratio of fine root mass to leaf mass was observed across all treatments suggesting a functional partitioning response to optimize resource gain did not occur.
 
@@
 Here, increases in root length where detected in several of the soil volume treatments.
-This is not surprising as plants in containers have been shown to have different root morphology to field grown plants as roots essentially compete among themselves for nutrients  [@nesmith1998effect].
+This is not surprising as plants in containers have been shown to have different root morphology to field grown plants [@nesmith1998effect].
 The poor soil quality used in our experiment and root restriction, however, likely decreased the capacity of this morphological response to increase N uptake.
@@
 \
-**Table 2**.
-Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean (&pm; 1 standard error) for each treatment.
-Units for A~max~ and R~dark~ are $\mu$mol m^-2^ s^-1^ and g~s~ are mol m^-2^ s^-1^, each measured at 25 &deg;C.
-Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n = 6).
+**Table 2.** Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Each value reflects the mean(standard error) for each treatment.
+A~max~, R~dark~ and g~s~ are each measured at 25 &deg;C.
+Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n=6).
 R~dark~, J~max~ and Vc~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements.
 Different letters represent significant differences between treatments.
-The container effect P value represents the overall difference between seedlings with soil volume restriction and the free seedling treatment.
+The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
 
@@
   sprinkle_colnames("Volume (L)", 
-                        "Seedling~mass (g)", 
-                        "SLA TNC-free (m^2^ kg^-1^)",
+                        "Seedling mass (g)", 
+                        "SLA~TNC-free~ (m^2^ kg^-1^)",
                         "Leaf Starch (%)", 
@@
 Each value reflects the mean(standard error) for each treatment.
-Units for A~max~ and R~dark~ are $\mu$mol m^-2^ s^-1^ and g~s~ are mol m^-2^ s^-1^, each at at 25 &deg;C.
+A~max~, R~dark~ and g~s~ are each measured at 25 &deg;C.
 Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n=6).
@@
   sprinkle_colnames("Volume (L)", 
-                        "A~max~", 
-                        "R~dark~",
+                        "A~max~ ($\\mu$mol m^-2^ s^-1^)", 
+                        "R~dark~ ($\\mu$mol m^-2^ s^-1^)",
                         "J~max~",
                         "Vc~max~",
-                        "g~s~",
+                        "g~s~ (mol m^-2^ s^-1^)",
                         "g~1~") +
@@
 
-**Figure S1**.
+**Figure S1**. Seedling growth model default parameters.
+```{r tabels1, echo=FALSE, warning=FALSE}
+dust(modeltable)+
+  sprinkle(rows= 1, part="head",bold=TRUE)+
+  sprinkle_print_method("markdown")
+```
 

### 2015-10-01 manuscript/manuscript_pve.Rmd
edits from MT

@@
 However, reductions in A were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic], and stomatal limitation [@li2005photosynthesis].
-These mixed results are not surprising as we still know little about the pathways in which plants achieve balance between assimilation, storage, and growth across temporal scales [@smith2007coordination].
+These mixed results are not surprising as we still know little about the balance between assimilation, storage, and growth across temporal scales in plants [@smith2007coordination].
 As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to the occurence large fruiting sinks, they tell us little about source-sink coordination in typical growing conditions for woody species.
@@
 \
-An alternative experimental approach is to reduce belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size.
-The advantage of this approach is that it allows a large range of treatment levels, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
+An alternative experimental approach is to reduce belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size [@arp1991effects; @nesmith1998effect; @poorter2012pot].
+Possible advantages of this approach are that it allows a large range of treatment levels, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
 Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, A, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
@@
 2).
-As the finite pool of rooting volume and soil nutrients will decline faster in trees growing in small containers, we expected reductions in partitioning to fine root mass to be magnified with decreasing container size.
+As the finite pool of rooting volume and soil nutrients will decline faster in trees growing in small containers, we expected reductions in partitioning to fine root mass relative to tree size with decreasing container size.
 
 3).
-Reduced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, and a resulting downregulation of A.
+Reduced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, and a resulting down regulation of A.
 We therefore expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume.
@@
 Root mass was collected by removing the roots system and passing soil from each container through a 1 mm sieve, washing, separating into fine and coarse roots (<2 mm and >2 mm diameter, respectively) and then drying to a constant mass.
+Roots of seedlings in containers were not considered pot bound, as clusters of roots along the soil-container interface were not observed.
 Roots from the free seedlings were collected by excavating each 1 m^2^ subplot to the hard layer and keeping only roots within the subplot.
-25 g fresh weight subsamples of washed fine roots were analyzed, using WhinoRhizo software (Regent Instruments Inc., Quebec, QC, Canada), for specific root length (SRL, m g^-1^).
+For each seedling, a 25 g subsample of washed fine roots was analyzed for root length using WhinoRhizo software (Regent Instruments Inc., Quebec, QC, Canada).
+Here, specific root length (SRL) is reported as the root length divided by the dry mass of each subsample (m g^-1^).
 
@@
 $$P_i = L\left(\frac{C_{day'i}~\sigma_s}{\epsilon_c}\right) - R$$
-where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^), $\sigma$~s~ is a self shading parameter, $\epsilon$~c~ is a biomass conversion efficiency parameter and R is the mass based total respiration of all tissue components (g C d^-1^).
+where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^), $\sigma$~s~ is a self shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and R is the mass based total respiration of all tissue components (g C d^-1^).
 Total respiration was calculated as
@@
 $$R = \Sigma(R_c~M_c)$$
-where R~c~ is publsihed or local tissue respiration rates of fine roots, coarse roots or stems (Table S1, g C g mass ^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
+where R~c~ is publsihed or local tissue respiration rates of fine roots, coarse roots or stems (Table S1, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
 R~leaf~ is represented in the calculation of C~day~ (described below).
@@
 ##Data analysis
-Differences in experimental parameters with soil volume were analysed by mixed-effects models in R with individual containers as random effects and soil volume treatment as a categorical fixed effect iwth seven levels.
+Differences in experimental parameters with soil volume were analysed by mixed-effects models in R with individual containers and experimental blocks as random effects and soil volume treatment as a categorical fixed effect with seven levels.
 Tukey's post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
@@
 ## Growth and morphology
-
 Plant height, diameter, and leaf area diverged between container volumes soon after start of the experiment (Figure `r allomfig`).
-First, seedling leaf area significantly diverged between soil volumes (P < 0.026) during the 5^th^ week of the experiment.
-Following this period both height (8^th^) week) and then diameter (9^th^ week) significantly deviated across soil volumes (P < 0.002 & 0.001, respectively).
+First, seedling leaf area significantly diverged between soil volumes (P < 0.029) during the 5^th^ week of the experiment.
+Following this period both height (8^th^) week) and then diameter (9^th^ week) significantly deviated across soil volumes (P < 0.045 & 0.035, respectively).
 The large reductions in height gain and total leaf area in smaller compared to larger containers continued throughout the experiment.
@@
 [-@poorter2012pot].
-Additionally, plant biomass was highly correlated with total leaf area across all treatments (R^2^ = 0.97, P < 0.001).
+Additionally, plant biomass was postively correlated with total leaf area across all treatments (R^2^ = 0.97, P < 0.001).
 Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass across treatments was factored in the analysis (Figure `r allocfig`a,b).
@@
 \
-Next, we performed a series of model simulations to test possible C allocation scenarios to account for this excess pool of C.
+Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over predictions of seedling C mass.
 Testing the sensitivity of the model to treatment-specific LMF from the final harvest (M~2~) improved model predictions of seedling C mass but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
-Using harvest values of LMF, however, does not capture the increase in senescence of seedlings in small containers (Figure `r allomfig`c).
+Using harvest values of LMF, however, does not capture the increase in leaf turnover of seedlings in small containers (Figure `r allomfig`c).
 Thus, the 7-61 % reduction in harvest avlues of LMF from large to small soil volumes compared to the optimized LMF (M~0~) represents an underestimation of realized leaf C allocation.
@@
 This study utilized a simple but novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
-We addressed questions regarding the coordination of A and growth by complementing empirical results with a carbon balance model.
-We found that reductions in leaf A across container sizes were not sufficient to explain observed reductions in total plant biomass production.
+We addressed questions regarding the coordination of A and growth by complementing empirical results with a C balance model.
+We found that reductions in leaf A across container sizes, when integrated across the 120 day experiment, were alone insufficient to account for observed reductions in total plant biomass production.
+
 We thus encourage the utilization of mass balance approaches and provide direction for future studies when testing factors that control plant growth under environmental change.
@@
 \
-Although the soil N % declined evenly across all treatments, leaf N was lowest in the smallest containers, suggesting sink limitation was the greatest in these containers.
-This makes sense as small containers may result in a reduction of total N uptake, either from physical root restriction or decreased supply, which will affect growth, Rubisco limitation, sugar metabolism, and carbohydrate partitioning between source and sink tissues [@stitt1991rising; @hermans2006plants].
-Mycorrhizal colonization could also have been affected in containers.
-Whether unrestricted mycorrhizal recruitment facilitated the increase in leaf N uptake in free seedlings is unknown.
-Regardless of whether sink limitation occurred from root or mycorrhizal restriction, the stark contrast in leaf N between free seedlings and seedlings in containers was significantly correlated to reductions in A.
+Here, reductions in A were postively correlated with decreases in leaf N and leaf N was considerably reduced for seedlings in containers.
+Physical root restriction or decreased supply as been shown cause reductions in N uptake (citations), which could explain the observed reductions in leaf N in the smallest containers.
+Root N at the end of the experiment was on average higher in free seedlings but not consistently higher than every container volume treatment.
+Unrestricted mycorrhizal recruitment could have instead faciliated the increases in leaf N in free seedlings, but this effect is unknown.
+Combined with the fact that soil N % declined evenly across all treatments, there was no clear mechanism present to identify changes in root N uptake between free seedlings and seedlings in containers.
+In these already low quality soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
+Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the affects of belowground sink limitation on A of seedlings in containers was evidents throughout the experiment.
 
@@
 It was necessary to distinguish if growth was affected beyond ontogenetic constraints, by correcting for size, as biomass distribution is strongly size-dependent [@gould1966allometry; @lleonart2000removing].
-In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, outside of ontogenetic drift.
+In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, outside of ontogenetic drift (Figure `r allocfig`a,b).
 This is a surprising result as shifts in allocation have been noted specifically for nutrient limitation  [@mcconnaughay1999biomass, and references therein].
@@
 This could be because lateral root development is affected by inanimate obstacles and avoiding growth towards container walls could improve the efficiency of resource allocation [@falik2005root].
-Also, the sensitivity of roots to their own exudates near obstructions may be used to adjust growth before stressful conditions occur [@semchenko2008foraging].
+Also, the sensitivity of roots to their own exudates near obstructions may prevent further growth [@semchenko2008foraging].
 Alternatively, physical restriction of root proliferation could have impacted root development and morphology prior to shifts in mass partitioning.
@@
 ## Do reductions in photosynthesis explain reductions in seedling growth?
-Our growth model used a simple but conventional approach to drive seedling growth with fluctuations in A while treating C use efficiency, respiration and C allocation as fixed processes.
+Our conventional growth model used a simple approach to drive seedling growth with fluctuations in A while treating C use efficiency, respiration and C allocation as fixed processes.
 Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
@@
 Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).
-Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high .
+Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high.
 Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~mass~ as a function of starch and nitrogen.

### 2015-10-08 manuscript/manuscript_pve.Rmd
edits to manuscrupt from MT

@@
 We found that although belowground sink limitation resulted in down regulation of A, these reductions were not large enough to explain observed growth responses.
-Thus, as A and growth were not tightly coordinated, an unaccounted for pool of non-biomass C resulted in seedlings with soil volume restriction.
-These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that A and growth are not always directly related.
+Thus, as A and growth were not tightly coordinated, excess photosynthetic C not attributed to biomass resulted in seedlings with soil volume restriction.
+These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that important feedbacks exist between belowgroud sink strength and leaf C uptake.
 
-# Keywords {.unnumbered}
+## Keywords {.unnumbered}
 photosynthesis, growth, sink regulation, carbon allocation, soil volume
@@
 On average, harvested biomass of free seedlings was 84% higher than seedlings in containers.
-We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, consistent with the meta-analysis of Poorter et al.
-[-@poorter2012pot].
-Additionally, plant biomass was postively correlated with total leaf area across all treatments (R^2^ = 0.97, P < 0.001).
+Plant biomass was postively correlated with total leaf area across all treatments (R^2^ = 0.97, P < 0.001).
 Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass across treatments was factored in the analysis (Figure `r allocfig`a,b).
@@
 Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table 1).
-Over the duration of the experiment SLA~f~ was higher in free seedlings but was not different across containers sizes (Table 1, P < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (P < 0.001).
+Over the duration of the experiment SLA~f~ was higher in free seedlings, but was not different across containers sizes (Table 1, P < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (P < 0.001).
 
@@
 ## Modelling seedling biomass
-Model M~0~, was optimized so that the free seedling would fit as well as possible and then used to predicted biomass for seedlings in containers.
+The default model M~0~, was optimized so that the free seedling would fit as well as possible and then used to predicted biomass for seedlings in containers.
 M~0~ was able to converge on an optimum LMF (21.6 %) which predicted the mean harvest total biomass of free seedlings within 1.2 %.
@@
 This led to the large reductions in biomass in small containers, compared to freely rooted seedlings.
+We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, consistent with the meta-analysis of Poorter et al.
+[-@poorter2012pot].
 These growth reductions were expected, as the impedance of root growth can cause reductions in overall plant growth and activity [@mcconnaughay1991physical; @young1997mechanical].
@@
 ## Do reductions in photosynthesis explain reductions in seedling growth?
-Our conventional growth model used a simple approach to drive seedling growth with fluctuations in A while treating C use efficiency, respiration and C allocation as fixed processes.
+Our model used a simple approach to drive seedling growth with measured reductions in leaf level A , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
 Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
 Although reductions in A~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
-[-@poorter2012pot], we provide evidence that links between sink limitation and A do not necessarily imply the same coordination between reduced A and growth.
-These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon].
-Our results indicate a need to evaluate the use of fixed processes in models which distinguish the fate of assimilate C within a plant.
+[-@poorter2012pot], we provide evidence that the negative effects of sink limitation on A can not fully explain explain reduced seedling growth.
+These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
+It is possible that the overestimation of growth was due to an initial overestimation of A, however, the robust empirical based methods used to generate phtosynthetic parameters (J~max~, V~cmax~, R~d~ and g~1~) make this unlikely.
+Instead, our results indicate a need to evaluate how oversimplified representations of proceses other than A affect models which distinguish the fate of assimilate C within a plant.
 Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven  plant growth models, yet C partitioning remains a key weakness  [@lacointe2000carbon].
-To address this issue we utilized the flexibility of this model to test plausible fates of the extra pool of non-biomass C unaccounted for with mass balance.
+To address this issue, we utilized the flexibility of this model to test plausible fates of the pool of simulated non-biomass C unaccounted for with observed mass balance.
 Similar to Lohier et al.
-[-@lohier2014explaining] we manipulated processes contributing to seedling C mass balance, including changes to leaf C allocation or non-leaf tissue respiration, to quantitatively test their respective influences on model predictions.
+[-@lohier2014explaining] we manipulated processes contributing to modeled seedling C mass balance, including changes to leaf C allocation or non-leaf tissue respiration, to quantitatively test their respective influences on model predictions.
 

### 2015-10-23 manuscript/manuscript_pve.Rmd
manuscripts edits from MT

@@
 The relationships between photosynthetic capacity, leaf starch, and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001).
+We used predictions from the linear mixed effect model equation to visualize these relationship of A~max~ to either leaf N content or leaf starch at muliple bin levels (n=5) of the covariate parameter (Figure `r achemfig`).
 Across all measurement campaigns and treatments A~max~ was higher when foliar N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
@@
 This study utilized a simple but novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
-We addressed questions regarding the coordination of A and growth by complementing empirical results with a C balance model.
+We addressed questions regarding the coordination of A and growth by complementing empirical results with a C mass balance model.
 We found that reductions in leaf A across container sizes, when integrated across the 120 day experiment, were alone insufficient to account for observed reductions in total plant biomass production.
-
-We thus encourage the utilization of mass balance approaches and provide direction for future studies when testing factors that control plant growth under environmental change.
 
@@
 Using measured LMF from the harvest, instead of the optimized seedling control (M~2~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond A.
-The sensitivity of the model to shifts in LMF could represent changes in senescence that could not be explicitly quantified in this field study.
+The sensitivity of the model to shifts in LMF could represent leaf loss throughout the experiment that could not be explicitly quantified in this field study.
 As TNC accumulation can lead to accelerated leaf senescence [@paul2001sink], this could explain the observed decline in total leaf area of seedlings in small containers.
-Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of A and the fate of C allocated to leaves.
+Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of A and the fate of C allocated to growth, respiration and C storage in leaves.
 It will be the interactions between these two components that will determine the total C gain available for plant growth.
@@
 ## Conclusions
-
 The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
@@
 **Figure 3**.
-Soil volume treatment means of biomass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c).
-For (b) lines represent standardized major axis fitting of the log transformed allometric relationships of leaf mass fraction by treatment.
+Soil volume treatment means of biomass partitioning to leaves, stems, and roots at harvest (a), bivariate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c).
+For (b) lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment.
 For (c) the dashed line is the 1:1 relationship and the solid line represents the significant linear model fit (R^2^=0.81).
@@
 **Figure 4**.
-Soil volume treatment means &pm; standard error, across all measurement campaigns (n=6), of light saturated rates of photosynthesis at 25&deg;C.
+Soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25&deg;C.
 Different letters represent significant differences between treatments.

### 2015-10-24 manuscript/manuscript_pve.Rmd
manuscript edits from MT

@@
 Cumulative net leaf C gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling C was assumed to equal half of the final mass for both modeled and observed seedlings.
-First, a default model was optimized to produce a final LMF that correctly predicted both the final leaf mass and total biomass of the harvested free seedling controls (M~0~).
-This optimized LMF was then applied to model runs with treatment specific C~day~ to determine if changes in leaf A alone could accurately predict biomass (M~1~).
-Next, model sensitivity to different C allocation scenarios, including non-optimized treatment specific LMF and up regulation of non-leaf tissue respiration by 50 % of default values (M~2,3~, respectively), was used to improve predictions of initial model simulations from measured harvest biomass.
+
+First, a default model was fitted with mean photosynthetic parameters from the free seedlings and then optimized to produce a LMF that correctly predicted both the leaf mass and total biomass of the harvested free seedling (M~free~).
+This optimized LMF was then used to constrain model runs with soil volume treatment specific C~day~, while keeping tissue respiration rates and turnover parameters constant, to determine if changes in leaf A alone could predict biomass of seedlings in containers (M~pots~).
+Next, model sensitivity to different C allocation scenarios, including non-optimized treatment specific LMF and up regulation of non-leaf tissue respiration by 50 % of default values (M~s1,s2~, respectively), was used to improve predictions of model simulations compared to measured harvest biomass.
 For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment specific mean daily C assimilation by first scaling values to the free seedling control.
@@
 ## Modelling seedling biomass
-The default model M~0~, was optimized so that the free seedling would fit as well as possible and then used to predicted biomass for seedlings in containers.
-M~0~ was able to converge on an optimum LMF (21.6 %) which predicted the mean harvest total biomass of free seedlings within 1.2 %.
-Using this optimized LMF, the total biomass of modeled seedlings with soil volume restriction (M~1~) was on average 23&pm;2.4 g C more than measured seedlings when comparing against predicted total net leaf C gain (Figure `r massmodelfig`a).
+The default model M~free~, successfully optimized a LMF (21.6 %) which then allowed model to predict mean harvest total biomass of free seedlings within 1.2 %.
+Using this optimized LMF, the total biomass of modeled seedlings for each soil volume treatment (M~pots~) were on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf C gain (Figure `r massmodelfig`a).
 Thus, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments (Figure `r massmodelfig`b).
@@
 Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over predictions of seedling C mass.
-Testing the sensitivity of the model to treatment-specific LMF from the final harvest (M~2~) improved model predictions of seedling C mass but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
-Using harvest values of LMF, however, does not capture the increase in leaf turnover of seedlings in small containers (Figure `r allomfig`c).
-Thus, the 7-61 % reduction in harvest avlues of LMF from large to small soil volumes compared to the optimized LMF (M~0~) represents an underestimation of realized leaf C allocation.
-Increases of 50 % in non-leaf tissue respiration (M~3~) improved biomass estimates slightly but overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
+Testing the sensitivity of the model to observed treatment-specific LMF from the final harvest (M~s1~), which were each lower than the optmized LMF value (see Figure `r allocfig`a), improved model predictions of seedling C mass but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
+Using harvest values of LMF, however, does not capture the observed increase in leaf turnover of seedlings in small containers (Figure `r allomfig`c).
+Thus, the use of harvest LMF values for seedlings in containers in M~s1~ likely underestimates daily C allocation to leaves over the final montsh of the experiment.
+Increases of 50 % in non-leaf tissue respiration (M~s2~) improved biomass estimates slightly but overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
 With M~3~, non-tissue respiration rates would need to be increased by ca.
@@
 This initially suggests a strong link between growth and an apparent down regulation of A.
-However, there are several possible mechanisms that can explain reduced A in small pots including nutrient content, water or reduced sink strength [@poorter2012pot].
+However, there are several possible mechanisms that can explain reduced A in small containers including nutrient content, water or reduced sink strength [@poorter2012pot].
 It was therefore necessary to examine each of these factors to determine if the induced belowground sink limitation actually triggered photosynthetic down regulation.
@@
 ## Conclusions
+With a novel field-based design we detected a massive effect of container volume on seedling growth, not between containers but with naturally planted seedlings.
+This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants has seldom been studied.
+Although biomass partitioning was conserved, our empirical and model results suggest that the amount of photosynthate allocated to non-biomass pools such as TNC or respiration were likely altered by sink inhibition.
 The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
-Here, although biomass partitioning was conserved our model results infer that the allocation of photosynthate between non-biomass pools was altered by sink inhibition.
-This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants has seldom been studied.
-Our findings add more evidence that A and growth are not always entirely synced, an important distinction often missed in studies that manipulate source/sink activity.
+Our combined empirical and modeling approach shows that when non-photosynthesis parameters were kept contant changes in A were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
 K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control A through the demand for C.
-Although this may be true, we argue that attempts to quantify or at least predict the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
+Although this may be true, we results infer that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
 Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.

### 2015-10-26 manuscript/manuscript_pve.Rmd
made a new table of root data
edits from MT comments

RLD and SRL need to be double checked

leafN is no without TNC and is in manuscript

@@
 table1 <- read.csv("master_scripts/pve_table1.csv")
-table2 <- read.csv("master_scripts/pve_table2.csv")
+table2 <- read.csv("master_scripts/root_table.csv")
+table3 <- read.csv("master_scripts/pve_table2.csv")
 modeltable <- read.csv("master_scripts/modeltable.csv")
@@
 Roots from the free seedlings were collected by excavating each 1 m^2^ subplot to the hard layer and keeping only roots within the subplot.
-For each seedling, a 25 g subsample of washed fine roots was analyzed for root length using WhinoRhizo software (Regent Instruments Inc., Quebec, QC, Canada).
-Here, specific root length (SRL) is reported as the root length divided by the dry mass of each subsample (m g^-1^).
+For each seedling, a subsample of washed fine roots was analyzed for root length using WhinoRhizo software (Regent Instruments Inc., Quebec, QC, Canada).
+Specific root length (SRL) is reported as the root length divided by the dry mass of each subsample (m g^-1^).
+Root length density (RLD) is reported as the root length divided by the total volume of each container (m dm^-3^).
 
@@
 Complete methods of the TNC assay are described in [@mitchell2013drought].
-TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^), for leaves sampled during gas exchange campaigns, was then calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass.
+TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, were calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf nitrogen content.
+Similarily, TNC-free leaf N (N~f~, %) was calculated on all gas exchange leaves from leaf mass content without TNC and leaf N content.
 
@@
 \
-Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table 1).
+Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table 2). Root length density increased  (Table 2)
+
 Over the duration of the experiment SLA~f~ was higher in free seedlings, but was not different across containers sizes (Table 1, P < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (P < 0.001).
 
-## Leaf chemistry
-Leaf N % was significantly higher in free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, P < 0.001).
-Throughout the remainder of the experiment the smallest container volume had a significant reduction in leaf N % compared to other soil volumes, while free seedlings maintained the highest leaf N % (Table 1, P < 0.001).
+## Leaf and root chemistry
+Leaf N~f~ was significantly higher in free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, P < 0.001).
+Throughout the remainder of the experiment the smallest container volume had a significant reduction in leaf N~f~ compared to other soil volumes, while free seedlings maintained the highest leaf N~f~ (Table 1, P < 0.001).
 Leaf starch content in the smallest container was ca.
@@
 Differences in leaf starch between the free seedling and the smallest container were evident during the first gas exchange campaign (P = 0.001).
+Root N % was higher in free seedlings compared to seedlings in containers but only for some of the container size treatments (Table 2).
 
@@
 At the first measurement campaign, both A~sat~ and A~max~ were significantly higher in the free seedling treatment compared to seedlings in containers (both P < 0.001).
-Across all measurement campaigns mean A~sat~ (Figure `r asatfig`) and A~max~ (Table 2) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
+Across all measurement campaigns mean A~sat~ (Figure `r asatfig`) and A~max~ (Table 3) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
 The relationships between photosynthetic capacity, leaf starch, and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001).
@@
 \
-Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table 2).
-Leaf dark respiration rates were not significantly different across soil volumes (Table 2).
-The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table 2).
+Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table 3).
+Leaf dark respiration rates were not significantly different across soil volumes (Table 3).
+The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table 3).
 
@@
 Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 MPa across all seedlings, respectively.
-Although g~s~ in free seedlings was generally higher than those in containers (Table 2.
+Although g~s~ in free seedlings was generally higher than those in containers (Table 3.
 P < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
@@
 Here, reductions in A were postively correlated with decreases in leaf N and leaf N was considerably reduced for seedlings in containers.
-Physical root restriction or decreased supply as been shown cause reductions in N uptake (citations), which could explain the observed reductions in leaf N in the smallest containers.
+As leaf N reductions were detected with TNC-free leaf mass, this suggests that physical root restriction or decreased supply likely affected seedling N uptake instead of TNC dilution in leaves in the smalles containers.
 Root N at the end of the experiment was on average higher in free seedlings but not consistently higher than every container volume treatment.
@@
 This could be because lateral root development is affected by inanimate obstacles and avoiding growth towards container walls could improve the efficiency of resource allocation [@falik2005root].
-Also, the sensitivity of roots to their own exudates near obstructions may prevent further growth [@semchenko2008foraging].
+The sensitivity of roots to their own exudates near obstructions may prevent further growth [@semchenko2008foraging].
 Alternatively, physical restriction of root proliferation could have impacted root development and morphology prior to shifts in mass partitioning.
@@
 \
-Using measured LMF from the harvest, instead of the optimized seedling control (M~2~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond A.
+Using measured LMF from the harvest, instead of the optimized seedling control (M~s1~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond A.
 The sensitivity of the model to shifts in LMF could represent leaf loss throughout the experiment that could not be explicitly quantified in this field study.
@@
 \
-Increasing rates of non-leaf respiration (M~3~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation.
-This is noteworthy as it shows that sink limitation could differentially affect respiration of component tissues.
-Additionally, keeping rates of respiration fixed in growth models may underestimate impacts of environmental change on tissue respiration above and belowground.
-The fraction of photosynthate used in respiration varies substantially among species and environments  and is sensitive to changes in growth rates [@Lambers2008].
-As C balance is a delicate equilibrium between fluxes of A and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions (Valentini et al.
+Increasing rates of non-leaf respiration (M~s2~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation.
+We also show that very large increases in non-leaf respiration rates would have been required to accurately predict observed seedling biomass.
+Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], results from M~s2~ highlight a lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change.
+This is noteworthy, as C balance is a delicate equilibrium between fluxes of A and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions (Valentini et al.
 2000).
-We agree with Delucia et al.
+These results from infer that using fixed rates of respiration in models likely underestimates plant responses to sink limitation.
+Thus, we agree with Delucia et al.
 [-@delucia2007forest] that it is likely inappropriate to assume that respiration is a constant fraction of gross primary production in models.
-Our findings reveal that a combination of different mechanisms, beyond A, is likely at play in driving the observed seedling biomass response to sink manipulation.
+Our findings reveal that a combination of different mechanisms, beyond A, are likely at play in driving the observed seedling biomass response to sink manipulation.
 However, the degree to which these mechanisms will regulate a growth will undoubtedly shift across different experimental manipulations and plant species.
@@
 
-**Table 1**.
-Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean (&pm; 1 standard error) for each treatment.
-Seedling mass, SRL, root nitrogen and leaf $\delta$^13^C values are from final harvest.
+**Table 1**.Responses of plant and leaf characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Each value reflects the mean(standard error) for each treatment.
+Seedling mass and leaf $\delta$^13^C values are from final harvest.
 Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6).
 Different letters represent significant differences between treatments.
-The container effect P value represents the overall difference between seedlings with soil volume restriction and the free seedling treatment.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
 
 \
-**Table 2.** Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+**Table 2.** Responses of root characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Each value reflects the mean(standard error) for each treatment.
+All values are from the final harvest.
+Vaules for RLD are only calculated for seedlings in containers as free seedlings have potentially unlimeted soil volume to exploit.
+Different letters represent significant differences between treatments.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for RLD which represents only diffeences between seedlings in containers.
+
+\
+**Table 3.** Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.
@@
 Different letters represent significant differences between treatments.
-The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
 
@@
 Each value reflects the mean(standard error) for each treatment.
-Seedling mass, SRL, root nitrogen and leaf $\delta$^13^C values are from final harvest.
+Seedling mass and leaf $\delta$^13^C values are from final harvest.
 Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6).
 Different letters represent significant differences between treatments.
-The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
 
@@
 
-dust(table1)+
+dust(table1)%>%
   sprinkle_colnames("Volume (L)", 
@@
                         "Leaf Sugars (%)", 
-                        "Leaf Nitrogen (%)",
+                        "Leaf Nitrogen~TNC-free~ (%)",
+                        paste0("Leaf ", greeks['delta'],"^13^C"," (\u2030)")) %>%
+  sprinkle(rows= 1, part="head",bold=TRUE)%>%
+  sprinkle_print_method("markdown")
+```
+
+**Table 2.** Responses of root characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Each value reflects the mean(standard error) for each treatment.
+All values are from the final harvest.
+Vaules for RLD were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
+Different letters represent significant differences between treatments.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for RLD which represents only diffeences between seedlings in containers.
+```{r, echo=FALSE, warning=FALSE}
+dust(table2)%>%
+  sprinkle_colnames("Volume (L)", 
                         "Root Nitrogen (%)", 
-                        "SRL (cm m^-1^)",
-                        paste0("Leaf ", greeks['delta'],"^13^C"," (\u2030)")) +
-  sprinkle(rows= 1, part="head",bold=TRUE)+
+                        "SRL (m g^-1^)",
+                        "RLD (m dm^-3^)") %>%
+  sprinkle(rows= 1, part="head",bold=TRUE)%>%
   sprinkle_print_method("markdown")
@@
 \
-**Table 2.** Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+**Table 3.** Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.
@@
 Different letters represent significant differences between treatments.
-The container effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
 
 ```{r table2, echo=FALSE, warning=FALSE}
-dust(table2)+
+dust(table3)%>%
   sprinkle_colnames("Volume (L)", 
@@
                         "g~s~ (mol m^-2^ s^-1^)",
-                        "g~1~") +
-  sprinkle(rows= 1, part="head",bold=TRUE)+
+                        "g~1~") %>%
+  sprinkle(rows= 1, part="head",bold=TRUE)%>%
   sprinkle_print_method("markdown")
@@
 ```{r tabels1, echo=FALSE, warning=FALSE}
-dust(modeltable)+
-  sprinkle(rows= 1, part="head",bold=TRUE)+
+dust(modeltable)%>%
+  sprinkle(rows= 1, part="head",bold=TRUE)%>%
   sprinkle_print_method("markdown")

### 2015-10-26 Stats/leafparam_stats.R

@@ -16,6 +16,9 @@ leaf_param <- photo_chem[,c(1:3,22:23,11:12, 14:17, 7:8)]
 #leaf_param$volume <- gsub("05", "5", leaf_param$volume)
 
 
+
+
+
 ###stats on leaf parameters for manuscript
 library(visreg)
 library(multcomp)
@@ -116,6 +119,50 @@ tukey_leafN<- glht(leafN_container4, linfct = mcp(volume = "Tukey"))
   leafN_siglets <-cld(tukey_leafN)
   leafN_siglets2 <- leafN_siglets$mcletters$Letters
   
-write.csv(leafN_siglets2, "master_scripts/sigletters/sigletts_plant/sl_leafN.csv", row.names=FALSE)
+#write.csv(leafN_siglets2, "master_scripts/sigletters/sigletts_plant/sl_leafN.csv", row.names=FALSE)
+
+
+#5: leaf N no tnc
+
+
+##back calculate N content on mass basis
+##subtract tnc from leaf mass
+##redo N percentage on mass-tnc
+
+nitrodat <- leaf_param[, c(1,2,3,5,6,11:13)]
+nitrodat$starchcontent <- with(leaf_param, mass * starch)
+nitrodat$sugarcontent <- with(leaf_param, mass * sugars)
+
+nitrodat$mass_notnc <- with(nitrodat, mass - (starchcontent+sugarcontent))
+
+nitrodat$Nperc_notnc <- with(nitrodat, (1-(mass_notnc-Nmass)/mass_notnc)*100)
+
+
+###save nitro_notnc for table
+write.csv(nitrodat[,c(1:3,12)],"calculated data/leafnitrogen_notnc.csv", row.names = FALSE)
+
+
+#redo stats
+nitrodat$volume <- as.factor(nitrodat$volume)
+nitrodat$volume <- relevel(nitrodat$volume, ref="1000")
+nitrodat$block <- as.factor(gsub("-[1-9]", "", nitrodat$ID))
+
+leafNadj_mod <- lme(Nperc_notnc ~ volume, random= ~1|block/ID, data=nitrodat)
+anova(leafNadj_mod)
+summary(leafNadj_mod)
+
+tukey_leafNadj<- glht(leafNadj_mod, linfct = mcp(volume = "Tukey"))
+leafNadj_siglets <-cld(tukey_leafNadj)
[…]

### 2015-10-26 master_scripts/rootdensity.R

@@ -1,5 +1,7 @@
 ###fine root length vs leaf area
 source("functions and packages/startscripts.R")
+library(visreg)
+library(multcomp)
 
 ###root lenght density (lenght of roots per unit soil volume)
 
@@ -11,24 +13,46 @@ leafarea <- read.csv("calculated data/LA_harvest.csv")
 
 ##calculate root lenght density
 rootlength$rootlengthdensity <- with(rootlength, total_length_cm/volume) ##cm/l
+rootlength$rootlengthdensity2 <- with(rootlength, rootlengthdensity*.01) ##m/dm3
+rootlength$rootlengthdensity3 <- with(rootlength, rootlengthdensity*.00001) ##m/cm3
 
 ##now make volume a factor and relevel
 rootlength$volume <- as.factor(rootlength$volume)
 rootlength$volume <- relevel(rootlength$volume, ref="1000")
 rootlength$block <- as.factor(gsub("-[1-9]", "", rootlength$ID))
 
+write.csv(rootlength[,c(1:3,7:9,12)], "calculated data/RLD.csv", row.names=FALSE)
+
+
+###make a means dataframe with empty spaces for free and save for table----------------------------------------------------------
+
+rld_agg <- summaryBy(rootlengthdensity2 ~ volume, data=rootlength[rootlength$volume != 1000,], FUN=c(mean,se))
+emptyfree <- data.frame(volume = 1000, rootlengthdensity2.mean = "", rootlengthdensity2.se = "")
+
+rld_agg2 <- rbind(rld_agg, emptyfree)
+write.csv(rld_agg2, "calculated data/RLD_agg.csv", row.names=FALSE)
+
+
+
+
 ##is rootlength density different by soil volume-------------------------------------------------------------------------------
 
 bargraph.CI(volume, rootlengthdensity, data=rootlength)
 
-rootdensity_mod <- lme(rootlengthdensity ~ volume, random= ~1|block/ID, data=rootlength)
-anova(rootdensity_mod)
-summary(rootdensity_mod)
-library(visreg)
-library(multcomp)
-visreg(rootdensity_mod)
+###this isnt that great because soil volume is unlimited for free
+# rootdensity_mod <- lme(rootlengthdensity ~ volume, random= ~1|block/ID, data=rootlength)
+# anova(rootdensity_mod)
[…]

### 2015-10-26 rootmorph_pots.R

@@ -1,0 +1,62 @@
+source("functions and packages/startscripts.R")
+
+#read in plot design and harvest data
+plotsumm <- read.csv("raw data/plot_summary.csv")
+plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
+
+#SRL------------------------------------------------------------------------------------------------------
+srl <- read.csv("raw data/SRLmass.csv")
+srl$ID <- paste(srl$plot, srl$pot, sep = "-")
+srl <- merge(srl, plotsumm[3:4], all=TRUE)
+srl <- subset(srl, !is.na(volume))
+srl$SRL <- with(srl, (total_length_cm/100)*(srl_fw*(ss_dw/ss_fw)))
+srl$SRL2 <- with(srl, (total_length_cm/100)/(srl_fw*(ss_dw/ss_fw)))
+srl$volume <- as.factor(srl$volume)
+row.names(srl) <- NULL
+#srl <- vollab_func(srl)
+
+
+###roots from harvest
+rootharvest <- read.csv("calculated data/seedling mass.csv")
+rootharvest2 <- rootharvest[, c(1,2,8)]
+
+
+rootmorph <- merge(rootharvest2,srl)
+rootmorph$potrootlength <- with(rootmorph, (total_length_cm * fineroot)/ss_dw)
+
+rootmorph$potrootdensity <- with(rootmorph, potrootlength/volume)
+
+rootmorph$SRLpot <- with(rootmorph, (potrootlength/100)/fineroot)##m g-1
+
+rootmorph$volume <- as.factor(rootmorph$volume)
+
+with(rootmorph, boxplot(SRLpot~volume))
+
+
+
+
+##some values really high, remove to pots from boxplot of data  
+#srl_clean <- srl[srl$SRL2 <= 100,]  
+rootmorph_clean <- rootmorph[rootmorph$ID != "5-8" & rootmorph$ID != "7-8",]  
+
+
+
+#stats on RLD
+root_pots <- rootmorph[rootmorph$volume != "1000",]
+root_pots <- droplevels(root_pots)
+
+rld_container <- lme(potrootdensity ~ volume, random= ~1|ID, data=root_pots)
+anova(rld_container)
+summary(rld_container)
+
+tukey_rld<- glht(rld_container, linfct = mcp(volume = "Tukey"))
+rld_siglets <-cld(tukey_rld)
+rld_siglets2 <- rld_siglets$mcletters$Letters
[…]

### 2015-10-28 manuscript/manuscript_pve.Rmd
final edits from MT.  includes FRLD and new root table
this version sent to BEM

@@
 Interpreting limitations to plant growth requires understanding of the balance between carbon (C) source and sink activity.
-This study used manipulations of soil volume to test how growth is coupled to physiology, carbon allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
-We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown ('free') seedlings.
+This study used manipulations of soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
+We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown (free) seedlings.
 We developed a seedling growth model that utilized leaf photosynthesis rates (A) to allocate daily C uptake towards mass growth of stems, leaves and roots.
@@
 As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues and organs.
-At long enough time scales photosynthesis (A) and growth must be coordinated to maintain mass balance, however, at shorter temporal scales growth can instead be mediated by tissue C storage pools.
+At long enough time scales photosynthesis (A) and respiratory losses together determine net C balance and will be coordinated to plant growth.
+At shorter temporal scales, however, growth can instead be mediated by tissue C storage pools.
 This has led to the current debate on how strongly plant growth is controlled by either source or sink activity.
@@
 Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
-In partial defoliation experiments, increases in A of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased], and regulatory sugar signaling [@eyles2013whole].
+In partial defoliation experiments, increases in A of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
 However, increases in A in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
@@
 If sink inhibition of A occurs, a close coordination between declines in A and growth should be expected.
-Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal, phloem girdling, and low temperatures at high elevations.
+Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal, phloem girdling and low temperatures at high elevations.
 In these studies, down regulation of A was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
-However, reductions in A were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic], and stomatal limitation [@li2005photosynthesis].
-These mixed results are not surprising as we still know little about the balance between assimilation, storage, and growth across temporal scales in plants [@smith2007coordination].
+However, reductions in A were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
+These mixed results are not surprising as we still know little about the balance between assimilation, storage and growth across temporal scales in plants [@smith2007coordination].
 As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to the occurence large fruiting sinks, they tell us little about source-sink coordination in typical growing conditions for woody species.
@@
 Specific root length (SRL) is reported as the root length divided by the dry mass of each subsample (m g^-1^).
-Root length density (RLD) is reported as the root length divided by the total volume of each container (m dm^-3^).
+Fine root length density (FRLD) for seedlings in containers is reported as the total fine root length divided by the volume of each container (m dm^-3^).
 
@@
 TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, were calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf nitrogen content.
-Similarily, TNC-free leaf N (N~f~, %) was calculated on all gas exchange leaves from leaf mass content without TNC and leaf N content.
+Similarily, TNC-free leaf N (N~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC and leaf N content.
 
@@
 $$\frac{dM_c}{dt} = A_{c}~P_{i}~-~(\Lambda_{c}~M_{c})$$
-where A~c~ is the component specific biomass partitioning  to whole plant biomass (%) and $\Lambda$~c~ is component specific turnover rate.
+where A~c~ is the component specific biomass partitioning  to whole plant biomass (%) and $\Lambda$~c~ is component specific turnover rate (yr^-1^).
 Because we did not observe branch turnover, $\Lambda$~stem~ was assumed to equal 0.
@@
 
-First, a default model was fitted with mean photosynthetic parameters from the free seedlings and then optimized to produce a LMF that correctly predicted both the leaf mass and total biomass of the harvested free seedling (M~free~).
-This optimized LMF was then used to constrain model runs with soil volume treatment specific C~day~, while keeping tissue respiration rates and turnover parameters constant, to determine if changes in leaf A alone could predict biomass of seedlings in containers (M~pots~).
-Next, model sensitivity to different C allocation scenarios, including non-optimized treatment specific LMF and up regulation of non-leaf tissue respiration by 50 % of default values (M~s1,s2~, respectively), was used to improve predictions of model simulations compared to measured harvest biomass.
-For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment specific mean daily C assimilation by first scaling values to the free seedling control.
+\
+First, a default model was fitted with mean photosynthetic parameters from the free seedlings and then optimized to produce a LMF which correctly predicted both the leaf mass and total biomass of the harvested free seedling (M~free~).
+This optimized LMF was then used to constrain model runs with soil volume treatment specific C~day~, while keeping tissue respiration and turnover parameters constant, to determine if changes in leaf A alone could predict biomass of seedlings in containers (M~pots~).
+Next, model sensitivity to different C allocation scenarios, including observed treatment specific LMF and up regulation of non-leaf tissue respiration by 50 % of default values (M~S1~ and M~S2~, respectively), was used to improve model biomass predictions compared to measured harvest biomass.
+For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment specific mean C~day~ by first scaling values to the free seedling control.
 
@@
 ## Growth and morphology
-Plant height, diameter, and leaf area diverged between container volumes soon after start of the experiment (Figure `r allomfig`).
+Plant height, diameter and leaf area diverged between container volumes soon after start of the experiment (Figure `r allomfig`).
 First, seedling leaf area significantly diverged between soil volumes (P < 0.029) during the 5^th^ week of the experiment.
@@
 Plant biomass was postively correlated with total leaf area across all treatments (R^2^ = 0.97, P < 0.001).
-Differences in biomass partitioning to leaves, stems, and roots were not different across soil volumes after variation in seedling biomass across treatments was factored in the analysis (Figure `r allocfig`a,b).
+Differences in biomass partitioning to leaves, stems and roots were not different across soil volumes after variation in seedling biomass across treatments was factored in the analysis (Figure `r allocfig`a,b).
 Across all treatments, the final harvest root:shoot biomass ratio was conserved in these seedlings which exhibited a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119]) and a near identical ratio of leaf to fine root mass (Figure `r allocfig`c).
@@
 \
-Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table 2). Root length density increased  (Table 2)
-
+Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table 2, P = 0.009).
+Fine root length density was significantly higher in the two smallest container sizes and was the lowest in the largest container size (Table 2, P < 0.001).
 Over the duration of the experiment SLA~f~ was higher in free seedlings, but was not different across containers sizes (Table 1, P < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (P < 0.001).
@@
 Differences in leaf starch between the free seedling and the smallest container were evident during the first gas exchange campaign (P = 0.001).
-Root N % was higher in free seedlings compared to seedlings in containers but only for some of the container size treatments (Table 2).
+Root N was higher in free seedlings compared to seedlings in containers but only for some of the container size treatments (Table 2).
 
@@
 Across all measurement campaigns mean A~sat~ (Figure `r asatfig`) and A~max~ (Table 3) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
-The relationships between photosynthetic capacity, leaf starch, and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001).
+The relationships between photosynthetic capacity, leaf starch and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001).
 We used predictions from the linear mixed effect model equation to visualize these relationship of A~max~ to either leaf N content or leaf starch at muliple bin levels (n=5) of the covariate parameter (Figure `r achemfig`).
@@
 Combined these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment.
-Soil N % at harvest was not different across soil volumes ($\bar{x}$ = 4.5 %), with minimal decreases from pre-planting value ($\bar{x}$ = 4.9 %).
+Soil N at harvest was not different across soil volumes ($\bar{x}$ = 4.5 %), with minimal decreases from pre-planting value ($\bar{x}$ = 4.9 %).
 This indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
@@
 ## Modelling seedling biomass
-The default model M~free~, successfully optimized a LMF (21.6 %) which then allowed model to predict mean harvest total biomass of free seedlings within 1.2 %.
+The default model M~free~, successfully optimized a LMF (21.6 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %.
 Using this optimized LMF, the total biomass of modeled seedlings for each soil volume treatment (M~pots~) were on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf C gain (Figure `r massmodelfig`a).
@@
 Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over predictions of seedling C mass.
-Testing the sensitivity of the model to observed treatment-specific LMF from the final harvest (M~s1~), which were each lower than the optmized LMF value (see Figure `r allocfig`a), improved model predictions of seedling C mass but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
+Testing the sensitivity of the model to observed treatment-specific LMF from the final harvest (M~S1~), which were each lower than the optmized LMF value (see Figure `r allocfig`a), improved model predictions of seedling C mass but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
 Using harvest values of LMF, however, does not capture the observed increase in leaf turnover of seedlings in small containers (Figure `r allomfig`c).
-Thus, the use of harvest LMF values for seedlings in containers in M~s1~ likely underestimates daily C allocation to leaves over the final montsh of the experiment.
-Increases of 50 % in non-leaf tissue respiration (M~s2~) improved biomass estimates slightly but overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
-With M~3~, non-tissue respiration rates would need to be increased by ca.
+Thus, the use of harvest LMF values for seedlings in containers in M~S1~ likely underestimates daily C allocation to leaves over the final montsh of the experiment.
+Increases of 50 % in non-leaf tissue respiration (M~S2~) improved biomass estimates slightly but overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
+With M~S2~, non-tissue respiration rates would need to be increased by ca.
 250% in order for mass balance to be achieved.
@@
 Unrestricted mycorrhizal recruitment could have instead faciliated the increases in leaf N in free seedlings, but this effect is unknown.
-Combined with the fact that soil N % declined evenly across all treatments, there was no clear mechanism present to identify changes in root N uptake between free seedlings and seedlings in containers.
+Combined with the fact that soil N declined evenly across all treatments, there was no clear mechanism present to identify changes in root N uptake between free seedlings and seedlings in containers.
 In these already low quality soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
@@
 The sensitivity of roots to their own exudates near obstructions may prevent further growth [@semchenko2008foraging].
-Alternatively, physical restriction of root proliferation could have impacted root development and morphology prior to shifts in mass partitioning.
-Here, increases in root length where detected in several of the soil volume treatments.
+Here, we show that FRLD was highest in smallest containers suggesting that root restiction likely occurred as simple function of available rooting space.
+Alternatively, physical restriction of root proliferation could also have impacted root development and morphology prior to shifts in mass partitioning.
+Here, increases in SRL where detected in several of the soil volume treatments.
 This is not surprising as plants in containers have been shown to have different root morphology to field grown plants [@nesmith1998effect].
@@
 ## Do reductions in photosynthesis explain reductions in seedling growth?
-Our model used a simple approach to drive seedling growth with measured reductions in leaf level A , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
+Our model used a simple approach to drive seedling growth with measured reductions in leaf A , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
 Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
@@
 These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
-It is possible that the overestimation of growth was due to an initial overestimation of A, however, the robust empirical based methods used to generate phtosynthetic parameters (J~max~, V~cmax~, R~d~ and g~1~) make this unlikely.
+It is possible that the overestimation of growth was due to an initial overestimation of A, however, the robust empirical based methods used to generate photosynthetic parameters (J~max~, V~cmax~, R~d~ and g~1~) make this unlikely.
 Instead, our results indicate a need to evaluate how oversimplified representations of proceses other than A affect models which distinguish the fate of assimilate C within a plant.
@@
 \
-Using measured LMF from the harvest, instead of the optimized seedling control (M~s1~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond A.
+Using measured LMF from the harvest, instead of the optimized seedling control (M~S1~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond A.
 The sensitivity of the model to shifts in LMF could represent leaf loss throughout the experiment that could not be explicitly quantified in this field study.
@@
 \
-Increasing rates of non-leaf respiration (M~s2~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation.
+Increasing rates of non-leaf respiration (M~S2~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation.
 We also show that very large increases in non-leaf respiration rates would have been required to accurately predict observed seedling biomass.
-Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], results from M~s2~ highlight a lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change.
+Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], results from M~S2~ highlight a lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change.
 This is noteworthy, as C balance is a delicate equilibrium between fluxes of A and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions (Valentini et al.
 2000).
-These results from infer that using fixed rates of respiration in models likely underestimates plant responses to sink limitation.
+These results infer that using fixed rates of respiration in models likely underestimates plant responses to sink limitation.
 Thus, we agree with Delucia et al.
@@
 All values are from the final harvest.
-Vaules for RLD are only calculated for seedlings in containers as free seedlings have potentially unlimeted soil volume to exploit.
+Vaules for FRLD are only calculated for seedlings in containers as free seedlings have potentially unlimeted soil volume to exploit.
 Different letters represent significant differences between treatments.
-The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for RLD which represents only diffeences between seedlings in containers.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only diffeences between seedlings in containers.
 
@@
 
+\
 **Table S1**. Seedling growth model default parameters.
@@
 For (b) lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment.
-For (c) the dashed line is the 1:1 relationship and the solid line represents the significant linear model fit (R^2^=0.81).
+For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (R^2^ = 0.82) with equation: log(x) = 0.983(log(y)) - 0.036.
 
@@
 
-```{r, echo=FALSE, warning=FALSE}
+```{r table1, echo=FALSE, warning=FALSE}
 greeks=c(alpha='\u03b1', Delta='\u0394', Sigma='\u03A3', mu='\u03bc',delta = '\u03b4')
@@
 All values are from the final harvest.
-Vaules for RLD were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
+Vaules for FRLD were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
 Different letters represent significant differences between treatments.
-The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for RLD which represents only diffeences between seedlings in containers.
-```{r, echo=FALSE, warning=FALSE}
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only diffeences between seedlings in containers.
+```{r table2, echo=FALSE, warning=FALSE}
 dust(table2)%>%
@@
                         "SRL (m g^-1^)",
-                        "RLD (m dm^-3^)") %>%
+                        "FRLD (m dm^-3^)") %>%
   sprinkle(rows= 1, part="head",bold=TRUE)%>%
@@
 
-```{r table2, echo=FALSE, warning=FALSE}
+```{r table3, echo=FALSE, warning=FALSE}
 dust(table3)%>%
@@
 # Figures {.unnumbered}
-```{r allometry, fig.width=6, fig.height=8, echo=FALSE,  dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=400, dev.args=list(type="cairo")}
 source("master_scripts/allometryplotting.R")
@@
 **Figure 4**.
-<!---
+
 ```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
@@
 ```
--->
 
@@
 # Supporting Information {.unnumbered}
-**Table S1**.
+**Table S1**.Seedling growth model default parameters.
 
-```{r model_scenarios, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=300, dev.args=list(type="cairo")}
-source("master_scripts/massmodel_optimize_scenarios.R")
-```
-
-**Figure S1**. Seedling growth model default parameters.
 ```{r tabels1, echo=FALSE, warning=FALSE}
@@
 
+```{r model_scenarios, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+source("master_scripts/massmodel_optimize_scenarios.R")
+```
+
+**Figure S1**.
+
 # References {.unnumbered}

### 2015-10-28 master_scripts/allocation_plotting.R

@@ -1,5 +1,5 @@
 #this script is for sourcing the allocation plots into master
-#source("functions and packages/startscripts.R")
+# source("functions and packages/startscripts.R")
 
 library(smatr)
 

### 2015-10-28 master_scripts/leafd2h.R

@@ -24,6 +24,25 @@ allom$d2h <- with(allom, diameter^2 * height)
 allom$volume <- as.factor(allom$volume)
 
 
-##plot leafmass * d2h
+leafd2h_mod <- lm(log10(leafmass) ~ log10(d2h), data=allom)
+anova(leafd2h_mod)
+summary(leafd2h_mod)
+library(visreg)
+visreg(leafd2h_mod)
 
-plot(leafmass ~ d2h, data=allom, pch=pchs[volume], col=volume, cex=1.5)
+
+##plot leafmass * d2h
+library(magicaxis)
+library(plotrix)
+
+windows(7,7)
+plot(log10(leafmass) ~ log10(d2h), data=allom, pch=pchs[volume], col=volume, cex=1.5, axes=FALSE)
+magaxis(side=c(1,2), unlog=c(1,2), frame.plot=TRUE)
+box()
+ablineclip(leafd2h_mod, x1=min(log10(allom$d2h)), x2=max(log10(allom$d2h)),lwd=2)
+
+dev.copy2pdf(file= "master_scripts/manuscript_figs/leafmassd2h.pdf")
+dev.off()
+
+
+

### 2015-10-28 master_scripts/rootdensity.R

@@ -11,33 +11,49 @@ rootlength <- read.csv("calculated data/srl_clean.csv")
 ##read final harvest leaf area
 leafarea <- read.csv("calculated data/LA_harvest.csv")
 
+##Read in final harvest data for RLD (all root length)
+harvest <- read.csv("calculated data/seedling mass.csv")
+harvestroots <- harvest[,c("ID","volume", "fineroot")] ##grams
+
+##need to merge harvest fine root mass with SRL
+
+rootlength2 <- merge(rootlength, harvestroots, all=TRUE)
+
 ##calculate root lenght density
-rootlength$rootlengthdensity <- with(rootlength, total_length_cm/volume) ##cm/l
-rootlength$rootlengthdensity2 <- with(rootlength, rootlengthdensity*.01) ##m/dm3
-rootlength$rootlengthdensity3 <- with(rootlength, rootlengthdensity*.00001) ##m/cm3
+# rootlength$rootlengthdensity <- with(rootlength, total_length_cm/volume) ##cm/l
+# rootlength$rootlengthdensity2 <- with(rootlength, rootlengthdensity*.01) ##m/dm3
+# rootlength$rootlengthdensity3 <- with(rootlength, rootlengthdensity*.00001) ##m/cm3
+
+
+rootlength2$rootlengthpot <- with(rootlength2, SRL2*fineroot) #meters
+rootlength2$frld <- with(rootlength2, rootlengthpot/volume) ##m/dm3
+
+###remove the empty IDs that were outliers from SRL
+rootlength3 <- rootlength2[complete.cases(rootlength2),]
+
 
 ##now make volume a factor and relevel
-rootlength$volume <- as.factor(rootlength$volume)
-rootlength$volume <- relevel(rootlength$volume, ref="1000")
-rootlength$block <- as.factor(gsub("-[1-9]", "", rootlength$ID))
+rootlength3$volume <- as.factor(rootlength3$volume)
+rootlength3$volume <- relevel(rootlength3$volume, ref="1000")
+rootlength3$block <- as.factor(gsub("-[1-9]", "", rootlength3$ID))
 
-write.csv(rootlength[,c(1:3,7:9,12)], "calculated data/RLD.csv", row.names=FALSE)
+###save as calculated data
[…]

### 2015-11-11 manuscript/manuscript_pve.Rmd
abstract edit

@@
 Thus, as A and growth were not tightly coordinated, excess photosynthetic C not attributed to biomass resulted in seedlings with soil volume restriction.
-These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that important feedbacks exist between belowgroud sink strength and leaf C uptake.
+These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that important feedbacks exist between belowground sink strength and leaf C uptake.
 

### 2015-11-11 manuscript/manuscript_pve.Rmd
spell check

@@
 An accumulation of leaf non-structural carbohydrates, resulting from reduced belowground sink strength, was expected to correlate to reductions in photosynthetic capacity.
-We observed a negative effect of contatiner volume on aboveground growth soon after the experiment started.
+We observed a negative effect of container volume on aboveground growth soon after the experiment started.
 Although growth was consistently different across soil volumes, dry mass partitioning to leaves, stems and roots was unchanged after 120 days.
@@
 These mixed results are not surprising as we still know little about the balance between assimilation, storage and growth across temporal scales in plants [@smith2007coordination].
-As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to the occurence large fruiting sinks, they tell us little about source-sink coordination in typical growing conditions for woody species.
+As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to the occurrence of large fruiting sinks, they tell us little about source-sink coordination in typical growing conditions for woody species.
 
@@
 Seedlings were planted in summer (January 21^st^ 2013) and stem height, diameter at 15 cm and leaf count were measured weekly thereafter.
-Once the growth rate of individual plants had significantly declined a full biomass harvest was completed abd the experiment ended (May 21^st^ 2013).
+Once the growth rate of individual plants had significantly declined a full biomass harvest was completed and the experiment ended (May 21^st^ 2013).
 Dry mass of leaves, stems, roots and total leaf area (LI-3100C Area Meter; LI-COR, Lincoln, NE, USA) were measured for each seedling.
@@
 Roots from the free seedlings were collected by excavating each 1 m^2^ subplot to the hard layer and keeping only roots within the subplot.
-For each seedling, a subsample of washed fine roots was analyzed for root length using WhinoRhizo software (Regent Instruments Inc., Quebec, QC, Canada).
-Specific root length (SRL) is reported as the root length divided by the dry mass of each subsample (m g^-1^).
+For each seedling, a sub-sample of washed fine roots was analyzed for root length using WhinoRhizo software (Regent Instruments Inc., Quebec, QC, Canada).
+Specific root length (SRL) is reported as the root length divided by the dry mass of each sub-sample (m g^-1^).
 Fine root length density (FRLD) for seedlings in containers is reported as the total fine root length divided by the volume of each container (m dm^-3^).
@@
 These measurements were conducted during midday (10:00-14:00 h) with leaf temperature maintained at 25 &deg;C.
-After CO~2~ and water vapor flux values stabalized in the leaf chamber, net CO~2~ assimilation rate and stomatal conductance (g~s~) were logged 5 times and averaged for both A~sat~ and A~max~.
+After CO~2~ and water vapor flux values stabilized in the leaf chamber, net CO~2~ assimilation rate and stomatal conductance (g~s~) were logged 5 times and averaged for both A~sat~ and A~max~.
 
@@
 TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, were calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf nitrogen content.
-Similarily, TNC-free leaf N (N~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC and leaf N content.
+Similarly, TNC-free leaf N (N~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC and leaf N content.
 
@@
 $$R = \Sigma(R_c~M_c)$$
-where R~c~ is publsihed or local tissue respiration rates of fine roots, coarse roots or stems (Table S1, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
+where R~c~ is published or local tissue respiration rates of fine roots, coarse roots or stems (Table S1, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
 R~leaf~ is represented in the calculation of C~day~ (described below).
@@
 On average, harvested biomass of free seedlings was 84% higher than seedlings in containers.
-Plant biomass was postively correlated with total leaf area across all treatments (R^2^ = 0.97, P < 0.001).
+Plant biomass was positively correlated with total leaf area across all treatments (R^2^ = 0.97, P < 0.001).
 Differences in biomass partitioning to leaves, stems and roots were not different across soil volumes after variation in seedling biomass across treatments was factored in the analysis (Figure `r allocfig`a,b).
@@
 The relationships between photosynthetic capacity, leaf starch and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001).
-We used predictions from the linear mixed effect model equation to visualize these relationship of A~max~ to either leaf N content or leaf starch at muliple bin levels (n=5) of the covariate parameter (Figure `r achemfig`).
+We used predictions from the linear mixed effect model equation to visualize these relationship of A~max~ to either leaf N content or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
 Across all measurement campaigns and treatments A~max~ was higher when foliar N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
 A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b).
-Overall, A~max~ was postively correlated with final harvest biomass across all seedlings (P < 0.001).
+Overall, A~max~ was positively correlated with final harvest biomass across all seedlings (P < 0.001).
 
@@
 Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over predictions of seedling C mass.
-Testing the sensitivity of the model to observed treatment-specific LMF from the final harvest (M~S1~), which were each lower than the optmized LMF value (see Figure `r allocfig`a), improved model predictions of seedling C mass but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
+Testing the sensitivity of the model to observed treatment-specific LMF from the final harvest (M~S1~), which were each lower than the optimized LMF value (see Figure `r allocfig`a), improved model predictions of seedling C mass but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
 Using harvest values of LMF, however, does not capture the observed increase in leaf turnover of seedlings in small containers (Figure `r allomfig`c).
-Thus, the use of harvest LMF values for seedlings in containers in M~S1~ likely underestimates daily C allocation to leaves over the final montsh of the experiment.
+Thus, the use of harvest LMF values for seedlings in containers in M~S1~ likely underestimates daily C allocation to leaves over the final months of the experiment.
 Increases of 50 % in non-leaf tissue respiration (M~S2~) improved biomass estimates slightly but overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
@@
 Additionally, severe reductions in A in coffee plants were not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
-It is likely that reductions in A of well-watered seedlings oberved in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
+It is likely that reductions in A of well-watered seedlings observed in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
 
 \
-Here, reductions in A were postively correlated with decreases in leaf N and leaf N was considerably reduced for seedlings in containers.
-As leaf N reductions were detected with TNC-free leaf mass, this suggests that physical root restriction or decreased supply likely affected seedling N uptake instead of TNC dilution in leaves in the smalles containers.
+Here, reductions in A were positively correlated with decreases in leaf N and leaf N was considerably reduced for seedlings in containers.
+As leaf N reductions were detected with TNC-free leaf mass, this suggests that physical root restriction or decreased supply likely affected seedling N uptake instead of TNC dilution in leaves in the smallest containers.
 Root N at the end of the experiment was on average higher in free seedlings but not consistently higher than every container volume treatment.
-Unrestricted mycorrhizal recruitment could have instead faciliated the increases in leaf N in free seedlings, but this effect is unknown.
+Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N in free seedlings, but this effect is unknown.
 Combined with the fact that soil N declined evenly across all treatments, there was no clear mechanism present to identify changes in root N uptake between free seedlings and seedlings in containers.
 In these already low quality soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
-Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the affects of belowground sink limitation on A of seedlings in containers was evidents throughout the experiment.
+Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the affects of belowground sink limitation on A of seedlings in containers was evident throughout the experiment.
 
@@
 The sensitivity of roots to their own exudates near obstructions may prevent further growth [@semchenko2008foraging].
-Here, we show that FRLD was highest in smallest containers suggesting that root restiction likely occurred as simple function of available rooting space.
+Here, we show that FRLD was highest in smallest containers suggesting that root restriction likely occurred as simple function of available rooting space.
 Alternatively, physical restriction of root proliferation could also have impacted root development and morphology prior to shifts in mass partitioning.
@@
 It is possible that the overestimation of growth was due to an initial overestimation of A, however, the robust empirical based methods used to generate photosynthetic parameters (J~max~, V~cmax~, R~d~ and g~1~) make this unlikely.
-Instead, our results indicate a need to evaluate how oversimplified representations of proceses other than A affect models which distinguish the fate of assimilate C within a plant.
+Instead, our results indicate a need to evaluate how oversimplified representations of processes other than A affect models which distinguish the fate of assimilate C within a plant.
 Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven  plant growth models, yet C partitioning remains a key weakness  [@lacointe2000carbon].
@@
 The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
-Our combined empirical and modeling approach shows that when non-photosynthesis parameters were kept contant changes in A were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
+Our combined empirical and modeling approach shows that when non-photosynthesis parameters were kept constant changes in A were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
 K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control A through the demand for C.
@@
 
-**Table 1**.Responses of plant and leaf characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+**Table 1**.Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.
@@
 \
-**Table 2.** Responses of root characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+**Table 2.** Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.
 All values are from the final harvest.
-Vaules for FRLD are only calculated for seedlings in containers as free seedlings have potentially unlimeted soil volume to exploit.
+Values for FRLD are only calculated for seedlings in containers as free seedlings have potentially unlimited soil volume to exploit.
 Different letters represent significant differences between treatments.
-The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only diffeences between seedlings in containers.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only differences between seedlings in containers.
 
@@
 **Figure 3**.
-Soil volume treatment means of biomass partitioning to leaves, stems, and roots at harvest (a), bivariate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c).
+Soil volume treatment means of biomass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c).
 For (b) lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment.
@@
 # Tables {.unnumbered}
-**Table 1**.Responses of plant and leaf characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+**Table 1**.Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.
@@
 
-**Table 2.** Responses of root characterisitics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+**Table 2.** Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.
 All values are from the final harvest.
-Vaules for FRLD were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
+Values for FRLD were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
 Different letters represent significant differences between treatments.
-The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only diffeences between seedlings in containers.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only differences between seedlings in containers.
 ```{r table2, echo=FALSE, warning=FALSE}

### 2015-11-13 manuscript/manuscript_pve.Rmd
spelling

@@
 Our findings reveal that a combination of different mechanisms, beyond A, are likely at play in driving the observed seedling biomass response to sink manipulation.
-However, the degree to which these mechanisms will regulate a growth will undoubtedly shift across different experimental manipulations and plant species.
+However, the degree to which these mechanisms will regulate growth will undoubtedly shift across different experimental manipulations and plant species.
 

### 2015-11-13 manuscript/manuscript_pve.Rmd
spelling

@@
 K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control A through the demand for C.
-Although this may be true, we results infer that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
+Although this may be true, our results infer that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
 Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.

### 2015-12-01 manuscript/manuscript_pve.Rmd
abbreviations updated

@@
 We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown (free) seedlings.
-We developed a seedling growth model that utilized leaf photosynthesis rates (A) to allocate daily C uptake towards mass growth of stems, leaves and roots.
+We developed a seedling growth model that utilized leaf photosynthesis rates (*A*) to allocate daily C uptake towards mass growth of stems, leaves and roots.
 Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
@@
 Photosynthetic capacity was significantly reduced in containers compared to free seedlings, and was related to both leaf nitrogen content and starch accumulation.
-We then asked whether the observed reductions in A explained the observed differences in seedling biomass.
-We found that although belowground sink limitation resulted in down regulation of A, these reductions were not large enough to explain observed growth responses.
-Thus, as A and growth were not tightly coordinated, excess photosynthetic C not attributed to biomass resulted in seedlings with soil volume restriction.
+We then asked whether the observed reductions in *A* explained the observed differences in seedling biomass.
+We found that although belowground sink limitation resulted in down regulation of *A*, these reductions were not large enough to explain observed growth responses.
+Thus, as *A* and growth were not tightly coordinated, excess photosynthetic C not attributed to biomass resulted in seedlings with soil volume restriction.
 These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that important feedbacks exist between belowground sink strength and leaf C uptake.
@@
 As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues and organs.
-At long enough time scales photosynthesis (A) and respiratory losses together determine net C balance and will be coordinated to plant growth.
+At long enough time scales photosynthesis (*A*) and respiratory losses together determine net C balance and will be coordinated to plant growth.
 At shorter temporal scales, however, growth can instead be mediated by tissue C storage pools.
@@
 \
-In woody species, the coordination of A and growth has been studied with manipulations of C source activity.
+In woody species, the coordination of *A* and growth has been studied with manipulations of C source activity.
 Examples included elevated CO~2~ experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments.
-Elevated CO~2~ has been shown to increase A [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a stimulation of 23 % in forest biomass production [@norby2005forest].
+Elevated CO~2~ has been shown to increase *A* [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a stimulation of 23 % in forest biomass production [@norby2005forest].
 Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
-In partial defoliation experiments, increases in A of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
-However, increases in A in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
-These manipulations of C source activity expose unresolved issues with how changes in A do not always infer similar responses in growth.
+In partial defoliation experiments, increases in *A* of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
+However, increases in *A* in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
+These manipulations of C source activity expose unresolved issues with how changes in *A* do not always infer similar responses in growth.
 
 \
-Alternatively, manipulating plant tissue C sinks is often used to investigate the correlation of A and growth.
+Alternatively, manipulating plant tissue C sinks is often used to investigate the correlation of *A* and growth.
 This is because metabolic signaling networks, relaying information on C and N status of different tissues, can regulate photosynthetic activity [@paul2001sink].
-If sink inhibition of A occurs, a close coordination between declines in A and growth should be expected.
+If sink inhibition of *A* occurs, a close coordination between declines in *A* and growth should be expected.
 Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal, phloem girdling and low temperatures at high elevations.
-In these studies, down regulation of A was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
-However, reductions in A were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
+In these studies, down regulation of *A* was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
+However, reductions in *A* were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
 These mixed results are not surprising as we still know little about the balance between assimilation, storage and growth across temporal scales in plants [@smith2007coordination].
@@
 Possible advantages of this approach are that it allows a large range of treatment levels, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
-Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, A, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
+Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, *A*, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
 Inadequate rooting volume may decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root].
@@
 A meta-analysis by Poorter et al.
-[-@poorter2012pot] concluded that A is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used.
+[-@poorter2012pot] concluded that *A* is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used.
 This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower C exchange and assimilate export rates [@robbins1988effect].
 However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].
-Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test the extent to which growth and A are coordinated.
+Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test the extent to which growth and *A* are coordinated.
 
 \
-This study utilizes a novel field design to investigate the coordination between growth and A in *Eucalyptus tereticornis* Sm.
+This study utilizes a novel field design to investigate the coordination between growth and *A* in *Eucalyptus tereticornis* Sm.
 seedlings, by manipulating container size and thus rooting volume.
@@
 Empirical results were combined with a simple plant growth model to simulate seedling growth with a C mass balance approach, which was then compared to observed harvested seedling mass.
-The model used whole-plant C gain, scaled from instantaneous rates of leaf A, to quantify seedling dry mass production over the 120 day experiment.
+The model used whole-plant C gain, scaled from instantaneous rates of leaf *A*, to quantify seedling dry mass production over the 120 day experiment.
 
@@
 Each AC~i~ curve was started at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light (above).
-From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@Duursma2014] in R [@RDevelopmentCoreTeam2011].
+From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011].
 
@@
 Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions.
-Reported values of R are standardized rates at 25 &deg;C using a Q10 value (1.86) developed for these seedlings in a separate experiment (Drake et al.
+Reported values of R are standardized rates at 25 &deg;C using a Q~10~ value (1.86) developed for these seedlings in a separate experiment (Drake et al.
 unpublished).
@@
 ## Leaf water potential
-Predawn ($\Psi$~pd~) and midday ($\Psi$~l~) leaf water potentials were measured for each seedling using a PMS 1505D pressure chamber (PMS Instruments, Albany, OR, USA) on fully expanded leaves during the same time period as AC~i~ and R~d~.
+Predawn ($\Psi$~pd~) and midday ($\Psi$~l~) leaf water potentials were measured for each seedling using a PMS 1505D pressure chamber (PMS Instruments, Albany, OR, USA) on fully expanded leaves during the same time period as AC~i~ and R.
 Leaves were detached and immediately stored inside foil covered bags before water potential measurements were performed.
@@
 Complete methods of the TNC assay are described in [@mitchell2013drought].
-TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, were calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf nitrogen content.
+TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, were calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf N content.
 Similarly, TNC-free leaf N (N~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC and leaf N content.
@@
 ## Seedling growth model
-We developed a simple seedling growth model that utilized leaf A rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
+We developed a simple seedling growth model that utilized leaf *A* rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
 The model begins with mean initial tissue component biomass (leaf~i~, stem~i~ and root~i~) and a starting leaf area (LA~i~) measured prior to planting.
@@
 \
-C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package in R with the mean photosynthetic parameters (J~max~, V~cmax~, R~d~ and g~1~) for each treatment and meteorological data from an onsite weather station.
-J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), R~d~ was empirically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed g~s~ values.
+C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package in R with the mean photosynthetic parameters (J~max~, V~cmax~, R and g~1~) for each treatment and meteorological data from an onsite weather station.
+J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), R was empirically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed g~s~ values.
 Methods of the coupled leaf gas exchange model are described in Duursma et al [-@duursma2014peaked].
-Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf A rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
+Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A* rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
 C~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
@@
 \
-It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf A with total plant leaf area.
+It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf *A* with total plant leaf area.
 This was accomplished by utilizing 61 previously digitized Eucalyptus seedlings, covering 5 total species which include *E.
@@
 [-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
-Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total A, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
-The ratio of total A with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments.
+Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
+The ratio of total *A* with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments.
 Next, the linear relationship between $\sigma$~s~ and total leaf area was for determined across digitized seedlings, within each treatment.
@@
 \
-We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf A where sufficient to accurately predict overall seedling biomass production after 120 days.
-Each model run utilized changes in A and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
+We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A* where sufficient to accurately predict overall seedling biomass production after 120 days.
+Each model run utilized changes in *A* and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
 Cumulative net leaf C gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling C was assumed to equal half of the final mass for both modeled and observed seedlings.
@@
 Tests of allometric relationships between log-transformed biomass components were implemented using standardized major axis regression in the 'smatr' package in R [@warton2012smatr].
-Results were considered significant at P < 0.05.
+All tests of statistical significance were conducted at an alpha of 0.05.
 
@@
 We used predictions from the linear mixed effect model equation to visualize these relationship of A~max~ to either leaf N content or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
-Across all measurement campaigns and treatments A~max~ was higher when foliar N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
+Across all measurement campaigns and treatments A~max~ was higher when leaf N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
 A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b).
@@
 Thus, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments (Figure `r massmodelfig`b).
-As a result, the observed reductions in leaf A with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
+As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
 
@@
 This study utilized a simple but novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
-We addressed questions regarding the coordination of A and growth by complementing empirical results with a C mass balance model.
-We found that reductions in leaf A across container sizes, when integrated across the 120 day experiment, were alone insufficient to account for observed reductions in total plant biomass production.
+We addressed questions regarding the coordination of *A* and growth by complementing empirical results with a C mass balance model.
+We found that reductions in leaf *A* across container sizes, when integrated across the 120 day experiment, were alone insufficient to account for observed reductions in total plant biomass production.
 
@@
 Decreases in A~sat~ occurred at the same time as reductions in height and diameter of seedlings in containers.
-This initially suggests a strong link between growth and an apparent down regulation of A.
-However, there are several possible mechanisms that can explain reduced A in small containers including nutrient content, water or reduced sink strength [@poorter2012pot].
+This initially suggests a strong link between growth and an apparent down regulation of *A*.
+However, there are several possible mechanisms that can explain reduced *A* in small containers including nutrient content, water or reduced sink strength [@poorter2012pot].
 It was therefore necessary to examine each of these factors to determine if the induced belowground sink limitation actually triggered photosynthetic down regulation.
@@
 \
-With high rates of g~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in A.
+With high rates of g~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A*.
 This finding is consistent with other container size studies without drought treatments.
 For example, reduced A~max~ in cotton seedlings grown at elevated CO~2~ was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased g~s~ [@thomas1991root].
-Additionally, severe reductions in A in coffee plants were not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
-It is likely that reductions in A of well-watered seedlings observed in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
+Additionally, severe reductions in *A* in coffee plants were not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
+It is likely that reductions in *A* of well-watered seedlings observed in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
 
 \
-Here, reductions in A were positively correlated with decreases in leaf N and leaf N was considerably reduced for seedlings in containers.
+Here, reductions in *A* were positively correlated with decreases in leaf N and leaf N was considerably reduced for seedlings in containers.
 As leaf N reductions were detected with TNC-free leaf mass, this suggests that physical root restriction or decreased supply likely affected seedling N uptake instead of TNC dilution in leaves in the smallest containers.
@@
 In these already low quality soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
-Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the affects of belowground sink limitation on A of seedlings in containers was evident throughout the experiment.
+Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the affects of belowground sink limitation on *A* of seedlings in containers was evident throughout the experiment.
 
@@
 As both rooting space and resources were finite in containers, the inability of seedlings to maintain the capacity of the belowground C sink resulted in the buildup of C assimilate in leaves.
-The feedback inhibition of A from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process (Nebauer et al.
+The feedback inhibition of *A* from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process (Nebauer et al.
 2011).
@@
 This agrees with a study on a deciduous conifer by Equiza et al.
-(2006) where photosynthetic downregulation from reduced sink strength was correlated with starch content.
-As starch content in leaves of plants grown in the smallest containers was nearly double that of free seedlings in our study, this suggests the response of A to sink inhibition was regulated by this accumulation, as hypothesized.
+[-@equiza2006photosynthetic] where photosynthetic downregulation from reduced sink strength was correlated with starch content.
+As starch content in leaves of plants grown in the smallest containers was nearly double that of free seedlings in our study, this suggests the response of *A* to sink inhibition was regulated by this accumulation, as hypothesized.
 
@@
 ## Do reductions in photosynthesis explain reductions in seedling growth?
-Our model used a simple approach to drive seedling growth with measured reductions in leaf A , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
+Our model used a simple approach to drive seedling growth with measured reductions in leaf *A* , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
 Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
 Although reductions in A~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
-[-@poorter2012pot], we provide evidence that the negative effects of sink limitation on A can not fully explain explain reduced seedling growth.
+[-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A* can not fully explain explain reduced seedling growth.
 These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
-It is possible that the overestimation of growth was due to an initial overestimation of A, however, the robust empirical based methods used to generate photosynthetic parameters (J~max~, V~cmax~, R~d~ and g~1~) make this unlikely.
-Instead, our results indicate a need to evaluate how oversimplified representations of processes other than A affect models which distinguish the fate of assimilate C within a plant.
+It is possible that the overestimation of growth was due to an initial overestimation of *A*, however, the robust empirical based methods used to generate photosynthetic parameters (J~max~, V~cmax~, R and g~1~) make this unlikely.
+Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A* affect models which distinguish the fate of assimilate C within a plant.
 Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven  plant growth models, yet C partitioning remains a key weakness  [@lacointe2000carbon].
@@
 \
-Using measured LMF from the harvest, instead of the optimized seedling control (M~S1~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond A.
+Using measured LMF from the harvest, instead of the optimized seedling control (M~S1~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond *A*.
 The sensitivity of the model to shifts in LMF could represent leaf loss throughout the experiment that could not be explicitly quantified in this field study.
 As TNC accumulation can lead to accelerated leaf senescence [@paul2001sink], this could explain the observed decline in total leaf area of seedlings in small containers.
-Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of A and the fate of C allocated to growth, respiration and C storage in leaves.
+Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A* and the fate of C allocated to growth, respiration and C storage in leaves.
 It will be the interactions between these two components that will determine the total C gain available for plant growth.
@@
 Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], results from M~S2~ highlight a lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change.
-This is noteworthy, as C balance is a delicate equilibrium between fluxes of A and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions (Valentini et al.
+This is noteworthy, as C balance is a delicate equilibrium between fluxes of *A* and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions (Valentini et al.
 2000).
@@
 [-@delucia2007forest] that it is likely inappropriate to assume that respiration is a constant fraction of gross primary production in models.
-Our findings reveal that a combination of different mechanisms, beyond A, are likely at play in driving the observed seedling biomass response to sink manipulation.
+Our findings reveal that a combination of different mechanisms, beyond *A*, are likely at play in driving the observed seedling biomass response to sink manipulation.
 However, the degree to which these mechanisms will regulate growth will undoubtedly shift across different experimental manipulations and plant species.
@@
 The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
-Our combined empirical and modeling approach shows that when non-photosynthesis parameters were kept constant changes in A were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
-K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control A through the demand for C.
+Our combined empirical and modeling approach shows that when non-photosynthesis parameters were kept constant changes in *A* were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
+K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A* through the demand for C.
 Although this may be true, our results infer that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
@@
 Each value reflects the mean(standard error) for each treatment.
-A~max~, R~dark~ and g~s~ are each measured at 25 &deg;C.
+A~max~, R and g~s~ are each measured at 25 &deg;C.
 Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n=6).
-R~dark~, J~max~ and Vc~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements.
+R, J~max~ and Vc~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements.
 Different letters represent significant differences between treatments.
@@
                         "A~max~ ($\\mu$mol m^-2^ s^-1^)", 
-                        "R~dark~ ($\\mu$mol m^-2^ s^-1^)",
+                        "R ($\\mu$mol m^-2^ s^-1^)",
                         "J~max~",

### 2015-12-03 manuscript/manuscript_pve.Rmd
checked for applie models and then fixed A abbr

@@
 We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown (free) seedlings.
-We developed a seedling growth model that utilized leaf photosynthesis rates (*A*) to allocate daily C uptake towards mass growth of stems, leaves and roots.
+We developed a seedling growth model that utilized leaf photosynthesis rates (*A~n~*) to allocate daily C uptake towards mass growth of stems, leaves and roots.
 Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
@@
 Photosynthetic capacity was significantly reduced in containers compared to free seedlings, and was related to both leaf nitrogen content and starch accumulation.
-We then asked whether the observed reductions in *A* explained the observed differences in seedling biomass.
-We found that although belowground sink limitation resulted in down regulation of *A*, these reductions were not large enough to explain observed growth responses.
-Thus, as *A* and growth were not tightly coordinated, excess photosynthetic C not attributed to biomass resulted in seedlings with soil volume restriction.
+We then asked whether the observed reductions in *A~n~* explained the observed differences in seedling biomass.
+We found that although belowground sink limitation resulted in down regulation of *A~n~*, these reductions were not large enough to explain observed growth responses.
+Thus, as *A~n~* and growth were not tightly coordinated, excess photosynthetic C not attributed to biomass resulted in seedlings with soil volume restriction.
 These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that important feedbacks exist between belowground sink strength and leaf C uptake.
@@
 As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues and organs.
-At long enough time scales photosynthesis (*A*) and respiratory losses together determine net C balance and will be coordinated to plant growth.
+At long enough time scales leaf photosynthesis (*A~n~*) and respiratory losses together determine net C balance and will correlate to plant growth.
 At shorter temporal scales, however, growth can instead be mediated by tissue C storage pools.
@@
 \
-In woody species, the coordination of *A* and growth has been studied with manipulations of C source activity.
+In woody species, the coordination of *A~n~* and growth has been studied with manipulations of C source activity.
 Examples included elevated CO~2~ experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments.
-Elevated CO~2~ has been shown to increase *A* [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a stimulation of 23 % in forest biomass production [@norby2005forest].
+Elevated CO~2~ has been shown to increase *A~n~* [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a stimulation of 23 % in forest biomass production [@norby2005forest].
 Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
-In partial defoliation experiments, increases in *A* of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
-However, increases in *A* in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
-These manipulations of C source activity expose unresolved issues with how changes in *A* do not always infer similar responses in growth.
+In partial defoliation experiments, increases in *A~n~* of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
+However, increases in *A~n~* in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
+These manipulations of C source activity expose unresolved issues with how changes in *A~n~* do not always infer similar responses in growth.
 
 \
-Alternatively, manipulating plant tissue C sinks is often used to investigate the correlation of *A* and growth.
+Alternatively, manipulating plant tissue C sinks is often used to investigate the correlation of *A~n~* and growth.
 This is because metabolic signaling networks, relaying information on C and N status of different tissues, can regulate photosynthetic activity [@paul2001sink].
-If sink inhibition of *A* occurs, a close coordination between declines in *A* and growth should be expected.
+If sink inhibition of *A~n~* occurs, a close coordination between declines in *A* and growth should be expected.
 Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal, phloem girdling and low temperatures at high elevations.
 In these studies, down regulation of *A* was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
-However, reductions in *A* were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
+However, reductions in *A~n~* were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
 These mixed results are not surprising as we still know little about the balance between assimilation, storage and growth across temporal scales in plants [@smith2007coordination].
@@
 Possible advantages of this approach are that it allows a large range of treatment levels, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
-Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, *A*, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
+Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, *A~n~*, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
 Inadequate rooting volume may decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root].
@@
 A meta-analysis by Poorter et al.
-[-@poorter2012pot] concluded that *A* is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used.
+[-@poorter2012pot] concluded that *A~n~* is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used.
 This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower C exchange and assimilate export rates [@robbins1988effect].
 However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].
-Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test the extent to which growth and *A* are coordinated.
+Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test the extent to which growth and *A~n~* are coordinated.
 
 \
-This study utilizes a novel field design to investigate the coordination between growth and *A* in *Eucalyptus tereticornis* Sm.
+This study utilizes a novel field design to investigate the coordination between growth and *A~n~* in *Eucalyptus tereticornis* Sm.
 seedlings, by manipulating container size and thus rooting volume.
@@
 Empirical results were combined with a simple plant growth model to simulate seedling growth with a C mass balance approach, which was then compared to observed harvested seedling mass.
-The model used whole-plant C gain, scaled from instantaneous rates of leaf *A*, to quantify seedling dry mass production over the 120 day experiment.
+The model used whole-plant C gain, scaled from instantaneous rates of leaf *A~n~*, to quantify seedling dry mass production over the 120 day experiment.
 
@@
 Tests of allometric relationships between log-transformed biomass components were implemented using standardized major axis regression in the 'smatr' package in R [@warton2012smatr].
-All tests of statistical significance were conducted at an alpha of 0.05.
+All tests of statistical significance were conducted at an alpha level of 0.05.
 
@@
 This study utilized a simple but novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
-We addressed questions regarding the coordination of *A* and growth by complementing empirical results with a C mass balance model.
-We found that reductions in leaf *A* across container sizes, when integrated across the 120 day experiment, were alone insufficient to account for observed reductions in total plant biomass production.
+We addressed questions regarding the coordination of *A~n~* and growth by complementing empirical results with a C mass balance model.
+We found that reductions in leaf *A~n~* across container sizes, when integrated across the 120 day experiment, were alone insufficient to account for observed reductions in total plant biomass production.
 
@@
 Decreases in A~sat~ occurred at the same time as reductions in height and diameter of seedlings in containers.
-This initially suggests a strong link between growth and an apparent down regulation of *A*.
-However, there are several possible mechanisms that can explain reduced *A* in small containers including nutrient content, water or reduced sink strength [@poorter2012pot].
+This initially suggests a strong link between growth and an apparent down regulation of *A~n~*.
+However, there are several possible mechanisms that can explain reduced *A~n~* in small containers including nutrient content, water or reduced sink strength [@poorter2012pot].
 It was therefore necessary to examine each of these factors to determine if the induced belowground sink limitation actually triggered photosynthetic down regulation.
@@
 \
-With high rates of g~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A*.
+With high rates of g~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A~n~*.
 This finding is consistent with other container size studies without drought treatments.
 For example, reduced A~max~ in cotton seedlings grown at elevated CO~2~ was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased g~s~ [@thomas1991root].
-Additionally, severe reductions in *A* in coffee plants were not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
-It is likely that reductions in *A* of well-watered seedlings observed in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
+Additionally, severe reductions in *A~n~* in coffee plants were not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
+It is likely that reductions in *A~n~* of well-watered seedlings observed in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
 
 \
-Here, reductions in *A* were positively correlated with decreases in leaf N and leaf N was considerably reduced for seedlings in containers.
+Here, reductions in *A~n~* were positively correlated with decreases in leaf N and leaf N was considerably reduced for seedlings in containers.
 As leaf N reductions were detected with TNC-free leaf mass, this suggests that physical root restriction or decreased supply likely affected seedling N uptake instead of TNC dilution in leaves in the smallest containers.
@@
 In these already low quality soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
-Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the affects of belowground sink limitation on *A* of seedlings in containers was evident throughout the experiment.
+Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the affects of belowground sink limitation on *A~n~* of seedlings in containers was evident throughout the experiment.
 
@@
 As both rooting space and resources were finite in containers, the inability of seedlings to maintain the capacity of the belowground C sink resulted in the buildup of C assimilate in leaves.
-The feedback inhibition of *A* from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process (Nebauer et al.
+The feedback inhibition of *A~n~* from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process (Nebauer et al.
 2011).
@@
 [-@equiza2006photosynthetic] where photosynthetic downregulation from reduced sink strength was correlated with starch content.
-As starch content in leaves of plants grown in the smallest containers was nearly double that of free seedlings in our study, this suggests the response of *A* to sink inhibition was regulated by this accumulation, as hypothesized.
+As starch content in leaves of plants grown in the smallest containers was nearly double that of free seedlings in our study, this suggests the response of *A~n~* to sink inhibition was regulated by this accumulation, as hypothesized.
 
@@
 ## Do reductions in photosynthesis explain reductions in seedling growth?
-Our model used a simple approach to drive seedling growth with measured reductions in leaf *A* , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
+Our model used a simple approach to drive seedling growth with measured reductions in leaf *A~n~* , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
 Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
 Although reductions in A~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
-[-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A* can not fully explain explain reduced seedling growth.
+[-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A~n~* can not fully explain explain reduced seedling growth.
 These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
-It is possible that the overestimation of growth was due to an initial overestimation of *A*, however, the robust empirical based methods used to generate photosynthetic parameters (J~max~, V~cmax~, R and g~1~) make this unlikely.
-Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A* affect models which distinguish the fate of assimilate C within a plant.
+It is possible that the overestimation of growth was due to an initial overestimation of *A~n~*, however, the robust empirical based methods used to generate photosynthetic parameters (J~max~, V~cmax~, R and g~1~) make this unlikely.
+Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A~n~* affect models which distinguish the fate of assimilate C within a plant.
 Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven  plant growth models, yet C partitioning remains a key weakness  [@lacointe2000carbon].
@@
 \
-Using measured LMF from the harvest, instead of the optimized seedling control (M~S1~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond *A*.
+Using measured LMF from the harvest, instead of the optimized seedling control (M~S1~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond *A~n~*.
 The sensitivity of the model to shifts in LMF could represent leaf loss throughout the experiment that could not be explicitly quantified in this field study.
 As TNC accumulation can lead to accelerated leaf senescence [@paul2001sink], this could explain the observed decline in total leaf area of seedlings in small containers.
-Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A* and the fate of C allocated to growth, respiration and C storage in leaves.
+Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A~n~* and the fate of C allocated to growth, respiration and C storage in leaves.
 It will be the interactions between these two components that will determine the total C gain available for plant growth.
@@
 Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], results from M~S2~ highlight a lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change.
-This is noteworthy, as C balance is a delicate equilibrium between fluxes of *A* and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions (Valentini et al.
-2000).
+This is noteworthy, as C balance is a delicate equilibrium between fluxes of *A~n~* and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions [@valentini2000respiration].
 These results infer that using fixed rates of respiration in models likely underestimates plant responses to sink limitation.
@@
 [-@delucia2007forest] that it is likely inappropriate to assume that respiration is a constant fraction of gross primary production in models.
-Our findings reveal that a combination of different mechanisms, beyond *A*, are likely at play in driving the observed seedling biomass response to sink manipulation.
+Our findings reveal that a combination of different mechanisms, beyond *A~n~*, are likely at play in driving the observed seedling biomass response to sink manipulation.
 However, the degree to which these mechanisms will regulate growth will undoubtedly shift across different experimental manipulations and plant species.
@@
 The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
-Our combined empirical and modeling approach shows that when non-photosynthesis parameters were kept constant changes in *A* were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
-K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A* through the demand for C.
+Our combined empirical and modeling approach shows that when non-photosynthesis parameters were kept constant changes in *A~n~* were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
+K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A~n~* through the demand for C.
 Although this may be true, our results infer that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.

### 2015-12-07 manuscript/manuscript_pve.Rmd
nlme package cite
labels names of tables editted

@@
 Tukey's post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
-A linear mixed effect model of A~max~ and leaf chemistry was performed using the 'nlme' package [@nlme] in R.
+A linear mixed effect model of A~max~ and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R.
 Explained variance (R^2^) of mixed models were computed as in  [@nakagawa2013general].
@@
 \
-**Table 2.** Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+**Table 2**.
+Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.
@@
 \
-**Table 3.** Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+**Table 3**.
+Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.
@@
 
-**Table 2.** Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+**Table 2**.
+Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.

### 2015-12-07 manuscript/manuscript_pve.Rmd
moved figures and tables in text
started a notes scripts

made a backup of table and figures for pubs

@@
 ```{r, echo=FALSE}
-allomfig <- "1"
-airvarsfig <- "2"
-allocfig <- "3"
-asatfig <- "4"
-achemfig <- "5"
-massmodelfig <- "6"
-massmodelfig2 <- "S1"
+allomfig <- "2.1"
+airvarsfig <- "2.2"
+allocfig <- "2.3"
+asatfig <- "2.4"
+achemfig <- "2.5"
+massmodelfig <- "2.6"
+massmodelfig2 <- "2.S1"
 ```
@@
 \
+```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=400, dev.args=list(type="cairo")}
+source("master_scripts/allometryplotting.R")
+```  
+\
+**Figure 2.1**.
+Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
+
+\
+```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+source("master_scripts/airvars_plotting.R")
+```  
+\
+**Figure 2.2**. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.
+
+\
 Total seedling biomass at harvest was significantly different across container volumes (P < 0.001) and between container treatments and free seedlings (P < 0.001, Table 1).
@@
 \
+**Table 1**.Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Each value reflects the mean(standard error) for each treatment.
+Seedling mass and leaf $\delta$^13^C values are from final harvest.
+Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6).
+Different letters represent significant differences between treatments.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
+
+```{r table1, echo=FALSE, warning=FALSE}
+greeks=c(alpha='\u03b1', Delta='\u0394', Sigma='\u03A3', mu='\u03bc',delta = '\u03b4')
+
+dust(table1)%>%
+  sprinkle_colnames("Volume (L)", 
+                        "Seedling mass (g)", 
+                        "SLA~TNC-free~ (m^2^ kg^-1^)",
+                        "Leaf Starch (%)", 
+                        "Leaf Sugars (%)", 
+                        "Leaf Nitrogen~TNC-free~ (%)",
+                        paste0("Leaf ", greeks['delta'],"^13^C"," (\u2030)")) %>%
+  sprinkle(rows= 1, part="head",bold=TRUE)%>%
+  sprinkle_print_method("markdown")
+```
+
+\
+```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+source("master_scripts/allocation_plotting.R")
+```  
+\
+**Figure 2.3**.
+Soil volume treatment means of biomass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c).
+For (b) lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment.
+For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (R^2^ = 0.82) with equation: log(x) = 0.983(log(y)) - 0.036.
+
+\
 Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table 2, P = 0.009).
@@
 Over the duration of the experiment SLA~f~ was higher in free seedlings, but was not different across containers sizes (Table 1, P < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (P < 0.001).
+
+\
+**Table 2**.
+Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Each value reflects the mean(standard error) for each treatment.
+All values are from the final harvest.
+Values for FRLD were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
+Different letters represent significant differences between treatments.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only differences between seedlings in containers.
+```{r table2, echo=FALSE, warning=FALSE}
+dust(table2)%>%
+  sprinkle_colnames("Volume (L)", 
+                        "Root Nitrogen (%)", 
+                        "SRL (m g^-1^)",
+                        "FRLD (m dm^-3^)") %>%
+  sprinkle(rows= 1, part="head",bold=TRUE)%>%
+  sprinkle_print_method("markdown")
+```
 
@@
 Overall, A~max~ was positively correlated with final harvest biomass across all seedlings (P < 0.001).
+
+\
+```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+source("master_scripts/A_stats_plotting.R")
+```
+
+\
+**Figure 2.4**.
+Soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25&deg;C.
+Different letters represent significant differences between treatments.
+
+\
+```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+source("master_scripts/Amax_TNC_N_plotting2.R")
+```  
+\
+**Figure 2.5**.
+Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).
+Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high.
+Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~mass~ as a function of starch and nitrogen.
+The marginal R^2^ (fixed effects only) was 0.37 and the conditional R^2^ (fixed and random effects) was 0.48 for the complete model.
 
@@
 As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
+
+\
+```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+source("master_scripts/massmodel_optimize.R")
+```  
+\
+**Figure 2.6**.
+Total carbon mass for harvested and modeled seedlings versus predicted total carbon gain after 120 days (a) and  reductions in final seedling carbon mass, both modeled and observed, as a function of the reduction in leaf photosynthesis across treatments (b).
+For (a) the dashed 1:1 identifies the difference between net total leaf carbon gain and gross seedling production.
+For (b) both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.
 
@@
 
-# List of Tables
-
-**Table 1**.Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
-Seedling mass and leaf $\delta$^13^C values are from final harvest.
-Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6).
-Different letters represent significant differences between treatments.
-The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
-
-\
-**Table 2**.
-Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
-All values are from the final harvest.
-Values for FRLD are only calculated for seedlings in containers as free seedlings have potentially unlimited soil volume to exploit.
-Different letters represent significant differences between treatments.
-The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only differences between seedlings in containers.
-
-\
-**Table 3**.
-Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
-A~max~, R and g~s~ are each measured at 25 &deg;C.
-Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n=6).
-R, J~max~ and Vc~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements.
-Different letters represent significant differences between treatments.
-The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
-
-\
-**Table S1**. Seedling growth model default parameters.
-
-# List of Figures
-**Figure 1**.
-Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
-
-\
-**Figure 2**. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.
-
-\
-**Figure 3**.
-Soil volume treatment means of biomass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c).
-For (b) lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment.
-For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (R^2^ = 0.82) with equation: log(x) = 0.983(log(y)) - 0.036.
-
-\
-**Figure 4**.
-Soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25&deg;C.
-Different letters represent significant differences between treatments.
-
-\
-**Figure 5**.
-Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).
-Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high.
-Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~mass~ as a function of starch and nitrogen.
-The marginal R^2^ (fixed effects only) was 0.37 and the conditional R^2^ (fixed and random effects) was 0.48 for the complete model.
-
-\
-**Figure 6**.
-Total carbon mass for harvested and modeled seedlings versus predicted total carbon gain after 120 days (a) and  reductions in final seedling carbon mass, both modeled and observed, as a function of the reduction in leaf photosynthesis across treatments (b).
-For (a) the dashed 1:1 identifies the difference between net total leaf carbon gain and gross seedling production.
-For (b) both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.
-
-\
-**Figure S1**.
-Sensitivity testing of seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50 % (b).
-Open and filled symbols represent default model and harvest values, while shaded symbols represent model sensitivity to each scenario by soil volume treatment.
-Both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.
-
-# Tables {.unnumbered}
-**Table 1**.Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
-Seedling mass and leaf $\delta$^13^C values are from final harvest.
-Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6).
-Different letters represent significant differences between treatments.
-The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
-
-```{r table1, echo=FALSE, warning=FALSE}
-greeks=c(alpha='\u03b1', Delta='\u0394', Sigma='\u03A3', mu='\u03bc',delta = '\u03b4')
-
-dust(table1)%>%
-  sprinkle_colnames("Volume (L)", 
-                        "Seedling mass (g)", 
-                        "SLA~TNC-free~ (m^2^ kg^-1^)",
-                        "Leaf Starch (%)", 
-                        "Leaf Sugars (%)", 
-                        "Leaf Nitrogen~TNC-free~ (%)",
-                        paste0("Leaf ", greeks['delta'],"^13^C"," (\u2030)")) %>%
-  sprinkle(rows= 1, part="head",bold=TRUE)%>%
-  sprinkle_print_method("markdown")
-```
-
-**Table 2**.
-Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
-All values are from the final harvest.
-Values for FRLD were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
-Different letters represent significant differences between treatments.
-The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only differences between seedlings in containers.
-```{r table2, echo=FALSE, warning=FALSE}
-dust(table2)%>%
-  sprinkle_colnames("Volume (L)", 
-                        "Root Nitrogen (%)", 
-                        "SRL (m g^-1^)",
-                        "FRLD (m dm^-3^)") %>%
-  sprinkle(rows= 1, part="head",bold=TRUE)%>%
-  sprinkle_print_method("markdown")
-```
-
-\
-**Table 3**.
-Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
-A~max~, R and g~s~ are each measured at 25 &deg;C.
-Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n=6).
-R, J~max~ and Vc~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements.
-Different letters represent significant differences between treatments.
-The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
-
-```{r table3, echo=FALSE, warning=FALSE}
-dust(table3)%>%
-  sprinkle_colnames("Volume (L)", 
-                        "A~max~ ($\\mu$mol m^-2^ s^-1^)", 
-                        "R ($\\mu$mol m^-2^ s^-1^)",
-                        "J~max~",
-                        "Vc~max~",
-                        "g~s~ (mol m^-2^ s^-1^)",
-                        "g~1~") %>%
-  sprinkle(rows= 1, part="head",bold=TRUE)%>%
-  sprinkle_print_method("markdown")
-```
-
-# Figures {.unnumbered}
-```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=400, dev.args=list(type="cairo")}
-source("master_scripts/allometryplotting.R")
-```
-
-**Figure 1**.
-
-```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
-source("master_scripts/airvars_plotting.R")
-```
-
-**Figure 2**.
-
-```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
-source("master_scripts/allocation_plotting.R")
-```
-
-**Figure 3**.
-
-```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
-source("master_scripts/A_stats_plotting.R")
-```
-
-**Figure 4**.
-
-```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
-source("master_scripts/Amax_TNC_N_plotting2.R")
-```
-
-**Figure 5**.
-
-```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
-source("master_scripts/massmodel_optimize.R")
-```
-
-**Figure 6**.
-
 # Supporting Information {.unnumbered}
-**Table S1**.Seedling growth model default parameters.
+**Table 2.S1**.Seedling growth model default parameters.
 
@@
 
-**Figure S1**.
+**Figure 2.S1**.
+Sensitivity testing of seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50 % (b).
+Open and filled symbols represent default model and harvest values, while shaded symbols represent model sensitivity to each scenario by soil volume treatment.
+Both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.
 

### 2015-12-07 manuscript/tablesfigures_backup.Rmd
moved figures and tables in text
started a notes scripts

made a backup of table and figures for pubs

--- 2015-12-07 manuscript/manuscript_pve.Rmd
@@
 ---
-title: "Below-ground sink limitation alters growth and carbon balance of Eucalyptus seedlings"
-author: ""
-date: ""
-output:
-  word_document:
-    reference_docx: manuscriptstyle.docx
-  pdf_document: default
-  html_document:
-    number_sections: yes
-csl: tree-physiology.csl
-bibliography: references.bib
+title: "tablesfigures"
+author: "Court Campany"
+date: "December 7, 2015"
+output: word_document
 ---
-
-\
-Courtney E. Campany^1^, Belinda Medlyn^1^, Remko A. Duursma^1^.
-
-\
-^1^ Hawkesbury Institute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW, Australia
-
-\
-*Corresponding author*: 
-Courtney Campany
-E: courtneycampany@gmail.com
 
@@
 ```{r, echo=FALSE}
-allomfig <- "1"
-airvarsfig <- "2"
-allocfig <- "3"
-asatfig <- "4"
-achemfig <- "5"
-massmodelfig <- "6"
-massmodelfig2 <- "S1"
+allomfig <- "2.1"
+airvarsfig <- "2.2"
+allocfig <- "2.3"
+asatfig <- "2.4"
+achemfig <- "2.5"
+massmodelfig <- "2.6"
+massmodelfig2 <- "2.S1"
 ```
-
-# Abstract {.unnumbered}
-
-Interpreting limitations to plant growth requires understanding of the balance between carbon (C) source and sink activity.
-This study used manipulations of soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
-We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown (free) seedlings.
-We developed a seedling growth model that utilized leaf photosynthesis rates (*A~n~*) to allocate daily C uptake towards mass growth of stems, leaves and roots.
-Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
-It was hypothesized that the soil volume effect would be largest in the smallest containers, negatively impacting mass partitioning belowground.
-An accumulation of leaf non-structural carbohydrates, resulting from reduced belowground sink strength, was expected to correlate to reductions in photosynthetic capacity.
-We observed a negative effect of container volume on aboveground growth soon after the experiment started.
-Although growth was consistently different across soil volumes, dry mass partitioning to leaves, stems and roots was unchanged after 120 days.
-Photosynthetic capacity was significantly reduced in containers compared to free seedlings, and was related to both leaf nitrogen content and starch accumulation.
-We then asked whether the observed reductions in *A~n~* explained the observed differences in seedling biomass.
-We found that although belowground sink limitation resulted in down regulation of *A~n~*, these reductions were not large enough to explain observed growth responses.
-Thus, as *A~n~* and growth were not tightly coordinated, excess photosynthetic C not attributed to biomass resulted in seedlings with soil volume restriction.
-These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that important feedbacks exist between belowground sink strength and leaf C uptake.
-
-## Keywords {.unnumbered}
-photosynthesis, growth, sink regulation, carbon allocation, soil volume
-
-# Introduction
-
-Understanding plant growth and its relationship to C assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
-As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues and organs.
-At long enough time scales leaf photosynthesis (*A~n~*) and respiratory losses together determine net C balance and will correlate to plant growth.
-At shorter temporal scales, however, growth can instead be mediated by tissue C storage pools.
-This has led to the current debate on how strongly plant growth is controlled by either source or sink activity.
-Consequently, plant growth cannot always be simply determined by the photosynthesis rate, making it complex to understand and challenging to model [@fourcaud2008plant].
-Despite a wealth of studies, large uncertainties still remain regarding the coordination of C supply and growth of woody species.
-
-\
-In woody species, the coordination of *A~n~* and growth has been studied with manipulations of C source activity.
-Examples included elevated CO~2~ experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments.
-Elevated CO~2~ has been shown to increase *A~n~* [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a stimulation of 23 % in forest biomass production [@norby2005forest].
-Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
-In partial defoliation experiments, increases in *A~n~* of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
-However, increases in *A~n~* in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
-These manipulations of C source activity expose unresolved issues with how changes in *A~n~* do not always infer similar responses in growth.
-
-\
-Alternatively, manipulating plant tissue C sinks is often used to investigate the correlation of *A~n~* and growth.
-This is because metabolic signaling networks, relaying information on C and N status of different tissues, can regulate photosynthetic activity [@paul2001sink].
-If sink inhibition of *A~n~* occurs, a close coordination between declines in *A* and growth should be expected.
-Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal, phloem girdling and low temperatures at high elevations.
-In these studies, down regulation of *A* was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
-However, reductions in *A~n~* were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
-These mixed results are not surprising as we still know little about the balance between assimilation, storage and growth across temporal scales in plants [@smith2007coordination].
-As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to the occurrence of large fruiting sinks, they tell us little about source-sink coordination in typical growing conditions for woody species.
-
-\
-An alternative experimental approach is to reduce belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size [@arp1991effects; @nesmith1998effect; @poorter2012pot].
-Possible advantages of this approach are that it allows a large range of treatment levels, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
-Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, *A~n~*, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
-Inadequate rooting volume may decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root].
-Container size studies frequently exhibit photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
-A meta-analysis by Poorter et al.
-[-@poorter2012pot] concluded that *A~n~* is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used.
-This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower C exchange and assimilate export rates [@robbins1988effect].
-However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].
-Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test the extent to which growth and *A~n~* are coordinated.
-
-\
-This study utilizes a novel field design to investigate the coordination between growth and *A~n~* in *Eucalyptus tereticornis* Sm.
-seedlings, by manipulating container size and thus rooting volume.
-Seedlings were maintained under well watered conditions in order to isolate the effect of restricted soil volume.
-We used freely-rooted seedlings as a control for the container size treatments.
-Empirical results were combined with a simple plant growth model to simulate seedling growth with a C mass balance approach, which was then compared to observed harvested seedling mass.
-The model used whole-plant C gain, scaled from instantaneous rates of leaf *A~n~*, to quantify seedling dry mass production over the 120 day experiment.
-
-\
-Our hypotheses were as follows:
-\
-1).
-The manipulations of container size were expected to induce a belowground sink limitation compared to free seedlings.
-We hypothesized that declines in seedling growth would be largest in the smallest containers.
-
-2).
-As the finite pool of rooting volume and soil nutrients will decline faster in trees growing in small containers, we expected reductions in partitioning to fine root mass relative to tree size with decreasing container size.
-
-3).
-Reduced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, and a resulting down regulation of A.
-We therefore expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume.
-
-4). Last, observed seedling mass was expected to correspond to growth model mass predicted from a simple C balance model taking into account measured rates of photosynthesis.
-
-# Materials and Methods
-
-## Experimental design
-This experiment was located at the Hawkesbury Forest Experiment site in Richmond, NSW, Australia.
-Plots were located in an open cover paddock that was converted from native pasture grasses.
-Top soils at this site are an alluvial formation of low-fertility sandy loam soils (380 and 108 mg kg^-1^ total N and phosphorus respectively) with low organic matter (0.7 %) and low water holding capacity.
-At this site a soil hard layer exists at ~1.0 m with a transition to heavy clay soils.
-The climate for the region is classified as sub-humid temperate.
-
-\
-*Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain cohort.
-Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.Previous pot experiments have confirmed that species with tap roots (similar to *E.
-tereticornis*) use the center of the container as the medium for thick roots leaving the periphery of the soil as the most active sites for fine root proliferation [@biran1980a; @biran1980b].
-By using a species with tap root growth and manipulations of container length rather than width, we believed that a more realistic test of growth inhibition through constrained soil volume would be achieved.
-
-\
-Six container volumes were used ranging from 5 L to 35 L, with a 22.5 cm diameter, and lengths ranging from 15 to 100 cm.
-Containers were constructed of PVC pipe and were filled with local top soil (described above).
-Soil in each container was packed to achieve a target soil bulk density that matched local soil conditions of 1.7 g cm^-3^.
-A Imidacloprid (BAYER CropScience) insecticide tablet was planted 5 cm below the roots of each seedling.
-Containers were planted flush with the soil surface inside metal sleeves, designed to minimize excess air space between the container and outside soil while also allowing for container removal.
-This allowed for soil temperatures in containers to reflect conditions of naturally planted ('free') seedlings.
-Each experimental block (n=7) contained a complete replicate set of six container volumes as well as one free seedling, with 1 m^2^ spacing.
-For each free seedling, used as the control, a 1 m^2^ subplot was excavated to the hard layer and replaced with the same soil used in each container.
-A border of root exclusion material was buried 0.25 m deep and extended 0.25 m above the ground surface around each subplot to exclude local vegetation.
-
-\
-Plants were watered weekly or when needed to maintain soil moisture at field capacity (13-15 %).
-Drain systems were built into each pot to prevent pooling of water throughout the experiment.
-Pooling of water could lead to an anaerobic environment around the root that could hinder the uptake of water through reduced root conductance [@poorter2009causes], an undesired experimental artifact.
-A collection compartment in the bottom of containers, containing gravel covered by root exclusion mesh, was used to collect excess water for 20, 25, and 35 l containers.
-Plastic tubing (6 mm diameter) was inset into the gravel layer and extended through the top of the container.
-A lysimeter pump was then used to suction excess water, through the tubing, as needed.
-For small containers (5, 10, and 15 L) a simple bottom plug was used to drain excess water from the gravel compartment.
-Each containers was inspected after every rainfall event to determine if pooling had occurred.
-
-## Growth and morphology metrics
-Seedlings were planted in summer (January 21^st^ 2013) and stem height, diameter at 15 cm and leaf count were measured weekly thereafter.
-Once the growth rate of individual plants had significantly declined a full biomass harvest was completed and the experiment ended (May 21^st^ 2013).
-Dry mass of leaves, stems, roots and total leaf area (LI-3100C Area Meter; LI-COR, Lincoln, NE, USA) were measured for each seedling.
-Mean individual leaf area for each harvested seedling was calculated by dividing total measured leaf area by total leaf count of only fully expanded leaves.
-Mean individual leaf area was then used to interpolate total seedling leaf area through time with weekly leaf counts.
-Root mass was collected by removing the roots system and passing soil from each container through a 1 mm sieve, washing, separating into fine and coarse roots (<2 mm and >2 mm diameter, respectively) and then drying to a constant mass.
-Roots of seedlings in containers were not considered pot bound, as clusters of roots along the soil-container interface were not observed.
-Roots from the free seedlings were collected by excavating each 1 m^2^ subplot to the hard layer and keeping only roots within the subplot.
-For each seedling, a sub-sample of washed fine roots was analyzed for root length using WhinoRhizo software (Regent Instruments Inc., Quebec, QC, Canada).
-Specific root length (SRL) is reported as the root length divided by the dry mass of each sub-sample (m g^-1^).
-Fine root length density (FRLD) for seedlings in containers is reported as the total fine root length divided by the volume of each container (m dm^-3^).
-
-## Photosynthetic parameters
-Leaf gas exchange measurements were performed fortnightly at saturating light (A~sat~) and saturating light and [CO~2~] (A~max~) on new fully expanded leaves.
-Measurements were initiated only after sufficient new leaf growth occurred (March 05^th^, 2013), approximately 6 weeks following planting, and continued until the biomass harvest.
-Leaf level gas exchange was measured with a standard leaf chamber (2 x 3 cm) equipped with blue-red light emitting diodes using a portable gas exchange system (LI-6400, LI-COR, Lincoln, NE, USA).
-A~sat~ measurements were made at PPFD of 1800 $\mu$mol m^-1^ s^-1^ and [CO~2~] of 400 $\mu$l l^-1^ and A~max~ with [CO~2~] of 1600 $\mu$l l^-1^ and PPFD of 1800 $\mu$mol photons m^-1^ s^-1^.
-This choice of light level to achieve light saturation is consistent with other studies on *Eucalyptus* species [@kallarackal1997ecophysiological;@pinkard1998photosynthetic;@crous2013photosynthesis;@drake2014capacity].
-These measurements were conducted during midday (10:00-14:00 h) with leaf temperature maintained at 25 &deg;C.
-After CO~2~ and water vapor flux values stabilized in the leaf chamber, net CO~2~ assimilation rate and stomatal conductance (g~s~) were logged 5 times and averaged for both A~sat~ and A~max~.
-
-\
-Photosynthetic CO~2~ response (AC~i~) curves were measured at 25 &deg;C on a random subset of each container size (n=3) after new leaves were first produced (March 13-14^th^, 2013) and prior to the final harvest (May 14-15~th~, 2013).
-Each AC~i~ curve was started at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light (above).
-From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011].
-
-\
-Leaf dark respiration rates (R) was measured on each seedling during the same dates as AC~i~ curves.
-Freshly detached leaves were collected at least 1 hour after sundown and placed inside a conifer chamber attached to the Licor 6400.
-Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions.
-Reported values of R are standardized rates at 25 &deg;C using a Q~10~ value (1.86) developed for these seedlings in a separate experiment (Drake et al.
-unpublished).
-Leaf area and dry mass were recorded for each leaf during gas exchange campaigns.
-
-## Leaf water potential
-Predawn ($\Psi$~pd~) and midday ($\Psi$~l~) leaf water potentials were measured for each seedling using a PMS 1505D pressure chamber (PMS Instruments, Albany, OR, USA) on fully expanded leaves during the same time period as AC~i~ and R.
-Leaves were detached and immediately stored inside foil covered bags before water potential measurements were performed.
-$\Psi$~pd~ was measured before sunrise and $\Psi$~l~ at midday 13:00-14:30 h.
-These measurements were used as a measure of static water stress on the seedlings [@sellin1999does] and to ensure that the bulk soil water availability was high enough for plants to avoid water stress as they became larger and roots filled the soil volume.
-
-## Leaf, root and soil chemistry
-Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of N content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
-Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis of N.
-Nitrogen concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of N~2~ and CO~2~).
-The percentage of N in the sample was calculated by comparison with certified standards.
-Leaf $\delta$^13^C was analyzed  with an Delta V Advantage coupled to a Flash HT and Conflo IV isotope ratio mass spectrometer.
-Leaf samples were flash combusted at 1000&deg;C to convert to CO~2~, feed to the mass spectrometer and isotopic signatures are reported relative to the VPDP scale.
-
-\
-Leaf total non-structural carbohydrate (TNC) concentration was analyzed on dried and milled leaf samples using a total starch assay kit (Megazyme International, Wicklow, Ireland) and includes the starch  and soluble sugar concentrations (mg g^-1^).
-Starch was quantified using a thermostable $\alpha$-amylase and amyloglucosidase assay [@McCleary_starch] and soluble sugars were determined following the anthrone method [@ebell1969variation].
-Complete methods of the TNC assay are described in [@mitchell2013drought].
-TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, were calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf N content.
-Similarly, TNC-free leaf N (N~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC and leaf N content.
-
-## Seedling growth model
-We developed a simple seedling growth model that utilized leaf *A* rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
-The model begins with mean initial tissue component biomass (leaf~i~, stem~i~ and root~i~) and a starting leaf area (LA~i~) measured prior to planting.
-The initial biomass of roots was divided evenly between fine and coarse roots.
-The daily net biomass production of seedlings (P~i~) is then given by
-
-\
-(1)
-$$P_i = L\left(\frac{C_{day'i}~\sigma_s}{\epsilon_c}\right) - R$$
-where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^), $\sigma$~s~ is a self shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and R is the mass based total respiration of all tissue components (g C d^-1^).
-Total respiration was calculated as
-
-\
-(2)
-$$R = \Sigma(R_c~M_c)$$
-where R~c~ is published or local tissue respiration rates of fine roots, coarse roots or stems (Table S1, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
-R~leaf~ is represented in the calculation of C~day~ (described below).
-The change in individual component biomass (M~c~), here solved on a daily time step, is given by
-
-\
-(3)
-$$\frac{dM_c}{dt} = A_{c}~P_{i}~-~(\Lambda_{c}~M_{c})$$
-where A~c~ is the component specific biomass partitioning  to whole plant biomass (%) and $\Lambda$~c~ is component specific turnover rate (yr^-1^).
-Because we did not observe branch turnover, $\Lambda$~stem~ was assumed to equal 0.
-Total seedling biomass, per time step, was then equal to the sum of all biomass components; leaves, stems, fine roots and coarse roots.
-
-\
-C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package in R with the mean photosynthetic parameters (J~max~, V~cmax~, R and g~1~) for each treatment and meteorological data from an onsite weather station.
-J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), R was empirically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed g~s~ values.
-Methods of the coupled leaf gas exchange model are described in Duursma et al [-@duursma2014peaked].
-Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A* rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
-C~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
-This resulted in 120 unique values of C~day~ for each soil volume treatment, one value for each day of the experiment.
-Thus, each daily time step for model runs included a value of C~day~ that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
-
-\
-It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf *A* with total plant leaf area.
-This was accomplished by utilizing 61 previously digitized Eucalyptus seedlings, covering 5 total species which include *E.
-tereticornis*, from Duursma et al.
-[-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
-Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
-The ratio of total *A* with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments.
-Next, the linear relationship between $\sigma$~s~ and total leaf area was for determined across digitized seedlings, within each treatment.
-For the growth model, $\sigma$~s~ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to C~day,i~.
-All default parameters used in model simulations are reported in Table S1.
-
-\
-We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A* where sufficient to accurately predict overall seedling biomass production after 120 days.
-Each model run utilized changes in *A* and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
-Cumulative net leaf C gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling C was assumed to equal half of the final mass for both modeled and observed seedlings.
-
-\
-First, a default model was fitted with mean photosynthetic parameters from the free seedlings and then optimized to produce a LMF which correctly predicted both the leaf mass and total biomass of the harvested free seedling (M~free~).
-This optimized LMF was then used to constrain model runs with soil volume treatment specific C~day~, while keeping tissue respiration and turnover parameters constant, to determine if changes in leaf A alone could predict biomass of seedlings in containers (M~pots~).
-Next, model sensitivity to different C allocation scenarios, including observed treatment specific LMF and up regulation of non-leaf tissue respiration by 50 % of default values (M~S1~ and M~S2~, respectively), was used to improve model biomass predictions compared to measured harvest biomass.
-For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment specific mean C~day~ by first scaling values to the free seedling control.
-
-##Data analysis
-Differences in experimental parameters with soil volume were analysed by mixed-effects models in R with individual containers and experimental blocks as random effects and soil volume treatment as a categorical fixed effect with seven levels.
-Tukey's post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
-A linear mixed effect model of A~max~ and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R.
-Explained variance (R^2^) of mixed models were computed as in  [@nakagawa2013general].
-Tests of allometric relationships between log-transformed biomass components were implemented using standardized major axis regression in the 'smatr' package in R [@warton2012smatr].
-All tests of statistical significance were conducted at an alpha level of 0.05.
-
-# Results
-
-## Growth and morphology
-Plant height, diameter and leaf area diverged between container volumes soon after start of the experiment (Figure `r allomfig`).
-First, seedling leaf area significantly diverged between soil volumes (P < 0.029) during the 5^th^ week of the experiment.
-Following this period both height (8^th^) week) and then diameter (9^th^ week) significantly deviated across soil volumes (P < 0.045 & 0.035, respectively).
-The large reductions in height gain and total leaf area in smaller compared to larger containers continued throughout the experiment.
-In this field study, colder temperatures and reductions in total PPFD per day (Figure `r airvarsfig`) likely slowed the growth of seedlings in the final weeks of the experiment (Figure `r allomfig`).
-Seedlings maintained diameter growth throughout the experiment, although marginal with smaller soil volumes in the final month.
-Final seedling height significantly increased with increasing soil volume (P < 0.001).
-Increases in both final stem diameter (P < 0.001) and cumulative leaf area (both P < 0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling treatments.
-
-\
-Total seedling biomass at harvest was significantly different across container volumes (P < 0.001) and between container treatments and free seedlings (P < 0.001, Table 1).
-On average, harvested biomass of free seedlings was 84% higher than seedlings in containers.
-Plant biomass was positively correlated with total leaf area across all treatments (R^2^ = 0.97, P < 0.001).
-Differences in biomass partitioning to leaves, stems and roots were not different across soil volumes after variation in seedling biomass across treatments was factored in the analysis (Figure `r allocfig`a,b).
-Across all treatments, the final harvest root:shoot biomass ratio was conserved in these seedlings which exhibited a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119]) and a near identical ratio of leaf to fine root mass (Figure `r allocfig`c).
-
-\
-Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table 2, P = 0.009).
-Fine root length density was significantly higher in the two smallest container sizes and was the lowest in the largest container size (Table 2, P < 0.001).
-Over the duration of the experiment SLA~f~ was higher in free seedlings, but was not different across containers sizes (Table 1, P < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (P < 0.001).
-
-## Leaf and root chemistry
-Leaf N~f~ was significantly higher in free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, P < 0.001).
-Throughout the remainder of the experiment the smallest container volume had a significant reduction in leaf N~f~ compared to other soil volumes, while free seedlings maintained the highest leaf N~f~ (Table 1, P < 0.001).
-Leaf starch content in the smallest container was ca.
-double  that of free seedlings (P = 0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table 1).
-Differences in leaf starch between the free seedling and the smallest container were evident during the first gas exchange campaign (P = 0.001).
-Root N was higher in free seedlings compared to seedlings in containers but only for some of the container size treatments (Table 2).
-
-## Gas exchange and photosynthetic parameters
-At the first measurement campaign, both A~sat~ and A~max~ were significantly higher in the free seedling treatment compared to seedlings in containers (both P < 0.001).
-Across all measurement campaigns mean A~sat~ (Figure `r asatfig`) and A~max~ (Table 3) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
-The relationships between photosynthetic capacity, leaf starch and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001).
-We used predictions from the linear mixed effect model equation to visualize these relationship of A~max~ to either leaf N content or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
-Across all measurement campaigns and treatments A~max~ was higher when leaf N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
-A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b).
-Overall, A~max~ was positively correlated with final harvest biomass across all seedlings (P < 0.001).
-
-\
-Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table 3).
-Leaf dark respiration rates were not significantly different across soil volumes (Table 3).
-The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table 3).
-
-\
-Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 MPa across all seedlings, respectively.
-Although g~s~ in free seedlings was generally higher than those in containers (Table 3.
-P < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
-Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table 1).
-Combined these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment.
-Soil N at harvest was not different across soil volumes ($\bar{x}$ = 4.5 %), with minimal decreases from pre-planting value ($\bar{x}$ = 4.9 %).
-This indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
-
-## Modelling seedling biomass
-The default model M~free~, successfully optimized a LMF (21.6 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %.
-Using this optimized LMF, the total biomass of modeled seedlings for each soil volume treatment (M~pots~) were on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf C gain (Figure `r massmodelfig`a).
-Thus, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments (Figure `r massmodelfig`b).
-As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
-
-\
-Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over predictions of seedling C mass.
-Testing the sensitivity of the model to observed treatment-specific LMF from the final harvest (M~S1~), which were each lower than the optimized LMF value (see Figure `r allocfig`a), improved model predictions of seedling C mass but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
-Using harvest values of LMF, however, does not capture the observed increase in leaf turnover of seedlings in small containers (Figure `r allomfig`c).
-Thus, the use of harvest LMF values for seedlings in containers in M~S1~ likely underestimates daily C allocation to leaves over the final months of the experiment.
-Increases of 50 % in non-leaf tissue respiration (M~S2~) improved biomass estimates slightly but overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
-With M~S2~, non-tissue respiration rates would need to be increased by ca.
-250% in order for mass balance to be achieved.
-
-# Discussion
-This study utilized a simple but novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
-We addressed questions regarding the coordination of *A~n~* and growth by complementing empirical results with a C mass balance model.
-We found that reductions in leaf *A~n~* across container sizes, when integrated across the 120 day experiment, were alone insufficient to account for observed reductions in total plant biomass production.
-
-## Reductions in growth and physiology under sink limitation
-Soon after seedlings became established both height and diameter growth were negatively affected by decreasing soil volume.
-This led to the large reductions in biomass in small containers, compared to freely rooted seedlings.
-We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, consistent with the meta-analysis of Poorter et al.
-[-@poorter2012pot].
-These growth reductions were expected, as the impedance of root growth can cause reductions in overall plant growth and activity [@mcconnaughay1991physical; @young1997mechanical].
-It has been shown that roots subjected to environmental stress may send inhibitory signals to the shoots that affect g~s~, cell expansion, cell division and the rate of leaf appearance [@passioura2002soil].
-Here, this was evident in a large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
-
-\
-Decreases in A~sat~ occurred at the same time as reductions in height and diameter of seedlings in containers.
-This initially suggests a strong link between growth and an apparent down regulation of *A~n~*.
-However, there are several possible mechanisms that can explain reduced *A~n~* in small containers including nutrient content, water or reduced sink strength [@poorter2012pot].
-It was therefore necessary to examine each of these factors to determine if the induced belowground sink limitation actually triggered photosynthetic down regulation.
-
-\
-With high rates of g~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A~n~*.
-This finding is consistent with other container size studies without drought treatments.
-For example, reduced A~max~ in cotton seedlings grown at elevated CO~2~ was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased g~s~ [@thomas1991root].
-Additionally, severe reductions in *A~n~* in coffee plants were not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
-It is likely that reductions in *A~n~* of well-watered seedlings observed in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
-
-\
-Here, reductions in *A~n~* were positively correlated with decreases in leaf N and leaf N was considerably reduced for seedlings in containers.
-As leaf N reductions were detected with TNC-free leaf mass, this suggests that physical root restriction or decreased supply likely affected seedling N uptake instead of TNC dilution in leaves in the smallest containers.
-Root N at the end of the experiment was on average higher in free seedlings but not consistently higher than every container volume treatment.
-Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N in free seedlings, but this effect is unknown.
-Combined with the fact that soil N declined evenly across all treatments, there was no clear mechanism present to identify changes in root N uptake between free seedlings and seedlings in containers.
-In these already low quality soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
-Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the affects of belowground sink limitation on *A~n~* of seedlings in containers was evident throughout the experiment.
-
-\
-As both rooting space and resources were finite in containers, the inability of seedlings to maintain the capacity of the belowground C sink resulted in the buildup of C assimilate in leaves.
-The feedback inhibition of *A~n~* from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process (Nebauer et al.
-2011).
-Here, declines in A~max~ were correlated with higher starch content throughout the experiment.
-This agrees with a study on a deciduous conifer by Equiza et al.
-[-@equiza2006photosynthetic] where photosynthetic downregulation from reduced sink strength was correlated with starch content.
-As starch content in leaves of plants grown in the smallest containers was nearly double that of free seedlings in our study, this suggests the response of *A~n~* to sink inhibition was regulated by this accumulation, as hypothesized.
-
-## Biomass partitioning under sink limitation
-As biomass partitioning is likely controlled by the source and sink strength of all organs [@poorter2012biomass], it was important to determine which tissue components were most affected by the container size treatments.
-It was necessary to distinguish if growth was affected beyond ontogenetic constraints, by correcting for size, as biomass distribution is strongly size-dependent [@gould1966allometry; @lleonart2000removing].
-In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, outside of ontogenetic drift (Figure `r allocfig`a,b).
-This is a surprising result as shifts in allocation have been noted specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein].
-Surprisingly, a constant ratio of fine root mass to leaf mass was observed across all treatments suggesting a functional partitioning response to optimize resource gain did not occur.
-
-\
-As partitioning to fine roots did not change this provides evidence against an optimal foraging strategy for seedlings in containers.
-This could be because lateral root development is affected by inanimate obstacles and avoiding growth towards container walls could improve the efficiency of resource allocation [@falik2005root].
-The sensitivity of roots to their own exudates near obstructions may prevent further growth [@semchenko2008foraging].
-Here, we show that FRLD was highest in smallest containers suggesting that root restriction likely occurred as simple function of available rooting space.
-Alternatively, physical restriction of root proliferation could also have impacted root development and morphology prior to shifts in mass partitioning.
-Here, increases in SRL where detected in several of the soil volume treatments.
-This is not surprising as plants in containers have been shown to have different root morphology to field grown plants [@nesmith1998effect].
-The poor soil quality used in our experiment and root restriction, however, likely decreased the capacity of this morphological response to increase N uptake.
-
-## Do reductions in photosynthesis explain reductions in seedling growth?
-Our model used a simple approach to drive seedling growth with measured reductions in leaf *A~n~* , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
-Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
-Although reductions in A~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
-[-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A~n~* can not fully explain explain reduced seedling growth.
-These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
-It is possible that the overestimation of growth was due to an initial overestimation of *A~n~*, however, the robust empirical based methods used to generate photosynthetic parameters (J~max~, V~cmax~, R and g~1~) make this unlikely.
-Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A~n~* affect models which distinguish the fate of assimilate C within a plant.
-Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven  plant growth models, yet C partitioning remains a key weakness  [@lacointe2000carbon].
-To address this issue, we utilized the flexibility of this model to test plausible fates of the pool of simulated non-biomass C unaccounted for with observed mass balance.
-Similar to Lohier et al.
-[-@lohier2014explaining] we manipulated processes contributing to modeled seedling C mass balance, including changes to leaf C allocation or non-leaf tissue respiration, to quantitatively test their respective influences on model predictions.
-
-\
-Using measured LMF from the harvest, instead of the optimized seedling control (M~S1~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond *A~n~*.
-The sensitivity of the model to shifts in LMF could represent leaf loss throughout the experiment that could not be explicitly quantified in this field study.
-As TNC accumulation can lead to accelerated leaf senescence [@paul2001sink], this could explain the observed decline in total leaf area of seedlings in small containers.
-Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A~n~* and the fate of C allocated to growth, respiration and C storage in leaves.
-It will be the interactions between these two components that will determine the total C gain available for plant growth.
-
-\
-Increasing rates of non-leaf respiration (M~S2~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation.
-We also show that very large increases in non-leaf respiration rates would have been required to accurately predict observed seedling biomass.
-Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], results from M~S2~ highlight a lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change.
-This is noteworthy, as C balance is a delicate equilibrium between fluxes of *A~n~* and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions [@valentini2000respiration].
-These results infer that using fixed rates of respiration in models likely underestimates plant responses to sink limitation.
-Thus, we agree with Delucia et al.
-[-@delucia2007forest] that it is likely inappropriate to assume that respiration is a constant fraction of gross primary production in models.
-Our findings reveal that a combination of different mechanisms, beyond *A~n~*, are likely at play in driving the observed seedling biomass response to sink manipulation.
-However, the degree to which these mechanisms will regulate growth will undoubtedly shift across different experimental manipulations and plant species.
-
-## Conclusions
-With a novel field-based design we detected a massive effect of container volume on seedling growth, not between containers but with naturally planted seedlings.
-This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants has seldom been studied.
-Although biomass partitioning was conserved, our empirical and model results suggest that the amount of photosynthate allocated to non-biomass pools such as TNC or respiration were likely altered by sink inhibition.
-The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
-Our combined empirical and modeling approach shows that when non-photosynthesis parameters were kept constant changes in *A~n~* were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
-K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A~n~* through the demand for C.
-Although this may be true, our results infer that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
-Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
-The approach used here has the flexibility to account for multiple drivers of C allocation and provides an avenue to address future questions regarding the impact of environmental change on plant growth.
 
@@
 # Figures {.unnumbered}
+
 ```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=400, dev.args=list(type="cairo")}
@@
 **Figure S1**.
-
-# References {.unnumbered}

### 2015-12-07 reproducibility_notes.R

@@ -1,0 +1,10 @@
+###reproducibility notes
+
+
+###between thesis and pub
+
+#1. I saved the figures and tables in a secondary RMD, maybe easier to convert back from thesis (which are inbedded)
+#2. Figure #s in thesis inbedded have been re# with thesis chapter Figure #.#
+#3. Likely will need to use pdf figures anyway, but then a list of figure tables is available.
+
+#4. for RMD will use two dummy docx files for thesis and pub, thesis will need to reflect binding requirements.

### 2015-12-07 manuscript/manuscript_pve.Rmd
fixed chapters figure #s
tables now automated

@@
 massmodelfig2 <- "2.S1"
+
+pvetab1 <- "2.1"
+pvetab2 <- "2.2"
+pvetab3 <- "2.3"
+pvetabS <- "2.S3"
+
 ```
@@
 $$R = \Sigma(R_c~M_c)$$
-where R~c~ is published or local tissue respiration rates of fine roots, coarse roots or stems (Table S1, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
+where R~c~ is published or local tissue respiration rates of fine roots, coarse roots or stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
 R~leaf~ is represented in the calculation of C~day~ (described below).
@@
 For the growth model, $\sigma$~s~ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to C~day,i~.
-All default parameters used in model simulations are reported in Table S1.
+All default parameters used in model simulations are reported in Table `r pvetabS`.
 
@@
 \
-Total seedling biomass at harvest was significantly different across container volumes (P < 0.001) and between container treatments and free seedlings (P < 0.001, Table 1).
+Total seedling biomass at harvest was significantly different across container volumes (P < 0.001) and between container treatments and free seedlings (P < 0.001, Table `r pvetab1`).
 On average, harvested biomass of free seedlings was 84% higher than seedlings in containers.
@@
 \
-**Table 1**.Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+**Table 2.1**.Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
 Each value reflects the mean(standard error) for each treatment.
@@
 \
-Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table 2, P = 0.009).
-Fine root length density was significantly higher in the two smallest container sizes and was the lowest in the largest container size (Table 2, P < 0.001).
-Over the duration of the experiment SLA~f~ was higher in free seedlings, but was not different across containers sizes (Table 1, P < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (P < 0.001).
+Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table `r pvetab2`, P = 0.009).
+Fine root length density was significantly higher in the two smallest container sizes and was the lowest in the largest container size (Table `r pvetab2`, P < 0.001).
+Over the duration of the experiment SLA~f~ was higher in free seedlings, but was not different across containers sizes (Table `r pvetab1`, P < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (P < 0.001).
 
 \
-**Table 2**.
+**Table 2.2**.
 Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
@@
 Leaf N~f~ was significantly higher in free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, P < 0.001).
-Throughout the remainder of the experiment the smallest container volume had a significant reduction in leaf N~f~ compared to other soil volumes, while free seedlings maintained the highest leaf N~f~ (Table 1, P < 0.001).
+Throughout the remainder of the experiment the smallest container volume had a significant reduction in leaf N~f~ compared to other soil volumes, while free seedlings maintained the highest leaf N~f~ (Table `r pvetab1`, P < 0.001).
 Leaf starch content in the smallest container was ca.
-double  that of free seedlings (P = 0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table 1).
+double  that of free seedlings (P = 0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table `r pvetab1`).
 Differences in leaf starch between the free seedling and the smallest container were evident during the first gas exchange campaign (P = 0.001).
-Root N was higher in free seedlings compared to seedlings in containers but only for some of the container size treatments (Table 2).
+Root N was higher in free seedlings compared to seedlings in containers but only for some of the container size treatments (Table `r pvetab2`).
 
@@
 At the first measurement campaign, both A~sat~ and A~max~ were significantly higher in the free seedling treatment compared to seedlings in containers (both P < 0.001).
-Across all measurement campaigns mean A~sat~ (Figure `r asatfig`) and A~max~ (Table 3) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
+Across all measurement campaigns mean A~sat~ (Figure `r asatfig`) and A~max~ (Table `r pvetab3`) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
 The relationships between photosynthetic capacity, leaf starch and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001).
@@
 \
-Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table 3).
-Leaf dark respiration rates were not significantly different across soil volumes (Table 3).
-The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table 3).
+Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab2`).
+Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab2`).
+The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab2`).
 
@@
 Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 MPa across all seedlings, respectively.
-Although g~s~ in free seedlings was generally higher than those in containers (Table 3.
-P < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
-Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table 1).
+Although g~s~ in free seedlings was generally higher than those in containers (Table `r pvetab2`, P < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
+Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table `r pvetab1`).
 Combined these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment.

### 2015-12-08 manuscript/manuscript_pve.Rmd
text edits
changed dpi=600 on figures

@@
 \
-```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/allometryplotting.R")
@@
 \
-```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/airvars_plotting.R")
@@
 \
-```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/allocation_plotting.R")
@@
 \
-```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/A_stats_plotting.R")
@@
 \
-```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/Amax_TNC_N_plotting2.R")
@@
 \
-```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/massmodel_optimize.R")
@@
 
-```{r model_scenarios, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r model_scenarios, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/massmodel_optimize_scenarios.R")

### 2015-12-08 manuscript/tablesfigures_backup.Rmd
changed dpi=600 on figures

@@
 
-```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/allometryplotting.R")
@@
 
-```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/airvars_plotting.R")
@@
 
-```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/allocation_plotting.R")
@@
 
-```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/A_stats_plotting.R")
@@
 
-```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/Amax_TNC_N_plotting2.R")
@@
 
-```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
+```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/massmodel_optimize.R")

### 2015-12-08 manuscript/manuscript_pve.Rmd
switched to thesis docx for margins

@@
   word_document:
-    reference_docx: manuscriptstyle.docx
+    reference_docx: manuscriptstyle_thesis.docx
   pdf_document: default

### 2015-12-08 manuscript/manuscript_pve.Rmd
figure spacing for thesis

--- 2015-12-08 manuscript/manuscript_pve.Rmd
@@
     number_sections: yes
+
 csl: tree-physiology.csl
@@
 Increases in both final stem diameter (P < 0.001) and cumulative leaf area (both P < 0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling treatments.
-
 \
@@
 Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
-
 \
-```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
+```{r airvars, fig.width=6, fig.height=7.8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/airvars_plotting.R")
@@
 ```
-
 \
@@
 ```  
+\
 \
@@
 Overall, A~max~ was positively correlated with final harvest biomass across all seedlings (P < 0.001).
-
 \
@@
 ```  
-
 \
@@
 Different letters represent significant differences between treatments.
-
 \
@@
 As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
-
 \
@@
 ```  
+\
+\
 \
@@
 ```  
-
+\
+\
+\
 **Figure 2.S1**.

### 2015-12-08 reproducibility_notes.R

@@ -8,3 +8,6 @@
 #3. Likely will need to use pdf figures anyway, but then a list of figure tables is available.
 
 #4. for RMD will use two dummy docx files for thesis and pub, thesis will need to reflect binding requirements.
+
+
+##airvars fig: height=8

### 2015-12-08 manuscript/manuscript_pve.Rmd
added chapter heading
added chapter#s to section

removed key words and author correspondence

@@
 ---
-title: "Below-ground sink limitation alters growth and carbon balance of Eucalyptus seedlings"
+title: |
+  | Chapter 2 
+  | Below-ground sink limitation alters growth and carbon balance of Eucalyptus seedlings
 author: ""
@@
 
-\
-*Corresponding author*: 
-Courtney Campany
-E: courtneycampany@gmail.com
+<!-- \ -->
+<!-- *Corresponding author*:  -->
+<!-- Courtney Campany -->
+<!-- E: courtneycampany@gmail.com -->
 
@@
 
-# Abstract {.unnumbered}
+#2.1  Abstract
 
@@
 
-## Keywords {.unnumbered}
-photosynthesis, growth, sink regulation, carbon allocation, soil volume
+<!-- ## Keywords {.unnumbered} -->
+<!-- photosynthesis, growth, sink regulation, carbon allocation, soil volume -->
 
-# Introduction
+#2.2  Introduction
 
@@
 
-# Materials and Methods
+#2.3  Materials and Methods
 
-## Experimental design
+##2.3.1 Experimental design
 This experiment was located at the Hawkesbury Forest Experiment site in Richmond, NSW, Australia.
@@
 
-## Growth and morphology metrics
+##2.3.2 Growth and morphology metrics
 Seedlings were planted in summer (January 21^st^ 2013) and stem height, diameter at 15 cm and leaf count were measured weekly thereafter.
@@
 
-## Photosynthetic parameters
+##2.3.3 Photosynthetic parameters
 Leaf gas exchange measurements were performed fortnightly at saturating light (A~sat~) and saturating light and [CO~2~] (A~max~) on new fully expanded leaves.
@@
 
-## Leaf water potential
+##2.3.4 Leaf water potential
 Predawn ($\Psi$~pd~) and midday ($\Psi$~l~) leaf water potentials were measured for each seedling using a PMS 1505D pressure chamber (PMS Instruments, Albany, OR, USA) on fully expanded leaves during the same time period as AC~i~ and R.
@@
 
-## Leaf, root and soil chemistry
+##2.3.5 Leaf, root and soil chemistry
 Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of N content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
@@
 
-## Seedling growth model
+##2.3.6 Seedling growth model
 We developed a simple seedling growth model that utilized leaf *A* rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
@@
 
-##Data analysis
+##2.3.7 Data analysis
 Differences in experimental parameters with soil volume were analysed by mixed-effects models in R with individual containers and experimental blocks as random effects and soil volume treatment as a categorical fixed effect with seven levels.
@@
 
-# Results
+#2.4 Results
 
-## Growth and morphology
+##2.4.1 Growth and morphology
 Plant height, diameter and leaf area diverged between container volumes soon after start of the experiment (Figure `r allomfig`).
@@
 
-## Leaf and root chemistry
+##2.4.2 Leaf and root chemistry
 Leaf N~f~ was significantly higher in free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, P < 0.001).
@@
 
-## Gas exchange and photosynthetic parameters
+##2.4.3 Gas exchange and photosynthetic parameters
 At the first measurement campaign, both A~sat~ and A~max~ were significantly higher in the free seedling treatment compared to seedlings in containers (both P < 0.001).
@@
 
-## Modelling seedling biomass
+##2.4.4 Modelling seedling biomass
 The default model M~free~, successfully optimized a LMF (21.6 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %.
@@
 
-# Discussion
+#2.5  Discussion
 This study utilized a simple but novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
@@
 
-## Reductions in growth and physiology under sink limitation
+##2.5.1 Reductions in growth and physiology under sink limitation
 Soon after seedlings became established both height and diameter growth were negatively affected by decreasing soil volume.
@@
 
-## Biomass partitioning under sink limitation
+##2.5.2 Biomass partitioning under sink limitation
 As biomass partitioning is likely controlled by the source and sink strength of all organs [@poorter2012biomass], it was important to determine which tissue components were most affected by the container size treatments.
@@
 
-## Do reductions in photosynthesis explain reductions in seedling growth?
+##2.5.3 Do reductions in photosynthesis explain reductions in seedling growth?
 Our model used a simple approach to drive seedling growth with measured reductions in leaf *A~n~* , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
@@
 
-## Conclusions
+##2.5.4 Conclusions
 With a novel field-based design we detected a massive effect of container volume on seedling growth, not between containers but with naturally planted seedlings.
@@
 
-# Supporting Information {.unnumbered}
+#2.6  Supporting Information
 **Table 2.S1**.Seedling growth model default parameters.

### 2015-12-09 manuscript/manuscript_pve.Rmd
text edits
hid authors for thesis, this version goes to RD as first whole thesis draft

@@
 
-\
-Courtney E. Campany^1^, Belinda Medlyn^1^, Remko A. Duursma^1^.
+<!-- \ -->
+<!-- Courtney E. Campany^1^, Belinda Medlyn^1^, Remko A. Duursma^1^. -->
 
-\
-^1^ Hawkesbury Institute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW, Australia
+<!-- \ -->
+<!-- ^1^ Hawkesbury Institute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW, Australia -->
 
@@
 This has led to the current debate on how strongly plant growth is controlled by either source or sink activity.
-Consequently, plant growth cannot always be simply determined by the photosynthesis rate, making it complex to understand and challenging to model [@fourcaud2008plant].
+Consequently, plant growth cannot always be simply determined by *A~n~*, making it complex to understand and challenging to model [@fourcaud2008plant].
 Despite a wealth of studies, large uncertainties still remain regarding the coordination of C supply and growth of woody species.
@@
 *Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain cohort.
-Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.Previous pot experiments have confirmed that species with tap roots (similar to *E.
+Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.
+Previous container experiments have confirmed that species with tap roots (similar to *E.
 tereticornis*) use the center of the container as the medium for thick roots leaving the periphery of the soil as the most active sites for fine root proliferation [@biran1980a; @biran1980b].
@@
 Here, we show that FRLD was highest in smallest containers suggesting that root restriction likely occurred as simple function of available rooting space.
-Alternatively, physical restriction of root proliferation could also have impacted root development and morphology prior to shifts in mass partitioning.
+Additionally, physical restriction of root proliferation could have impacted root development and morphology prior to shifts in mass partitioning.
 Here, increases in SRL where detected in several of the soil volume treatments.
@@
 Although reductions in A~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
-[-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A~n~* can not fully explain explain reduced seedling growth.
+[-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A~n~* do not fully explain reduced seedling growth.
 These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
@@
 Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A~n~* affect models which distinguish the fate of assimilate C within a plant.
-Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven  plant growth models, yet C partitioning remains a key weakness  [@lacointe2000carbon].
+Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven  plant growth models [@lacointe2000carbon].
 To address this issue, we utilized the flexibility of this model to test plausible fates of the pool of simulated non-biomass C unaccounted for with observed mass balance.

### 2015-12-09 manuscript/manuscript_pve.Rmd
text edit

@@
   | Chapter 2 
-  | Below-ground sink limitation alters growth and carbon balance of Eucalyptus seedlings
+  | Belowground sink limitation alters growth and carbon balance of Eucalyptus seedlings
 author: ""

### 2015-12-09 manuscript/manuscript_pve.Rmd
failed changes to doc.x
this manuscrupt saved as thesis draft 1

@@
 Thus, as *A~n~* and growth were not tightly coordinated, excess photosynthetic C not attributed to biomass resulted in seedlings with soil volume restriction.
-These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirms that important feedbacks exist between belowground sink strength and leaf C uptake.
+These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf C uptake.
 
@@
 \
-```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=600, dev.args=list(type="cairo")}
+```{r allometry, fig.width=6, fig.height=7.6, echo=FALSE,  dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/allometryplotting.R")
@@
 \
-```{r airvars, fig.width=6, fig.height=7.8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
+```{r airvars, fig.width=6, fig.height=7.6, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
 source("master_scripts/airvars_plotting.R")

### 2015-12-09 reproducibility_notes.R

@@ -10,7 +10,7 @@
 #4. for RMD will use two dummy docx files for thesis and pub, thesis will need to reflect binding requirements.
 
 
-##airvars fig: height=8
+##airvars/allometry fig: height=8
 ### Abstract {.unnumbered} (not sure what .unnub does)
 
 ##key words commented out

### 2015-12-09 manuscript/manuscript_pve.Rmd
last spelling check

@@
 In these already low quality soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
-Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the affects of belowground sink limitation on *A~n~* of seedlings in containers was evident throughout the experiment.
+Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the effects of belowground sink limitation on *A~n~* of seedlings in containers was evident throughout the experiment.
 

### 2015-12-14 manuscript/manuscript_pve.Rmd
abbreviation changes (added to notes).
manuscripts edits made to all documents and in thesis word document

@@
 ---
-title: |
-  | Chapter 2 
-  | Belowground sink limitation alters growth and carbon balance of Eucalyptus seedlings
+title: Belowground sink limitation alters growth and carbon balance of *Eucalyptus* seedlings
 author: ""
@@
 
-<!-- \ -->
-<!-- Courtney E. Campany^1^, Belinda Medlyn^1^, Remko A. Duursma^1^. -->
+\
+Courtney E. Campany^1^, Belinda Medlyn^1^, Remko A. Duursma^1^.
 
-<!-- \ -->
-<!-- ^1^ Hawkesbury Institute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW, Australia -->
+\
+^1^ Hawkesbury Institute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW, Australia
 
-<!-- \ -->
-<!-- *Corresponding author*:  -->
-<!-- Courtney Campany -->
-<!-- E: courtneycampany@gmail.com -->
+\
+*Corresponding author*:
+Courtney Campany
+E: courtneycampany@gmail.com
 
@@
 ```{r, echo=FALSE}
-allomfig <- "2.1"
-airvarsfig <- "2.2"
-allocfig <- "2.3"
-asatfig <- "2.4"
-achemfig <- "2.5"
-massmodelfig <- "2.6"
-massmodelfig2 <- "2.S1"
+allomfig <- "1"
+airvarsfig <- "2"
+allocfig <- "3"
+asatfig <- "4"
+achemfig <- "5"
+massmodelfig <- "6"
+massmodelfig2 <- "S1"
 
-pvetab1 <- "2.1"
-pvetab2 <- "2.2"
-pvetab3 <- "2.3"
-pvetabS <- "2.S3"
+pvetab1 <- "1"
+pvetab2 <- "2"
+pvetab3 <- "3"
+pvetabS <- "S3"
 
@@
 
-#2.1  Abstract
+#Abstract
 
-Interpreting limitations to plant growth requires understanding of the balance between carbon (C) source and sink activity.
-This study used manipulations of soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
+Interpreting limitations to plant growth requires understanding of the balance between carbon (*C*) source and sink activity.
+This study used manipulations of soil volume to test how growth is coupled to physiology, *C* allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
 We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown (free) seedlings.
-We developed a seedling growth model that utilized leaf photosynthesis rates (*A~n~*) to allocate daily C uptake towards mass growth of stems, leaves and roots.
+We developed a seedling growth model that utilized leaf photosynthesis rates (*A*~n~) to allocate daily *C* uptake towards mass growth of stems, leaves and roots.
 Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
@@
 Photosynthetic capacity was significantly reduced in containers compared to free seedlings, and was related to both leaf nitrogen content and starch accumulation.
-We then asked whether the observed reductions in *A~n~* explained the observed differences in seedling biomass.
-We found that although belowground sink limitation resulted in down regulation of *A~n~*, these reductions were not large enough to explain observed growth responses.
-Thus, as *A~n~* and growth were not tightly coordinated, excess photosynthetic C not attributed to biomass resulted in seedlings with soil volume restriction.
-These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf C uptake.
+We then asked whether the observed reductions in *A*~n~ explained the observed differences in seedling biomass.
+We found that although belowground sink limitation resulted in down regulation of *A*~n~, these reductions were not large enough to explain observed growth responses.
+Thus, as *A*~n~ and growth were not tightly coordinated, excess photosynthetic *C* not attributed to biomass resulted in seedlings with soil volume restriction.
+These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf *C* uptake.
 
-<!-- ## Keywords {.unnumbered} -->
-<!-- photosynthesis, growth, sink regulation, carbon allocation, soil volume -->
+## Keywords {.unnumbered}
+photosynthesis, growth, sink regulation, carbon allocation, soil volume
 
-#2.2  Introduction
+#Introduction
 
-Understanding plant growth and its relationship to C assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
+Understanding plant growth and its relationship to *C* assimilation requires knowledge of the mass balance that must be achieved between *C* uptake and subsequent allocation to growth, storage, and respiration.
 As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues and organs.
-At long enough time scales leaf photosynthesis (*A~n~*) and respiratory losses together determine net C balance and will correlate to plant growth.
-At shorter temporal scales, however, growth can instead be mediated by tissue C storage pools.
+At long enough time scales leaf photosynthesis (*A*~n~) and respiratory losses together determine net *C* balance and will correlate to plant growth.
+At shorter temporal scales, however, growth can instead be mediated by tissue *C* storage pools.
 This has led to the current debate on how strongly plant growth is controlled by either source or sink activity.
-Consequently, plant growth cannot always be simply determined by *A~n~*, making it complex to understand and challenging to model [@fourcaud2008plant].
-Despite a wealth of studies, large uncertainties still remain regarding the coordination of C supply and growth of woody species.
+Consequently, plant growth cannot always be simply determined by *A*~n~, making it complex to understand and challenging to model [@fourcaud2008plant].
+Despite a wealth of studies, large uncertainties still remain regarding the coordination of *C* supply and growth of woody species.
 
 \
-In woody species, the coordination of *A~n~* and growth has been studied with manipulations of C source activity.
+In woody species, the coordination of *A*~n~ and growth has been studied with manipulations of *C* source activity.
 Examples included elevated CO~2~ experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments.
-Elevated CO~2~ has been shown to increase *A~n~* [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a stimulation of 23 % in forest biomass production [@norby2005forest].
+Elevated CO~2~ has been shown to increase *A*~n~ [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a stimulation of 23 % in forest biomass production [@norby2005forest].
 Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
-In partial defoliation experiments, increases in *A~n~* of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
-However, increases in *A~n~* in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
-These manipulations of C source activity expose unresolved issues with how changes in *A~n~* do not always infer similar responses in growth.
+In partial defoliation experiments, increases in *A*~n~ of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
+However, increases in *A*~n~ in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], *C* limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant *C* gain [@ovaska1993a].
+These manipulations of C source activity expose unresolved issues with how changes in *A*~n~ do not always infer similar responses in growth.
 
 \
-Alternatively, manipulating plant tissue C sinks is often used to investigate the correlation of *A~n~* and growth.
-This is because metabolic signaling networks, relaying information on C and N status of different tissues, can regulate photosynthetic activity [@paul2001sink].
-If sink inhibition of *A~n~* occurs, a close coordination between declines in *A* and growth should be expected.
+Alternatively, manipulating plant tissue *C* sinks is often used to investigate the correlation of *A*~n~ and growth.
+This is because metabolic signaling networks, relaying information on *C* and *N* status of different tissues, can regulate photosynthetic activity [@paul2001sink].
+If sink inhibition of *A*~n~ occurs, a close coordination between declines in *A*~n~ and growth should be expected.
 Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal, phloem girdling and low temperatures at high elevations.
-In these studies, down regulation of *A* was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
-However, reductions in *A~n~* were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
+In these studies, down regulation of *A*~n~ was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
+However, reductions in *A*~n~ were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
 These mixed results are not surprising as we still know little about the balance between assimilation, storage and growth across temporal scales in plants [@smith2007coordination].
@@
 \
-An alternative experimental approach is to reduce belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size [@arp1991effects; @nesmith1998effect; @poorter2012pot].
+An alternative experimental approach is to reduce belowground *C* sink strength in tree seedlings by manipulating rooting volume, by varying the container size [@arp1991effects; @nesmith1998effect; @poorter2012pot].
 Possible advantages of this approach are that it allows a large range of treatment levels, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
-Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, *A~n~*, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
-Inadequate rooting volume may decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root].
+Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, *A*~n~, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
+Inadequate rooting volume may decrease *C* sink strength by progressively restricting root growth in growing plants [@thomas1991root].
 Container size studies frequently exhibit photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
 A meta-analysis by Poorter et al.
-[-@poorter2012pot] concluded that *A~n~* is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used.
-This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower C exchange and assimilate export rates [@robbins1988effect].
-However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].
-Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test the extent to which growth and *A~n~* are coordinated.
+[-@poorter2012pot] concluded that *A*~n~ is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used.
+This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower *C* exchange and assimilate export rates [@robbins1988effect].
+However, evidence in support for a trade-off between *C* storage and growth in trees is, to date, inconclusive [@palacio2014does].
+Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test the extent to which growth and *A*~n~ are coordinated.
 
 \
-This study utilizes a novel field design to investigate the coordination between growth and *A~n~* in *Eucalyptus tereticornis* Sm.
+This study utilizes a novel field design to investigate the coordination between growth and *A*~n~ in *Eucalyptus tereticornis* Sm.
 seedlings, by manipulating container size and thus rooting volume.
@@
 We used freely-rooted seedlings as a control for the container size treatments.
-Empirical results were combined with a simple plant growth model to simulate seedling growth with a C mass balance approach, which was then compared to observed harvested seedling mass.
-The model used whole-plant C gain, scaled from instantaneous rates of leaf *A~n~*, to quantify seedling dry mass production over the 120 day experiment.
+Empirical results were combined with a simple plant growth model to simulate seedling growth with a *C* mass balance approach, which was then compared to observed harvested seedling mass.
+The model used whole-plant *C* gain, scaled from instantaneous rates of leaf *A*~n~, to quantify seedling dry mass production over the 120 day experiment.
 
@@
 
-4). Last, observed seedling mass was expected to correspond to growth model mass predicted from a simple C balance model taking into account measured rates of photosynthesis.
+4). Last, observed seedling mass was expected to correspond to growth model mass predicted from a simple *C* balance model taking into account measured rates of photosynthesis.
 
-#2.3  Materials and Methods
+#Materials and Methods
 
-##2.3.1 Experimental design
+##Experimental design
 This experiment was located at the Hawkesbury Forest Experiment site in Richmond, NSW, Australia.
@@
 
-##2.3.2 Growth and morphology metrics
+##Growth and morphology metrics
 Seedlings were planted in summer (January 21^st^ 2013) and stem height, diameter at 15 cm and leaf count were measured weekly thereafter.
@@
 
-##2.3.3 Photosynthetic parameters
-Leaf gas exchange measurements were performed fortnightly at saturating light (A~sat~) and saturating light and [CO~2~] (A~max~) on new fully expanded leaves.
+##Photosynthetic parameters
+Leaf gas exchange measurements were performed fortnightly at saturating light (*A*~sat~) and saturating light and [CO~2~] (*A*~max~) on new fully expanded leaves.
 Measurements were initiated only after sufficient new leaf growth occurred (March 05^th^, 2013), approximately 6 weeks following planting, and continued until the biomass harvest.
 Leaf level gas exchange was measured with a standard leaf chamber (2 x 3 cm) equipped with blue-red light emitting diodes using a portable gas exchange system (LI-6400, LI-COR, Lincoln, NE, USA).
-A~sat~ measurements were made at PPFD of 1800 $\mu$mol m^-1^ s^-1^ and [CO~2~] of 400 $\mu$l l^-1^ and A~max~ with [CO~2~] of 1600 $\mu$l l^-1^ and PPFD of 1800 $\mu$mol photons m^-1^ s^-1^.
+*A*~sat~ measurements were made at PPFD of 1800 $\mu$mol m^-1^ s^-1^ and [CO~2~] of 400 $\mu$l l^-1^ and *A*~max~ with [CO~2~] of 1600 $\mu$l l^-1^ and PPFD of 1800 $\mu$mol photons m^-1^ s^-1^.
 This choice of light level to achieve light saturation is consistent with other studies on *Eucalyptus* species [@kallarackal1997ecophysiological;@pinkard1998photosynthetic;@crous2013photosynthesis;@drake2014capacity].
 These measurements were conducted during midday (10:00-14:00 h) with leaf temperature maintained at 25 &deg;C.
-After CO~2~ and water vapor flux values stabilized in the leaf chamber, net CO~2~ assimilation rate and stomatal conductance (g~s~) were logged 5 times and averaged for both A~sat~ and A~max~.
+After CO~2~ and water vapor flux values stabilized in the leaf chamber, net CO~2~ assimilation rate and stomatal conductance (*g*~s~) were logged 5 times and averaged for both *A*~sat~ and *A*~max~.
 
@@
 Each AC~i~ curve was started at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light (above).
-From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011].
+From these curves the photosynthetic parameters, *J*~max~ and *Vc*~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011].
 
 \
-Leaf dark respiration rates (R) was measured on each seedling during the same dates as AC~i~ curves.
+Leaf dark respiration rates (*R*) was measured on each seedling during the same dates as AC~i~ curves.
 Freshly detached leaves were collected at least 1 hour after sundown and placed inside a conifer chamber attached to the Licor 6400.
 Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions.
-Reported values of R are standardized rates at 25 &deg;C using a Q~10~ value (1.86) developed for these seedlings in a separate experiment (Drake et al.
+Reported values of *R* are standardized rates at 25 &deg;C using a *Q*~10~ value (1.86) developed for these seedlings in a separate experiment (Drake et al.
 unpublished).
@@
 
-##2.3.4 Leaf water potential
-Predawn ($\Psi$~pd~) and midday ($\Psi$~l~) leaf water potentials were measured for each seedling using a PMS 1505D pressure chamber (PMS Instruments, Albany, OR, USA) on fully expanded leaves during the same time period as AC~i~ and R.
+##Leaf water potential
+Predawn ($\Psi$~pd~) and midday ($\Psi$~l~) leaf water potentials were measured for each seedling using a PMS 1505D pressure chamber (PMS Instruments, Albany, OR, USA) on fully expanded leaves during the same time period as AC~i~ and *R*.
 Leaves were detached and immediately stored inside foil covered bags before water potential measurements were performed.
@@
 
-##2.3.5 Leaf, root and soil chemistry
-Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of N content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
-Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis of N.
+##Leaf, root and soil chemistry
+Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of *N* content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
+Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis of *N*.
 Nitrogen concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of N~2~ and CO~2~).
-The percentage of N in the sample was calculated by comparison with certified standards.
+The percentage of *N* in the sample was calculated by comparison with certified standards.
 Leaf $\delta$^13^C was analyzed  with an Delta V Advantage coupled to a Flash HT and Conflo IV isotope ratio mass spectrometer.
-Leaf samples were flash combusted at 1000&deg;C to convert to CO~2~, feed to the mass spectrometer and isotopic signatures are reported relative to the VPDP scale.
+Leaf samples were flash combusted at 1000&deg;C to convert to CO~2~, feed to the mass spectrometer and isotopic signatures are reported relative to the standard Vienna Pee Dee Belemnite scale.
 
@@
 Complete methods of the TNC assay are described in [@mitchell2013drought].
-TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, were calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf N content.
-Similarly, TNC-free leaf N (N~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC and leaf N content.
+TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, were calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf *N* content.
+Similarly, TNC-free leaf *N* (*N*~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC and leaf *N* content.
 
-##2.3.6 Seedling growth model
-We developed a simple seedling growth model that utilized leaf *A* rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
+##Seedling growth model
+We developed a simple seedling growth model that utilized leaf *A*~n~ rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
 The model begins with mean initial tissue component biomass (leaf~i~, stem~i~ and root~i~) and a starting leaf area (LA~i~) measured prior to planting.
 The initial biomass of roots was divided evenly between fine and coarse roots.
-The daily net biomass production of seedlings (P~i~) is then given by
+The daily net biomass production of seedlings (*P*~i~) is then given by
 
@@
 (1)
-$$P_i = L\left(\frac{C_{day'i}~\sigma_s}{\epsilon_c}\right) - R$$
-where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^), $\sigma$~s~ is a self shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and R is the mass based total respiration of all tissue components (g C d^-1^).
+$$P_i = L\left(\frac{C_\mathrm{day'i}~\sigma_\mathrm{s}}{\epsilon_\mathrm{c}}\right) - R$$
+where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^), $\sigma$~s~ is a self shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
 Total respiration was calculated as
@@
 (2)
-$$R = \Sigma(R_c~M_c)$$
-where R~c~ is published or local tissue respiration rates of fine roots, coarse roots or stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
-R~leaf~ is represented in the calculation of C~day~ (described below).
-The change in individual component biomass (M~c~), here solved on a daily time step, is given by
+$$R = \Sigma(R_\mathrm{c}~M_\mathrm{c})$$
+where *R*~c~ is published or local tissue respiration rates of fine roots, coarse roots or stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and *M*~c~ is the standing biomass of each component (g).
+*R*~leaf~ is represented in the calculation of *C*~day~ (described below).
+The change in individual component biomass (*M*~c~), here solved on a daily time step, is given by
 
@@
 (3)
-$$\frac{dM_c}{dt} = A_{c}~P_{i}~-~(\Lambda_{c}~M_{c})$$
-where A~c~ is the component specific biomass partitioning to whole plant biomass (%) and $\Lambda$~c~ is component specific turnover rate (yr^-1^).
+$$\frac{dM_\mathrm{c}}{dt} = A_\mathrm{c}~P_\mathrm{i}~-~(\Lambda_\mathrm{c}~M_\mathrm{c})$$
+where *A*~c~ is the component specific biomass partitioning to whole plant biomass (%) and $\Lambda$~c~ is component specific turnover rate (yr^-1^).
 Because we did not observe branch turnover, $\Lambda$~stem~ was assumed to equal 0.
@@
 \
-C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package in R with the mean photosynthetic parameters (J~max~, V~cmax~, R and g~1~) for each treatment and meteorological data from an onsite weather station.
-J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), R was empirically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed g~s~ values.
+*C*~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package in R with the mean photosynthetic parameters (*J*~max~, *Vc*~max~, R and *g*~1~) for each treatment and meteorological data from an onsite weather station.
+*J*~max~ and *Vc*~max~ were estimated from AC~i~ curves (explained above), *R* was empirically measured and the *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed *g*~s~ values.
 Methods of the coupled leaf gas exchange model are described in Duursma et al [-@duursma2014peaked].
-Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A* rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
-C~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
-This resulted in 120 unique values of C~day~ for each soil volume treatment, one value for each day of the experiment.
-Thus, each daily time step for model runs included a value of C~day~ that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
+Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A*~n~ rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
+*C*~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
+This resulted in 120 unique values of *C*~day~ for each soil volume treatment, one value for each day of the experiment.
+Thus, each daily time step for model runs included a value of *C*~day~ that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
 
 \
-It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf *A* with total plant leaf area.
-This was accomplished by utilizing 61 previously digitized Eucalyptus seedlings, covering 5 total species which include *E.
+It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf *A*~n~ with total plant leaf area.
+This was accomplished by utilizing 61 previously digitized *Eucalyptus* seedlings, covering 5 total species which include *E.
 tereticornis*, from Duursma et al.
 [-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
-Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
-The ratio of total *A* with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments.
-Next, the linear relationship between $\sigma$~s~ and total leaf area was for determined across digitized seedlings, within each treatment.
+Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*~n~, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
+The ratio of total *A*~n~ with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments.
+Next, the linear relationship between $\sigma$~s~ and total leaf area was determined across digitized seedlings, within each treatment.
 For the growth model, $\sigma$~s~ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to C~day,i~.
@@
 \
-We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A* where sufficient to accurately predict overall seedling biomass production after 120 days.
-Each model run utilized changes in *A* and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
-Cumulative net leaf C gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling C was assumed to equal half of the final mass for both modeled and observed seedlings.
+We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ where sufficient to accurately predict overall seedling biomass production after 120 days.
+Each model run utilized changes in *A*~n~ and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
+Cumulative net leaf *C* gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling *C* was assumed to equal half of the final mass for both modeled and observed seedlings.
 
 \
-First, a default model was fitted with mean photosynthetic parameters from the free seedlings and then optimized to produce a LMF which correctly predicted both the leaf mass and total biomass of the harvested free seedling (M~free~).
-This optimized LMF was then used to constrain model runs with soil volume treatment specific C~day~, while keeping tissue respiration and turnover parameters constant, to determine if changes in leaf A alone could predict biomass of seedlings in containers (M~pots~).
-Next, model sensitivity to different C allocation scenarios, including observed treatment specific LMF and up regulation of non-leaf tissue respiration by 50 % of default values (M~S1~ and M~S2~, respectively), was used to improve model biomass predictions compared to measured harvest biomass.
-For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment specific mean C~day~ by first scaling values to the free seedling control.
+First, a default model was fitted with mean photosynthetic parameters from the free seedlings and then optimized to produce a LMF which correctly predicted both the leaf mass and total biomass of the harvested free seedling (*M*~free~).
+This optimized LMF was then used to constrain model runs with soil volume treatment specific *C*~day~, while keeping tissue respiration and turnover parameters constant, to determine if changes in leaf *A*~n~ alone could predict biomass of seedlings in containers (*M*~pots~).
+Next, model sensitivity to different *C* allocation scenarios, including observed treatment specific LMF and up-regulation of non-leaf tissue respiration by 50 % of default values (*M*~S1~ and *M*~S2~, respectively), was used to improve model biomass predictions compared to measured harvest biomass.
+For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment specific mean *C*~day~ by first scaling values to the free seedling control.
 
-##2.3.7 Data analysis
+##Data analysis
 Differences in experimental parameters with soil volume were analysed by mixed-effects models in R with individual containers and experimental blocks as random effects and soil volume treatment as a categorical fixed effect with seven levels.
 Tukey's post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
-A linear mixed effect model of A~max~ and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R.
-Explained variance (R^2^) of mixed models were computed as in  [@nakagawa2013general].
+A linear mixed effect model of *A*~max~ and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R.
+Explained variance (*R*^2^) of mixed models were computed as in  [@nakagawa2013general].
 Tests of allometric relationships between log-transformed biomass components were implemented using standardized major axis regression in the 'smatr' package in R [@warton2012smatr].
@@
 
-#2.4 Results
+#Results
 
-##2.4.1 Growth and morphology
-Plant height, diameter and leaf area diverged between container volumes soon after start of the experiment (Figure `r allomfig`).
-First, seedling leaf area significantly diverged between soil volumes (P < 0.029) during the 5^th^ week of the experiment.
-Following this period both height (8^th^) week) and then diameter (9^th^ week) significantly deviated across soil volumes (P < 0.045 & 0.035, respectively).
+##Growth and morphology
+Plant height, diameter and leaf area diverged between container volumes soon after start of the experiment (Figure `r allomfig`a-c).
+First, seedling leaf area significantly diverged between soil volumes (*P* < 0.029) during the 5^th^ week of the experiment.
+Following this period both height (8^th^) week) and then diameter (9^th^ week) significantly deviated across soil volumes (*P* < 0.045 & 0.035, respectively).
 The large reductions in height gain and total leaf area in smaller compared to larger containers continued throughout the experiment.
-In this field study, colder temperatures and reductions in total PPFD per day (Figure `r airvarsfig`) likely slowed the growth of seedlings in the final weeks of the experiment (Figure `r allomfig`).
+In this field study, colder temperatures and reductions in total PPFD per day (Figure `r airvarsfig`) likely slowed the growth of seedlings in the final weeks of the experiment.
 Seedlings maintained diameter growth throughout the experiment, although marginal with smaller soil volumes in the final month.
-Final seedling height significantly increased with increasing soil volume (P < 0.001).
-Increases in both final stem diameter (P < 0.001) and cumulative leaf area (both P < 0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling treatments.
-\
-```{r allometry, fig.width=6, fig.height=7.6, echo=FALSE,  dev="png", dpi=600, dev.args=list(type="cairo")}
-source("master_scripts/allometryplotting.R")
-```  
-\
-**Figure 2.1**.
-Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
-\
-```{r airvars, fig.width=6, fig.height=7.6, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
-source("master_scripts/airvars_plotting.R")
-```  
-\
-**Figure 2.2**. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.
+Final seedling height significantly increased with increasing soil volume (*P* < 0.001).
+Increases in both final stem diameter (*P* < 0.001) and cumulative leaf area (both *P* < 0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling treatments.
 
 \
-Total seedling biomass at harvest was significantly different across container volumes (P < 0.001) and between container treatments and free seedlings (P < 0.001, Table `r pvetab1`).
+Total seedling biomass at harvest was significantly different across container volumes (*P* < 0.001) and between container treatments and free seedlings (*P* < 0.001, Table `r pvetab1`).
 On average, harvested biomass of free seedlings was 84% higher than seedlings in containers.
-Plant biomass was positively correlated with total leaf area across all treatments (R^2^ = 0.97, P < 0.001).
+Plant biomass was positively correlated with total leaf area across all treatments (*R*^2^ = 0.97, *P* < 0.001).
 Differences in biomass partitioning to leaves, stems and roots were not different across soil volumes after variation in seedling biomass across treatments was factored in the analysis (Figure `r allocfig`a,b).
@@
 \
-**Table 2.1**.Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
-Seedling mass and leaf $\delta$^13^C values are from final harvest.
-Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6).
-Different letters represent significant differences between treatments.
-The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
+Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table `r pvetab2`, *P* = 0.009).
+Fine root length density was significantly higher in the two smallest container sizes and was the lowest in the largest container size (Table `r pvetab2`, *P* < 0.001).
+Over the duration of the experiment SLA~f~ was higher in free seedlings, but was not different across containers sizes (Table `r pvetab1`, *P* < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (*P* < 0.001).
 
-```{r table1, echo=FALSE, warning=FALSE}
-greeks=c(alpha='\u03b1', Delta='\u0394', Sigma='\u03A3', mu='\u03bc',delta = '\u03b4')
+##Leaf and root chemistry
+Leaf *N*~f~ was significantly higher in free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, *P* < 0.001).
+Throughout the remainder of the experiment the smallest container volume had a significant reduction in leaf *N*~f~ compared to other soil volumes, while free seedlings maintained the highest leaf *N*~f~ (Table `r pvetab1`, *P* < 0.001).
+Leaf starch content in the smallest container was ca.
+double  that of free seedlings (*P* = 0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table `r pvetab1`).
+Differences in leaf starch between the free seedling and the smallest container were evident during the first gas exchange campaign (*P* = 0.001).
+Root *N* was higher in free seedlings compared to seedlings in containers but only for some of the container size treatments (Table `r pvetab2`).
 
-dust(table1)%>%
-  sprinkle_colnames("Volume (L)", 
-                        "Seedling mass (g)", 
-                        "SLA~TNC-free~ (m^2^ kg^-1^)",
-                        "Leaf Starch (%)", 
-                        "Leaf Sugars (%)", 
-                        "Leaf Nitrogen~TNC-free~ (%)",
-                        paste0("Leaf ", greeks['delta'],"^13^C"," (\u2030)")) %>%
-  sprinkle(rows= 1, part="head",bold=TRUE)%>%
-  sprinkle_print_method("markdown")
-```
-\
-```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
-source("master_scripts/allocation_plotting.R")
-```  
-\
-\
-**Figure 2.3**.
-Soil volume treatment means of biomass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c).
-For (b) lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment.
-For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (R^2^ = 0.82) with equation: log(x) = 0.983(log(y)) - 0.036.
+##Gas exchange and photosynthetic parameters
+At the first measurement campaign, both *A*~sat~ and *A*~max~ were significantly higher in the free seedling treatment compared to seedlings in containers (both *P* < 0.001).
+Across all measurement campaigns mean *A*~sat~ (Figure `r asatfig`) and *A*~max~ (Table `r pvetab3`) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
+The relationships between photosynthetic capacity, leaf starch and leaf *N* on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated to both leaf *N* content and leaf starch (both *P* < 0.001).
+We used predictions from the linear mixed effect model equation to visualize these relationship of *A*~max~ to either leaf *N* content or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
+Across all measurement campaigns and treatments *A*~max~ was higher when leaf *N* was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
+*A*~max~  was also lower when leaf starch was high as higher leaf *N* often did not coincide with high leaf starch (Figure `r achemfig`b).
+Overall, *A*~max~ was positively correlated with final harvest biomass across all seedlings (*P* < 0.001).
 
 \
-Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table `r pvetab2`, P = 0.009).
-Fine root length density was significantly higher in the two smallest container sizes and was the lowest in the largest container size (Table `r pvetab2`, P < 0.001).
-Over the duration of the experiment SLA~f~ was higher in free seedlings, but was not different across containers sizes (Table `r pvetab1`, P < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (P < 0.001).
-
-\
-**Table 2.2**.
-Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
-All values are from the final harvest.
-Values for FRLD were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
-Different letters represent significant differences between treatments.
-The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only differences between seedlings in containers.
-```{r table2, echo=FALSE, warning=FALSE}
-dust(table2)%>%
-  sprinkle_colnames("Volume (L)", 
-                        "Root Nitrogen (%)", 
-                        "SRL (m g^-1^)",
-                        "FRLD (m dm^-3^)") %>%
-  sprinkle(rows= 1, part="head",bold=TRUE)%>%
-  sprinkle_print_method("markdown")
-```
-
-##2.4.2 Leaf and root chemistry
-Leaf N~f~ was significantly higher in free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, P < 0.001).
-Throughout the remainder of the experiment the smallest container volume had a significant reduction in leaf N~f~ compared to other soil volumes, while free seedlings maintained the highest leaf N~f~ (Table `r pvetab1`, P < 0.001).
-Leaf starch content in the smallest container was ca.
-double  that of free seedlings (P = 0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table `r pvetab1`).
-Differences in leaf starch between the free seedling and the smallest container were evident during the first gas exchange campaign (P = 0.001).
-Root N was higher in free seedlings compared to seedlings in containers but only for some of the container size treatments (Table `r pvetab2`).
-
-##2.4.3 Gas exchange and photosynthetic parameters
-At the first measurement campaign, both A~sat~ and A~max~ were significantly higher in the free seedling treatment compared to seedlings in containers (both P < 0.001).
-Across all measurement campaigns mean A~sat~ (Figure `r asatfig`) and A~max~ (Table `r pvetab3`) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
-The relationships between photosynthetic capacity, leaf starch and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001).
-We used predictions from the linear mixed effect model equation to visualize these relationship of A~max~ to either leaf N content or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
-Across all measurement campaigns and treatments A~max~ was higher when leaf N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
-A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b).
-Overall, A~max~ was positively correlated with final harvest biomass across all seedlings (P < 0.001).
-\
-```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
-source("master_scripts/A_stats_plotting.R")
-```  
-\
-**Figure 2.4**.
-Soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25&deg;C.
-Different letters represent significant differences between treatments.
-\
-```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
-source("master_scripts/Amax_TNC_N_plotting2.R")
-```  
-\
-**Figure 2.5**.
-Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).
-Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high.
-Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~mass~ as a function of starch and nitrogen.
-The marginal R^2^ (fixed effects only) was 0.37 and the conditional R^2^ (fixed and random effects) was 0.48 for the complete model.
-
-\
-Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab2`).
+Both *J*~max~ and *Vc*~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab2`).
 Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab2`).
-The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab2`).
+The *g*~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab2`).
 
@@
 Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 MPa across all seedlings, respectively.
-Although g~s~ in free seedlings was generally higher than those in containers (Table `r pvetab2`, P < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
+Although *g*~s~ in free seedlings was generally higher than those in containers (Table `r pvetab2`, *P* < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
 Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table `r pvetab1`).
@@
 
-##2.4.4 Modelling seedling biomass
-The default model M~free~, successfully optimized a LMF (21.6 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %.
-Using this optimized LMF, the total biomass of modeled seedlings for each soil volume treatment (M~pots~) were on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf C gain (Figure `r massmodelfig`a).
+##Modelling seedling biomass
+The default model *M*~free~, successfully optimized a LMF (21.6 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %.
+Using this optimized LMF, the total biomass of modeled seedlings for each soil volume treatment (*M*~pots~) were on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf *C* gain (Figure `r massmodelfig`a).
 Thus, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments (Figure `r massmodelfig`b).
 As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
-\
-```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
-source("master_scripts/massmodel_optimize.R")
-```  
-\
-\
-\
-**Figure 2.6**.
-Total carbon mass for harvested and modeled seedlings versus predicted total carbon gain after 120 days (a) and  reductions in final seedling carbon mass, both modeled and observed, as a function of the reduction in leaf photosynthesis across treatments (b).
-For (a) the dashed 1:1 identifies the difference between net total leaf carbon gain and gross seedling production.
-For (b) both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.
 
 \
-Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over predictions of seedling C mass.
-Testing the sensitivity of the model to observed treatment-specific LMF from the final harvest (M~S1~), which were each lower than the optimized LMF value (see Figure `r allocfig`a), improved model predictions of seedling C mass but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
+Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over predictions of seedling *C* mass.
+Testing the sensitivity of the model to observed treatment-specific LMF from the final harvest (*M*~S1~), which were each lower than the optimized LMF value (see Figure `r allocfig`a), improved model predictions of seedling C mass but still overestimated seedling total *C* by 32&pm;11.1 % (Figure `r massmodelfig2`a).
 Using harvest values of LMF, however, does not capture the observed increase in leaf turnover of seedlings in small containers (Figure `r allomfig`c).
-Thus, the use of harvest LMF values for seedlings in containers in M~S1~ likely underestimates daily C allocation to leaves over the final months of the experiment.
-Increases of 50 % in non-leaf tissue respiration (M~S2~) improved biomass estimates slightly but overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
-With M~S2~, non-tissue respiration rates would need to be increased by ca.
+Thus, the use of harvest LMF values for seedlings in containers in *M*~S1~ likely underestimates daily C allocation to leaves over the final months of the experiment.
+Increases of 50 % in non-leaf tissue respiration (*M*~S2~) improved biomass estimates slightly but overestimated mass *C* by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
+With *M*~S2~, non-tissue respiration rates would need to be increased by ca.
 250% in order for mass balance to be achieved.
 
-#2.5  Discussion
+#Discussion
 This study utilized a simple but novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
-We addressed questions regarding the coordination of *A~n~* and growth by complementing empirical results with a C mass balance model.
-We found that reductions in leaf *A~n~* across container sizes, when integrated across the 120 day experiment, were alone insufficient to account for observed reductions in total plant biomass production.
+We addressed questions regarding the coordination of *A*~n~ and growth by complementing empirical results with a *C* mass balance model.
+We found that reductions in leaf *A*~n~ across container sizes, when integrated across the 120 day experiment, were alone insufficient to account for observed reductions in total plant biomass production.
 
-##2.5.1 Reductions in growth and physiology under sink limitation
+##Reductions in growth and physiology under sink limitation
 Soon after seedlings became established both height and diameter growth were negatively affected by decreasing soil volume.
@@
 These growth reductions were expected, as the impedance of root growth can cause reductions in overall plant growth and activity [@mcconnaughay1991physical; @young1997mechanical].
-It has been shown that roots subjected to environmental stress may send inhibitory signals to the shoots that affect g~s~, cell expansion, cell division and the rate of leaf appearance [@passioura2002soil].
+It has been shown that roots subjected to environmental stress may send inhibitory signals to the shoots that affect *g*~s~, cell expansion, cell division and the rate of leaf appearance [@passioura2002soil].
 Here, this was evident in a large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
@@
 \
-Decreases in A~sat~ occurred at the same time as reductions in height and diameter of seedlings in containers.
-This initially suggests a strong link between growth and an apparent down regulation of *A~n~*.
-However, there are several possible mechanisms that can explain reduced *A~n~* in small containers including nutrient content, water or reduced sink strength [@poorter2012pot].
+Decreases in *A*~sat~ occurred at the same time as reductions in height and diameter of seedlings in containers.
+This initially suggests a strong link between growth and an apparent down regulation of *A*~n~.
+However, there are several possible mechanisms that can explain reduced *A*~n~ in small containers including nutrient content, water or reduced sink strength [@poorter2012pot].
 It was therefore necessary to examine each of these factors to determine if the induced belowground sink limitation actually triggered photosynthetic down regulation.
@@
 \
-With high rates of g~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A~n~*.
+With high rates of *g*~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A*~n~.
 This finding is consistent with other container size studies without drought treatments.
-For example, reduced A~max~ in cotton seedlings grown at elevated CO~2~ was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased g~s~ [@thomas1991root].
-Additionally, severe reductions in *A~n~* in coffee plants were not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
-It is likely that reductions in *A~n~* of well-watered seedlings observed in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
+For example, reduced *A*~max~ in cotton seedlings grown at elevated CO~2~ was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased *g*~s~ [@thomas1991root].
+Additionally, severe reductions in *A*~n~ in coffee plants were not attributed to impacts of container size on leaf water potentials or *g*~s~ [@ronchi2006growth].
+It is likely that reductions in *A*~n~ of well-watered seedlings observed in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
 
 \
-Here, reductions in *A~n~* were positively correlated with decreases in leaf N and leaf N was considerably reduced for seedlings in containers.
-As leaf N reductions were detected with TNC-free leaf mass, this suggests that physical root restriction or decreased supply likely affected seedling N uptake instead of TNC dilution in leaves in the smallest containers.
-Root N at the end of the experiment was on average higher in free seedlings but not consistently higher than every container volume treatment.
-Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N in free seedlings, but this effect is unknown.
-Combined with the fact that soil N declined evenly across all treatments, there was no clear mechanism present to identify changes in root N uptake between free seedlings and seedlings in containers.
+Here, reductions in *A*~n~ were positively correlated with decreases in leaf *N* and leaf *N* was considerably reduced for seedlings in containers.
+As leaf *N* reductions were detected with TNC-free leaf mass, this suggests that physical root restriction or decreased supply likely affected seedling *N* uptake instead of TNC dilution in leaves in the smallest containers.
+Root *N* at the end of the experiment was on average higher in free seedlings but not consistently higher than every container volume treatment.
+Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf *N* in free seedlings, but this effect is unknown.
+Combined with the fact that soil *N* declined evenly across all treatments, there was no clear mechanism present to identify changes in root *N* uptake between free seedlings and seedlings in containers.
 In these already low quality soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
-Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the effects of belowground sink limitation on *A~n~* of seedlings in containers was evident throughout the experiment.
+Although no clear feedback could be determined between the available soil *N* pool and decreases in leaf *N*, the effects of belowground sink limitation on *A*~n~ of seedlings in containers was evident throughout the experiment.
 
 \
-As both rooting space and resources were finite in containers, the inability of seedlings to maintain the capacity of the belowground C sink resulted in the buildup of C assimilate in leaves.
-The feedback inhibition of *A~n~* from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process (Nebauer et al.
-2011).
-Here, declines in A~max~ were correlated with higher starch content throughout the experiment.
+As both rooting space and resources were finite in containers, the inability of seedlings to maintain the capacity of the belowground *C* sink resulted in the buildup of *C* assimilate in leaves.
+The feedback inhibition of *A*~n~ from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process [@nebauer2011photosynthesis].
+Here, declines in *A*~max~ were correlated with higher starch content throughout the experiment.
 This agrees with a study on a deciduous conifer by Equiza et al.
 [-@equiza2006photosynthetic] where photosynthetic downregulation from reduced sink strength was correlated with starch content.
-As starch content in leaves of plants grown in the smallest containers was nearly double that of free seedlings in our study, this suggests the response of *A~n~* to sink inhibition was regulated by this accumulation, as hypothesized.
+As starch content in leaves of plants grown in the smallest containers was nearly double that of free seedlings in our study, this suggests the response of *A*~n~ to sink inhibition was regulated by this accumulation, as hypothesized.
 
-##2.5.2 Biomass partitioning under sink limitation
+##Biomass partitioning under sink limitation
 As biomass partitioning is likely controlled by the source and sink strength of all organs [@poorter2012biomass], it was important to determine which tissue components were most affected by the container size treatments.
@@
 
-##2.5.3 Do reductions in photosynthesis explain reductions in seedling growth?
-Our model used a simple approach to drive seedling growth with measured reductions in leaf *A~n~* , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
+##Do reductions in photosynthesis explain reductions in seedling growth?
+Our model used a simple approach to drive seedling growth with measured reductions in leaf *A*~n~ , via soil volume effects, while treating *C* use efficiency, respiration and *C* allocation as fixed processes.
 Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
-Although reductions in A~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
-[-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A~n~* do not fully explain reduced seedling growth.
-These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
-It is possible that the overestimation of growth was due to an initial overestimation of *A~n~*, however, the robust empirical based methods used to generate photosynthetic parameters (J~max~, V~cmax~, R and g~1~) make this unlikely.
-Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A~n~* affect models which distinguish the fate of assimilate C within a plant.
+Although reductions in *A*~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
+[-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth.
+These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of *C* assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
+It is possible that the overestimation of growth was due to an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *Vc*~max~, *R* and *g*~1~) make this unlikely.
+Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A*~n~ affect models which distinguish the fate of assimilate C within a plant.
 Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven  plant growth models [@lacointe2000carbon].
-To address this issue, we utilized the flexibility of this model to test plausible fates of the pool of simulated non-biomass C unaccounted for with observed mass balance.
+To address this issue, we utilized the flexibility of this model to test plausible fates of the pool of simulated non-biomass *C* unaccounted for with observed mass balance.
 Similar to Lohier et al.
-[-@lohier2014explaining] we manipulated processes contributing to modeled seedling C mass balance, including changes to leaf C allocation or non-leaf tissue respiration, to quantitatively test their respective influences on model predictions.
+[-@lohier2014explaining] we manipulated processes contributing to modeled seedling *C* mass balance, including changes to leaf *C* allocation or non-leaf tissue respiration, to quantitatively test their respective influences on model predictions.
 
 \
-Using measured LMF from the harvest, instead of the optimized seedling control (M~S1~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond *A~n~*.
+Using measured LMF from the harvest, instead of the optimized seedling control (*M*~S1~), improved biomass predictions and provided insight into how sink limitation can impact leaf *C* allocation beyond *A*~n~.
 The sensitivity of the model to shifts in LMF could represent leaf loss throughout the experiment that could not be explicitly quantified in this field study.
 As TNC accumulation can lead to accelerated leaf senescence [@paul2001sink], this could explain the observed decline in total leaf area of seedlings in small containers.
-Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A~n~* and the fate of C allocated to growth, respiration and C storage in leaves.
-It will be the interactions between these two components that will determine the total C gain available for plant growth.
+Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A*~n~ and the fate of *C* allocated to growth, respiration and *C* storage in leaves.
+It will be the interactions between these two components that will determine the total *C* gain available for plant growth.
 
 \
-Increasing rates of non-leaf respiration (M~S2~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation.
+Increasing rates of non-leaf respiration (*M*~S2~) improved biomass predictions but to a far lesser extent than changes to leaf *C* allocation.
 We also show that very large increases in non-leaf respiration rates would have been required to accurately predict observed seedling biomass.
-Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], results from M~S2~ highlight a lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change.
-This is noteworthy, as C balance is a delicate equilibrium between fluxes of *A~n~* and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions [@valentini2000respiration].
+Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], results from *M*~S2~ highlight a lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change.
+This is noteworthy, as *C* balance is a delicate equilibrium between fluxes of *A*~n~ and respiration, partial accounting of *C* dynamics can easily lead to erroneous conclusions [@valentini2000respiration].
 These results infer that using fixed rates of respiration in models likely underestimates plant responses to sink limitation.
@@
 [-@delucia2007forest] that it is likely inappropriate to assume that respiration is a constant fraction of gross primary production in models.
-Our findings reveal that a combination of different mechanisms, beyond *A~n~*, are likely at play in driving the observed seedling biomass response to sink manipulation.
+Our findings reveal that a combination of different mechanisms, beyond *A*~n~, are likely at play in driving the observed seedling biomass response to sink manipulation.
 However, the degree to which these mechanisms will regulate growth will undoubtedly shift across different experimental manipulations and plant species.
 
-##2.5.4 Conclusions
+##Conclusions
 With a novel field-based design we detected a massive effect of container volume on seedling growth, not between containers but with naturally planted seedlings.
@@
 The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
-Our combined empirical and modeling approach shows that when non-photosynthesis parameters were kept constant changes in *A~n~* were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
-K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A~n~* through the demand for C.
-Although this may be true, our results infer that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
-Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
-The approach used here has the flexibility to account for multiple drivers of C allocation and provides an avenue to address future questions regarding the impact of environmental change on plant growth.
+Our combined empirical and modeling approach shows that when non-photosynthesis parameters were kept constant changes in *A*~n~ were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
+K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A*~n~ through the demand for *C*.
+Although this may be true, our results infer that quantifying the fate of assimilated *C* into known pools of growth, storage and *C* loss are needed prior to addressing this debate.
+Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of *C* and other constituents.
+The approach used here has the flexibility to account for multiple drivers of *C* allocation and provides an avenue to address future questions regarding the impact of environmental change on plant growth.
 
-#2.6  Supporting Information
-**Table 2.S1**.Seedling growth model default parameters.
+# Tables {.unnumbered}
+**Table 1**.Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Each value reflects the mean(standard error) for each treatment.
+Seedling mass and leaf $\delta$^13^C values are from final harvest.
+Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6).
+Different letters represent significant differences between treatments.
+The volume effect *P* value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
 
+```{r table1, echo=FALSE, warning=FALSE}
+greeks=c(alpha='\u03b1', Delta='\u0394', Sigma='\u03A3', mu='\u03bc',delta = '\u03b4')
+
+dust(table1)%>%
+  sprinkle_colnames("Volume (L)", 
+                        "Seedling mass (g)", 
+                        "SLA~TNC-free~ (m^2^ kg^-1^)",
+                        "Leaf Starch (%)", 
+                        "Leaf Sugars (%)", 
+                        "Leaf Nitrogen~TNC-free~ (%)",
+                        paste0("Leaf ", greeks['delta'],"^13^C"," (\u2030)")) %>%
+  sprinkle(rows= 1, part="head",bold=TRUE)%>%
+  sprinkle_print_method("markdown")
+```
+
+**Table 2**.
+Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Each value reflects the mean(standard error) for each treatment.
+All values are from the final harvest.
+Values for FRLD were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
+Different letters represent significant differences between treatments.
+The volume effect *P* value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only differences between seedlings in containers.
+```{r table2, echo=FALSE, warning=FALSE}
+dust(table2)%>%
+  sprinkle_colnames("Volume (L)", 
+                        "Root Nitrogen (%)", 
+                        "SRL (m g^-1^)",
+                        "FRLD (m dm^-3^)") %>%
+  sprinkle(rows= 1, part="head",bold=TRUE)%>%
+  sprinkle_print_method("markdown")
+```
+
+\
+**Table 3**.
+Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Each value reflects the mean(standard error) for each treatment.
+*A*~max~, *R* and *g*~s~ are each measured at 25 &deg;C.
+Values of *A*~max~, *g*~s~ and *g*~1~ represent overall means across measurement campaigns (n=6).
+R, *J*~max~ and *Vc*~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements.
+Different letters represent significant differences between treatments.
+The volume effect *P* value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
+
+```{r table3, echo=FALSE, warning=FALSE}
+dust(table3)%>%
+  sprinkle_colnames("Volume (L)", 
+                        "*A*~max~ ($\\mu$mol m^-2^ s^-1^)", 
+                        "R ($\\mu$mol m^-2^ s^-1^)",
+                        "*J*~max~",
+                        "*Vc*~max~",
+                        "*g*~s~ (mol m^-2^ s^-1^)",
+                        "*g*~1~") %>%
+  sprinkle(rows= 1, part="head",bold=TRUE)%>%
+  sprinkle_print_method("markdown")
+```
+
+# Figures {.unnumbered}
+
+```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=600, dev.args=list(type="cairo")}
+source("master_scripts/allometryplotting.R")
+```  
+**Figure 1**.
+Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013
+
+```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
+source("master_scripts/airvars_plotting.R")
+```  
+**Figure 2**. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.
+
+```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
+source("master_scripts/allocation_plotting.R")
+```  
+**Figure 3**.
+Soil volume treatment means of biomass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c).
+For (b) lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment.
+For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (*R*^2^ = 0.82) with equation: log(x) = 0.983(log(y)) - 0.036.
+
+```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
+source("master_scripts/A_stats_plotting.R")
+```  
+**Figure 4**.
+Soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25&deg;C.
+Different letters represent significant differences between treatments.
+
+```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
+source("master_scripts/Amax_TNC_N_plotting2.R")
+```  
+**Figure 5**.
+Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).
+Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high.
+Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~mass~ as a function of starch and nitrogen.
+The marginal *R*^2^ (fixed effects only) was 0.37 and the conditional *R*^2^ (fixed and random effects) was 0.48 for the complete model.
+
+```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
+source("master_scripts/massmodel_optimize.R")
+```  
+**Figure 6**.
+Total carbon mass for harvested and modeled seedlings versus predicted total carbon gain after 120 days (a) and  reductions in final seedling carbon mass, both modeled and observed, as a function of the reduction in leaf photosynthesis across treatments (b).
+For (a) the dashed 1:1 identifies the difference between net total leaf carbon gain and gross seedling production.
+For (b) both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.
+
+# Supporting Information {.unnumbered}
+
+**Table S1**.Seedling growth model default parameters.
 ```{r tabels1, echo=FALSE, warning=FALSE}
@@
 ```  
-\
-\
-\
-**Figure 2.S1**.
+**Figure S1**.
 Sensitivity testing of seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50 % (b).

### 2015-12-14 manuscript/thesis_pve.Rmd
abbreviation changes (added to notes).
manuscripts edits made to all documents and in thesis word document

--- 2015-12-09 manuscript/manuscript_pve.Rmd
@@
   | Chapter 2 
-  | Belowground sink limitation alters growth and carbon balance of Eucalyptus seedlings
+  | Belowground sink limitation alters growth and carbon balance of *Eucalyptus* seedlings
 author: ""
@@
 This is because metabolic signaling networks, relaying information on C and N status of different tissues, can regulate photosynthetic activity [@paul2001sink].
-If sink inhibition of *A~n~* occurs, a close coordination between declines in *A* and growth should be expected.
+If sink inhibition of *A~n~* occurs, a close coordination between declines in *A~n~* and growth should be expected.
 Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal, phloem girdling and low temperatures at high elevations.
-In these studies, down regulation of *A* was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
+In these studies, down regulation of *A~n~* was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
 However, reductions in *A~n~* were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
@@
 Leaf $\delta$^13^C was analyzed  with an Delta V Advantage coupled to a Flash HT and Conflo IV isotope ratio mass spectrometer.
-Leaf samples were flash combusted at 1000&deg;C to convert to CO~2~, feed to the mass spectrometer and isotopic signatures are reported relative to the VPDP scale.
+Leaf samples were flash combusted at 1000&deg;C to convert to CO~2~, feed to the mass spectrometer and isotopic signatures are reported relative to the standard Vienna Pee Dee Belemnite scale.
 
@@
 ##2.3.6 Seedling growth model
-We developed a simple seedling growth model that utilized leaf *A* rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
+We developed a simple seedling growth model that utilized leaf *A~n~* rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
 The model begins with mean initial tissue component biomass (leaf~i~, stem~i~ and root~i~) and a starting leaf area (LA~i~) measured prior to planting.
@@
 \
-C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package in R with the mean photosynthetic parameters (J~max~, V~cmax~, R and g~1~) for each treatment and meteorological data from an onsite weather station.
+C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package in R with the mean photosynthetic parameters (J~max~, Vc~max~, R and g~1~) for each treatment and meteorological data from an onsite weather station.
 J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), R was empirically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed g~s~ values.
@@
 \
-It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf *A* with total plant leaf area.
-This was accomplished by utilizing 61 previously digitized Eucalyptus seedlings, covering 5 total species which include *E.
+It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf *A~n~* with total plant leaf area.
+This was accomplished by utilizing 61 previously digitized *Eucalyptus* seedlings, covering 5 total species which include *E.
 tereticornis*, from Duursma et al.
 [-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
-Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
-The ratio of total *A* with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments.
-Next, the linear relationship between $\sigma$~s~ and total leaf area was for determined across digitized seedlings, within each treatment.
+Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A~n~*, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
+The ratio of total *A~n~* with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments.
+Next, the linear relationship between $\sigma$~s~ and total leaf area was determined across digitized seedlings, within each treatment.
 For the growth model, $\sigma$~s~ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to C~day,i~.
@@
 \
-We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A* where sufficient to accurately predict overall seedling biomass production after 120 days.
-Each model run utilized changes in *A* and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
+We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A~n~* where sufficient to accurately predict overall seedling biomass production after 120 days.
+Each model run utilized changes in *A~n~* and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
 Cumulative net leaf C gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling C was assumed to equal half of the final mass for both modeled and observed seedlings.
@@
 First, a default model was fitted with mean photosynthetic parameters from the free seedlings and then optimized to produce a LMF which correctly predicted both the leaf mass and total biomass of the harvested free seedling (M~free~).
-This optimized LMF was then used to constrain model runs with soil volume treatment specific C~day~, while keeping tissue respiration and turnover parameters constant, to determine if changes in leaf A alone could predict biomass of seedlings in containers (M~pots~).
-Next, model sensitivity to different C allocation scenarios, including observed treatment specific LMF and up regulation of non-leaf tissue respiration by 50 % of default values (M~S1~ and M~S2~, respectively), was used to improve model biomass predictions compared to measured harvest biomass.
+This optimized LMF was then used to constrain model runs with soil volume treatment specific C~day~, while keeping tissue respiration and turnover parameters constant, to determine if changes in leaf *A~n~* alone could predict biomass of seedlings in containers (M~pots~).
+Next, model sensitivity to different C allocation scenarios, including observed treatment specific LMF and up-regulation of non-leaf tissue respiration by 50 % of default values (M~S1~ and M~S2~, respectively), was used to improve model biomass predictions compared to measured harvest biomass.
 For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment specific mean C~day~ by first scaling values to the free seedling control.
@@
 ##2.4.1 Growth and morphology
-Plant height, diameter and leaf area diverged between container volumes soon after start of the experiment (Figure `r allomfig`).
+Plant height, diameter and leaf area diverged between container volumes soon after start of the experiment (Figure `r allomfig`a-c).
 First, seedling leaf area significantly diverged between soil volumes (P < 0.029) during the 5^th^ week of the experiment.
@@
 The large reductions in height gain and total leaf area in smaller compared to larger containers continued throughout the experiment.
-In this field study, colder temperatures and reductions in total PPFD per day (Figure `r airvarsfig`) likely slowed the growth of seedlings in the final weeks of the experiment (Figure `r allomfig`).
+In this field study, colder temperatures and reductions in total PPFD per day (Figure `r airvarsfig`) likely slowed the growth of seedlings in the final weeks of the experiment.
 Seedlings maintained diameter growth throughout the experiment, although marginal with smaller soil volumes in the final month.
@@
 Across all measurement campaigns mean A~sat~ (Figure `r asatfig`) and A~max~ (Table `r pvetab3`) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
-The relationships between photosynthetic capacity, leaf starch and leaf N on a mass basis was marginally significant (P = 0.058) but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001).
+The relationships between photosynthetic capacity, leaf starch and leaf N on a mass basis was marginally significant (P = 0.058), but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001).
 We used predictions from the linear mixed effect model equation to visualize these relationship of A~max~ to either leaf N content or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
@@
 As both rooting space and resources were finite in containers, the inability of seedlings to maintain the capacity of the belowground C sink resulted in the buildup of C assimilate in leaves.
-The feedback inhibition of *A~n~* from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process (Nebauer et al.
-2011).
+The feedback inhibition of *A~n~* from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process [@nebauer2011photosynthesis].
 Here, declines in A~max~ were correlated with higher starch content throughout the experiment.
@@
 ##2.5.3 Do reductions in photosynthesis explain reductions in seedling growth?
-Our model used a simple approach to drive seedling growth with measured reductions in leaf *A~n~* , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
+Our model used a simple approach to drive seedling growth with measured reductions in leaf *A~n~*, via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
 Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
@@
 These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
-It is possible that the overestimation of growth was due to an initial overestimation of *A~n~*, however, the robust empirical based methods used to generate photosynthetic parameters (J~max~, V~cmax~, R and g~1~) make this unlikely.
+It is possible that the overestimation of growth was due to an initial overestimation of *A~n~*, however, the robust empirical based methods used to generate photosynthetic parameters (J~max~, Vc~max~, R and g~1~) make this unlikely.
 Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A~n~* affect models which distinguish the fate of assimilate C within a plant.

### 2015-12-14 reproducibility_notes.R

@@ -15,3 +15,12 @@
 
 ##key words commented out
 ##author correspondence commented out
+
+
+
+###pub
+
+##currently using tree physiology abbr guidelines
+## abbr are made the same in text and in equations (remove italics from subscripts)
+
+##abstract 300 words

### 2015-12-14 manuscript/manuscript_pve.Rmd
more small edits to manusscript....made in thesis word document too

@@
 This led to the large reductions in biomass in small containers, compared to freely rooted seedlings.
-We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, consistent with the meta-analysis of Poorter et al.
+We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, consistent with the meta-analysis of Poorter, Bühler, et al.
 [-@poorter2012pot].
@@
 In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, outside of ontogenetic drift (Figure `r allocfig`a,b).
-This is a surprising result as shifts in allocation have been noted specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein].
+This is a surprising result as shifts in partitioning have been noted specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein].
 Surprisingly, a constant ratio of fine root mass to leaf mass was observed across all treatments suggesting a functional partitioning response to optimize resource gain did not occur.

### 2015-12-15 manuscript/tablesfigures_backup.Rmd
added missing table 2.3 to thesis chapter output
changed mean(se) to match other chapeters

@@
 date: "December 7, 2015"
-output: word_document
+output:
+  word_document:
+    reference_docx: manuscriptstyle_thesis.docx
 ---
@@
 **Table 1**.Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
+Each value reflects the mean (&pm; 1 standard error) for each treatment.
 Seedling mass and leaf $\delta$^13^C values are from final harvest.
@@
 Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
+Each value reflects the mean (&pm; 1 standard error) for each treatment.
 All values are from the final harvest.
@@
 Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
+Each value reflects the mean (&pm; 1 standard error) for each treatment.
 A~max~, R and g~s~ are each measured at 25 &deg;C.

### 2015-12-15 manuscript/thesis_pve.Rmd
added missing table 2.3 to thesis chapter output
changed mean(se) to match other chapeters

@@
 **Table 2.1**.Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
+Each value reflects the mean (&pm; 1 standard error) for each treatment.
 Seedling mass and leaf $\delta$^13^C values are from final harvest.
@@
 Different letters represent significant differences between treatments.
+
+\
+**Table 2.3**.
+Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Each value reflects the mean (&pm; 1 standard error) for each treatment.
+A~max~, R and g~s~ are each measured at 25 &deg;C.
+Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n=6).
+R, J~max~ and Vc~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements.
+Different letters represent significant differences between treatments.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
+
+```{r table3, echo=FALSE, warning=FALSE}
+dust(table3)%>%
+  sprinkle_colnames("Volume (L)", 
+                        "A~max~ ($\\mu$mol m^-2^ s^-1^)", 
+                        "R ($\\mu$mol m^-2^ s^-1^)",
+                        "J~max~",
+                        "Vc~max~",
+                        "g~s~ (mol m^-2^ s^-1^)",
+                        "g~1~") %>%
+  sprinkle(rows= 1, part="head",bold=TRUE)%>%
+  sprinkle_print_method("markdown")
+```
+
 \

### 2015-12-18 manuscript/manuscript_pve.Rmd
added missing table 2.3 to thesis chapter output
changed mean(se) to match other chapeters
edits from RD (most finished) all are in word document so far

@@
 
-Interpreting limitations to plant growth requires understanding of the balance between carbon (*C*) source and sink activity.
+Interpreting limitations to plant growth requires understanding the balance between carbon (*C*) source and sink activity.
 This study used manipulations of soil volume to test how growth is coupled to physiology, *C* allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
@@
 However, increases in *A*~n~ in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], *C* limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant *C* gain [@ovaska1993a].
-These manipulations of C source activity expose unresolved issues with how changes in *A*~n~ do not always infer similar responses in growth.
+These manipulations of C source activity expose unresolved issues with how changes in *A*~n~ do not always infer proportional responses in growth.
 
 \
-Alternatively, manipulating plant tissue *C* sinks is often used to investigate the correlation of *A*~n~ and growth.
+Alternatively, manipulating plant tissue *C* sinks is often used to investigate the correlation between *A*~n~ and growth.
 This is because metabolic signaling networks, relaying information on *C* and *N* status of different tissues, can regulate photosynthetic activity [@paul2001sink].
 If sink inhibition of *A*~n~ occurs, a close coordination between declines in *A*~n~ and growth should be expected.
-Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal, phloem girdling and low temperatures at high elevations.
-In these studies, down regulation of *A*~n~ was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
+Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal and phloem girdling.
+In these studies, down regulation of *A*~n~ was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@urban2007girdling; @haouari2013fruit].
 However, reductions in *A*~n~ were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
@@
 Leaf level gas exchange was measured with a standard leaf chamber (2 x 3 cm) equipped with blue-red light emitting diodes using a portable gas exchange system (LI-6400, LI-COR, Lincoln, NE, USA).
-*A*~sat~ measurements were made at PPFD of 1800 $\mu$mol m^-1^ s^-1^ and [CO~2~] of 400 $\mu$l l^-1^ and *A*~max~ with [CO~2~] of 1600 $\mu$l l^-1^ and PPFD of 1800 $\mu$mol photons m^-1^ s^-1^.
+*A*~sat~ measurements were made at PPFD of 1800 $\mu$mol m^-1^ s^-1^ and [CO~2~] of 400 $\mu$l l^-1^ and *A*~max~ with [CO~2~] of 1600 $\mu$l l^-1^ and PPFD of 1800 $\mu$mol m^-1^ s^-1^.
 This choice of light level to achieve light saturation is consistent with other studies on *Eucalyptus* species [@kallarackal1997ecophysiological;@pinkard1998photosynthetic;@crous2013photosynthesis;@drake2014capacity].
@@
 TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, were calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf *N* content.
-Similarly, TNC-free leaf *N* (*N*~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC and leaf *N* content.
+Similarly, TNC-free leaf *N* (*N*~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC content.
 
@@
 $$P_i = L\left(\frac{C_\mathrm{day'i}~\sigma_\mathrm{s}}{\epsilon_\mathrm{c}}\right) - R$$
-where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^), $\sigma$~s~ is a self shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
+where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^,, explained below), $\sigma$~s~ is a self shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
 Total respiration was calculated as
@@
 where *R*~c~ is published or local tissue respiration rates of fine roots, coarse roots or stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and *M*~c~ is the standing biomass of each component (g).
-*R*~leaf~ is represented in the calculation of *C*~day~ (described below).
+Leaf respiration is represented in the calculation of *C*~day~ (described below).
 The change in individual component biomass (*M*~c~), here solved on a daily time step, is given by
@@
 \
-*C*~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package in R with the mean photosynthetic parameters (*J*~max~, *Vc*~max~, R and *g*~1~) for each treatment and meteorological data from an onsite weather station.
+*C*~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *Vc*~max~, R and *g*~1~) for each treatment and meteorological data from an onsite weather station.
 *J*~max~ and *Vc*~max~ were estimated from AC~i~ curves (explained above), *R* was empirically measured and the *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed *g*~s~ values.
-Methods of the coupled leaf gas exchange model are described in Duursma et al [-@duursma2014peaked].
+Methods of the coupled leaf gas exchange model are also described in Duursma et al [-@duursma2014peaked].
 Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A*~n~ rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
@@
 [-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
-Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*~n~, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
+Using the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*~n~, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
 The ratio of total *A*~n~ with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments.
@@
 This optimized LMF was then used to constrain model runs with soil volume treatment specific *C*~day~, while keeping tissue respiration and turnover parameters constant, to determine if changes in leaf *A*~n~ alone could predict biomass of seedlings in containers (*M*~pots~).
-Next, model sensitivity to different *C* allocation scenarios, including observed treatment specific LMF and up-regulation of non-leaf tissue respiration by 50 % of default values (*M*~S1~ and *M*~S2~, respectively), was used to improve model biomass predictions compared to measured harvest biomass.
+Next, model sensitivity to different *C* allocation scenarios, including observed treatment specific LMF and up-regulation of non-leaf tissue respiration by 50 % of default values (*M*~S1~ and *M*~S2~, respectively), was used to test for improvement of model biomass predictions compared to measured harvest biomass.
 For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment specific mean *C*~day~ by first scaling values to the free seedling control.
@@
 ##Data analysis
-Differences in experimental parameters with soil volume were analysed by mixed-effects models in R with individual containers and experimental blocks as random effects and soil volume treatment as a categorical fixed effect with seven levels.
+Differences in measured parameters with soil volume were analysed by mixed-effects models in R with individual containers and experimental blocks as random effects and soil volume treatment as a categorical fixed effect with seven levels.
 Tukey's post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
-A linear mixed effect model of *A*~max~ and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R.
+A linear mixed effect model of *A*~mass~ and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R.
 Explained variance (*R*^2^) of mixed models were computed as in  [@nakagawa2013general].
 Tests of allometric relationships between log-transformed biomass components were implemented using standardized major axis regression in the 'smatr' package in R [@warton2012smatr].
-All tests of statistical significance were conducted at an alpha level of 0.05.
+All tests of statistical significance were conducted at an $\alpha$ level of 0.05.
 
@@
 Differences in biomass partitioning to leaves, stems and roots were not different across soil volumes after variation in seedling biomass across treatments was factored in the analysis (Figure `r allocfig`a,b).
-Across all treatments, the final harvest root:shoot biomass ratio was conserved in these seedlings which exhibited a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119]) and a near identical ratio of leaf to fine root mass (Figure `r allocfig`c).
+Across all treatments, the final harvest root:shoot biomass ratio was conserved in these seedlings which exhibited a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119]) and the ratio of leaf to fine root mass was also not different (Figure `r allocfig`c).
 
@@
 \
-Both *J*~max~ and *Vc*~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab2`).
-Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab2`).
-The *g*~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab2`).
+Both *J*~max~ and *Vc*~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`).
+Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`).
+The *g*~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab3`).
 
@@
 Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 MPa across all seedlings, respectively.
-Although *g*~s~ in free seedlings was generally higher than those in containers (Table `r pvetab2`, *P* < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
+Although *g*~s~ in free seedlings was generally higher than those in containers (Table `r pvetab3`, *P* < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
 Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table `r pvetab1`).
@@
 ##Modelling seedling biomass
-The default model *M*~free~, successfully optimized a LMF (21.6 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %.
+The default model (*M*~free~), successfully optimized a LMF (21.6 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %.
 Using this optimized LMF, the total biomass of modeled seedlings for each soil volume treatment (*M*~pots~) were on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf *C* gain (Figure `r massmodelfig`a).
-Thus, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments (Figure `r massmodelfig`b).
+As a result, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b).
 As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
@@
 #Discussion
-This study utilized a simple but novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
+This study utilized a novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
 We addressed questions regarding the coordination of *A*~n~ and growth by complementing empirical results with a *C* mass balance model.
@@
 It has been shown that roots subjected to environmental stress may send inhibitory signals to the shoots that affect *g*~s~, cell expansion, cell division and the rate of leaf appearance [@passioura2002soil].
-Here, this was evident in a large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
+Here, this was likely evident in a large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
 
@@
 \
-With high rates of *g*~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A*~n~.
+With high rates of *g*~s~, non-limiting leaf water potential ($\Psi$~pd~) and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A*~n~.
 This finding is consistent with other container size studies without drought treatments.
@@
 \
-As partitioning to fine roots did not change this provides evidence against an optimal foraging strategy for seedlings in containers.
+The lack of detected shifts in partitioning to fine roots provides evidence against an optimal foraging strategy for seedlings in containers.
 This could be because lateral root development is affected by inanimate obstacles and avoiding growth towards container walls could improve the efficiency of resource allocation [@falik2005root].
 The sensitivity of roots to their own exudates near obstructions may prevent further growth [@semchenko2008foraging].
-Here, we show that FRLD was highest in smallest containers suggesting that root restriction likely occurred as simple function of available rooting space.
+Here, we found that FRLD was highest in smallest containers suggesting that root restriction likely occurred as simple function of available rooting space.
 Additionally, physical restriction of root proliferation could have impacted root development and morphology prior to shifts in mass partitioning.
@@
 Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
-Although reductions in *A*~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
+Although reductions in both *A*~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
 [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth.
@@
 The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
-Our combined empirical and modeling approach shows that when non-photosynthesis parameters were kept constant changes in *A*~n~ were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
+Our combined empirical and modeling approach shows that when non-photosynthetic parameters were kept constant changes in *A*~n~ were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
 K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A*~n~ through the demand for *C*.
@@
 Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
+Each value reflects the mean (&pm; 1 standard error) for each treatment.
 All values are from the final harvest.
-Values for FRLD were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
+Values for fine root length density (FRLD) were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
 Different letters represent significant differences between treatments.
@@
 Responses of leaf level gas exchange parameters of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean(standard error) for each treatment.
+Each value reflects the mean (&pm; 1 standard error) for each treatment.
 *A*~max~, *R* and *g*~s~ are each measured at 25 &deg;C.
@@
 **Figure 1**.
-Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013
+Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and seedling leaf area estimated from leaf counts (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
 
@@
 For (b) lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment.
-For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (*R*^2^ = 0.82) with equation: log(x) = 0.983(log(y)) - 0.036.
+For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (*R*^2^ = 0.82) with equation: log(x) = 0.983log(y) - 0.036.
 

### 2015-12-18 manuscript/tablesfigures_backup.Rmd
edits from RD (most finished) all are in word document so far

@@
 All values are from the final harvest.
-Values for FRLD are only calculated for seedlings in containers as free seedlings have potentially unlimited soil volume to exploit.
+Values for fine root length density (FRLD) are only calculated for seedlings in containers as free seedlings have potentially unlimited soil volume to exploit.
 Different letters represent significant differences between treatments.
@@
 **Figure 1**.
-Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
+Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and seedling leaf area estimated from leaf counts (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
 
@@
 For (b) lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment.
-For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (R^2^ = 0.82) with equation: log(x) = 0.983(log(y)) - 0.036.
+For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (R^2^ = 0.82) with equation: log(x) = 0.983log(y) - 0.036.
 

### 2015-12-18 manuscript/thesis_pve.Rmd
edits from RD (most finished) all are in word document so far

@@
 
-Interpreting limitations to plant growth requires understanding of the balance between carbon (C) source and sink activity.
+Interpreting limitations to plant growth requires understanding the balance between carbon (C) source and sink activity.
 This study used manipulations of soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
@@
 However, increases in *A~n~* in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
-These manipulations of C source activity expose unresolved issues with how changes in *A~n~* do not always infer similar responses in growth.
+These manipulations of C source activity expose unresolved issues with how changes in *A~n~* do not always infer proportional responses in growth.
 
 \
-Alternatively, manipulating plant tissue C sinks is often used to investigate the correlation of *A~n~* and growth.
+Alternatively, manipulating plant tissue C sinks is often used to investigate the correlation between *A~n~* and growth.
 This is because metabolic signaling networks, relaying information on C and N status of different tissues, can regulate photosynthetic activity [@paul2001sink].
 If sink inhibition of *A~n~* occurs, a close coordination between declines in *A~n~* and growth should be expected.
-Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal, phloem girdling and low temperatures at high elevations.
-In these studies, down regulation of *A~n~* was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@hoch2002altitudinal; @urban2007girdling; @haouari2013fruit].
+Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal and phloem girdling.
+In these studies, down regulation of *A~n~* was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation; @urban2007girdling; @haouari2013fruit].
 However, reductions in *A~n~* were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
@@
 Leaf level gas exchange was measured with a standard leaf chamber (2 x 3 cm) equipped with blue-red light emitting diodes using a portable gas exchange system (LI-6400, LI-COR, Lincoln, NE, USA).
-A~sat~ measurements were made at PPFD of 1800 $\mu$mol m^-1^ s^-1^ and [CO~2~] of 400 $\mu$l l^-1^ and A~max~ with [CO~2~] of 1600 $\mu$l l^-1^ and PPFD of 1800 $\mu$mol photons m^-1^ s^-1^.
+A~sat~ measurements were made at PPFD of 1800 $\mu$mol m^-1^ s^-1^ and [CO~2~] of 400 $\mu$l l^-1^ and A~max~ with [CO~2~] of 1600 $\mu$l l^-1^ and PPFD of 1800 $\mu$mol m^-1^ s^-1^.
 This choice of light level to achieve light saturation is consistent with other studies on *Eucalyptus* species [@kallarackal1997ecophysiological;@pinkard1998photosynthetic;@crous2013photosynthesis;@drake2014capacity].
@@
 TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, were calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf N content.
-Similarly, TNC-free leaf N (N~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC and leaf N content.
+Similarly, TNC-free leaf N (N~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC content.
 
@@
 $$P_i = L\left(\frac{C_{day'i}~\sigma_s}{\epsilon_c}\right) - R$$
-where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^), $\sigma$~s~ is a self shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and R is the mass based total respiration of all tissue components (g C d^-1^).
+where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^, explained below), $\sigma$~s~ is a self shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and R is the mass based total respiration of all tissue components (g C d^-1^).
 Total respiration was calculated as
@@
 where R~c~ is published or local tissue respiration rates of fine roots, coarse roots or stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
-R~leaf~ is represented in the calculation of C~day~ (described below).
+Leaf respiration is represented in the calculation of C~day~.
 The change in individual component biomass (M~c~), here solved on a daily time step, is given by
@@
 \
-C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package in R with the mean photosynthetic parameters (J~max~, Vc~max~, R and g~1~) for each treatment and meteorological data from an onsite weather station.
+C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (J~max~, Vc~max~, R and g~1~) for each treatment and meteorological data from an onsite weather station.
 J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), R was empirically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed g~s~ values.
-Methods of the coupled leaf gas exchange model are described in Duursma et al [-@duursma2014peaked].
-Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A* rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
+Methods of the coupled leaf gas exchange model are also described in Duursma et al [-@duursma2014peaked].
+Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A~n~* rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
 C~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
@@
 [-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
-Inputting the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A~n~*, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
+Using the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A~n~*, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
 The ratio of total *A~n~* with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments.
@@
 This optimized LMF was then used to constrain model runs with soil volume treatment specific C~day~, while keeping tissue respiration and turnover parameters constant, to determine if changes in leaf *A~n~* alone could predict biomass of seedlings in containers (M~pots~).
-Next, model sensitivity to different C allocation scenarios, including observed treatment specific LMF and up-regulation of non-leaf tissue respiration by 50 % of default values (M~S1~ and M~S2~, respectively), was used to improve model biomass predictions compared to measured harvest biomass.
+Next, model sensitivity to different C allocation scenarios, including observed treatment specific LMF and up-regulation of non-leaf tissue respiration by 50 % of default values (M~S1~ and M~S2~, respectively), was used to test for improvement of biomass predictions compared to measured harvest biomass.
 For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment specific mean C~day~ by first scaling values to the free seedling control.
@@
 ##2.3.7 Data analysis
-Differences in experimental parameters with soil volume were analysed by mixed-effects models in R with individual containers and experimental blocks as random effects and soil volume treatment as a categorical fixed effect with seven levels.
+Differences in measured parameters with soil volume were analysed by mixed-effects models in R with individual containers and experimental blocks as random effects and soil volume treatment as a categorical fixed effect with seven levels.
 Tukey's post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
-A linear mixed effect model of A~max~ and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R.
+A linear mixed effect model of A~mass~ and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R.
 Explained variance (R^2^) of mixed models were computed as in  [@nakagawa2013general].
 Tests of allometric relationships between log-transformed biomass components were implemented using standardized major axis regression in the 'smatr' package in R [@warton2012smatr].
-All tests of statistical significance were conducted at an alpha level of 0.05.
+All tests of statistical significance were conducted at an $\alpha$ level of 0.05.
 
@@
 **Figure 2.1**.
-Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
+Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and seedling leaf area estimated from leaf counts (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
 \
@@
 greeks=c(alpha='\u03b1', Delta='\u0394', Sigma='\u03A3', mu='\u03bc',delta = '\u03b4')
+greeks2=c('\u03b1', '\u0394', '\u03A3', '\u03bc','\u03b4')
 
@@
                         "Leaf Nitrogen~TNC-free~ (%)",
-                        paste0("Leaf ", greeks['delta'],"^13^C"," (\u2030)")) %>%
+                        paste0("Leaf ", "$\\delta$","^13^C"," (\u2030)")) %>%
   sprinkle(rows= 1, part="head",bold=TRUE)%>%
@@
 All values are from the final harvest.
-Values for FRLD were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
+Values for fine root length density (FRLD) were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
 Different letters represent significant differences between treatments.
@@
 \
-Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab2`).
-Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab2`).
-The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab2`).
+Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`).
+Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`).
+The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab3`).
 
@@
 Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 MPa across all seedlings, respectively.
-Although g~s~ in free seedlings was generally higher than those in containers (Table `r pvetab2`, P < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
+Although g~s~ in free seedlings was generally higher than those in containers (Table `r pvetab3`, P < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
 Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table `r pvetab1`).
@@
 ##2.4.4 Modelling seedling biomass
-The default model M~free~, successfully optimized a LMF (21.6 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %.
+The default model (M~free~), successfully optimized a LMF (21.6 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %.
 Using this optimized LMF, the total biomass of modeled seedlings for each soil volume treatment (M~pots~) were on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf C gain (Figure `r massmodelfig`a).
-Thus, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments (Figure `r massmodelfig`b).
+As a result, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b).
 As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
@@
 #2.5  Discussion
-This study utilized a simple but novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
+This study utilized a novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
 We addressed questions regarding the coordination of *A~n~* and growth by complementing empirical results with a C mass balance model.
@@
 It has been shown that roots subjected to environmental stress may send inhibitory signals to the shoots that affect g~s~, cell expansion, cell division and the rate of leaf appearance [@passioura2002soil].
-Here, this was evident in a large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
+Here, this was likely evident in a large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
 
@@
 \
-With high rates of g~s~, non-limiting leaf water potential and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A~n~*.
+With high rates of g~s~, non-limiting leaf water potential ($\Psi$~pd~) and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A~n~*.
 This finding is consistent with other container size studies without drought treatments.
@@
 Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
-Although reductions in A~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
+Although reductions in both A~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
 [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A~n~* do not fully explain reduced seedling growth.
@@
 The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
-Our combined empirical and modeling approach shows that when non-photosynthesis parameters were kept constant changes in *A~n~* were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
+Our combined empirical and modeling approach shows that when non-photosynthetic parameters were kept constant changes in *A~n~* were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
 K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A~n~* through the demand for C.

### 2016-01-02 manuscript/manuscript_pve.Rmd
thesis edits RD

@@
 A linear mixed effect model of *A*~mass~ and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R.
-Explained variance (*R*^2^) of mixed models were computed as in  [@nakagawa2013general].
+Explained variance (*R*^2^) of mixed models were computed as in [@nakagawa2013general], in which the marginal *R*^2^ represents variance explained by fixed factors and the conditional *R*^2^ by both fixed and random factors.
 Tests of allometric relationships between log-transformed biomass components were implemented using standardized major axis regression in the 'smatr' package in R [@warton2012smatr].

### 2016-01-02 manuscript/thesis_pve.Rmd
thesis edits RD

@@
 A linear mixed effect model of A~mass~ and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R.
-Explained variance (R^2^) of mixed models were computed as in  [@nakagawa2013general].
+Explained variance (R^2^) of mixed models were computed as in [@nakagawa2013general], in which the marginal R^2^ represents variance explained by fixed factors and the conditional R^2^ by both fixed and random factors.
 Tests of allometric relationships between log-transformed biomass components were implemented using standardized major axis regression in the 'smatr' package in R [@warton2012smatr].

### 2016-01-02 manuscript/manuscript_pve.Rmd
changed 'free' to free and added freely-rooted

@@
 This study used manipulations of soil volume to test how growth is coupled to physiology, *C* allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
-We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown (free) seedlings.
+We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally planted freely-rooted (free) seedlings.
 We developed a seedling growth model that utilized leaf photosynthesis rates (*A*~n~) to allocate daily *C* uptake towards mass growth of stems, leaves and roots.
@@
 Containers were planted flush with the soil surface inside metal sleeves, designed to minimize excess air space between the container and outside soil while also allowing for container removal.
-This allowed for soil temperatures in containers to reflect conditions of naturally planted ('free') seedlings.
+This allowed for soil temperatures in containers to reflect conditions of naturally planted (free) seedlings.
 Each experimental block (n=7) contained a complete replicate set of six container volumes as well as one free seedling, with 1 m^2^ spacing.

### 2016-01-02 manuscript/thesis_pve.Rmd
changed 'free' to free and added freely-rooted

@@
 This study used manipulations of soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
-We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally sown (free) seedlings.
+We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally planted freely-rooted (free) seedlings.
 We developed a seedling growth model that utilized leaf photosynthesis rates (*A~n~*) to allocate daily C uptake towards mass growth of stems, leaves and roots.

### 2016-01-02 manuscript/manuscript_pve.Rmd
plant ecophys packaged default parameters intext

@@
 Each AC~i~ curve was started at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light (above).
-From these curves the photosynthetic parameters, *J*~max~ and *Vc*~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011].
+From these curves the photosynthetic parameters, *J*~max~ and *Vc*~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011] using default parameters.
 

### 2016-01-02 manuscript/thesis_pve.Rmd
plant ecophys packaged default parameters intext

@@
 Each AC~i~ curve was started at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light (above).
-From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011].
+From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011] using default parameters.
 

### 2016-01-03 manuscript/thesis_pve.Rmd
italicized R abbr for respiration

@@
 \
-Leaf dark respiration rates (R) was measured on each seedling during the same dates as AC~i~ curves.
+Leaf dark respiration rates (*R*) was measured on each seedling during the same dates as AC~i~ curves.
 Freshly detached leaves were collected at least 1 hour after sundown and placed inside a conifer chamber attached to the Licor 6400.
 Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions.
-Reported values of R are standardized rates at 25 &deg;C using a Q~10~ value (1.86) developed for these seedlings in a separate experiment (Drake et al.
+Reported values of *R* are standardized rates at 25 &deg;C using a Q~10~ value (1.86) developed for these seedlings in a separate experiment (Drake et al.
 unpublished).
@@
 $$P_i = L\left(\frac{C_{day'i}~\sigma_s}{\epsilon_c}\right) - R$$
-where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^, explained below), $\sigma$~s~ is a self shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and R is the mass based total respiration of all tissue components (g C d^-1^).
+where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^, explained below), $\sigma$~s~ is a self shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
 Total respiration was calculated as
@@
 $$R = \Sigma(R_c~M_c)$$
-where R~c~ is published or local tissue respiration rates of fine roots, coarse roots or stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
+where *R~c~* is published or local tissue respiration rates of fine roots, coarse roots or stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
 Leaf respiration is represented in the calculation of C~day~.
@@
 \
-C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (J~max~, Vc~max~, R and g~1~) for each treatment and meteorological data from an onsite weather station.
-J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), R was empirically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed g~s~ values.
+C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (J~max~, Vc~max~, *R* and g~1~) for each treatment and meteorological data from an onsite weather station.
+J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), *R* was empirically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed g~s~ values.
 Methods of the coupled leaf gas exchange model are also described in Duursma et al [-@duursma2014peaked].
@@
 Each value reflects the mean (&pm; 1 standard error) for each treatment.
-A~max~, R and g~s~ are each measured at 25 &deg;C.
+A~max~, *R* and g~s~ are each measured at 25 &deg;C.
 Values of A~max~, g~s~ and g~1~ represent overall means across measurement campaigns (n=6).
-R, J~max~ and Vc~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements.
+*R*, J~max~ and Vc~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements.
 Different letters represent significant differences between treatments.
@@
                         "A~max~ ($\\mu$mol m^-2^ s^-1^)", 
-                        "R ($\\mu$mol m^-2^ s^-1^)",
+                        "*R* ($\\mu$mol m^-2^ s^-1^)",
                         "J~max~",
@@
 These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
-It is possible that the overestimation of growth was due to an initial overestimation of *A~n~*, however, the robust empirical based methods used to generate photosynthetic parameters (J~max~, Vc~max~, R and g~1~) make this unlikely.
+It is possible that the overestimation of growth was due to an initial overestimation of *A~n~*, however, the robust empirical based methods used to generate photosynthetic parameters (J~max~, Vc~max~, *R* and g~1~) make this unlikely.
 Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A~n~* affect models which distinguish the fate of assimilate C within a plant.

### 2016-01-03 manuscript/thesis_pve.Rmd
A abbr

@@
 As a result, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b).
-As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
+As a result, the observed reductions in leaf *A~n~* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
 \

### 2016-01-06 manuscript/manuscript_pve.Rmd
caption fix
manuscript publishers additions to pve

@@
 \
-Courtney E. Campany^1^, Belinda Medlyn^1^, Remko A. Duursma^1^.
+COURTNEY E. CAMPANY^1,2^, BELINDA MEDLYN^1^ and REMKO A. DUURSMA^1^
 
@@
 ^1^ Hawkesbury Institute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW, Australia
+\
+^2^ Corresponding author (courtneycampany@gmail.com)
 
 \
-*Corresponding author*:
-Courtney Campany
-E: courtneycampany@gmail.com
+Hawkesbury Institute for the Environment, Western Sydney University
+Hawkesbury Campus
+Ground Floor, Building R2
+Locked Bag 1797
+Penrith 2751 NSW Australia
+
+\
+RUNNING HEAD:
 
@@
 pvetab3 <- "3"
-pvetabS <- "S3"
+pvetabS <- "S1"
 
@@
 
+# Acknowledgements
+We thank Burhan Amiji for for his outstanding technical assitance.
+We would like to thank the many Hawkesbury Institute for the Environment staff and students who provded field work help during the experimental harvest.
+
 # References {.unnumbered}

### 2016-01-07 manuscript/manuscript_pve.Rmd
pve manuscript to tree physliogy update

@@
 \
-RUNNING HEAD:
+RUNNING HEAD: SINK LIMITATION ALTERS SEEDLING CARBON BALANCE
 
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 In woody species, the coordination of *A*~n~ and growth has been studied with manipulations of *C* source activity.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Alternatively, manipulating plant tissue *C* sinks is often used to investigate the correlation between *A*~n~ and growth.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 An alternative experimental approach is to reduce belowground *C* sink strength in tree seedlings by manipulating rooting volume, by varying the container size [@arp1991effects; @nesmith1998effect; @poorter2012pot].
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 This study utilizes a novel field design to investigate the coordination between growth and *A*~n~ in *Eucalyptus tereticornis* Sm.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Our hypotheses were as follows: 
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 *Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain cohort.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Six container volumes were used ranging from 5 L to 35 L, with a 22.5 cm diameter, and lengths ranging from 15 to 100 cm.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Plants were watered weekly or when needed to maintain soil moisture at field capacity (13-15 %).
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Photosynthetic CO~2~ response (AC~i~) curves were measured at 25 &deg;C on a random subset of each container size (n=3) after new leaves were first produced (March 13-14^th^, 2013) and prior to the final harvest (May 14-15~th~, 2013).
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Leaf dark respiration rates (*R*) was measured on each seedling during the same dates as AC~i~ curves.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Leaf total non-structural carbohydrate (TNC) concentration was analyzed on dried and milled leaf samples using a total starch assay kit (Megazyme International, Wicklow, Ireland) and includes the starch  and soluble sugar concentrations (mg g^-1^).
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 *C*~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *Vc*~max~, R and *g*~1~) for each treatment and meteorological data from an onsite weather station.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf *A*~n~ with total plant leaf area.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ where sufficient to accurately predict overall seedling biomass production after 120 days.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 First, a default model was fitted with mean photosynthetic parameters from the free seedlings and then optimized to produce a LMF which correctly predicted both the leaf mass and total biomass of the harvested free seedling (*M*~free~).
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Total seedling biomass at harvest was significantly different across container volumes (*P* < 0.001) and between container treatments and free seedlings (*P* < 0.001, Table `r pvetab1`).
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table `r pvetab2`, *P* = 0.009).
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Both *J*~max~ and *Vc*~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`).
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 MPa across all seedlings, respectively.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over predictions of seedling *C* mass.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Decreases in *A*~sat~ occurred at the same time as reductions in height and diameter of seedlings in containers.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 With high rates of *g*~s~, non-limiting leaf water potential ($\Psi$~pd~) and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A*~n~.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Here, reductions in *A*~n~ were positively correlated with decreases in leaf *N* and leaf *N* was considerably reduced for seedlings in containers.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 As both rooting space and resources were finite in containers, the inability of seedlings to maintain the capacity of the belowground *C* sink resulted in the buildup of *C* assimilate in leaves.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 The lack of detected shifts in partitioning to fine roots provides evidence against an optimal foraging strategy for seedlings in containers.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Using measured LMF from the harvest, instead of the optimized seedling control (*M*~S1~), improved biomass predictions and provided insight into how sink limitation can impact leaf *C* allocation beyond *A*~n~.
@@
 \
+<br/>
+<br/>
+<br/>
+<br/>
 Increasing rates of non-leaf respiration (*M*~S2~) improved biomass predictions but to a far lesser extent than changes to leaf *C* allocation.
@@
 
+\
 **Table 2**.
@@
 Different letters represent significant differences between treatments.
-The volume effect *P* value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only differences between seedlings in containers.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only differences between seedlings in containers.
 ```{r table2, echo=FALSE, warning=FALSE}

### 2016-01-08 manuscript/manuscript_pve.Rmd
MT edits to thesis, made in all versions

@@
 Although growth was consistently different across soil volumes, dry mass partitioning to leaves, stems and roots was unchanged after 120 days.
-Photosynthetic capacity was significantly reduced in containers compared to free seedlings, and was related to both leaf nitrogen content and starch accumulation.
+Photosynthetic capacity was significantly reduced in containers compared to free seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
 We then asked whether the observed reductions in *A*~n~ explained the observed differences in seedling biomass.
@@
 Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
-In partial defoliation experiments, increases in *A*~n~ of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
+In partial defoliation experiments, increases in *A*~n~ of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
 However, increases in *A*~n~ in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], *C* limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant *C* gain [@ovaska1993a].
-These manipulations of C source activity expose unresolved issues with how changes in *A*~n~ do not always infer proportional responses in growth.
+These manipulations of C source activity expose unresolved issues with how changes in *A*~n~ do not always correspond with proportional responses in growth.
 
@@
 3).
-Reduced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, and a resulting down regulation of A.
+Reduced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, and a resulting down regulation of *A~n~*.
 We therefore expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume.
@@
 For each free seedling, used as the control, a 1 m^2^ subplot was excavated to the hard layer and replaced with the same soil used in each container.
-A border of root exclusion material was buried 0.25 m deep and extended 0.25 m above the ground surface around each subplot to exclude local vegetation.
+A border of root exclusion material was buried 0.25 m deep and extended 0.25 m above the ground surface around each subplot to exclude local vegetation, which was further kept out by periodic weeding.
 
@@
 For small containers (5, 10, and 15 L) a simple bottom plug was used to drain excess water from the gravel compartment.
-Each containers was inspected after every rainfall event to determine if pooling had occurred.
+Each container was inspected after every watering and rainfall event to determine if pooling had occurred.
 
@@
 <br/>
-We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ where sufficient to accurately predict overall seedling biomass production after 120 days.
+We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.
 Each model run utilized changes in *A*~n~ and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
-Cumulative net leaf *C* gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling *C* was assumed to equal half of the final mass for both modeled and observed seedlings.
+Cumulative net leaf *C* gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling *C* was assumed to equal half of the final dry mass for both modeled and observed seedlings.
 
@@
 Combined with the fact that soil *N* declined evenly across all treatments, there was no clear mechanism present to identify changes in root *N* uptake between free seedlings and seedlings in containers.
-In these already low quality soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
+In these already low fertility soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
 Although no clear feedback could be determined between the available soil *N* pool and decreases in leaf *N*, the effects of belowground sink limitation on *A*~n~ of seedlings in containers was evident throughout the experiment.
@@
 Additionally, physical restriction of root proliferation could have impacted root development and morphology prior to shifts in mass partitioning.
-Here, increases in SRL where detected in several of the soil volume treatments.
+Here, increases in SRL were detected in several of the soil volume treatments.
 This is not surprising as plants in containers have been shown to have different root morphology to field grown plants [@nesmith1998effect].
@@
 This is noteworthy, as *C* balance is a delicate equilibrium between fluxes of *A*~n~ and respiration, partial accounting of *C* dynamics can easily lead to erroneous conclusions [@valentini2000respiration].
-These results infer that using fixed rates of respiration in models likely underestimates plant responses to sink limitation.
+These results imply that using fixed rates of respiration in models likely underestimates plant responses to sink limitation.
 Thus, we agree with Delucia et al.
@@
 ##Conclusions
-With a novel field-based design we detected a massive effect of container volume on seedling growth, not between containers but with naturally planted seedlings.
+With a novel field-based design we detected a massive effect of container volume on seedling growth, when compared with naturally planted seedlings.
 This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants has seldom been studied.
@@
 The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
-Our combined empirical and modeling approach shows that when non-photosynthetic parameters were kept constant changes in *A*~n~ were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
+Our combined empirical and modeling approach shows that when non-photosynthetic parameters were kept constant, changes in *A*~n~ were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
 K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A*~n~ through the demand for *C*.
-Although this may be true, our results infer that quantifying the fate of assimilated *C* into known pools of growth, storage and *C* loss are needed prior to addressing this debate.
+Although this may be true, our results imply that quantifying the fate of assimilated *C* into known pools of growth, storage and *C* loss are needed prior to addressing this debate.
 Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of *C* and other constituents.
@@
 **Figure 4**.
-Soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25&deg;C.
+Soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25 &deg;C.
 Different letters represent significant differences between treatments.
@@
 **Figure S1**.
-Sensitivity testing of seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50 % (b).
+Sensitivity testing of the seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50 % (b).
 Open and filled symbols represent default model and harvest values, while shaded symbols represent model sensitivity to each scenario by soil volume treatment.

### 2016-01-08 manuscript/thesis_pve.Rmd
figure double check
MT edits to thesis, made in all versions

@@
 pvetab3 <- "2.3"
-pvetabS <- "2.S3"
+pvetabS <- "2.S1"
 
@@
 Although growth was consistently different across soil volumes, dry mass partitioning to leaves, stems and roots was unchanged after 120 days.
-Photosynthetic capacity was significantly reduced in containers compared to free seedlings, and was related to both leaf nitrogen content and starch accumulation.
+Photosynthetic capacity was significantly reduced in containers compared to free seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
 We then asked whether the observed reductions in *A~n~* explained the observed differences in seedling biomass.
@@
 Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
-In partial defoliation experiments, increases in *A~n~* of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
+In partial defoliation experiments, increases in *A~n~* of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
 However, increases in *A~n~* in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
-These manipulations of C source activity expose unresolved issues with how changes in *A~n~* do not always infer proportional responses in growth.
+These manipulations of C source activity expose unresolved issues with how changes in *A~n~* do not always correspond with proportional responses in growth.
 
@@
 \
-We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A~n~* where sufficient to accurately predict overall seedling biomass production after 120 days.
+We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A~n~* were sufficient to accurately predict overall seedling biomass production after 120 days.
 Each model run utilized changes in *A~n~* and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
-Cumulative net leaf C gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling C was assumed to equal half of the final mass for both modeled and observed seedlings.
+Cumulative net leaf C gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling C was assumed to equal half of the final dry mass for both modeled and observed seedlings.
 
@@
 **Figure 2.4**.
-Soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25&deg;C.
+Soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25 &deg;C.
 Different letters represent significant differences between treatments.
@@
 Combined with the fact that soil N declined evenly across all treatments, there was no clear mechanism present to identify changes in root N uptake between free seedlings and seedlings in containers.
-In these already low quality soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
+In these already low fertility soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
 Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the effects of belowground sink limitation on *A~n~* of seedlings in containers was evident throughout the experiment.
@@
 This is noteworthy, as C balance is a delicate equilibrium between fluxes of *A~n~* and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions [@valentini2000respiration].
-These results infer that using fixed rates of respiration in models likely underestimates plant responses to sink limitation.
+These results imply that using fixed rates of respiration in models likely underestimates plant responses to sink limitation.
 Thus, we agree with Delucia et al.
@@
 ##2.5.4 Conclusions
-With a novel field-based design we detected a massive effect of container volume on seedling growth, not between containers but with naturally planted seedlings.
+With a novel field-based design we detected a massive effect of container volume on seedling growth, when compared with naturally planted seedlings.
 This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants has seldom been studied.
@@
 The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
-Our combined empirical and modeling approach shows that when non-photosynthetic parameters were kept constant changes in *A~n~* were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
+Our combined empirical and modeling approach shows that when non-photosynthetic parameters were kept constant, changes in *A~n~* were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
 K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A~n~* through the demand for C.
-Although this may be true, our results infer that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
+Although this may be true, our results imply that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
 Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
@@
 **Figure 2.S1**.
-Sensitivity testing of seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50 % (b).
+Sensitivity testing of the seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50 % (b).
 Open and filled symbols represent default model and harvest values, while shaded symbols represent model sensitivity to each scenario by soil volume treatment.

### 2016-01-11 manuscript/thesis_pve.Rmd
final thesis edits from MT

@@
 We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally planted freely-rooted (free) seedlings.
-We developed a seedling growth model that utilized leaf photosynthesis rates (*A~n~*) to allocate daily C uptake towards mass growth of stems, leaves and roots.
+We developed a seedling growth model that utilized leaf photosynthesis rates (*A~n~*) to allocate daily C uptake towards mass growth of leaves, stems and roots.
 Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
@@
 We found that although belowground sink limitation resulted in down regulation of *A~n~*, these reductions were not large enough to explain observed growth responses.
-Thus, as *A~n~* and growth were not tightly coordinated, excess photosynthetic C not attributed to biomass resulted in seedlings with soil volume restriction.
+Thus, as *A~n~* and growth were not tightly coordinated, an unaccounted for pool of photosynthetic C resulted in seedlings with soil volume restriction.
 These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf C uptake.
@@
 $$P_i = L\left(\frac{C_{day'i}~\sigma_s}{\epsilon_c}\right) - R$$
-where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^, explained below), $\sigma$~s~ is a self shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
+where L is total plant leaf area (m^2^), C~day,i~ is the predicted daily C assimilation (g C g mass^-1^ d^-1^, explained below), $\sigma$~s~ is a self-shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
 Total respiration was calculated as

### 2016-01-11 manuscript/manuscript_pve.Rmd
final thesis edits from MT

@@
 We found that although belowground sink limitation resulted in down regulation of *A*~n~, these reductions were not large enough to explain observed growth responses.
-Thus, as *A*~n~ and growth were not tightly coordinated, excess photosynthetic *C* not attributed to biomass resulted in seedlings with soil volume restriction.
+Thus, as *A*~n~ and growth were not tightly coordinated, an unaccounted for pool of photosynthetic *C* resulted in seedlings with soil volume restriction.
 These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf *C* uptake.
@@
 $$P_i = L\left(\frac{C_\mathrm{day'i}~\sigma_\mathrm{s}}{\epsilon_\mathrm{c}}\right) - R$$
-where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^,, explained below), $\sigma$~s~ is a self shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
+where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^,, explained below), $\sigma$~s~ is a self-shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
 Total respiration was calculated as

### 2016-01-12 manuscript/manuscript_pve.Rmd
changed abstract

@@
 We then asked whether the observed reductions in *A*~n~ explained the observed differences in seedling biomass.
-We found that although belowground sink limitation resulted in down regulation of *A*~n~, these reductions were not large enough to explain observed growth responses.
+Although belowground sink limitation resulted in a reduction of *A*~n~, the model concluded that these reductions were not large enough to explain observed growth responses.
 Thus, as *A*~n~ and growth were not tightly coordinated, an unaccounted for pool of photosynthetic *C* resulted in seedlings with soil volume restriction.

### 2016-01-12 manuscript/thesis_pve.Rmd
changed abstract

@@
 We then asked whether the observed reductions in *A~n~* explained the observed differences in seedling biomass.
-We found that although belowground sink limitation resulted in down regulation of *A~n~*, these reductions were not large enough to explain observed growth responses.
+Although belowground sink limitation resulted in a reduction of *A~n~*, the model concluded that these reductions were not large enough to explain observed growth responses.
 Thus, as *A~n~* and growth were not tightly coordinated, an unaccounted for pool of photosynthetic C resulted in seedlings with soil volume restriction.

### 2016-01-12 manuscript/thesis_pve.Rmd
spelling

@@
 Additionally, severe reductions in *A~n~* in coffee plants were not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth].
-It is likely that reductions in *A~n~* of well-watered seedlings observed in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
+It is likely that reductions in *A~n~* of well-watered seedlings observed in our study of *E.
+tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
 

### 2016-01-15 manuscript/manuscript_pve.Rmd
updates cites, sent this manuscript version to BM

@@
   word_document:
-    reference_docx: manuscriptstyle_thesis.docx
+    reference_docx: manuscriptstyle.docx
   pdf_document: default
@@
 csl: tree-physiology.csl
-bibliography: references.bib
+bibliography: references2.bib
 ---

### 2016-03-08 manuscript/manuscript_pve.Rmd
now have corrected model (from BM) and it runs through plotting scripts for manuscript
regenerated daily model output script for time_course figures

renamed orginal mass model script (possibly delte)

spelling edits to manuscript

@@
 $$P_i = L\left(\frac{C_\mathrm{day'i}~\sigma_\mathrm{s}}{\epsilon_\mathrm{c}}\right) - R$$
-where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^,, explained below), $\sigma$~s~ is a self-shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
+where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$~s~ is a self-shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
 Total respiration was calculated as
@@
 ##Modelling seedling biomass
-The default model (*M*~free~), successfully optimized a LMF (21.6 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %.
+The default model (*M*~free~), successfully optimized a LMF (22.8 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %.
 Using this optimized LMF, the total biomass of modeled seedlings for each soil volume treatment (*M*~pots~) were on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf *C* gain (Figure `r massmodelfig`a).
@@
 # Acknowledgements
-We thank Burhan Amiji for for his outstanding technical assitance.
-We would like to thank the many Hawkesbury Institute for the Environment staff and students who provded field work help during the experimental harvest.
+We thank Burhan Amiji for his outstanding technical assistance. We would like to thank the many Hawkesbury Institute for the Environment staff and students who helped during the experimental harvest.
 

### 2016-03-08 master_scripts/massmodel_optimize.R

@@ -1,9 +1,7 @@
 source("functions and packages/startscripts.R")
 
 source("gC_day_model/model_start.R")
-source("functions and packages/massmodel_LAconstrain.R")
 source("functions and packages/massmodel.R")
-source("functions and packages/massmodel2.R")
 
 ##Build an optimization model for leaf mass fraction based on both leaf area and biomass
   ##used self shading as a function of leaf area (daily increment in model)
@@ -26,7 +24,7 @@ source("functions and packages/massmodel2.R")
 
 #4. ex of Base Model ex. using mean allocation, 120 days of Cday for reference (missing M)
 
-    sim_free <- productionmodel2(gCday=free, lma=lma_mean,frfrac=fr_frac_mean,crfrac=cr_frac_mean,
+    sim_free <- productionmodel(gCday=free, lma=lma_mean,frfrac=fr_frac_mean,crfrac=cr_frac_mean,
                 stemfrac=stem_frac_mean, leaffrac=lf, 
                 returnwhat="lastval")
 
@@ -38,7 +36,7 @@ source("functions and packages/massmodel2.R")
     
     ofrac <- (1-leaffrac)/3
     
-    p <- productionmodel2(leaffrac=leaffrac, frfrac=ofrac,crfrac=ofrac,stemfrac=ofrac,
+    p <- productionmodel3(leaffrac=leaffrac, frfrac=ofrac,crfrac=ofrac,stemfrac=ofrac,
                          gCday=free, lma=lma_trt[7], M_slope=Mcoef$b[7], M_intercept= Mcoef$intercept[7],
                          ...)
     if(returnhow == "output")return(p)
@@ -69,21 +67,20 @@ source("functions and packages/massmodel2.R")
   #model now uses optimized LMF for all volume trts, includes self shadeing
   optmassmodel<- list()
   for(i in 1:7){
-    optmassmodel[[i]] <- data.frame(productionmodel2(gCday=c120_trt[[i]][[1]], 
+    optmassmodel[[i]] <- data.frame(productionmodel(gCday=c120_trt[[i]][[1]], 
                          lma=lma_trt[i],frfrac=opt_ofrac, crfrac=opt_ofrac, stemfrac=opt_ofrac,
[…]

### 2016-03-08 master_scripts/massmodel_optimize_scenarios.R

@@ -1,9 +1,7 @@
-#source("functions and packages/startscripts.R")
+source("functions and packages/startscripts.R")
 
 source("gC_day_model/model_start.R")
-source("functions and packages/massmodel_LAconstrain.R")
 source("functions and packages/massmodel.R")
-source("functions and packages/massmodel2.R")
 
 ##Build an optimization model for leaf mass fraction based on both leaf area and biomass
 ##used self shading as a function of leaf area (daily increment in model)
@@ -24,11 +22,11 @@ LEAF_measured <- mean(free_harvest$leafmass)
 #3. vector of gcday 120 for free plant
 free <- as.vector(c120_trt[[7]][1:121,])
 
-#4. ex of Base Model ex. using mean allocation, 120 days of Cday for reference
+#4. ex of Base Model using mean allocation, 120 days of Cday for reference
 # 
 #     sim_free <- productionmodel2(gCday=free, lma=lma_mean,frfrac=fr_frac_mean,crfrac=cr_frac_mean,
 #                 stemfrac=stem_frac_mean, leaffrac=lf, M_slope=Mcoef$b[i], M_intercept= Mcoef$intercept[i],
-#                 returnwhat="lastval"returnwhat="lastval")
+#                 returnwhat="lastval")
 
 
 #5. optimise leaf mass fraction from free plant with harvest mass and leaf area
@@ -38,7 +36,7 @@ O.lmf <- function(leaffrac, ..., returnhow=c("objective","output")){
   
   ofrac <- (1-leaffrac)/3
   
-  p <- productionmodel2(leaffrac=leaffrac, frfrac=ofrac,crfrac=ofrac,stemfrac=ofrac,
+  p <- productionmodel(leaffrac=leaffrac, frfrac=ofrac,crfrac=ofrac,stemfrac=ofrac,
                         gCday=free, lma=lma_trt[7],M_slope=Mcoef$b[7], M_intercept= Mcoef$intercept[7],
                         ...)
   if(returnhow == "output")return(p)
@@ -49,11 +47,6 @@ O.lmf <- function(leaffrac, ..., returnhow=c("objective","output")){
   (LEAF - LEAF_measured)^2 + (MASS - MASS_measured)^2
   
 }
-
-# #6. Visualize if there is an optimum
-# lfs <- seq(0.05,0.3, length=101)
-# test_opt <- mapply(O.lmf, leaffrac=lfs)
-# plot(lfs,test_opt)  
 
[…]

### 2016-03-09 manuscript/manuscript_pve.Rmd
new model equation 1

@@
 (1)
-$$P_i = L\left(\frac{C_\mathrm{day'i}~\sigma_\mathrm{s}}{\epsilon_\mathrm{c}}\right) - R$$
+$$P_i = \frac{L~C_\mathrm{day'i}~\sigma_\mathrm{s} - R}{\epsilon_\mathrm{c}}$$
+
 where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$~s~ is a self-shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).

### 2016-03-09 biomass_timecourse.R

@@ -9,25 +9,37 @@ uniqueDate <- seq.Date(from=as.Date("2013/01/22"), to=as.Date("2013/05/21"), by=
 
 biomass_time$Date <- rep(uniqueDate, 7)
 
-#quick biomass plot
-plot(biomass~ Date, type='n', ylim=c(0, 200),data=biomass_time)
-points(biomass~ Date, data=biomass_time, col=cols[volume], pch=pchs[volume])
 
-#quick LA plot
-plot(leafarea~ Date, type='n', ylim=c(0, .55),data=biomass_time)
+##model output-----------------------------------------------------------------------------------------
+
+windows(7,10)
+
+####multipanel plot of s1, s2
+par(las=1,mgp=c(3,1,0),mfrow=c(2,1), las=1, cex=1)
+
+#biomass plot
+par(mar=c(2,5,1,1))
+plot(biomass~ Date, type='n', ylim=c(0, 200),data=biomass_time, ylab="Biomass", xlab="")
+points(biomass~ Date, data=biomass_time, col=cols[volume], pch=pchs[volume])
+legend("topleft", leglab, pch=c(rep(16,6),17),text.font=1,  title=vollab, cex=1, col=palette(), bty='n', inset=.01)
+
+#LA plot
+par(mar=c(4,5,1,1))
+plot(leafarea~ Date, type='n', ylim=c(0, .55),data=biomass_time, ylab="Leaf Area", xlab="")
 points(leafarea~ Date, data=biomass_time, col=cols[volume], pch=pchs[volume])
 
-##need to determine relative rate of decrease to free----------------------------------------------------------------------
+dev.copy2pdf(file= "master_scripts/manuscript_figs/modeloutput.pdf")  
+dev.off() 
 
+###make 2-panel with leaf area and biomass-------------------------------------------------------------------------
+
+##need to determine relative rate of decrease to free
 biomass_ls <- split(biomass_time, biomass_time$volume)
 free_mass <- biomass_ls[[7]]$biomass
 free_la <- biomass_ls[[7]]$leafarea
 
-
 biomass_reductions <- lapply(biomass_ls, function(x) {x$reduction_scaled = x$biomass/free_mass; return(x)})
 leafarea_reductions <- lapply(biomass_ls, function(x) {x$reduction_scaled = x$leafarea/free_la; return(x)})
-
-###make 2-panel with leaf area and biomass-------------------------------------------------------------------------
 
 ###multiply biomass *.5 if C
 windows(7,10)

### 2016-03-11 manuscript/manuscript_pve.Rmd
started tnc model
edits from BM to manuscript

added new best way script to eventaully replace scenarios

@@
 ---
-title: Belowground sink limitation alters growth and carbon balance of *Eucalyptus* seedlings
+title: Reduced growth due to belowground sink limitation is not explained by reduced photosynthesis
 author: ""
@@
 Although belowground sink limitation resulted in a reduction of *A*~n~, the model concluded that these reductions were not large enough to explain observed growth responses.
-Thus, as *A*~n~ and growth were not tightly coordinated, an unaccounted for pool of photosynthetic *C* resulted in seedlings with soil volume restriction.
+Thus, as *A*~n~ and growth were not tightly coordinated, an unaccounted-for pool of photosynthetic *C* resulted in seedlings with soil volume restriction.
 These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf *C* uptake.
@@
 At shorter temporal scales, however, growth can instead be mediated by tissue *C* storage pools.
-This has led to the current debate on how strongly plant growth is controlled by either source or sink activity.
+This discrepancy has led to the current debate on how strongly plant growth is controlled by either source or sink activity.
 Consequently, plant growth cannot always be simply determined by *A*~n~, making it complex to understand and challenging to model [@fourcaud2008plant].
@@
 <br/>
-In woody species, the coordination of *A*~n~ and growth has been studied with manipulations of *C* source activity.
-Examples included elevated CO~2~ experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments.
-Elevated CO~2~ has been shown to increase *A*~n~ [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a stimulation of 23 % in forest biomass production [@norby2005forest].
+One approach to examine the coordination of *A*~n~ and growth is to manipulate *C* source activity.
+Examples include elevated CO~2~ and partial defoliation experiments.
+Elevated CO~2~ has been shown to increase *A*~n~ [@drake1997more; @ainsworth2007response]; across four forest Free-Air CO~2~ Enrichment (FACE) experiments this increased photosynthetic uptake resulted in a stimulation of biomass production by 23 % on average [@norby2005forest].
 Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
-In partial defoliation experiments, increases in *A*~n~ of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
+In partial defoliation experiments, increases in *A*~n~ of the remaining foliage are commonly shown, and are attributed to reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
 However, increases in *A*~n~ in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], *C* limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant *C* gain [@ovaska1993a].
-These manipulations of C source activity expose unresolved issues with how changes in *A*~n~ do not always correspond with proportional responses in growth.
+These manipulations of C source activity demonstrate that changes in *A*~n~ do not always correspond with proportional responses of growth.
 
@@
 <br/>
-Alternatively, manipulating plant tissue *C* sinks is often used to investigate the correlation between *A*~n~ and growth.
+Alternatively, manipulation of plant tissue *C* sinks is often used to investigate the correlation between *A*~n~ and growth.
 This is because metabolic signaling networks, relaying information on *C* and *N* status of different tissues, can regulate photosynthetic activity [@paul2001sink].
 If sink inhibition of *A*~n~ occurs, a close coordination between declines in *A*~n~ and growth should be expected.
-Whether photosynthetic down regulation is evident in woody species has been tested through fruit removal and phloem girdling.
-In these studies, down regulation of *A*~n~ was frequently correlated to carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@urban2007girdling; @haouari2013fruit].
+The occurrence of photosynthetic down regulation has been tested through fruit removal and phloem girdling.
+In these studies, down regulation of *A*~n~ was found to correlate with carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@urban2007girdling; @haouari2013fruit].
 However, reductions in *A*~n~ were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
-These mixed results are not surprising as we still know little about the balance between assimilation, storage and growth across temporal scales in plants [@smith2007coordination].
+This lack of continuity among findings is not surprising, as we still know little about the balance between assimilation, storage and growth across temporal scales in plants [@smith2007coordination].
 As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to the occurrence of large fruiting sinks, they tell us little about source-sink coordination in typical growing conditions for woody species.
@@
 Possible advantages of this approach are that it allows a large range of treatment levels, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
-Seedlings undergo many physiological and morphological changes in response to rooting volume, including biomass partitioning, *A*~n~, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
+Seedlings undergo many physiological and morphological changes in response to rooting volume, including changes in biomass partitioning, *A*~n~, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
 Inadequate rooting volume may decrease *C* sink strength by progressively restricting root growth in growing plants [@thomas1991root].
@@
 Plots were located in an open cover paddock that was converted from native pasture grasses.
-Top soils at this site are an alluvial formation of low-fertility sandy loam soils (380 and 108 mg kg^-1^ total N and phosphorus respectively) with low organic matter (0.7 %) and low water holding capacity.
+Top soils are an alluvial formation of low-fertility sandy loam soils (380 and 108 mg kg^-1^ total N and phosphorus respectively) with low organic matter (0.7 %) and low water holding capacity.
 At this site a soil hard layer exists at ~1.0 m with a transition to heavy clay soils.
@@
 <br/>
-*Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain cohort.
+Forty-nine *Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain cohort.
 Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.
 Previous container experiments have confirmed that species with tap roots (similar to *E.
-tereticornis*) use the center of the container as the medium for thick roots leaving the periphery of the soil as the most active sites for fine root proliferation [@biran1980a; @biran1980b].
+tereticornis*) use the center of the container as the medium for thick roots, leaving the periphery of the soil as the most active sites for fine root proliferation [@biran1980a; @biran1980b].
 By using a species with tap root growth and manipulations of container length rather than width, we believed that a more realistic test of growth inhibition through constrained soil volume would be achieved.
@@
 Soil in each container was packed to achieve a target soil bulk density that matched local soil conditions of 1.7 g cm^-3^.
-A Imidacloprid (BAYER CropScience) insecticide tablet was planted 5 cm below the roots of each seedling.
+An Imidacloprid (BAYER CropScience) insecticide tablet was planted 5 cm below the roots of each seedling.
 Containers were planted flush with the soil surface inside metal sleeves, designed to minimize excess air space between the container and outside soil while also allowing for container removal.
@@
 Leaf gas exchange measurements were performed fortnightly at saturating light (*A*~sat~) and saturating light and [CO~2~] (*A*~max~) on new fully expanded leaves.
-Measurements were initiated only after sufficient new leaf growth occurred (March 05^th^, 2013), approximately 6 weeks following planting, and continued until the biomass harvest.
-Leaf level gas exchange was measured with a standard leaf chamber (2 x 3 cm) equipped with blue-red light emitting diodes using a portable gas exchange system (LI-6400, LI-COR, Lincoln, NE, USA).
+Measurements were initiated only after sufficient new leaf growth occurred (March 5^th^, 2013), approximately 6 weeks following planting, and continued until the biomass harvest.
+Leaf gas exchange was measured with a standard leaf chamber (2 x 3 cm) equipped with blue-red light emitting diodes using a portable gas exchange system (LI-6400, LI-COR, Lincoln, NE, USA).
 *A*~sat~ measurements were made at PPFD of 1800 $\mu$mol m^-1^ s^-1^ and [CO~2~] of 400 $\mu$l l^-1^ and *A*~max~ with [CO~2~] of 1600 $\mu$l l^-1^ and PPFD of 1800 $\mu$mol m^-1^ s^-1^.
@@
 <br/>
-Photosynthetic CO~2~ response (AC~i~) curves were measured at 25 &deg;C on a random subset of each container size (n=3) after new leaves were first produced (March 13-14^th^, 2013) and prior to the final harvest (May 14-15~th~, 2013).
+Photosynthetic CO~2~ response (AC~i~) curves were measured at 25 &deg;C on a random subset of each container size (n=3) after new leaves were first produced (March 13-14^th^, 2013) and prior to the final harvest (May 14-15^th^, 2013).
 Each AC~i~ curve was started at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light (above).
-From these curves the photosynthetic parameters, *J*~max~ and *Vc*~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011] using default parameters.
+From these curves the photosynthetic parameters, *J*~max~ and *V*~cmax~, were quantified using the biochemical model of @farquhar1980biochemical and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011] using default parameters.
 
@@
 <br/>
-Leaf dark respiration rates (*R*) was measured on each seedling during the same dates as AC~i~ curves.
+Leaf dark respiration rates (*R*) were measured on each seedling on the same dates as AC~i~ curves.
 Freshly detached leaves were collected at least 1 hour after sundown and placed inside a conifer chamber attached to the Licor 6400.
@@
 Predawn ($\Psi$~pd~) and midday ($\Psi$~l~) leaf water potentials were measured for each seedling using a PMS 1505D pressure chamber (PMS Instruments, Albany, OR, USA) on fully expanded leaves during the same time period as AC~i~ and *R*.
-Leaves were detached and immediately stored inside foil covered bags before water potential measurements were performed.
+Leaves were detached and immediately stored inside foil-covered bags before water potential measurements were performed.
 $\Psi$~pd~ was measured before sunrise and $\Psi$~l~ at midday 13:00-14:30 h.
@@
 ##Leaf, root and soil chemistry
-Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of *N* content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
+Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of nitrogen (*N*) content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
 Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis of *N*.
-Nitrogen concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of N~2~ and CO~2~).
+Nitrogen concentrations ([*N*]) of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of N~2~ and CO~2~).
 The percentage of *N* in the sample was calculated by comparison with certified standards.
@@
 Starch was quantified using a thermostable $\alpha$-amylase and amyloglucosidase assay [@McCleary_starch] and soluble sugars were determined following the anthrone method [@ebell1969variation].
-Complete methods of the TNC assay are described in [@mitchell2013drought].
-TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, were calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf *N* content.
+Complete methods of the TNC assay are described in @mitchell2013drought.
+TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, was calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf *N* content.
 Similarly, TNC-free leaf *N* (*N*~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC content.
@@
 <br/>
-*C*~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *Vc*~max~, R and *g*~1~) for each treatment and meteorological data from an onsite weather station.
-*J*~max~ and *Vc*~max~ were estimated from AC~i~ curves (explained above), *R* was empirically measured and the *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed *g*~s~ values.
+*C*~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *R* and *g*~1~) for each treatment and meteorological data from an onsite weather station.
+*J*~max~ and *V*~cmax~ were estimated from AC~i~ curves (explained above), *R* was empirically measured and the *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values.
 Methods of the coupled leaf gas exchange model are also described in Duursma et al [-@duursma2014peaked].
@@
 <br/>
-We then utilized this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.
-Each model run utilized changes in *A*~n~ and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
+We then used this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.
+Each model run used changes in *A*~n~ and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
 Cumulative net leaf *C* gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling *C* was assumed to equal half of the final dry mass for both modeled and observed seedlings.
@@
 <br/>
-First, a default model was fitted with mean photosynthetic parameters from the free seedlings and then optimized to produce a LMF which correctly predicted both the leaf mass and total biomass of the harvested free seedling (*M*~free~).
-This optimized LMF was then used to constrain model runs with soil volume treatment specific *C*~day~, while keeping tissue respiration and turnover parameters constant, to determine if changes in leaf *A*~n~ alone could predict biomass of seedlings in containers (*M*~pots~).
-Next, model sensitivity to different *C* allocation scenarios, including observed treatment specific LMF and up-regulation of non-leaf tissue respiration by 50 % of default values (*M*~S1~ and *M*~S2~, respectively), was used to test for improvement of model biomass predictions compared to measured harvest biomass.
-For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment specific mean *C*~day~ by first scaling values to the free seedling control.
+To test the hypothesis, a default model with mean photosynthetic parameters from the free seedlings was optimized to estimate a LMF which correctly predicted both the leaf mass and total biomass of the harvested free seedling (*M*~free~).
+This optimized LMF was then used to constrain model runs with treatment-specific *C*~day~, while keeping tissue respiration and turnover parameters constant, to determine if changes in leaf *A*~n~ alone could predict biomass of seedlings in containers (*M*~pots~).
+Next, model sensitivity to different *C* allocation scenarios, including observed treatment-specific LMF and up-regulation of non-leaf tissue respiration by 50 % of default values (*M*~S1~ and *M*~S2~, respectively), was used to test for improvement of model biomass predictions compared to measured harvest biomass.
+For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment-specific mean *C*~day~ by first scaling values to the free seedling control.
 
@@
 A linear mixed effect model of *A*~mass~ and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R.
-Explained variance (*R*^2^) of mixed models were computed as in [@nakagawa2013general], in which the marginal *R*^2^ represents variance explained by fixed factors and the conditional *R*^2^ by both fixed and random factors.
+Explained variance (*R*^2^) of mixed models were computed as in @nakagawa2013general, in which the marginal *R*^2^ represents variance explained by fixed factors and the conditional *R*^2^ by both fixed and random factors.
 Tests of allometric relationships between log-transformed biomass components were implemented using standardized major axis regression in the 'smatr' package in R [@warton2012smatr].
@@
 Plant height, diameter and leaf area diverged between container volumes soon after start of the experiment (Figure `r allomfig`a-c).
-First, seedling leaf area significantly diverged between soil volumes (*P* < 0.029) during the 5^th^ week of the experiment.
-Following this period both height (8^th^) week) and then diameter (9^th^ week) significantly deviated across soil volumes (*P* < 0.045 & 0.035, respectively).
+First to diverge was seedling leaf area, which significantly differed among soil volumes (*P* < 0.029) during the 5^th^ week of the experiment.
+Significant differences were then observed in both height (8^th^ week) and then diameter (9^th^ week) significantly among soil volumes (*P* < 0.045 & 0.035, respectively).
 The large reductions in height gain and total leaf area in smaller compared to larger containers continued throughout the experiment.
 In this field study, colder temperatures and reductions in total PPFD per day (Figure `r airvarsfig`) likely slowed the growth of seedlings in the final weeks of the experiment.
-Seedlings maintained diameter growth throughout the experiment, although marginal with smaller soil volumes in the final month.
+Seedlings maintained diameter growth throughout the experiment, although growth was marginal in smaller soil volumes in the final month.
 Final seedling height significantly increased with increasing soil volume (*P* < 0.001).
-Increases in both final stem diameter (*P* < 0.001) and cumulative leaf area (both *P* < 0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling treatments.
+Increases in both final stem diameter and cumulative leaf area (both *P* < 0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling treatments.
 
@@
 Total seedling biomass at harvest was significantly different across container volumes (*P* < 0.001) and between container treatments and free seedlings (*P* < 0.001, Table `r pvetab1`).
-On average, harvested biomass of free seedlings was 84% higher than seedlings in containers.
+On average, harvested biomass of free seedlings was 84% higher than that of seedlings in containers.
 Plant biomass was positively correlated with total leaf area across all treatments (*R*^2^ = 0.97, *P* < 0.001).
@@
 Fine root length density was significantly higher in the two smallest container sizes and was the lowest in the largest container size (Table `r pvetab2`, *P* < 0.001).
-Over the duration of the experiment SLA~f~ was higher in free seedlings, but was not different across containers sizes (Table `r pvetab1`, *P* < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (*P* < 0.001).
+Over the duration of the experiment SLA~f~ was higher in free seedlings, but was not different across container sizes (Table `r pvetab1`, *P* < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (*P* < 0.001).
 
@@
 Leaf *N*~f~ was significantly higher in free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, *P* < 0.001).
-Throughout the remainder of the experiment the smallest container volume had a significant reduction in leaf *N*~f~ compared to other soil volumes, while free seedlings maintained the highest leaf *N*~f~ (Table `r pvetab1`, *P* < 0.001).
+Throughout the remainder of the experiment the smallest container volume had significantly lower leaf *N*~f~ than other soil volumes, while free seedlings maintained the highest leaf *N*~f~ (Table `r pvetab1`, *P* < 0.001).
 Leaf starch content in the smallest container was ca.
@@
 At the first measurement campaign, both *A*~sat~ and *A*~max~ were significantly higher in the free seedling treatment compared to seedlings in containers (both *P* < 0.001).
-Across all measurement campaigns mean *A*~sat~ (Figure `r asatfig`) and *A*~max~ (Table `r pvetab3`) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
-The relationships between photosynthetic capacity, leaf starch and leaf *N* on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated to both leaf *N* content and leaf starch (both *P* < 0.001).
-We used predictions from the linear mixed effect model equation to visualize these relationship of *A*~max~ to either leaf *N* content or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
+Across all measurement campaigns, mean *A*~sat~ (Figure `r asatfig`) and *A*~max~ (Table `r pvetab3`) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
+The relationship between leaf starch and leaf *N* on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated with both leaf *N* content and leaf starch (both *P* < 0.001).
+We used predictions from the linear mixed effect model equation to visualize these relationships of *A*~max~ to either leaf *N* content or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
 Across all measurement campaigns and treatments *A*~max~ was higher when leaf *N* was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
@@
 <br/>
-Both *J*~max~ and *Vc*~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`).
+Both *J*~max~ and *V*~cmax~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`).
 Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`).
@@
 Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table `r pvetab1`).
-Combined these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment.
+Combined, these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment.
 Soil N at harvest was not different across soil volumes ($\bar{x}$ = 4.5 %), with minimal decreases from pre-planting value ($\bar{x}$ = 4.9 %).
-This indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
+This similarity indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
 
 ##Modelling seedling biomass
-The default model (*M*~free~), successfully optimized a LMF (22.8 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %.
-Using this optimized LMF, the total biomass of modeled seedlings for each soil volume treatment (*M*~pots~) were on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf *C* gain (Figure `r massmodelfig`a).
+Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 22.8 %l with this LMF, the model predicted mean harvest total biomass of free seedlings within 1.2 %.
+Using this optimized LMF, the modeled total biomass of seedlings for each soil volume treatment (*M*~pots~) was on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf *C* gain (Figure `r massmodelfig`a).
 As a result, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b).
@@
 <br/>
-Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over predictions of seedling *C* mass.
-Testing the sensitivity of the model to observed treatment-specific LMF from the final harvest (*M*~S1~), which were each lower than the optimized LMF value (see Figure `r allocfig`a), improved model predictions of seedling C mass but still overestimated seedling total *C* by 32&pm;11.1 % (Figure `r massmodelfig2`a).
+Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over-predictions of seedling *C* mass.
+Running the model with observed treatment-specific LMF values from the final harvest (*M*~S1~), which were each lower than the optimized LMF value (see Figure `r allocfig`a), improved model predictions of seedling C mass but still overestimated seedling total *C* by 32&pm;11.1 % (Figure `r massmodelfig2`a).
 Using harvest values of LMF, however, does not capture the observed increase in leaf turnover of seedlings in small containers (Figure `r allomfig`c).
 Thus, the use of harvest LMF values for seedlings in containers in *M*~S1~ likely underestimates daily C allocation to leaves over the final months of the experiment.
-Increases of 50 % in non-leaf tissue respiration (*M*~S2~) improved biomass estimates slightly but overestimated mass *C* by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
+Increases of 50 % in non-leaf tissue respiration (*M*~S2~) improved biomass estimates slightly but nonetheless overestimated mass *C* by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
 With *M*~S2~, non-tissue respiration rates would need to be increased by ca.
@@
 ##Reductions in growth and physiology under sink limitation
-Soon after seedlings became established both height and diameter growth were negatively affected by decreasing soil volume.
-This led to the large reductions in biomass in small containers, compared to freely rooted seedlings.
+Soon after seedlings became established, both height and diameter growth were negatively affected by decreasing soil volume.
+Low growth led to large reductions in biomass in small containers, compared to freely rooted seedlings.
 We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, consistent with the meta-analysis of Poorter, Bühler, et al.
@@
 It has been shown that roots subjected to environmental stress may send inhibitory signals to the shoots that affect *g*~s~, cell expansion, cell division and the rate of leaf appearance [@passioura2002soil].
-Here, this was likely evident in a large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
+Here, we observed a large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
 
@@
 Decreases in *A*~sat~ occurred at the same time as reductions in height and diameter of seedlings in containers.
-This initially suggests a strong link between growth and an apparent down regulation of *A*~n~.
-However, there are several possible mechanisms that can explain reduced *A*~n~ in small containers including nutrient content, water or reduced sink strength [@poorter2012pot].
+This observation initially suggests a strong link between growth and an apparent down regulation of *A*~n~.
+However, there are several possible mechanisms that can explain reduced *A*~n~ in small containers including reduced nutrient content or water availability, or reduced sink strength [@poorter2012pot].
 It was therefore necessary to examine each of these factors to determine if the induced belowground sink limitation actually triggered photosynthetic down regulation.
@@
 <br/>
-With high rates of *g*~s~, non-limiting leaf water potential ($\Psi$~pd~) and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A*~n~.
+With high rates of *g*~s~, non-limiting leaf water potential ($\Psi$~pd~), and consistent leaf $\delta$^13^C across soil volume treatments, there was little evidence that water stress caused the reduction in *A*~n~.
 This finding is consistent with other container size studies without drought treatments.
 For example, reduced *A*~max~ in cotton seedlings grown at elevated CO~2~ was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased *g*~s~ [@thomas1991root].
-Additionally, severe reductions in *A*~n~ in coffee plants were not attributed to impacts of container size on leaf water potentials or *g*~s~ [@ronchi2006growth].
-It is likely that reductions in *A*~n~ of well-watered seedlings observed in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
+Similarly, severe reductions in *A*~n~ in coffee plants were not attributed to impacts of container size on leaf water potentials or *g*~s~ [@ronchi2006growth].
+It is thus likely that reductions in *A*~n~ of well-watered seedlings observed in our study of *E.
+tereticornis* seedlings are not the result of limiting soil moisture availability.
 
@@
 <br/>
-Here, reductions in *A*~n~ were positively correlated with decreases in leaf *N* and leaf *N* was considerably reduced for seedlings in containers.
-As leaf *N* reductions were detected with TNC-free leaf mass, this suggests that physical root restriction or decreased supply likely affected seedling *N* uptake instead of TNC dilution in leaves in the smallest containers.
+with respect to nutrient availability, reductions in *A*~n~ were positively correlated with decreases in leaf *N* and leaf *N* was considerably reduced for seedlings in containers.
+As leaf *N* reductions were detected with TNC-free leaf mass, it is likely that physical root restriction or decreased supply affected seedling *N* uptake instead of TNC dilution in leaves in the smallest containers.
 Root *N* at the end of the experiment was on average higher in free seedlings but not consistently higher than every container volume treatment.
 Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf *N* in free seedlings, but this effect is unknown.
-Combined with the fact that soil *N* declined evenly across all treatments, there was no clear mechanism present to identify changes in root *N* uptake between free seedlings and seedlings in containers.
+Combined with the fact that soil *N* declined evenly across all treatments, there was no clear mechanism present to drive changes in root *N* uptake between free seedlings and seedlings in containers.
 In these already low fertility soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
@@
 Values of *A*~max~, *g*~s~ and *g*~1~ represent overall means across measurement campaigns (n=6).
-R, *J*~max~ and *Vc*~max~ values are means of two measurement campaigns at beginning and end of gas exchange measurements.
+R, *J*~max~ and *V*~cmax~ values are means of two measurement campaigns at beginning and end of gas exchange measurements.
 Different letters represent significant differences between treatments.
@@
                         "*J*~max~",
-                        "*Vc*~max~",
+                        "*V*~cmax~",
                         "*g*~s~ (mol m^-2^ s^-1^)",
@@
 **Figure S1**.
-Sensitivity testing of the seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50 % (b).
-Open and filled symbols represent default model and harvest values, while shaded symbols represent model sensitivity to each scenario by soil volume treatment.
+Sensitivity testing of the seedling growth model to different carbon allocation strategies, including; (a) leaf mass fraction set to treatment-specific final harvest values and (b) increases in respiration of non-leaf tissue components by 50 %.
+Open and filled symbols represent default model and harvest values, respectively, while shaded symbols represent model sensitivity to each scenario by soil volume treatment.
 Both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.

### 2016-03-11 master_scripts/allocation_plotting.R

@@ -73,8 +73,8 @@ text(x=7.1, 63, "(b)", cex=1.51)
 
 par(mar=c(5,7,1,.3),xpd = FALSE)
 with(ratio_agg, plot(log10(fineroot.mean), log10(leafmass.mean), ylim=c(0,2.25), xlim=c(0,2.25),
-                     xlab = "log10(Fine Root Mass)  (g)",
-                     ylab = "log10(Leaf Mass)  (g)",
+                     xlab = "Fine Root Mass  (g)",
+                     ylab = "Leaf Mass  (g)",
                     axes=FALSE, type='n'))
 abline(0,1, lwd=2, lty=2, col="grey35")
 text(x=.09, 2.2, "(c)", cex=1.51)

### 2016-03-22 manuscript/manuscript_pve.Rmd
starting values for leaf area not resolved
fixed error in leaf count raw datasheet

calculated Cday gross

@@
 ##Modelling seedling biomass
-Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 22.8 %l with this LMF, the model predicted mean harvest total biomass of free seedlings within 1.2 %.
+Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 25.7 %; with this LMF, the model predicted mean harvest total biomass of free seedlings within 0.1 %.
 Using this optimized LMF, the modeled total biomass of seedlings for each soil volume treatment (*M*~pots~) was on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf *C* gain (Figure `r massmodelfig`a).

### 2016-03-22 clean Scripts/harvest leaves.R

@@ -30,40 +30,41 @@ leafharvest_agg <- aggregate(cbind(totalarea, totalcount) ~ volume , data = leaf
 
 
 ####relationship between leaf length and area-------------------------------------------------------------------
-area_length <- leafharvest[,c(1, 12, 15:16)]
-  area_length$ratio <- with(area_length, areaperleaf/leaf_length)
-
-ll_mod <- lm(areaperleaf~leaf_length, data=area_length)
-  extract_func(ll_mod)
-ll_mod_1000<- lm(areaperleaf~leaf_length, data=area_length, subset=volume==1000)
-extract_func(ll_mod_1000)
-
-ll_mod2 <- lm(ratio~volume, data=area_length)
-  anova(ll_mod2)
-  summary(ll_mod2)
-  library(visreg)
-  visreg(ll_mod2)
-
-plot(areaperleaf~leaf_length, ylim=c(0,40), xlim=c(0,15),col=volume,pch=16,data=area_length, subset=volume==1000)
-abline(ll_mod)
+# area_length <- leafharvest[,c(1, 12, 15:16)]
+#   area_length$ratio <- with(area_length, areaperleaf/leaf_length)
+# 
+# ll_mod <- lm(areaperleaf~leaf_length, data=area_length)
+#   extract_func(ll_mod)
+# ll_mod_1000<- lm(areaperleaf~leaf_length, data=area_length, subset=volume==1000)
+# extract_func(ll_mod_1000)
+# 
+# ll_mod2 <- lm(ratio~volume, data=area_length)
+#   anova(ll_mod2)
+#   summary(ll_mod2)
+#   library(visreg)
+#   visreg(ll_mod2)
+# 
+# plot(areaperleaf~leaf_length, ylim=c(0,40), xlim=c(0,15),col=volume,pch=16,data=area_length, subset=volume==1000)
+# abline(ll_mod)
 ####half the volumes have a pretty bad relationship, so continue using mean leafarea and leaf count 
 
 
-#calculate leaf area trough time------------------------------------------------------------------------------
+#calculate leaf area trough time using leaf count data-------------------------------------------------------------
 leafindex <- subset(leafharvest, select = c("ID", "areaperleaf", "volume"))
 
 #format leaf count data
-leafcount$X1.21.2013   <- as.integer(leafcount$X1.21.2013)
-  leafcount <- melt(leafcount, id=c("plot", "pot"))
-  names(leafcount)[3:4] <- c("Date", "count")
[…]

### 2016-03-22 clean Scripts/leaf_interpolation.R

@@ -9,7 +9,8 @@ leafarea <- read.csv("calculated data/leafareabypot.csv")
 plotsumm <- read.csv("raw data/plot_summary.csv")
 plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
 
-#need to interpolate leaf area in m2 across all dates
+
+#need to interpolate leaf area in m2 across all dates----------------------------------------------------------------------
 leafarea1 <- subset(leafarea, select = c("Date", "ID", "canopysqm"))
 #need to interpolate leaf area in m2 across all dates
 leafnum <- subset(leafarea, select = c("Date", "ID", "count"))
@@ -24,6 +25,7 @@ datemaker <- for (i in unique(plotsumm$ID)){
                             ID = i)} 
 # row-bind everything together:
 dateseq <- do.call(rbind,datels)
+
 
 #SECOND merge leaf area and count dataset with dateseq dfr and interpolate
 leafarea_alldays <- merge(dateseq, leafarea1, by = c("Date", "ID"), all=TRUE)

### 2016-03-22 master_scripts/massmodel_optimize.R

@@ -116,11 +116,15 @@ write.csv(biomass_time, "calculated data/biomass_time.csv", row.names=FALSE)
   mass_actual$Date <- as.Date("2013-05-21")
   mass_actual$mass_adj <- with(mass_actual, mass/mass[7])
   
+  ##look at free for optimization %
+  # percdiff <- (C_stnd$modelmass - mass_actual$mass)/C_stnd$modelmass
   
-#9. plot plant carbon with optmized LMF sim vs total c gain (LA from sim cday120) and scaled
+  
+  
+#9. plot plant carbon with optmized LMF sim vs total c gain (LA from sim cday120) and scaled------------------------------
   pch3 <- c(rep(1,6), 6)
   
-  windows(7,8)
+  # windows(7,8)
   par(cex.axis=.96, cex.lab=1.2,mfrow=c(2,1),oma=c(0.1,0.1,0.1,0.1), las=1)   
   
   par(mar=c(4,5,2,2), cex.axis=0.8, las=1)
@@ -142,31 +146,10 @@ write.csv(biomass_time, "calculated data/biomass_time.csv", row.names=FALSE)
   text(.6,.01,"(b)", cex=1.2)
   legend("topright", simleg, pch=simpch,text.font=1,   inset=0.025,bty='n',cex=1.0)
   
- # dev.copy2pdf(file= "master_scripts/manuscript_figs/massmodel_totalC.pdf")  
- # dev.off() 
+ # dev.copy2pdf(file= "master_scripts/manuscript_figs/massmodel_totalC.pdf")
+ # dev.off()
 
-###calculate percent diff between model and observed biomass-------------------------------------------------------
-  
-# test <- 0
-# for(i in 1:7){
-#     test[i] <- (optmassmodel[[i]][[1,1]] - mass_actual$mass[i]) / optmassmodel[[i]][[1,1]]
-#    }
-# 
-#      mean(test[1:6])
-#      se(test[1:6])
 
-#
-# test <- (C_stnd$modelmass - mass_actual$mass)/C_stnd$modelmass
-# test2 <- C_stnd$modelmass - mass_actual$mass
-#
-# mean(test[1:6])
-# mean(test2[1:6])
-#
-# se(test[1:6])
-# se(test2[1:6])
-#
-# test3 <-  (mass_actual$mass*.5) /totalC_trt2
-#  mean(test3[1:6])
-#
-# test4 <-  (C_stnd$modelmass*.5) /totalC_trt2
-# mean(test4[1:6])
+
+
+

### 2016-03-22 master_scripts/model_start.R

@@ -50,6 +50,8 @@ rootshoot_pre_mean <- mean(seedling_pre$rootshoot)
 #mean lma and leafarea (apply to modeled leaf area)------------------------------------------------------------------
 lma <- read.csv("calculated data/leafmassarea.csv")
 lma_vol <- summaryBy(massarea ~volume, data=lma, FUN=mean, keep.names=TRUE)
+lma_campaign <- summaryBy(massarea ~campaign, data=lma, FUN=mean, keep.names=TRUE)
+
 #lma_mean <- mean(lma$massarea)
 leafarea_mean <- (mean(lma$area))/10000
 
@@ -61,11 +63,13 @@ Aleaf_agg <- read.csv("calculated data/model_runs/gCday_means_clean.csv")
 
 #leaf area interpolated----------------------------------------------------------------------------------------------
 leafarea_time <- read.csv("calculated data/LApred_volume.csv")
+###########
   ##get mean on first day for starting leaf area
-  leafarea_dayone <- mean(leafarea_time[leafarea_time$Date == "2013-01-21","canopysqm_pred"])
-
+  LA_start <- mean(leafarea_time[leafarea_time$Date == "2013-01-21","canopysqm_pred"])
+###########
+  
 #read in M regression coefs for model (calculates self shading as a linear function of leaf area)
-Mcoef <- read.csv("gC_day_model/M_leafarea_model.csv")
+Mcoef <- read.csv("calculated data/M_leafarea_model.csv")
 
 
 ####MODEL---------------------------------------------------------------------------------
@@ -73,7 +77,7 @@ LA_sp <- dlply(leafarea_time, .(volume))
 
 ##model start values
 lma_mean <- mean(lma$massarea)#average lma from harvest
-LA_start <- (mean_leafnum * leafarea_mean) #(m2)
+# LA_start <- (mean_leafnum * leafarea_mean) #(m2)
 mass_mean <- mean(seedling_pre$seedling_mass)
 Cday <- as.vector(Aleaf_agg[,2]) 
 

### 2016-03-22 yplant/M_calc_LA.R

@@ -48,14 +48,14 @@ M_eucs2<- lapply(M_eucs, function(x) merge(x, eucs_allom, by="plant_id", all=TRU
 
 #2. for each volume trt (list) run model of M vs leafN, 
 
-M_regress <- lapply(M_eucs2, function(x) lm(M ~ LA, data=x))
-
- test <- M_eucs2[[7]]
- test_lm <- lm(M ~ LA, data=test)
- windows(8,10)
- visreg(test_lm)
- dev.copy2pdf(file= "gC_day_model/model_output/Mleafarea.pdf")
- dev.off()
+# M_regress <- lapply(M_eucs2, function(x) lm(M ~ LA, data=x))
+# 
+#  test <- M_eucs2[[7]]
+#  test_lm <- lm(M ~ LA, data=test)
+#  windows(8,10)
+#  visreg(test_lm)
+#  dev.copy2pdf(file= "gC_day_model/model_output/Mleafarea.pdf")
+#  dev.off()
  
   
 #3. extract coefs for each model by trt
@@ -69,4 +69,4 @@ M_coefs2$volume <- gsub("free", 1000, M_coefs2$volume)
 #reorder
 M_coefs3 <- M_coefs2[c(6, 1:5, 7),]
 
-write.csv(M_coefs3, "gC_day_model/M_leafarea_model.csv", row.names=FALSE)
+write.csv(M_coefs3, "calcualted data/M_leafarea_model.csv", row.names=FALSE)

### 2016-03-22 manuscript/manuscript_pve.Rmd
manuscript edits, setup for newphyt

@@
   word_document:
-    reference_docx: manuscriptstyle.docx
+    reference_docx: manuscriptstyle_newphyt.docx
   pdf_document: default
@@
 
-csl: tree-physiology.csl
+csl: net_phytologist.csl
 bibliography: references2.bib
@@
 
-Interpreting limitations to plant growth requires understanding the balance between carbon (*C*) source and sink activity.
-This study used manipulations of soil volume to test how growth is coupled to physiology, *C* allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
+Interpreting limitations to plant growth requires understanding the balance between carbon (C) source and sink activity.
+This study used manipulations of soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
 We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally planted freely-rooted (free) seedlings.
-We developed a seedling growth model that utilized leaf photosynthesis rates (*A*~n~) to allocate daily *C* uptake towards mass growth of stems, leaves and roots.
+We developed a seedling growth model that utilized leaf photosynthesis rates (*A*~n~) to allocate daily C uptake towards mass growth of stems, leaves and roots.
 Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
@@
 Although belowground sink limitation resulted in a reduction of *A*~n~, the model concluded that these reductions were not large enough to explain observed growth responses.
-Thus, as *A*~n~ and growth were not tightly coordinated, an unaccounted-for pool of photosynthetic *C* resulted in seedlings with soil volume restriction.
-These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf *C* uptake.
+Thus, as *A*~n~ and growth were not tightly coordinated, an unaccounted-for pool of photosynthetic C resulted in seedlings with soil volume restriction.
+These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf C uptake.
 
@@
 
-Understanding plant growth and its relationship to *C* assimilation requires knowledge of the mass balance that must be achieved between *C* uptake and subsequent allocation to growth, storage, and respiration.
+Understanding plant growth and its relationship to C assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
 As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues and organs.
-At long enough time scales leaf photosynthesis (*A*~n~) and respiratory losses together determine net *C* balance and will correlate to plant growth.
-At shorter temporal scales, however, growth can instead be mediated by tissue *C* storage pools.
+At long enough time scales leaf photosynthesis (*A*~n~) and respiratory losses together determine net C balance and will correlate to plant growth.
+At shorter temporal scales, however, growth can instead be mediated by tissue C storage pools.
 This discrepancy has led to the current debate on how strongly plant growth is controlled by either source or sink activity.
 Consequently, plant growth cannot always be simply determined by *A*~n~, making it complex to understand and challenging to model [@fourcaud2008plant].
-Despite a wealth of studies, large uncertainties still remain regarding the coordination of *C* supply and growth of woody species.
+Despite a wealth of studies, large uncertainties still remain regarding the coordination of C supply and growth of woody species.
 
@@
 <br/>
-One approach to examine the coordination of *A*~n~ and growth is to manipulate *C* source activity.
+One approach to examine the coordination of *A*~n~ and growth is to manipulate C source activity.
 Examples include elevated CO~2~ and partial defoliation experiments.
@@
 In partial defoliation experiments, increases in *A*~n~ of the remaining foliage are commonly shown, and are attributed to reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
-However, increases in *A*~n~ in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], *C* limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant *C* gain [@ovaska1993a].
+However, increases in *A*~n~ in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
 These manipulations of C source activity demonstrate that changes in *A*~n~ do not always correspond with proportional responses of growth.
@@
 <br/>
-Alternatively, manipulation of plant tissue *C* sinks is often used to investigate the correlation between *A*~n~ and growth.
-This is because metabolic signaling networks, relaying information on *C* and *N* status of different tissues, can regulate photosynthetic activity [@paul2001sink].
+Alternatively, manipulation of plant tissue C sinks is often used to investigate the correlation between *A*~n~ and growth.
+This is because metabolic signaling networks, relaying information on C and N status of different tissues, can regulate photosynthetic activity [@paul2001sink].
 If sink inhibition of *A*~n~ occurs, a close coordination between declines in *A*~n~ and growth should be expected.
@@
 <br/>
-An alternative experimental approach is to reduce belowground *C* sink strength in tree seedlings by manipulating rooting volume, by varying the container size [@arp1991effects; @nesmith1998effect; @poorter2012pot].
+An alternative experimental approach is to reduce belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size [@arp1991effects; @nesmith1998effect; @poorter2012pot].
 Possible advantages of this approach are that it allows a large range of treatment levels, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
 Seedlings undergo many physiological and morphological changes in response to rooting volume, including changes in biomass partitioning, *A*~n~, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
-Inadequate rooting volume may decrease *C* sink strength by progressively restricting root growth in growing plants [@thomas1991root].
+Inadequate rooting volume may decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root].
 Container size studies frequently exhibit photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
@@
 [-@poorter2012pot] concluded that *A*~n~ is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used.
-This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower *C* exchange and assimilate export rates [@robbins1988effect].
-However, evidence in support for a trade-off between *C* storage and growth in trees is, to date, inconclusive [@palacio2014does].
+This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower C exchange and assimilate export rates [@robbins1988effect].
+However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].
 Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test the extent to which growth and *A*~n~ are coordinated.
@@
 We used freely-rooted seedlings as a control for the container size treatments.
-Empirical results were combined with a simple plant growth model to simulate seedling growth with a *C* mass balance approach, which was then compared to observed harvested seedling mass.
-The model used whole-plant *C* gain, scaled from instantaneous rates of leaf *A*~n~, to quantify seedling dry mass production over the 120 day experiment.
+Empirical results were combined with a simple plant growth model to simulate seedling growth with a C mass balance approach, which was then compared to observed harvested seedling mass.
+The model used whole-plant C gain, scaled from instantaneous rates of leaf *A*~n~, to quantify seedling dry mass production over the 120 day experiment.
 
@@
 
-4). Last, observed seedling mass was expected to correspond to growth model mass predicted from a simple *C* balance model taking into account measured rates of photosynthesis.
+4). Last, observed seedling mass was expected to correspond to growth model mass predicted from a simple C balance model taking into account measured rates of photosynthesis.
 
@@
 ##Leaf, root and soil chemistry
-Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of nitrogen (*N*) content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
-Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis of *N*.
-Nitrogen concentrations ([*N*]) of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of N~2~ and CO~2~).
-The percentage of *N* in the sample was calculated by comparison with certified standards.
+Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of nitrogen (N) content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
+Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis of N.
+Nitrogen concentrations ([N]) of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of N~2~ and CO~2~).
+The percentage of N in the sample was calculated by comparison with certified standards.
 Leaf $\delta$^13^C was analyzed  with an Delta V Advantage coupled to a Flash HT and Conflo IV isotope ratio mass spectrometer.
@@
 Complete methods of the TNC assay are described in @mitchell2013drought.
-TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, was calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf *N* content.
-Similarly, TNC-free leaf *N* (*N*~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC content.
+TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, was calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf N content.
+Similarly, TNC-free leaf N (N~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC content.
 
@@
 Each model run used changes in *A*~n~ and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
-Cumulative net leaf *C* gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling *C* was assumed to equal half of the final dry mass for both modeled and observed seedlings.
+Cumulative net leaf C gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling C was assumed to equal half of the final dry mass for both modeled and observed seedlings.
 
@@
 This optimized LMF was then used to constrain model runs with treatment-specific *C*~day~, while keeping tissue respiration and turnover parameters constant, to determine if changes in leaf *A*~n~ alone could predict biomass of seedlings in containers (*M*~pots~).
-Next, model sensitivity to different *C* allocation scenarios, including observed treatment-specific LMF and up-regulation of non-leaf tissue respiration by 50 % of default values (*M*~S1~ and *M*~S2~, respectively), was used to test for improvement of model biomass predictions compared to measured harvest biomass.
+Next, model sensitivity to different C allocation scenarios, including observed treatment-specific LMF and up-regulation of non-leaf tissue respiration by 50 % of default values (*M*~S1~ and *M*~S2~, respectively), was used to test for improvement of model biomass predictions compared to measured harvest biomass.
 For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment-specific mean *C*~day~ by first scaling values to the free seedling control.
@@
 ##Leaf and root chemistry
-Leaf *N*~f~ was significantly higher in free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, *P* < 0.001).
-Throughout the remainder of the experiment the smallest container volume had significantly lower leaf *N*~f~ than other soil volumes, while free seedlings maintained the highest leaf *N*~f~ (Table `r pvetab1`, *P* < 0.001).
+Leaf N~f~ was significantly higher in free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, *P* < 0.001).
+Throughout the remainder of the experiment the smallest container volume had significantly lower leaf N~f~ than other soil volumes, while free seedlings maintained the highest leaf N~f~ (Table `r pvetab1`, *P* < 0.001).
 Leaf starch content in the smallest container was ca.
@@
 Differences in leaf starch between the free seedling and the smallest container were evident during the first gas exchange campaign (*P* = 0.001).
-Root *N* was higher in free seedlings compared to seedlings in containers but only for some of the container size treatments (Table `r pvetab2`).
+Root N was higher in free seedlings compared to seedlings in containers but only for some of the container size treatments (Table `r pvetab2`).
 
@@
 Across all measurement campaigns, mean *A*~sat~ (Figure `r asatfig`) and *A*~max~ (Table `r pvetab3`) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
-The relationship between leaf starch and leaf *N* on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated with both leaf *N* content and leaf starch (both *P* < 0.001).
-We used predictions from the linear mixed effect model equation to visualize these relationships of *A*~max~ to either leaf *N* content or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
-Across all measurement campaigns and treatments *A*~max~ was higher when leaf *N* was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
-*A*~max~  was also lower when leaf starch was high as higher leaf *N* often did not coincide with high leaf starch (Figure `r achemfig`b).
+The relationship between leaf starch and leaf N on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated with both leaf N content and leaf starch (both *P* < 0.001).
+We used predictions from the linear mixed effect model equation to visualize these relationships of *A*~max~ to either leaf N content or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
+Across all measurement campaigns and treatments *A*~max~ was higher when leaf N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
+*A*~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b).
 Overall, *A*~max~ was positively correlated with final harvest biomass across all seedlings (*P* < 0.001).
@@
 Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 25.7 %; with this LMF, the model predicted mean harvest total biomass of free seedlings within 0.1 %.
-Using this optimized LMF, the modeled total biomass of seedlings for each soil volume treatment (*M*~pots~) was on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf *C* gain (Figure `r massmodelfig`a).
+Using this optimized LMF, the modeled total biomass of seedlings for each soil volume treatment (*M*~pots~) was on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf C gain (Figure `r massmodelfig`a).
 As a result, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b).
@@
 <br/>
-Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over-predictions of seedling *C* mass.
-Running the model with observed treatment-specific LMF values from the final harvest (*M*~S1~), which were each lower than the optimized LMF value (see Figure `r allocfig`a), improved model predictions of seedling C mass but still overestimated seedling total *C* by 32&pm;11.1 % (Figure `r massmodelfig2`a).
+Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over-predictions of seedling C mass.
+Running the model with observed treatment-specific LMF values from the final harvest (*M*~S1~), which were each lower than the optimized LMF value (see Figure `r allocfig`a), improved model predictions of seedling C mass but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
 Using harvest values of LMF, however, does not capture the observed increase in leaf turnover of seedlings in small containers (Figure `r allomfig`c).
 Thus, the use of harvest LMF values for seedlings in containers in *M*~S1~ likely underestimates daily C allocation to leaves over the final months of the experiment.
-Increases of 50 % in non-leaf tissue respiration (*M*~S2~) improved biomass estimates slightly but nonetheless overestimated mass *C* by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
+Increases of 50 % in non-leaf tissue respiration (*M*~S2~) improved biomass estimates slightly but nonetheless overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
 With *M*~S2~, non-tissue respiration rates would need to be increased by ca.
@@
 This study utilized a novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
-We addressed questions regarding the coordination of *A*~n~ and growth by complementing empirical results with a *C* mass balance model.
+We addressed questions regarding the coordination of *A*~n~ and growth by complementing empirical results with a C mass balance model.
 We found that reductions in leaf *A*~n~ across container sizes, when integrated across the 120 day experiment, were alone insufficient to account for observed reductions in total plant biomass production.
@@
 <br/>
-with respect to nutrient availability, reductions in *A*~n~ were positively correlated with decreases in leaf *N* and leaf *N* was considerably reduced for seedlings in containers.
-As leaf *N* reductions were detected with TNC-free leaf mass, it is likely that physical root restriction or decreased supply affected seedling *N* uptake instead of TNC dilution in leaves in the smallest containers.
-Root *N* at the end of the experiment was on average higher in free seedlings but not consistently higher than every container volume treatment.
-Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf *N* in free seedlings, but this effect is unknown.
-Combined with the fact that soil *N* declined evenly across all treatments, there was no clear mechanism present to drive changes in root *N* uptake between free seedlings and seedlings in containers.
+with respect to nutrient availability, reductions in *A*~n~ were positively correlated with decreases in leaf [N] and leaf N was considerably reduced for seedlings in containers.
+As leaf N reductions were detected with TNC-free leaf mass, it is likely that physical root restriction or decreased supply affected seedling N uptake instead of TNC dilution in leaves in the smallest containers.
+Root N at the end of the experiment was on average higher in free seedlings but not consistently higher than every container volume treatment.
+Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N in free seedlings, but this effect is unknown.
+Combined with the fact that soil N declined evenly across all treatments, there was no clear mechanism present to drive changes in root N uptake between free seedlings and seedlings in containers.
 In these already low fertility soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
-Although no clear feedback could be determined between the available soil *N* pool and decreases in leaf *N*, the effects of belowground sink limitation on *A*~n~ of seedlings in containers was evident throughout the experiment.
+Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the effects of belowground sink limitation on *A*~n~ of seedlings in containers was evident throughout the experiment.
 
@@
 <br/>
-As both rooting space and resources were finite in containers, the inability of seedlings to maintain the capacity of the belowground *C* sink resulted in the buildup of *C* assimilate in leaves.
+As both rooting space and resources were finite in containers, the inability of seedlings to maintain the capacity of the belowground C sink resulted in the buildup of C assimilate in leaves.
 The feedback inhibition of *A*~n~ from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process [@nebauer2011photosynthesis].
@@
 ##Do reductions in photosynthesis explain reductions in seedling growth?
-Our model used a simple approach to drive seedling growth with measured reductions in leaf *A*~n~ , via soil volume effects, while treating *C* use efficiency, respiration and *C* allocation as fixed processes.
+Our model used a simple approach to drive seedling growth with measured reductions in leaf *A*~n~ , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
 Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
@@
 [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth.
-These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of *C* assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
+These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
 It is possible that the overestimation of growth was due to an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *Vc*~max~, *R* and *g*~1~) make this unlikely.
@@
 Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven  plant growth models [@lacointe2000carbon].
-To address this issue, we utilized the flexibility of this model to test plausible fates of the pool of simulated non-biomass *C* unaccounted for with observed mass balance.
+To address this issue, we utilized the flexibility of this model to test plausible fates of the pool of simulated non-biomass C unaccounted for with observed mass balance.
 Similar to Lohier et al.
-[-@lohier2014explaining] we manipulated processes contributing to modeled seedling *C* mass balance, including changes to leaf *C* allocation or non-leaf tissue respiration, to quantitatively test their respective influences on model predictions.
+[-@lohier2014explaining] we manipulated processes contributing to modeled seedling C mass balance, including changes to leaf C allocation or non-leaf tissue respiration, to quantitatively test their respective influences on model predictions.
 
@@
 <br/>
-Using measured LMF from the harvest, instead of the optimized seedling control (*M*~S1~), improved biomass predictions and provided insight into how sink limitation can impact leaf *C* allocation beyond *A*~n~.
+Using measured LMF from the harvest, instead of the optimized seedling control (*M*~S1~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond *A*~n~.
 The sensitivity of the model to shifts in LMF could represent leaf loss throughout the experiment that could not be explicitly quantified in this field study.
 As TNC accumulation can lead to accelerated leaf senescence [@paul2001sink], this could explain the observed decline in total leaf area of seedlings in small containers.
-Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A*~n~ and the fate of *C* allocated to growth, respiration and *C* storage in leaves.
-It will be the interactions between these two components that will determine the total *C* gain available for plant growth.
+Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A*~n~ and the fate of C allocated to growth, respiration and C storage in leaves.
+It will be the interactions between these two components that will determine the total C gain available for plant growth.
 
@@
 <br/>
-Increasing rates of non-leaf respiration (*M*~S2~) improved biomass predictions but to a far lesser extent than changes to leaf *C* allocation.
+Increasing rates of non-leaf respiration (*M*~S2~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation.
 We also show that very large increases in non-leaf respiration rates would have been required to accurately predict observed seedling biomass.
 Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], results from *M*~S2~ highlight a lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change.
-This is noteworthy, as *C* balance is a delicate equilibrium between fluxes of *A*~n~ and respiration, partial accounting of *C* dynamics can easily lead to erroneous conclusions [@valentini2000respiration].
+This is noteworthy, as C balance is a delicate equilibrium between fluxes of *A*~n~ and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions [@valentini2000respiration].
 These results imply that using fixed rates of respiration in models likely underestimates plant responses to sink limitation.
@@
 Our combined empirical and modeling approach shows that when non-photosynthetic parameters were kept constant, changes in *A*~n~ were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
-K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A*~n~ through the demand for *C*.
-Although this may be true, our results imply that quantifying the fate of assimilated *C* into known pools of growth, storage and *C* loss are needed prior to addressing this debate.
-Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of *C* and other constituents.
-The approach used here has the flexibility to account for multiple drivers of *C* allocation and provides an avenue to address future questions regarding the impact of environmental change on plant growth.
+K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A*~n~ through the demand for C.
+Although this may be true, our results imply that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
+Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
+The approach used here has the flexibility to account for multiple drivers of C allocation and provides an avenue to address future questions regarding the impact of environmental change on plant growth.
 

### 2016-03-23 manuscript/manuscript_pve.Rmd
manuscript edits BM

@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 One approach to examine the coordination of *A*~n~ and growth is to manipulate C source activity.
@@
 In partial defoliation experiments, increases in *A*~n~ of the remaining foliage are commonly shown, and are attributed to reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
-However, increases in *A*~n~ in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
+Similar to elevated CO~2~ experiments, these increases in *A*~n~ in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
 These manipulations of C source activity demonstrate that changes in *A*~n~ do not always correspond with proportional responses of growth.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Alternatively, manipulation of plant tissue C sinks is often used to investigate the correlation between *A*~n~ and growth.
-This is because metabolic signaling networks, relaying information on C and N status of different tissues, can regulate photosynthetic activity [@paul2001sink].
+Plant metabolic signalling networks have the ability to regulate photosythetic activity, according to carbon status of different plant tissues [@paul2001sink].
 If sink inhibition of *A*~n~ occurs, a close coordination between declines in *A*~n~ and growth should be expected.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 An alternative experimental approach is to reduce belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size [@arp1991effects; @nesmith1998effect; @poorter2012pot].
-Possible advantages of this approach are that it allows a large range of treatment levels, can be easily compared to naturally planted seedlings and may mimic natural conditions as seedlings compete for space or reach bedrock.
-Seedlings undergo many physiological and morphological changes in response to rooting volume, including changes in biomass partitioning, *A*~n~, water relations, nutrient uptake and respiration [@nesmith1998effect;@poorter2012pot and references therein].
-Inadequate rooting volume may decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root].
+Inadequate rooting volume can decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root].
 Container size studies frequently exhibit photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
@@
 This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower C exchange and assimilate export rates [@robbins1988effect].
+
 However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].
-Based on these previous studies, using container size as a sink-strength manipulation can be used to empirically test the extent to which growth and *A*~n~ are coordinated.
+Whether or not down regulation of *A*~n~ and reductions of growth are quantitavely similiar has rarely been tested.
+
+Based on these previous studies, using a range of container sizes as a sink-strength manipulation can be used to empirically test the extent to which growth and *A*~n~ are coordinated.
 
 \
-<br/>
-<br/>
-<br/>
-<br/>
 This study utilizes a novel field design to investigate the coordination between growth and *A*~n~ in *Eucalyptus tereticornis* Sm.
@@
 We used freely-rooted seedlings as a control for the container size treatments.
+We tracked leaf-level gas exchange, leaf carbohydrate accumulation and seedling allometry over the course of 4 months.
 Empirical results were combined with a simple plant growth model to simulate seedling growth with a C mass balance approach, which was then compared to observed harvested seedling mass.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
-Our hypotheses were as follows: 
-\
-1).
-The manipulations of container size were expected to induce a belowground sink limitation compared to free seedlings.
-We hypothesized that declines in seedling growth would be largest in the smallest containers.
-
-2).
-As the finite pool of rooting volume and soil nutrients will decline faster in trees growing in small containers, we expected reductions in partitioning to fine root mass relative to tree size with decreasing container size.
-
-3).
-Reduced sink strength was expected to lead to accumulation of leaf non-structural carbohydrates, and a resulting down regulation of *A~n~*.
-We therefore expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume.
-
-4). Last, observed seedling mass was expected to correspond to growth model mass predicted from a simple C balance model taking into account measured rates of photosynthesis.
+Manipulations of container size were expected to induce a belowground sink limitation compared to free seedlings, resulting in growth reductions in the smallest containers.
+Specifically, reductions in biomass partitioning to root mass, relative to tree size, were predicted to occur with decreasing rooting volume and soil nutrients in container treatments.
+We also expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume, as reduced sink strength would lead to accumulation of leaf non-structural carbohydrates and down regulation of *A~n~*.
+Taking into account measured rates of photosynthesis, we expected biomass predictions from the growth model to correspond to observed seedling mass
 
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Forty-nine *Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain cohort.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Six container volumes were used ranging from 5 L to 35 L, with a 22.5 cm diameter, and lengths ranging from 15 to 100 cm.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Plants were watered weekly or when needed to maintain soil moisture at field capacity (13-15 %).
@@
 Seedlings were planted in summer (January 21^st^ 2013) and stem height, diameter at 15 cm and leaf count were measured weekly thereafter.
-Once the growth rate of individual plants had significantly declined a full biomass harvest was completed and the experiment ended (May 21^st^ 2013).
+After four months, a full biomass harvest was completed and the experiment ended (May 21^st^ 2013).
 Dry mass of leaves, stems, roots and total leaf area (LI-3100C Area Meter; LI-COR, Lincoln, NE, USA) were measured for each seedling.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Photosynthetic CO~2~ response (AC~i~) curves were measured at 25 &deg;C on a random subset of each container size (n=3) after new leaves were first produced (March 13-14^th^, 2013) and prior to the final harvest (May 14-15^th^, 2013).
-Each AC~i~ curve was started at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light (above).
-From these curves the photosynthetic parameters, *J*~max~ and *V*~cmax~, were quantified using the biochemical model of @farquhar1980biochemical and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011] using default parameters.
+Each AC~i~ curve was started at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light.
+From these curves the photosynthetic parameters, *J*~max~ and *V*~cmax~, were quantified using the biochemical model of @farquhar1980biochemical and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011].
 
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Leaf dark respiration rates (*R*) were measured on each seedling on the same dates as AC~i~ curves.
@@
 Leaves were detached and immediately stored inside foil-covered bags before water potential measurements were performed.
-$\Psi$~pd~ was measured before sunrise and $\Psi$~l~ at midday 13:00-14:30 h.
+$\Psi$~pd~ was measured before sunrise and $\Psi$~l~ at 13:00 h (&pm30 m).
 These measurements were used as a measure of static water stress on the seedlings [@sellin1999does] and to ensure that the bulk soil water availability was high enough for plants to avoid water stress as they became larger and roots filled the soil volume.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Leaf total non-structural carbohydrate (TNC) concentration was analyzed on dried and milled leaf samples using a total starch assay kit (Megazyme International, Wicklow, Ireland) and includes the starch  and soluble sugar concentrations (mg g^-1^).
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 *C*~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *R* and *g*~1~) for each treatment and meteorological data from an onsite weather station.
-*J*~max~ and *V*~cmax~ were estimated from AC~i~ curves (explained above), *R* was empirically measured and the *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values.
+Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above), *R* was empirically measured and the *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values.
 Methods of the coupled leaf gas exchange model are also described in Duursma et al [-@duursma2014peaked].
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf *A*~n~ with total plant leaf area.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 We then used this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 To test the hypothesis, a default model with mean photosynthetic parameters from the free seedlings was optimized to estimate a LMF which correctly predicted both the leaf mass and total biomass of the harvested free seedling (*M*~free~).
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Total seedling biomass at harvest was significantly different across container volumes (*P* < 0.001) and between container treatments and free seedlings (*P* < 0.001, Table `r pvetab1`).
@@
 Differences in biomass partitioning to leaves, stems and roots were not different across soil volumes after variation in seedling biomass across treatments was factored in the analysis (Figure `r allocfig`a,b).
-Across all treatments, the final harvest root:shoot biomass ratio was conserved in these seedlings which exhibited a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119]) and the ratio of leaf to fine root mass was also not different (Figure `r allocfig`c).
+Across all treatments, the final harvest root:shoot biomass ratio and  was conserved in these seedlings which exhibited a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119]) and the ratio of leaf to fine root mass was also not different (Figure `r allocfig`c).
 
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table `r pvetab2`, *P* = 0.009).
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Both *J*~max~ and *V*~cmax~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`).
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 MPa across all seedlings, respectively.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over-predictions of seedling C mass.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Decreases in *A*~sat~ occurred at the same time as reductions in height and diameter of seedlings in containers.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 With high rates of *g*~s~, non-limiting leaf water potential ($\Psi$~pd~), and consistent leaf $\delta$^13^C across soil volume treatments, there was little evidence that water stress caused the reduction in *A*~n~.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 with respect to nutrient availability, reductions in *A*~n~ were positively correlated with decreases in leaf [N] and leaf N was considerably reduced for seedlings in containers.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 As both rooting space and resources were finite in containers, the inability of seedlings to maintain the capacity of the belowground C sink resulted in the buildup of C assimilate in leaves.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 The lack of detected shifts in partitioning to fine roots provides evidence against an optimal foraging strategy for seedlings in containers.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Using measured LMF from the harvest, instead of the optimized seedling control (*M*~S1~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond *A*~n~.
@@
 \
-<br/>
-<br/>
-<br/>
-<br/>
 Increasing rates of non-leaf respiration (*M*~S2~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation.

### 2016-03-24 manuscript/manuscript_pve.Rmd
manuscript edits BM, errors to make rmd run fixed

@@
 
-csl: net_phytologist.csl
+csl: new-phytologist.csl
 bibliography: references2.bib
@@
 We developed a simple seedling growth model that utilized leaf *A*~n~ rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
-The model begins with mean initial tissue component biomass (leaf~i~, stem~i~ and root~i~) and a starting leaf area (LA~i~) measured prior to planting.
+The model begins with mean initial tissue component biomass (leaf~0,i~, stem~0,i~ and root~0,i~) and a starting leaf area (L~0,i~) measured prior to planting.
 The initial biomass of roots was divided evenly between fine and coarse roots.
@@
 (1)
-$$P_i = \frac{L~C_\mathrm{day'i}~\sigma_\mathrm{s} - R}{\epsilon_\mathrm{c}}$$
+$$P_i = \frac{L~C_\mathrm{day'i}~\sigma - R}{\epsilon}$$
 
-where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$~s~ is a self-shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
+where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), $\epsilon$ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
 Total respiration was calculated as
@@
 \
-It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf *A*~n~ with total plant leaf area.
+It was further necessary to calculate a self-shading parameter ($\sigma$) when scaling leaf *A*~n~ with total plant leaf area.
 This was accomplished by utilizing 61 previously digitized *Eucalyptus* seedlings, covering 5 total species which include *E.
@@
 Using the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*~n~, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
-The ratio of total *A*~n~ with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments.
-Next, the linear relationship between $\sigma$~s~ and total leaf area was determined across digitized seedlings, within each treatment.
-For the growth model, $\sigma$~s~ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to C~day,i~.
+The ratio of total *A*~n~ with self-shading to horizontal leaf was then used to calculate $\sigma$ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments.
+Next, the linear relationship between $\sigma$ and total leaf area was determined across digitized seedlings, within each treatment.
+For the growth model, $\sigma$ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to C~day,i~.
 All default parameters used in model simulations are reported in Table `r pvetabS`.
@@
 Differences in biomass partitioning to leaves, stems and roots were not different across soil volumes after variation in seedling biomass across treatments was factored in the analysis (Figure `r allocfig`a,b).
-Across all treatments, the final harvest root:shoot biomass ratio and  was conserved in these seedlings which exhibited a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119]) and the ratio of leaf to fine root mass was also not different (Figure `r allocfig`c).
+The final harvest root:shoot biomass ratio and  was conserved across all treatments, with a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119]).
+The ratio of leaf to fine root mass was also not different between treatments (Figure `r allocfig`c).
 
@@
 \
-Decreases in *A*~sat~ occurred at the same time as reductions in height and diameter of seedlings in containers.
-This observation initially suggests a strong link between growth and an apparent down regulation of *A*~n~.
+Decreases in *A*~sat~ occurred simultaneously with reductions growth of seedlings in containers. This observation initially suggests 
+that sink limitation may be driving the down regulation of photosynthesis, and thus growth.
 However, there are several possible mechanisms that can explain reduced *A*~n~ in small containers including reduced nutrient content or water availability, or reduced sink strength [@poorter2012pot].
@@
 Here, declines in *A*~max~ were correlated with higher starch content throughout the experiment.
-This agrees with a study on a deciduous conifer by Equiza et al.
+These results agree with a study on a deciduous conifer by Equiza et al.
 [-@equiza2006photosynthetic] where photosynthetic downregulation from reduced sink strength was correlated with starch content.
@@
 In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, outside of ontogenetic drift (Figure `r allocfig`a,b).
-This is a surprising result as shifts in partitioning have been noted specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein].
+This result is unexpected as shifts in partitioning have been noted specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein].
 Surprisingly, a constant ratio of fine root mass to leaf mass was observed across all treatments suggesting a functional partitioning response to optimize resource gain did not occur.
@@
 The lack of detected shifts in partitioning to fine roots provides evidence against an optimal foraging strategy for seedlings in containers.
-This could be because lateral root development is affected by inanimate obstacles and avoiding growth towards container walls could improve the efficiency of resource allocation [@falik2005root].
-The sensitivity of roots to their own exudates near obstructions may prevent further growth [@semchenko2008foraging].
+It is instead possible that lateral root development is affected by inanimate obstacles and avoiding growth towards container walls may improve resource gain [@falik2005root].
+The sensitivity of roots to their own exudates near obstructions may also prevent further growth [@semchenko2008foraging].
 Here, we found that FRLD was highest in smallest containers suggesting that root restriction likely occurred as simple function of available rooting space.

### 2016-03-24 master_scripts/massmodel_optimize.R

@@ -1,4 +1,4 @@
-source("functions and packages/startscripts.R")
+# source("functions and packages/startscripts.R")
 
 source("master_scripts/model_start.R")
 source("master_scripts/massmodel.R")
@@ -124,7 +124,7 @@ write.csv(biomass_time, "calculated data/biomass_time.csv", row.names=FALSE)
 #9. plot plant carbon with optmized LMF sim vs total c gain (LA from sim cday120) and scaled------------------------------
   pch3 <- c(rep(1,6), 6)
 
-  windows(7,8)
+  # windows(7,8)
   par(cex.axis=.96, cex.lab=1.2,mfrow=c(2,1),oma=c(0.1,0.1,0.1,0.1), las=1)   
   
   par(mar=c(4,5,2,2), cex.axis=0.8, las=1)

### 2016-03-24 master_scripts/massmodel_optimize_scenarios.R

@@ -1,4 +1,4 @@
-source("functions and packages/startscripts.R")
+# source("functions and packages/startscripts.R")
 
 source("master_scripts/model_start.R")
 source("master_scripts/massmodel.R")
@@ -66,15 +66,6 @@ for(i in 1:7){
                                                    leaffrac=opt_lmf,M_slope=Mcoef$b[i], M_intercept= Mcoef$intercept[i],
                                                    returnwhat="lastval"))
 }  
-##return all values
-optmassmodel2<- list()
-for(i in 1:7){
-  optmassmodel2[[i]] <- data.frame(productionmodel(gCday=c120_trt[[i]][[1]], 
-                                                    lma=lma_trt[i],frfrac=opt_ofrac, crfrac=opt_ofrac, stemfrac=opt_ofrac,
-                                                    leaffrac=opt_lmf,M_slope=Mcoef$b[i], M_intercept= Mcoef$intercept[i],
-                                                    returnwhat="all"))
-}  
-
 
 #8. Test scenarios--------------------------------------------------------------------------------------------------------
 
@@ -123,7 +114,7 @@ for(i in 1:7){
   
   ##add actual mass and Cday scaled
   ##mean daily carbon gain scaled
-  C_stnd <- read.csv("calculated data/model_runs/gCday_means_clean.csv")
+  C_stnd <- read.csv("calculated data/Aleaf_model/gCday_means_clean.csv")
     C_stnd$C_stnd_free <- with(C_stnd, carbon_day/carbon_day[7])
     
     ##modelled biomass scaled

### 2016-03-29 manuscript/manuscript_pve.Rmd
manuscript edits from BM
style changes for New Phyt

@@
 \
-COURTNEY E. CAMPANY^1,2^, BELINDA MEDLYN^1^ and REMKO A. DUURSMA^1^
+COURTNEY E. CAMPANY^1^, BELINDA MEDLYN^1^ and REMKO A. DUURSMA^1^
 
@@
 ^1^ Hawkesbury Institute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW, Australia
-\
-^2^ Corresponding author (courtneycampany@gmail.com)
 
@@
 \
-RUNNING HEAD: SINK LIMITATION ALTERS SEEDLING CARBON BALANCE
+Corresponding author: CE Campany, email: courtneycampany@gmail.com, telephone: +61 02 4570 1421, fax: +61 02 4570 1103
+
+\
+Word counts
+Main text:
+Introduction:
+Materials and methods:
+Results:
+Discussion:
+Acknowledgements:
+7 figures (6 color), 3 tables
+Supporting information: 1 table
 
@@
 
-#Abstract
+#Summary
+- Interpreting limitations to plant growth requires accounting of carbon (C) mass balance between uptake and allocation.
+This study manipulated soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
 
-Interpreting limitations to plant growth requires understanding the balance between carbon (C) source and sink activity.
-This study used manipulations of soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
-We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally planted freely-rooted (free) seedlings.
-We developed a seedling growth model that utilized leaf photosynthesis rates (*A*~n~) to allocate daily C uptake towards mass growth of stems, leaves and roots.
-Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings.
-It was hypothesized that the soil volume effect would be largest in the smallest containers, negatively impacting mass partitioning belowground.
-An accumulation of leaf non-structural carbohydrates, resulting from reduced belowground sink strength, was expected to correlate to reductions in photosynthetic capacity.
-We observed a negative effect of container volume on aboveground growth soon after the experiment started.
-Although growth was consistently different across soil volumes, dry mass partitioning to leaves, stems and roots was unchanged after 120 days.
-Photosynthetic capacity was significantly reduced in containers compared to free seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
-We then asked whether the observed reductions in *A*~n~ explained the observed differences in seedling biomass.
-Although belowground sink limitation resulted in a reduction of *A*~n~, the model concluded that these reductions were not large enough to explain observed growth responses.
-Thus, as *A*~n~ and growth were not tightly coordinated, an unaccounted-for pool of photosynthetic C resulted in seedlings with soil volume restriction.
+- Seedlings were grown in a range of container sizes and containers were planted flush to the soil alongside freely-rooted (free) seedlings.
+We developed a growth model that utilized net leaf photosynthesis rates (*A*~n~) to allocate daily C uptake towards mass growth of stems, leaves and roots.
+
+- Container volume negatively affected aboveground growth throughout the experiment, yet, mass partitioning to leaves, stems and roots was unchanged after 120 days.
+Photosynthetic capacity was significantly reduced in containered seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
+Although belowground sink limitation reduced *A*~n~, the model concluded that these reductions were not large enough to explain observed growth responses.
+
+- As *A*~n~ and growth were not tightly coordinated, an unaccounted-for pool of photosynthetic C resulted in seedlings with soil volume restriction.
 These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf C uptake.
@@
 (1)
-$$P_i = \frac{L~C_\mathrm{day'i}~\sigma - R}{\epsilon}$$
+$$P_i = \frac{L_i~C_\mathrm{day'i}~\sigma - R_i}{\epsilon}$$
 
-where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), $\epsilon$ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
+where *L*~i~ is modelled total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), $\epsilon$ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R*~i~ is the mass based total respiration of all tissue components (g C d^-1^).
 Total respiration was calculated as
@@
 (2)
-$$R = \Sigma(R_\mathrm{c}~M_\mathrm{c})$$
-where *R*~c~ is published or local tissue respiration rates of fine roots, coarse roots or stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and *M*~c~ is the standing biomass of each component (g).
-Leaf respiration is represented in the calculation of *C*~day~ (described below).
-The change in individual component biomass (*M*~c~), here solved on a daily time step, is given by
+$$R_i = \Sigma(R_\mathrm{c}~M_\mathrm{c,i})$$
+where *R*~c~ is published or measured tissue respiration rates of each woody tissue component, including fine roots, coarse roots and stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and *M*~c,i~ is the modelled standing biomass of each component (g).
+Leaf respiration is included in the calculation of *C*~day~ (described below).
+The change in individual component biomass (*M*~c,i~), here solved on a daily time step, is given by
 
@@
 (3)
-$$\frac{dM_\mathrm{c}}{dt} = A_\mathrm{c}~P_\mathrm{i}~-~(\Lambda_\mathrm{c}~M_\mathrm{c})$$
-where *A*~c~ is the component specific biomass partitioning to whole plant biomass (%) and $\Lambda$~c~ is component specific turnover rate (yr^-1^).
-Because we did not observe branch turnover, $\Lambda$~stem~ was assumed to equal 0.
+$$\frac{dM_\mathrm{c}}{dt} = \theta_\mathrm{c}~P_\mathrm{i}~-~(\Lambda_\mathrm{c}~M_\mathrm{c,i})$$
+where $\theta$~c~ is the component specific biomass partitioning to whole plant biomass (%) and $\Lambda$~c~ is component specific turnover rate (yr^-1^).
+Because we did not observe branch turnover, $\Lambda$ of stems was assumed to equal 0.
 Total seedling biomass, per time step, was then equal to the sum of all biomass components; leaves, stems, fine roots and coarse roots.
@@
 Next, the linear relationship between $\sigma$ and total leaf area was determined across digitized seedlings, within each treatment.
-For the growth model, $\sigma$ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to C~day,i~.
+For the growth model, $\sigma$ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to *C*~day,i~.
 All default parameters used in model simulations are reported in Table `r pvetabS`.
@@
 We then used this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.
-Each model run used changes in *A*~n~ and leaf mass fraction (LMF), with values of stem and root respiration rates, to generate total seedling mass and leaf area after 120 days.
-Cumulative net leaf C gain for each treatment was equal to the sum of each value of C~day,i~ over 120 days and final seedling C was assumed to equal half of the final dry mass for both modeled and observed seedlings.
-
-\
-To test the hypothesis, a default model with mean photosynthetic parameters from the free seedlings was optimized to estimate a LMF which correctly predicted both the leaf mass and total biomass of the harvested free seedling (*M*~free~).
-This optimized LMF was then used to constrain model runs with treatment-specific *C*~day~, while keeping tissue respiration and turnover parameters constant, to determine if changes in leaf *A*~n~ alone could predict biomass of seedlings in containers (*M*~pots~).
-Next, model sensitivity to different C allocation scenarios, including observed treatment-specific LMF and up-regulation of non-leaf tissue respiration by 50 % of default values (*M*~S1~ and *M*~S2~, respectively), was used to test for improvement of model biomass predictions compared to measured harvest biomass.
-For all cases, seedling biomass production was compared between model output and harvested seedlings with treatment-specific mean *C*~day~ by first scaling values to the free seedling control.
+First, a default model with mean photosynthetic parameters from the free seedlings was optimized to estimate a LMF which correctly predicted both the leaf mass and total biomass of the harvested free seedling (*M*~free~).
+This optimized LMF was then used to constrain model runs with treatment-specific *C*~day~, while keeping woody tissue respiration and tissue turnover parameters constant, to determine if changes in leaf *A*~n~ alone could predict biomass of seedlings in containers (*M*~pots~).
+Cumulative net leaf C gain for each treatment was equal to the sum of each value of *C*~day,i~ over 120 days and final seedling C was assumed to equal half of the final dry mass for both modeled and observed seedlings.
+Seedling biomass production was compared between model output and harvested seedlings with treatment-specific mean *C*~day~ by first scaling values to the free seedling control.
 

### 2016-04-01 manuscript/manuscript_pve.Rmd
automated package installing if not installed already

@@
 opts_knit$set(root.dir = '../')
+```
+
+```{r install packages, echo=FALSE, message=FALSE, warning=FALSE,results="hide"}
+#install packages if not already installed
+.packages = c("RColorBrewer", "doBy", "sciplot", "plyr","nlme", "multcomp", "plantecophys", "scales","smatr",
+                           "lme4", "lmerTest", "broom", "reporttools", "visreg")
+
+# Install CRAN packages (if not already installed)
+.inst <- .packages %in% installed.packages()
+if(length(.packages[!.inst]) > 0) install.packages(.packages[!.inst], repos = "http://cran.at.r-project.org")
+
+# Load packages into session
+lapply(.packages, library, character.only=TRUE)
+
 ```
@@
 [-@poorter2012pot] concluded that *A*~n~ is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used.
-This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower C exchange and assimilate export rates [@robbins1988effect].
-
+This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower assimilation rates [@robbins1988effect].
 However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].
-Whether or not down regulation of *A*~n~ and reductions of growth are quantitavely similiar has rarely been tested.
-
-Based on these previous studies, using a range of container sizes as a sink-strength manipulation can be used to empirically test the extent to which growth and *A*~n~ are coordinated.
+Whether down regulation of *A*~n~ and subsequent reductions of growth are quantitavely similiar has rarely been tested.
+Based on these previous studies, using a range of container sizes as a sink-strength manipulation provdies a way to empirically test the extent to which growth and *A*~n~ are coordinated.
 
@@
 (1)
-$$P_i = \frac{L_i~C_\mathrm{day'i}~\sigma - R_i}{\epsilon}$$
+$$P_i(t) = \frac{L_i(t-1)~Cday_i}~\sigma - R_i}{\epsilon}$$
 
 where *L*~i~ is modelled total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), $\epsilon$ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R*~i~ is the mass based total respiration of all tissue components (g C d^-1^).
+Here, i represents model runs for each experimental treatment (1:7).
 Total respiration was calculated as
@@
 (2)
-$$R_i = \Sigma(R_\mathrm{c}~M_\mathrm{c,i})$$
+$$R_i(t) = \Sigma_{c=1}^{3}(R_\mathrm{c}~M_\mathrm{c,i})$$
+
 where *R*~c~ is published or measured tissue respiration rates of each woody tissue component, including fine roots, coarse roots and stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and *M*~c,i~ is the modelled standing biomass of each component (g).

### 2016-04-01 master_scripts/Amax_TNC_N_plotting2.R

@@ -1,7 +1,7 @@
 #this script is for sourcing the Amax vs TNC and N plots into master
 source("functions and packages/startscripts.R")
-require(lme4)
-require(lmerTest)
+library(lme4)
+library(lmerTest)
 library(effects)
 
 

### 2016-04-01 manuscript/manuscript_pve.Rmd
manuscript edits BM

@@
 Word counts
+\
 Main text:
+\
 Introduction:
+\
 Materials and methods:
+\
 Results:
+\
 Discussion:
+\
 Acknowledgements:
+\
 7 figures (6 color), 3 tables
+\
 Supporting information: 1 table
@@
 (1)
-$$P_i(t) = \frac{L_i(t-1)~Cday_i}~\sigma - R_i}{\epsilon}$$
+$$P_i(t) = \frac{L_\mathrm{i}~Cday_\mathrm{i}~\sigma - R_\mathrm{i}}{\epsilon}$$
 
-where *L*~i~ is modelled total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), $\epsilon$ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R*~i~ is the mass based total respiration of all tissue components (g C d^-1^).
+where *L*~i~ is modelled total plant leaf area (m^2^), *Cday*~i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), $\epsilon$ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R*~i~ is the mass based total respiration of all tissue components (g C d^-1^).
 Here, i represents model runs for each experimental treatment (1:7).
@@
 (2)
-$$R_i(t) = \Sigma_{c=1}^{3}(R_\mathrm{c}~M_\mathrm{c,i})$$
+$$R_i(t) = \Sigma_{c=1}^{3}(R_\mathrm{c}~M_\mathrm{c,i}(t))$$
 
-where *R*~c~ is published or measured tissue respiration rates of each woody tissue component, including fine roots, coarse roots and stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and *M*~c,i~ is the modelled standing biomass of each component (g).
-Leaf respiration is included in the calculation of *C*~day~ (described below).
+where *R*~c~ is published or measured tissue respiration rates of different woody tissue components (Table `r pvetabS`, g C g mass^-1^ d^-1^) and *M*~c,i~ is the modelled standing biomass for each component (g).
+Here, c represents fine roots, coarse roots or stems.
+Leaf respiration is included in the calculation of *Cday* (described below).
 The change in individual component biomass (*M*~c,i~), here solved on a daily time step, is given by
@@
 (3)
-$$\frac{dM_\mathrm{c}}{dt} = \theta_\mathrm{c}~P_\mathrm{i}~-~(\Lambda_\mathrm{c}~M_\mathrm{c,i})$$
+$$\frac{dM_\mathrm{c}}{dt} = \theta_\mathrm{c}~P_\mathrm{i}(t)~-~(\Lambda_\mathrm{c}~M_\mathrm{c,i})$$
+
 where $\theta$~c~ is the component specific biomass partitioning to whole plant biomass (%) and $\Lambda$~c~ is component specific turnover rate (yr^-1^).
@@
 \
-*C*~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *R* and *g*~1~) for each treatment and meteorological data from an onsite weather station.
+*Cday* was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *R* and *g*~1~) for each treatment and meteorological data from an onsite weather station.
 Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above), *R* was empirically measured and the *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values.
@@
 Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A*~n~ rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
-*C*~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
-This resulted in 120 unique values of *C*~day~ for each soil volume treatment, one value for each day of the experiment.
-Thus, each daily time step for model runs included a value of *C*~day~ that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
+*Cday* was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
+This resulted in 120 unique values of *Cday* for each soil volume treatment, one value for each day of the experiment.
+Thus, each daily time step for model runs included a value of *Cday* that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
 
@@
 Next, the linear relationship between $\sigma$ and total leaf area was determined across digitized seedlings, within each treatment.
-For the growth model, $\sigma$ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to *C*~day,i~.
+For the growth model, $\sigma$ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to *Cday*~i~.
 All default parameters used in model simulations are reported in Table `r pvetabS`.
@@
 We then used this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.
-First, a default model with mean photosynthetic parameters from the free seedlings was optimized to estimate a LMF which correctly predicted both the leaf mass and total biomass of the harvested free seedling (*M*~free~).
-This optimized LMF was then used to constrain model runs with treatment-specific *C*~day~, while keeping woody tissue respiration and tissue turnover parameters constant, to determine if changes in leaf *A*~n~ alone could predict biomass of seedlings in containers (*M*~pots~).
-Cumulative net leaf C gain for each treatment was equal to the sum of each value of *C*~day,i~ over 120 days and final seedling C was assumed to equal half of the final dry mass for both modeled and observed seedlings.
-Seedling biomass production was compared between model output and harvested seedlings with treatment-specific mean *C*~day~ by first scaling values to the free seedling control.
+First, a default model with mean photosynthetic parameters from the free seedlings was optimized to estimate a leaf mass fraction (LMF) which correctly predicted both the leaf mass and total biomass of the harvested free seedling (*M*~free~).
+This optimized LMF was then used to constrain model runs with treatment-specific *Cday*, while keeping woody tissue respiration and tissue turnover parameters constant, to determine if changes in leaf *A*~n~ alone could predict biomass of seedlings in containers (*M*~pots~).
+Cumulative net leaf C gain for each treatment was equal to the sum of each value of *Cday*~i~ over 120 days and final seedling C was assumed to equal half of the final dry mass for both modeled and observed seedlings.
+Seedling biomass production was compared between model output and harvested seedlings with treatment-specific mean *Cday* by first scaling values to the free seedling control.
 
@@
 # Acknowledgements
-We thank Burhan Amiji for his outstanding technical assistance. We would like to thank the many Hawkesbury Institute for the Environment staff and students who helped during the experimental harvest.
+We thank Burhan Amiji for his outstanding technical assistance.
+We would like to thank the many Hawkesbury Institute for the Environment staff and students who helped during the experimental harvest.
+This research was funded by a PhD Scholarship drom the Hawkesbury Institute for the Environment (Western Sydney University).
 

### 2016-04-07 manuscript/manuscript_pve.Rmd
edits from BM
added newphyt cites

@@
 \
-with respect to nutrient availability, reductions in *A*~n~ were positively correlated with decreases in leaf [N] and leaf N was considerably reduced for seedlings in containers.
-As leaf N reductions were detected with TNC-free leaf mass, it is likely that physical root restriction or decreased supply affected seedling N uptake instead of TNC dilution in leaves in the smallest containers.
-Root N at the end of the experiment was on average higher in free seedlings but not consistently higher than every container volume treatment.
+With respect to nutrient availability, reductions in *A*~n~ were positively correlated with decreases in leaf [N] and leaf N was considerably reduced for seedlings in containers.
+Since reductions in leaf N were detected with TNC-free leaf mass, it is likely that nutrient uptake was affected in the smallest containers instead of TNC dilution in leaves.
+It it possible that physical root restriction or decreased supply reduced seedling N uptake in small containers.
+Although root N was on average higher in free seedlings at the end of the experiment, it was not consistently higher than the smallest container volume treatment.
 Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N in free seedlings, but this effect is unknown.
-Combined with the fact that soil N declined evenly across all treatments, there was no clear mechanism present to drive changes in root N uptake between free seedlings and seedlings in containers.
+Soil N also declined evenly across all treatments, providing no clear evidence for decreased supply between free seedlings and seedlings in containers.
 In these already low fertility soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.

### 2016-04-08 manuscript/manuscript_pve.Rmd
deleted unused files
manuscript edits from BM

new CUE figures

added new phyt cites

@@
     number_sections: yes
-
 csl: new-phytologist.csl
@@
 Understanding plant growth and its relationship to C assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
-As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues and organs.
+As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate from source leaves among different tissues and organs.
 At long enough time scales leaf photosynthesis (*A*~n~) and respiratory losses together determine net C balance and will correlate to plant growth.
@@
 We would like to thank the many Hawkesbury Institute for the Environment staff and students who helped during the experimental harvest.
-This research was funded by a PhD Scholarship drom the Hawkesbury Institute for the Environment (Western Sydney University).
+This research was funded by a PhD Scholarship from the Hawkesbury Institute for the Environment (Western Sydney University).
 

### 2016-04-08 functions and packages/stats packages.R

@@ -1,13 +1,0 @@
-#packages for stats
-require(lme4)
-require(nlme)
-require(car)
-library(effects)
-library(doBy)
-library(plyr)
-library(plotrix)
-require(visreg)
-require(effects)
-#special plotting
-library(scatterplot3d)
-library(rgl)

### 2016-04-08 functions and packages/unused list.R

@@ -1,15 +1,0 @@
-volume <- unique(plotsumm$volume)
-
-#function to add volume to met data for each campaign
-met_volume<- function(vol,cam){
-  merge(subset(eucpve_met,campaign==cam), subset(ps_param,campaign==cam&volume==vol))
-}
-
-lista <- list()
-listb <- list()
-for (i in 1:length(volume)){
-  lista[[i]] <- met_volume(vol=volume[i],cam="a")
-  lista[[i]] <- met_volume(vol=volume[i],cam="b") 
-}
-
-model_parameters <- rbind.fill(rbind.fill(testa),rbind.fill(testb))

### 2016-04-08 newbestway.R

@@ -2,16 +2,14 @@ source("functions and packages/plot objects.R")
 library(doBy)
 
 ### this replaces the model scenarios
-### calulate total net daily carbon gain (modelled)
-### combine with emprical estimates of daiil leaf area
-### compare to harvest mass, the difference represents fraction to unmeasured pools
+### calulate total net daily carbon gain (modelled using gross, net and shading)
+### compare to harvest mass, calculate CUE
 
-##read data
+##read data-----------------------------------------------------------------------------------------------------------------
 finalmass <- read.csv("calculated data/harvest_mass_means.csv")
 
 la_pred <- read.csv("Calculated data/LApred_volume.csv")
   names(la_pred)[3] <- "LA"
-  
   
 Cday_net <- read.csv("calculated data/Aleaf_model/cday_120_clean.csv")
 Cday_gross <- read.csv("calculated data/Aleaf_model/cday_120_clean_gross.csv")
@@ -21,18 +19,18 @@ sigma <- read.csv("calculated data/M_leafarea_model.csv")
 
 
 #Calculate total net daily carbon day per tree with Cday and real leaf area------------------------------------------------
-  dailyC <- merge(la_pred,Cday_net)
+  dailyCnet <- merge(la_pred,Cday_net)
   ##this needs to include self shadeing (M as a linear function of leaf area)
-  dailyC <- merge(dailyC, sigma[, c(2,3,5)], by="volume")
-    dailyC$M <- with(dailyC, b*LA+intercept)
+  dailyCnet <- merge(dailyCnet, sigma[, c(2,3,5)], by="volume")
+  dailyCnet$M <- with(dailyCnet, b*LA+intercept)
     #calculate total daily C gain with self shading
-    dailyC$tdcg <- with(dailyC, LA * carbon_day * M)
+  dailyCnet$tdcg <- with(dailyCnet, LA * carbon_day * M)
 
 #Calculate total seedling C gain over experiment (120d)
-  plantC <- summaryBy(tdcg ~ volume, FUN=sum, data=dailyC)
+  plantCnet <- summaryBy(tdcg ~ volume, FUN=sum, data=dailyCnet)
 
 #Compare estimated Daily C gain with final mass from harvest
-  harvestC <- merge(finalmass, plantC)
+  harvestC <- merge(finalmass, plantCnet)
[…]

### 2016-04-08 unused scripts/massmodel2.R

@@ -1,86 +1,0 @@
-
-###this model has self shading (M)
-
-
-# model as a function
-productionmodel2 <- function(leaffrac = .25,
-                            crfrac = .25,
-                            frfrac = .25,
-                            stemfrac=.25,
-                            gCday = 1,
-                            conversionEfficiency = 0.65,
-                            fr_resp = .010368, #gC/gFroot day Marsden et al
-                            cr_resp = .00124, #gC/gCroot day
-                            wd_resp = .001877, #gc/gwood day Drake with 1.86 q10 to 20C
-                            turnover = 1/365, #production/standing crop
-                            numdays=120,
-                            lma = 97.5,
-                            M_slope = -.02,
-                            M_intercept = .9,
-                            returnwhat=c("lastval","all")
-){
-  
-  
-  sumf <- leaffrac + crfrac + frfrac + stemfrac
-  leaffrac <- leaffrac / sumf
-  crfrac <- crfrac / sumf
-  frfrac <- frfrac / sumf
-  stemfrac <- stemfrac / sumf
-  
-  returnwhat <- match.arg(returnwhat)
-  
-  leafarea <- vector()
-  leafarea[1] <- LA_start
-  
-  biomass <- vector()
-  biomass[1] <- mass_mean
-  
-  frootmass <- vector()
-  frootmass[1] <- pre_root*.5
-  
-  crootmass <- vector()
-  crootmass[1] <- pre_root*.5
-  
-  stemmass <- vector()
-  stemmass[1] <- pre_stem
-  
-  leafmass <- vector()
-  leafmass[1] <- LA_start*lma
-  
-  LMF <- vector()
-  LMF[1] <- (LA_start*lma)/mass_mean
-  
-  
-  if(length(gCday) == 1)gCday <- rep(gCday,numdays)
-  if(length(gCday) < numdays)stop("Need at least ",numdays," photosynthesis values.")
-  
-  #run model simulation------------------------------------------------------------------
-  for (i in 2:numdays) {
-    M <- M_slope*leafarea[i-1] + M_intercept
-    
-    grossbiomassprod <- leafarea[i-1] * ((gCday[i]*M)/conversionEfficiency) 
-    
[…]

### 2016-04-08 unused scripts/massmodel_noshading.R

@@ -1,82 +1,0 @@
-
-####this model has no self shading
-
-
-# model as a function
-productionmodel <- function(leaffrac = .25,
-                            crfrac = .25,
-                            frfrac = .25,
-                            stemfrac=.25,
-                            gCday = 1,
-                            conversionEfficiency = 0.65,
-                            fr_resp = .010368, #gC/gFroot day Marsden et al
-                            cr_resp = .00124, #gC/gCroot day
-                            wd_resp = .001877, #gc/gwood day Drake with 1.86 q10 to 20C
-                            turnover = 1/365, #production/standing crop
-                            numdays=120,
-                            lma = 97.5,
-                            returnwhat=c("lastval","all")
-){
-  
-  
-  sumf <- leaffrac + crfrac + frfrac + stemfrac
-  leaffrac <- leaffrac / sumf
-  crfrac <- crfrac / sumf
-  frfrac <- frfrac / sumf
-  stemfrac <- stemfrac / sumf
-  
-  returnwhat <- match.arg(returnwhat)
-  
-  leafarea <- vector()
-  leafarea[1] <- LA_start
-  
-  biomass <- vector()
-  biomass[1] <- mass_mean
-  
-  frootmass <- vector()
-  frootmass[1] <- pre_root*.5
-  
-  crootmass <- vector()
-  crootmass[1] <- pre_root*.5
-  
-  stemmass <- vector()
-  stemmass[1] <- pre_stem
-  
-  leafmass <- vector()
-  leafmass[1] <- LA_start*lma
-  
-  LMF <- vector()
-  LMF[1] <- (LA_start*lma)/mass_mean
-  
-  
-  if(length(gCday) == 1)gCday <- rep(gCday,numdays)
-  if(length(gCday) < numdays)stop("Need at least ",numdays," photosynthesis values.")
-  
-  #run model simulation------------------------------------------------------------------
-  for (i in 2:numdays) {
-    grossbiomassprod <- leafarea[i-1] * gCday[i]/conversionEfficiency  # gc day-1
-    
-    netbiomassprod <- grossbiomassprod - fr_resp*frootmass[i-1] - cr_resp*crootmass[i-1] - wd_resp*frootmass[i-1]
-    
-    #fractions,stems and wood need respiration
[…]

### 2016-04-08 manuscript/manuscript_pve.Rmd
moved files out of master (model scenarios).  BM edits

@@
 massmodelfig <- "6"
-massmodelfig2 <- "S1"
 
@@
 Understanding plant growth and its relationship to C assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
-As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate from source leaves among different tissues and organs.
-At long enough time scales leaf photosynthesis (*A*~n~) and respiratory losses together determine net C balance and will correlate to plant growth.
-At shorter temporal scales, however, growth can instead be mediated by tissue C storage pools.
+As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth is driven by the allocation of photosynthate from source leaves among these different tissues sinks.
+At long enough time scales leaf photosynthesis (*A*~n~) and respiratory losses together determine net C balance and plant growth.
+At shorter temporal scales growth can instead be mediated by tissue C storage pools [@chapin1990ecology], disrupting the coordination between *A*~n~ and growth.
 This discrepancy has led to the current debate on how strongly plant growth is controlled by either source or sink activity.
-Consequently, plant growth cannot always be simply determined by *A*~n~, making it complex to understand and challenging to model [@fourcaud2008plant].
+
+As plant growth cannot simply be determined by *A*~n~, growth models must take into account several simultanesous processes affecting the C balance at any given time [@fourcaud2008plant].
+
 Despite a wealth of studies, large uncertainties still remain regarding the coordination of C supply and growth of woody species.
+*when growth is limited* interpretations of how the C balance reponds.......
 
@@
 We developed a simple seedling growth model that utilized leaf *A*~n~ rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
-The model begins with mean initial tissue component biomass (leaf~0,i~, stem~0,i~ and root~0,i~) and a starting leaf area (L~0,i~) measured prior to planting.
+The model begins with mean initial tissue component biomass (leaf~0, stem~0~ and root~0~) and a starting leaf area (L~0~) measured prior to planting.
 The initial biomass of roots was divided evenly between fine and coarse roots.
-The daily net biomass production of seedlings (*P*~i~) is then given by
+The daily net biomass production of seedlings (*G*), from @makela1997carbon, is then given by
 
@@
 (1)
-$$P_i(t) = \frac{L_\mathrm{i}~Cday_\mathrm{i}~\sigma - R_\mathrm{i}}{\epsilon}$$
+$$G(t) = \frac{L~P~\sigma - R}{\epsilon}$$
 
-where *L*~i~ is modelled total plant leaf area (m^2^), *Cday*~i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), $\epsilon$ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R*~i~ is the mass based total respiration of all tissue components (g C d^-1^).
-Here, i represents model runs for each experimental treatment (1:7).
+where *L* is modelled total plant leaf area (m^2^), *P* is the daily carbon assimilation per unit leaf area (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), $\epsilon$ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
 Total respiration was calculated as
@@
 (2)
-$$R_i(t) = \Sigma_{c=1}^{3}(R_\mathrm{c}~M_\mathrm{c,i}(t))$$
+$$R(t) = R_\mathrm{s}M_\mathrm{s}~+~R_\mathrm{fr}M_\mathrm{fr}~+~R_\mathrm{cr}M_\mathrm{cr}$$
 
-where *R*~c~ is published or measured tissue respiration rates of different woody tissue components (Table `r pvetabS`, g C g mass^-1^ d^-1^) and *M*~c,i~ is the modelled standing biomass for each component (g).
-Here, c represents fine roots, coarse roots or stems.
-Leaf respiration is included in the calculation of *Cday* (described below).
-The change in individual component biomass (*M*~c,i~), here solved on a daily time step, is given by
+where *R* is published or measured tissue respiration rates (g C g mass^-1^ d^-1^) of stems (s), fine roots (fr) and coarse roots (cr) and *M* is the modelled standing biomass for each tissue component (g).
+Leaf respiration is included in the calculation of *P*.
+The change in each tissue component biomass (*M*) on daily time steps, including leaves, stems fine roots and coarse roots, is given by
 
@@
 (3)
-$$\frac{dM_\mathrm{c}}{dt} = \theta_\mathrm{c}~P_\mathrm{i}(t)~-~(\Lambda_\mathrm{c}~M_\mathrm{c,i})$$
+$$\frac{dM}{dt} = \theta~P(t)~-~(\Lambda~M)$$
 
-where $\theta$~c~ is the component specific biomass partitioning to whole plant biomass (%) and $\Lambda$~c~ is component specific turnover rate (yr^-1^).
+where $\theta$ is the component specific biomass partitioning to whole plant biomass (%) and $\Lambda$ is component specific turnover rate (yr^-1^).
 Because we did not observe branch turnover, $\Lambda$ of stems was assumed to equal 0.
@@
 
-\
-*Cday* was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *R* and *g*~1~) for each treatment and meteorological data from an onsite weather station.
+##Model parameters and simulations
+*P* was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *R* and *g*~1~) for each treatment and meteorological data from an onsite weather station.
 Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above), *R* was empirically measured and the *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values.
@@
 Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A*~n~ rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
-*Cday* was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
-This resulted in 120 unique values of *Cday* for each soil volume treatment, one value for each day of the experiment.
-Thus, each daily time step for model runs included a value of *Cday* that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
+*P* was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
+This resulted in 120 unique values of *P* for each soil volume treatment, one value for each day of the experiment.
+Thus, each daily time step for model runs included a value of *P* that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
 
@@
 Next, the linear relationship between $\sigma$ and total leaf area was determined across digitized seedlings, within each treatment.
-For the growth model, $\sigma$ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to *Cday*~i~.
+For the growth model, $\sigma$ was then predicted for each daily time step using the previous days cumulative leaf area and this value was then applied to *P*.
 All default parameters used in model simulations are reported in Table `r pvetabS`.
@@
 First, a default model with mean photosynthetic parameters from the free seedlings was optimized to estimate a leaf mass fraction (LMF) which correctly predicted both the leaf mass and total biomass of the harvested free seedling (*M*~free~).
-This optimized LMF was then used to constrain model runs with treatment-specific *Cday*, while keeping woody tissue respiration and tissue turnover parameters constant, to determine if changes in leaf *A*~n~ alone could predict biomass of seedlings in containers (*M*~pots~).
-Cumulative net leaf C gain for each treatment was equal to the sum of each value of *Cday*~i~ over 120 days and final seedling C was assumed to equal half of the final dry mass for both modeled and observed seedlings.
-Seedling biomass production was compared between model output and harvested seedlings with treatment-specific mean *Cday* by first scaling values to the free seedling control.
+This optimized LMF was then used to constrain model runs with treatment-specific *P*, while keeping woody tissue respiration and tissue turnover parameters constant, to determine if changes in leaf *A*~n~ alone could predict biomass of seedlings in containers (*M*~pots~).
+Cumulative net leaf C gain for each treatment was equal to the sum of each value of *P* over 120 days and final seedling C was assumed to equal half of the final dry mass for both modeled and observed seedlings.
+Seedling biomass production was compared between model output and harvested seedlings with treatment-specific mean *P* by first scaling values to the free seedling control.
 
@@
 As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
-
-\
-Next, we performed a series of model simulations to test possible C allocation scenarios to account for the over-predictions of seedling C mass.
-Running the model with observed treatment-specific LMF values from the final harvest (*M*~S1~), which were each lower than the optimized LMF value (see Figure `r allocfig`a), improved model predictions of seedling C mass but still overestimated seedling total C by 32&pm;11.1 % (Figure `r massmodelfig2`a).
-Using harvest values of LMF, however, does not capture the observed increase in leaf turnover of seedlings in small containers (Figure `r allomfig`c).
-Thus, the use of harvest LMF values for seedlings in containers in *M*~S1~ likely underestimates daily C allocation to leaves over the final months of the experiment.
-Increases of 50 % in non-leaf tissue respiration (*M*~S2~) improved biomass estimates slightly but nonetheless overestimated mass C by an average of 46&pm;9.3 % in seedlings with soil volume restriction (Figure `r massmodelfig2`b).
-With *M*~S2~, non-tissue respiration rates would need to be increased by ca.
-250% in order for mass balance to be achieved.
 
@@
 \
-Increasing rates of non-leaf respiration (*M*~S2~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation.
-We also show that very large increases in non-leaf respiration rates would have been required to accurately predict observed seedling biomass.
-Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], results from *M*~S2~ highlight a lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change.
-This is noteworthy, as C balance is a delicate equilibrium between fluxes of *A*~n~ and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions [@valentini2000respiration].
+**this section needs to address why different, implications for models (what they do and need to do)*
+
+Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], it is often conisdered a static parameter in process based growth models.
+
 These results imply that using fixed rates of respiration in models likely underestimates plant responses to sink limitation.
@@
 [-@delucia2007forest] that it is likely inappropriate to assume that respiration is a constant fraction of gross primary production in models.
+
+A lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change.
+
+This is noteworthy, as C balance is a delicate equilibrium between fluxes of *A*~n~ and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions [@valentini2000respiration].
+
 Our findings reveal that a combination of different mechanisms, beyond *A*~n~, are likely at play in driving the observed seedling biomass response to sink manipulation.
 However, the degree to which these mechanisms will regulate growth will undoubtedly shift across different experimental manipulations and plant species.
+
+Empirical data in this study point to *A*~n~ driving reductions in growth, however, modelling result highlight the importance of investigating other components of C balance.
+
+*growth limitation affects both photosynthesis and other components of the C balance*
 
@@
 
-```{r model_scenarios, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
-source("master_scripts/massmodel_optimize_scenarios.R")
-```
-**Figure S1**.
-Sensitivity testing of the seedling growth model to different carbon allocation strategies, including; (a) leaf mass fraction set to treatment-specific final harvest values and (b) increases in respiration of non-leaf tissue components by 50 %.
-Open and filled symbols represent default model and harvest values, respectively, while shaded symbols represent model sensitivity to each scenario by soil volume treatment.
-Both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.
-
 # Acknowledgements

### 2016-04-12 manuscript/manuscript_pve.Rmd
BM edits

@@
 #Summary
-- Interpreting limitations to plant growth requires accounting of carbon (C) mass balance between uptake and allocation.
+
+- The difficulty in quantifying all components of plant carbon (C) balance inhibits our ability to interpret growth limitation in woody species.
 This study manipulated soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
@@
 #Introduction
-
 Understanding plant growth and its relationship to C assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
-As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth is driven by the allocation of photosynthate from source leaves among these different tissues sinks.
+As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth is driven by the allocation of photosynthate from source leaves among these different tissue sinks.
 At long enough time scales leaf photosynthesis (*A*~n~) and respiratory losses together determine net C balance and plant growth.
-At shorter temporal scales growth can instead be mediated by tissue C storage pools [@chapin1990ecology], disrupting the coordination between *A*~n~ and growth.
+At shorter temporal scales growth can instead be mediated by tissue C storage pools [@chapin1990ecology], which disrupts the coordination between *A*~n~ and growth.
 This discrepancy has led to the current debate on how strongly plant growth is controlled by either source or sink activity.
-
-As plant growth cannot simply be determined by *A*~n~, growth models must take into account several simultanesous processes affecting the C balance at any given time [@fourcaud2008plant].
-
-Despite a wealth of studies, large uncertainties still remain regarding the coordination of C supply and growth of woody species.
-*when growth is limited* interpretations of how the C balance reponds.......
+As plant growth cannot be simply determined by *A*~n~, growth models must take into account several simultaneous processes affecting the C balance at any given time [@fourcaud2008plant].
+Whether growth limitation in woody species is driven mostly by *A*~n~ or other components of the C balance remains largely uncertain.
 
@@
 With a novel field-based design we detected a massive effect of container volume on seedling growth, when compared with naturally planted seedlings.
-This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants has seldom been studied.
+This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants is seldom studied.
 Although biomass partitioning was conserved, our empirical and model results suggest that the amount of photosynthate allocated to non-biomass pools such as TNC or respiration were likely altered by sink inhibition.

### 2016-04-13 manuscript/manuscript_pve.Rmd
manuscript edits BM

@@
 \
-7 figures (6 color), 3 tables
+6 figures (6 color), 3 tables
 \
@@
 - Container volume negatively affected aboveground growth throughout the experiment, yet, mass partitioning to leaves, stems and roots was unchanged after 120 days.
-Photosynthetic capacity was significantly reduced in containered seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
-Although belowground sink limitation reduced *A*~n~, the model concluded that these reductions were not large enough to explain observed growth responses.
+Photosynthetic capacity was significantly reduced in containered seedlings, and was related to reduced leaf nitrogen content and starch accumulation.
+Although belowground sink limitation reduced *A*~n~, the model concluded that these reductions were too small to explain observed growth responses.
 
 - As *A*~n~ and growth were not tightly coordinated, an unaccounted-for pool of photosynthetic C resulted in seedlings with soil volume restriction.
-These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf C uptake.
+These results highlight the need to utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf C uptake.
 
@@
 We also expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume, as reduced sink strength would lead to accumulation of leaf non-structural carbohydrates and down regulation of *A~n~*.
-Taking into account measured rates of photosynthesis, we expected biomass predictions from the growth model to correspond to observed seedling mass
+Taking into account measured rates of photosynthesis, we expected biomass predictions from the growth model to correspond to observed seedling mass.
 
@@
 Six container volumes were used ranging from 5 L to 35 L, with a 22.5 cm diameter, and lengths ranging from 15 to 100 cm.
-Containers were constructed of PVC pipe and were filled with local top soil (described above).
+Containers were constructed of PVC pipe and were filled with local top soil.
 Soil in each container was packed to achieve a target soil bulk density that matched local soil conditions of 1.7 g cm^-3^.
@@
 Root mass was collected by removing the roots system and passing soil from each container through a 1 mm sieve, washing, separating into fine and coarse roots (<2 mm and >2 mm diameter, respectively) and then drying to a constant mass.
-Roots of seedlings in containers were not considered pot bound, as clusters of roots along the soil-container interface were not observed.
+Roots of seedlings in containers were not considered pot bound, as matted roots along the soil-container interface were not observed.
 Roots from the free seedlings were collected by excavating each 1 m^2^ subplot to the hard layer and keeping only roots within the subplot.
@@
 Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis of N.
-Nitrogen concentrations ([N]) of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of N~2~ and CO~2~).
-The percentage of N in the sample was calculated by comparison with certified standards.
+Nitrogen concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of N~2~ and CO~2~).
+The percentange of N in samples was calculated by comparison with certified standards.
 Leaf $\delta$^13^C was analyzed  with an Delta V Advantage coupled to a Flash HT and Conflo IV isotope ratio mass spectrometer.
@@
 Complete methods of the TNC assay are described in @mitchell2013drought.
-TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, was calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass or the leaf N content.
-Similarly, TNC-free leaf N (N~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC content.
+TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, was calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass.
+Similarly, TNC-free leaf N content (N~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC content.
 
@@
 We developed a simple seedling growth model that utilized leaf *A*~n~ rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
-The model begins with mean initial tissue component biomass (leaf~0, stem~0~ and root~0~) and a starting leaf area (L~0~) measured prior to planting.
+The model begins with mean initial tissue component biomass (leaf~0~, stem~0~ and root~0~) and a starting leaf area (L~0~) measured prior to planting.
 The initial biomass of roots was divided evenly between fine and coarse roots.
@@
 Leaf respiration is included in the calculation of *P*.
-The change in each tissue component biomass (*M*) on daily time steps, including leaves, stems fine roots and coarse roots, is given by
+The change in each tissue component biomass (*M*) on daily time steps, including leaves, stems, fine roots and coarse roots, is given by
 
@@
 We then used this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.
-First, a default model with mean photosynthetic parameters from the free seedlings was optimized to estimate a leaf mass fraction (LMF) which correctly predicted both the leaf mass and total biomass of the harvested free seedling (*M*~free~).
+First, a default model with mean photosynthetic parameters from the free seedlings was optimized to estimate a leaf mass fraction (LMF) which correctly predicted both the leaf mass and total biomass of the harvested free seedlings (*M*~free~).
 This optimized LMF was then used to constrain model runs with treatment-specific *P*, while keeping woody tissue respiration and tissue turnover parameters constant, to determine if changes in leaf *A*~n~ alone could predict biomass of seedlings in containers (*M*~pots~).
@@
 Across all measurement campaigns, mean *A*~sat~ (Figure `r asatfig`) and *A*~max~ (Table `r pvetab3`) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
-The relationship between leaf starch and leaf N on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated with both leaf N content and leaf starch (both *P* < 0.001).
-We used predictions from the linear mixed effect model equation to visualize these relationships of *A*~max~ to either leaf N content or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
-Across all measurement campaigns and treatments *A*~max~ was higher when leaf N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
-*A*~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b).
+The relationship between leaf starch and leaf N~f~ on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated with both leaf N~f~ and leaf starch (both *P* < 0.001).
+We used predictions from the linear mixed effect model equation to visualize these relationships of *A*~max~ to either leaf N~f~ or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
+Across all measurement campaigns and treatments *A*~max~ was higher when leaf N~f~ was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
+*A*~max~  was also lower when leaf starch was high as higher leaf N~f~ often did not coincide with high leaf starch (Figure `r achemfig`b).
 Overall, *A*~max~ was positively correlated with final harvest biomass across all seedlings (*P* < 0.001).
@@
 ##Modelling seedling biomass
-Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 25.7 %; with this LMF, the model predicted mean harvest total biomass of free seedlings within 0.1 %.
-Using this optimized LMF, the modeled total biomass of seedlings for each soil volume treatment (*M*~pots~) was on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf C gain (Figure `r massmodelfig`a).
-As a result, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b).
+Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 25.7 %; with this LMF, the model predicted mean harvest total biomass of free seedlings within 1.0 %.
+Using this optimized LMF, the modeled total biomass of seedlings for each soil volume treatment (*M*~pots~) was on average 11&pm;2.3 g C more than measured seedling biomass when compared against predicted total net leaf C gain (Figure `r massmodelfig`a).
+As a result, seedling C mass was overestimated by an average of 45&pm;6.2 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b).
 As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the container size treatments.
@@
 Low growth led to large reductions in biomass in small containers, compared to freely rooted seedlings.
-We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, consistent with the meta-analysis of Poorter, Bühler, et al.
+We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, consistent with the meta-analysis of Poorter et al.
 [-@poorter2012pot].
@@
 \
-With respect to nutrient availability, reductions in *A*~n~ were positively correlated with decreases in leaf [N] and leaf N was considerably reduced for seedlings in containers.
-Since reductions in leaf N were detected with TNC-free leaf mass, it is likely that nutrient uptake was affected in the smallest containers instead of TNC dilution in leaves.
-It it possible that physical root restriction or decreased supply reduced seedling N uptake in small containers.
+With respect to nutrient availability, reductions in *A*~n~ were positively correlated with decreases in leaf N~f~ and leaf N~f~ was considerably reduced for seedlings in containers.
+Since reductions in leaf N~f~ were detected with TNC-free leaf mass, it is likely that nutrient uptake was affected in the smallest containers instead of TNC dilution in leaves.
+It it possible that either physical root restriction or decreased supply reduced seedling N uptake in small containers.
 Although root N was on average higher in free seedlings at the end of the experiment, it was not consistently higher than the smallest container volume treatment.
-Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N in free seedlings, but this effect is unknown.
+Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N~f~ in free seedlings, but this effect is unknown.
 Soil N also declined evenly across all treatments, providing no clear evidence for decreased supply between free seedlings and seedlings in containers.
 In these already low fertility soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
-Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the effects of belowground sink limitation on *A*~n~ of seedlings in containers was evident throughout the experiment.
+Although no clear feedback could be determined between the available soil N pool and decreases in leaf N~f~, the effects of belowground sink limitation on *A*~n~ of seedlings in containers was evident throughout the experiment.
 
@@
 Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven plant growth models [@lacointe2000carbon].
-To address this issue, we utilized the flexibility of this model to test plausible fates of the pool of simulated non-biomass C unaccounted for with observed mass balance.
-Similar to Lohier et al.
-[-@lohier2014explaining] we manipulated processes contributing to modeled seedling C mass balance, including changes to leaf C allocation or non-leaf tissue respiration, to quantitatively test their respective influences on model predictions.
 
 \
-Using measured LMF from the harvest, instead of the optimized seedling control (*M*~S1~), improved biomass predictions and provided insight into how sink limitation can impact leaf C allocation beyond *A*~n~.
-The sensitivity of the model to shifts in LMF could represent leaf loss throughout the experiment that could not be explicitly quantified in this field study.
-As TNC accumulation can lead to accelerated leaf senescence [@paul2001sink], this could explain the observed decline in total leaf area of seedlings in small containers.
+Focusing only on empirical results in this study points to *A*~n~ driving reductions in seedling growth.
+Our modelling results reveal that other components of the C balance, beyond *A*~n~, are required to explain the observed seedling biomass response to sink manipulation.
+This discrepancy is noteworty as partial accounting of the different mechaninsms involved in plant carbon balance can lead to erroneous conclusions [@valentini2000respiration].
+For example, the fraction of photosynthate used in respiration is known to vary depending on species and local environmental conditions [@Lambers2008], yet is often considered a static parameter in process based growth models.
+The use of fixed rates of respiration in our model likely underestimates seedling responses to sink limitation.
+Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
 Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A*~n~ and the fate of C allocated to growth, respiration and C storage in leaves.
-It will be the interactions between these two components that will determine the total C gain available for plant growth.
-
-\
-**this section needs to address why different, implications for models (what they do and need to do)*
-
-Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], it is often conisdered a static parameter in process based growth models.
-
-These results imply that using fixed rates of respiration in models likely underestimates plant responses to sink limitation.
-Thus, we agree with Delucia et al.
-[-@delucia2007forest] that it is likely inappropriate to assume that respiration is a constant fraction of gross primary production in models.
-
-A lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change.
-
-This is noteworthy, as C balance is a delicate equilibrium between fluxes of *A*~n~ and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions [@valentini2000respiration].
-
-Our findings reveal that a combination of different mechanisms, beyond *A*~n~, are likely at play in driving the observed seedling biomass response to sink manipulation.
-However, the degree to which these mechanisms will regulate growth will undoubtedly shift across different experimental manipulations and plant species.
-
-Empirical data in this study point to *A*~n~ driving reductions in growth, however, modelling result highlight the importance of investigating other components of C balance.
-
-*growth limitation affects both photosynthesis and other components of the C balance*
+However, the degree to which these mechanisms regulate the C available for growth will undoubtedly shift across different species and environmental conditions.
 
@@
 With a novel field-based design we detected a massive effect of container volume on seedling growth, when compared with naturally planted seedlings.
-This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants is seldom studied.
-Although biomass partitioning was conserved, our empirical and model results suggest that the amount of photosynthate allocated to non-biomass pools such as TNC or respiration were likely altered by sink inhibition.
+This finding is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants is seldom studied.
+Although biomass partitioning was conserved, our empirical and model results suggest that the amount of photosynthate allocated to non-biomass pools were likely altered by sink inhibition.
 The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
@@
 Although this may be true, our results imply that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
+
 Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
+
 The approach used here has the flexibility to account for multiple drivers of C allocation and provides an avenue to address future questions regarding the impact of environmental change on plant growth.
@@
 Seedling mass and leaf $\delta$^13^C values are from final harvest.
-Values of leaf starch, sugars, nitrogen and SLA represent overall means across measurement campaigns (n=6).
+Values of SLA~f~, leaf starch, leaf sugars and leaf N~f~ represent overall means across measurement campaigns (n=6).
 Different letters represent significant differences between treatments.
@@
                         "Seedling mass (g)", 
-                        "SLA~TNC-free~ (m^2^ kg^-1^)",
+                        "SLA~f~ (m^2^ kg^-1^)",
                         "Leaf Starch (%)", 
                         "Leaf Sugars (%)", 
-                        "Leaf Nitrogen~TNC-free~ (%)",
+                        "Leaf N~f~ (%)",
                         paste0("Leaf ", "$\\delta$","^13^C"," (\u2030)")) %>%
@@
 # Acknowledgements
-We thank Burhan Amiji for his outstanding technical assistance.
-We would like to thank the many Hawkesbury Institute for the Environment staff and students who helped during the experimental harvest.
-This research was funded by a PhD Scholarship from the Hawkesbury Institute for the Environment (Western Sydney University).
+We thank Burhan Amiji for his outstanding technical assistance. We would like to thank the many Hawkesbury Institute for the Environment staff and students who helped during the experimental harvest.
 

### 2016-04-13 master_scripts/massmodel_optimize.R

@@ -1,4 +1,4 @@
-# source("functions and packages/startscripts.R")
+source("functions and packages/startscripts.R")
 
 source("master_scripts/model_start.R")
 source("master_scripts/massmodel.R")
@@ -116,11 +116,16 @@ write.csv(biomass_time, "calculated data/biomass_time.csv", row.names=FALSE)
   mass_actual$Date <- as.Date("2013-05-21")
   mass_actual$mass_adj <- with(mass_actual, mass/mass[7])
   
-  ##look at free for optimization %
-   #percdiff <- (C_stnd$modelmass - mass_actual$mass)/C_stnd$modelmass
-  
-  
-  
+##RESULTs SECTION------------------------------------------------------------------------------------------------------
+  # ##look at free for optimization %, mean/se of container seedlings 
+  #  percdiff <- (C_stnd$modelmass - mass_actual$mass)/C_stnd$modelmass
+  #  mean(percdiff[1:6])
+  #  se(percdiff[1:6])
+  # ##mean/se difference in mass in gC for containers
+  #  massdiff <- (C_stnd$modelmass - mass_actual$mass)*.5
+  #  mean(massdiff[1:6])
+  #  se(massdiff[1:6])
+   
 #9. plot plant carbon with optmized LMF sim vs total c gain (LA from sim cday120) and scaled------------------------------
   pch3 <- c(rep(1,6), 6)
 

### 2016-04-13 master_scripts/model_table.R

@@ -1,3 +1,4 @@
+
 ###make model parameter table
 
 r1 = c("Leaf area~0~", "initial leaf area",	0.035,	"m^2^",	"this study")
@@ -8,7 +9,7 @@ r5 = c("$\\epsilon$",	"biomass conversion efficiency",	0.65,	"g C g mass^-1^",	"
 r6 = c("R~coarse~ ~root~",	"coarse root respiration",	0.00124,	"g C g root^-1^ d^-1^",	"Marden et al. (2008)")
 r7 = c("R~fine~ ~root~",	"fine root respiration",	0.01037,	"g C g root^-1^ d^-1^","Ryan et al. (2010)")
 r8 = c("R~stem~",	"stem respiration",	0.00187,	"g C g stem^-1^ d^-1^", "Drake et al. (unpublished)")
-r9 = c("C~day~",	"daily leaf carbon assimilation",	'5.4 - 7.6',	"g C m^-2^ d^-1^",	"this study")
+r9 = c("P",	"daily leaf carbon assimilation",	'5.4 - 7.6',	"g C m^-2^ d^-1^", "this study")
 r10 = c("$\\Lambda$",	"leaf or root turnover", 	1,	"yr^-1^",	"theoretical")
 
 modeltable <- rbind(r1, r2,r3,r4,r5,r6,r7,r8,r9,r10)

### 2016-04-14 manuscript/manuscript_pve.Rmd
final edits BM

@@
 \
-Hawkesbury Institute for the Environment, Western Sydney University
-Hawkesbury Campus
-Ground Floor, Building R2
-Locked Bag 1797
-Penrith 2751 NSW Australia
-
-\
 Corresponding author: CE Campany, email: courtneycampany@gmail.com, telephone: +61 02 4570 1421, fax: +61 02 4570 1103
@@
 Main text:
+\
+Summary: 200
 \
@@
 \
-Acknowledgements:
+Acknowledgements: 30
 \
-6 figures (6 color), 3 tables
+6 figures (5 color), 3 tables
 \
@@
 .packages = c("RColorBrewer", "doBy", "sciplot", "plyr","nlme", "multcomp", "plantecophys", "scales","smatr",
-                           "lme4", "lmerTest", "broom", "reporttools", "visreg")
+                           "lme4", "lmerTest", "broom", "reporttools", "visreg", "pixiedust")
 
@@
 ```{r global data/sourcing, echo=FALSE, message=FALSE, warning=FALSE}
-# Two useful packages for printing numbers, accessing content of objects.
-library(broom)
-library(reporttools)
 # Set Flag to include figures in text or not.
@@
 #table data
-library(pixiedust)
 table1 <- read.csv("master_scripts/pve_table1.csv")
@@
 ## Keywords {.unnumbered}
-photosynthesis, growth, sink regulation, carbon allocation, soil volume
+photosynthesis, plant growth, sink regulation, carbon allocation, soil volume
 
 #Introduction
-Understanding plant growth and its relationship to C assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
+Understanding plant growth and its relationship to carbon (C) assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
 As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth is driven by the allocation of photosynthate from source leaves among these different tissue sinks.
@@
 that sink limitation may be driving the down regulation of photosynthesis, and thus growth.
-However, there are several possible mechanisms that can explain reduced *A*~n~ in small containers including reduced nutrient content or water availability, or reduced sink strength [@poorter2012pot].
+However, there are several possible mechanisms that can explain reduced *A*~n~ in small containers including reduced water availability or nutrient content, or reduced sink strength [@poorter2012pot].
 It was therefore necessary to examine each of these factors to determine if the induced belowground sink limitation actually triggered photosynthetic down regulation.
@@
 With respect to nutrient availability, reductions in *A*~n~ were positively correlated with decreases in leaf N~f~ and leaf N~f~ was considerably reduced for seedlings in containers.
-Since reductions in leaf N~f~ were detected with TNC-free leaf mass, it is likely that nutrient uptake was affected in the smallest containers instead of TNC dilution in leaves.
+Since reductions in leaf N~f~ were detected with TNC-free leaf mass, TNC dilution of leaf N was accounted for in all seedlings.
 It it possible that either physical root restriction or decreased supply reduced seedling N uptake in small containers.
@@
 Our modelling results reveal that other components of the C balance, beyond *A*~n~, are required to explain the observed seedling biomass response to sink manipulation.
-This discrepancy is noteworty as partial accounting of the different mechaninsms involved in plant carbon balance can lead to erroneous conclusions [@valentini2000respiration].
+This discrepancy is noteworty, as partial accounting of the different mechaninsms involved in plant carbon balance can lead to erroneous conclusions [@valentini2000respiration].
 For example, the fraction of photosynthate used in respiration is known to vary depending on species and local environmental conditions [@Lambers2008], yet is often considered a static parameter in process based growth models.
 The use of fixed rates of respiration in our model likely underestimates seedling responses to sink limitation.
-Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
+Thus, our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
 Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A*~n~ and the fate of C allocated to growth, respiration and C storage in leaves.
@@
 Our combined empirical and modeling approach shows that when non-photosynthetic parameters were kept constant, changes in *A*~n~ were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
-K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A*~n~ through the demand for C.
+It has been suggested that tissue sink activity strongly feedbacks onto source activity, causing growth to control *A*~n~ through the demand for C [@korner2013growth; @korner2015paradigm].
 Although this may be true, our results imply that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
-
-Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
-
 The approach used here has the flexibility to account for multiple drivers of C allocation and provides an avenue to address future questions regarding the impact of environmental change on plant growth.
@@
   sprinkle_colnames("Volume (L)", 
-                        "Root Nitrogen (%)", 
+                        "Root N (%)", 
                         "SRL (m g^-1^)",

### 2016-05-18 manuscript/manuscript_pve.Rmd
thesis edits, only added to manuscript if appropriate
adds a few new cites

apparently i didnt push the CUE plots for BM yet

@@
 Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
-In partial defoliation experiments, increases in *A*~n~ of the remaining foliage are commonly shown, and are attributed to reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
+In partial defoliation experiments, increases in *A*~n~ of the remaining foliage are commonly shown, and are attributed to reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end;@pinkard2011gas], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased;@pinkard2011gas] and regulatory sugar signaling [@eyles2013whole].
 Similar to elevated CO~2~ experiments, these increases in *A*~n~ in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
@@
 Both *J*~max~ and *V*~cmax~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`).
+Overall, the J~max~:Vc~max~ ratio was relatively conserved across all treatments (1.6&pm;0.02), which is consistent with findings across many tree species [@medlyn1996optimal; @leuning1997scaling; @medlyn1999effects; @warren2003photosynthesis; @crous2008elevated].
 Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`).
@@
 \
-Decreases in *A*~sat~ occurred simultaneously with reductions growth of seedlings in containers. This observation initially suggests 
-that sink limitation may be driving the down regulation of photosynthesis, and thus growth.
+Decreases in *A*~sat~ occurred simultaneously with reductions growth of seedlings in containers.
+This observation initially suggests that sink limitation may be driving the down regulation of photosynthesis, and thus growth.
 However, there are several possible mechanisms that can explain reduced *A*~n~ in small containers including reduced water availability or nutrient content, or reduced sink strength [@poorter2012pot].
@@
                         "R ($\\mu$mol m^-2^ s^-1^)",
-                        "*J*~max~",
-                        "*V*~cmax~",
+                        "*J*~max~ ($\\mu$mol m^-2^ s^-1^)",
+                        "*V*~cmax~ ($\\mu$mol m^-2^ s^-1^)",
                         "*g*~s~ (mol m^-2^ s^-1^)",

### 2016-05-18 manuscript/thesis_pve.Rmd
thesis edits, only added to manuscript if appropriate
adds a few new cites

apparently i didnt push the CUE plots for BM yet

@@
 ---
-
-<!-- \ -->
-<!-- Courtney E. Campany^1^, Belinda Medlyn^1^, Remko A. Duursma^1^. -->
-
-<!-- \ -->
-<!-- ^1^ Hawkesbury Institute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW, Australia -->
-
-<!-- \ -->
-<!-- *Corresponding author*:  -->
-<!-- Courtney Campany -->
-<!-- E: courtneycampany@gmail.com -->
 
@@
 Although belowground sink limitation resulted in a reduction of *A~n~*, the model concluded that these reductions were not large enough to explain observed growth responses.
-Thus, as *A~n~* and growth were not tightly coordinated, an unaccounted for pool of photosynthetic C resulted in seedlings with soil volume restriction.
+As *A~n~* and growth were not tightly coupled, an unaccounted for pool of photosynthetic C resulted was predicted in seedlings with soil volume restriction.
 These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf C uptake.
-
-<!-- ## Keywords {.unnumbered} -->
-<!-- photosynthesis, growth, sink regulation, carbon allocation, soil volume -->
 
@@
 Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
-In partial defoliation experiments, increases in *A~n~* of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole].
+In partial defoliation experiments, increases in *A~n~* of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end; @pinkard2011gas], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased; @pinkard2011gas] and regulatory sugar signaling [@eyles2013whole].
 However, increases in *A~n~* in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
@@
 For each free seedling, used as the control, a 1 m^2^ subplot was excavated to the hard layer and replaced with the same soil used in each container.
+This ensured that any possible feedbacks from soil disturbance would be similar between seedlings in containers and free seedlings.
 A border of root exclusion material was buried 0.25 m deep and extended 0.25 m above the ground surface around each subplot to exclude local vegetation, which was further kept out by periodic weeding.
@@
 Freshly detached leaves were collected at least 1 hour after sundown and placed inside a conifer chamber attached to the Licor 6400.
+This method increases the measureable surface area of each leaf, beyond the standard leaf chamber, to accurately quantify *R*.
 Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions.
@@
 $$R = \Sigma(R_c~M_c)$$
-where *R~c~* is published or local tissue respiration rates of fine roots, coarse roots or stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
+where *R~c~* is tissue respiration rates of fine roots, coarse roots or stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g).
+Tissue respiration rates were not directly measured in this experiment, so published or local default values from Eucalyptus species were used.
 Leaf respiration is represented in the calculation of C~day~.
@@
 C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (J~max~, Vc~max~, *R* and g~1~) for each treatment and meteorological data from an onsite weather station.
-J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), *R* was empirically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed g~s~ values.
+J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), *R* was empirically measured and the g~1~ parameter, describing the plants water-use strategy, was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed g~s~ values.
 Methods of the coupled leaf gas exchange model are also described in Duursma et al [-@duursma2014peaked].
@@
 It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf *A~n~* with total plant leaf area.
+Accurately modelling canopy photosynthesis requires inclusion of the heterogeneous nature of light availability that occurs from self-shading and the limitations this then imposes on leaf *A~n~* [@de1997simple; @marchiori2014photosynthetic].
 This was accomplished by utilizing 61 previously digitized *Eucalyptus* seedlings, covering 5 total species which include *E.
@@
                         "*R* ($\\mu$mol m^-2^ s^-1^)",
-                        "J~max~",
-                        "Vc~max~",
+                        "J~max~ ($\\mu$mol m^-2^ s^-1^)",
+                        "Vc~max~ ($\\mu$mol m^-2^ s^-1^)",
                         "g~s~ (mol m^-2^ s^-1^)",
@@
 Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`).
+Overall, the J~max~:Vc~max~ ratio was relatively conserved across all treatments (1.6&pm;0.02), which is consistent with findings across many tree species [@medlyn1996optimal; @leuning1997scaling; @medlyn1999effects; @warren2003photosynthesis; @crous2008elevated].
 Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`).
@@
 ```{r model_scenarios, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
-source("master_scripts/massmodel_optimize_scenarios.R")
+source("clean Scripts/massmodel_optimize_scenarios.R")
 ```  

### 2016-05-18 clean Scripts/cue.R

@@ -1,0 +1,98 @@
+source("functions and packages/startscripts.R")
+###CUE bar plot
+
+##use modelled C net and gross to determine respiration
+##use harvest mass + respiration + unaccounted as fractions of total gross
+
+##read data-----------------------------------------------------------------------------------------------------------------
+finalmass <- read.csv("calculated data/harvest_mass_means.csv")
+
+la_pred <- read.csv("Calculated data/LApred_volume.csv")
+  names(la_pred)[3] <- "LA"
+  la_pred$Date <- as.Date(la_pred$Date)
+
+Cday_net <- read.csv("calculated data/Aleaf_model/cday_120_clean.csv")
+  Cday_net$Date <- as.Date(Cday_net$Date)
+  
+Cday_gross <- read.csv("calculated data/Aleaf_model/cday_120_clean_gross.csv")
+  Cday_gross$Date <- as.Date(Cday_gross$Date)
+
+##Cday with leaf area needs self shading (use slope intercept, from 5-1000 vol)
+sigma <- read.csv("calculated data/M_leafarea_model.csv")
+
+##function to generate total plant daily C gain
+modelledC_func <- function(leafarea, shading, Cday){ #leafarea dfr, self shading dfr, and modelled C gain (gm2)
+  dailyCnet <- merge(leafarea,Cday)
+  ##this needs to include self shadeing (M as a linear function of leaf area)
+  dailyCnet <- merge(dailyCnet, shading[, c(2,3,5)], by="volume")
+    dailyCnet$M <- with(dailyCnet, b*LA+intercept)
+    #calculate total daily C gain with self shading
+    dailyCnet$tdcg <- with(dailyCnet, LA * carbon_day * M)
+  print("successfully calculated total daily carbon with modelled Cgain, leaf area and self shading")
+  
+    dailyCnet$volume <- as.factor(dailyCnet$volume)
+  return(dailyCnet)
+}
+
+##calculate net and gross C gain, then quantify leaf respiration--------------------------------------------------------------
+dailyCnet <- modelledC_func(la_pred, sigma, Cday_net)
+  names(dailyCnet)[8] <- "tdc_net"
+  names(dailyCnet)[4] <- "cday_net"
[…]

### 2016-05-20 manuscript/manuscript_pve.Rmd
added thesis reviewer comment on future experiment only to thesis rmd

@@
 #install packages if not already installed
-.packages = c("RColorBrewer", "doBy", "sciplot", "plyr","nlme", "multcomp", "plantecophys", "scales","smatr",
-                           "lme4", "lmerTest", "broom", "reporttools", "visreg", "pixiedust")
+.packages = c("RColorBrewer", "doBy", "sciplot", "plyr","nlme", "multcomp", "plantecophys", "scales","smatr","plotrix",
+                           "lme4", "lmerTest", "broom", "reporttools", "visreg", "pixiedust", "lubridate", "reshape",
+              "magicaxis", "effects")
 

### 2016-05-30 manuscript/thesis_pve.Rmd
added thesis reviewer comment on future experiment only to thesis rmd
tested area based realtionships

@@
 A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b).
+These relationships were also analyzed when variables were expressed per unit leaf area and the interpretation of the results did not change, as SLA was similar between treatments.
 Overall, A~max~ was positively correlated with final harvest biomass across all seedlings (P < 0.001).
@@
 Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the effects of belowground sink limitation on *A~n~* of seedlings in containers was evident throughout the experiment.
+Future experiments, in which soil N treatments are added, may be able to elucidate the apparent feedbacks between N uptake by roots and leaf N content.
 

### 2016-05-30 areavariable_test.R

@@ -1,0 +1,73 @@
+#this script is for sourcing the Amax vs TNC and N plots into master
+source("functions and packages/startscripts.R")
+library(lme4)
+library(lmerTest)
+library(effects)
+
+
+photo_chem <- read.csv("calculated data/Amax_chem.csv")
+#run volume format func
+photo_chem<- vollab_func(photo_chem)
+#get better units for plotting
+photo_chem$starch_perc <- photo_chem$starch*100
+photo_chem$nitro_mg <- photo_chem$Nmass_notnc *1000
+
+
+photo_chem$starch_area <- with(photo_chem, massarea * (starch_perc/100))
+photo_chem$Narea2 <- with(photo_chem, lma_notnc * (Npercentage/100))
+
+legpch <- c(5, 10, 15, 20, 25, 35, "free")
+
+windows(10, 7)
+par(cex.axis=.96, cex.lab=1.2,mfrow=c(1,2),  oma=c(0.1,0.1,0.1,0.1), las=1)
+plot(Photo ~ Narea2,data=photo_chem)  
+plot(Photo ~ starch_area,data=photo_chem) 
+
+
+###two panel of graph above, using predict------------------------------------------------------------
+
+
+##plot
+alab <- expression(A[mass]~~(n*mol~g^-1~s^-1))
+nitro_noTNC <- expression(Leaf~Nitrogen[TNC[free]]~~(mg~g^-1))
+
+
+windows(10, 7)
+
+par(cex.axis=.96, cex.lab=1.2,mfrow=c(1,2),  oma=c(0.1,0.1,0.1,0.1), las=1)
+
+# First Panel
+par(mar=c(5,5,2,0))
+plot(A_mass ~ starch_perc, data=photo_chem,type='n',ylim=c(0,800), xlim=c(0, 27.5),ylab=alab, axes=FALSE, xlab="")  
+box()
+axis(1, labels=TRUE) 
+axis(2, labels=TRUE)  
+#mtext(alab, outer=TRUE, line=2.5, side=2, cex=1.5)
+points(A_mass ~ starch_perc, pch=21, data=photo_chem, bg=coln2[nitrobin], ylab="",
+       xlab="",cex=1.2, ylab="")
+
+for(i in 1:length(unique(TNCpred$nitro_mg))){
+  m <- subset(TNCpred, nitro_mg == unique(TNCpred$nitro_mg)[i])
[…]

### 2016-06-01 Stats/leafN_tnc_stats.R
possibly still an issue with Nmass calcultaion
changed labels for clairty and made other thesis reviewer comments

@@ -1,111 +1,0 @@
-source("functions and packages/functions.R")
-source("functions and packages/load packages.R")
-source("functions and packages/plot objects.R")
-
-#read TNC and calculated leafN, merge
-
-tnc_leaf <- read.csv("calculated data/leaf_tnc.csv")
-N_leaf <- read.csv( "calculated data/leaf N content.csv")
-
-leaf_traits <- merge(N_leaf, tnc_leaf[,c(1:4,8:11)])
-leaf_traits$volume <- as.factor(leaf_traits$volume)
-leaf_traits$Date <- as.Date(leaf_traits$Date)
-leaf_traits$invest <- with(leaf_traits, Nmass/leafstarch)
-leaf_traits$N_TNC <- with(leaf_traits, Nmass/(leafstarch+leafsugar))
-#tnc free leaf N
-leaf_traits$N_noTNC <- with(leaf_traits, (mass-(leafstarch+leafsugar))*Nperc)
-leaf_traits$Narea_noTNC <- with(leaf_traits, N_noTNC/area)
-
-#means
-
-Nleafagg_noTNC<- summaryBy(N_noTNC +Narea_noTNC~ volume+Date, data=leaf_traits, FUN=c(mean, se))
-
-#---------------------------------------------------------------------------------------
-#plot raw data
-
-#Nmass
-windows()
-par(mfrow=c(3,3))
-leafN_mass<- dlply(leaf_traits, .(volume), function(x) c(plotBy(N_noTNC ~ Date | ID, how="col", type='o', 
-              legend=F, col=x$volume, ylim=c(0, .02),lty=1, ylab="", xlab="", data=x), 
-              title(main=paste("volume = ", unique(x$volume)), line=-1.5, font.main=1, adj=.05, cex.main=1),
-              title(ylab=nmasslab, mgp=ypos)))
-dev.copy2pdf(file="output/stats_plots/Nmass_noTNC_date.pdf")
-dev.off()
-
-#Nmass
-windows()
-par(mfrow=c(3,3))
-leafN_mass<- dlply(leaf_traits, .(volume), function(x) c(plotBy(Narea_noTNC ~ Date | ID, how="col", type='o', 
-             legend=F, col=x$volume, ylim=c(0, .0005),lty=1, ylab="", xlab="", data=x), 
-             title(main=paste("volume = ", unique(x$volume)), line=-1.5, font.main=1, adj=.05, cex.main=1),
[…]

### 2016-06-01 clean Scripts/photo_chem.R

@@ -1,25 +1,30 @@
 #Read amax, leafN, and TNC
 amax <- read.csv("calculated data/Amax.csv")
+
 leafN <- read.csv("calculated data/leaf N content.csv")
+##am i using no tnc leaf N in manuscript figures
+leafN_notnc <- read.csv("calculated data/leafnitrogen_notnc.csv")
 
 tnc <- read.csv("calculated data/tnc_leaf.csv")
-tnc$ID <- gsub("'", "",tnc$ID)
+  tnc$ID <- gsub("'", "",tnc$ID)
 
-#merge data sets
+#merge data sets-----------------------------------------------------------------------------------------------------
 photo_N <- merge(amax[,c(1:2, 5:6, 9)], leafN, all=TRUE)
-#remove the missing values for amax (4-7 #3)
-photo_N_noNA <-  subset(photo_N, !is.na(Photo))
-#re work labels for volume
-photo_N_noNA$volume <- gsub("1000", "free", photo_N_noNA$volume)
-photo_N_noNA$volume <- gsub("^5", "05", photo_N_noNA$volume)
-photo_N_noNA$volume <- as.factor(photo_N_noNA$volume)
+photo_N2 <- merge(photo_N, leafN_notnc, all=TRUE)  
+  
+  #remove the missing values for amax (4-7 #3)
+  photo_N_noNA <-  subset(photo_N2, !is.na(Photo))
+  #re work labels for volume
+  photo_N_noNA$volume <- gsub("1000", "free", photo_N_noNA$volume)
+  photo_N_noNA$volume <- gsub("^5", "05", photo_N_noNA$volume)
+  photo_N_noNA$volume <- as.factor(photo_N_noNA$volume)
 
 #add tnc
 photo_chem <- merge(photo_N_noNA, tnc, all=TRUE)
-#remove the missing vales from both the N and tnc dataset
-photo_chem <-  subset(photo_chem, !is.na(Nperc))
-photo_chem <-  subset(photo_chem, !is.na(starch_mgperg))
-row.names(photo_chem) <- NULL
+  #remove the missing vales from both the N and tnc dataset
+  photo_chem <-  subset(photo_chem, !is.na(Nperc))
+  photo_chem <-  subset(photo_chem, !is.na(starch_mgperg))
+  row.names(photo_chem) <- NULL
 
 #calculate variables for stats
 #tnc variables are g g-1, everything else should be g m-2

### 2016-06-09 manuscript/manuscript_pve.Rmd
possibly still an issue with Nmass calcultaion
changed labels for clairty and made other thesis reviewer comments
ongoing revisions from BM

@@
 ---
-title: Reduced growth due to belowground sink limitation is not explained by reduced photosynthesis
+title: Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis
 author: ""
@@
 
-- The difficulty in quantifying all components of plant carbon (C) balance inhibits our ability to interpret growth limitation in woody species.
-This study manipulated soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings.
+- Sink limitation is known to reduce plant growth, but it is not known how plant carbon (C) balance is affected, limiting our ability to predict growth under sink-limited conditions.
 
-- Seedlings were grown in a range of container sizes and containers were planted flush to the soil alongside freely-rooted (free) seedlings.
-We developed a growth model that utilized net leaf photosynthesis rates (*A*~n~) to allocate daily C uptake towards mass growth of stems, leaves and roots.
+- We manipulated soil volume to impose sink limitation of growth in Eucalyptus tereticornis seedlings.
+Seedlings were grown in containers of different sizes and planted flush to the soil alongside freely-rooted seedlings.
 
-- Container volume negatively affected aboveground growth throughout the experiment, yet, mass partitioning to leaves, stems and roots was unchanged after 120 days.
-Photosynthetic capacity was significantly reduced in containered seedlings, and was related to reduced leaf nitrogen content and starch accumulation.
-Although belowground sink limitation reduced *A*~n~, the model concluded that these reductions were too small to explain observed growth responses.
+- Container volume negatively affected aboveground growth throughout the experiment, but mass partitioning to leaves, stems and roots was unchanged after 120 days.
+Photosynthetic capacity was significantly reduced in containerized seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
+However, the reduction in net leaf photosynthesis over the growth period was insufficient to explain the reduction in growth, so that we also observed a reduction in whole-plant carbon use efficiency (CUE) with container size.
 
-- As *A*~n~ and growth were not tightly coordinated, an unaccounted-for pool of photosynthetic C resulted in seedlings with soil volume restriction.
-These results highlight the need to utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf C uptake.
+- Our results show that sink limitation affects plant growth through feedbacks to both photosynthesis and CUE.
+Mass balance approaches to predicting plant growth under sink-limited conditions need to incorporate both of these feedbacks.
 
@@
 #Introduction
+The source-sink limitation paradigm for plant growth argues that growth may be limited either by source activity, i.e.
+the amount of carbon that the plants are able to take up through photosynthesis, or by sink strength, i.e.
+the amount of carbon that the plants are able to utilize in growth.
+To be able to predict plant growth responses to environmental change, we need models that can account for both source and sink limitation.
+
+Most current models of plant growth are based on the physical principle of mass balance: carbon (C) entering the plant through photosynthesis must be balanced by C loss to respiration and C allocation to growth and storage.
+Plant growth is thus predicted as the outcome of the processes of photosynthesis, respiration and allocation.
+It is easy to see how source-limited growth can be implemented in such models: increasing source activity increases photosynthetic C uptake, flowing through to increased growth.
+It is less easy to know how to implement sink limitation of growth in such models, because it requires that we know whether, and how, sink limitation influences the contributing processes of photosynthesis, respiration and allocation.
+It has been suggested that sink limitation affects the carbon balance by causing a down-regulation of photosynthetic rate, possibly mediated by carbohydrate accumulation (refs), but there is also evidence that photosynthesis and growth are decoupled under sink limitation (refs), suggesting that other processes must also be affected.
+
+In the absence of a good understanding of the effects of sink limitation on physiological processes, most attempts to model sink limitation of growth to date have done so by abandoning the principle of mass balance (e.g.
+Leuzinger; CLM nutrient limitation; Fatichi).
+This approach is unsatisfactory because mechanistic models should obey the laws of physics.
+Our goal in this paper was to investigate how the carbon balance of plants is modified by sink limitation, by experimentally imposing a sink limitation to growth.
+
 Understanding plant growth and its relationship to carbon (C) assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
@@
 \
-One approach to examine the coordination of *A*~n~ and growth is to manipulate C source activity.
-Examples include elevated CO~2~ and partial defoliation experiments.
-Elevated CO~2~ has been shown to increase *A*~n~ [@drake1997more; @ainsworth2007response]; across four forest Free-Air CO~2~ Enrichment (FACE) experiments this increased photosynthetic uptake resulted in a stimulation of biomass production by 23 % on average [@norby2005forest].
+In previous studies, the sink limitation of growth has been explored by manipulations of both C source and C sink activity.
+Examples of experimental approaches that manipulate C source activity include elevated atmospheric CO2 concentration and partial defoliation experiments.
+
+Elevated CO~2~ causes an increase in leaf-level photosynthetic rate, *A*~n~ [@drake1997more; @ainsworth2007response]; across four forest Free-Air CO~2~ Enrichment (FACE) experiments this increased photosynthetic uptake resulted in a stimulation of biomass production by 23 % on average [@norby2005forest].
 Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
-In partial defoliation experiments, increases in *A*~n~ of the remaining foliage are commonly shown, and are attributed to reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end;@pinkard2011gas], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased;@pinkard2011gas] and regulatory sugar signaling [@eyles2013whole].
+
+In partial defoliation experiments, source activity is decreased by reduction of photosynthesizing leaf area.
+In these experiments, compensatory increases in *A*~n~ of the remaining foliage are commonly found, and have been attributed to several processes including indirect effects on resource availability, such as increaed stomatal conductance [@layne1995end] or enhanced leaf nutrient status [@turnbull2007increased; @pinkard2011gas], or more direct effects of modified sink-source balance such as, reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end;@pinkard2011gas], and regulatory sugar signaling [@eyles2013whole].
+However, there have been few attempts *(any??)* to determine the overall C balance in these experiments, and it is unclear whether the change in growth following defoliation can be explained by the reduction in leaf area and changes to A~n~
+
 Similar to elevated CO~2~ experiments, these increases in *A*~n~ in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
@@
 \
-Alternatively, manipulation of plant tissue C sinks is often used to investigate the correlation between *A*~n~ and growth.
-Plant metabolic signalling networks have the ability to regulate photosythetic activity, according to carbon status of different plant tissues [@paul2001sink].
-If sink inhibition of *A*~n~ occurs, a close coordination between declines in *A*~n~ and growth should be expected.
-The occurrence of photosynthetic down regulation has been tested through fruit removal and phloem girdling.
-In these studies, down regulation of *A*~n~ was found to correlate with carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@urban2007girdling; @haouari2013fruit].
-However, reductions in *A*~n~ were also attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
+Alternatively, sink limitation can be investigated by manipulating plant tissue C sinks, for example by fruit remove or phloem girdling.
+In these studies, down regulation of *A*~n~ is often observed, and typically correlates with carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@urban2007girdling; @haouari2013fruit].
+However, reductions in *A*~n~ have also been attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
 This lack of continuity among findings is not surprising, as we still know little about the balance between assimilation, storage and growth across temporal scales in plants [@smith2007coordination].
@@
 \
-An alternative experimental approach is to reduce belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size [@arp1991effects; @nesmith1998effect; @poorter2012pot].
+Yet another experimental approach is to reduce belowground C sink strength in tree seedlings by manipulating container size and thus rooting volume [@arp1991effects; @nesmith1998effect; @poorter2012pot].
 Inadequate rooting volume can decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root].
+
 Container size studies frequently exhibit photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
@@
 \
-This study utilizes a novel field design to investigate the coordination between growth and *A*~n~ in *Eucalyptus tereticornis* Sm.
-seedlings, by manipulating container size and thus rooting volume.
-Seedlings were maintained under well watered conditions in order to isolate the effect of restricted soil volume.
-We used freely-rooted seedlings as a control for the container size treatments.
+Our goal in this paper was to impose a sink limitation of growth, by manipulating container size and thus rooting volume, and to examine how the C balance of the plants was affected.
+We grew *Eucalyptus tereticornis* seedlings in a range of container sizes, using freely-rooted seedlings as a control for the container size treatments.
+Seedlings were maintained under well-watered conditions in order to isolate the effect of restricted soil volume from that of low water availability.
 We tracked leaf-level gas exchange, leaf carbohydrate accumulation and seedling allometry over the course of 4 months.
-Empirical results were combined with a simple plant growth model to simulate seedling growth with a C mass balance approach, which was then compared to observed harvested seedling mass.
-The model used whole-plant C gain, scaled from instantaneous rates of leaf *A*~n~, to quantify seedling dry mass production over the 120 day experiment.
-
-\
-Manipulations of container size were expected to induce a belowground sink limitation compared to free seedlings, resulting in growth reductions in the smallest containers.
-Specifically, reductions in biomass partitioning to root mass, relative to tree size, were predicted to occur with decreasing rooting volume and soil nutrients in container treatments.
-We also expected a correlation between carbohydrate accumulation and photosynthetic capacity as a function of soil volume, as reduced sink strength would lead to accumulation of leaf non-structural carbohydrates and down regulation of *A~n~*.
-Taking into account measured rates of photosynthesis, we expected biomass predictions from the growth model to correspond to observed seedling mass.
+We drove a simple whole-plant photosynthesis model with measured leaf gas exchange and interpolated leaf area data to estimated net canopy carbon uptake over the experimental period, and compared the result with total seedling biomass.
+We anticipated that both photosynthesis and growth would be reduced under belowground sink limitation.
+The principal questions that we addressed were: Firstly, which physiological process best explains the down-regulation of photosynthesis?
+Secondly, does this down-regulation fully explain the observed response of growth, or are other components of the carbon balance also affected
 
@@
 TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, was calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass.
-Similarly, TNC-free leaf N content (N~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC content.
+Similarly, TNC-free leaf N concentration (N~f~, %) was calculated on all gas exchange leaves from leaf mass without TNC content.
 
-##Seedling growth model
+##Net carbon uptake model
 We developed a simple seedling growth model that utilized leaf *A*~n~ rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
@@
 Final seedling height significantly increased with increasing soil volume (*P* < 0.001).
-Increases in both final stem diameter and cumulative leaf area (both *P* < 0.001) were found with increasing soil volume and these differences were driven mainly by the largest container and the free seedling treatments.
+Increases in both final stem diameter and cumulative leaf area (both *P* < 0.001) were found with increasing soil volume.
+We did not find a continuous effect of container size; rathe, plant size was similar among smaller containers, and these differences were driven mainly by the largest container and the free seedling treatments.
 
@@
 Combined, these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment.
-Soil N at harvest was not different across soil volumes ($\bar{x}$ = 4.5 %), with minimal decreases from pre-planting value ($\bar{x}$ = 4.9 %).
+Soil N at harvest was not different across soil volumes ($\bar{x}$ = .045 %), with minimal decreases from pre-planting values ($\bar{x}$ = .049 %).
 This similarity indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
@@
 This study utilized a novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
+Our goal was to identify how sink limitation of growth modified the carbon balance of seedlings.
+We found a strong reduction of growth in containerized plants.
+Leaf *A*~n~ was also strongly reduced, but this reduction was insufficient to fully explain the reduction in growth, implying that whole-plant respiratory loss was likely affected as well.
+
 We addressed questions regarding the coordination of *A*~n~ and growth by complementing empirical results with a C mass balance model.
@@
 
-##Reductions in growth and physiology under sink limitation
+##Changes in growth and physiology under sink limitation
 Soon after seedlings became established, both height and diameter growth were negatively affected by decreasing soil volume.
-Low growth led to large reductions in biomass in small containers, compared to freely rooted seedlings.
+Low growth rates led to large reductions in biomass in small containers, compared to freely rooted seedlings.
 We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, consistent with the meta-analysis of Poorter et al.
@@
 \
-Decreases in *A*~sat~ occurred simultaneously with reductions growth of seedlings in containers.
+Decreases in *A*~sat~ occurred simultaneously with reductions of growth of seedlings in containers.
 This observation initially suggests that sink limitation may be driving the down regulation of photosynthesis, and thus growth.
 However, there are several possible mechanisms that can explain reduced *A*~n~ in small containers including reduced water availability or nutrient content, or reduced sink strength [@poorter2012pot].
-It was therefore necessary to examine each of these factors to determine if the induced belowground sink limitation actually triggered photosynthetic down regulation.
+It was therefore necessary to examine each of these factors to determine the mechanism by which the induced belowground sink limitation triggered photosynthetic down regulation.
 
@@
 Since reductions in leaf N~f~ were detected with TNC-free leaf mass, TNC dilution of leaf N was accounted for in all seedlings.
-It it possible that either physical root restriction or decreased supply reduced seedling N uptake in small containers.
+It is possible that either physical root restriction or decreased supply reduced seedling N uptake in small containers.
 Although root N was on average higher in free seedlings at the end of the experiment, it was not consistently higher than the smallest container volume treatment.
@@
 It was necessary to distinguish if growth was affected beyond ontogenetic constraints, by correcting for size, as biomass distribution is strongly size-dependent [@gould1966allometry; @lleonart2000removing].
-In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, outside of ontogenetic drift (Figure `r allocfig`a,b).
+In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, once ontogenetic drift was taken into account (Figure `r allocfig`a,b).
 This result is unexpected as shifts in partitioning have been noted specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein].
@@
 Our modelling results reveal that other components of the C balance, beyond *A*~n~, are required to explain the observed seedling biomass response to sink manipulation.
-This discrepancy is noteworty, as partial accounting of the different mechaninsms involved in plant carbon balance can lead to erroneous conclusions [@valentini2000respiration].
+This discrepancy is noteworthy, as partial accounting of the different mechanisms involved in plant carbon balance can lead to erroneous conclusions [@valentini2000respiration].
 For example, the fraction of photosynthate used in respiration is known to vary depending on species and local environmental conditions [@Lambers2008], yet is often considered a static parameter in process based growth models.

### 2016-06-10 manuscript/manuscript_pve.Rmd
BM revisions

@@
 Inadequate rooting volume can decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root].
+In a comprehensive meta-analysis, Poorter et al.
+[-@poorter2012pot] demonstrated a large effect of container size on plant biomass accumulation.
+Photosynthetic down-regulation is generally observed in these studies [e.g.
+@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
+Poorter et al.
+[-@poorter2012pot] examined the components of relative growth rate and found the unit leaf rate to be most strongly affected.
+As unit leaf rate is correlated with An, they concluded that down-regulation of An may best explain the effects of container size on biomass growth.
 
-Container size studies frequently exhibit photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
-A meta-analysis by Poorter et al.
-[-@poorter2012pot] concluded that *A*~n~ is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used.
 This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower assimilation rates [@robbins1988effect].
 However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].
-Whether down regulation of *A*~n~ and subsequent reductions of growth are quantitavely similiar has rarely been tested.
+Whether down regulation of *A*~n~ and subsequent reductions of growth are quantitatively similar has rarely been tested.
 Based on these previous studies, using a range of container sizes as a sink-strength manipulation provdies a way to empirically test the extent to which growth and *A*~n~ are coordinated.

### 2016-06-15 manuscript/manuscript_pve.Rmd
BM edits, CUE figures

@@
 
-In the absence of a good understanding of the effects of sink limitation on physiological processes, most attempts to model sink limitation of growth to date have done so by abandoning the principle of mass balance (e.g.
-Leuzinger; CLM nutrient limitation; Fatichi).
+In the absence of a good understanding of the effects of sink limitation on physiological processes, most attempts to model sink limitation of growth to date have done so by abandoning the principle of mass balance *(e.g.
+Leuzinger; CLM nutrient limitation; Fatichi)*.
 This approach is unsatisfactory because mechanistic models should obey the laws of physics.
@@
 
-Understanding plant growth and its relationship to carbon (C) assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration.
-As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth is driven by the allocation of photosynthate from source leaves among these different tissue sinks.
-At long enough time scales leaf photosynthesis (*A*~n~) and respiratory losses together determine net C balance and plant growth.
-At shorter temporal scales growth can instead be mediated by tissue C storage pools [@chapin1990ecology], which disrupts the coordination between *A*~n~ and growth.
-This discrepancy has led to the current debate on how strongly plant growth is controlled by either source or sink activity.
+*also deleted below 2 sentences*
 As plant growth cannot be simply determined by *A*~n~, growth models must take into account several simultaneous processes affecting the C balance at any given time [@fourcaud2008plant].
@@
 Examples of experimental approaches that manipulate C source activity include elevated atmospheric CO2 concentration and partial defoliation experiments.
+Elevated CO~2~ causes an increase in leaf-level photosynthetic rate, *A*~n~ [@drake1997more; @ainsworth2007response].
+While this increase is often observed to drive an increase in plant biomass production (eg any number of papers),
 
-Elevated CO~2~ causes an increase in leaf-level photosynthetic rate, *A*~n~ [@drake1997more; @ainsworth2007response]; across four forest Free-Air CO~2~ Enrichment (FACE) experiments this increased photosynthetic uptake resulted in a stimulation of biomass production by 23 % on average [@norby2005forest].
+across four forest Free-Air CO~2~ Enrichment (FACE) experiments this increased photosynthetic uptake resulted in a stimulation of biomass production by 23 % on average [@norby2005forest].
 Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
 
+\
 In partial defoliation experiments, source activity is decreased by reduction of photosynthesizing leaf area.
@@
 [-@poorter2012pot] examined the components of relative growth rate and found the unit leaf rate to be most strongly affected.
-As unit leaf rate is correlated with An, they concluded that down-regulation of An may best explain the effects of container size on biomass growth.
+As unit leaf rate is correlated with *A*~n~, they concluded that down-regulation of *A*~n~ may best explain the effects of container size on biomass growth.
+However, they were unable to determine the physiological mechanism  driving the downregulation of *A*~n~, nor to test whether the reduction in *A*~n~ could explain the observed reduction in growth.
 
+*delete bellow*
 This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower assimilation rates [@robbins1988effect].
@@
 Whether down regulation of *A*~n~ and subsequent reductions of growth are quantitatively similar has rarely been tested.
-Based on these previous studies, using a range of container sizes as a sink-strength manipulation provdies a way to empirically test the extent to which growth and *A*~n~ are coordinated.
+Based on these previous studies, using a range of container sizes as a sink-strength manipulation provides a way to empirically test the extent to which growth and *A*~n~ are coordinated.
 
@@
 Increases in both final stem diameter and cumulative leaf area (both *P* < 0.001) were found with increasing soil volume.
-We did not find a continuous effect of container size; rathe, plant size was similar among smaller containers, and these differences were driven mainly by the largest container and the free seedling treatments.
+We did not find a continuous effect of container size; rather, plant size was similar among smaller containers, and differences were driven mainly by the largest container and the free seedling treatments.
 
@@
 
-##Modelling seedling biomass
+##Whole-plant C balance
 Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 25.7 %; with this LMF, the model predicted mean harvest total biomass of free seedlings within 1.0 %.
@@
 We addressed questions regarding the coordination of *A*~n~ and growth by complementing empirical results with a C mass balance model.
-We found that reductions in leaf *A*~n~ across container sizes, when integrated across the 120 day experiment, were alone insufficient to account for observed reductions in total plant biomass production.
+
+*Poorter review talks about water availability (rule out) temperature effects on soil volume (can rule out) nutrient availability (possible) root signaling (magic) but strangely, not carbohydrate feedback*
 
@@
 Low growth rates led to large reductions in biomass in small containers, compared to freely rooted seedlings.
-We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, consistent with the meta-analysis of Poorter et al.
+We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, close to the 43 % reported in the meta-analysis by Poorter et al.
 [-@poorter2012pot].
@@
 This observation initially suggests that sink limitation may be driving the down regulation of photosynthesis, and thus growth.
-However, there are several possible mechanisms that can explain reduced *A*~n~ in small containers including reduced water availability or nutrient content, or reduced sink strength [@poorter2012pot].
+However, there are several possible mechanisms that can explain reduced *A*~n~ in small containers including reduced water availability or nutrient content, increased soil temperatures, or reduced sink strength [@poorter2012pot].
 It was therefore necessary to examine each of these factors to determine the mechanism by which the induced belowground sink limitation triggered photosynthetic down regulation.
+In this study, the impacts of increasing soil temperatures with decreasing container sizes was controlled by burying of all containers flush to the soil surface.
 
@@
 The poor soil quality used in our experiment and root restriction, however, likely decreased the capacity of this morphological response to increase N uptake.
+*add exudation*
+Alternatively, root exudation may have increased with reduced rooting volumes to facilitate N uptake in favour of increasing partitioning to root biomass.
 
@@
 **Figure 6**.
-Total carbon mass for harvested and modeled seedlings versus predicted total carbon gain after 120 days (a) and  reductions in final seedling carbon mass, both modeled and observed, as a function of the reduction in leaf photosynthesis across treatments (b).
-For (a) the dashed 1:1 identifies the difference between net total leaf carbon gain and gross seedling production.
-For (b) both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.
+(a) Total C mass of harvested seedlings versus modelled net leaf carbon gain over 120 days.
+The dashed black line hows the 1:1 line and the dashed red line shows the seedling biomass that would be expected if all seedlings had the same carbon use efficiency as the freely grown seedling.
+(b) Carbon use efficiency (ration of final biomass to modelled net leaf C gain) of plants growth in different container sizes.
 

### 2016-06-15 manuscript/manuscript_pve.Rmd
BM edits

@@
 pvetab3 <- "3"
-pvetabS <- "S1"
 
@@
 ##Net carbon uptake model
-We developed a simple seedling growth model that utilized leaf *A*~n~ rates to allocate daily C assimilate towards biomass production of stems, leaves, fine roots and coarse roots.
-The model begins with mean initial tissue component biomass (leaf~0~, stem~0~ and root~0~) and a starting leaf area (L~0~) measured prior to planting.
-The initial biomass of roots was divided evenly between fine and coarse roots.
-The daily net biomass production of seedlings (*G*), from @makela1997carbon, is then given by
+The daily net C gain of seedlings (*G*), from @makela1997carbon, is given by
 
@@
 (1)
-$$G(t) = \frac{L~P~\sigma - R}{\epsilon}$$
+$$G(t) = L(P~\sigma - R)$$
 
-where *L* is modelled total plant leaf area (m^2^), *P* is the daily carbon assimilation per unit leaf area (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), $\epsilon$ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^).
-Total respiration was calculated as
+where *L* is modelled total plant leaf area (m^2^), *P* is the daily carbon assimilation per unit leaf area (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), and *R* is the mass based leaf respiration (g C d^-1^).
+Leaf respiration is included in the calculation of *P*.
 
 \
-(2)
-$$R(t) = R_\mathrm{s}M_\mathrm{s}~+~R_\mathrm{fr}M_\mathrm{fr}~+~R_\mathrm{cr}M_\mathrm{cr}$$
-
-where *R* is published or measured tissue respiration rates (g C g mass^-1^ d^-1^) of stems (s), fine roots (fr) and coarse roots (cr) and *M* is the modelled standing biomass for each tissue component (g).
-Leaf respiration is included in the calculation of *P*.
-The change in each tissue component biomass (*M*) on daily time steps, including leaves, stems, fine roots and coarse roots, is given by
-
-\
-(3)
-$$\frac{dM}{dt} = \theta~P(t)~-~(\Lambda~M)$$
-
-where $\theta$ is the component specific biomass partitioning to whole plant biomass (%) and $\Lambda$ is component specific turnover rate (yr^-1^).
-Because we did not observe branch turnover, $\Lambda$ of stems was assumed to equal 0.
-Total seedling biomass, per time step, was then equal to the sum of all biomass components; leaves, stems, fine roots and coarse roots.
-
-##Model parameters and simulations
-*P* was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *R* and *g*~1~) for each treatment and meteorological data from an onsite weather station.
-Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above), *R* was empirically measured and the *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values.
+*P* was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *R*~dark~ and *g*~1~) for each treatment and meteorological data from an onsite weather station.
+Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above), *R*~dark~ was empirically measured and the *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values.
 Methods of the coupled leaf gas exchange model are also described in Duursma et al [-@duursma2014peaked].
@@
 
-\
+*make sure this is correct, add CUE bit *
 We then used this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.
-First, a default model with mean photosynthetic parameters from the free seedlings was optimized to estimate a leaf mass fraction (LMF) which correctly predicted both the leaf mass and total biomass of the harvested free seedlings (*M*~free~).
-This optimized LMF was then used to constrain model runs with treatment-specific *P*, while keeping woody tissue respiration and tissue turnover parameters constant, to determine if changes in leaf *A*~n~ alone could predict biomass of seedlings in containers (*M*~pots~).
-Cumulative net leaf C gain for each treatment was equal to the sum of each value of *P* over 120 days and final seedling C was assumed to equal half of the final dry mass for both modeled and observed seedlings.
-Seedling biomass production was compared between model output and harvested seedlings with treatment-specific mean *P* by first scaling values to the free seedling control.
+Cumulative net leaf C gain for each treatment was equal to the sum of each value of *P* over 120 days and final seedling C was assumed to equal half of the final dry mass for observed seedlings.
 
@@
 These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
-It is possible that the overestimation of growth was due to an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *Vc*~max~, *R* and *g*~1~) make this unlikely.
+It is possible that the overestimation of growth was due to an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *Vc*~max~, *R*~dark~ and *g*~1~) make this unlikely.
 Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A*~n~ affect models which distinguish the fate of assimilate C within a plant.
@@
 Each value reflects the mean (&pm; 1 standard error) for each treatment.
-*A*~max~, *R* and *g*~s~ are each measured at 25 &deg;C.
+*A*~max~, *R*~dark~ and *g*~s~ are each measured at 25 &deg;C.
 Values of *A*~max~, *g*~s~ and *g*~1~ represent overall means across measurement campaigns (n=6).
@@
                         "*A*~max~ ($\\mu$mol m^-2^ s^-1^)", 
-                        "R ($\\mu$mol m^-2^ s^-1^)",
+                        "*R*~dark~ ($\\mu$mol m^-2^ s^-1^)",
                         "*J*~max~ ($\\mu$mol m^-2^ s^-1^)",
@@
 The marginal *R*^2^ (fixed effects only) was 0.37 and the conditional *R*^2^ (fixed and random effects) was 0.48 for the complete model.
+The equation for the full model is y = 28.58(N) - 3.31(Starch) - 0.87(N*Starch) - 221.96.
 
@@
 
-# Supporting Information {.unnumbered}
-
-**Table S1**.Seedling growth model default parameters.
-```{r tabels1, echo=FALSE, warning=FALSE}
-dust(modeltable)%>%
-  sprinkle(rows= 1, part="head",bold=TRUE)%>%
-  sprinkle_print_method("markdown")
-```
-
 # Acknowledgements

### 2016-06-16 manuscript/manuscript_pve.Rmd
BM edits

@@
 (a) Total C mass of harvested seedlings versus modelled net leaf carbon gain over 120 days.
-The dashed black line hows the 1:1 line and the dashed red line shows the seedling biomass that would be expected if all seedlings had the same carbon use efficiency as the freely grown seedling.
-(b) Carbon use efficiency (ration of final biomass to modelled net leaf C gain) of plants growth in different container sizes.
+The dashed black line shows the 1:1 line and the dotted black line shows the seedling biomass that would be expected if all seedlings had the same carbon use efficiency as the freely grown seedling.
+(b) Ratio of final biomass to modelled net leaf C gain of plants growth in different container sizes.
 

### 2016-06-16 clean Scripts/cue.R

@@ -1,110 +1,0 @@
-source("functions and packages/startscripts.R")
-###CUE bar plot
-
-##use modelled C net and gross to determine respiration
-##use harvest mass + respiration + unaccounted as fractions of total gross
-
-##read data-----------------------------------------------------------------------------------------------------------------
-finalmass <- read.csv("calculated data/harvest_mass_means.csv")
-
-la_pred <- read.csv("Calculated data/LApred_volume.csv")
-  names(la_pred)[3] <- "LA"
-  la_pred$Date <- as.Date(la_pred$Date)
-
-Cday_net <- read.csv("calculated data/Aleaf_model/cday_120_clean.csv")
-  Cday_net$Date <- as.Date(Cday_net$Date)
-  
-Cday_gross <- read.csv("calculated data/Aleaf_model/cday_120_clean_gross.csv")
-  Cday_gross$Date <- as.Date(Cday_gross$Date)
-
-##Cday with leaf area needs self shading (use slope intercept, from 5-1000 vol)
-sigma <- read.csv("calculated data/M_leafarea_model.csv")
-
-##function to generate total plant daily C gain
-modelledC_func <- function(leafarea, shading, Cday){ #leafarea dfr, self shading dfr, and modelled C gain (gm2)
-  dailyCnet <- merge(leafarea,Cday)
-  ##this needs to include self shadeing (M as a linear function of leaf area)
-  dailyCnet <- merge(dailyCnet, shading[, c(2,3,5)], by="volume")
-    dailyCnet$M <- with(dailyCnet, b*LA+intercept)
-    #calculate total daily C gain with self shading
-    dailyCnet$tdcg <- with(dailyCnet, LA * carbon_day * M)
-  print("successfully calculated total daily carbon with modelled Cgain, leaf area and self shading")
-  
-    dailyCnet$volume <- as.factor(dailyCnet$volume)
-  return(dailyCnet)
-}
-
-##calculate net and gross C gain, then quantify leaf respiration--------------------------------------------------------------
-dailyCnet <- modelledC_func(la_pred, sigma, Cday_net)
-  names(dailyCnet)[8] <- "tdc_net"
[…]

### 2016-06-16 master_scripts/massmodel_optimize.R

@@ -153,8 +153,7 @@ write.csv(biomass_time, "calculated data/biomass_time.csv", row.names=FALSE)
   plot(0.5*mass_actual$mass ~ totalC_trt2,pch=pchs,col=palette(),cex=1.6, xlim=c(0, 200),
        ylim=c(0, 200), ylab="Seedling Mass (g C)", xlab="Net Total Leaf Carbon Gain (g C)")
   segments(x0=min(plantC2$totalC_trt2), x1=max(plantC2$totalC_trt2),y0=min(plantC2$netCgain), y1=max(plantC2$netCgain), 
-           lwd=3, lty=3, col="black")
-  # lines(netCgain ~ totalC_trt2, data= plantC2,col="black", lwd=2, lty=3)
+           lwd=3, lty=3, col="darkblue")
   abline(0,1, lwd=2, lty=2, col="grey35")
   text(0,195,"(a)", cex=1.2)
 

### 2016-06-16 manuscript/manuscript_pve.Rmd
bm edits

@@
 It is instead possible that lateral root development is affected by inanimate obstacles and avoiding growth towards container walls may improve resource gain [@falik2005root].
+Root exudation may have increased with reduced rooting volumes to facilitate N uptake in favour of increasing partitioning to root biomass.
 The sensitivity of roots to their own exudates near obstructions may also prevent further growth [@semchenko2008foraging].
@@
 The poor soil quality used in our experiment and root restriction, however, likely decreased the capacity of this morphological response to increase N uptake.
-*add exudation*
-Alternatively, root exudation may have increased with reduced rooting volumes to facilitate N uptake in favour of increasing partitioning to root biomass.
 
@@
 (a) Total C mass of harvested seedlings versus modelled net leaf carbon gain over 120 days.
-The dashed black line shows the 1:1 line and the dotted black line shows the seedling biomass that would be expected if all seedlings had the same carbon use efficiency as the freely grown seedling.
+The dashed black line shows the 1:1 line and the dotted blue line shows the seedling biomass that would be expected if all seedlings had the same carbon use efficiency as the freely grown seedling.
 (b) Ratio of final biomass to modelled net leaf C gain of plants growth in different container sizes.

### 2016-06-17 manuscript/manuscript_pve.Rmd
added cites and edits from BM

@@
 However, reductions in *A*~n~ have also been attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
-This lack of continuity among findings is not surprising, as we still know little about the balance between assimilation, storage and growth across temporal scales in plants [@smith2007coordination].
-As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to the occurrence of large fruiting sinks, they tell us little about source-sink coordination in typical growing conditions for woody species.
+*In addition, it is unclear whether these impacts on An can fully explain the resulting impacts on growth, (?
+Has anyone attempted to determine this?
+Is there any evidence for impacts on respiration??)*
 
@@
 However, they were unable to determine the physiological mechanism  driving the downregulation of *A*~n~, nor to test whether the reduction in *A*~n~ could explain the observed reduction in growth.
-
-*delete bellow*
-This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower assimilation rates [@robbins1988effect].
-However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].
-Whether down regulation of *A*~n~ and subsequent reductions of growth are quantitatively similar has rarely been tested.
-Based on these previous studies, using a range of container sizes as a sink-strength manipulation provides a way to empirically test the extent to which growth and *A*~n~ are coordinated.
 
@@
 tereticornis*) use the center of the container as the medium for thick roots, leaving the periphery of the soil as the most active sites for fine root proliferation [@biran1980a; @biran1980b].
-By using a species with tap root growth and manipulations of container length rather than width, we believed that a more realistic test of growth inhibition through constrained soil volume would be achieved.
+By using a species with taproot growth and manipulations of container length rather than width, we believed that a more realistic test of growth inhibition through constrained soil volume would be achieved.
 
@@
 
-##Net carbon uptake model
+##Modelled net seedling C uptake
 The daily net C gain of seedlings (*G*), from @makela1997carbon, is given by
@@
 ##Whole-plant C balance
+*this needs to reflect C gain vs mass*
 Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 25.7 %; with this LMF, the model predicted mean harvest total biomass of free seedlings within 1.0 %.
@@
 This study utilized a novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
-Our goal was to identify how sink limitation of growth modified the carbon balance of seedlings.
+Our goal was to identify how sink limitation of growth modified the C balance of seedlings.
 We found a strong reduction of growth in containerized plants.
-Leaf *A*~n~ was also strongly reduced, but this reduction was insufficient to fully explain the reduction in growth, implying that whole-plant respiratory loss was likely affected as well.
-
-We addressed questions regarding the coordination of *A*~n~ and growth by complementing empirical results with a C mass balance model.
-
-*Poorter review talks about water availability (rule out) temperature effects on soil volume (can rule out) nutrient availability (possible) root signaling (magic) but strangely, not carbohydrate feedback*
+Leaf *A*~n~ was also strongly reduced, but this reduction was insufficient to fully explain the reduction in growth, implying that components such as whole-plant respiratory loss were also likely affected.
 

### 2016-07-08 manuscript/thesis/thesis_pve.Rmd
made thesis folder in manuscripts
added make figures script

--- 2016-05-30 manuscript/thesis_pve.Rmd
@@
 Combined these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment.
-Soil N at harvest was not different across soil volumes ($\bar{x}$ = 4.5 %), with minimal decreases from pre-planting value ($\bar{x}$ = 4.9 %).
+Soil N at harvest was not different across soil volumes ($\bar{x}$ = .045 %), with minimal decreases from pre-planting values ($\bar{x}$ = .049 %).
 This indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
@@
 The poor soil quality used in our experiment and root restriction, however, likely decreased the capacity of this morphological response to increase N uptake.
+Alternatively, root exudation may have increased with reduced rooting volumes to facilitate N uptake in favour of increasing partitioning to root biomass.
 

### 2016-07-08 manuscript/make_figures.R

@@ -1,0 +1,22 @@
+to_pdf <- function(expr, filename, ..., verbose=TRUE) {
+  if(!file.exists(dirname(filename)))
+    dir.create(dirname(filename), recursive=TRUE)
+  if ( verbose )
+    cat(sprintf("Creating %s\n", filename))
+  pdf(filename, ...)
+  on.exit(dev.off())
+  eval.parent(substitute(expr))
+}
+
+
+source("functions and packages/startscripts.R")
+
+
+fn <- function(...)file.path("manuscript",...)
+
+to_pdf(source("master_scripts/allometryplotting.R"), fn("Figure1.pdf"), width=6, height=7.8)
+to_pdf(source("master_scripts/airvars_plotting.R"), fn("Figure2.pdf"), width=6, height=8)
+to_pdf(source("master_scripts/allocation_plotting.R"), fn("Figure3.pdf"), width=6, height=8)
+to_pdf(source("master_scripts/A_stats_plotting.R"), fn("Figure4.pdf"), width=6, height=6)
+to_pdf(source("master_scripts/Amax_TNC_N_plotting2.R"), fn("Figure5.pdf"), width=8, height=6)
+to_pdf(source("master_scripts/massmodel_optimize.R"), fn("Figure6.pdf"), width=6, height=8)

### 2016-07-08 manuscript/manuscript_pve.Rmd
bm edits to manuscript

@@
 
-In the absence of a good understanding of the effects of sink limitation on physiological processes, most attempts to model sink limitation of growth to date have done so by abandoning the principle of mass balance *(e.g.
-Leuzinger; CLM nutrient limitation; Fatichi)*.
+In the absence of a good understanding of the effects of sink limitation on physiological processes, most attempts to model sink limitation of growth to date have done so by abandoning the principle of mass balance [e.g.
+@fatichi2013reconciling; @fatichi2014moving].
 This approach is unsatisfactory because mechanistic models should obey the laws of physics.
+Growth models must take into account several simultaneous processes affecting the C balance at any given time [@fourcaud2008plant], thus incomplete modelling approaches often lead to unaccounted for C.
 Our goal in this paper was to investigate how the carbon balance of plants is modified by sink limitation, by experimentally imposing a sink limitation to growth.
-
-*also deleted below 2 sentences*
-As plant growth cannot be simply determined by *A*~n~, growth models must take into account several simultaneous processes affecting the C balance at any given time [@fourcaud2008plant].
-Whether growth limitation in woody species is driven mostly by *A*~n~ or other components of the C balance remains largely uncertain.
 
@@
 Elevated CO~2~ causes an increase in leaf-level photosynthetic rate, *A*~n~ [@drake1997more; @ainsworth2007response].
-While this increase is often observed to drive an increase in plant biomass production (eg any number of papers),
-
-across four forest Free-Air CO~2~ Enrichment (FACE) experiments this increased photosynthetic uptake resulted in a stimulation of biomass production by 23 % on average [@norby2005forest].
+This increased photosynthetic uptake is often observed to drive an increase in plant biomass production [@norby2005forest].
 Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does].
+This implies that other process of tree C balance must be affected, which has been noted in CO~2~ manipulation studies that attempt to close the C budget [@wang1998carbon; @hamilton2002forest; @schafer2003exposure].
 
@@
 In these experiments, compensatory increases in *A*~n~ of the remaining foliage are commonly found, and have been attributed to several processes including indirect effects on resource availability, such as increaed stomatal conductance [@layne1995end] or enhanced leaf nutrient status [@turnbull2007increased; @pinkard2011gas], or more direct effects of modified sink-source balance such as, reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end;@pinkard2011gas], and regulatory sugar signaling [@eyles2013whole].
-However, there have been few attempts *(any??)* to determine the overall C balance in these experiments, and it is unclear whether the change in growth following defoliation can be explained by the reduction in leaf area and changes to A~n~
-
-Similar to elevated CO~2~ experiments, these increases in *A*~n~ in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a].
-These manipulations of C source activity demonstrate that changes in *A*~n~ do not always correspond with proportional responses of growth.
+Similar to elevated CO~2~ experiments, these increases in *A*~n~ in defoliation experiments do not increase tree growth [@palacio2012fast; @markkola2004defoliation; @ovaska1993a].
+As these studies do not attempt to scale the degree of compensentory response in leaf C gain to the entire canopy, the overall affect of source manipulation on tree C balance and growth is still unclear.
 
@@
 However, reductions in *A*~n~ have also been attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis].
-*In addition, it is unclear whether these impacts on An can fully explain the resulting impacts on growth, (?
-Has anyone attempted to determine this?
-Is there any evidence for impacts on respiration??)*
+Similar to C source manipulations, it is still unclear whether these impacts on *A*~n~ can fully explain the resulting impacts on growth.
 
@@
 Poorter et al.
-[-@poorter2012pot] examined the components of relative growth rate and found the unit leaf rate to be most strongly affected.
+[-@poorter2012pot] examined the components of relative growth rate and found the unit leaf rate to be most strongly affected by rooting volume.
 As unit leaf rate is correlated with *A*~n~, they concluded that down-regulation of *A*~n~ may best explain the effects of container size on biomass growth.
@@
 This observation initially suggests that sink limitation may be driving the down regulation of photosynthesis, and thus growth.
-However, there are several possible mechanisms that can explain reduced *A*~n~ in small containers including reduced water availability or nutrient content, increased soil temperatures, or reduced sink strength [@poorter2012pot].
+However, there are several possible mechanisms that can explain reduced *A*~n~ in small containers including increased soil temperatures, reduced water availability or nutrient content, or reduced sink strength [@poorter2012pot].
 It was therefore necessary to examine each of these factors to determine the mechanism by which the induced belowground sink limitation triggered photosynthetic down regulation.
@@
 As starch content in leaves of plants grown in the smallest containers was nearly double that of free seedlings in our study, this suggests the response of *A*~n~ to sink inhibition was regulated by this accumulation, as hypothesized.
+Overall, it is likely that both nutrient content and reduced sink strength played a role in observed photosynthetic down regulation, but future studies are needed to identify the specific mechanisms which prommpted these feedbacks.
 
@@
 In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, once ontogenetic drift was taken into account (Figure `r allocfig`a,b).
-This result is unexpected as shifts in partitioning have been noted specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein].
-Surprisingly, a constant ratio of fine root mass to leaf mass was observed across all treatments suggesting a functional partitioning response to optimize resource gain did not occur.
+Although shifts in partitioning have been previosuly reported, specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein], a constant ratio of fine root mass to leaf mass was observed in this study across all treatments.
+These results suggest that seedlings kept a conservative strategy to maintain homeostatis with with biomass partitioning, instead of a functional partitioning response to optimize limiting soil resources.
 
@@
 This finding is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants is seldom studied.
-Although biomass partitioning was conserved, our empirical and model results suggest that the amount of photosynthate allocated to non-biomass pools were likely altered by sink inhibition.
-The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role].
+As seedlings maintained a conservative partitioning strategy, aboveground biomass was restricted in coordination with root restriction from limited soil volume.
+Photosynthesis was affected by both reduced nutrient uptake and the buildup of starch, both potential mechanism for downregulation of *A*~n~.
 Our combined empirical and modeling approach shows that when non-photosynthetic parameters were kept constant, changes in *A*~n~ were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
 It has been suggested that tissue sink activity strongly feedbacks onto source activity, causing growth to control *A*~n~ through the demand for C [@korner2013growth; @korner2015paradigm].
-Although this may be true, our results imply that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate.
-The approach used here has the flexibility to account for multiple drivers of C allocation and provides an avenue to address future questions regarding the impact of environmental change on plant growth.
+Our results imply that testing this hypothesis requires accurate modelling of C mass balance before addressing this debate.
 

### 2016-07-08 manuscript/manuscript_pve.Rmd
improved RMD knitting with make pdfs and preload scripts

@@
 6 figures (5 color), 3 tables
-\
-Supporting information: 1 table
 
@@
 
-```{r install packages, echo=FALSE, message=FALSE, warning=FALSE,results="hide"}
-#install packages if not already installed
-.packages = c("RColorBrewer", "doBy", "sciplot", "plyr","nlme", "multcomp", "plantecophys", "scales","smatr","plotrix",
-                           "lme4", "lmerTest", "broom", "reporttools", "visreg", "pixiedust", "lubridate", "reshape",
-              "magicaxis", "effects")
-
-# Install CRAN packages (if not already installed)
-.inst <- .packages %in% installed.packages()
-if(length(.packages[!.inst]) > 0) install.packages(.packages[!.inst], repos = "http://cran.at.r-project.org")
-
-# Load packages into session
-lapply(.packages, library, character.only=TRUE)
-
-```
-
 ```{r global data/sourcing, echo=FALSE, message=FALSE, warning=FALSE}
@@
 includeFigs <- TRUE
+```
 
-source("functions and packages/startscripts.R")
-source("functions and packages/gamplotfunctions.R")
+```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
 
-#table data
-table1 <- read.csv("master_scripts/pve_table1.csv")
-table2 <- read.csv("master_scripts/root_table.csv")
-table3 <- read.csv("master_scripts/pve_table2.csv")
-modeltable <- read.csv("master_scripts/modeltable.csv")
+source("manuscri[t/manuscript_preload.R")
+
+# Make figure PDFs.
+source("manuscript/make_figures.R")
 
@@
 
-*make sure this is correct, add CUE bit *
+*make sure this is correct, add CUE bit*
 We then used this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.

### 2016-07-08 manuscript/manuscript_preload.R
cleaned plotting scripts
deleted model table as we no longer use it

@@ -9,11 +9,14 @@ pacman::p_load(RColorBrewer, doBy, sciplot, plyr,nlme, multcomp, plantecophys, s
                magicaxis, effects)
 
 
-source("functions and packages/startscripts.R")
+source("functions and packages/load packages.R")
+source("functions and packages/functions.R")
+source("functions and packages/plot objects.R")
+
 source("functions and packages/gamplotfunctions.R")
 
 #table data
 table1 <- read.csv("master_scripts/pve_table1.csv")
 table2 <- read.csv("master_scripts/root_table.csv")
 table3 <- read.csv("master_scripts/pve_table2.csv")
-modeltable <- read.csv("master_scripts/modeltable.csv")
+

### 2016-07-08 master_scripts/A_stats_plotting.R

@@ -120,15 +120,4 @@ bar(Photo, volume, PSsat_ID,half.errbar=FALSE, xlab="Soil Volume  (l)",ylab="", 
     col="grey", legend=FALSE, bg="white")
 title(ylab=satlab, mgp=ypos)
 text(c(.7,1.9,3.1,4.3,5.5,6.75,7.9), 10, sl2, cex=1.3)
-#dev.copy2pdf(file= "master_scripts/manuscript_figs/Asat.pdf")
-#dev.off()
 
-
-###png
-# png(filename = "master_scripts/manuscript_figs/png/asat.png", width = 11, height = 8.5, units = "in", res= 400)
-# par(cex.axis=1.5,cex.lab=1.5 ,las=1)
-# bar(Photo, volume, PSsat_ID,half.errbar=FALSE, xlab="Soil Volume  (l)",ylab="", ylim=c(0,25), names.arg = leglab,
-#     col="grey", legend=FALSE, xpd=TRUE,mar=c(5,5,2,2))
-# title(ylab=satlab, mgp=ypos)
-# text(c(.7,1.9,3.1,4.3,5.5,6.75,7.9), 10, SigLetters, cex=1.3)
-#  dev.off()

### 2016-07-08 master_scripts/Amax_TNC_N_plotting2.R

@@ -106,5 +106,3 @@ plot(A_mass ~ nitro_mg, data=photo_chem, type='n',ylab="", axes=FALSE, xlim=c(0,
   mtext(nitromasslab, side=1, cex=1.2, line=3.5)
   legend("bottomright", binlab, pch=21, text.font=1, inset=0.02, pt.bg=coln2,title="Leaf Starch (%)" , bty='n', cex=1)
 
-# dev.copy2pdf(file= "master_scripts/manuscript_figs/A_leafchem.pdf")
-#dev.off()

### 2016-07-08 master_scripts/allocation_plotting.R

@@ -93,6 +93,4 @@ with(ratio_agg, arrows(x0=log10(fineroot.mean), y0=log10(leafmass.mean), y1=log1
                        length=0.05,col=palette(), lwd=1))
 magaxis(side=c(1,2), unlog=c(1,2), frame.plot=TRUE)
 
-# dev.copy2pdf(file= "master_scripts/manuscript_figs/massfractions.pdf")
-# dev.off()
 

### 2016-07-08 master_scripts/allometryplotting.R

@@ -75,66 +75,3 @@ with(leafarea_time, arrows(Date, canopysqm.mean, Date, canopysqm.mean-canopysqm.
 d_ply(leafarea_time, .(volume), function(x) points(x$canopysqm.mean ~ x$Date,  
                                                    col=x$volume, pch = pchs[x$volume],cex=2))
 text(x=15855, .65, "(c)", cex=1.51)
-
-
-# dev.copy2pdf(file= "master_scripts/manuscript_figs/allometry.pdf")
-# dev.off()
-
-
-####png 
-# png(filename = "master_scripts/manuscript_figs/png/height.png", width = 11, height = 8.5, units = "in", res= 400)
-# par(mar=c(5,5,2,2), cex.axis=1.5,cex.lab=1.75 ,las=1)
-# 
-# plot(height.mean ~ Date, data=height_agg,type='n',ylab=expression(Height~~(cm)),  
-#      ylim=c(20,135), axes=FALSE, xlab="", xlim=xlimdays)  
-# axis.Date(1, at=xAT, labels=TRUE)
-# axis(2, labels=TRUE, at=c(0,20,40,60,80,100,120))  
-# 
-# 
-# with(height_agg, arrows(Date, height.mean, Date, height.mean+height.se, angle=90, col=palette(),length=0.03, cex=2))
-# with(height_agg, arrows(Date, height.mean, Date, height.mean-height.se, angle=90, col=palette(),length=0.03, cex=2))
-# points(height.mean ~ Date, data=height_agg,pch=pchs[volume], cex=2, col = volume)      
-# box()
-# legend("topleft", leglab, pch=c(rep(16,6),17),text.font=1.2, inset=0.025, title=vollab, 
-#        cex=1.51, col=palette(), bty='n')
-# 
-# dev.off()
-# 
-# png(filename = "master_scripts/manuscript_figs/png/diam.png", width = 11, height = 8.5, units = "in", res= 400)
-# par(mar=c(5,5,2,2), cex.axis=1.5,cex.lab=1.75 ,las=1)
-# 
-# plot(diameter.mean ~ Date, data=diam_agg, type='n',ylab=expression(Diameter~~(mm)),ylim=c(0,17), 
-#      axes = FALSE, xlab="",xlim=xlimdays)
-# axis.Date(1, at=xAT, labels=TRUE)  
-# axis(2)     
-# 
[…]

### 2016-07-09 manuscript/manuscript_pve.Rmd
cleaned plotting scripts
deleted model table as we no longer use it
new cue figure, not in folder yet
new results from modelled C gain and CUE

bolded discussion for remko to look at, probably need to delete

@@
 
-```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
+```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
 
-source("manuscri[t/manuscript_preload.R")
+source("manuscript/manuscript_preload.R")
 
@@
 For the growth model, $\sigma$ was then predicted for each daily time step using the previous days cumulative leaf area and this value was then applied to *P*.
-All default parameters used in model simulations are reported in Table `r pvetabS`.
 
-*make sure this is correct, add CUE bit*
-We then used this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.
+\
+We used the model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.
 Cumulative net leaf C gain for each treatment was equal to the sum of each value of *P* over 120 days and final seedling C was assumed to equal half of the final dry mass for observed seedlings.
+We then compared seedling carbon use efficiency (CUE) across treatments, as the proportion of modelled cumulative net leaf C gain allocated to observed seedling biomass.
 
@@
 ##Whole-plant C balance
-*this needs to reflect C gain vs mass*
-Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 25.7 %; with this LMF, the model predicted mean harvest total biomass of free seedlings within 1.0 %.
-Using this optimized LMF, the modeled total biomass of seedlings for each soil volume treatment (*M*~pots~) was on average 11&pm;2.3 g C more than measured seedling biomass when compared against predicted total net leaf C gain (Figure `r massmodelfig`a).
-As a result, seedling C mass was overestimated by an average of 45&pm;6.2 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b).
-As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the container size treatments.
+Modelled cumulative net leaf C gain over 120 days varied two-fold across containers sizes (25.6 - 55.1 g C).
+The free seedling control had five-fold greater modelled total C gain than the average of container treatments (213.6 - 42.7&pm;8.2 g C).
+For seedlings in containers, an average of 67 &pm;0.01 % of modelled C gain was not allocated to biomass, compared to 59.2 % for the free seedling control (Figure `r massmodelfig`a).
+Consequently, the average CUE of containerized seedlings (32&pm;0.01 %) was lower than the free seedling control (40.8 %) (Figure `r massmodelfig`b).
+As a result, the observed reductions in leaf *A*~n~ with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the container size treatments.
 
@@
 ##Do reductions in photosynthesis explain reductions in seedling growth?
-Our model used a simple approach to drive seedling growth with measured reductions in leaf *A*~n~ , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes.
-Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.
-Although reductions in both *A*~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
+Our model used a simple approach to estimate cumulative seedling C gain with measured reductions in leaf *A*~n~ , via soil volume effects.
+*while treating C use efficiency, respiration and C allocation as fixed processes*.
+*Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.* Although reductions in both *A*~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
 [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth.
-These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
-It is possible that the overestimation of growth was due to an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *Vc*~max~, *R*~dark~ and *g*~1~) make this unlikely.
+These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and *processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].* It is possible that the overestimation of growth was due to an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *Vc*~max~, *R*~dark~ and *g*~1~) make this unlikely.
 Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A*~n~ affect models which distinguish the fate of assimilate C within a plant.
@@
 Our modelling results reveal that other components of the C balance, beyond *A*~n~, are required to explain the observed seedling biomass response to sink manipulation.
-This discrepancy is noteworthy, as partial accounting of the different mechanisms involved in plant carbon balance can lead to erroneous conclusions [@valentini2000respiration].
-For example, the fraction of photosynthate used in respiration is known to vary depending on species and local environmental conditions [@Lambers2008], yet is often considered a static parameter in process based growth models.
-The use of fixed rates of respiration in our model likely underestimates seedling responses to sink limitation.
-Thus, our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
+This discrepancy is noteworthy, as partial accounting of the different mechanisms involved in plant C balance can lead to erroneous conclusions [@valentini2000respiration].*For example, the fraction of photosynthate used in respiration is known to vary depending on species and local environmental conditions [@Lambers2008], yet is often considered a static parameter in process based growth models.
+The use of fixed rates of tissue respiration in our model likely underestimates seedling responses to sink limitation.* Thus, our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
 Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A*~n~ and the fate of C allocated to growth, respiration and C storage in leaves.

### 2016-07-09 cue.R

@@ -1,0 +1,55 @@
+source("functions and packages/startscripts.R")
+
+##use modelled C net and gross to determine respiration
+##use harvest mass + respiration + unaccounted as fractions of total gross
+
+##read data-----------------------------------------------------------------------------------------------------------------
+finalmass <- read.csv("calculated data/harvest_mass_means.csv")
+
+la_pred <- read.csv("Calculated data/LApred_volume.csv")
+   names(la_pred)[3] <- "LA"
+   la_pred$Date <- as.Date(la_pred$Date)
+   
+Cday_net <- read.csv("calculated data/Aleaf_model/cday_120_clean.csv")
+   Cday_net$Date <- as.Date(Cday_net$Date)
+  
+Cday_gross <- read.csv("calculated data/Aleaf_model/cday_120_clean_gross.csv")
+    Cday_gross$Date <- as.Date(Cday_gross$Date)
+    
+##Cday with leaf area needs self shading (use slope intercept, from 5-free vol)
+sigma <- read.csv("calculated data/M_leafarea_model.csv")
+      
+##function to generate total plant daily C gain-----------------------------------------------------------------------------
+modelledC_func <- function(leafarea, shading, Cday){ #leafarea dfr, self shading dfr, and modelled C gain (gm2)
+          dailyCnet <- merge(leafarea,Cday)
+            ##this needs to include self shadeing (M as a linear function of leaf area)
+            dailyCnet <- merge(dailyCnet, shading[, c(2,3,5)], by="volume")
+                dailyCnet$M <- with(dailyCnet, b*LA+intercept)
+            #calculate total daily C gain with self shading
+            dailyCnet$tdcg <- with(dailyCnet, LA * carbon_day * M)
+              print("successfully calculated total daily carbon with modelled Cgain, leaf area and self shading")
+
+            dailyCnet$volume <- as.factor(dailyCnet$volume)
+              return(dailyCnet)
+            }
+
+##calculate net and gross C gain, then quantify leaf respiration--------------------------------------------------------------
+dailyCnet <- modelledC_func(la_pred, sigma, Cday_net)
+    names(dailyCnet)[8] <- "tdc_net"
+    names(dailyCnet)[4] <- "cday_net"
+    
+dailyCgross <- modelledC_func(la_pred, sigma, Cday_gross)
[…]

### 2016-07-09 manuscript/manuscript_pve.Rmd
added intro point

@@
 the amount of carbon that the plants are able to utilize in growth.
+This debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role; @korner2015paradigm].
 To be able to predict plant growth responses to environmental change, we need models that can account for both source and sink limitation.
@@
 **Figure 6**.
-(a) Total C mass of harvested seedlings versus modelled net leaf carbon gain over 120 days.
+(a) Total carbon mass of harvested seedlings versus modelled net leaf carbon gain over 120 days.
 The dashed black line shows the 1:1 line and the dotted blue line shows the seedling biomass that would be expected if all seedlings had the same carbon use efficiency as the freely grown seedling.

### 2016-07-11 manuscript/manuscript_pve.Rmd
manuscript revisions from BM, cleaned repo

@@
 \
-Summary: 200
+Summary: 
 \
@@
 \
-Acknowledgements: 30
+Acknowledgements: 
 \
@@
 # Set Flag to include figures in text or not.
-includeFigs <- TRUE
+includeFigs <- FALSE
 ```
@@
 achemfig <- "5"
-massmodelfig <- "6"
+cuefig <- "6"
 
@@
 
-- We manipulated soil volume to impose sink limitation of growth in Eucalyptus tereticornis seedlings.
+- We manipulated soil volume to impose sink limitation of growth in *Eucalyptus tereticornis* seedlings.
 Seedlings were grown in containers of different sizes and planted flush to the soil alongside freely-rooted seedlings.
@@
 Photosynthetic capacity was significantly reduced in containerized seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
-However, the reduction in net leaf photosynthesis over the growth period was insufficient to explain the reduction in growth, so that we also observed a reduction in whole-plant carbon use efficiency (CUE) with container size.
+However, the reduction in net leaf photosynthesis over the growth period was insufficient to explain the reduction in growth, so that we also observed a reduction in whole-plant C use efficiency (CUE) with container size.
 
@@
 The source-sink limitation paradigm for plant growth argues that growth may be limited either by source activity, i.e.
-the amount of carbon that the plants are able to take up through photosynthesis, or by sink strength, i.e.
+the amount of carbon (C) that the plants are able to take up through photosynthesis, or by sink strength, i.e.
 the amount of carbon that the plants are able to utilize in growth.
@@
 
-Most current models of plant growth are based on the physical principle of mass balance: carbon (C) entering the plant through photosynthesis must be balanced by C loss to respiration and C allocation to growth and storage.
+\
+Most current models of plant growth are based on the physical principle of mass balance: C entering the plant through photosynthesis must be balanced by C loss to respiration and C allocation to growth and storage.
 Plant growth is thus predicted as the outcome of the processes of photosynthesis, respiration and allocation.
@@
 It is less easy to know how to implement sink limitation of growth in such models, because it requires that we know whether, and how, sink limitation influences the contributing processes of photosynthesis, respiration and allocation.
-It has been suggested that sink limitation affects the carbon balance by causing a down-regulation of photosynthetic rate, possibly mediated by carbohydrate accumulation (refs), but there is also evidence that photosynthesis and growth are decoupled under sink limitation (refs), suggesting that other processes must also be affected.
+It has been suggested that sink limitation affects the C balance by causing a down-regulation of photosynthetic rate, possibly mediated by carbohydrate accumulation (refs), but there is also evidence that photosynthesis and growth are decoupled under sink limitation (refs), suggesting that other processes must also be affected.
 
+\
 In the absence of a good understanding of the effects of sink limitation on physiological processes, most attempts to model sink limitation of growth to date have done so by abandoning the principle of mass balance [e.g.
@@
 Growth models must take into account several simultaneous processes affecting the C balance at any given time [@fourcaud2008plant], thus incomplete modelling approaches often lead to unaccounted for C.
-Our goal in this paper was to investigate how the carbon balance of plants is modified by sink limitation, by experimentally imposing a sink limitation to growth.
+Our goal in this paper was to investigate how the C balance of plants is modified by sink limitation, by experimentally imposing a sink limitation to growth.
 
@@
 In partial defoliation experiments, source activity is decreased by reduction of photosynthesizing leaf area.
-In these experiments, compensatory increases in *A*~n~ of the remaining foliage are commonly found, and have been attributed to several processes including indirect effects on resource availability, such as increaed stomatal conductance [@layne1995end] or enhanced leaf nutrient status [@turnbull2007increased; @pinkard2011gas], or more direct effects of modified sink-source balance such as, reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end;@pinkard2011gas], and regulatory sugar signaling [@eyles2013whole].
+In these experiments, compensatory increases in *A*~n~ of the remaining foliage are commonly found, and have been attributed to several processes including indirect effects on resource availability, such as increased stomatal conductance [@layne1995end] or enhanced leaf nutrient status [@turnbull2007increased; @pinkard2011gas], or more direct effects of modified sink-source balance such as, reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end;@pinkard2011gas], and regulatory sugar signaling [@eyles2013whole].
 Similar to elevated CO~2~ experiments, these increases in *A*~n~ in defoliation experiments do not increase tree growth [@palacio2012fast; @markkola2004defoliation; @ovaska1993a].
-As these studies do not attempt to scale the degree of compensentory response in leaf C gain to the entire canopy, the overall affect of source manipulation on tree C balance and growth is still unclear.
+As these studies do not attempt to scale the degree of compensatory response in leaf C gain to the entire canopy, the overall affect of source manipulation on tree C balance and growth is still unclear.
 
@@
 Inadequate rooting volume can decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root].
-In a comprehensive meta-analysis, Poorter et al.
-[-@poorter2012pot] demonstrated a large effect of container size on plant biomass accumulation.
+In a comprehensive meta-analysis, Poorter *et al.* [-@poorter2012pot] demonstrated a large effect of container size on plant biomass accumulation.
 Photosynthetic down-regulation is generally observed in these studies [e.g.
 @arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
-Poorter et al.
-[-@poorter2012pot] examined the components of relative growth rate and found the unit leaf rate to be most strongly affected by rooting volume.
+Poorter *et al.* [-@poorter2012pot] examined the components of relative growth rate and found the unit leaf rate to be most strongly affected by rooting volume.
 As unit leaf rate is correlated with *A*~n~, they concluded that down-regulation of *A*~n~ may best explain the effects of container size on biomass growth.
@@
 We tracked leaf-level gas exchange, leaf carbohydrate accumulation and seedling allometry over the course of 4 months.
-We drove a simple whole-plant photosynthesis model with measured leaf gas exchange and interpolated leaf area data to estimated net canopy carbon uptake over the experimental period, and compared the result with total seedling biomass.
+We drove a simple whole-plant photosynthesis model with measured leaf gas exchange and interpolated leaf area data to estimated net canopy C uptake over the experimental period, and compared the result with total seedling biomass.
 We anticipated that both photosynthesis and growth would be reduced under belowground sink limitation.
 The principal questions that we addressed were: Firstly, which physiological process best explains the down-regulation of photosynthesis?
-Secondly, does this down-regulation fully explain the observed response of growth, or are other components of the carbon balance also affected
+Secondly, does this down-regulation fully explain the observed response of growth, or are other components of the C balance also affected.
 
@@
 These measurements were conducted during midday (10:00-14:00 h) with leaf temperature maintained at 25 &deg;C.
-After CO~2~ and water vapor flux values stabilized in the leaf chamber, net CO~2~ assimilation rate and stomatal conductance (*g*~s~) were logged 5 times and averaged for both *A*~sat~ and *A*~max~.
+After CO~2~ and water vapour flux values stabilized in the leaf chamber, net CO~2~ assimilation rate and stomatal conductance (*g*~s~) were logged 5 times and averaged for both *A*~sat~ and *A*~max~.
 
@@
 Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions.
-Reported values of *R* are standardized rates at 25 &deg;C using a *Q*~10~ value (1.86) developed for these seedlings in a separate experiment (Drake et al.
-unpublished).
+Reported values of *R* are standardized rates at 25 &deg;C using a *Q*~10~ value (1.86) developed for these seedlings in a separate experiment (Drake *et al.* unpublished).
 Leaf area and dry mass were recorded for each leaf during gas exchange campaigns.
@@
 Nitrogen concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of N~2~ and CO~2~).
-The percentange of N in samples was calculated by comparison with certified standards.
+The percentage of N in samples was calculated by comparison with certified standards.
 Leaf $\delta$^13^C was analyzed  with an Delta V Advantage coupled to a Flash HT and Conflo IV isotope ratio mass spectrometer.
@@
 
-where *L* is modelled total plant leaf area (m^2^), *P* is the daily carbon assimilation per unit leaf area (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), and *R* is the mass based leaf respiration (g C d^-1^).
+where *L* is modelled total plant leaf area (m^2^), *P* is the daily C assimilation per unit leaf area (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), and *R* is the mass based leaf respiration (g C d^-1^).
 Leaf respiration is included in the calculation of *P*.
@@
 Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above), *R*~dark~ was empirically measured and the *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values.
-Methods of the coupled leaf gas exchange model are also described in Duursma et al [-@duursma2014peaked].
+Methods of the coupled leaf gas exchange model are also described in Duursma *et al.* [-@duursma2014peaked].
 Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A*~n~ rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
@@
 This was accomplished by utilizing 61 previously digitized *Eucalyptus* seedlings, covering 5 total species which include *E.
-tereticornis*, from Duursma et al.
-[-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
+tereticornis*, from Duursma *et al.* [-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
 Using the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*~n~, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
@@
 \
-We used the model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.
+We used modelled C gain  to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.
 Cumulative net leaf C gain for each treatment was equal to the sum of each value of *P* over 120 days and final seedling C was assumed to equal half of the final dry mass for observed seedlings.
-We then compared seedling carbon use efficiency (CUE) across treatments, as the proportion of modelled cumulative net leaf C gain allocated to observed seedling biomass.
+We then compared seedling C use efficiency (CUE) across treatments, as the proportion of modelled cumulative net leaf C gain allocated to observed seedling biomass.
 
@@
 Both *J*~max~ and *V*~cmax~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`).
-Overall, the J~max~:Vc~max~ ratio was relatively conserved across all treatments (1.6&pm;0.02), which is consistent with findings across many tree species [@medlyn1996optimal; @leuning1997scaling; @medlyn1999effects; @warren2003photosynthesis; @crous2008elevated].
+Overall, the J~max~:V~cmax~ ratio was relatively conserved across all treatments (1.6&pm;0.02), which is consistent with findings across many tree species [@medlyn1996optimal; @leuning1997scaling; @medlyn1999effects; @warren2003photosynthesis; @crous2008elevated].
 Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`).
-The *g*~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab3`).
+The *g*~1~ parameter, generated for each seedling from the Medlyn *et al.* [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab3`).
 
@@
 The free seedling control had five-fold greater modelled total C gain than the average of container treatments (213.6 - 42.7&pm;8.2 g C).
-For seedlings in containers, an average of 67 &pm;0.01 % of modelled C gain was not allocated to biomass, compared to 59.2 % for the free seedling control (Figure `r massmodelfig`a).
-Consequently, the average CUE of containerized seedlings (32&pm;0.01 %) was lower than the free seedling control (40.8 %) (Figure `r massmodelfig`b).
+For seedlings in containers, an average of 67 &pm;0.01 % of modelled C gain was not allocated to observed biomass, compared to 59.2 % for the free seedling control.
+Consequently, the CUE of containerized seedlings was lower than the free seedling control (Figure `r cuefig`).
 As a result, the observed reductions in leaf *A*~n~ with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the container size treatments.
@@
 Low growth rates led to large reductions in biomass in small containers, compared to freely rooted seedlings.
-We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, close to the 43 % reported in the meta-analysis by Poorter et al.
-[-@poorter2012pot].
+We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, close to the 43 % reported in the meta-analysis by Poorter *et al.* [-@poorter2012pot].
 These growth reductions were expected, as the impedance of root growth can cause reductions in overall plant growth and activity [@mcconnaughay1991physical; @young1997mechanical].
@@
 Here, declines in *A*~max~ were correlated with higher starch content throughout the experiment.
-These results agree with a study on a deciduous conifer by Equiza et al.
-[-@equiza2006photosynthetic] where photosynthetic downregulation from reduced sink strength was correlated with starch content.
+These results agree with a study on a deciduous conifer by Equiza *et al.* [-@equiza2006photosynthetic] where photosynthetic downregulation from reduced sink strength was correlated with starch content.
 As starch content in leaves of plants grown in the smallest containers was nearly double that of free seedlings in our study, this suggests the response of *A*~n~ to sink inhibition was regulated by this accumulation, as hypothesized.
-Overall, it is likely that both nutrient content and reduced sink strength played a role in observed photosynthetic down regulation, but future studies are needed to identify the specific mechanisms which prommpted these feedbacks.
+Overall, it is likely that both nutrient content and reduced sink strength played a role in observed photosynthetic down regulation, but future studies are needed to identify the specific mechanisms which prompted these feedbacks.
 
@@
 In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, once ontogenetic drift was taken into account (Figure `r allocfig`a,b).
-Although shifts in partitioning have been previosuly reported, specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein], a constant ratio of fine root mass to leaf mass was observed in this study across all treatments.
-These results suggest that seedlings kept a conservative strategy to maintain homeostatis with with biomass partitioning, instead of a functional partitioning response to optimize limiting soil resources.
+Although shifts in partitioning have been previously reported, specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein], a constant ratio of fine root mass to leaf mass was observed in this study across all treatments.
+These results suggest that seedlings kept a conservative strategy to maintain homeostasis with with biomass partitioning, instead of a functional partitioning response to optimize limiting soil resources.
 
@@
 It is instead possible that lateral root development is affected by inanimate obstacles and avoiding growth towards container walls may improve resource gain [@falik2005root].
-Root exudation may have increased with reduced rooting volumes to facilitate N uptake in favour of increasing partitioning to root biomass.
+Root exudation may have increased with reduced rooting volumes to facilitate N uptake in favor of increasing partitioning to root biomass.
 The sensitivity of roots to their own exudates near obstructions may also prevent further growth [@semchenko2008foraging].
@@
 ##Do reductions in photosynthesis explain reductions in seedling growth?
-Our model used a simple approach to estimate cumulative seedling C gain with measured reductions in leaf *A*~n~ , via soil volume effects.
-*while treating C use efficiency, respiration and C allocation as fixed processes*.
-*Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.* Although reductions in both *A*~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al.
-[-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth.
-These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and *processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].* It is possible that the overestimation of growth was due to an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *Vc*~max~, *R*~dark~ and *g*~1~) make this unlikely.
+We use a simple approach to estimate cumulative seedling C gain with measured reductions in leaf *A*~n~ , via soil volume effects.
+Although reductions in both *A*~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter *et al.* [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth.
+As whole-plant C use efficiency was decreased in seedlings with belowground sink limitation, this suggests that other components of the C balance were affected.
+These results are especially noteworthy for process-based growth models that parameterize CUE, tissue respiration and C allocation as fixed processes.
+For example, classical approaches in tree growth and production modelling are often driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
+It is possible these results represent an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *Vc*~max~, *R*~dark~ and *g*~1~) make this unlikely.
 Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A*~n~ affect models which distinguish the fate of assimilate C within a plant.
-Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven plant growth models [@lacointe2000carbon].
+Doing so will provide valuable input to future models as assimilate allocation is a key component in C-balance driven plant growth models [@lacointe2000carbon].
 
@@
 Focusing only on empirical results in this study points to *A*~n~ driving reductions in seedling growth.
-Our modelling results reveal that other components of the C balance, beyond *A*~n~, are required to explain the observed seedling biomass response to sink manipulation.
-This discrepancy is noteworthy, as partial accounting of the different mechanisms involved in plant C balance can lead to erroneous conclusions [@valentini2000respiration].*For example, the fraction of photosynthate used in respiration is known to vary depending on species and local environmental conditions [@Lambers2008], yet is often considered a static parameter in process based growth models.
-The use of fixed rates of tissue respiration in our model likely underestimates seedling responses to sink limitation.* Thus, our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
+Modelling cumulative net seedling C gain, however, reveals that other components of the C balance, beyond *A*~n~, are required to explain the observed seedling biomass response to sink manipulation.
+This finding is noteworthy, as partial accounting of the different mechanisms involved in plant C balance can lead to erroneous conclusions [@valentini2000respiration].
+For example, the fraction of photosynthate used in respiration is known to vary depending on species and local environmental conditions [@Lambers2008], yet is often considered a static parameter in process based growth models.
+Thus, we agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
 Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A*~n~ and the fate of C allocated to growth, respiration and C storage in leaves.
@@
 
-```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=600, dev.args=list(type="cairo")}
+```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=600,eval=includeFigs}
 source("master_scripts/allometryplotting.R")
@@
 
-```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
+```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600,eval=includeFigs}
 source("master_scripts/airvars_plotting.R")
@@
 
-```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
+```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600,eval=includeFigs}
 source("master_scripts/allocation_plotting.R")
@@
 
-```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
+```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600,eval=includeFigs}
 source("master_scripts/A_stats_plotting.R")
@@
 
-```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
+```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, eval=includeFigs}
 source("master_scripts/Amax_TNC_N_plotting2.R")
@@
 
-```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
-source("master_scripts/massmodel_optimize.R")
+```{r cuefig, fig.width=6, fig.height=6, echo=FALSE, dev="png", dpi=600, eval=includeFigs}
+source("master_scripts/cuefig.R")
 ```  
-**Figure 6**.
-(a) Total carbon mass of harvested seedlings versus modelled net leaf carbon gain over 120 days.
-The dashed black line shows the 1:1 line and the dotted blue line shows the seedling biomass that would be expected if all seedlings had the same carbon use efficiency as the freely grown seedling.
-(b) Ratio of final biomass to modelled net leaf C gain of plants growth in different container sizes.
+**Figure 6**. Ratio of final biomass to modelled net leaf C gain of plants growth in different container sizes.
 

### 2016-07-11 master_scripts/massmodel.R

@@ -1,87 +1,0 @@
-
-# model as a function
-productionmodel <- function(leaffrac = .25,
-                            crfrac = .25,
-                            frfrac = .25,
-                            stemfrac=.25,
-                            gCday = 1,
-                            conversionEfficiency = 0.65,
-                            fr_resp = .010368, #gC/gFroot day Marsden et al
-                            cr_resp = .00124, #gC/gCroot day
-                            wd_resp = .001877, #gc/gwood day Drake with 1.86 q10 to 20C
-                            turnover = 1/365, #production/standing crop
-                            numdays=120,
-                            lma = 97.5,
-                            lma_start = 81.1, #this is the mean of free seedlings
-                            M_slope = -.02,
-                            M_intercept = .9,
-                            returnwhat=c("lastval","all")
-){
-  
-  
-  sumf <- leaffrac + crfrac + frfrac + stemfrac
-  leaffrac <- leaffrac / sumf
-  crfrac <- crfrac / sumf
-  frfrac <- frfrac / sumf
-  stemfrac <- stemfrac / sumf
-  
-  returnwhat <- match.arg(returnwhat)
-  
-  leafarea <- vector()
-  leafarea[1] <- LA_start
-  
-  biomass <- vector()
-  biomass[1] <- mass_mean
-  
-  frootmass <- vector()
-  frootmass[1] <- pre_root*.5
-  
-  crootmass <- vector()
-  crootmass[1] <- pre_root*.5
-  
-  stemmass <- vector()
-  stemmass[1] <- pre_stem
-  
-  leafmass <- vector()
-  leafmass[1] <- LA_start*lma_start #use one lma here to start, set it to free
-  
-  LMF <- vector()
-  LMF[1] <- (LA_start*lma)/mass_mean
-  
-  
-  if(length(gCday) == 1)gCday <- rep(gCday,numdays)
-  if(length(gCday) < numdays)stop("Need at least ",numdays," photosynthesis values.")
-  
-  #run model simulation------------------------------------------------------------------
-  for (i in 2:numdays) {
-    
-    #self shading
-    M <- M_slope*leafarea[i-1] + M_intercept
-    #respiration based on previous days mass
[…]

### 2016-07-11 master_scripts/model_start.R

@@ -1,95 +1,0 @@
-library(plyr)
-
-#experiment length---------------------------------------------------------------------
-numdays <- as.numeric(as.Date("2013-05-21") - as.Date("2013-01-21"))
-volume <- c("5", "10", "15", "20", "25", "35", "1000")
-
-#date is for plotting, starts day2
-uniqueDate <- seq.Date(from=as.Date("2013/01/22"), to=as.Date("2013/05/21"), by="days")
-
-#harvest mass and leaf area for model comparison----------------------------------------------------------------
-harvestmass <- read.csv("calculated data/seedling mass.csv")
-mass_actual <- read.csv("calculated data/harvest_mass_means.csv")
-
-
-#pre seedling data for intial biomass and leaf area (use mean)--------------------------------------------------
-seedling_pre <- read.csv("raw data/seedling_initial.csv")
-  seedling_pre$seedling_mass <- with(seedling_pre, leaf_mass+root_mass+wood_mass)
-  seedling_pre$rootshoot <- with(seedling_pre, root_mass/(leaf_mass+wood_mass))
-
-leaffractions <- mean (seedling_pre$leaf_mass/seedling_pre$seedling_mass)
-#average mass of seedlings at start
-mean_leafnum <- mean(seedling_pre$leaf_numb)
-pre_root <- mean(seedling_pre$root_mass)
-pre_stem <- mean(seedling_pre$wood_mass)
-
-#root-shoot ratios, and froot and croot mass fractions---------------------------------------------------------
-ratio <- subset(harvestmass, select = c("ID", "volume", "fineroot", "Croot", "stemmass", "leafmass",
-                                        "root", "shoot", "totalmass"))
-  ratio$rootshoot <-with(ratio, root/shoot)
-  ratio$froot_frac <- with(ratio, fineroot/totalmass)
-  ratio$croot_frac <- with(ratio, Croot/totalmass)
-  ratio$stem_frac <- with(ratio, stemmass/totalmass)
-  ratio$leaf_frac <- with(ratio, leafmass/totalmass)
-
-#mean component fractions
-rs_mean <- mean(ratio$rootshoot)
-fr_frac_mean <- mean(ratio$froot_frac)
-cr_frac_mean <- mean(ratio$croot_frac)
-stem_frac_mean <- mean(ratio$stem_frac)
-
-#fraction volume means
[…]

### 2016-07-11 manuscript/manuscript_pve.Rmd
added cites, still missing A and growth decouple cites

@@
 It is less easy to know how to implement sink limitation of growth in such models, because it requires that we know whether, and how, sink limitation influences the contributing processes of photosynthesis, respiration and allocation.
-It has been suggested that sink limitation affects the C balance by causing a down-regulation of photosynthetic rate, possibly mediated by carbohydrate accumulation (refs), but there is also evidence that photosynthesis and growth are decoupled under sink limitation (refs), suggesting that other processes must also be affected.
+It has been suggested that sink limitation affects the C balance by causing a down-regulation of photosynthetic rate, possibly mediated by carbohydrate accumulation [@arp1991effects; @paul2001sink;@ainsworth2004testing; @ronchi2006growth; @nebauer2011photosynthesis], but there is also evidence that photosynthesis and growth are decoupled under sink limitation *(refs)*, suggesting that other processes must also be affected.
 

### 2016-07-11 manuscript/manuscript_pve.Rmd
added cites in intro, added author contributions

--- 2016-07-11 manuscript/manuscript_pve.Rmd
@@
 It is less easy to know how to implement sink limitation of growth in such models, because it requires that we know whether, and how, sink limitation influences the contributing processes of photosynthesis, respiration and allocation.
-It has been suggested that sink limitation affects the C balance by causing a down-regulation of photosynthetic rate, possibly mediated by carbohydrate accumulation (refs), but there is also evidence that photosynthesis and growth are decoupled under sink limitation (refs), suggesting that other processes must also be affected.
+It has been suggested that sink limitation affects the C balance by causing a down-regulation of photosynthetic rate, possibly mediated by carbohydrate accumulation [@arp1991effects; @paul2001sink;@ainsworth2004testing; @ronchi2006growth; @nebauer2011photosynthesis], but there is also evidence that photosynthesis and growth are decoupled under sink limitation [@muller2011water;@leuzinger2013sink], suggesting that other processes must also be affected.
 
@@
 
+# Acknowledgements
+We thank Burhan Amiji for his outstanding technical assistance. We would like to thank the many Hawkesbury Institute for the Environment staff and students who helped during the experimental harvest.
+
+# Author Contributions
+CC contributed to the design of the research, data analysis, collection, interpretation and writing the manuscript.
+BM contributed to the design of the research, interpretation and writing the manuscript.
+RD contributed to the design of the research, data analysis, interpretation and writing the manuscript.
+
 # Tables {.unnumbered}
@@
 
-# Acknowledgements
-We thank Burhan Amiji for his outstanding technical assistance. We would like to thank the many Hawkesbury Institute for the Environment staff and students who helped during the experimental harvest.
-
 # References {.unnumbered}

### 2016-07-15 manuscript/manuscript_pve.Rmd
very minor edits

@@
 \
-COURTNEY E. CAMPANY^1^, BELINDA MEDLYN^1^ and REMKO A. DUURSMA^1^
+Courtney E. Campany^1^, Belinda Medlyn^1^ and Remko A. Duursma^1^
 
 \
-^1^ Hawkesbury Institute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW, Australia
+^1^ Hawkesbury Institute for the Environment, Western Sydney University, Locked Bag 1797, Penrith, NSW, Australia
 
 \
-Corresponding author: CE Campany, email: courtneycampany@gmail.com, telephone: +61 02 4570 1421, fax: +61 02 4570 1103
+Corresponding author: C.E. Campany, email: courtneycampany@gmail.com, telephone: +61 02 4570 1421, fax: +61 02 4570 1103
 
@@
 - We manipulated soil volume to impose sink limitation of growth in *Eucalyptus tereticornis* seedlings.
-Seedlings were grown in containers of different sizes and planted flush to the soil alongside freely-rooted seedlings.
+Seedlings were grown in the field in containers of different sizes and planted flush to the soil alongside freely-rooted seedlings.
 
-- Container volume negatively affected aboveground growth throughout the experiment, but mass partitioning to leaves, stems and roots was unchanged after 120 days.
+- Container volume negatively affected aboveground growth throughout the experiment, but after 120 days, biomass distribution in  leaves, stems and roots was not different.
 Photosynthetic capacity was significantly reduced in containerized seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
@@
 This approach is unsatisfactory because mechanistic models should obey the laws of physics.
-Growth models must take into account several simultaneous processes affecting the C balance at any given time [@fourcaud2008plant], thus incomplete modelling approaches often lead to unaccounted for C.
+Growth models must take into account several simultaneous processes affecting the C balance at any given time [@fourcaud2008plant], thus incomplete modelling approaches often lead to unaccounted-for C.
 Our goal in this paper was to investigate how the C balance of plants is modified by sink limitation, by experimentally imposing a sink limitation to growth.
@@
 In previous studies, the sink limitation of growth has been explored by manipulations of both C source and C sink activity.
-Examples of experimental approaches that manipulate C source activity include elevated atmospheric CO2 concentration and partial defoliation experiments.
+Examples of experimental approaches that manipulate C source activity include elevated atmospheric CO~2~ concentration and partial defoliation experiments.
 Elevated CO~2~ causes an increase in leaf-level photosynthetic rate, *A*~n~ [@drake1997more; @ainsworth2007response].
@@
 \
-In partial defoliation experiments, source activity is decreased by reduction of photosynthesizing leaf area.
+In partial defoliation experiments, source activity is decreased by a reduction of photosynthesizing leaf area.
 In these experiments, compensatory increases in *A*~n~ of the remaining foliage are commonly found, and have been attributed to several processes including indirect effects on resource availability, such as increased stomatal conductance [@layne1995end] or enhanced leaf nutrient status [@turnbull2007increased; @pinkard2011gas], or more direct effects of modified sink-source balance such as, reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end;@pinkard2011gas], and regulatory sugar signaling [@eyles2013whole].
@@
 Our goal in this paper was to impose a sink limitation of growth, by manipulating container size and thus rooting volume, and to examine how the C balance of the plants was affected.
-We grew *Eucalyptus tereticornis* seedlings in a range of container sizes, using freely-rooted seedlings as a control for the container size treatments.
+We grew *Eucalyptus tereticornis* seedlings in a range of container sizes in field conditions, using freely-rooted seedlings as a control for the container size treatments.
 Seedlings were maintained under well-watered conditions in order to isolate the effect of restricted soil volume from that of low water availability.
@@
 We anticipated that both photosynthesis and growth would be reduced under belowground sink limitation.
-The principal questions that we addressed were: Firstly, which physiological process best explains the down-regulation of photosynthesis?
-Secondly, does this down-regulation fully explain the observed response of growth, or are other components of the C balance also affected.
+The principal questions that we addressed were: 1) which physiological process best explains the down-regulation of photosynthesis?, and 2) does this down-regulation fully explain the observed response of growth, or are other components of the C balance also affected?
 
@@
 \
-Forty-nine *Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain cohort.
+Forty-nine *Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain (western Sydney) cohort.
 Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.
@@
 Drain systems were built into each pot to prevent pooling of water throughout the experiment.
-Pooling of water could lead to an anaerobic environment around the root that could hinder the uptake of water through reduced root conductance [@poorter2009causes], an undesired experimental artifact.
+Pooling of water could lead to an anaerobic environment around the root that could hinder the uptake of water through reduced root conductance [@poorter2009causes], an undesired experimental artefact.
 A collection compartment in the bottom of containers, containing gravel covered by root exclusion mesh, was used to collect excess water for 20, 25, and 35 l containers.
@@
 Leaves were detached and immediately stored inside foil-covered bags before water potential measurements were performed.
-$\Psi$~pd~ was measured before sunrise and $\Psi$~l~ at 13:00 h (&pm30 m).
+$\Psi$~pd~ was measured before sunrise and $\Psi$~l~ at 13:00 h (&pm; 30 min).
 These measurements were used as a measure of static water stress on the seedlings [@sellin1999does] and to ensure that the bulk soil water availability was high enough for plants to avoid water stress as they became larger and roots filled the soil volume.
@@
 Both *J*~max~ and *V*~cmax~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`).
-Overall, the J~max~:V~cmax~ ratio was relatively conserved across all treatments (1.6&pm;0.02), which is consistent with findings across many tree species [@medlyn1996optimal; @leuning1997scaling; @medlyn1999effects; @warren2003photosynthesis; @crous2008elevated].
+Overall, the *J*~max~ / *V*~cmax~ ratio was conserved across all treatments (1.6&pm;0.02), which is consistent with findings across many tree species [@medlyn1996optimal; @leuning1997scaling; @medlyn1999effects; @warren2003photosynthesis; @crous2008elevated].
 Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`).
@@
 Combined, these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment.
-Soil N at harvest was not different across soil volumes ($\bar{x}$ = .045 %), with minimal decreases from pre-planting values ($\bar{x}$ = .049 %).
+Soil N at harvest was not different across soil volumes (mean of .045 %), with minimal decreases from pre-planting values (mean of = .049 %).
 This similarity indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
@@
 #Discussion
-This study utilized a novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production.
+This study utilized a novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling growth.
 Our goal was to identify how sink limitation of growth modified the C balance of seedlings.
 We found a strong reduction of growth in containerized plants.
-Leaf *A*~n~ was also strongly reduced, but this reduction was insufficient to fully explain the reduction in growth, implying that components such as whole-plant respiratory loss were also likely affected.
+Leaf *A*~n~ was also reduced, but this reduction was insufficient to fully explain the reduction in growth, implying that components such as whole-plant respiratory loss were also likely affected.
 
@@
 Although shifts in partitioning have been previously reported, specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein], a constant ratio of fine root mass to leaf mass was observed in this study across all treatments.
-These results suggest that seedlings kept a conservative strategy to maintain homeostasis with with biomass partitioning, instead of a functional partitioning response to optimize limiting soil resources.
+These results suggest that seedlings kept a conservative strategy to maintain homeostasis with biomass partitioning, instead of a functional partitioning response to optimize limiting soil resources.
 
@@
 The sensitivity of roots to their own exudates near obstructions may also prevent further growth [@semchenko2008foraging].
-Here, we found that FRLD was highest in smallest containers suggesting that root restriction likely occurred as simple function of available rooting space.
+Here, we found that fine root length density was highest in smallest containers suggesting that root restriction likely occurred as simple function of available rooting space.
 Additionally, physical restriction of root proliferation could have impacted root development and morphology prior to shifts in mass partitioning.
-Here, increases in SRL were detected in several of the soil volume treatments.
+Here, increases in specific root length were detected in several of the soil volume treatments.
 This is not surprising as plants in containers have been shown to have different root morphology to field grown plants [@nesmith1998effect].
@@
 For example, classical approaches in tree growth and production modelling are often driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].
-It is possible these results represent an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *Vc*~max~, *R*~dark~ and *g*~1~) make this unlikely.
+It is possible these results represent an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *V*~cmax~, *R*~dark~ and *g*~1~) make this unlikely.
 Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A*~n~ affect models which distinguish the fate of assimilate C within a plant.
@@
 For example, the fraction of photosynthate used in respiration is known to vary depending on species and local environmental conditions [@Lambers2008], yet is often considered a static parameter in process based growth models.
-Thus, we agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
+Thus, we agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] that the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
 Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A*~n~ and the fate of C allocated to growth, respiration and C storage in leaves.

### 2016-07-18 manuscript/manuscript_pve.Rmd
edits to fit word count of new phyt

@@
 \
-Summary: 
+Summary: 174
 \
-Introduction:
+Introduction: 1206
 \
-Materials and methods:
+Materials and methods: 2171
 \
-Results:
+Results: 1138
 \
-Discussion:
+Discussion: 1759
 \
-Acknowledgements: 
+Acknowledgements: 30
 \
@@
 At this site a soil hard layer exists at ~1.0 m with a transition to heavy clay soils.
-The climate for the region is classified as sub-humid temperate.
 
@@
 Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.
-Previous container experiments have confirmed that species with tap roots (similar to *E.
-tereticornis*) use the center of the container as the medium for thick roots, leaving the periphery of the soil as the most active sites for fine root proliferation [@biran1980a; @biran1980b].
-By using a species with taproot growth and manipulations of container length rather than width, we believed that a more realistic test of growth inhibition through constrained soil volume would be achieved.
-
-\
 Six container volumes were used ranging from 5 L to 35 L, with a 22.5 cm diameter, and lengths ranging from 15 to 100 cm.
@@
 Pooling of water could lead to an anaerobic environment around the root that could hinder the uptake of water through reduced root conductance [@poorter2009causes], an undesired experimental artefact.
-A collection compartment in the bottom of containers, containing gravel covered by root exclusion mesh, was used to collect excess water for 20, 25, and 35 l containers.
-Plastic tubing (6 mm diameter) was inset into the gravel layer and extended through the top of the container.
-A lysimeter pump was then used to suction excess water, through the tubing, as needed.
-For small containers (5, 10, and 15 L) a simple bottom plug was used to drain excess water from the gravel compartment.
 Each container was inspected after every watering and rainfall event to determine if pooling had occurred.
@@
 In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, once ontogenetic drift was taken into account (Figure `r allocfig`a,b).
-Although shifts in partitioning have been previously reported, specifically for nutrient limitation [@mcconnaughay1999biomass, and references therein], a constant ratio of fine root mass to leaf mass was observed in this study across all treatments.
-These results suggest that seedlings kept a conservative strategy to maintain homeostasis with biomass partitioning, instead of a functional partitioning response to optimize limiting soil resources.
+A conserved ratio of fine root mass to leaf mass was observed across all treatments, suggesting that seedlings maintained homeostasis with biomass partitioning instead of a functional partitioning response to optimize limiting soil resources.
 
@@
 The lack of detected shifts in partitioning to fine roots provides evidence against an optimal foraging strategy for seedlings in containers.
-It is instead possible that lateral root development is affected by inanimate obstacles and avoiding growth towards container walls may improve resource gain [@falik2005root].
 Root exudation may have increased with reduced rooting volumes to facilitate N uptake in favor of increasing partitioning to root biomass.

### 2016-07-19 manuscript/manuscript_pve.Rmd
fix space, ready to submit
fig 6 caption change

@@
 Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and seedling leaf area estimated from leaf counts (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
-
+\
 ```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600,eval=includeFigs}
@@
 **Figure 2**. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013. 
-
+\
 ```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600,eval=includeFigs}
@@
 For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (*R*^2^ = 0.82) with equation: log(x) = 0.983log(y) - 0.036.
-
+\
 ```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600,eval=includeFigs}
@@
 Different letters represent significant differences between treatments.
-
+\
 ```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, eval=includeFigs}
@@
 The equation for the full model is y = 28.58(N) - 3.31(Starch) - 0.87(N*Starch) - 221.96.
-
+\
 ```{r cuefig, fig.width=6, fig.height=6, echo=FALSE, dev="png", dpi=600, eval=includeFigs}
@@
 ```  
-**Figure 6**. Ratio of final biomass to modelled net leaf C gain of plants growth in different container sizes.
+**Figure 6**. Ratio of final biomass to modelled net leaf C gain of seedlings growth in different container sizes and freely-rooted seedlings.
 

### 2016-07-20 manuscript/manuscript_pve.Rmd
captions expanded

--- 2016-07-18 manuscript/manuscript_pve.Rmd
@@
 **Figure 1**.
-Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and seedling leaf area estimated from leaf counts (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
-
+Seedling growth over the duration of the experiment was strongly reduced in containerized seedlings compared to freely rooted seedlings.
+Height growth (a), diameter growth (b), and seedling leaf area estimated from leaf counts (c) measured weekly on *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.
+Shown are soil volume treatment means &pm; standard error.
+\
 ```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600,eval=includeFigs}
@@
 ```  
-**Figure 2**. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.
-
+**Figure 2**. Environmental drivers over the course of the experiment. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) in 2013. 
+\
 ```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600,eval=includeFigs}
@@
 **Figure 3**.
-Soil volume treatment means of biomass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c).
-For (b) lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment.
-For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (*R*^2^ = 0.82) with equation: log(x) = 0.983log(y) - 0.036.
-
+Biomass partitioning at final harvest did not respond strongly to soil volume treatment.
+(a) Relative partitioning to leaves, stems, and roots at the final harvest, shown as treatment means (standard errors omitted for clarity).
+(b) Bi-variate relationships between mass partitioning to leaves and stems + roots.
+Each symbol is a plant.
+Lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment.
+(c) Total plant leaf mass as a function of fine root biomass with &pm; standard error.
+The dashed line is a 1:1 line and the solid line represents the significant log-log model fit (*R*^2^ = 0.82) with equation: log(x) = -0.36 + 0.983 * log(y).
+\
 ```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600,eval=includeFigs}
@@
 **Figure 4**.
-Soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25 &deg;C.
-Different letters represent significant differences between treatments.
-
+Light-saturated photosynthesis (A~sat~) was reduced in containerized seedlings compared to freely-rooted seedlings ('Free').
+Shown are soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25 &deg;C.
+Different letters represent significant differences between treatments (p < 0.05).
+\
 ```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, eval=includeFigs}
@@
 **Figure 5**.
-Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).
+Photosynthetic capacity on a leaf mass basis (A~mass~), was correlated to both leaf starch and nitrogen content.
+(a) A~mass~ was negatively related to leaf starch (shown as percentage of dry mass), in particular for leaves with higher nitrogen content (N~mass~).
+(b) A~mass~ was positively related to N~mass~ (expressed as N per unit mass after subtracting TNC content).
+In both panels, each symbol is an individual measurement of A~mass~ (data across all campaigns are shown).
 Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high.
@@
 The marginal *R*^2^ (fixed effects only) was 0.37 and the conditional *R*^2^ (fixed and random effects) was 0.48 for the complete model.
-The equation for the full model is y = 28.58(N) - 3.31(Starch) - 0.87(N*Starch) - 221.96.
-
+The equation for the full model is y = - 221.96 + 28.58(N) - 3.31(Starch) - 0.87(N*Starch).
+\
 ```{r cuefig, fig.width=6, fig.height=6, echo=FALSE, dev="png", dpi=600, eval=includeFigs}
@@
 ```  
-**Figure 6**. Ratio of final biomass to modelled net leaf C gain of plants growth in different container sizes.
+**Figure 6**.
+The final biomass attained per unit total photosynthesis over the duration of the experiment.
+Note the higher ratio for the freely rooted seedlings compared to the containerized seedlings, indicating a higher carbon-use efficiency.
+Shown are treatment means, as the model scaling instantaneous leaf photosynthesis to total plant photosynthesis was run once for every treatment.
 

### 2016-07-20 manuscript/manuscript_pve.Rmd
Amass clarification
final edits, submitted this version to new phyt

@@
 \
-In the absence of a good understanding of the effects of sink limitation on physiological processes, most attempts to model sink limitation of growth to date have done so by abandoning the principle of mass balance [e.g.
-@fatichi2013reconciling; @fatichi2014moving].
+In the absence of a good understanding of the effects of sink limitation on physiological processes, most attempts to model sink limitation of growth to date have done so by abandoning the principle of mass balance [@fatichi2014moving].
 This approach is unsatisfactory because mechanistic models should obey the laws of physics.
@@
 Containers were planted flush with the soil surface inside metal sleeves, designed to minimize excess air space between the container and outside soil while also allowing for container removal.
-This allowed for soil temperatures in containers to reflect conditions of naturally planted (free) seedlings.
-Each experimental block (n=7) contained a complete replicate set of six container volumes as well as one free seedling, with 1 m^2^ spacing.
-For each free seedling, used as the control, a 1 m^2^ subplot was excavated to the hard layer and replaced with the same soil used in each container.
+This allowed for soil temperatures in containers to reflect conditions of naturally planted (Free) seedlings.
+Each experimental block (n=7) contained a complete replicate set of six container volumes as well as one Free seedling, with 1 m^2^ spacing.
+For each Free seedling, used as the control, a 1 m^2^ subplot was excavated to the hard layer and replaced with the same soil used in each container.
 A border of root exclusion material was buried 0.25 m deep and extended 0.25 m above the ground surface around each subplot to exclude local vegetation, which was further kept out by periodic weeding.
@@
 Roots of seedlings in containers were not considered pot bound, as matted roots along the soil-container interface were not observed.
-Roots from the free seedlings were collected by excavating each 1 m^2^ subplot to the hard layer and keeping only roots within the subplot.
+Roots from the Free seedlings were collected by excavating each 1 m^2^ subplot to the hard layer and keeping only roots within the subplot.
 For each seedling, a sub-sample of washed fine roots was analyzed for root length using WhinoRhizo software (Regent Instruments Inc., Quebec, QC, Canada).
@@
 Increases in both final stem diameter and cumulative leaf area (both *P* < 0.001) were found with increasing soil volume.
-We did not find a continuous effect of container size; rather, plant size was similar among smaller containers, and differences were driven mainly by the largest container and the free seedling treatments.
+We did not find a continuous effect of container size; rather, plant size was similar among smaller containers, and differences were driven mainly by the largest container and the Free seedling treatments.
 
 \
-Total seedling biomass at harvest was significantly different across container volumes (*P* < 0.001) and between container treatments and free seedlings (*P* < 0.001, Table `r pvetab1`).
-On average, harvested biomass of free seedlings was 84% higher than that of seedlings in containers.
+Total seedling biomass at harvest was significantly different across container volumes (*P* < 0.001) and between container treatments and Free seedlings (*P* < 0.001, Table `r pvetab1`).
+On average, harvested biomass of Free seedlings was 84% higher than that of seedlings in containers.
 Plant biomass was positively correlated with total leaf area across all treatments (*R*^2^ = 0.97, *P* < 0.001).
@@
 \
-Overall, SRL was higher in seedlings in containers compared to free seedlings but only in some of the container size treatments (Table `r pvetab2`, *P* = 0.009).
+Overall, SRL was higher in seedlings in containers compared to Free seedlings but only in some of the container size treatments (Table `r pvetab2`, *P* = 0.009).
 Fine root length density was significantly higher in the two smallest container sizes and was the lowest in the largest container size (Table `r pvetab2`, *P* < 0.001).
-Over the duration of the experiment SLA~f~ was higher in free seedlings, but was not different across container sizes (Table `r pvetab1`, *P* < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (*P* < 0.001).
+Over the duration of the experiment SLA~f~ was higher in Free seedlings, but was not different across container sizes (Table `r pvetab1`, *P* < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (*P* < 0.001).
 
 ##Leaf and root chemistry
-Leaf N~f~ was significantly higher in free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, *P* < 0.001).
-Throughout the remainder of the experiment the smallest container volume had significantly lower leaf N~f~ than other soil volumes, while free seedlings maintained the highest leaf N~f~ (Table `r pvetab1`, *P* < 0.001).
+Leaf N~f~ was significantly higher in Free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, *P* < 0.001).
+Throughout the remainder of the experiment the smallest container volume had significantly lower leaf N~f~ than other soil volumes, while Free seedlings maintained the highest leaf N~f~ (Table `r pvetab1`, *P* < 0.001).
 Leaf starch content in the smallest container was ca.
-double  that of free seedlings (*P* = 0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table `r pvetab1`).
-Differences in leaf starch between the free seedling and the smallest container were evident during the first gas exchange campaign (*P* = 0.001).
-Root N was higher in free seedlings compared to seedlings in containers but only for some of the container size treatments (Table `r pvetab2`).
+double  that of Free seedlings (*P* = 0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table `r pvetab1`).
+Differences in leaf starch between the Free seedling and the smallest container were evident during the first gas exchange campaign (*P* = 0.001).
+Root N was higher in Free seedlings compared to seedlings in containers but only for some of the container size treatments (Table `r pvetab2`).
 
 ##Gas exchange and photosynthetic parameters
-At the first measurement campaign, both *A*~sat~ and *A*~max~ were significantly higher in the free seedling treatment compared to seedlings in containers (both *P* < 0.001).
-Across all measurement campaigns, mean *A*~sat~ (Figure `r asatfig`) and *A*~max~ (Table `r pvetab3`) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively).
+At the first measurement campaign, both *A*~sat~ and *A*~max~ were significantly higher in the Free seedling treatment compared to seedlings in containers (both *P* < 0.001).
+Across all measurement campaigns, mean *A*~sat~ (Figure `r asatfig`) and *A*~max~ (Table `r pvetab3`) were consistently higher in Free seedlings than in containers (26 % and 29 %, respectively).
 The relationship between leaf starch and leaf N~f~ on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated with both leaf N~f~ and leaf starch (both *P* < 0.001).
@@
 \
-Both *J*~max~ and *V*~cmax~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`).
+Both *J*~max~ and *V*~cmax~ were significantly higher in Free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`).
 Overall, the *J*~max~ / *V*~cmax~ ratio was conserved across all treatments (1.6&pm;0.02), which is consistent with findings across many tree species [@medlyn1996optimal; @leuning1997scaling; @medlyn1999effects; @warren2003photosynthesis; @crous2008elevated].
 Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`).
-The *g*~1~ parameter, generated for each seedling from the Medlyn *et al.* [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab3`).
+The *g*~1~ parameter, generated for each seedling from the Medlyn *et al.* [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the Free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab3`).
 
@@
 Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 MPa across all seedlings, respectively.
-Although *g*~s~ in free seedlings was generally higher than those in containers (Table `r pvetab3`, *P* < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
+Although *g*~s~ in Free seedlings was generally higher than those in containers (Table `r pvetab3`, *P* < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
 Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table `r pvetab1`).
@@
 Soil N at harvest was not different across soil volumes (mean of .045 %), with minimal decreases from pre-planting values (mean of = .049 %).
-This similarity indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
+This similarity indicates that nutrient leaching from Free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
 
@@
 Modelled cumulative net leaf C gain over 120 days varied two-fold across containers sizes (25.6 - 55.1 g C).
-The free seedling control had five-fold greater modelled total C gain than the average of container treatments (213.6 - 42.7&pm;8.2 g C).
-For seedlings in containers, an average of 67 &pm;0.01 % of modelled C gain was not allocated to observed biomass, compared to 59.2 % for the free seedling control.
-Consequently, the CUE of containerized seedlings was lower than the free seedling control (Figure `r cuefig`).
+The Free seedling control had five-fold greater modelled total C gain than the average of container treatments (213.6 - 42.7&pm;8.2 g C).
+For seedlings in containers, an average of 67 &pm;0.01 % of modelled C gain was not allocated to observed biomass, compared to 59.2 % for the Free seedling control.
+Consequently, the CUE of containerized seedlings was lower than the Free seedling control (Figure `r cuefig`).
 As a result, the observed reductions in leaf *A*~n~ with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the container size treatments.
@@
 It has been shown that roots subjected to environmental stress may send inhibitory signals to the shoots that affect *g*~s~, cell expansion, cell division and the rate of leaf appearance [@passioura2002soil].
-Here, we observed a large divergence in leaf area between seedlings in containers and free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
+Here, we observed a large divergence in leaf area between seedlings in containers and Free seedlings through time, with the eventual cessation of new leaf growth in seedlings in small containers.
 
@@
 It is possible that either physical root restriction or decreased supply reduced seedling N uptake in small containers.
-Although root N was on average higher in free seedlings at the end of the experiment, it was not consistently higher than the smallest container volume treatment.
-Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N~f~ in free seedlings, but this effect is unknown.
-Soil N also declined evenly across all treatments, providing no clear evidence for decreased supply between free seedlings and seedlings in containers.
+Although root N was on average higher in Free seedlings at the end of the experiment, it was not consistently higher than the smallest container volume treatment.
+Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N~f~ in Free seedlings, but this effect is unknown.
+Soil N also declined evenly across all treatments, providing no clear evidence for decreased supply between Free seedlings and seedlings in containers.
 In these already low fertility soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
@@
 These results agree with a study on a deciduous conifer by Equiza *et al.* [-@equiza2006photosynthetic] where photosynthetic downregulation from reduced sink strength was correlated with starch content.
-As starch content in leaves of plants grown in the smallest containers was nearly double that of free seedlings in our study, this suggests the response of *A*~n~ to sink inhibition was regulated by this accumulation, as hypothesized.
+As starch content in leaves of plants grown in the smallest containers was nearly double that of Free seedlings in our study, this suggests the response of *A*~n~ to sink inhibition was regulated by this accumulation, as hypothesized.
 Overall, it is likely that both nutrient content and reduced sink strength played a role in observed photosynthetic down regulation, but future studies are needed to identify the specific mechanisms which prompted these feedbacks.
@@
 It was necessary to distinguish if growth was affected beyond ontogenetic constraints, by correcting for size, as biomass distribution is strongly size-dependent [@gould1966allometry; @lleonart2000removing].
-In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to free seedlings, once ontogenetic drift was taken into account (Figure `r allocfig`a,b).
+In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to Free seedlings, once ontogenetic drift was taken into account (Figure `r allocfig`a,b).
 A conserved ratio of fine root mass to leaf mass was observed across all treatments, suggesting that seedlings maintained homeostasis with biomass partitioning instead of a functional partitioning response to optimize limiting soil resources.
@@
 All values are from the final harvest.
-Values for fine root length density (FRLD) were only calculated for seedlings in containers as free seedlings had potentially unlimited soil volume to exploit.
+Values for fine root length density (FRLD) were only calculated for seedlings in containers as Free seedlings had potentially unlimited soil volume to exploit.
 Different letters represent significant differences between treatments.
@@
 **Figure 5**.
-Photosynthetic capacity on a leaf mass basis (A~mass~), was correlated to both leaf starch and nitrogen content.
+Photosynthetic capacity on a leaf mass basis (A~mass~, measured at saturating light and [CO~2~]) was correlated to both leaf starch and nitrogen content.
 (a) A~mass~ was negatively related to leaf starch (shown as percentage of dry mass), in particular for leaves with higher nitrogen content (N~mass~).

### 2016-07-20 master_scripts/Amax_TNC_N_plotting2.R

@@ -37,10 +37,9 @@ f2 <- fixef(Afit2_full)
 
 #plot and predict (2 graphs)---------------------------------------------------------------------
 cols <- c("green3", "cyan4", "#0081FFFF", "darkviolet", "red")
-#cols <- c("forestgreen", "#80FE1AFF","#ECFD08FF","#FF7500FF","#FF3300FF")
-#coln <- c("#FF3300FF", "#FF7500FF","#ECFD08FF",  "#80FE1AFF", "forestgreen" )
 coln <- c("red", "darkviolet", "#0081FFFF", "cyan4", "green3")
-binlab <- c("0-4", "4-8", "8-12", "12-16", ">16")
+# binlab <- c("0-4", "4-8", "8-12", "12-16", ">16")
+binlab <- c(">16", "12-16", "8-12", "4-8", "0-4")
 binlab2 <- c("0-1", "1-3", "3-6", "6-8", ">8")
 
 pchbin <- c(1,2,3,4,5)

### 2016-08-22 manuscript/manuscript_pve.Rmd
added word count
removed new phyt formatting

@@
     number_sections: yes
-csl: new-phytologist.csl
+csl: tree-physiology.csl
 bibliography: references2.bib
@@
 Corresponding author: C.E. Campany, email: courtneycampany@gmail.com, telephone: +61 02 4570 1421, fax: +61 02 4570 1103
-
-\
-Word counts
-\
-Main text:
-\
-Summary: 174
-\
-Introduction: 1206
-\
-Materials and methods: 2171
-\
-Results: 1138
-\
-Discussion: 1759
-\
-Acknowledgements: 30
-\
-6 figures (5 color), 3 tables
 
@@
 
-- Sink limitation is known to reduce plant growth, but it is not known how plant carbon (C) balance is affected, limiting our ability to predict growth under sink-limited conditions.
-
-- We manipulated soil volume to impose sink limitation of growth in *Eucalyptus tereticornis* seedlings.
+Sink limitation is known to reduce plant growth, but it is not known how plant carbon (C) balance is affected, limiting our ability to predict growth under sink-limited conditions.
+We manipulated soil volume to impose sink limitation of growth in *Eucalyptus tereticornis* seedlings.
 Seedlings were grown in the field in containers of different sizes and planted flush to the soil alongside freely-rooted seedlings.
-
-- Container volume negatively affected aboveground growth throughout the experiment, but after 120 days, biomass distribution in  leaves, stems and roots was not different.
+Container volume negatively affected aboveground growth throughout the experiment, but after 120 days, biomass distribution in  leaves, stems and roots was not different.
 Photosynthetic capacity was significantly reduced in containerized seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
 However, the reduction in net leaf photosynthesis over the growth period was insufficient to explain the reduction in growth, so that we also observed a reduction in whole-plant C use efficiency (CUE) with container size.
-
-- Our results show that sink limitation affects plant growth through feedbacks to both photosynthesis and CUE.
+Our results show that sink limitation affects plant growth through feedbacks to both photosynthesis and CUE.
 Mass balance approaches to predicting plant growth under sink-limited conditions need to incorporate both of these feedbacks.
+*quantitative results and refer to figure*
 

### 2016-11-01 manuscript/manuscript_pve.Rmd
reviewer edits.  Mostly softened language around modelling.  Added back in container design.  Left TNC methods as is, changed text to say exact methods can be found in mitchell cite. added to R method

@@
 
-#Summary
+#Abstract
 
@@
 Photosynthetic capacity was significantly reduced in containerized seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
-However, the reduction in net leaf photosynthesis over the growth period was insufficient to explain the reduction in growth, so that we also observed a reduction in whole-plant C use efficiency (CUE) with container size.
+However, the reduction in net leaf photosynthesis over the growth period was insufficient to explain the reduction in growth, so that we also observed an apparent reduction in whole-plant C use efficiency (CUE) with container size.
 Our results show that sink limitation affects plant growth through feedbacks to both photosynthesis and CUE.
 Mass balance approaches to predicting plant growth under sink-limited conditions need to incorporate both of these feedbacks.
-*quantitative results and refer to figure*
 
@@
 It is less easy to know how to implement sink limitation of growth in such models, because it requires that we know whether, and how, sink limitation influences the contributing processes of photosynthesis, respiration and allocation.
-It has been suggested that sink limitation affects the C balance by causing a down-regulation of photosynthetic rate, possibly mediated by carbohydrate accumulation [@arp1991effects; @paul2001sink;@ainsworth2004testing; @ronchi2006growth; @nebauer2011photosynthesis], but there is also evidence that photosynthesis and growth are decoupled under sink limitation [@muller2011water;@leuzinger2013sink], suggesting that other processes must also be affected.
+It has been suggested that sink limitation affects the C balance by causing a down-regulation of photosynthetic rate, possibly mediated by carbohydrate accumulation [@arp1991effects; @paul2001sink;@ainsworth2004testing; @ronchi2006growth; @nebauer2011photosynthesis], but there is also evidence that photosynthesis and growth can become strongly decoupled under sink limitation [@muller2011water;@leuzinger2013sink], suggesting that other processes must also be affected.
 
@@
 Six container volumes were used ranging from 5 L to 35 L, with a 22.5 cm diameter, and lengths ranging from 15 to 100 cm.
-Containers were constructed of PVC pipe and were filled with local top soil.
+Containers were constructed of PVC pipe, which were capped at the bottom end, and were filled with local top soil.
 Soil in each container was packed to achieve a target soil bulk density that matched local soil conditions of 1.7 g cm^-3^.
@@
 Plants were watered weekly or when needed to maintain soil moisture at field capacity (13-15 %).
-Drain systems were built into each pot to prevent pooling of water throughout the experiment.
+Drain systems were built into each container to prevent pooling of water before root expansion, from reduced root uptake, or from large rainfall events.
 Pooling of water could lead to an anaerobic environment around the root that could hinder the uptake of water through reduced root conductance [@poorter2009causes], an undesired experimental artefact.
+A compartment in the bottom of each container, containing gravel covered by root exclusion mesh, was used to collect excess water.
+For small containers (5, 10, and 15 l) a simple bottom plug was used to drain excess water from the compartment.
+For larger containers, plastic tubing (6 mm diameter) was inset into the gravel layer and extended through the top of the container and a lysimeter pump was then used to suction excess water, through the tubing, as needed.
 Each container was inspected after every watering and rainfall event to determine if pooling had occurred.
@@
 Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions.
+*R* was logged 5 times for each leaf after CO~2~ and water vapour flux values stabilized in the conifer chamber.
 Reported values of *R* are standardized rates at 25 &deg;C using a *Q*~10~ value (1.86) developed for these seedlings in a separate experiment (Drake *et al.* unpublished).
@@
 ##Leaf, root and soil chemistry
-Leaves used in each gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of nitrogen (N) content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
+Each leaf used in gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of nitrogen (N) content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
 Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis of N.
-Nitrogen concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer with thermal conductivity and mass spectromic detection (of N~2~ and CO~2~).
-The percentage of N in samples was calculated by comparison with certified standards.
+Nitrogen concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer and the percentage of N in samples was calculated by comparison with certified standards.
 Leaf $\delta$^13^C was analyzed  with an Delta V Advantage coupled to a Flash HT and Conflo IV isotope ratio mass spectrometer.
@@
 Starch was quantified using a thermostable $\alpha$-amylase and amyloglucosidase assay [@McCleary_starch] and soluble sugars were determined following the anthrone method [@ebell1969variation].
-Complete methods of the TNC assay are described in @mitchell2013drought.
+Exact methods of the TNC assay used in this study are fully described in @mitchell2013drought.
 TNC-free specific leaf area (SLA~f~, m^2^ kg^-1^) for leaves sampled during gas exchange campaigns, was calculated by first subtracting the TNC content from individual dry leaf mass before dividing leaf area by leaf mass.
@@
 For seedlings in containers, an average of 67 &pm;0.01 % of modelled C gain was not allocated to observed biomass, compared to 59.2 % for the Free seedling control.
-Consequently, the CUE of containerized seedlings was lower than the Free seedling control (Figure `r cuefig`).
+Consequently, the estimated CUE of containerized seedlings was lower than the Free seedling control (Figure `r cuefig`).
 As a result, the observed reductions in leaf *A*~n~ with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the container size treatments.
@@
 As starch content in leaves of plants grown in the smallest containers was nearly double that of Free seedlings in our study, this suggests the response of *A*~n~ to sink inhibition was regulated by this accumulation, as hypothesized.
-Overall, it is likely that both nutrient content and reduced sink strength played a role in observed photosynthetic down regulation, but future studies are needed to identify the specific mechanisms which prompted these feedbacks.
+Overall, it is likely that both nutrient limitation and reduced sink strength played a role in observed photosynthetic down regulation, but future studies are needed to identify the specific mechanisms which prompted these feedbacks.
 
@@
 Although reductions in both *A*~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter *et al.* [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth.
-As whole-plant C use efficiency was decreased in seedlings with belowground sink limitation, this suggests that other components of the C balance were affected.
+As estimated whole-plant C use efficiency was decreased in seedlings with belowground sink limitation, this suggests that other components of the C balance were affected.
 These results are especially noteworthy for process-based growth models that parameterize CUE, tissue respiration and C allocation as fixed processes.
@@
 Focusing only on empirical results in this study points to *A*~n~ driving reductions in seedling growth.
-Modelling cumulative net seedling C gain, however, reveals that other components of the C balance, beyond *A*~n~, are required to explain the observed seedling biomass response to sink manipulation.
+Modelling cumulative net seedling C gain, however, suggests that other components of the C balance, beyond *A*~n~, are required to explain the observed seedling biomass response to sink manipulation.
 This finding is noteworthy, as partial accounting of the different mechanisms involved in plant C balance can lead to erroneous conclusions [@valentini2000respiration].
@@
 ##Conclusions
-With a novel field-based design we detected a massive effect of container volume on seedling growth, when compared with naturally planted seedlings.
+With a unique field-based design we detected a massive effect of container volume on seedling growth, when compared with naturally planted seedlings.
 This finding is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants is seldom studied.

### 2016-11-03 manuscript/manuscript_pve.Rmd
added running head
apparently i need to say that the containers had a bottom
edits to abstract removed author contributions manuscript is now double spaced

@@
 Corresponding author: C.E. Campany, email: courtneycampany@gmail.com, telephone: +61 02 4570 1421, fax: +61 02 4570 1103
+
+Runnging Head: Sink limitation and reduced seedling growth
 
@@
 We manipulated soil volume to impose sink limitation of growth in *Eucalyptus tereticornis* seedlings.
-Seedlings were grown in the field in containers of different sizes and planted flush to the soil alongside freely-rooted seedlings.
-Container volume negatively affected aboveground growth throughout the experiment, but after 120 days, biomass distribution in  leaves, stems and roots was not different.
-Photosynthetic capacity was significantly reduced in containerized seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
+Seedlings were grown in the field in containers of different sizes and planted flush to the soil alongside freely-rooted (Free) seedlings.
+Container volume negatively affected aboveground growth throughout the experiment, and light saturated rates of leaf photosynthesis were consistently lower in seedlings in containers (-26%) compared to Free seedlings.
+Photosynthetic capacity was also significantly reduced in containerized seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
+After 120 days, harvested biomass of Free seedlings was on average 84% higher than seedlings in containers, but biomass distribution in leaves, stems and roots was not different.
  However, the reduction in net leaf photosynthesis over the growth period was insufficient to explain the reduction in growth, so that we also observed an apparent reduction in whole-plant C use efficiency (CUE) with container size.
@@
 Six container volumes were used ranging from 5 L to 35 L, with a 22.5 cm diameter, and lengths ranging from 15 to 100 cm.
-Containers were constructed of PVC pipe, which were capped at the bottom end, and were filled with local top soil.
+Containers were constructed of PVC pipe capped at the bottom end and were filled with local top soil.
 Soil in each container was packed to achieve a target soil bulk density that matched local soil conditions of 1.7 g cm^-3^.
@@
 
-# Author Contributions
-CC contributed to the design of the research, data analysis, collection, interpretation and writing the manuscript.
-BM contributed to the design of the research, interpretation and writing the manuscript.
-RD contributed to the design of the research, data analysis, interpretation and writing the manuscript.
-
 # Tables {.unnumbered}

### 2016-11-04 manuscript/manuscript_pve.Rmd
tiny fixes front page
last edits

@@
 \
-Courtney E. Campany^1^, Belinda Medlyn^1^ and Remko A. Duursma^1^
+Courtney E. Campany^1^, Belinda E. Medlyn^1^ and Remko A. Duursma^1^
 
@@
 
-Runnging Head: Sink limitation and reduced seedling growth
+Running Head: Sink limitation and reduced seedling growth
 
@@
 Seedlings were grown in the field in containers of different sizes and planted flush to the soil alongside freely-rooted (Free) seedlings.
-Container volume negatively affected aboveground growth throughout the experiment, and light saturated rates of leaf photosynthesis were consistently lower in seedlings in containers (-26%) compared to Free seedlings.
+Container volume negatively affected aboveground growth throughout the experiment, and light saturated rates of leaf photosynthesis were consistently lower in seedlings in containers (-26 %) compared to Free seedlings.
 Photosynthetic capacity was also significantly reduced in containerized seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
-After 120 days, harvested biomass of Free seedlings was on average 84% higher than seedlings in containers, but biomass distribution in leaves, stems and roots was not different.
+After 120 days, harvested biomass of Free seedlings was on average 84 % higher than seedlings in containers, but biomass distribution in leaves, stems and roots was not different.
 However, the reduction in net leaf photosynthesis over the growth period was insufficient to explain the reduction in growth, so that we also observed an apparent reduction in whole-plant C use efficiency (CUE) with container size.
@@
 Total seedling biomass at harvest was significantly different across container volumes (*P* < 0.001) and between container treatments and Free seedlings (*P* < 0.001, Table `r pvetab1`).
-On average, harvested biomass of Free seedlings was 84% higher than that of seedlings in containers.
+On average, harvested biomass of Free seedlings was 84 % higher than that of seedlings in containers.
 Plant biomass was positively correlated with total leaf area across all treatments (*R*^2^ = 0.97, *P* < 0.001).
 Differences in biomass partitioning to leaves, stems and roots were not different across soil volumes after variation in seedling biomass across treatments was factored in the analysis (Figure `r allocfig`a,b).
-The final harvest root:shoot biomass ratio and  was conserved across all treatments, with a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95% CI = [0.846,1.119]).
+The final harvest root:shoot biomass ratio and  was conserved across all treatments, with a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95 % CI = [0.846,1.119]).
 The ratio of leaf to fine root mass was also not different between treatments (Figure `r allocfig`c).

### 2016-12-12 manuscript/reviewer_response_tree_physiology.Rmd
started reviwer response

---
output:
  word_document:
    reference_docx: manuscriptstyle_pce2.docx
  pdf_document: default
  html_document:
    number_sections: yes
---

```{r, results='asis', echo=FALSE, warning=FALSE}
library(knitr)
opts_knit$set(root.dir = '../')
```

Dr Ram Oren
\
Editor-in-Chief
\
Tree Physiology

\
Dear Professor Mott,

We are grateful for the opportunity to resubmit our manuscript. We thank the reviewers for providing insightful comments to improve our manuscript. We have responded in detail to each comment, which has improved the overall quality of the manuscript. Below, we have itemized our response to each comment from the Editor and both referees.

### **Referee #1**

\
*Reviewer: 1. pp35: "to utilize in growth and storage”*

\
*Response*: editorial change made

\
*Reviewer: 2. pp 40-45: Should be improved. Carbon losses are due to respiration and photorespiration.*

\
*Response*: **Change to net photosynthesis** instead of reviwer suggestion???

\
*Reviewer: 3. pp 63: “…the sink limitation of growth has been explored by manipulations of C source and sink activity…. Examples of …that manipulate C source activity include… and partial defoliation..” (partial defoliation should impose a sink limitation to growth?) Compensatory increases of An are commonly found, but not allowing a higher C net gain leading to sink limitation.*

\
*Response*:

\
*Reviewer: 4. pp 365: No changes in stomatal conductance during the experiment in the described field conditions (Figure 2)?*

\
*Response*: Soil moisture for each seedling were maitained at field capacity, throughout the duration of the experiment, in order to minimize affects of reduced water availability on photosynthesis and growth. The consistent lack of water stress on theses seedlings (see Discussion "Changes in growth and physiology under sink limitation") was an implement of the experimental design.

\
*Reviewer: 5. pp 373: Modelled cumulative net leaf gain could be displayed in a table? (e.g. Table 1)*

\
*Response*:

\
*Reviewer: 5. Table 1 and 2: Reorganize. Biomass, SLA, SRL and FRLD in one table, and chemistry parameters in a second table.*

\
*Response*

*Reviewer: 6. Figure 4: Significant differences between 5 and 15 L soil volumes? Are SE or SD displayed?*

\
*Response*: Bar plots of Figure 4 are means and standard errors which are described in figure caption. Yes, the 5 l containers had smaller rates of A~sat~ than either 15 or 20 L containers. The 5 l containers also had the lowest measured rates overall, indicative of a strong impact of a small container size on sink strength.  For simplicity, we report the large overall difference in Free seedlings and seedlings in containers in terms of rates of photosynthesis.

### **Referee #2**

\
*Reviewer: 1.  It is not clear whether trees used in this experiment come from a nursery or if they were lifted from the field*

\
*Response*: We have clarifed in "Experimental design" that seedlings were nursery seed grown in 40cm tall tubestock.

\
*Reviewer: 2. For Free saplings, it is not clear if roots could have expanded beyond the limits of the subplot or not.*

\
*Response*: We have clarified in "Experimental design" that roots were able to grow unrestricted below border material.

\
*Reviewer: 3 In relation to the “Photosynthetic parameters”, please, define Jmax and Vcmax.*

\
*Response*: We have defined both *V*~cmax~ and *J*~max~ in the section "Photosynthetic parameters"

\
*Reviewer: 4. In “Leaf, root and soil chemistry” indicate how plant samples were dried (temperature, drying time), how they were milled (type of mill used, model, etc.) and how soils were sieved (pore size) and milled (type of mill used, model, etc.)*

\
*Response*: We have clairified in “Leaf, root and soil chemistry” that samples were over dried at 60&degC to a constant mass and ball milled for analysis.We have also added the pore size, drying time and mill type to explanation of soil processing.

\
*Reviewer: 5.  Clairify how did soil volume treatments relate to the 61 digitalized seedlings, which include different *Eucalyptus* species? Were the 61 digitized seedlings grown in different soil volumes*

\
*Response*: The digitized seedlings used here are a collection of digitized plants from differing environments including understorey, glasshouse and plantation (see Duursma et al. 2012).  We selected 5 *Eucalpytus* species from this collection, which represent canopy structures of similar seedling types and sizes. Although the digitized plants are from seperate experiments, they allow us to estimate self shading of the *Eucalyptus* seedlings in this experiment.  As this experiment had an ~4 month duration, leaf counts and total leaf area of seedlings were generally small.  This resulted in only a modest adjsutment of the self-shading factor to total canopy carbon uptake.

\
*Reviewer: 6. Instead of using C concentration data (which they had), the authors assumed that C accounted for half of the final dry mass of seedlings. I think this is quite a strong assumption to make; differences in C concentration above 5% could be in place*

\
*Response*: **insert, I can implement the 48% from dryad wood C database, will change things very little but has citations**

\
*Reviewer: 7.  I would strongly recommend adopting a whole-plant approach and the consideration of all possible sources and sinks in mass-balance models. For example, root exudation can account for an important proportion of the total C budget of a plant, but yet this was not considered in the C budget calculations (nor even suggested as an important component to include in future models, see line 501)*

\
*Response*: The reviewer makes a very good point relating to how mass balance attempts should account for all possible fates of net C uptake. In this study, as in many, it is difficult to accurately measure every facet of C allocation throughout the plant and into the soil. It is entirely possible that aspects of belowground sink limitation could have impacted patterns of root exudation in these seedlings.  As we were not able many the possible fates of net C uptake, such as root exudation or woody tissue respiration, we utilized the mass balance approach to esimate the residual difference in C mass between the modelled seedling C uptake and harvested biomass. It is for this reason that we report differences in CUE, as a far more conservative approach in testing the coordiantion between photosynthesis and growth. For example, modelling the impacts of root exudation would require a priori knowledge of the effects of sink limitation/root restriction/container volume on this process. Consequently, we report the more conservative appraoch but give recommendations for future studies and models *here..here..here*

\
*Reviewer: 8.  I think future empirical and C models should evaluate the inter-relationship between the different sinks and sources AT THE WHOLE PLANT level, and not just the leaf level as indicated in lines 499-501.*

\
*Response*: We absolutely agree with the reviewer. We have made the editorial change to include the fate of C allocation at whole plant level, which includes the addition of root exudation from the previous comment.

\
*Reviewer: 9.  Lines 56-59. Yes, but beware the suggested approach also ignores part of the C budget of plants, because you are not accounting for root exudates.*

\
*Response*:

\
*Reviewer: 10.  Lines 71-72. Yes, indeed, C allocation belowground (both to roots and exudates) is enhanced under high CO2 supply.*

\
*Response*:  **add phillips/iversen sentence**??

\
*Reviewer: 11. Line 90. “Remove” or “removal”?*

\
*Response*: editorial change made

\
*Reviewer: 13.  Line 300. Use of prepositions. Replace “during” by “from”?*

\
*Response*: editorial change made

\
*Reviewer: 14.  Line 301. Remove “significantly” before “among”?*

\
*Response*: editorial change made

\
*Reviewer: 15.  Line 318. “…after variation in seedling biomass across treatments was factored in the analysis”, what do you mean by “factored”?*

\
*Response*: Replaced "factored" to "accounted for"

\
*Reviewer: 16.  Line 319. Remove “and” before “was”.*

\
*Response*: editorial change made

\
*Reviewer: 17.  Line 386. Or root exudates…*

\
*Response*:

\
*Reviewer: 18.  Line 461-462. Yes, and this could also explain the observed lower CUE in trees grown in small containers.*

\
*Response*:  **add exudation somewhere to CUE??**

\
*Reviewer: 19.  Line 513. Remove “to” before “predict”.*

\
*Response*: editorial change made

### 2016-12-12 manuscript/manuscript_pve.Rmd
started reviwer response

@@
 \
-Alternatively, sink limitation can be investigated by manipulating plant tissue C sinks, for example by fruit remove or phloem girdling.
+Alternatively, sink limitation can be investigated by manipulating plant tissue C sinks, for example by fruit removal or phloem girdling.
 In these studies, down regulation of *A*~n~ is often observed, and typically correlates with carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@urban2007girdling; @haouari2013fruit].
@@
 \
-Forty-nine *Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain (western Sydney) cohort.
+Forty-nine *Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were nursery seed grown from a single local Cumberland plain (western Sydney) cohort.
 Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots.
@@
 A border of root exclusion material was buried 0.25 m deep and extended 0.25 m above the ground surface around each subplot to exclude local vegetation, which was further kept out by periodic weeding.
+Roots of Free seedlings were allowed to grow unrestricted below the root exlusion border.
 
@@
 Each AC~i~ curve was started at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l^-1^ at 25 &deg;C at saturating light.
-From these curves the photosynthetic parameters, *J*~max~ and *V*~cmax~, were quantified using the biochemical model of @farquhar1980biochemical and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011].
+From these curves, the maximum rate of Rubisco carboxylation (*V*~cmax~) and the maximum rate of electron transport for RuBP regeneration under saturating light (*J*~max~) were quantified using the biochemical model of @farquhar1980biochemical and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011].
 
@@
 ##Leaf, root and soil chemistry
-Each leaf used in gas exchange measurements and subsamples of harvested roots were dried to a constant mass and milled for analysis of nitrogen (N) content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
-Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were sieved to remove organic material, air dried and milled for analysis of N.
+Each leaf used in gas exchange measurements and subsamples of harvested roots were oven dried at 60&degC to a constant mass and ball milled for analysis of nitrogen (N) content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
+Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were passed through a 1 mm sieve to remove organic material, air dried at 40&degC for 72 h and ball milled for analysis of N.
 Nitrogen concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer and the percentage of N in samples was calculated by comparison with certified standards.
@@
 Plant height, diameter and leaf area diverged between container volumes soon after start of the experiment (Figure `r allomfig`a-c).
-First to diverge was seedling leaf area, which significantly differed among soil volumes (*P* < 0.029) during the 5^th^ week of the experiment.
-Significant differences were then observed in both height (8^th^ week) and then diameter (9^th^ week) significantly among soil volumes (*P* < 0.045 & 0.035, respectively).
+First to diverge was seedling leaf area, which significantly differed among soil volumes (*P* < 0.029) from the 5^th^ week of the experiment.
+Significant differences were then observed in both height (8^th^ week) and then diameter (9^th^ week) among soil volumes (*P* < 0.045 & 0.035, respectively).
 The large reductions in height gain and total leaf area in smaller compared to larger containers continued throughout the experiment.
@@
 Plant biomass was positively correlated with total leaf area across all treatments (*R*^2^ = 0.97, *P* < 0.001).
-Differences in biomass partitioning to leaves, stems and roots were not different across soil volumes after variation in seedling biomass across treatments was factored in the analysis (Figure `r allocfig`a,b).
-The final harvest root:shoot biomass ratio and  was conserved across all treatments, with a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95 % CI = [0.846,1.119]).
+Differences in biomass partitioning to leaves, stems and roots were not different across soil volumes after variation in seedling biomass across treatments was accounted for in the analysis (Figure `r allocfig`a,b).
+The final harvest root:shoot biomass ratio was conserved across all treatments, with a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95 % CI = [0.846,1.119]).
 The ratio of leaf to fine root mass was also not different between treatments (Figure `r allocfig`c).
@@
 Thus, we agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] that the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents.
-Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A*~n~ and the fate of C allocated to growth, respiration and C storage in leaves.
+Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A*~n~ and the fate of C allocated at the whole plant level to growth, respiration, exudation and C storage.
 However, the degree to which these mechanisms regulate the C available for growth will undoubtedly shift across different species and environmental conditions.
@@
 Photosynthesis was affected by both reduced nutrient uptake and the buildup of starch, both potential mechanism for downregulation of *A*~n~.
-Our combined empirical and modeling approach shows that when non-photosynthetic parameters were kept constant, changes in *A*~n~ were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
+Our combined empirical and modeling approach shows that when non-photosynthetic parameters were kept constant, changes in *A*~n~ were not able to fully predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity.
 It has been suggested that tissue sink activity strongly feedbacks onto source activity, causing growth to control *A*~n~ through the demand for C [@korner2013growth; @korner2015paradigm].

### 2016-12-14 manuscript/reviewer_response_tree_physiology.Rmd
edits
edits to manuscript and reviewer comments, made new Table 1 and 2, need to implement new tables in manuscript

@@
 We have responded in detail to each comment, which has improved the overall quality of the manuscript.
-Below, we have itemized our response to each comment from the Editor and both referees.
+Below, we have itemized our response to each comment from both referees.
 
@@
 \
-*Reviewer: 1. pp35: "to utilize in growth and storage”*
+*Reviewer: 1. The role of nutrient defiency may have been underestimated...The relative contribution should be determined...*
+
+\
+*Response*: Unfortunately, we do not have the ability with this data set to determine the relative contribution of nutrient deficiency on the down regulation of photosynthesis.
+We were able to identify not one, but two processes that likely contributed to photosynthetic inhibition.
+Both of these processes, nutrient limitation and starch accumulation, are discussed at length in the discussion.
+We absolutely agree that determining the contribution of each of these processes will provide valuable insights on how sink limitation impacts the carbon balance of plants.
+By providing convincing empirical evidence of these processes, should give a framework for future work to hopefully quantify the contributions of each.
+
+\
+*Reviewer: 2.
+authors indicated that one of the principal question in the paper was to address which physiological process best explains the down-regulation of photosynthesis...the physiological processes involved have not been determined in the work*
+
+\
+*Response*: We agree with the reviewers point here. We have re-worded the first principle question to more accurately address what we were able to test with the presented data.
+
+\
+*Reviewer: 3.
+After reading the title, aim of the work and abstract, it seems that the manuscript focused specifically on carbon source-sink relations and regulation.
+In this regard, too much conclusions are derived from the presented data.
+Nevertheless, discussion and conclusions focused more accurately on the obtained results*
+
+\
+*Response*: We have clarified the role of sink limitation, via nutrient limitation and starch accumulation, on photosynthetic down regulation in the abstract.
+In addition to the response to comment #2, the focus of the beginning of the paper should now better align with the impacts of sink manipulation that are addressed at length in the discussion.
+
+\
+*Reviewer: 4. pp35: "to utilize in growth and storage”*
 
@@
 \
-*Reviewer: 2. pp 40-45: Should be improved. Carbon losses are due to respiration and photorespiration.*
+*Reviewer: 5. pp 40-45: Should be improved. Carbon losses are due to respiration and photorespiration.*
 
 \
-*Response*: **Change to net photosynthesis** instead of reviwer suggestion???
+*Response*: We understand what the reviewer is suggesting but disagree with the suggested change.
+Instead we have re-worded the sentence to say "C entering the planted through net photosynthesis must be balanced by C loss to respiration...".
 
 \
-*Reviewer: 3.
+*Reviewer: 6.
 pp 63: “…the sink limitation of growth has been explored by manipulations of C source and sink activity….
@@
 \
-*Response*:
+*Response*: Regardless of the downstream effects of defoliation on growth processes, the removal of leaves is first and foremost a source manipulation.
+This has been repeatedly shown and is a commonly utilized manipulation in fruit trees and crops species.
 
 \
-*Reviewer: 4. pp 365: No changes in stomatal conductance during the experiment in the described field conditions (Figure 2)?*
+*Reviewer: 7. pp 365: No changes in stomatal conductance during the experiment in the described field conditions (Figure 2)?*
 
 \
-*Response*: Soil moisture for each seedling were maitained at field capacity, throughout the duration of the experiment, in order to minimize affects of reduced water availability on photosynthesis and growth.
-The consistent lack of water stress on theses seedlings (see Discussion "Changes in growth and physiology under sink limitation") was an implement of the experimental design.
+*Response*: Soil moisture for each seedling were maintained at field capacity, throughout the duration of the experiment, in order to minimize affects of reduced water availability on photosynthesis and growth.
+The consistent lack of water stress on theses seedlings (see Discussion "Changes in growth and physiology under sink limitation") was an successful implement of the experimental design.
 
 \
-*Reviewer: 5. pp 373: Modelled cumulative net leaf gain could be displayed in a table? (e.g. Table 1)*
+*Reviewer: 8. pp 373: Modelled cumulative net leaf gain could be displayed in a table? (e.g. Table 1)*
 
 \
-*Response*:
+*Response*: We have added modelled cumulative net leaf gain to Table 1. and refer to it in the Results section "Whole-plant C balance"
 
 \
-*Reviewer: 5. Table 1 and 2: Reorganize. Biomass, SLA, SRL and FRLD in one table, and chemistry parameters in a second table.*
+*Reviewer: 9. Table 1 and 2: Reorganize. Biomass, SLA, SRL and FRLD in one table, and chemistry parameters in a second table.*
 
 \
-*Response*
+*Response*: We agree with the reviewer.  Table 1 and 2 have been reorganized, as suggested, to match how the data are presented in the Results section.
 
-*Reviewer: 6. Figure 4: Significant differences between 5 and 15 L soil volumes? Are SE or SD displayed?*
+\
+*Reviewer: 10. Figure 4: Significant differences between 5 and 15 L soil volumes? Are SE or SD displayed?*
 
@@
 The 5 l containers also had the lowest measured rates overall, indicative of a strong impact of a small container size on sink strength.
-For simplicity, we report the large overall difference in Free seedlings and seedlings in containers in terms of rates of photosynthesis.
+For simplicity, we report the large overall difference in Free seedlings and seedlings in containers in terms of photosynthesis rates.
 
@@
 \
-*Response*: We have clarifed in "Experimental design" that seedlings were nursery seed grown in 40cm tall tubestock.
+*Response*: We have clarified in "Experimental design" that seedlings were nursery seed grown in 40cm tall tube-stock.
 
@@
 \
-*Response*: We have clairified in “Leaf, root and soil chemistry” that samples were over dried at 60&degC to a constant mass and ball milled for analysis.We have also added the pore size, drying time and mill type to explanation of soil processing.
+*Response*: We have clarified in “Leaf, root and soil chemistry” that samples were over dried at 60&degC to a constant mass and ball milled for analysis.We have also added the pore size, drying time and mill type to explanation of soil processing.
 
@@
 \
-*Response*: The digitized seedlings used here are a collection of digitized plants from differing environments including understorey, glasshouse and plantation (see Duursma et al.
+*Response*: The digitized seedlings used here are a collection of digitized plants from differing environments including understory, glasshouse and plantation (see Duursma et al.
 2012).
 We selected 5 *Eucalpytus* species from this collection, which represent canopy structures of similar seedling types and sizes.
-Although the digitized plants are from seperate experiments, they allow us to estimate self shading of the *Eucalyptus* seedlings in this experiment.
+Although the digitized plants are from separate experiments, they allow us to estimate self shading of the *Eucalyptus* seedlings in this experiment.
 As this experiment had an ~4 month duration, leaf counts and total leaf area of seedlings were generally small.
-This resulted in only a modest adjsutment of the self-shading factor to total canopy carbon uptake.
+This resulted in only a modest adjustment of the self-shading factor to total canopy carbon uptake.
 
@@
 \
-*Response*: **insert, I can implement the 48% from dryad wood C database, will change things very little but has citations**
+*Response*: Unfortunately, we do not have available C concentration data for plant tissues.
+Our plant chemistry data set includes leaf and root tissue nitrogen content and leaf TNC and 13C.
+Consequently, we have to assume a C concentration for plant tissues.
+Our use of a 50% C content is likely very close to any assumption of C content that we have to make.
+For example, an average value of C content of angiosperm woody tissues from the DRYAD wood C database is ~48%.
 
@@
 In this study, as in many, it is difficult to accurately measure every facet of C allocation throughout the plant and into the soil.
-It is entirely possible that aspects of belowground sink limitation could have impacted patterns of root exudation in these seedlings.
-As we were not able many the possible fates of net C uptake, such as root exudation or woody tissue respiration, we utilized the mass balance approach to esimate the residual difference in C mass between the modelled seedling C uptake and harvested biomass.
-It is for this reason that we report differences in CUE, as a far more conservative approach in testing the coordiantion between photosynthesis and growth.
-For example, modelling the impacts of root exudation would require a priori knowledge of the effects of sink limitation/root restriction/container volume on this process.
-Consequently, we report the more conservative appraoch but give recommendations for future studies and models *here..here..here*
+As the reviewer point out, it is entirely possible that aspects of belowground sink limitation could have impacted patterns of root exudation in these seedlings.
+However, root exudation is just one of these possible fates, which also include woody tissue respiration, herbivory or VOC's.
+As we were not able measure all of these possible fates of net C uptake, we utilized the mass balance approach to estimate the residual difference between the modelled seedling C uptake and harvested C mass.
+It is for this reason that we report differences in CUE, as a more conservative approach in testing the coordination between photosynthesis and growth.
+Modelling the impacts of other potential fates of C, including root exudation, would require a priori knowledge of the effects of sink limitation/root restriction/container volume on each of these process.
+As so many of these processes are extremely difficult to measure, we do not yet have the ability to make such predictions.
+Possible impacts of root exudation are addressed in "Biomass partitioning under sink limitation", but we do not include it ubiquitously in the discussion because it is just one of many potential pathways of C loss.
 
@@
 \
-*Response*:
+*Response*: see response to comment #7.  Our approach uses the residual C from mass balance to all other potential C losses.
 
@@
 \
-*Response*:  **add phillips/iversen sentence**??
+*Response*:  no change made
 
@@
 \
-*Response*:
+*Response*: No change made. See response to comment #7.
 
@@
 \
-*Response*:  **add exudation somewhere to CUE??**
+*Response*: No change made. See response to comment #7.
 

### 2016-12-14 manuscript/manuscript_pve.Rmd
edits to manuscript and reviewer comments, made new Table 1 and 2, need to implement new tables in manuscript

@@
 Container volume negatively affected aboveground growth throughout the experiment, and light saturated rates of leaf photosynthesis were consistently lower in seedlings in containers (-26 %) compared to Free seedlings.
-Photosynthetic capacity was also significantly reduced in containerized seedlings, and was related to both reduced leaf nitrogen content and starch accumulation.
+Significant reductions in photosynthetic capacity in containerized seedlings was related to both reduced leaf nitrogen content and starch accumulation, indicating direct effects of sink limitation on photosynthetic down regulation.
 After 120 days, harvested biomass of Free seedlings was on average 84 % higher than seedlings in containers, but biomass distribution in leaves, stems and roots was not different.
@@
 \
-Most current models of plant growth are based on the physical principle of mass balance: C entering the plant through photosynthesis must be balanced by C loss to respiration and C allocation to growth and storage.
+Most current models of plant growth are based on the physical principle of mass balance: C entering the plant through net photosynthesis must be balanced by C loss to respiration and C allocation to growth and storage.
 Plant growth is thus predicted as the outcome of the processes of photosynthesis, respiration and allocation.
@@
 We anticipated that both photosynthesis and growth would be reduced under belowground sink limitation.
-The principal questions that we addressed were: 1) which physiological process best explains the down-regulation of photosynthesis?, and 2) does this down-regulation fully explain the observed response of growth, or are other components of the C balance also affected?
+The principal questions that we addressed were: 1) can we identify the main physiological processes that best explain the down-regulation of photosynthesis?, and 2) does this down-regulation fully explain the observed response of growth, or are other components of the C balance also affected?
 
@@
 ##Whole-plant C balance
-Modelled cumulative net leaf C gain over 120 days varied two-fold across containers sizes (25.6 - 55.1 g C).
+Modelled cumulative net leaf C gain over 120 days varied three-fold across containers sizes (23.1 - 79.9 g C).
 The Free seedling control had five-fold greater modelled total C gain than the average of container treatments (213.6 - 42.7&pm;8.2 g C).

### 2016-12-14 master_scripts/table1.R

@@ -1,0 +1,104 @@
+### new table 1 based on reviewer suggestions:
+
+#Biomass, SLA, SRL FRLD, Model C
+
+library(doBy)
+source("functions and packages/functions.R")
+source("functions and packages/plot objects.R")
+
+
+# table1 variables ---------------------------------------------------------
+
+#1. seedling mass
+harvestmass <- read.csv("calculated data/seedling mass.csv") 
+
+  #totalmass
+  table1 <- summaryBy(totalmass~volume, data=harvestmass, FUN=c(mean, se))
+  names(table1)[2:3]<- c("Seedling mass", "Seedling mass_se")
+
+#2. SLAnotnc
+sla_free <- read.csv("calculated data/sla_free_clean.csv")
+  
+  table1 <- merge(table1, sla_free)
+
+#3. SRL
+srl <- read.csv("calculated data/srl_means.csv")
+  srl$srl <- srl$SRL2.mean
+  srl$srl.se <- srl$SRL2.se
+  
+  table1 <- merge(table1,srl[,c(1,4:5)])
+  
+#4. RLD
+  
+rld <- read.csv("calculated data/RLD_agg.csv")
+  
+  table1 <- merge(table1,rld, all=TRUE)
+  
+#seperate dfr in two with mean and se------------------------------------------------------------------
+  tab1_means <- table1[, c(2,4,6,8)]
+  tab1_se <- table1[, c(3,5,7,9)]
+  
+  ###now paste together and round
+  dat1 <- data.frame(paste0(sprintf("%2.1f",round(tab1_means[,1], 1)), " (", sprintf("%3.2f", round(tab1_se[,1],2)),")"))
+  dat2 <- data.frame(paste0(sprintf("%2.1f",round(tab1_means[,2], 1)), " (", sprintf("%3.2f", round(tab1_se[,2],2)),")"))
+  dat3 <- data.frame(paste0(sprintf("%2.1f",round(tab1_means[,3], 1)), " (", sprintf("%2.2f", round(tab1_se[,3],2)),")"))
+  dat4 <- data.frame(paste0(sprintf("%2.1f",round(tab1_means[,4], 1)), " (", sprintf("%2.2f", round(tab1_se[,4],2)),")"))
+ 
+pve_table1 <- cbind(leglab, dat1)
+  pve_table1 <- cbind(pve_table1, dat2)
+  pve_table1 <- cbind(pve_table1, dat3)
[…]

### 2016-12-15 manuscript/reviewer_response_tree_physiology.Rmd
final edits from reviewers, manusript and reply sent to coauthors

@@
 \
-*Reviewer: 1. The role of nutrient defiency may have been underestimated...The relative contribution should be determined...*
+- *Reviewer: 1. The role of nutrient defiency may have been underestimated...The relative contribution should be determined...*
 
@@
 We absolutely agree that determining the contribution of each of these processes will provide valuable insights on how sink limitation impacts the carbon balance of plants.
-By providing convincing empirical evidence of these processes, should give a framework for future work to hopefully quantify the contributions of each.
+By providing convincing empirical evidence of these processes, this experimental desish should provide a framework for future work to quantify the contributions of each.
 
 \
-*Reviewer: 2.
-authors indicated that one of the principal question in the paper was to address which physiological process best explains the down-regulation of photosynthesis...the physiological processes involved have not been determined in the work*
+- *Reviewer: 2.
+Authors indicated that one of the principal question in the paper was to address which physiological process best explains the down-regulation of photosynthesis...the physiological processes involved have not been determined in the work*
 
 \
-*Response*: We agree with the reviewers point here. We have re-worded the first principle question to more accurately address what we were able to test with the presented data.
+*Response*: We agree with the reviewers point here.
+We have re-worded the first principle question to say "1) can we identify the main physiological processes that best explain the down-regulation of photosynthesis?" to more accurately address what we were able to test with the presented data.
 
 \
-*Reviewer: 3.
+- *Reviewer: 3.
 After reading the title, aim of the work and abstract, it seems that the manuscript focused specifically on carbon source-sink relations and regulation.
@@
 \
-*Reviewer: 4. pp35: "to utilize in growth and storage”*
+- *Reviewer: 4. pp35: "to utilize in growth and storage”*
 
@@
 \
-*Reviewer: 5. pp 40-45: Should be improved. Carbon losses are due to respiration and photorespiration.*
+- *Reviewer: 5. pp 40-45: Should be improved. Carbon losses are due to respiration and photorespiration.*
 
@@
 \
-*Reviewer: 6.
+- *Reviewer: 6.
 pp 63: “…the sink limitation of growth has been explored by manipulations of C source and sink activity….
@@
 \
-*Reviewer: 7. pp 365: No changes in stomatal conductance during the experiment in the described field conditions (Figure 2)?*
+- *Reviewer: 7. pp 365: No changes in stomatal conductance during the experiment in the described field conditions (Figure 2)?*
 
@@
 \
-*Reviewer: 8. pp 373: Modelled cumulative net leaf gain could be displayed in a table? (e.g. Table 1)*
+- *Reviewer: 8. pp 373: Modelled cumulative net leaf gain could be displayed in a table? (e.g. Table 1)*
 
@@
 \
-*Reviewer: 9. Table 1 and 2: Reorganize. Biomass, SLA, SRL and FRLD in one table, and chemistry parameters in a second table.*
+- *Reviewer: 9. Table 1 and 2: Reorganize. Biomass, SLA, SRL and FRLD in one table, and chemistry parameters in a second table.*
 
@@
 \
-*Reviewer: 10. Figure 4: Significant differences between 5 and 15 L soil volumes? Are SE or SD displayed?*
+- *Reviewer: 10. Figure 4: Significant differences between 5 and 15 L soil volumes? Are SE or SD displayed?*
 
@@
 \
-*Reviewer: 1.  It is not clear whether trees used in this experiment come from a nursery or if they were lifted from the field*
+- *Reviewer: 1. It is not clear whether trees used in this experiment come from a nursery or if they were lifted from the field*
 
@@
 \
-*Reviewer: 2. For Free saplings, it is not clear if roots could have expanded beyond the limits of the subplot or not.*
+- *Reviewer: 2. For Free saplings, it is not clear if roots could have expanded beyond the limits of the subplot or not.*
 
@@
 \
-*Reviewer: 3 In relation to the “Photosynthetic parameters”, please, define Jmax and Vcmax.*
+- *Reviewer: 3 In relation to the “Photosynthetic parameters”, please, define Jmax and Vcmax.*
 
@@
 \
-*Reviewer: 4.
+- *Reviewer: 4.
 In “Leaf, root and soil chemistry” indicate how plant samples were dried (temperature, drying time), how they were milled (type of mill used, model, etc.) and how soils were sieved (pore size) and milled (type of mill used, model, etc.)*
@@
 \
-*Response*: We have clarified in “Leaf, root and soil chemistry” that samples were over dried at 60&degC to a constant mass and ball milled for analysis.We have also added the pore size, drying time and mill type to explanation of soil processing.
+*Response*: We have clarified in “Leaf, root and soil chemistry” that samples were over dried at 60&deg;C to a constant mass and ball milled for analysis.
+We have also added the pore size, drying time and mill type to the explanation of soil processing.
 
 \
-*Reviewer: 5.
-Clairify how did soil volume treatments relate to the 61 digitalized seedlings, which include different *Eucalyptus* species?
+- *Reviewer: 5.
+Clairify how did soil volume treatments relate to the 61 digitalized seedlings, which include different Eucalyptus species?
 Were the 61 digitized seedlings grown in different soil volumes*
@@
 We selected 5 *Eucalpytus* species from this collection, which represent canopy structures of similar seedling types and sizes.
-Although the digitized plants are from separate experiments, they allow us to estimate self shading of the *Eucalyptus* seedlings in this experiment.
+Although the digitized plants are from separate experiments, they allowed us to estimate self shading of the *Eucalyptus* seedlings in this experiment.
 As this experiment had an ~4 month duration, leaf counts and total leaf area of seedlings were generally small.
@@
 \
-*Reviewer: 6.
+- *Reviewer: 6.
 Instead of using C concentration data (which they had), the authors assumed that C accounted for half of the final dry mass of seedlings.
@@
 \
-*Reviewer: 7.
+- *Reviewer: 7.
 I would strongly recommend adopting a whole-plant approach and the consideration of all possible sources and sinks in mass-balance models.
@@
 As so many of these processes are extremely difficult to measure, we do not yet have the ability to make such predictions.
-Possible impacts of root exudation are addressed in "Biomass partitioning under sink limitation", but we do not include it ubiquitously in the discussion because it is just one of many potential pathways of C loss.
+Possible impacts of root exudation are addressed in "Biomass partitioning under sink limitation", but we do not address it ubiquitously in the discussion because it is just one of many potential pathways of C loss.
 
 \
-*Reviewer: 8.
+- *Reviewer: 8.
 I think future empirical and C models should evaluate the inter-relationship between the different sinks and sources AT THE WHOLE PLANT level, and not just the leaf level as indicated in lines 499-501.*
@@
 \
-*Reviewer: 9.  Lines 56-59. Yes, but beware the suggested approach also ignores part of the C budget of plants, because you are not accounting for root exudates.*
+- *Reviewer: 9. Lines 56-59. Yes, but beware the suggested approach also ignores part of the C budget of plants, because you are not accounting for root exudates.*
 
 \
-*Response*: see response to comment #7.  Our approach uses the residual C from mass balance to all other potential C losses.
+*Response*: see response to comment #7.  Our approach uses the residual C from mass balance to estimate all other potential C losses.
 
 \
-*Reviewer: 10.  Lines 71-72. Yes, indeed, C allocation belowground (both to roots and exudates) is enhanced under high CO2 supply.*
+- *Reviewer: 10. Lines 71-72. Yes, indeed, C allocation belowground (both to roots and exudates) is enhanced under high CO2 supply.*
 
@@
 \
-*Reviewer: 11. Line 90. “Remove” or “removal”?*
+- *Reviewer: 11. Line 90. “Remove” or “removal”?*
 
@@
 \
-*Reviewer: 13.  Line 300. Use of prepositions. Replace “during” by “from”?*
+- *Reviewer: 13. Line 300. Use of prepositions. Replace “during” by “from”?*
 
@@
 \
-*Reviewer: 14.  Line 301. Remove “significantly” before “among”?*
+- *Reviewer: 14. Line 301. Remove “significantly” before “among”?*
 
@@
 \
-*Reviewer: 15.  Line 318. “…after variation in seedling biomass across treatments was factored in the analysis”, what do you mean by “factored”?*
+- *Reviewer: 15. Line 318. “…after variation in seedling biomass across treatments was factored in the analysis”, what do you mean by “factored”?*
 
@@
 \
-*Reviewer: 16.  Line 319. Remove “and” before “was”.*
+- *Reviewer: 16. Line 319. Remove “and” before “was”.*
 
@@
 \
-*Reviewer: 17.  Line 386. Or root exudates…*
+- *Reviewer: 17. Line 386. Or root exudates…*
 
@@
 \
-*Reviewer: 18.  Line 461-462. Yes, and this could also explain the observed lower CUE in trees grown in small containers.*
+- *Reviewer: 18. Line 461-462. Yes, and this could also explain the observed lower CUE in trees grown in small containers.*
 
@@
 \
-*Reviewer: 19.  Line 513. Remove “to” before “predict”.*
+- *Reviewer: 19. Line 513. Remove “to” before “predict”.*
 

### 2016-12-15 manuscript/manuscript_pve.Rmd
final edits from reviewers, manusript and reply sent to coauthors

@@
 A border of root exclusion material was buried 0.25 m deep and extended 0.25 m above the ground surface around each subplot to exclude local vegetation, which was further kept out by periodic weeding.
-Roots of Free seedlings were allowed to grow unrestricted below the root exlusion border.
+Roots of Free seedlings were allowed to grow unrestricted below the root exclusion border.
 
@@
 \
-Overall, SRL was higher in seedlings in containers compared to Free seedlings but only in some of the container size treatments (Table `r pvetab2`, *P* = 0.009).
-Fine root length density was significantly higher in the two smallest container sizes and was the lowest in the largest container size (Table `r pvetab2`, *P* < 0.001).
+Overall, SRL was higher in seedlings in containers compared to Free seedlings but only in some of the container size treatments (Table `r pvetab1`, *P* = 0.009).
+Fine root length density was significantly higher in the two smallest container sizes and was the lowest in the largest container size (Table `r pvetab1`, *P* < 0.001).
 Over the duration of the experiment SLA~f~ was higher in Free seedlings, but was not different across container sizes (Table `r pvetab1`, *P* < 0.001) and this pattern was evident beginning in the first gas exchange measurement campaign (*P* < 0.001).
@@
 Leaf N~f~ was significantly higher in Free seedlings and the largest container volume compared to the smaller container volumes at the onset of gas exchange measurements (6th week, *P* < 0.001).
-Throughout the remainder of the experiment the smallest container volume had significantly lower leaf N~f~ than other soil volumes, while Free seedlings maintained the highest leaf N~f~ (Table `r pvetab1`, *P* < 0.001).
+Throughout the remainder of the experiment the smallest container volume had significantly lower leaf N~f~ than other soil volumes, while Free seedlings maintained the highest leaf N~f~ (Table `r pvetab2`, *P* < 0.001).
 Leaf starch content in the smallest container was ca.
-double  that of Free seedlings (*P* = 0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table `r pvetab1`).
+double  that of Free seedlings (*P* = 0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table `r pvetab2`).
 Differences in leaf starch between the Free seedling and the smallest container were evident during the first gas exchange campaign (*P* = 0.001).
@@
 Although *g*~s~ in Free seedlings was generally higher than those in containers (Table `r pvetab3`, *P* < 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not change throughout the course of the experiment.
-Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table `r pvetab1`).
+Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table `r pvetab2`).
 Combined, these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment.
@@
 This similarity indicates that nutrient leaching from Free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
-
 ##Whole-plant C balance
-Modelled cumulative net leaf C gain over 120 days varied three-fold across containers sizes (23.1 - 79.9 g C).
+Modelled cumulative net leaf C gain over 120 days varied three-fold across containers sizes (Table `r pvetab1`).
 The Free seedling control had five-fold greater modelled total C gain than the average of container treatments (213.6 - 42.7&pm;8.2 g C).
@@
 # Tables {.unnumbered}
-**Table 1**.Responses of plant and leaf characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
-Each value reflects the mean (&pm; 1 standard error) for each treatment.
-Seedling mass and leaf $\delta$^13^C values are from final harvest.
+**Table 1**.
+Responses of plant characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments, including modelled cumulative net leaf carbon gain.
+Empirical values reflect the mean (&pm; 1 standard error) for each treatment.
+Seedling mass, SRL, and fine root length density (FRLD) values are from final harvest.
 Values of SLA~f~, leaf starch, leaf sugars and leaf N~f~ represent overall means across measurement campaigns (n=6).
-Different letters represent significant differences between treatments.
-The volume effect *P* value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
+Values for FRLD were only calculated for seedlings in containers as Free seedlings had potentially unlimited soil volume to exploit.
+For empirical values, different letters represent significant differences between treatments.
+The volume effect *P* value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only differences between seedlings in containers.
 
@@
                     "SLA~f~ (m^2^ kg^-1^)",
-                        "Leaf Starch (%)", 
-                        "Leaf Sugars (%)", 
-                        "Leaf N~f~ (%)",
-                        paste0("Leaf ", "$\\delta$","^13^C"," (\u2030)")) %>%
+                    "SRL (m g^-1^)",
+                    "FRLD (m dm^-3^)",
+                    "Total Net C Gain (g)") %>%
   sprinkle(rows= 1, part="head",bold=TRUE)%>%
@@
 **Table 2**.
-Responses of root characteristics of *Eucalyptus tereticornis* seedlings to soil volume treatments.
+Responses of leaf and root chemistry of *Eucalyptus tereticornis* seedlings to soil volume treatments.
 Each value reflects the mean (&pm; 1 standard error) for each treatment.
-All values are from the final harvest.
-Values for fine root length density (FRLD) were only calculated for seedlings in containers as Free seedlings had potentially unlimited soil volume to exploit.
+Values of leaf starch, leaf sugars and leaf N~f~ represent overall means across measurement campaigns (n=6).
+Leaf $\delta$^13^C and root N values are from final harvest.
 Different letters represent significant differences between treatments.
-The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings, except for FRLD which represents only differences between seedlings in containers.
+The volume effect P value represents the overall difference between seedlings with soil volume restriction and the control seedlings.
 ```{r table2, echo=FALSE, warning=FALSE}
@@
   sprinkle_colnames("Volume (L)", 
-                        "Root N (%)", 
-                        "SRL (m g^-1^)",
-                        "FRLD (m dm^-3^)") %>%
+                    "Leaf Starch (%)", 
+                    "Leaf Sugars (%)", 
+                    "Leaf N~f~ (%)",
+                    paste0("Leaf ", "$\\delta$","^13^C"," (\u2030)"),
+                    "Root N (%)") %>%
   sprinkle(rows= 1, part="head",bold=TRUE)%>%

### 2016-12-15 master_scripts/phys_table.R

@@ -100,7 +100,7 @@ pve_table2$leglab <- as.character(pve_table2$leglab)
 pve_table3 <- rbind(pve_table2, pval)
 
   
-write.csv(pve_table3, "master_scripts/pve_table2.csv", row.names=FALSE)
+write.csv(pve_table3, "master_scripts/pve_table3.csv", row.names=FALSE)
 
 
 

### 2016-12-20 manuscript/reviewer_response_tree_physiology.Rmd
remkos comments on review response

@@
 
-Dr Ram Oren
+Prof Ram Oren
 \
@@
 \
-Dear Professor Mott,
+Dear Professor Oren,
 
@@
 \
-*Response*: Unfortunately, we do not have the ability with this data set to determine the relative contribution of nutrient deficiency on the down regulation of photosynthesis.
+*Response*: Unfortunately, we do not have the ability with these data to determine the relative contribution of nutrient deficiency on the down regulation of photosynthesis.
 We were able to identify not one, but two processes that likely contributed to photosynthetic inhibition.
@@
 We absolutely agree that determining the contribution of each of these processes will provide valuable insights on how sink limitation impacts the carbon balance of plants.
-By providing convincing empirical evidence of these processes, this experimental desish should provide a framework for future work to quantify the contributions of each.
+By providing convincing empirical evidence of these processes, this experimental design should provide a framework for future work to quantify the contributions of each.
 
@@
 \
-*Response*: Soil moisture for each seedling were maintained at field capacity, throughout the duration of the experiment, in order to minimize affects of reduced water availability on photosynthesis and growth.
+*Response*: Soil moisture for each seedling was maintained at field capacity, throughout the duration of the experiment, in order to minimize affects of reduced water availability on photosynthesis and growth.
 The consistent lack of water stress on theses seedlings (see Discussion "Changes in growth and physiology under sink limitation") was an successful implement of the experimental design.
@@
 *Response*: Bar plots of Figure 4 are means and standard errors which are described in figure caption.
-Yes, the 5 l containers had smaller rates of A~sat~ than either 15 or 20 L containers.
-The 5 l containers also had the lowest measured rates overall, indicative of a strong impact of a small container size on sink strength.
+Yes, the 5 L containers had smaller rates of A~sat~ than either 15 or 20 L containers.
+The 5 L containers also had the lowest measured rates overall, indicative of a strong impact of a small container size on sink strength.
 For simplicity, we report the large overall difference in Free seedlings and seedlings in containers in terms of photosynthesis rates.
@@
 We selected 5 *Eucalpytus* species from this collection, which represent canopy structures of similar seedling types and sizes.
-Although the digitized plants are from separate experiments, they allowed us to estimate self shading of the *Eucalyptus* seedlings in this experiment.
-As this experiment had an ~4 month duration, leaf counts and total leaf area of seedlings were generally small.
+Although the digitized plants are from separate experiments, they allowed us to estimate self shading of the *Eucalyptus* seedlings in this experiment from regressions with total plant leaf area and canopy dimensions (cf.
+Duursma et al.
+2012).
+As this experiment had a ~4 month duration, leaf counts and total leaf area of seedlings were generally small.
 This resulted in only a modest adjustment of the self-shading factor to total canopy carbon uptake.
@@
 For example, an average value of C content of angiosperm woody tissues from the DRYAD wood C database is ~48%.
+These small differences have no impact on our conclusions.
 

### 2017-01-12 amodel_test.Rmd
quick html file to Remko to finalize A-tnc-N reviewer response. Will integrate these edits into response letter and Results section

---
title: "Amass_tnc_nitro comment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Model Code

```{r model, echo=TRUE, message=FALSE}
source("functions and packages/startscripts.R")
library(lme4)
library(lmerTest)
library(effects)

photo_chem <- read.csv("calculated data/Amax_chem.csv")
#run volume format func
photo_chem<- vollab_func(photo_chem)
#get better units for plotting
photo_chem$starch_perc <- photo_chem$starch*100
photo_chem$nitro_mg <- photo_chem$Nmass_notnc *1000

#model and stats
Afit_full <- lmer(A_mass ~ nitro_mg+starch_perc+nitro_mg:starch_perc + (1|ID), data=photo_chem)

# drop interaction 
Afit_noint <- lmer(A_mass ~ nitro_mg + starch_perc + (1|ID), data=photo_chem)

# only N
Afit_N <- lmer(A_mass ~ nitro_mg + (1|ID), data=photo_chem)

# only TNC
Afit_TNC <- lmer(A_mass ~ starch_perc + (1|ID), data=photo_chem)

# Calculate R2
library(MuMIn)
r.squaredGLMM(Afit_full)
r.squaredGLMM(Afit_noint)
r.squaredGLMM(Afit_N)
r.squaredGLMM(Afit_TNC)
```

### **Referee #1**

\
- *Reviewer: 1. The role of nutrient defiency may have been underestimated...The relative contribution should be determined...*

\
*Response*:

We were successfully able to identify not one, but two processes that likely contributed to photosynthetic inhibition. We agree that determining the contribution of both of the processes, nutrient limitation and starch accumulation, is important as they are addressed at length in the discussion. The full model including both nitrogen and starch explains 36% of the variation in *A*~max~ on a mass basis. Including only nitrogen in the model explains 25% and with only starch explains 11% of the variation. Consequently, nutrient deficiency composes 69% of the explained variation and starch accumulation the rest. We have added these new results in the "Gas exchange and photosynthetic parameters" section of the Results. By providing convincing empirical evidence of these processes, this experimental design should provide a framework for future work to further quantify the contributions of each.

\
*Results section*:

The relationship between leaf N~f~ and leaf starch with *A*~max~ on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated with both leaf N~f~ and leaf starch (both *P* < 0.001). Leaf N~f~ and leaf starch explained 25% and 11% of the variation in *A*~max~ on a mass basis, respectively.

### 2017-01-12 manuscript/manuscript_pve.Rmd
quick html file to Remko to finalize A-tnc-N reviewer response. Will integrate these edits into response letter and Results section

@@
 Across all measurement campaigns, mean *A*~sat~ (Figure `r asatfig`) and *A*~max~ (Table `r pvetab3`) were consistently higher in Free seedlings than in containers (26 % and 29 %, respectively).
-The relationship between leaf starch and leaf N~f~ on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated with both leaf N~f~ and leaf starch (both *P* < 0.001).
+The relationship between leaf starch and leaf N~f~ with *A*~max~ on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated with both leaf N~f~ and leaf starch (both *P* < 0.001).
 We used predictions from the linear mixed effect model equation to visualize these relationships of *A*~max~ to either leaf N~f~ or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
@@
 This similarity indicates that nutrient leaching from Free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
+
 ##Whole-plant C balance

### 2017-01-25 manuscript/manuscript_pve_editor.Rmd
started response to editor.  big change is dropping asat figure and adding it to table 3

--- 2016-12-15 manuscript/manuscript_pve.Rmd
@@
 allocfig <- "3"
-asatfig <- "4"
-achemfig <- "5"
-cuefig <- "6"
+achemfig <- "4"
+cuefig <- "5"
 
@@
 Freshly detached leaves were collected at least 1 hour after sundown and placed inside a conifer chamber attached to the Licor 6400.
-Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions.
+Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions (11.5-13.4 &deg;C).
 *R* was logged 5 times for each leaf after CO~2~ and water vapour flux values stabilized in the conifer chamber.
@@
 ##Leaf, root and soil chemistry
-Each leaf used in gas exchange measurements and subsamples of harvested roots were oven dried at 60&degC to a constant mass and ball milled for analysis of nitrogen (N) content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
-Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were passed through a 1 mm sieve to remove organic material, air dried at 40&degC for 72 h and ball milled for analysis of N.
+Each leaf used in gas exchange measurements and subsamples of harvested roots were oven dried at 60 &deg;C to a constant mass and ball milled for analysis of nitrogen (N) content, $\delta$^13^C, and total non-structural carbohydrates (TNC).
+Pre-planting soil samples (n=6) and subsamples of soil from each container following harvest were passed through a 1 mm sieve to remove organic material, air dried at 40 &deg;C for 72 h and ball milled for analysis of N.
 Nitrogen concentrations of leaf and soil samples were determined using a Carlo Erba CE1110 elemental analyzer and the percentage of N in samples was calculated by comparison with certified standards.
@@
 Differences in biomass partitioning to leaves, stems and roots were not different across soil volumes after variation in seedling biomass across treatments was accounted for in the analysis (Figure `r allocfig`a,b).
-The final harvest root:shoot biomass ratio was conserved across all treatments, with a slightly higher shoot than root mass ($\overline{x}$ = 0.904, 95 % CI = [0.846,1.119]).
+The final harvest root:shoot biomass ratio was conserved across all treatments, with a slightly higher shoot than root mass ($\overline{x}$ = 0.90, 95 % CI = [0.85,1.12]).
 The ratio of leaf to fine root mass was also not different between treatments (Figure `r allocfig`c).
@@
 At the first measurement campaign, both *A*~sat~ and *A*~max~ were significantly higher in the Free seedling treatment compared to seedlings in containers (both *P* < 0.001).
-Across all measurement campaigns, mean *A*~sat~ (Figure `r asatfig`) and *A*~max~ (Table `r pvetab3`) were consistently higher in Free seedlings than in containers (26 % and 29 %, respectively).
-The relationship between leaf starch and leaf N~f~ on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated with both leaf N~f~ and leaf starch (both *P* < 0.001).
+Across all measurement campaigns, mean *A*~sat~ and *A*~max~ (Table `r pvetab3`) were consistently higher in Free seedlings than in containers (26 % and 29 %, respectively).
+The relationship between leaf starch and leaf N~f~ on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was correlated with both leaf N~f~ and leaf starch (both *P* < 0.001).
 We used predictions from the linear mixed effect model equation to visualize these relationships of *A*~max~ to either leaf N~f~ or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
@@
 Both *J*~max~ and *V*~cmax~ were significantly higher in Free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`).
-Overall, the *J*~max~ / *V*~cmax~ ratio was conserved across all treatments (1.6&pm;0.02), which is consistent with findings across many tree species [@medlyn1996optimal; @leuning1997scaling; @medlyn1999effects; @warren2003photosynthesis; @crous2008elevated].
+Overall, the *J*~max~ / *V*~cmax~ ratio was conserved across all treatments (1.6&pm;0.02).
 Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`).
@@
 We found a strong reduction of growth in containerized plants.
-Leaf *A*~n~ was also reduced, but this reduction was insufficient to fully explain the reduction in growth, implying that components such as whole-plant respiratory loss were also likely affected.
+Leaf *A*~n~ was also reduced, but this reduction was insufficient to fully explain the reduction in growth, implying that components such as non-leaf respiratory losses were also likely affected.
 
@@
 Each value reflects the mean (&pm; 1 standard error) for each treatment.
-*A*~max~, *R*~dark~ and *g*~s~ are each measured at 25 &deg;C.
-Values of *A*~max~, *g*~s~ and *g*~1~ represent overall means across measurement campaigns (n=6).
+*A*~max~, *A*~sat~, *R*~dark~ and *g*~s~ are each measured at 25 &deg;C.
+Values of *A*~max~, *A*~sat~, *g*~s~ and *g*~1~ represent overall means across measurement campaigns (n=6).
 R, *J*~max~ and *V*~cmax~ values are means of two measurement campaigns at beginning and end of gas exchange measurements.
@@
                         "*A*~max~ ($\\mu$mol m^-2^ s^-1^)", 
+                        "*A*~sat~ ($\\mu$mol m^-2^ s^-1^)",
                         "*R*~dark~ ($\\mu$mol m^-2^ s^-1^)",
@@
 \
-```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600,eval=includeFigs}
-source("master_scripts/A_stats_plotting.R")
-```  
-**Figure 4**.
-Light-saturated photosynthesis (A~sat~) was reduced in containerized seedlings compared to freely-rooted seedlings ('Free').
-Shown are soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25 &deg;C.
-Different letters represent significant differences between treatments (p < 0.05).
-\
 ```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, eval=includeFigs}
@@
 ```  
-**Figure 5**.
+**Figure 4**.
 Photosynthetic capacity on a leaf mass basis (A~mass~, measured at saturating light and [CO~2~]) was correlated to both leaf starch and nitrogen content.
@@
 ```  
-**Figure 6**.
+**Figure 5**.
 The final biomass attained per unit total photosynthesis over the duration of the experiment.

### 2017-01-25 manuscript/make_figures.R

@@ -17,7 +17,6 @@ fn <- function(...)file.path("manuscript",...)
 to_pdf(source("master_scripts/allometryplotting.R"), fn("Figure1.pdf"), width=6, height=7.8)
 to_pdf(source("master_scripts/airvars_plotting.R"), fn("Figure2.pdf"), width=6, height=8)
 to_pdf(source("master_scripts/allocation_plotting.R"), fn("Figure3.pdf"), width=6, height=8)
-to_pdf(source("master_scripts/A_stats_plotting.R"), fn("Figure4.pdf"), width=6, height=6)
-to_pdf(source("master_scripts/Amax_TNC_N_plotting2.R"), fn("Figure5.pdf"), width=8, height=6)
-to_pdf(source("master_scripts/cuefig.R"), fn("Figure6.pdf"), width=6, height=6)
+to_pdf(source("master_scripts/Amax_TNC_N_plotting2.R"), fn("Figure4.pdf"), width=8, height=6)
+to_pdf(source("master_scripts/cuefig.R"), fn("Figure4.pdf"), width=6, height=6)
 

### 2017-01-25 master_scripts/phys_table.R

@@ -6,24 +6,24 @@ source("functions and packages/plot objects.R")
        
 ###variabvles:  Amax, Rd, Jmax, VCmax, gs, g1
   
-#1:Amax
+#1:Amax and Asat
 A_means <- read.csv("calculated data/A_treatment_means.csv")
   A_means$volume <- as.numeric(c("5", "10", "15", "20", "25", "35", "1000"))
 
-table2 <- A_means[, 1:3]
+table3 <- A_means
 
 #2: Rd
 
 rd <- read.csv("calculated data/rdark_clean.csv")
 
-table2 <- merge(table2, rd[,c(1:2,4)])
+table3 <- merge(table3, rd[,c(1:2,4)])
        
  
 ##2-3: jmax, vcmax
 phys <- read.csv("calculated data/jmax_vcmax_clean.csv")
   names(phys)[2:5]<- c("Jmax", "Vcmax", "Jmax_se", "Vcmax_se")
 
-table2 <- merge(table2, phys)
+table3 <- merge(table3, phys)
        
 #4. gs
 gs <- read.csv("calculated data/conductance.csv")
@@ -31,7 +31,7 @@ gs <- read.csv("calculated data/conductance.csv")
 
   gs_agg <- summaryBy(gs ~ volume, data=gs2, FUN=c(mean, se))
 
-table2 <- merge(table2, gs_agg)
+table3 <- merge(table3, gs_agg)
 
 #5. g1 (uses mean of g1 date)
 g1 <- read.csv("calculated data/g1_pred.csv")
@@ -39,24 +39,25 @@ g1 <- read.csv("calculated data/g1_pred.csv")
   g1_agg <- summaryBy(g1_date ~ volume, data=g1, FUN=c(mean, se))
   names(g1_agg)[2:3]<- c("g1", "g1_se")
 
-table2 <- merge(table2, g1_agg)
+table3 <- merge(table3, g1_agg)
 
 
 ###now sort the table into correct var + se--------------------------------------------------------------------
-phys_tab <-table2[,c(1,2,3,4,5,6,8,7,9,10,11,12,13)]
+phys_tab <-table3[,c(1,2,3,4,5,6,7,8,10, 9,11, 12,13,14,15)]
 
 
 #seperate dfr in two with mean and se, omit volume for now
-phys_means <- phys_tab[, c(2,4,6,8,10,12)]
[…]

### 2017-01-25 manuscript/reviewer_response_tree_physiology.Rmd

@@
 \
-*Response*: Unfortunately, we do not have the ability with these data to determine the relative contribution of nutrient deficiency on the down regulation of photosynthesis.
-We were able to identify not one, but two processes that likely contributed to photosynthetic inhibition.
-Both of these processes, nutrient limitation and starch accumulation, are discussed at length in the discussion.
-We absolutely agree that determining the contribution of each of these processes will provide valuable insights on how sink limitation impacts the carbon balance of plants.
-By providing convincing empirical evidence of these processes, this experimental design should provide a framework for future work to quantify the contributions of each.
+*Response*: We were successfully able to identify not one, but two processes that likely contributed to photosynthetic inhibition.
+We agree that determining the contribution of both of the processes, nutrient limitation and starch accumulation, is important as they are addressed at length in the discussion.
+The full model including both nitrogen and starch explains 36% of the variation in *A*~max~ on a mass basis.
+Including only nitrogen in the model explains 25% and with only starch explains 11% of the variation.
+The interaction between nitrogen and starch explained practically no variation.
+Consequently, nutrient deficiency composes 69% of the explained variation and starch accumulation the rest.
+We have added these new results in the "Gas exchange and photosynthetic parameters" section of the Results.
+By providing convincing empirical evidence of these processes, this experimental design should provide a framework for future work to further quantify the contributions of each.
 

### 2017-01-25 manuscript/manuscript_pve.Rmd

--- 2016-12-15 manuscript/manuscript_pve.Rmd
@@
 Across all measurement campaigns, mean *A*~sat~ (Figure `r asatfig`) and *A*~max~ (Table `r pvetab3`) were consistently higher in Free seedlings than in containers (26 % and 29 %, respectively).
-The relationship between leaf starch and leaf N~f~ on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated with both leaf N~f~ and leaf starch (both *P* < 0.001).
+The relationship between leaf N~f~ and leaf starch with *A*~max~ on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was highly correlated with both leaf N~f~ and leaf starch (both *P* < 0.001).
+Leaf N~f~ and leaf starch explained 25% and 11% of the variation in *A*~max~ on a mass basis, respectively.
+The interaction between leaf N~f~ and leaf starch explained practically no variation in *A*~max~ on a mass basis.
 We used predictions from the linear mixed effect model equation to visualize these relationships of *A*~max~ to either leaf N~f~ or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
@@
 ##Do reductions in photosynthesis explain reductions in seedling growth?
-We use a simple approach to estimate cumulative seedling C gain with measured reductions in leaf *A*~n~ , via soil volume effects.
+We use a simple approach to estimate cumulative seedling C gain with measured reductions in leaf *A*~n~, via soil volume effects.
 Although reductions in both *A*~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter *et al.* [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth.

### 2017-01-25 manuscript/editor_response_tree_physiology.Rmd
moved editor response

---
output:
  word_document:
    reference_docx: manuscriptstyle_pce2.docx
  pdf_document: default
  html_document:
    number_sections: yes
---

```{r, results='asis', echo=FALSE, warning=FALSE}
library(knitr)
opts_knit$set(root.dir = '../')
```

Prof Daniel Epron
\
Editor
\
Tree Physiology

We are grateful for the opportunity to resubmit our manuscript. We thank the editor for providing insightful comments to improve our manuscript. We have responded in detail to each comment, which has improved the overall quality of the manuscript. Below, we have itemized our response to each comment from the editor.

- *Comment: 1. It seems that there are two different effects: rooting volume and container/free rooting. And it seems that the latter is dominating and the clear relations with rooting volume are often missing... ignoring this later treatment may depply change your way of interpreting the results*

\
*Response*:

\
- *Comment: 2. L42: you may have mentioned here the other C loss such as exudation, VOC...*

\
*Response*:

\

- *Comment: 3. L212: you may give the temperature range during the respiration measurement*

\
*Response*: Temperature range for dark respiration measurements added to methods

\
- *Comment: 4. L226 and 229: typing errors*

\
*Response*: editorial change made

\

- *Comment: 5. L230: I don’t understand your response to the reviewer ‘Unfortunately, we do not have available C concentration data for plant tissues’. As soon as you get N, you may get C easily when using a Carlo Erba CE1110 elemental analyser.*

\
*Response*: The reviewer asked for C concentration data for the whole plant instead of assuming 50% for woody plant tissues.  We only have C and N data for leaves and roots.  We therefore use the 50% assumption to convert dry seedling biomass to final seedling C.

\

- *Comment: 6. L253-254: R, expressed in gC d-1 is not a mass based leaf respiration. And it is not clear that “leaf respiration is included in the calculation of P”. If it is included, it should not be subtracted again. To get the daily C gain of the seedling, what it is missing there is the night respiration of the foliage and the respiration of the other plant organ. So I guess G is not the daily C gain but the daily C uptake (or gross C gain versus net C gain). But it needs to be clarified.*

\
*Response*:

\
- *Comment: 7. L264: How do simulated An values fit with measured Asat?*

\
*Response*:

\
- *Comment: 8. L253-254: R, expressed in gC d-1 is not a mass based leaf respiration. And it is not clear that “leaf respiration is included in the calculation of P”. If it is included, it should not be subtracted again. To get the daily C gain of the seedling, what it is missing there is the night respiration of the foliage and the respiration of the other plant organ. So I guess G is not the daily C gain but the daily C uptake (or gross C gain versus net C gain). But it needs to be clarified.*

\
*Response*:

\
- *Comment: 9. L288: CUE is the ratio of net C gain (Pn) to gross C gain (Pg): CUE = Pn/Pg. With Pn=Pg-R, with R the respiration of the seedling. In your calculation CUE is the ratio of produced biomass divided by net leaf C gain. Leaf respiration is subtracted so that daily net leaf C gain is Pg-Rleaf. It is clear at the end that CUE is in your case proportion of modelled cumulative net leaf C gain allocated to observed seedling biomass. But it might be confusing for readers so you may try to improve this part by introducing earlier this notion of net leaf C gain, give a clear definition of leaf An. And at several place, it is not clear in leaf An is on a leaf area basis or at the whole plant basis.*

\
*Response*:

\
- *Comment: 10. L253-254: R, expressed in gC d-1 is not a mass based leaf respiration. And it is not clear that “leaf respiration is included in the calculation of P”. If it is included, it should not be subtracted again. To get the daily C gain of the seedling, what it is missing there is the night respiration of the foliage and the respiration of the other plant organ. So I guess G is not the daily C gain but the daily C uptake (or gross C gain versus net C gain). But it needs to be clarified.*

\
*Response*:

\
- *Comment: 11. L326: two digits is enough: 𝑥 = 0.90, 95 % CI = [0.85,1.12].*

\
*Response*: editorial change made

\
- *Comment: 12. L348: Asat can be added in Table 3 and Fig 4 removed*

\
*Response*: editorial change made

\
- *Comment: 13. L349-350: These sentences are confusing: does the first sentence refer to Amax on a leaf area basis. Please clarify.*

\
*Response*:

\
- *Comment: 14. L351: I will not say that Amass is highly correlated with both leaf Nf and leaf starch, when it only accounts for 28% and 11% of the total variations.*

\
*Response*: editorial change made (removed "highly")

\
- *Comment: 15. L359: I am not convinced that Amax was positively correlated with final harvest biomass. The correlation is driven by the free rooting values. Variation in Amax across rooting volume does not reflect those of biomass in the last point is removed. It means that the co-variation is not so much driven by soil volume. The only clear effect is between container/ free rooting. But it is no more a correlation.*

\
*Response*:

\
- *Comment: 16. L365-366: Remove citations from the results section. Move that sentence in the discussion if it is really needed (I don’t think so).*

\
*Response*: editorial change made

\
- *Comment: 17. L394: Leaf An (an leaf area basis) or whole plant C gain? Please clarify.*

\
*Response*:

\
- *Comment: 18. L395: not whole plant respiration loss, because leaf respiration is already accounted. So this is something that ‘non-leaf whole plant respiration’.*

\
*Response*: editorial change made

\
- *Comment: 19.L410: this is not true. There is large reduction in biomass related to container size, but not so much effect of container size on Amax.*

\
*Response*: 
\
- *Comment: 20. L413: what is An here? Leaf area or whole plant based?*

\
*Response*: 
\
- *Comment: 21. L430-431. Correlation between leaf N and An (what is it?) has not been shown in the result sections.*

\
*Response*: 
\
- *Comment: 22. L434: the connexion between root N and N uptake is not trivial.*

\
*Response*: 
\
- *Comment: 23. L441: You did not measure available soil N pool but total soil N, which is different. It would have been interesting to know if microbial N mineralization is affected by the containers or not. The key might not be at the plant level but at the microbe level. And what about other nutrients such as available P?*

\
*Response*: 
\
- *Comment: 24. L443: again, what is An? And please show us the evidence of a sink limitation on An of seedlings in container. There is not so much effect of container size on leaf photosynthetic parameter in Table 3*

\
*Response*:

\
- *Comment: 25. L449: I am not convinced that the decline in Amax is correlated with higher starch content, at least not across the different container size. This is not really an effect of rooting volume but again container versus free soil.*

\
*Response*: 
\
- *Comment: 26. L477: It is not true that “increases in specific root length were detected in several of the soil volume treatments” It is detected in only one, and not in the smallest one.*

\
*Response*: 
\
- *Comment: 27. L483: There is no reduction in leaf photosynthesis due to the restricted soil volume, according to the data you reported in Table 3. Make clear what is leaf An. The reduction in whole plant assimilation may mainly be due to a reduction in plant leaf area, which in fact is only evident for the largest soil volume. Final plant leaf area can be added in table 1 with stats. It will be helpful as it is not so easy to visualize differences on figure 1.*

\
*Response*: 
\
- *Comment: 28. L477: L483-484: I disagree that reductions in Amax and biomass were strongly correlated. The correlation is driven by high value of the free soil. R2 will drop from 0.88 to 0.32 if you remove this last treatment.*

\
*Response*: 
\
- *Comment: 29. L486: Again, CUE does not really decrease with belowground limitation. There is no effect of rooting volume on CUE if you don’t include free rooting values (R2 cue~container volume = 0.003). There is an effect container/ free rooting, but this effect is not related to the volume of the container, so not clearly related to belowground sink limitation.*

\
*Response*: 
\

### 2017-02-02 manuscript/editor_response_tree_physiology.Rmd
edits from editor to manuscript and editor response.  double checked the Amax to G stats

@@
 \
-*Response*:
+*Response*: Editorial change made.  We have included more examples of C losses beyond respiration.  The rest of the paragraph is also adjusted to discuss "C loss" as a more general inclusive term.
 
@@
 
+We have removed the statement "Leaf respiration is included in the calculation of *P*." and added a suffice description of how dark respiration was calculated for each 15 minute interval to then caluclate *A*~n~.
+
 \
@@
 \
-*Response*:
+*Response*: We agree with the editor here.
+We have introduced a new term *A*~mass to represent *A*max on a mass basis.
+This should help easily distinguish between the two variables in the text and is now consistent with Figure 4.
 
@@
 \
-*Response*:
+*Response*: This is entirely true and was overlooked by the authors.
+This statement has been removed from the results section.
+Perhaps this provides additionally evidence of how A and G can become decoupled under sink manipulation.
 
@@
 \
-*Response*: 
+*Response*: We have corrected this statment in the discussion to more accurately reflect the observed results.
 \

### 2017-02-02 manuscript/manuscript_pve_editor.Rmd
edits from editor to manuscript and editor response.  double checked the Amax to G stats

@@
 \
-Most current models of plant growth are based on the physical principle of mass balance: C entering the plant through net photosynthesis must be balanced by C loss to respiration and C allocation to growth and storage.
-Plant growth is thus predicted as the outcome of the processes of photosynthesis, respiration and allocation.
+Most current models of plant growth are based on the physical principle of mass balance: C entering the plant through net photosynthesis must be balanced by C allocation to growth and storage and C losses such as respiration, root exudation, volatile organic compounds and tissue turnover.
+Plant growth is thus predicted as the outcome of the processes of photosynthesis, C allocation and C loss.
 It is easy to see how source-limited growth can be implemented in such models: increasing source activity increases photosynthetic C uptake, flowing through to increased growth.
-It is less easy to know how to implement sink limitation of growth in such models, because it requires that we know whether, and how, sink limitation influences the contributing processes of photosynthesis, respiration and allocation.
+It is less easy to know how to implement sink limitation of growth in such models, because it requires that we know whether, and how, sink limitation influences the contributing processes of photosynthesis, C allocation and C loss.
 It has been suggested that sink limitation affects the C balance by causing a down-regulation of photosynthetic rate, possibly mediated by carbohydrate accumulation [@arp1991effects; @paul2001sink;@ainsworth2004testing; @ronchi2006growth; @nebauer2011photosynthesis], but there is also evidence that photosynthesis and growth can become strongly decoupled under sink limitation [@muller2011water;@leuzinger2013sink], suggesting that other processes must also be affected.
@@
 where *L* is modelled total plant leaf area (m^2^), *P* is the daily C assimilation per unit leaf area (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), and *R* is the mass based leaf respiration (g C d^-1^).
-Leaf respiration is included in the calculation of *P*.
 
@@
 *P* was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *R*~dark~ and *g*~1~) for each treatment and meteorological data from an onsite weather station.
-Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above), *R*~dark~ was empirically measured and the *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values.
+Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above).
+*R*~dark~ was was estimated using Eq.
+(2) from ***Tjoekler 2008***, which was parameterized with a mean reference empircal measurement for each treatment, a Q~10~ value of 1.86 from a seperate experiment using the same tube stock seedlings and air temperature at each time step.
+
+\
+(2)
+$$R~dark~ = R_{ref}Q_{10}~^{(T-T_{ref})/10}$$
+
+The *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values.
 Methods of the coupled leaf gas exchange model are also described in Duursma *et al.* [-@duursma2014peaked].
@@
 Across all measurement campaigns, mean *A*~sat~ and *A*~max~ (Table `r pvetab3`) were consistently higher in Free seedlings than in containers (26 % and 29 %, respectively).
-The relationship between leaf starch and leaf N~f~ on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis was correlated with both leaf N~f~ and leaf starch (both *P* < 0.001).
-We used predictions from the linear mixed effect model equation to visualize these relationships of *A*~max~ to either leaf N~f~ or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
-Across all measurement campaigns and treatments *A*~max~ was higher when leaf N~f~ was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
-*A*~max~  was also lower when leaf starch was high as higher leaf N~f~ often did not coincide with high leaf starch (Figure `r achemfig`b).
+The relationship between leaf starch and leaf N~f~ on a mass basis was marginally significant (*P* = 0.058), but *A*~max~ on a mass basis (*A*~mass~) was correlated with both leaf N~f~ and leaf starch (both *P* < 0.001).
+We used predictions from the linear mixed effect model equation to visualize these relationships of *A*~mass~ to either leaf N~f~ or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`).
+Across all measurement campaigns and treatments *A*~mass~ was higher when leaf N~f~ was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a).
+*A*~mass~  was also lower when leaf starch was high as higher leaf N~f~ often did not coincide with high leaf starch (Figure `r achemfig`b).
 Overall, *A*~max~ was positively correlated with final harvest biomass across all seedlings (*P* < 0.001).
@@
 Additionally, physical restriction of root proliferation could have impacted root development and morphology prior to shifts in mass partitioning.
-Here, increases in specific root length were detected in several of the soil volume treatments.
-This is not surprising as plants in containers have been shown to have different root morphology to field grown plants [@nesmith1998effect].
+Although plants in containers have been shown to have different root morphology to field grown plants [@nesmith1998effect], increases in specific root length were detected in only one of the the soil volume treatments.
 The poor soil quality used in our experiment and root restriction, however, likely decreased the capacity of this morphological response to increase N uptake.

### 2017-02-02 manuscript/make_figures.R

@@ -18,5 +18,5 @@ to_pdf(source("master_scripts/allometryplotting.R"), fn("Figure1.pdf"), width=6,
 to_pdf(source("master_scripts/airvars_plotting.R"), fn("Figure2.pdf"), width=6, height=8)
 to_pdf(source("master_scripts/allocation_plotting.R"), fn("Figure3.pdf"), width=6, height=8)
 to_pdf(source("master_scripts/Amax_TNC_N_plotting2.R"), fn("Figure4.pdf"), width=8, height=6)
-to_pdf(source("master_scripts/cuefig.R"), fn("Figure4.pdf"), width=6, height=6)
+to_pdf(source("master_scripts/cuefig.R"), fn("Figure5.pdf"), width=6, height=6)
 

### 2017-02-05 manuscript/editor_response_tree_physiology.Rmd
minor edits to editor response.  Tested final leaf area to volume

@@
 *Response*: 
+We have removed the statement "Leaf respiration is included in the calculation of *P*." and added a suffice description of how dark respiration was calculated for each 15 minute interval to then caluclate *A*~n~.
 
@@
 - *Comment: 8.
-L253-254: R, expressed in gC d-1 is not a mass based leaf respiration.
-And it is not clear that “leaf respiration is included in the calculation of P”.
-If it is included, it should not be subtracted again.
-To get the daily C gain of the seedling, what it is missing there is the night respiration of the foliage and the respiration of the other plant organ.
-So I guess G is not the daily C gain but the daily C uptake (or gross C gain versus net C gain).
-But it needs to be clarified.*
-
-\
-*Response*:
-
-\
-- *Comment: 9.
 L288: CUE is the ratio of net C gain (Pn) to gross C gain (Pg): CUE = Pn/Pg.
@@
 \
-- *Comment: 10.
-L253-254: R, expressed in gC d-1 is not a mass based leaf respiration.
-And it is not clear that “leaf respiration is included in the calculation of P”.
-If it is included, it should not be subtracted again.
-To get the daily C gain of the seedling, what it is missing there is the night respiration of the foliage and the respiration of the other plant organ.
-So I guess G is not the daily C gain but the daily C uptake (or gross C gain versus net C gain).
-But it needs to be clarified.*
-
-\
-*Response*:
-
-We have removed the statement "Leaf respiration is included in the calculation of *P*." and added a suffice description of how dark respiration was calculated for each 15 minute interval to then caluclate *A*~n~.
-
-\
-- *Comment: 11. L326: two digits is enough: 𝑥 = 0.90, 95 % CI = [0.85,1.12].*
+- *Comment: 9. L326: two digits is enough: 𝑥 = 0.90, 95 % CI = [0.85,1.12].*
 
@@
 \
-- *Comment: 12. L348: Asat can be added in Table 3 and Fig 4 removed*
+- *Comment: 10. L348: Asat can be added in Table 3 and Fig 4 removed*
 
@@
 \
-- *Comment: 13. L349-350: These sentences are confusing: does the first sentence refer to Amax on a leaf area basis. Please clarify.*
+- *Comment: 11. L349-350: These sentences are confusing: does the first sentence refer to Amax on a leaf area basis. Please clarify.*
 
@@
 *Response*: We agree with the editor here.
-We have introduced a new term *A*~mass to represent *A*max on a mass basis.
+We have introduced a new term *A*~mass~ to represent *A*~max~ on a mass basis.
 This should help easily distinguish between the two variables in the text and is now consistent with Figure 4.
@@
 \
-- *Comment: 14. L351: I will not say that Amass is highly correlated with both leaf Nf and leaf starch, when it only accounts for 28% and 11% of the total variations.*
+- *Comment: 12. L351: I will not say that Amass is highly correlated with both leaf Nf and leaf starch, when it only accounts for 28% and 11% of the total variations.*
 
@@
 \
-- *Comment: 15.
+- *Comment: 13.
 L359: I am not convinced that Amax was positively correlated with final harvest biomass.
@@
 \
-- *Comment: 16. L365-366: Remove citations from the results section. Move that sentence in the discussion if it is really needed (I don’t think so).*
+- *Comment: 14. L365-366: Remove citations from the results section. Move that sentence in the discussion if it is really needed (I don’t think so).*
 
@@
 \
-- *Comment: 17. L394: Leaf An (an leaf area basis) or whole plant C gain? Please clarify.*
+- *Comment: 15. L394: Leaf An (an leaf area basis) or whole plant C gain? Please clarify.*
 
@@
 \
-- *Comment: 18. L395: not whole plant respiration loss, because leaf respiration is already accounted. So this is something that ‘non-leaf whole plant respiration’.*
+- *Comment: 16. L395: not whole plant respiration loss, because leaf respiration is already accounted. So this is something that ‘non-leaf whole plant respiration’.*
 
@@
 \
-- *Comment: 19.L410: this is not true. There is large reduction in biomass related to container size, but not so much effect of container size on Amax.*
+- *Comment: 17. L410: this is not true. There is large reduction in biomass related to container size, but not so much effect of container size on Amax.*
 
@@
 \
-- *Comment: 20. L413: what is An here? Leaf area or whole plant based?*
+- *Comment: 18. L413: what is An here? Leaf area or whole plant based?*
 
@@
 \
-- *Comment: 21. L430-431. Correlation between leaf N and An (what is it?) has not been shown in the result sections.*
+- *Comment: 19. L430-431. Correlation between leaf N and An (what is it?) has not been shown in the result sections.*
 
@@
 \
-- *Comment: 22. L434: the connexion between root N and N uptake is not trivial.*
+- *Comment: 20. L434: the connexion between root N and N uptake is not trivial.*
 
@@
 \
-- *Comment: 23.
+- *Comment: 21.
 L441: You did not measure available soil N pool but total soil N, which is different.
@@
 \
-- *Comment: 24.
+- *Comment: 22.
 L443: again, what is An?
@@
 \
-- *Comment: 25.
+- *Comment: 23.
 L449: I am not convinced that the decline in Amax is correlated with higher starch content, at least not across the different container size.
@@
 \
-- *Comment: 26. L477: It is not true that “increases in specific root length were detected in several of the soil volume treatments” It is detected in only one, and not in the smallest one.*
+- *Comment: 24. L477: It is not true that “increases in specific root length were detected in several of the soil volume treatments” It is detected in only one, and not in the smallest one.*
 
@@
 \
-- *Comment: 27.
+- *Comment: 25.
 L483: There is no reduction in leaf photosynthesis due to the restricted soil volume, according to the data you reported in Table 3.
@@
 \
-- *Comment: 28.
+- *Comment: 26.
 L477: L483-484: I disagree that reductions in Amax and biomass were strongly correlated.
@@
 \
-- *Comment: 29.
+- *Comment: 27.
 L486: Again, CUE does not really decrease with belowground limitation.

### 2017-02-05 Stats/photomass.R

@@ -26,14 +26,6 @@ PS <- add_campaign_date(PS)
 #Amax_means for Data table-----------------------------------------------------------------------
 PSmax <- subset(PS, type=="Amax")
 
-#mean of 5 logs per plant
-PSmax_spot<- summaryBy(. ~ ID +Date, FUN=mean, keep.names=TRUE, data=PSmax)
-  PSmax_spot$volume <- as.factor(PSmax_spot$volume)
-
-#mean by plant over all dates, then treatment means
-PSmax_ID <- summaryBy(Photo~volume + ID, FUN=mean, keep.names=TRUE, data=PSmax_spot)
-  PSmax_ID$volume <- as.factor(PSmax_ID$volume)
-
 ###merge Amax with biomass
   
 massphoto <- merge(harvestmass[, c(1:2,11)], PSmax_ID)
@@ -77,3 +69,35 @@ mfree <- mean(massphoto[massphoto$volume == 1000, "totalmass"])
 mpot <-  mean(massphoto[massphoto$volume != 1000, "totalmass"])
 
 meffect <- (mfree-mpot)/mfree
+
+
+
+# harvest leaf area -------------------------------------------------------
+leaves <- read.csv("calculated data/LA_harvest.csv")
+leaves$volume <- as.factor(leaves$volume)
+library(multcomp)
+library(MuMIn)
+
+leafvol <-  lme(totalarea ~ volume, random= ~1|ID, data=leaves)
+library(car)
+Anova(leafvol)
+anova(leafvol)
+summary(leafvol)
+library(visreg)
+visreg(leafvol)
+r.squaredGLMM(leafvol)
+
+
+la_pots <- leaves[leaves$volume != 1000,]
+la_pots <- droplevels(la_pots)
+potleaf <- lme(totalarea ~ volume, random= ~1|ID, data=la_pots[la_pots$volume != 1000,])
+anova(potleaf)
+Anova(potleaf)
+summary(potleaf)
+visreg(potleaf)
+
+tukey_leaf<- glht(leafvol, linfct = mcp(volume = "Tukey"))
+leaf_siglets <-cld(tukey_leaf)
+leaf_siglets2 <- leaf_siglets$mcletters$Letters
+#write.csv(mass_siglets2, "master_scripts/sigletters/sigletts_plant/sl_leaf.csv", row.names=FALSE)   
+

### 2017-02-05 clean Scripts/A_plotting.R

@@ -35,6 +35,20 @@ PSsat_agg <- summaryBy(Photo ~ Date + volume, data=PSsat,
 
 PSsat_agg$SE <- with(PSsat_agg, Photo.sd/sqrt(Photo.length))
   PSsat_agg$volume <- as.factor(PSsat_agg$volume)
+  
+# asat ----------------------------------------------------------------------------------- 
+  
+ windows(7,7) 
+  
+  plot(Photo.mean ~ Date, data=PSsat_agg, xlab="", ylab=satlab,
+       ylim=c(10,27))
+  with(PSsat_agg, arrows(Date, Photo.mean, Date, Photo.mean+SE, angle=90, col=palette(),length=0.05))
+  with(PSsat_agg, arrows(Date, Photo.mean, Date, Photo.mean-SE, angle=90, col=palette(),length=0.05))
+  d_ply(PSsat_agg, .(volume), function(x) points(x$Photo.mean ~ x$Date,  
+                                                 col=x$volume, type="b", pch = pchs[x$volume], cex=1.6))
+  legend("topright", leglab, pch=pchs,text.font=3, inset=0.02, title=vollab, col=palette(), bty='n')
+  
+
 #----------------------------------------------------------------------------------------------------
 #two panel graph of A
 par(mfrow=c(2,1), omi=c(1,0,0.5,0.5),mar=c(0,5,0,0),mgp = c(2.5, 1, 0))
@@ -47,8 +61,9 @@ title(ylab=maxlab)
 with(PSagg, arrows(Date, Photo.mean, Date, Photo.mean+SE, angle=90, col=palette(),length=0.05))
 with(PSagg, arrows(Date, Photo.mean, Date, Photo.mean-SE, angle=90, col=palette(),length=0.05))
 d_ply(PSagg, .(volume), function(x) points(x$Photo.mean ~ x$Date,  
-                                           col=x$volume, type="b", pch = pchs[x$volume],cex=1.6,))
+                                           col=x$volume, type="b", pch = pchs[x$volume],cex=1.6))
 legend("bottomright", leglab, pch=pchs,text.font=3, inset=0.02, title=vollab, col=palette(), bty='n')
+
 
 #Asat
 plot(Photo.mean ~ Date, data=PSsat_agg, xlab="", ylab=satlab,

### 2017-02-06 manuscript/editor_response_tree_physiology.Rmd
editor comments reviews

@@
 And it seems that the latter is dominating and the clear relations with rooting volume are often missing...
-ignoring this later treatment may depply change your way of interpreting the results*
+ignoring this later treatment may depply change your way of interpreting the results.
+Even the stats are strongly influenced by this treatment (effect on residual error for example).*
 
 \
-*Response*:
+*Response*: We agree with the editor's comments that the effects of soil volume have not been properly accounted for in several places in the manuscript.
+Particularly in the discussion we have clarified the nature of the effect type, where soil volume effects have often been over-emphasized.
+We agree that the stats are strongly influenced by the Free seedling, but this is also representative of the observed effects of root restirction on *A*~sat~, TNC and leaf N across all containers throughout all measurement campaigns.
+As the impacts of root restriction and poor quality soil impacted were evident across all treatments
+We feel that addressing individual effects of specific volume treatments, or combining soil volume treament effects, would overly complicate the paper and would not improve our intrepretation of the results.
 
@@
 \
-*Response*: 
-We have removed the statement "Leaf respiration is included in the calculation of *P*." and added a suffice description of how dark respiration was calculated for each 15 minute interval to then caluclate *A*~n~.
+*Response*: The editor makes several good points here.
+We have re-written the equation to better descibe the way daily total leaf net C gain (*P*~day~) was calculated.
+We have also removed the statement "Leaf respiration is included in the calculation of *P*." and added a accurate description of how the area based respiration component was calculated at each 15 minute interval to then model leaf level net photosynthesis rates.
 
@@
 \
-*Response*:
+*Response*: We agree with each of the editors points here.
+With a comment #6 we have now clearly defined the "total net leaf C gain term".
+As the edigor points out there are several places where leaf *A*~n~ is discussed inappropriately, especially in the discussion.
+Throughout the manuscript we have revised use of terms for C gain to accurately reflect either measured photosynthesis rates (*A*~sat~), leaf level rates of net photosynthesis (*A*~n~) or modelled cumulative total net leaf C gain (*P*~day~).
 
@@
 \
-*Response*: editorial change made
+*Response*: editorial change made.
 
@@
 \
-*Response*: This is entirely true and was overlooked by the authors.
-This statement has been removed from the results section.
-Perhaps this provides additionally evidence of how A and G can become decoupled under sink manipulation.
+*Response*: This point was overlooked by the authors. This statement has been removed from the results section.
 
@@
 
-\
-*Response*: 
+*Response*: We agree with the editor's comments.
+There is convincing evidence that nutrient uptake was negatively affected in this experiment but the mechanism is yet unidentified.
+Understanding the processes by which belowground sink manipulation manifests belowground will be important for future expereiments using local soils.
+We hope that this dataset and experimental design can aid in future experiments to further investigate belowground sink limitation.
+
 \
@@
 *Response*:
+
 \
@@
 *Response*: We have corrected this statment in the discussion to more accurately reflect the observed results.
+
 \
+
 - *Comment: 25.
@@
 \
-*Response*: 
+*Response*: We have added both measured *A*~sat~ and harvested leaf area into Table 1 and 3, respectively.
+Both of *A*~sat~ and leaf area were significantly reduced in containers from the free seedlings.
+
 \

### 2017-02-06 manuscript/manuscript_pve_editor.Rmd
editor comments reviews

@@
 ##Modelled net seedling C uptake
-The daily net C gain of seedlings (*G*), from @makela1997carbon, is given by
+The daily total net C gain of seedlings (*G*), is given by
 
@@
 (1)
-$$G(t) = L(P~\sigma - R)$$
+$$G(t) = \sigma LP_{day}$$
 
-where *L* is modelled total plant leaf area (m^2^), *P* is the daily C assimilation per unit leaf area (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), and *R* is the mass based leaf respiration (g C d^-1^).
+where $\sigma$ is a self-shading parameter, *L* is modelled total plant leaf area (m^2^), and  *P*~day~ is the net daily C assimilation per unit leaf area (g C m^-2).
 
 \
-*P* was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *R*~dark~ and *g*~1~) for each treatment and meteorological data from an onsite weather station.
+*P* was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *g*~1~ and *R*~dark~) for each treatment and meteorological data from an onsite weather station.
 Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above).
+The *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values.
 *R*~dark~ was was estimated using Eq.
@@
 $$R~dark~ = R_{ref}Q_{10}~^{(T-T_{ref})/10}$$
-
-The *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values.
 Methods of the coupled leaf gas exchange model are also described in Duursma *et al.* [-@duursma2014peaked].
 Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A*~n~ rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
-*P* was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
+*P*~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
 This resulted in 120 unique values of *P* for each soil volume treatment, one value for each day of the experiment.
-Thus, each daily time step for model runs included a value of *P* that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
+Thus, each daily time step for model runs included a value of *P*~day~ that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
 

### 2017-02-06 clean Scripts/AsatAleaf.R

@@ -1,0 +1,54 @@
+#apply photosynthesis model to generate PS over the experiment
+#compare to actual measurements
+
+source("functions and packages/startscripts.R")
+
+#READ DATA, calculated data for A parameters
+
+#generated jmax and vcmax
+jmax_vcmax <- read.csv("calculated data/jmax_vcmax_clean.csv")
+
+#Rdark Q10 equations by volume
+rdarkq10 <- read.csv("calculated data/rdarkq10.csv")
+rd25_clean <- read.csv("calculated data/rdark_clean.csv")
+
+#---------------------------------------------------------------------------------------------
+#merge ps parameters to met data
+
+A_model <- merge(jmax_vcmax, rdarkq10[,1:2], by="volume")
+A_model <- merge(A_model, rd25_clean[,1:2], by="volume")
+
+q25_drake <- 1.86
+
+#rdark_eq$rd25_euct <- with(rdark_eq, rd12.3*(q25_drake^((abs(CTleaf-25))/10)))
+
+#refit RD
+A_model$Rd_pred2 <- with(A_model, rd12.3 * q25_drake^((25-12.3)/10))
+
+#------------------------------------------------------------------------------------------------------
+#input parameters from optimal conductance model (using nls)
+
+g1 <- read.csv("calculated data/g1_pred.csv")
+g1_agg <- summaryBy(g1_date ~ volume, data=g1, keep.names=TRUE)
+
+
+A_model <- merge(A_model, g1_agg, by="volume")
+
+#-------------------------------------------------------------------------------------------------
+#now run the model (includes pred Rdark from crouseq10, and gs parameters modelled from spot measurements)
+
+#convert RH to VPD
+A_model$VPD <- RHtoVPD(A_model$RH, A_model$temp, Pa=101)
+
+#model, should return the aleaf for every 15 minutes. (will retrun Aleaf at 15min interval)
+A_sat_pred <- Photosyn(RH=70,Ca=400, PPFD=1800, Tleaf=25, 
+                   Jmax=A_model$Jmax.mean, Vcmax=A_model$Vcmax.mean, Rd=A_model$Rd_pred2, g1=A_model$g1_date)
+
+
+##compare to Asat
+A_means <- read.csv("calculated data/A_treatment_means.csv")
+A_means$volume <- as.numeric(c("5", "10", "15", "20", "25", "35", "1000"))
+Asat <- A_means[, c(1, 4)]
+
[…]

### 2017-02-06 manuscript/editor_response_tree_physiology.Rmd
most editor comments finished, added leaf area to table 1 and stats into results

@@
 \
-
 - *Comment: 3. L212: you may give the temperature range during the respiration measurement*
@@
 \
-
 - *Comment: 5.
@@
 \
-
 - *Comment: 6.
@@
 \
-*Response*:
+*Response*: editorial change made.  Change *A*~n~ to *A*~sat (measured values)
 
@@
 \
-*Response*: 
+*Response*: editorial change made.  Changed *A*~n~ to *A*~sat (measured values).  
 \
@@
 \
-*Response*: 
+*Response*: We have corrected *A*~n~ to *A*~mass~, which is reported in the results section.
 \
@@
 \
-*Response*: 
+*Response*: We agree with the editor. We have changd this sentence to give a quantative description of root N content differences between roots of Free seedlings and seedlings in containers (+15 %). 
 \
@@
 
+\
 *Response*: We agree with the editor's comments.
@@
 Understanding the processes by which belowground sink manipulation manifests belowground will be important for future expereiments using local soils.
-We hope that this dataset and experimental design can aid in future experiments to further investigate belowground sink limitation.
+We hope that this dataset and experimental design can aid in future experiments to further investigate the mecanisms underpinning belowground sink limitation.
 
@@
 \
-*Response*:
+*Response*: editorial change made.
+Changed *A*~n~ to *A*~sat (measured values).
+As with comment #10, *A*~sat values are added in Table 3 to show reductions in measured leaf level photosynthesis in containerized seedlings.
 
@@
 \
-*Response*:
+*Response*: We agree with the editor.
+The use of *A*~max~ was incorrectly used here.
+We have edited this sentence to include the correlation with *A*~mass~ and starch, which is described in the results.
 
@@
 \
-
 - *Comment: 25.
@@
 \
-*Response*: We have added both measured *A*~sat~ and harvested leaf area into Table 1 and 3, respectively.
-Both of *A*~sat~ and leaf area were significantly reduced in containers from the free seedlings.
+*Response*: We have added both measured harvested leaf area and *A*~sat~ into Table 1 and 3, respectively.
+Both *A*~sat~ and leaf area were significantly reduced in seedings lin containers compared to the free seedlings.
 
@@
 \
-*Response*: 
+*Response*: editorial change made. We have removed the word "strongly"
+
 \
@@
 \
-*Response*: 
-\
+*Response*: We have changed this sentence to more accurately reflect the modelling results by removing reference to "belowground sink limitation" and stating that CUE was reduced in containerized seedlings.

### 2017-02-06 manuscript/manuscript_pve_editor.Rmd
most editor comments finished, added leaf area to table 1 and stats into results

@@
 *R*~dark~ was was estimated using Eq.
-(2) from ***Tjoekler 2008***, which was parameterized with a mean reference empircal measurement for each treatment, a Q~10~ value of 1.86 from a seperate experiment using the same tube stock seedlings and air temperature at each time step.
+(2) from @atkin2005response, which was parameterized with a mean reference empircal measurement for each treatment, a Q~10~ value of 1.86 from a seperate experiment using the same tube stock seedlings, a reference air temperature and air temperatures at each time step.
 
@@
 Total seedling biomass at harvest was significantly different across container volumes (*P* < 0.001) and between container treatments and Free seedlings (*P* < 0.001, Table `r pvetab1`).
-On average, harvested biomass of Free seedlings was 84 % higher than that of seedlings in containers.
+Total seedling leaf area at harvest was significantly different between container treatments and Free seedlings (*P* < 0.001, Table `r pvetab1`).
+On average, both harvested biomass and total leaf area of Free seedlings was >80 % higher than that of seedlings in containers.
 Plant biomass was positively correlated with total leaf area across all treatments (*R*^2^ = 0.97, *P* < 0.001).
@@
 We found a strong reduction of growth in containerized plants.
-Leaf *A*~n~ was also reduced, but this reduction was insufficient to fully explain the reduction in growth, implying that components such as non-leaf respiratory losses were also likely affected.
+Leaf *A*~sat~ was also reduced, but this reduction was insufficient to fully explain the reduction in growth, implying that components such as non-leaf respiratory losses were also likely affected.
 
@@
 This observation initially suggests that sink limitation may be driving the down regulation of photosynthesis, and thus growth.
-However, there are several possible mechanisms that can explain reduced *A*~n~ in small containers including increased soil temperatures, reduced water availability or nutrient content, or reduced sink strength [@poorter2012pot].
+However, there are several possible mechanisms that can explain reduced *A*~sat~ in small containers including increased soil temperatures, reduced water availability or nutrient content, or reduced sink strength [@poorter2012pot].
 It was therefore necessary to examine each of these factors to determine the mechanism by which the induced belowground sink limitation triggered photosynthetic down regulation.
@@
 \
-With high rates of *g*~s~, non-limiting leaf water potential ($\Psi$~pd~), and consistent leaf $\delta$^13^C across soil volume treatments, there was little evidence that water stress caused the reduction in *A*~n~.
+With high rates of *g*~s~, non-limiting leaf water potential ($\Psi$~pd~), and consistent leaf $\delta$^13^C across soil volume treatments, there was little evidence that water stress caused the reduction in *A*~sat~.
 This finding is consistent with other container size studies without drought treatments.
 For example, reduced *A*~max~ in cotton seedlings grown at elevated CO~2~ was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased *g*~s~ [@thomas1991root].
-Similarly, severe reductions in *A*~n~ in coffee plants were not attributed to impacts of container size on leaf water potentials or *g*~s~ [@ronchi2006growth].
-It is thus likely that reductions in *A*~n~ of well-watered seedlings observed in our study of *E.
+Similarly, severe reductions in leaf photosynthesis in coffee plants were not attributed to impacts of container size on leaf water potentials or *g*~s~ [@ronchi2006growth].
+It is thus likely that reductions in *A*~at~ of well-watered seedlings observed in our study of *E.
 tereticornis* seedlings are not the result of limiting soil moisture availability.
@@
 \
-With respect to nutrient availability, reductions in *A*~n~ were positively correlated with decreases in leaf N~f~ and leaf N~f~ was considerably reduced for seedlings in containers.
+With respect to nutrient availability, reductions in *A*~mass~ were positively correlated with decreases in leaf N~f~ and leaf N~f~ was considerably reduced for seedlings in containers.
 Since reductions in leaf N~f~ were detected with TNC-free leaf mass, TNC dilution of leaf N was accounted for in all seedlings.
 It is possible that either physical root restriction or decreased supply reduced seedling N uptake in small containers.
-Although root N was on average higher in Free seedlings at the end of the experiment, it was not consistently higher than the smallest container volume treatment.
-Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N~f~ in Free seedlings, but this effect is unknown.
+Overall, root N in Free seedlings was ~15 % higher than containerized seedlings at the end of the experiment.
+Unrestricted mycorrhizal recruitment could have facilitated the increases in leaf N~f~ in Free seedlings, but this effect is unknown.
 Soil N also declined evenly across all treatments, providing no clear evidence for decreased supply between Free seedlings and seedlings in containers.
 In these already low fertility soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength.
-Although no clear feedback could be determined between the available soil N pool and decreases in leaf N~f~, the effects of belowground sink limitation on *A*~n~ of seedlings in containers was evident throughout the experiment.
+Although no clear feedback could be determined between the soil N pool and decreases in leaf N~f~, the effects of belowground sink limitation on *A*~sat~ of seedlings in containers was evident throughout the experiment.
 
@@
 The feedback inhibition of *A*~n~ from starch accumulation has been proposed, yet it is still not known whether there is a starch threshold that triggers the down-regulation process [@nebauer2011photosynthesis].
-Here, declines in *A*~max~ were correlated with higher starch content throughout the experiment.
+Here, declines in *A*~mass~ were correlated with higher starch content throughout the experiment.
 These results agree with a study on a deciduous conifer by Equiza *et al.* [-@equiza2006photosynthetic] where photosynthetic downregulation from reduced sink strength was correlated with starch content.
@@
 We use a simple approach to estimate cumulative seedling C gain with measured reductions in leaf *A*~n~ , via soil volume effects.
-Although reductions in both *A*~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter *et al.* [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth.
-As estimated whole-plant C use efficiency was decreased in seedlings with belowground sink limitation, this suggests that other components of the C balance were affected.
+Although reductions in both *A*~max~ and biomass were correlated among treatments, as hypothesized by Poorter *et al.* [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth.
+As estimated whole-plant C use efficiency was decreased in containerized seedlings, this suggests that other components of the C balance were affected.
 These results are especially noteworthy for process-based growth models that parameterize CUE, tissue respiration and C allocation as fixed processes.
@@
 Empirical values reflect the mean (&pm; 1 standard error) for each treatment.
-Seedling mass, SRL, and fine root length density (FRLD) values are from final harvest.
+Seedling mass, leaf area, SRL, and fine root length density (FRLD) values are from final harvest.
 Values of SLA~f~, leaf starch, leaf sugars and leaf N~f~ represent overall means across measurement campaigns (n=6).
@@
                     "Seedling mass (g)", 
+                    "Leaf area (m^2^)",
                     "SLA~f~ (m^2^ kg^-1^)",

### 2017-02-07 manuscript/editor_response_tree_physiology.Rmd
editors response comments made

@@
 Particularly in the discussion we have clarified the nature of the effect type, where soil volume effects have often been over-emphasized.
-We agree that the stats are strongly influenced by the Free seedling, but this is also representative of the observed effects of root restirction on *A*~sat~, TNC and leaf N across all containers throughout all measurement campaigns.
+We agree that the stats are strongly influenced by the Free seedling, but this is also representative of the observed effects of root restriction on *A*~sat~, TNC and leaf N across all containers throughout all measurement campaigns.
 As the impacts of root restriction and poor quality soil impacted were evident across all treatments
-We feel that addressing individual effects of specific volume treatments, or combining soil volume treament effects, would overly complicate the paper and would not improve our intrepretation of the results.
+We feel that addressing individual effects of specific volume treatments, or combining soil volume treatment effects, would overly complicate the paper and would not improve our interpretation of the results.
 
@@
 *Response*: The editor makes several good points here.
-We have re-written the equation to better descibe the way daily total leaf net C gain (*P*~day~) was calculated.
+We have re-written the equation to better describe the way daily total leaf net C gain (*P*~day~) was calculated.
 We have also removed the statement "Leaf respiration is included in the calculation of *P*." and added a accurate description of how the area based respiration component was calculated at each 15 minute interval to then model leaf level net photosynthesis rates.
@@
 With a comment #6 we have now clearly defined the "total net leaf C gain term".
-As the edigor points out there are several places where leaf *A*~n~ is discussed inappropriately, especially in the discussion.
+As the editor points out there are several places where leaf *A*~n~ is discussed inappropriately, especially in the discussion.
 Throughout the manuscript we have revised use of terms for C gain to accurately reflect either measured photosynthesis rates (*A*~sat~), leaf level rates of net photosynthesis (*A*~n~) or modelled cumulative total net leaf C gain (*P*~day~).
@@
 \
-*Response*: 
+*Response*: We have revised this statement to make the point that reductions in measured *A*~sat~ and seedling allometry occurred simultaneosly during early measurement campaigns, and these reductions where sustained throughout the experiement.
+
 \
@@
 *Response*: editorial change made.  Changed *A*~n~ to *A*~sat (measured values).
+
 \
@@
 *Response*: We have corrected *A*~n~ to *A*~mass~, which is reported in the results section.
+
 \
@@
 \
-*Response*: We agree with the editor. We have changd this sentence to give a quantative description of root N content differences between roots of Free seedlings and seedlings in containers (+15 %). 
+*Response*: We agree with the editor.
+We have changed this sentence to give a quantitative description of root N content differences between roots of Free seedlings and seedlings in containers (+15 %).
 \
@@
 There is convincing evidence that nutrient uptake was negatively affected in this experiment but the mechanism is yet unidentified.
-Understanding the processes by which belowground sink manipulation manifests belowground will be important for future expereiments using local soils.
-We hope that this dataset and experimental design can aid in future experiments to further investigate the mecanisms underpinning belowground sink limitation.
+Understanding the processes by which belowground sink manipulation manifests belowground will be important for future experiments using local soils.
+We hope that this data-set and experimental design can aid in future experiments to further investigate the mechanisms underpinning belowground sink limitation.
 
@@
 \
-*Response*: We have corrected this statment in the discussion to more accurately reflect the observed results.
+*Response*: We have corrected this statement in the discussion to more accurately reflect the observed results.
 
@@
 *Response*: We have added both measured harvested leaf area and *A*~sat~ into Table 1 and 3, respectively.
-Both *A*~sat~ and leaf area were significantly reduced in seedings lin containers compared to the free seedlings.
+Both *A*~sat~ and leaf area were significantly reduced in seedlings in containers compared to the free seedlings.
+Leaf *A*~n~ was also replaced with "photosynthetic parameters".
 

### 2017-02-07 manuscript/manuscript_pve_editor.Rmd
editors response comments made

@@
 \
-Most current models of plant growth are based on the physical principle of mass balance: C entering the plant through net photosynthesis must be balanced by C allocation to growth and storage and C losses such as respiration, root exudation, volatile organic compounds and tissue turnover.
+Most current models of plant growth are based on the physical principle of mass balance: C entering the plant through net photosynthesis must be balanced by C allocation to growth and storage and C losses including respiration, root exudation, volatile organic compounds and tissue turnover.
 Plant growth is thus predicted as the outcome of the processes of photosynthesis, C allocation and C loss.
@@
 *R* was logged 5 times for each leaf after CO~2~ and water vapour flux values stabilized in the conifer chamber.
-Reported values of *R* are standardized rates at 25 &deg;C using a *Q*~10~ value (1.86) developed for these seedlings in a separate experiment (Drake *et al.* unpublished).
+Reported values of *R* are standardized rates at 25 &deg;C using a *Q*~10~ value (1.86) developed for these seedlings in a separate experiment.
 Leaf area and dry mass were recorded for each leaf during gas exchange campaigns.
@@
 (1)
-$$G(t) = \sigma LP_{day}$$
+$$G(t) =  L \sigma P_{day}$$
 
-where $\sigma$ is a self-shading parameter, *L* is modelled total plant leaf area (m^2^), and  *P*~day~ is the net daily C assimilation per unit leaf area (g C m^-2).
+where *L* is modelled total plant leaf area (m^2^), $\sigma$ is a self-shading parameter and  *P*~day~ is the net daily C assimilation per unit leaf area (g C m^-2^).
 
@@
 *R*~dark~ was was estimated using Eq.
-(2) from @atkin2005response, which was parameterized with a mean reference empircal measurement for each treatment, a Q~10~ value of 1.86 from a seperate experiment using the same tube stock seedlings, a reference air temperature and air temperatures at each time step.
+(2) from @atkin2005response, which was parameterized with a mean reference empircal measurement for each treatment, a Q~10~ value of 1.86, a reference air temperature for each treatment and air temperatures at each time step.
 
@@
 Methods of the coupled leaf gas exchange model are also described in Duursma *et al.* [-@duursma2014peaked].
-Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A*~n~ rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
+Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, net leaf photosynthesis rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
 *P*~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
@@
 \
-We used modelled C gain  to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.
+We used modelled C gain  to test the hypothesis that the effects of belowground sink limitation on rates of leaf photosynthesis were sufficient to accurately predict overall seedling biomass production after 120 days.
 Cumulative net leaf C gain for each treatment was equal to the sum of each value of *P* over 120 days and final seedling C was assumed to equal half of the final dry mass for observed seedlings.
@@
 *A*~mass~  was also lower when leaf starch was high as higher leaf N~f~ often did not coincide with high leaf starch (Figure `r achemfig`b).
-Overall, *A*~max~ was positively correlated with final harvest biomass across all seedlings (*P* < 0.001).
 
@@
 We found a strong reduction of growth in containerized plants.
-Leaf *A*~sat~ was also reduced, but this reduction was insufficient to fully explain the reduction in growth, implying that components such as non-leaf respiratory losses were also likely affected.
+Leaf *A*~sat~ was also reduced, but reductions in net leaf photosynthesis rates were insufficient to fully explain the reduction in growth, implying that components such as non-leaf respiratory losses were also likely affected.
 
@@
 \
-Decreases in *A*~sat~ occurred simultaneously with reductions of growth of seedlings in containers.
+Decreases in *A*~sat~ occurred simultaneously with reductions of height, diameter and leaf area of seedlings in containers throughout the duration of the experiment.
 This observation initially suggests that sink limitation may be driving the down regulation of photosynthesis, and thus growth.
@@
 These results agree with a study on a deciduous conifer by Equiza *et al.* [-@equiza2006photosynthetic] where photosynthetic downregulation from reduced sink strength was correlated with starch content.
-As starch content in leaves of plants grown in the smallest containers was nearly double that of Free seedlings in our study, this suggests the response of *A*~n~ to sink inhibition was regulated by this accumulation, as hypothesized.
+As starch content in leaves of plants grown in the smallest containers was nearly double that of Free seedlings in our study, this suggests the response of *A*~sat~ to sink inhibition was regulated by this accumulation, as hypothesized.
 Overall, it is likely that both nutrient limitation and reduced sink strength played a role in observed photosynthetic down regulation, but future studies are needed to identify the specific mechanisms which prompted these feedbacks.
@@
 ##Do reductions in photosynthesis explain reductions in seedling growth?
-We use a simple approach to estimate cumulative seedling C gain with measured reductions in leaf *A*~n~ , via soil volume effects.
+We use a simple approach to estimate cumulative seedling C gain with measured reductions in leaf photosynthetic parameters, via soil volume effects.
 Although reductions in both *A*~max~ and biomass were correlated among treatments, as hypothesized by Poorter *et al.* [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth.

### 2017-02-08 manuscript/editor_response_tree_physiology.Rmd
editor response finished and sent to Remko

@@
 
+\
+\
 We are grateful for the opportunity to resubmit our manuscript.
@@
 
+\
 - *Comment: 1.
@@
 And it seems that the latter is dominating and the clear relations with rooting volume are often missing...
-ignoring this later treatment may depply change your way of interpreting the results.
+ignoring this later treatment may deeply change your way of interpreting the results.
 Even the stats are strongly influenced by this treatment (effect on residual error for example).*
@@
 *Response*: We agree with the editor's comments that the effects of soil volume have not been properly accounted for in several places in the manuscript.
-Particularly in the discussion we have clarified the nature of the effect type, where soil volume effects have often been over-emphasized.
+Particularly in the discussion we have clarified the nature of the effect type, where soil volume effects were often been over-emphasized.
 We agree that the stats are strongly influenced by the Free seedling, but this is also representative of the observed effects of root restriction on *A*~sat~, TNC and leaf N across all containers throughout all measurement campaigns.
-As the impacts of root restriction and poor quality soil impacted were evident across all treatments
-We feel that addressing individual effects of specific volume treatments, or combining soil volume treatment effects, would overly complicate the paper and would not improve our interpretation of the results.
+We feel that addressing individual effects of specific volume treatments would overly complicate the paper and combining all soil volume treatment effects would not improve our interpretation of the results.
 
@@
 We have re-written the equation to better describe the way daily total leaf net C gain (*P*~day~) was calculated.
-We have also removed the statement "Leaf respiration is included in the calculation of *P*." and added a accurate description of how the area based respiration component was calculated at each 15 minute interval to then model leaf level net photosynthesis rates.
+We have also removed the statement "Leaf respiration is included in the calculation of *P*." and added a accurate description of how the area based respiration component was calculated at each 15 minute interval in the modelling of leaf net photosynthesis rates.
 
 \
-- *Comment: 7. L264: How do simulated An values fit with measured Asat?*
+- *Comment: 7. L264: How do simulated An values fit with measured *A*~sat~?*
 
 \
-*Response*:
+*Response*: It is difficult to accurately compare spot measurements of *A*~sat~ at saturating light inside the gas exchange cuvette with modelled values of *A*~n~ that are estimated over continually fluctuating meteorological conditions over 120 days.
+With simple modelling exercise, using Licor conditions and measured photosynthetic parameters the estimated rates are slightly higher than observed rates of *A*~sat~.
+Importantly, this does not effect the overall patterns of decreased CUE in containerized seedlings.
 
@@
 *Response*: We agree with each of the editors points here.
-With a comment #6 we have now clearly defined the "total net leaf C gain term".
+With comment #6 we have now clearly defined the "total net leaf C gain term".
 As the editor points out there are several places where leaf *A*~n~ is discussed inappropriately, especially in the discussion.
@@
 \
-- *Comment: 11. L349-350: These sentences are confusing: does the first sentence refer to Amax on a leaf area basis. Please clarify.*
+- *Comment: 11. L349-350: These sentences are confusing: does the first sentence refer to *A*~max~ on a leaf area basis. Please clarify.*
 
@@
 \
-- *Comment: 12. L351: I will not say that Amass is highly correlated with both leaf Nf and leaf starch, when it only accounts for 28% and 11% of the total variations.*
+- *Comment: 12. L351: I will not say that A~mass~ is highly correlated with both leaf N~f~ and leaf starch, when it only accounts for 28% and 11% of the total variations.*
 
@@
 The correlation is driven by the free rooting values.
-Variation in Amax across rooting volume does not reflect those of biomass in the last point is removed.
+Variation in A~mass~ across rooting volume does not reflect those of biomass in the last point is removed.
 It means that the co-variation is not so much driven by soil volume.
@@
 \
-- *Comment: 15. L394: Leaf An (an leaf area basis) or whole plant C gain? Please clarify.*
+- *Comment: 15. L394: Leaf A~n~ (an leaf area basis) or whole plant C gain? Please clarify.*
 
 \
-*Response*: editorial change made.  Change *A*~n~ to *A*~sat (measured values)
+*Response*: editorial change made.  Change *A*~n~ to *A*~sat~ (measured values)
 
@@
 \
-- *Comment: 17. L410: this is not true. There is large reduction in biomass related to container size, but not so much effect of container size on Amax.*
+- *Comment: 17. L410: this is not true. There is large reduction in biomass related to container size, but not so much effect of container size on A~max~.*
 
 \
-*Response*: We have revised this statement to make the point that reductions in measured *A*~sat~ and seedling allometry occurred simultaneosly during early measurement campaigns, and these reductions where sustained throughout the experiement.
+*Response*: We have revised this statement to make the point that reductions in measured *A*~sat~ and seedling allometry occurred simultaneously during early measurement campaigns, and these reductions where sustained throughout the experiment.
 
 \
-- *Comment: 18. L413: what is An here? Leaf area or whole plant based?*
+- *Comment: 18. L413: what is A~n~ here? Leaf area or whole plant based?*
 
 \
-*Response*: editorial change made.  Changed *A*~n~ to *A*~sat (measured values).
+*Response*: editorial change made.  Changed *A*~n~ to *A*~sat~ (measured values).
 
 \
-- *Comment: 19. L430-431. Correlation between leaf N and An (what is it?) has not been shown in the result sections.*
+- *Comment: 19. L430-431. Correlation between leaf N and A~n~ (what is it?) has not been shown in the result sections.*
 
@@
 We have changed this sentence to give a quantitative description of root N content differences between roots of Free seedlings and seedlings in containers (+15 %).
+
 \
@@
 - *Comment: 22.
-L443: again, what is An?
-And please show us the evidence of a sink limitation on An of seedlings in container.
+L443: again, what is A~n~?
+And please show us the evidence of a sink limitation on A~n~ of seedlings in container.
 There is not so much effect of container size on leaf photosynthetic parameter in Table 3*
@@
 *Response*: editorial change made.
-Changed *A*~n~ to *A*~sat (measured values).
-As with comment #10, *A*~sat values are added in Table 3 to show reductions in measured leaf level photosynthesis in containerized seedlings.
+Changed *A*~n~ to *A*~sat~ (measured values).
+As with comment #10, *A*~sat~ values are also added in Table 3 to show reductions in measured leaf level photosynthesis in containerized seedlings.
 
@@
 - *Comment: 23.
-L449: I am not convinced that the decline in Amax is correlated with higher starch content, at least not across the different container size.
+L449: I am not convinced that the decline in A~max~ is correlated with higher starch content, at least not across the different container size.
 This is not really an effect of rooting volume but again container versus free soil.*
@@
 L483: There is no reduction in leaf photosynthesis due to the restricted soil volume, according to the data you reported in Table 3.
-Make clear what is leaf An.
+Make clear what is leaf A~n~.
 The reduction in whole plant assimilation may mainly be due to a reduction in plant leaf area, which in fact is only evident for the largest soil volume.
@@
 - *Comment: 26.
-L477: L483-484: I disagree that reductions in Amax and biomass were strongly correlated.
+L477: L483-484: I disagree that reductions in A~max~ and biomass were strongly correlated.
 The correlation is driven by high value of the free soil.

### 2017-02-08 manuscript/manuscript_pve_editor.Rmd
editor response finished and sent to Remko

@@
 # Set Flag to include figures in text or not.
-includeFigs <- FALSE
+includeFigs <- TRUE
 ```
@@
 *R*~dark~ was was estimated using Eq.
-(2) from @atkin2005response, which was parameterized with a mean reference empircal measurement for each treatment, a Q~10~ value of 1.86, a reference air temperature for each treatment and air temperatures at each time step.
+(2) from @atkin2005response, which was parameterized with a mean reference empirical measurement for each treatment, a Q~10~ value of 1.86, a reference air temperature for each treatment and air temperatures at each time step.
 

### 2017-02-08 clean Scripts/AsatAleaf.R

@@ -3,6 +3,26 @@
 
 source("functions and packages/startscripts.R")
 
+#Read in spot A measurements and merge plot design
+#read in plot design and harvest data
+plotsumm <- read.csv("raw data/plot_summary.csv")
+plotsumm$ID <- paste(plotsumm$plot, plotsumm$pot, sep = "-")
+
+#read in gas exchange master file, all dates
+gasexchange <- read.csv("raw data/AsatAmax_master.csv")
+  gasexchange$Date <- as.Date(gasexchange$Date)
+  gasexchange$ID <- paste(gasexchange$plot, gasexchange$pot, sep = "-")
+
+PS <- merge(plotsumm, subset(gasexchange, select = c("campaign", "ID", "CO2", "Photo", "RH_S")))
+  PS$type <- factor(ifelse (PS$CO2 == "400", "Asat", "Amax"))
+
+#run function to add campaign date
+PS <- add_campaign_date(PS)
+
+asat <- PS[PS$CO2 == "400",]
+##get rh values from licor master
+rh <- asat[, "RH_S"]
+
 #READ DATA, calculated data for A parameters
 
 #generated jmax and vcmax
@@ -38,10 +58,10 @@ A_model <- merge(A_model, g1_agg, by="volume")
 #now run the model (includes pred Rdark from crouseq10, and gs parameters modelled from spot measurements)
 
 #convert RH to VPD
-A_model$VPD <- RHtoVPD(A_model$RH, A_model$temp, Pa=101)
+VPD_obs <- RHtoVPD(rh, 25, Pa=101)
 
 #model, should return the aleaf for every 15 minutes. (will retrun Aleaf at 15min interval)
-A_sat_pred <- Photosyn(RH=70,Ca=400, PPFD=1800, Tleaf=25, 
+A_sat_pred <- Photosyn(VPD=1.06,Ca=400, PPFD=1800, Tleaf=25, 
                    Jmax=A_model$Jmax.mean, Vcmax=A_model$Vcmax.mean, Rd=A_model$Rd_pred2, g1=A_model$g1_date)
 
 
@@ -52,3 +72,26 @@ Asat <- A_means[, c(1, 4)]
 
 Acompare <- cbind(Asat, A_sat_pred[,2])
 names(Acompare)[3] <- "Aleaf"
+
+
+require(nlme)
+library(multcomp)
+
+#relevel to free to evaluate container effect  
[…]

### 2017-02-08 master_scripts/cuefig.R

@@ -16,24 +16,24 @@ harvestC <- merge(mass_actual[,1:2], cue)
 
 #plot-----------------------------------------------------------------------------------------
 par(mar=c(5,5,2,2), cex.axis=0.8, las=1)
-plot(massC/tdc_net.sum ~ volume, data=harvestC, ylim=c(.25, .45), xaxt='n', cex=1.5, pch=pchs, col=cols, 
+plot(massC/(tdc_net.sum) ~ volume, data=harvestC, ylim=c(.25, .45), xaxt='n', cex=1.5, pch=pchs, col=cols, 
        ylab="Seedling Mass (g C) / \nModelled Total Net C Gain (g C)", 
        xlab="Soil Volume (l)")
     axis(1, at=c(5,10,15,20,25,35,40), labels=c(5,10,15,20,25,35,"Free"))
 
   
 ##results section----------------------------------------------------------------------------------------
-mean(harvestC$tdc_net.sum[1:6])
-se(harvestC$tdc_net.sum[1:6])
-
-harvestC$tdc_net.sum[7]
-  
-leftoverC <- with(harvestC, (tdc_net.sum-massC)/tdc_net.sum)
-mean(leftoverC[1:6])
-se(leftoverC[1:6])
-leftoverC[7]
-  
-cue_dat <- with(harvestC, massC/tdc_net.sum)
-mean(cue_dat[1:6])
-se(cue_dat[1:6])
-cue_dat[7]
+# mean(harvestC$tdc_net.sum[1:6])
+# se(harvestC$tdc_net.sum[1:6])
+# 
+# harvestC$tdc_net.sum[7]
+#   
+# leftoverC <- with(harvestC, (tdc_net.sum-massC)/tdc_net.sum)
+# mean(leftoverC[1:6])
+# se(leftoverC[1:6])
+# leftoverC[7]
+#   
+# cue_dat <- with(harvestC, massC/tdc_net.sum)
+# mean(cue_dat[1:6])
+# se(cue_dat[1:6])
+# cue_dat[7]

### 2017-02-15 manuscript/editor_response_tree_physiology.Rmd
final edits of tree phys manuscript.  ready to resumbit.

@@
 *Response*: We agree with the editor's comments that the effects of soil volume have not been properly accounted for in several places in the manuscript.
-Particularly in the discussion we have clarified the nature of the effect type, where soil volume effects were often been over-emphasized.
-We agree that the stats are strongly influenced by the Free seedling, but this is also representative of the observed effects of root restriction on *A*~sat~, TNC and leaf N across all containers throughout all measurement campaigns.
+In the revision, we have clarified the nature of the effect type, where soil volume effects were often over-emphasized.
+We agree that the stats are strongly influenced by the Free seedling.
+However, relationships with rooting volume that develop through time were missing because root restriction affected *A*~sat~, TNC and leaf N immediately for newly produced leaves across all containers and then throughout all measurement campaigns.
 We feel that addressing individual effects of specific volume treatments would overly complicate the paper and combining all soil volume treatment effects would not improve our interpretation of the results.
@@
 \
-*Response*: Editorial change made.  We have included more examples of C losses beyond respiration.  The rest of the paragraph is also adjusted to discuss "C loss" as a more general inclusive term.
+*Response*: We have now included more examples of C losses beyond respiration. The rest of the paragraph is also adjusted to discuss "C loss" as a more general inclusive term.
 
@@
 We only have C and N data for leaves and roots.
-We therefore use the 50% assumption to convert dry seedling biomass to final seedling C.
+We therefore use the 50% assumption for wood to convert dry seedling biomass to final seedling C.
 
@@
 We have re-written the equation to better describe the way daily total leaf net C gain (*P*~day~) was calculated.
-We have also removed the statement "Leaf respiration is included in the calculation of *P*." and added a accurate description of how the area based respiration component was calculated at each 15 minute interval in the modelling of leaf net photosynthesis rates.
+We have also removed the statement "Leaf respiration is included in the calculation of *P*." and added a more accurate description of how the area based respiration component was calculated at each 15 minute interval in the modelling of leaf net photosynthesis rates.
+Most importantly, the methods used to calculate total carbon uptake were correct, only the description of the methods was unclear.
 
@@
 *Response*: It is difficult to accurately compare spot measurements of *A*~sat~ at saturating light inside the gas exchange cuvette with modelled values of *A*~n~ that are estimated over continually fluctuating meteorological conditions over 120 days.
-With simple modelling exercise, using Licor conditions and measured photosynthetic parameters the estimated rates are slightly higher than observed rates of *A*~sat~.
+With a simple modelling exercise, using Licor conditions and measured photosynthetic parameters the estimated rates are comparable, and only slightly higher than observed rates of *A*~sat~.
 Importantly, this does not effect the overall patterns of decreased CUE in containerized seedlings.
@@
 With comment #6 we have now clearly defined the "total net leaf C gain term".
-As the editor points out there are several places where leaf *A*~n~ is discussed inappropriately, especially in the discussion.
-Throughout the manuscript we have revised use of terms for C gain to accurately reflect either measured photosynthesis rates (*A*~sat~), leaf level rates of net photosynthesis (*A*~n~) or modelled cumulative total net leaf C gain (*P*~day~).
+As the editor points out there are several places where leaf *A*~n~ was used inappropriately, especially in the discussion.
+Throughout the manuscript we have revised use of terms for C gain to accurately reflect either measured photosynthesis rates at saturating light (*A*~sat~), leaf level rates of net photosynthesis at prevailing conditions (*A*~n~) or modelled total net leaf C gain (*P*~day~).
 
@@
 *Response*: We agree with the editor here.
-We have introduced a new term *A*~mass~ to represent *A*~max~ on a mass basis.
+We have introduced a new term (*A*~mass~) to represent *A*~max~ on a mass basis.
 This should help easily distinguish between the two variables in the text and is now consistent with Figure 4.
@@
 \
-*Response*: This point was overlooked by the authors. This statement has been removed from the results section.
+*Response*: This statement has been removed from the results section.
 
@@
 \
-*Response*: editorial change made.  Change *A*~n~ to *A*~sat~ (measured values)
+*Response*: editorial change made.  Change *A*~n~ to *A*~sat~ (measured values at saturating light)
 
@@
 *Response*: We agree with the editor's comments.
-There is convincing evidence that nutrient uptake was negatively affected in this experiment but the mechanism is yet unidentified.
-Understanding the processes by which belowground sink manipulation manifests belowground will be important for future experiments using local soils.
-We hope that this data-set and experimental design can aid in future experiments to further investigate the mechanisms underpinning belowground sink limitation.
+There is convincing evidence that nutrient uptake was negatively affected in this experiment but we lack any data on mineralization rate.
+Unfortunately we also did not measure available P, or any other detailed description of the nutrient cycle.
+Clearly such measurements were outside the scope of the study.
+We hope that this data set and experimental design can aid in future experiments to further investigate the mechanisms underpinning belowground sink limitation.
 
@@
 *Response*: editorial change made.
-Changed *A*~n~ to *A*~sat~ (measured values).
+Changed *A*~n~ to *A*~sat~ (measured values at saturating light).
 As with comment #10, *A*~sat~ values are also added in Table 3 to show reductions in measured leaf level photosynthesis in containerized seedlings.

### 2017-02-15 manuscript/manuscript_pve_editor.Rmd
final edits of tree phys manuscript.  ready to resumbit.

@@
 
-where *L* is modelled total plant leaf area (m^2^), $\sigma$ is a self-shading parameter and  *P*~day~ is the net daily C assimilation per unit leaf area (g C m^-2^).
+where *L* is total plant leaf area (m^2^), $\sigma$ is a self-shading parameter and *P*~day~ is the net daily C assimilation per unit leaf area, accounting for leaf respiratory losses (g C m^-2^).
 

### 2017-02-27 manuscript/editor_response2_tree_physiology.Rmd
started revision of editor comments #2

---
output:
  word_document:
    reference_docx: manuscriptstyle_pce2.docx
  pdf_document: default
  html_document:
    number_sections: yes
---

```{r, results='asis', echo=FALSE, warning=FALSE}
library(knitr)
opts_knit$set(root.dir = '../')
```

Prof Daniel Epron
\
Editor
\
Tree Physiology

\
\
We are grateful for the opportunity to resubmit our manuscript. We thank the editor for providing insightful comments to improve our manuscript. We have responded in detail to each comment, which has improved the overall quality of the manuscript. Below, we have itemized our response to each comment from the editor.

\
- *Comment: 1. The abstract should be revised according to the main document. For example, there is no reduction in whole-plant C use efficiency (CUE) with container size, just a difference between container versus Free rooting.*

\
*Response*: We have corrected the CUE findings in the abstract to reference the decrease of CUE between Free seedlings and seedlings in containers, not of container size.

\
- *Comment: 2. Increasing rather than decreasing C sink activity is another approach that you did not mentioned in your introduction.*
I was done on rubber tree by comparing trees that are tapped for latex production with trees that are not tapped. You may have a look on the two following papers and see whether or not it can be included in your introduction.
Silpi, U., Lacointe, A., Kasempsap, P., Thanysawanyangkura, S., Chantuma, P., Gohet, E., Musigamart, N., Clément, A., Améglio, T., Thaler, P., 2007. Carbohydrate reserves as a competing sink: evidence from tapping rubber trees. Tree Physiology 27, 881–889.

\
*Response*:

Kanpanon, N., Kasemsap, P., Thaler, P., Kositsup, B., Gay, F., Lacote, R., Epron, D., 2015. Carbon isotope composition of latex does not reflect temporal variations of photosynthetic carbon isotope discrimination in rubber trees (Hevea brasiliensis). Tree Physiology 35, 1166–1175.

\
- *Comment: 3. g1 is not generated using only gs values. Provide more details please.*

\
*Response*:

\
- *Comment: 4. The Q10 relation (eqn 2) is much older than Atkin 2005. Please remove this useless reference.*

\
*Response*:

\
- *Comment: 5. L267: misusing punctuations*

\
*Response*:

\
- *Comment: 6. L275: Recall us here what "An" is.*

\
*Response*:

\
- *Comment: 7. L294: seedling C biomass (add C for clarity)*

\
*Response*: editorial change made

\
- *Comment:  8. L249-294: be consistent when using "P" or "Pday"*

\
*Response*: *P* corrected to *P*~day~ throughout this entire subsection.

\
- *Comment: 9. L300: "Amass" should be introduced before*

\
*Response*:

\
- *Comment: 10. L321-322 :"differences were driven mainly by the largest container and the Free seedling treatments". This is not what we can see on Table 1, at least for leaf area. Can final height and diameter added in this table, with their stats?*

\
*Response*: We agree that this result cannot be seen from clearly from Table 1.  However, it can be seen easily from Figure 1. Instead of increasing the size of an already large table, I have referenced Figure 1 at then end of this statement for simplicity.

\
- *Comment:11. L370-371: g1 "was lowest in the Free seedling treatment and was marginally different across soil volume treatments". This is not so clear in Table 3. it seems that larger soil volume are more similar to Free than to smaller soil volume.*

\
*Response*: Reworded the desciprtion of the findings with the g~1~ parameter. "The *g*~1~ parameter ... was highest in the smaller containers and decreased in larger containers and the Free seedling treatment"

\
- *Comment: 12. L386: replace "-" by "versus" or "vs" or anything else to avoid confusion*

\
*Response*: changed "-" to vs

\
- *Comment: 13. L430: uncorrect "Aat"*

\
*Response*: corrected to *A*~sat~

\
- *Comment: 14. L468-469: a reference is needed for "functional partitioning of ..."*

\
*Response*:

\
- *Comment: 15. L487 recall us again here what "An" is*

\
*Response*:

\
- *Comment: 17. L512: is "however" really needed?*

\
*Response*: removed "however"

\
- *Comment: 17. Fig3c: this is not plant total mass*

\
*Response*:

### 2017-02-27 manuscript/manuscript_pve_editor.Rmd
manuscript resubmitted
started revision of editor comments #2

@@
 After 120 days, harvested biomass of Free seedlings was on average 84 % higher than seedlings in containers, but biomass distribution in leaves, stems and roots was not different.
-However, the reduction in net leaf photosynthesis over the growth period was insufficient to explain the reduction in growth, so that we also observed an apparent reduction in whole-plant C use efficiency (CUE) with container size.
+However, the reduction in net leaf photosynthesis over the growth period was insufficient to explain the reduction in growth, so that we also observed an apparent reduction in whole-plant C use efficiency (CUE) between Free seedlings and seedlings in containers.
 Our results show that sink limitation affects plant growth through feedbacks to both photosynthesis and CUE.
@@
 \
-*P* was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *g*~1~ and *R*~dark~) for each treatment and meteorological data from an onsite weather station.
+*P*~day~  was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *g*~1~ and *R*~dark~) for each treatment and meteorological data from an onsite weather station.
 Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above).
@@
 *P*~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h.
-This resulted in 120 unique values of *P* for each soil volume treatment, one value for each day of the experiment.
+This resulted in 120 unique values of *P*~day~  for each soil volume treatment, one value for each day of the experiment.
 Thus, each daily time step for model runs included a value of *P*~day~ that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
@@
 We used modelled C gain  to test the hypothesis that the effects of belowground sink limitation on rates of leaf photosynthesis were sufficient to accurately predict overall seedling biomass production after 120 days.
-Cumulative net leaf C gain for each treatment was equal to the sum of each value of *P* over 120 days and final seedling C was assumed to equal half of the final dry mass for observed seedlings.
-We then compared seedling C use efficiency (CUE) across treatments, as the proportion of modelled cumulative net leaf C gain allocated to observed seedling biomass.
+Cumulative net leaf C gain for each treatment was equal to the sum of each value of *P*~day~ over 120 days and final seedling C was assumed to equal half of the final dry mass for observed seedlings.
+We then compared seedling C use efficiency (CUE) across treatments, as the proportion of modelled cumulative net leaf C gain allocated to observed seedling C biomass.
 
@@
 Increases in both final stem diameter and cumulative leaf area (both *P* < 0.001) were found with increasing soil volume.
-We did not find a continuous effect of container size; rather, plant size was similar among smaller containers, and differences were driven mainly by the largest container and the Free seedling treatments.
+We did not find a continuous effect of container size; rather, plant size was similar among smaller containers, and differences were driven mainly by the largest container and the Free seedling treatments (Figure `r allomfig`).
 
@@
 Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`).
-The *g*~1~ parameter, generated for each seedling from the Medlyn *et al.* [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the Free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab3`).
+The *g*~1~ parameter, generated for each seedling from the Medlyn *et al.* [-@medlyn2011reconciling] optimal stomatal conductance model, was highest in the smaller containers and decreased in larger containers and the Free seedling treatment (Table `r pvetab3`).
 
@@
 Modelled cumulative net leaf C gain over 120 days varied three-fold across containers sizes (Table `r pvetab1`).
-The Free seedling control had five-fold greater modelled total C gain than the average of container treatments (213.6 - 42.7&pm;8.2 g C).
+The Free seedling control had five-fold greater modelled total C gain than the average of container treatments (213.6 vs 42.7&pm;8.2 g C).
 For seedlings in containers, an average of 67 &pm;0.01 % of modelled C gain was not allocated to observed biomass, compared to 59.2 % for the Free seedling control.
@@
 Similarly, severe reductions in leaf photosynthesis in coffee plants were not attributed to impacts of container size on leaf water potentials or *g*~s~ [@ronchi2006growth].
-It is thus likely that reductions in *A*~at~ of well-watered seedlings observed in our study of *E.
+It is thus likely that reductions in *A*~sat~ of well-watered seedlings observed in our study of *E.
 tereticornis* seedlings are not the result of limiting soil moisture availability.
@@
 Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A*~n~ and the fate of C allocated at the whole plant level to growth, respiration, exudation and C storage.
-However, the degree to which these mechanisms regulate the C available for growth will undoubtedly shift across different species and environmental conditions.
+The degree to which these mechanisms regulate the C available for growth will undoubtedly shift across different species and environmental conditions.
 

### 2017-03-02 manuscript/editor_response2_tree_physiology.Rmd
maunscript comment edits

@@
 \
-- *Comment: 2. Increasing rather than decreasing C sink activity is another approach that you did not mentioned in your introduction.*
-I was done on rubber tree by comparing trees that are tapped for latex production with trees that are not tapped.
-You may have a look on the two following papers and see whether or not it can be included in your introduction.
-Silpi, U., Lacointe, A., Kasempsap, P., Thanysawanyangkura, S., Chantuma, P., Gohet, E., Musigamart, N., Clément, A., Améglio, T., Thaler, P., 2007.
-Carbohydrate reserves as a competing sink: evidence from tapping rubber trees.
-Tree Physiology 27, 881–889.
+- *Comment: 2.
+Increasing rather than decreasing C sink activity is another approach that you did not mentioned in your introduction.
+It was done on rubber tree by comparing trees that are tapped for latex production with trees that are not tapped.
+You may have a look on the two following papers and see whether or not it can be included in your introduction.*
 
 \
-*Response*:
-
-Kanpanon, N., Kasemsap, P., Thaler, P., Kositsup, B., Gay, F., Lacote, R., Epron, D., 2015.
-Carbon isotope composition of latex does not reflect temporal variations of photosynthetic carbon isotope discrimination in rubber trees (Hevea brasiliensis).
-Tree Physiology 35, 1166–1175.
+*Response*: Although both studies with rubber trees are extremely interesting in terms of the dymanics of storage carbohyrdate accumluation and mobilization, they lack empirical data for photosynthesis rates and only speculate about the impacts on growth.
+I have choosen to not mention them in the introduction, as they are mostly out of context with discusssion of the effects of sink limitation on physiological processes and growth.
 
@@
 \
-*Response*:
+*Response*: We have corrected to this statement to include observed values of *g*~s~, *A*~sat (which includes C~a~ of 400) and vapor presssure deficit.
 
@@
 \
-*Response*:
+*Response*: Reference to Atkin has been removed.
 
@@
 \
-*Response*:
+*Response*: editorial change made
 
@@
 \
-*Response*:
+*Response*: We have now introducted the term *A*~mass~ in this section as it had not been previously described.
 
@@
 \
-*Response*: Reworded the desciprtion of the findings with the g~1~ parameter.
+*Response*: We have reworded the desciprtion of the findings with the g~1~ parameter.
 "The *g*~1~ parameter ...

### 2017-03-02 manuscript/manuscript_pve_editor.Rmd
maunscript comment edits

@@
 Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above).
-The *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values.
+The *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed values of *g*~s~, *A*~sat~ and vapour pressure deficit.
 *R*~dark~ was was estimated using Eq.
-(2) from @atkin2005response, which was parameterized with a mean reference empirical measurement for each treatment, a Q~10~ value of 1.86, a reference air temperature for each treatment and air temperatures at each time step.
+(2), which was parameterized with a mean reference empirical measurement for each treatment, a Q~10~ value of 1.86, a reference air temperature for each treatment and air temperatures at each time step.
 
@@
 $$R~dark~ = R_{ref}Q_{10}~^{(T-T_{ref})/10}$$
-Methods of the coupled leaf gas exchange model are also described in Duursma *et al.* [-@duursma2014peaked].
+Methods of the coupled leaf gas exchange model are also described in Duursma et al.
+[-@duursma2014peaked].
 Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, net leaf photosynthesis rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment.
@@
 Tukey's post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different.
-A linear mixed effect model of *A*~mass~ and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R.
+A linear mixed effect model of *A*~max~ on a mass basis (*A*~mass~) and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R.
 Explained variance (*R*^2^) of mixed models were computed as in @nakagawa2013general, in which the marginal *R*^2^ represents variance explained by fixed factors and the conditional *R*^2^ by both fixed and random factors.

### 2017-03-03 manuscript/editor_response2_tree_physiology.Rmd
finsihed editor comments#2

@@
 \
-*Response*:
+*Response*: corrected *A*~n~ to *P*~day~
 
@@
 \
-*Response*:
+*Response*: We have added two citations in relation to the functional balance hypothesis of plant biomass partitioning.
 
@@
 \
-*Response*:
+*Response*: We have replaced *A*~n~ with *P*~day~ as this sentence refers to total net seedling C gain.
 
@@
 \
-*Response*:
+*Response*: There was not an error here (caption).  However, "total plant leaf mass" was replaced with "total leaf mass" for simplicity.

### 2017-03-03 manuscript/manuscript_pve_editor.Rmd
finsihed editor comments#2

@@
 \
-It was further necessary to calculate a self-shading parameter ($\sigma$) when scaling leaf *A*~n~ with total plant leaf area.
+It was further necessary to calculate a self-shading parameter ($\sigma$) when scaling *P*~day~ with total plant leaf area.
 This was accomplished by utilizing 61 previously digitized *Eucalyptus* seedlings, covering 5 total species which include *E.
@@
 In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to Free seedlings, once ontogenetic drift was taken into account (Figure `r allocfig`a,b).
-A conserved ratio of fine root mass to leaf mass was observed across all treatments, suggesting that seedlings maintained homeostasis with biomass partitioning instead of a functional partitioning response to optimize limiting soil resources.
+A conserved ratio of fine root mass to leaf mass was observed across all treatments, suggesting that seedlings maintained homeostasis with biomass partitioning instead of a functional partitioning response to optimize limiting soil resources [i.e.
+@davidson1969effect; @shipley2002balanced].
 
@@
 We use a simple approach to estimate cumulative seedling C gain with measured reductions in leaf photosynthetic parameters, via soil volume effects.
-Although reductions in both *A*~max~ and biomass were correlated among treatments, as hypothesized by Poorter *et al.* [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth.
+Although reductions in both *A*~max~ and biomass were correlated among treatments, as hypothesized by Poorter *et al.* [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *P*~day~ do not fully explain reduced seedling growth.
 As estimated whole-plant C use efficiency was decreased in containerized seedlings, this suggests that other components of the C balance were affected.
@@
 Lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment.
-(c) Total plant leaf mass as a function of fine root biomass with &pm; standard error.
+(c) Total leaf mass as a function of fine root biomass with &pm; standard error.
 The dashed line is a 1:1 line and the solid line represents the significant log-log model fit (*R*^2^ = 0.82) with equation: log(x) = -0.36 + 0.983 * log(y).

### 2017-03-05 manuscript/editor_response2_tree_physiology.Rmd
final edits to response#2

@@
 \
-*Response*: Although both studies with rubber trees are extremely interesting in terms of the dymanics of storage carbohyrdate accumluation and mobilization, they lack empirical data for photosynthesis rates and only speculate about the impacts on growth.
-I have choosen to not mention them in the introduction, as they are mostly out of context with discusssion of the effects of sink limitation on physiological processes and growth.
+*Response*: Although both studies with rubber trees are extremely interesting in terms of the dynamics of storage carbohydrate accumulation and mobilization, they lack empirical data for photosynthesis rates and only speculate about the impacts on growth.
+We have chosen to not mention them in the introduction, as they are mostly out of context with discussion of the effects of sink limitation on photosynthesis and growth.
 
@@
 \
-*Response*: We have corrected to this statement to include observed values of *g*~s~, *A*~sat (which includes C~a~ of 400) and vapor presssure deficit.
+*Response*: We have corrected to this statement to include observed values of *g*~s~, *A*~sat~ (which includes C~a~ of 400) and vapor pressure deficit.
 
@@
 \
-*Response*: Reference to Atkin has been removed.
+*Response*: Reference to Atkins has been removed.
 
@@
 \
-*Response*: We have now introducted the term *A*~mass~ in this section as it had not been previously described.
+*Response*: We have now introduced the term *A*~mass~ in this section as it had not been previously described.
 
@@
 \
-*Response*: We have reworded the desciprtion of the findings with the g~1~ parameter.
+*Response*: We have reworded the description of the findings with the g~1~ parameter.
 "The *g*~1~ parameter ...

### 2017-03-06 manuscript/manuscript_pve_editor.Rmd
minor edits, this version of manuscript was submitted to tree physiology

@@
 Inadequate rooting volume can decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root].
-In a comprehensive meta-analysis, Poorter *et al.* [-@poorter2012pot] demonstrated a large effect of container size on plant biomass accumulation.
+In a comprehensive meta-analysis, Poorter et al.
+[-@poorter2012pot] demonstrated a large effect of container size on plant biomass accumulation.
 Photosynthetic down-regulation is generally observed in these studies [e.g.
 @arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth].
-Poorter *et al.* [-@poorter2012pot] examined the components of relative growth rate and found the unit leaf rate to be most strongly affected by rooting volume.
+Poorter et al.
+[-@poorter2012pot] examined the components of relative growth rate and found the unit leaf rate to be most strongly affected by rooting volume.
 As unit leaf rate is correlated with *A*~n~, they concluded that down-regulation of *A*~n~ may best explain the effects of container size on biomass growth.
@@
 The *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed values of *g*~s~, *A*~sat~ and vapour pressure deficit.
-*R*~dark~ was was estimated using Eq.
+*R*~dark~ was estimated using Eq.
 (2), which was parameterized with a mean reference empirical measurement for each treatment, a Q~10~ value of 1.86, a reference air temperature for each treatment and air temperatures at each time step.
@@
 This was accomplished by utilizing 61 previously digitized *Eucalyptus* seedlings, covering 5 total species which include *E.
-tereticornis*, from Duursma *et al.* [-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
+tereticornis*, from Duursma et al.
+[-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure.
 Using the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*~n~, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf.
@@
 Increases in both final stem diameter and cumulative leaf area (both *P* < 0.001) were found with increasing soil volume.
-We did not find a continuous effect of container size; rather, plant size was similar among smaller containers, and differences were driven mainly by the largest container and the Free seedling treatments (Figure `r allomfig`).
+We did not find a continuous effect of container size; rather, plant size was similar among smaller containers, and differences were driven mainly by the largest containers and the Free seedling treatment (Figure `r allomfig`).
 
@@
 Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`).
-The *g*~1~ parameter, generated for each seedling from the Medlyn *et al.* [-@medlyn2011reconciling] optimal stomatal conductance model, was highest in the smaller containers and decreased in larger containers and the Free seedling treatment (Table `r pvetab3`).
+The *g*~1~ parameter, generated for each seedling from the Medlyn et al.
+[-@medlyn2011reconciling] optimal stomatal conductance model, was highest in the smaller containers and decreased in larger containers and the Free seedling treatment (Table `r pvetab3`).
 
@@
 Low growth rates led to large reductions in biomass in small containers, compared to freely rooted seedlings.
-We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, close to the 43 % reported in the meta-analysis by Poorter *et al.* [-@poorter2012pot].
+We analyzed the relationship between biomass growth and soil volume and found an increase of 34 % with a doubling of container volume, close to the 43 % reported in the meta-analysis by Poorter et al.
+[-@poorter2012pot].
 These growth reductions were expected, as the impedance of root growth can cause reductions in overall plant growth and activity [@mcconnaughay1991physical; @young1997mechanical].
@@
 Here, declines in *A*~mass~ were correlated with higher starch content throughout the experiment.
-These results agree with a study on a deciduous conifer by Equiza *et al.* [-@equiza2006photosynthetic] where photosynthetic downregulation from reduced sink strength was correlated with starch content.
+These results agree with a study on a deciduous conifer by Equiza et al.
+[-@equiza2006photosynthetic] where photosynthetic downregulation from reduced sink strength was correlated with starch content.
 As starch content in leaves of plants grown in the smallest containers was nearly double that of Free seedlings in our study, this suggests the response of *A*~sat~ to sink inhibition was regulated by this accumulation, as hypothesized.
@@
 Additionally, physical restriction of root proliferation could have impacted root development and morphology prior to shifts in mass partitioning.
-Although plants in containers have been shown to have different root morphology to field grown plants [@nesmith1998effect], increases in specific root length were detected in only one of the the soil volume treatments.
+Although plants in containers have been shown to have different root morphology to field grown plants [@nesmith1998effect], increases in specific root length were detected in only one of the soil volume treatments.
 The poor soil quality used in our experiment and root restriction, however, likely decreased the capacity of this morphological response to increase N uptake.
@@
 We use a simple approach to estimate cumulative seedling C gain with measured reductions in leaf photosynthetic parameters, via soil volume effects.
-Although reductions in both *A*~max~ and biomass were correlated among treatments, as hypothesized by Poorter *et al.* [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *P*~day~ do not fully explain reduced seedling growth.
+Although reductions in both *A*~max~ and biomass were correlated among treatments, as hypothesized by Poorter et al.
+[-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *P*~day~ do not fully explain reduced seedling growth.
 As estimated whole-plant C use efficiency was decreased in containerized seedlings, this suggests that other components of the C balance were affected.
@@
 # Acknowledgements
-We thank Burhan Amiji for his outstanding technical assistance. We would like to thank the many Hawkesbury Institute for the Environment staff and students who helped during the experimental harvest.
+We thank Burhan Amiji for his outstanding technical assistance.
+We would like to thank the many Hawkesbury Institute for the Environment staff and students who helped during the experimental harvest.
+The complete dataset can be downloaded from http://doi.org/10.4225/35/58b4eaa87c64d.
 
